### 2023-03-02 Epidemics_submission/outbreak_response_models_review_v2.tex
added manuscript files

% Template for PLoS
% Version 3.5 March 2018
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first \cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% \cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to \cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Models and modelling practices for assessing the impact of outbreak response interventions to human vaccine-preventable diseases (1970-2019): A systematic review}
}
\newline
\\
James M. Azam\textsuperscript{1*},
Xiaoxi Pang\textsuperscript{2},
Elisha B. Are\textsuperscript{1, 3},
Juliet R.C. Pulliam\textsuperscript{1},
Matthew J. Ferrari\textsuperscript{4}
\\
\bigskip
\textbf{1} DSI-NRF Centre of Excellence in Epidemiological Modelling and Analysis (SACEMA), Stellenbosch University, Stellenbosch 7600, South Africa
\\
\textbf{2} Department of Mathematics, The University of Manchester, Manchester, UK
\\
\textbf{3} Department of Mathematics, Simon Fraser University, Burnaby, BC, Canada
\\
\textbf{4} Center for Infectious Disease Dynamics, Department of Biology, The Pennsylvania
State University, University Park, Pennsylvania, USA
\\
\bigskip

* jamesazam@sun.ac.za

\end{flushleft}
\section*{Abstract}
\subsection*{Background}
Mathematical modelling can aid outbreak response decision-making. However, this would require collaboration among model developers, decision-makers, and local experts to incorporate appropriate realism. We conducted a systematic review of modelling studies on human vaccine-preventable disease (VPD) outbreaks to identify patterns in modelling practices among collaborations. We complemented this with a mini review of eligible studies from the foot-and-mouth disease (FMD) literature.   
\subsection*{Methods}
Three databases were searched for studies published during 1970-2019 that applied models to assess the impact of an outbreak response. Per included study, we extracted data on author affiliation type (academic institution, governmental, and non-governmental organizations), whether at least one author was affiliated to the country studied, interventions, and model characteristics. Furthermore, the studies were grouped into two collaboration types: purely academic (papers with only academic affiliations), and mixed (all other combinations) to help investigate differences in modelling patterns between collaboration types in the human disease literature. Additionally, we compared modelling practices between the human VPD and FMD literature. 
\subsection*{Results}
Human VPDs formed 228 of 253 included studies. Purely academic collaborations dominated the human disease studies (56\%). Notably, mixed collaborations increased in the last seven years (2013 - 2019). Most studies had an author in the country studied (75.2\%) but this was more likely among the mixed collaborations. Contrasted to the human VPDs, mixed collaborations dominated the FMD literature (56\%). Furthermore, FMD studies more often had an author affiliated to the country studied (92\%) and used complex model design, including stochasticity, and model parametrization and validation. 
\subsection*{Conclusion}
The increase in mixed collaboration studies over the past seven years could suggest an increase in the uptake of modelling for outbreak response decision-making. We encourage more mixed collaborations between academic and non-academic institutions and the involvement of locally affiliated authors to help ensure that the studies suit local contexts.

\subsection*{Keywords}
Infectious disease dynamics; outbreak response modelling

\section*{Highlights}
\begin{enumerate}
	\item We explored the nature of collaborative modelling in the human-vaccine preventable disease outbreak response literature.
	\item Author collaborations were grouped into purely academic and mixed types.
	\item Purely academic collaborations dominated the human vaccine-preventable diseases literature.
	\item Mixed collaborations were more likely to involve local experts and use complex methods.
	\item Mixed collaborations have more potential to lead to decision-making and are recommended.
\end{enumerate}

%\subsection*{Registration}
%A protocol following the PRISMA guidelines for systematic review protocols and outlining the procedures for this systematic review was registered on PROSPERO with registration number CRD42020160803 and published through a peer-reviewed process. 
\linenumbers

\section*{Introduction}
Successful outbreak response to infectious diseases is often the result of a highly collaborative process~\cite{Sigfrid2020}. Decision-making during outbreak response usually requires collaborations between academic and field experts, including governmental and Non-Governmental Organizations (NGOs)~\cite{Kretzschmar2020,Kerkhove2012,Okiror2021,Whitty2014,Sigfrid2020}. These collaborations ensure that important perspectives from both research and operations/implementation are accounted for in the decision-making process.

Outbreak response decision-making often requires adaptations to the affected location ~\cite{Whitty2014,Heesterbeek2015,Sigfrid2020}. The interventions and decisions are usually driven by data/evidence, information, and experiences from the past or in real-time, either locally or from similar phenomena elsewhere ~\cite{Abramowitz2015,Kerkhove2012}. Furthermore, involving local experts in the design of interventions has been found to boost the success of outbreak response efforts ~\cite{Sigfrid2020}. Consequently, outbreak response teams should ideally involve at least one local expert to provide more context~\cite{Sigfrid2020}.

Mathematical modelling can support outbreak response decision-making~\cite{Lofgren2015}. Modelling is a proven tool for revealing insights about the extent of disease spread, and impact of interventions, while drawing on lessons learnt to provide recommendations for decision-making during outbreaks~\cite{Kretzschmar2020,Whitty2014,Lofgren2015}. Insights from mathematical modelling, though often useful, only form part of the larger context (socio-economic, political, and so forth) to be considered during an outbreak, making it difficult to determine the extent to which it contributes to outbreak response decision-making ~\cite{Kretzschmar2020,Kerkhove2012}. One way to help ensure that modelling contributes to decision-making could be through the conduct of interdisciplinary research between model developers and decision-makers.

The link between interdisciplinarity in scientific research --- that is, research conducted by authors with diverse scientific backgrounds --- and research impact, for example, number of citations has been well-researched~\cite{Abramo2017,Wagner2011}. However, few studies have investigated the impact of interdisciplinary collaborations on the conduct of scientific research. One such study investigated the impact of interdisciplinarity on the scientific validity of the methods used in a selection of papers that applied machine learning on topics in biology or medicine~\cite{Littmann2020}. The study found that the methods used in the reviewed studies differed according to the nature of the scientific backgrounds of the authors who conducted the research. Our preliminary searches of the literature did not reveal any of such review studies investigating differences in research practices among collaborations in the outbreak response modelling literature. We, therefore, conducted a systematic review of outbreak response modelling studies of human vaccine-preventable diseases with the goal to explore the time and geographic (countries) patterns of collaboration types, and to ascertain differences in practices between the collaboration types in terms of the choice of model characteristics, modelling methods, and other topics.

We sought to answer the following questions with respect to the collaboration landscape in the human disease outbreak response modelling literature: (1) How are the studies distributed in time and geographic locations, and how often is at least one of the collaborators geographically connected to the location being studied? (2) What types of interventions are generally modelled and is there a difference between the conclusions drawn about the impact of interventions, especially, vaccination in comparison with other non-vaccination interventions during outbreaks? (3) Do the model characteristics (structure and dynamics) and modelling practices (parametrization, validation, and so forth) differ between the collaboration types?

We acknowledge that there is a parallel body of relevant modelling work in the livestock literature. Specifically, the outbreak response effort that resulted from the 2001 foot-and-mouth disease (FMD) virus outbreak in the United Kingdom has been a foundational example of the application of mathematical modelling for decision-making. Subsequent work based on this outbreak has been instrumental in the development of FMD outbreak intervention strategies around the world. Hence, even though the primary scope of this review is the application of models to inform outbreak response for human infectious diseases, we include the relevant FMD references for comparison. In the end, we, therefore, study the differences in terms of collaborations in the human disease modelling literature, and compare our observations to that of the FMD modelling literature to further ascertain any differences in approaches and practices between the human and livestock literature.

%The following were the objectives of the systematic review:
%\begin{enumerate}
%	\item To ascertain differences in model characteristics and modelling methods between collaboration types. 
%	\item To determine the distribution of outbreak response modelling studies over time (years) overall and in terms of collaboration types, 
%	\item To determine how often at least one of the authors on a paper was geographically connected to the country/location studied and whether there were differences between collaboration types,
%	\item To investigate types of interventions modelled and differences between the conclusions drawn about the impact of interventions.
%\end{enumerate}

\section*{Materials and methods}
We followed the 2020 Preferred Reporting Items for Systematic Reviews and Meta-analyses statement (PRISMA 2020)  to conduct this systematic review \cite{Page2021}.

\subsection*{Eligibility criteria}
The following definitions were used in the determining study eligibility:

\begin{itemize}
	\item ``Outbreak'': a new and sudden rise in the number of cases of a disease in a population, which when left uncontrolled, could lead to large scale geographic spread, AND 
	\item ``Outbreak response'': an intervention directly triggered by the outbreak of an infectious disease, AND
	\item ``Mechanistic models'': mathematical models that use an equation or system of equations to capture the biological mechanisms driving the transmission dynamics of the infectious disease at the level of an individual or population \cite{Lessler2016a,Reiner2013}, AND
	\item ``Outbreak intervention assessment'': a mechanistic model-based evaluation of the impact of an outbreak response intervention.
\end{itemize}

We included studies that used a mechanistic model to investigate the impact of interventions triggered by the outbreak of any of the human vaccine-preventable diseases we considered (Table 1 in \nameref{S1_File}), Ebola, or foot-and-mouth disease. Studies were considered unique even if they had a duplicated author list or a slight variation in the author list, probably representing the same modelling group, so far as the content of the paper was different.

We excluded studies that satisfied at least one of the following criteria:

\begin{itemize}
	\item Study used a model that is not mechanistic,
	\item Study is not about an outbreak as defined,
	\item Disease studied is not a human vaccine-preventable disease (Table 1 in \nameref{S1_File}), Ebola or foot-and-mouth disease,
	\item Study's objective is not to evaluate the impact of an intervention mounted in response to an outbreak, or
	\item Study is not published in English.
\end{itemize}

\subsection*{Information sources}
On January 15, 2020, we searched Scopus, PubMed, and Web of Science for eligible records. We searched each database from its earliest date of coverage through January 15, 2020.

\subsection*{Search strategy}
We constructed and validated search strings specific to each database. To validate the search strings, we first ran them in the specific database's search engine and obtained a database of records. We then searched the database for well-known papers that fit the criteria for included studies. We did this for each disease on our list.

The search strings were constructed by all five reviewers (JMA, XP, EBA, MJF, and JRCP) and in consultation with the Faculty of Science Librarian of Stellenbosch University to reflect three main topics and their synonyms, that is, ``outbreak'', ``intervention'', and ``mechanistic model''.

The following are the search strings per database.

\textbf{Scopus (Title, abstract, keywords search)}:

( TITLE-ABS-KEY ( epidemic  OR  outbreak  OR  emergency  OR  reactive  OR  crisis ) )  AND  ( TITLE-ABS-KEY ( respon*  OR  manage*  OR  control  OR  interven*  OR  strateg* ) )  AND  ( TITLE-ABS-KEY ( stochastic  OR  transmission  OR  computational  OR  mathematical  OR  mechanistic  OR  statistical  OR  simulation  OR  "In silico"  OR  dynamic* ) )  AND  ( TITLE-ABS-KEY ( model* ) )  AND  ( ( TITLE-ABS-KEY ( cholera  OR  dengue  OR  diphtheria  OR  ebola  OR  "Foot-and-mouth"  OR  "foot and mouth"  OR  fmd  OR  "Hepatitis A"  OR  "Hepatitis B"  OR  "Hepatitis E"  OR  "Haemophilus influenzae type b"  OR  hib  OR  "Human papillomavirus"  OR  hpv  OR  influenza ) )  OR  ( TITLE-ABS-KEY ( "Japanese encephalitis"  OR  malaria  OR  measles  OR  "Meningococcal meningitis"  OR  mumps  OR  pertussis  OR  "Whooping cough"  OR  "Pneumococcal disease"  OR  poliomyelitis  OR  polio  OR  rabies  OR  rotavirus  OR  rubella ) )  OR  ( TITLE-ABS-KEY ( tetanus  OR  "Tick-borne encephalitis"  OR  tuberculosis  OR  typhoid  OR  varicella  OR  chickenpox  OR  "Yellow Fever"  OR  "vaccine-preventable" ) ) )

\textbf{PubMed (Title and abstract search)}:

Search ((((((Epidemic OR Outbreak OR Emergency OR Reactive OR Crisis))) AND ((Response OR Management OR Control OR Intervention OR Strategies))) AND ((Stochastic OR Transmission OR Computational OR Mathematical OR Mechanistic OR Statistical OR Simulation OR "In silico" OR Dynamic*))) AND model*) AND ((Cholera OR Dengue OR Diphtheria OR Ebola OR "Foot-and-mouth" OR "foot and mouth" OR FMD OR "Hepatitis A" OR "Hepatitis B" OR "Hepatitis E" OR "Haemophilus influenzae type b" OR Hib OR "Human papillomavirus" OR HPV OR Influenza OR "Japanese encephalitis" OR Malaria OR Measles OR "Meningococcal meningitis" OR Mumps OR Pertussis OR "Whooping cough" OR "Pneumococcal disease" OR Poliomyelitis OR Polio OR Rabies OR Rotavirus OR Rubella OR Tetanus OR "Tick-borne encephalitis" OR Tuberculosis OR Typhoid OR Varicella OR Chickenpox OR "Yellow Fever" OR "vaccine-preventable"))

\textbf{Web of Science (Topic search)}:

TOPIC: (Epidemic OR Outbreak OR Emergency OR Reactive OR Crisis) AND TOPIC: (Respon* OR  Manage*  OR  Control  OR  Interven*  OR  Strateg*)) AND TOPIC: (Stochastic OR Transmission OR Computational OR Mathematical OR Mechanistic OR Statistical OR Simulation OR In silico OR Dynamic*) AND TOPIC: (model*) AND TOPIC: (Cholera OR Dengue OR Diphtheria OR Ebola OR "Foot-and-mouth" OR "foot and mouth" OR FMD OR "Hepatitis A" OR "Hepatitis B" OR "Hepatitis E" OR "Haemophilus influenzae type b" OR Hib OR "Human papillomavirus" OR HPV OR Influenza OR "Japanese encephalitis" OR Malaria OR Measles OR "Meningococcal meningitis" OR Mumps OR Pertussis OR "Whooping cough" OR "Pneumococcal disease" OR Poliomyelitis OR Polio OR Rabies OR Rotavirus OR Rubella OR Tetanus OR "Tick-borne encephalitis" OR Tuberculosis OR Typhoid OR Varicella OR Chickenpox OR "Yellow Fever" OR "vaccine-preventable")

\subsection*{Study selection}
We used Endnote version X7.8 and Rayyan web application (\url{https://www.rayyan.ai/}) to combine the results from the three databases and to identify and remove duplicate records. The unique records were exported into Rayyan web application, where they were screened in two stages by three reviewers (JMA, XP, and EBA).

Stage one screening involved excluding studies based on their title and abstract, using the questionnaire that follows. The reviewers only used the information provided in the title and abstract of each study to decide whether it was eligible for inclusion (``Include''), not eligible (``Exclude''), or likely to be included (``Maybe''). The ``Include'' and ``Maybe'' category of studies further went through stage two screening described ahead, which was more stringent.

\subsubsection*{Questionnaire for title and abstract screening (Stage 1)}
\begin{enumerate}
	\item	Is this article written in English?
	\begin{itemize}
		\item 	No: Exclude. Reason: Not English
	\end{itemize}
	\item 	Does the title of this article fit the scope of this review?
	\begin{itemize}
		\item 	No: Exclude. Reason: Title out of scope
	\end{itemize}
	\item	Does the topic of the abstract fit the scope of this review?
	\begin{itemize}
		\item 	No: Exclude. Reason: Topic out of scope
	\end{itemize}
	\item Is this study entirely a review (literature review, systematic review, scoping review, not indicated)? 
	\begin{itemize}
		\item 	Yes: Exclude. Reason: Review
	\end{itemize}
	\item Is any part of this study about an outbreak that happened in the past, was ongoing at the time of the study, or a hypothetical one, including one that could happen in the future? We define an outbreak as a new and sudden rise in the number of cases of a disease in a population, which when left uncontrolled, could lead to large scale geographic spread.
	\begin{itemize}
		\item 	No: Exclude. Reason: Not an outbreak
	\end{itemize}
	\item Is any part of this study about a human infectious disease (Table 1 in \nameref{S1_File}), Ebola or foot-and-mouth disease in livestock?
	\begin{itemize}
		\item 	No: Exclude. Reason: Disease not in scope
	\end{itemize}
	\item Does this study assess the impact – epidemiological or operational - of a real or hypothetical intervention that was mounted or could potentially be mounted in response to an outbreak of the disease in question? Note that we define an assessment as an evaluation of either the absolute or relative impact of an intervention on one of several outcomes including number/proportion of population reached with the intervention (coverage), and a change in size - number of people, duration, spatial - of the outbreak.
	\begin{itemize}
		\item 	No: Exclude. Reason: Not an outbreak intervention assessment
		\item 	Maybe. Reason: Intervention details unclear
	\end{itemize}
	\item Does this study solely use static methods for evaluating the intervention? Static methods include surveys, regression methods, descriptive, and exploratory statistical methods.
	\begin{itemize}
		\item 	No: Exclude. Reason: Not a model
	\end{itemize}
	\item Does this study use any kind of equation, system of equations, or computer simulation to capture the disease’s transmission process or natural history over time?
	\begin{itemize}
		\item 	No: Exclude. Reason: Model not mechanistic
		\item 	Maybe. Reason: Likely a model
	\end{itemize}
\end{enumerate}

Stage one was first piloted with all three reviewers screening the same 50 studies using Rayyan in ``blind mode''. This was so that the reviewers could not see each other's screening decisions (inclusion/exclusion/maybe). After the pilot screening, the results were compared and any inclusion/exclusion conflicts were discussed and resolved. The pilot phase ensured that all the reviewers were using a consistent screening approach. The remaining studies were then screened in duplicate and all conflicting decisions were resolved at the end through discussions among the reviewers.

Stage 2 involved screening the included studies from stage 1, using their full text, in duplicate and with the following questionnaire.

\subsubsection*{Questionnaire for full text screening (Stage 2)}
\begin{enumerate}
	\item Is this article written in English? (This was necessary because some articles could have English abstracts but non-English full text)
	\begin{itemize}
		\item 	If no, exclude. Reason: Not English	
	\end{itemize}
	\item Is this article a report, commentary or any kind of non-quantitative report?
	\begin{itemize}
		\item 	If yes, exclude. Reason: Article type out of scope
	\end{itemize}
	\item Is the full text readily available?
	\begin{itemize}
		\item 	If no, mark as Maybe. Reason: Full text not available	
	\end{itemize}
	\item Is this study entirely a review (literature review, systematic review, scoping review, not indicated)? 
	\begin{itemize}
		\item 	If yes, exclude. Reason: Review
	\end{itemize}
	\item Is the study or a part of it about an outbreak, real or hypothetical?
	\begin{itemize}
		\item 	If no, exclude. Reason: Not an outbreak
	\end{itemize}
	\item Is the disease a human vaccine-preventable disease (Table 1 in \nameref{S1_File}), Ebola, or foot-and-mouth disease? 
	\begin{itemize}
		\item 	If no, exclude. Reason: Not a listed disease
	\end{itemize}
	\item Does this study solely use static methods for evaluating the intervention? Static methods include surveys, regression methods, descriptive, exploratory statistical methods.
	\begin{itemize}
		\item 	If no, exclude. Reason: Static model or method
	\end{itemize}
	\item Does this study use any kind of equation, system of equations, or computer simulation to capture the disease’s transmission process in a dynamic way?
	\begin{itemize}
		\item 	If no, exclude. Reason: Model not mechanistic
		\item 	If unclear, maybe. Reason: Likely a model
	\end{itemize}
	\item Is the model about within-host dynamics?
	\begin{itemize}
		\item 	If yes, exclude. Reason: Within-host model
	\end{itemize}
	\item Does this study attempt to assess the impact – epidemiological or operational - of a real or hypothetical intervention that was mounted or could potentially be mounted in response to an outbreak of the disease in question? We define an assessment as an evaluation of either the absolute or relative impact of an intervention on one of several outcomes including number/proportion of population reached with the intervention (coverage), and a change in size - number of people, duration, spatial - of the outbreak.
	\begin{itemize}
		\item 	If no, exclude. Reason: Not an outbreak intervention assessment
		\item 	If unclear, maybe. Label: Intervention details unclear
	\end{itemize}
\end{enumerate}

\subsection*{Data extraction}
To extract the data from the studies, we used the data extraction questionnaire implemented with the KoboToolbox web application (Section 3 in \nameref{S1_File}). The questionnaire was first piloted with 10 papers among the three reviewers, who worked in duplicate. All conflicts in terms of extracted data were resolved.

Following the pilot phase, the full list of included studies was shared among three reviewers (JMA, XP, and EBA), who extracted the relevant data independently. The extracted data was cross-checked by one reviewer (JMA). When a discrepancy was found in the extracted data, the reviewer referred to the original paper and resolved the conflict.

We extracted data on the type of publication, author affiliation type (academic/government/non-governmental), country/setting studied, whether at least one author affiliation was situated in the country studied, disease studied, the study objectives (retrospective/prospective impact assessment, timing of the modelling practice with respect to the outbreak (retrospective/prospective/real-time), interventions studied, and whether vaccination was the most impactful intervention when compared as a single intervention (yes/no/inconclusive). A full list of the extracted data items are provided (Section 2 in \nameref{S1_File}).

From the model in each paper, we extracted data on the representation of individuals (compartmental vs individual-based), whether spatial structure was represented (yes/no), model structure (deterministic vs stochastic), model parameterization, and validation. We also extracted a predefined list of outcomes (cases averted, final epidemic size, etc) measured with the models. If an outcome was reported that was not on the pre-defined list, we collected it separately as free text for further analysis. We also extracted data on whether the studies included sensitivity analysis or not. This was to understand how uncertainties in the model inputs were dealt with.  We collected data on whether the studies used real world data, that is, excluding simulated data, and whether the data was openly available for download. We also extracted information on whether the code used for the analysis and visualization were made openly available.

\subsection*{Data analysis and synthesis}
To understand how the papers were distributed in terms of author affiliations, we first tallied the unique combinations of author affiliation types. We then grouped the author affiliations into the following two collaboration types and performed all further analyses by stratifying the variable(s) of interest by them:

\begin{enumerate}
	\item \textit{Purely academic:} papers with only academic author affiliations (academics collaborating with other academics), 
	\item \textit{Mixed:} papers with a mixture of academic, government and NGO affiliations. This collaboration type also included papers with only government or only NGO affiliations. 
\end{enumerate}

We first explored the trend in aggregated publications during 1970-2019 by counting the number of publications in each year irrespective of collaboration type.

To explore how the publications changed in time with respect to the collaboration types, we tallied the number of publications and relative proportion (mixed versus purely academic collaboration) of studies per year. We lumped together the publications from 1970 to 2005 due to the small numbers.

To study how the papers were distributed in terms of geographic locations, we split the studies into those that studied actual versus hypothetical locations and used the subset of studies about actual locations to rank the topmost studied locations (country and continent) by frequency.

We also investigated how connected the authors were to the locations studied. Here, we only considered studies on geographic scales up to actual countries and not larger. All studies about locations larger than a country were dropped from this part of the analysis. We tallied, in terms of collaboration types, the number of studies about actual locations (countries) with or without at least one author affiliation in the studied location. If a paper studied more than one location, we treated each location as a separate instance. This increased the denominators accordingly.

To summarize the conclusions drawn about the impact of vaccination as a single intervention, we grouped the studies into three categories, that is, studies that modelled non-vaccination interventions, those that modelled vaccination in combination with other interventions, and those that modelled vaccination as a single intervention for comparison with other interventions. The question was only applicable to the last category of interventions, so we counted the number of studies that found vaccination to be the most impactful or not. Where vaccination was not found to be the most impactful, we briefly summarised the reasons and modelling assumptions.

For the disease studied, model characteristics (structure, dynamics, and spatial heterogeneity), and modelling practices (parametrization, validation, sensitivity analysis, data and code use and availability), we counted the number of studies per collaboration type and reported the results as percentages and fractions of the total. In counting the number of papers per disease studied and outcome measured, if a study had more than one outcome measured or disease, we treated each instance as unique and counted them separately. Hence, in such cases, the denominator of the reported fraction increased from the total studies we reported in our search results.

To summarise the model outcomes, we stratified by the collaboration type and tallied the outcomes used within each group. We reported the top six most used outcomes by both collaboration types and compared the results between the two.

All analyses were perform in R 4.0.5 ~\cite{R2021}. We have provided a database of all the screened papers and their associated extracted data in a csv file, which can be accessed at \url{https://osf.io/dmvst/?view_only=b50a8d3ec21b4a07b7977d0f56e79fc3}. Additionally, all the analysis tables are provided as a supplement (\nameref{S2_File}).

\section*{Results}
\subsection*{Study selection}
We retrieved a total of $12, 986$ bibliographic records from Scopus, PubMed, and Web of Science (Fig \ref{PRISMA_flowchart}). Using Endnote and Rayyan, we identified and removed $7, 974$ duplicates, resulting in $5, 012$ unique records for title, abstract, and full text screening. We exported the unique records into Rayyan for the screening in two stages. Stage 1 involved a title and abstract screening in duplicate by the three reviewers and resulted $4, 211$ excluded studies. The stage 2 screening, which involved screening the full text, led to $548$ excluded studies.

After the full text screening, $253$ studies remained for the data extraction stage of which $228$ on human vaccine-preventable diseases and $25$ studies were on FMD. The FMD studies were only used for comparisons.

\begin{figure}[!h]
	\includegraphics[scale=0.85]{figs/fig1_PRISMA_flowchart}
	\caption{\bf The PRISMA flow chart. Numbers described here include studies for both the human vaccine-preventable diseases and foot-and-mouth disease.}
	\label{PRISMA_flowchart}
\end{figure}

\subsection*{Publications over time}
Overall, a few outbreak response modelling papers were published between 1970-2005 $(3.9\%; 9/228)$, followed by a marked increase in publications until 2019 $(96.1\%; 220/228)$ (Fig \ref{publications_per_year}).

\begin{figure}[!h]	
 \includegraphics[scale=0.65]{figs/fig2_publications_per_year.png}
	\caption{\bf Number of publications per year (1970-2019).}
	\label{publications_per_year}
\end{figure}

We first categorised the papers according to the unique combinations of author affiliation types (Table \ref{studies_per_author_affiliations_type}).

Overall, papers with only authors from academic institution affiliations were the most common (56.1\%; 128/228). Papers with author affiliations from academic and governmental organization affiliations were the second most common (25.0\%; 57/228), and followed by those with academic and NGO affiliations (7.5\%; 17/228). The least common were those with governmental and NGO affiliations (0.9\%; 2/228).

As explained earlier, we ultimately grouped the author affiliation combinations into two collaboration types. There were more purely academic collaborations (56.1\%; 128/228) than mixed collaborations (43.9\%; 100/228).

\begin{table}[!h]
\centering
\caption{\bf Number of studies per unique combination of author affiliations (human diseases). Here, we also show the grouping of author affiliation combinations into purely academic and mixed collaborations. Purely academic collaborations refer to those authored by only authors with academic institution affiliations whereas mixed collaborations include those authored by a mixture of authors with academic institution affiliations, government institutions, and NGOs or only one of the last two.}
\setlength\arrayrulewidth{1pt} 
\begin{tabular}{|l l c|}
\hline
\textbf{Collaboration type} & \textbf{Author affiliation combination} & \textbf{Number of publications} \\ \hline
Purely academic & academic only  & 128 \\ \hline
Mixed & academic + governmental   & 57 \\ \hline
Mixed & academic + NGO                 & 17  \\ \hline
Mixed & academic + governmental + NGO    & 14 \\ \hline
Mixed & governmental only                & 5 \\ \hline
Mixed & NGO only                       & 5  \\ \hline
Mixed & governmental + NGO               & 2 \\ \hline  \rowcolor{gray!20}
\textbf{Total} &  & \textbf{228} \\  \hline 
\end{tabular}
\label{studies_per_author_affiliations_type}
\end{table}

To investigate the changes in collaboration types over time, we calculated the number and proportion of studies per collaboration type per year (Fig \ref{studies_per_collab_type}). In the past seven years (2013-2019), there was an absolute increase in the number of papers by both collaboration types. However, in the same period, there was no increase in the relative proportion of publications per year of mixed collaborations (\nameref{S1_Fig}).

\begin{figure}[!h]
\includegraphics[scale=0.65]{figs/fig3_total_collabs_per_year_plot.png}
	\caption{\bf Total studies by collaboration type. The period from 1970-2005 has been lumped up due to the lack of publications. Academic collaborations refer to those authored by only authors with academic institution affiliations whereas mixed collaborations include those authored by a mixture of authors with academic institution affiliations, government institutions, and NGOs. Mixed collaborations are represented by the turquoise bars and purely academic collaborations by the brown bars.}
	\label{studies_per_collab_type}
\end{figure}

\subsection*{Locations studied}
Overall, most of the papers were about actual locations $(78.6\%; 195/248)$. Among these, some studied a geographic location spanning more than one country but not classifiable as a continent $(9.7\%; 19/195)$. Among those 19 studies, West Africa was studied the most $(47.4\%; 9/19)$, followed by the whole globe $(36.8\%; 7/19)$, Southeast Asia $(10.5\%; 2/19)$, and the Northern Hemisphere $(5.3\%; 1/19)$.

When aggregated into continents, the Americas were studied the most $(36.4\%; 68/187)$, followed by Asia $(25.1\%;47/187)$, Africa $(24.6\%; 46/187)$, Europe $(13.4\%; 25/187)$, and Oceania $(0.5\%; 1/187)$.

When disaggregated into countries, the United States was the most studied $(21.1\%; 37/176)$, followed by China $(10.8\%; 19/176)$, Canada $(6.2\%; 11/176)$, and Sierra Leone $(5.7\%; 10/176)$.

\subsection*{Connection of authors to the location studied}
We investigated the connection of the authors to the location studied and found that, overall, there were more studies with at least one author connected to the studied location $(75.2\%; 118/157)$ than not $(24.8\%; 39/157)$.

When stratified by collaboration types, mixed collaborations were more likely to have studies with at least one author in the location studied $(83.1\%; 63/77)$ compared with the purely academic collaborations $(67.5\%; 54/80)$.

\subsection*{Diseases studied}
Overall, the number of studies per disease was disproportionately distributed (Table \ref{studies_per_disease_and_collaboration_type}). Influenza was the most studied $(57.2\%; 135/236)$, followed by Ebola $(14.4\%; 34/236)$, Dengue $(5.1\%; 12/236)$, and a tie between Cholera $(4.7\%; 11/236)$, and Measles $(4.7\%; 11/236)$.

When the diseases were broken down in terms of collaboration type, there were clear differences in their distribution. Influenza, Dengue, and Measles were more studied by mixed collaborations whereas Ebola and Cholera were more studied by purely academic collaborations.

\begin{table}[!h]
		\setlength\arrayrulewidth{1pt} 
	\centering
	\caption{\bf Number of studies per disease and collaboration type. Percentages are calculated from the row totals. The number of studies making up the percentages are shown in brackets. In counting the number of papers per disease studied, if a study was about more than one disease, we treated each instance as unique and counted them separately, leading to a total greater than the reported number of studies.}
	\label{chap3-table: Number of studies per disease and collaboration type}
	\begin{tabular}{|l c c c|}
		\hline
		\textbf{Disease}         & \textbf{Purely academic} & \textbf{Mixed} & \textbf{Total} \\ \hline
		Influenza                & 52.6\% (71)     & 47.4\% (64) & 135   \\ \hline
		Ebola                    & 70.6\% (24)     & 29.4\% (10) & 35    \\ \hline
		Dengue                   & 50.0\% (6)      & 50.0\% (6)  & 12    \\ \hline
		Cholera                  & 81.8\% (9)      & 18.2\% (2)  & 11    \\ \hline
		Measles                  & 36.4\% (4)      & 63.6\% (7)  & 11    \\ \hline
		Tuberculosis             & 85.7\% (6)      & 14.3\% (1)  & 7     \\ \hline
		Poliomyelitis            & 28.6\% (2)      & 71.4\% (5)  & 7     \\ \hline
		Varicella                & 50.0\% (2)      & 50.0\% (2)  & 4     \\ \hline
		Meningococcal meningitis & 33.3\% (1)      & 66.7\% (2)  & 3     \\ \hline
		Pertussis                & 50.0\% (1)      & 50.0\% (1)  & 2     \\ \hline
		Pneumococcal disease     & 50.0\% (1)      & 50.0\% (1)  & 2     \\ \hline
		Yellow fever             & 50.0\% (1)      & 50.0\% (1)  & 2     \\ \hline
		Hepatitis A             & 100.0\% (1)     & 0.0\% (0)   & 1     \\ \hline
		Rubella                  & 100.0\% (1)     & 0.0\% (0)   & 1     \\ \hline
		Typhoid                  & 100.0\% (1)     & 0.0\% (0)   & 1     \\ \hline
		Hepatitis B              & 0.0\% (0)       & 100.0\% (1) & 1     \\ \hline
		Malaria                  & 0.0\% (0)       & 100.0\% (1) & 1     \\ \hline
		Mumps                    & 0.0\% (0)       & 100.0\% (1) & 1    \\ \hline \rowcolor{gray!20}
		\textbf{Overall}			&	\textbf{55.5\% (131)}   			& \textbf{44.5\% (105)}   & \textbf{100\% (236)} \\
		\hline
	\end{tabular}
	\label{studies_per_disease_and_collaboration_type}
\end{table}

\subsection*{Intervention types and impact of vaccination}
There were more papers about non-vaccination interventions $(48.2\%; 110/228)$, followed by those that modelled vaccination as part of a mix of interventions or do-nothing counterfactuals $(41.7\%; 95/228)$, and those that modelled vaccination as a single intervention for side-by-side comparison with other non-vaccination interventions $(10.1\%; 23/228)$.

The third group of papers that modelled vaccination as a single intervention allowed us to collate conclusions on the sole impact of vaccination. There were approximately the same number of studies in this set of studies belonging to the two collaborations types.

Concerning the conclusions about the sole impact of vaccination as a single intervention, most of the studies found vaccination to be the most impactful single intervention in side-by-side comparison with other non-vaccination interventions $(82.6\%; 19/23)$. Few studies found the vaccination to be less impactful compared to other interventions and for various reasons $(17.4\%; 4/23)$. Influenza was the disease studied in these latter four cases. Isolation, and antivirals were found to be more impactful than vaccination due to reasons including the delay until a strain-specific vaccine is developed to control the disease.

\subsection*{Model structure, spatial heterogeneity, and model dynamics}
There were more compartmental models $(78.5\%; 179/228)$ than agent-based models $(20.2\%; 46/228)$ with no clear difference in preference between the two collaboration types.

Approximately a third of the papers included spatial heterogeneity $(28.9\%; 66/228)$ with no clear difference between the two collaboration types.

Deterministic models were the most common $(62.3\%; 142/228)$ compared to stochastic $(31.6\%; 72/228)$ and hybrid models $(6.1\%; 14/228)$, that is models with both deterministic and stochastic components. Here, mixed collaborations were more likely to use stochastic models $(40.0\%; 40/100)$ than purely academic collaborations $(25.0\%; 32/128)$.

\subsection*{Model parametrization and validation}
The top three most commonly used parametrization methods included: combining literature sources and expert opinion/assumptions, literature sources and fitting to data, and literature sources only (Table \ref{model_parametrization_results}).

The most common parametrization method among mixed collaborations was the combination of literature sources and fitting $(27.3 \%; 35/128)$, whereas the combination of literature and expert opinion was the most common among purely academic collaborations $(28.0\%; 28/100)$.

\begin{table}[!h]
\setlength\arrayrulewidth{1pt} 
\centering
\caption{\bf Model parametrization methods. We define parametrization as the method of determining the parameter values for the model. In the table, ``Literature'' means the model's parameters were obtained from literature sources. ``Expert opinion'' means the values were assumed in consultation with experts of the field. ``Fitted'' means the model’s parameters were obtained through some form of mathematical or statistical fitting to a time series of data. }
\begin{adjustwidth}{-2.10in}{0in}
\begin{tabular}{| p{0.17\textwidth}  p{0.14\textwidth}  p{0.14\textwidth}  p{0.12\textwidth}  p{0.13\textwidth}  p{0.13\textwidth}  p{0.12\textwidth}  p{0.1\textwidth}  p{0.07\textwidth} |} \hline 
\textbf{Collaboration type} & \textbf{Literature and expert opinion} & \textbf{Literature and fitted} & \textbf{Literature} & \textbf{Expert opinion} & \textbf{Literature, expert opinion, and fitted} & \textbf{Fitted} & \textbf{Expert opinion and fitted} & \textbf{Total} \\ \hline
Academic & 27.3\% (35) & 22.7\% (29) & 18.0\% (23) & 13.3\% (17) & 9.4\% (12)  & 7.0\% (9) & 2.3\% (3) & 128 \\ \hline
Mixed & 25.0\% (25) & 28.0\% (28) & 15.0\% (15) & 7.0\% (7) & 19.0\% (19) & 5.0\% (5) & 1.0\% (1) & 100 \\ \hline \rowcolor{gray!20}
Overall & 26.3\% (60) & 25.0\% (57) & 16.7\% (38) & 10.5\% (24) & 13.6\% (31) & 6.1\% (14) & 1.8\% (4) & 228 \\ \hline 
\end{tabular}
\end{adjustwidth}
\label{model_parametrization_results}
\end{table}

Most studies did not perform any form of validation $(63.2\%; 144/228)$. Approximately a third used data to validate their models $(34.6\%; 79/228)$ (Table \ref{model_validation_results}). Mixed collaborations were more likely to validate their model with data or the output of an independent model.

\begin{table}[!h]
	\centering
	\setlength\arrayrulewidth{1pt} 
	\caption{\bf Model validation methods. We define model validation as the method by which the model's performance was measured. ``None'' means no validation was performed, or the model’s output was compared to another output from the same model. ``Data'' means the model was compared to independently observed data. ``Another model’s output'' means the model's output was compared to an independent model's output.}
	\begin{adjustwidth}{-0.00in}{0in}
		\begin{tabular}{| p{0.15\textwidth}  p{0.13\textwidth} p{0.13\textwidth} p{0.13\textwidth} p{0.13\textwidth} p{0.12\textwidth}|}
			\hline
			\textbf{Collaboration type} & \textbf{None} & \textbf{Data} & \textbf{Another model's output} & \textbf{Data and another model} & \textbf{Total} \\ \hline
			Academic & 70.3\% (90) & 28.9\% (37) & 0.8\% (1) & 0.0\% (0) & 128 \\ \hline
			Mixed & 54.0\% (54) & 42.0\% (42) & 3.0\% (3) & 1.0\% (1) & 100 \\ \hline \rowcolor{gray!20}
			Overall & 63.2\% (144) & 34.6\% (79) & 1.8\% (4) & 0.4\% (1) & 228\\ \hline
		\end{tabular}
	\end{adjustwidth}
	\label{model_validation_results}
\end{table}

\subsection*{Data and model simulation code}
More than half of the papers used datasets collected independent of the study for either the model parametrization or validation process $(56.1\%; 128/228)$. These papers were split approximately equally between the two collaboration types.

The use of accessible data was, however, different between the two groups. Purely academic collaborations were more likely to use data that could be accessed in the public domain $(81.0\%; 51/63)$ compared to mixed collaborations $(56.9\%; 37/65)$.

Few papers provided access to the model simulation code $(1.7\%; 4/228)$. Here, if a paper indicated that the authors could be contacted for the code, it was deemed as inaccessible due to the many hurdles with getting the code in time. Some papers reported the computer application/software/program/package used (R, Python, C++, Matlab, and so forth) but we did not collect that information.

\subsection*{Patterns in the foot and mouth disease (FMD) literature}
There were $25$ studies about foot and mouth disease outbreaks. Due to the small number of studies, the absolute differences between the two collaboration types were generally not large enough to be considered (\nameref{S2_File}), hence, we report on the aggregated patterns.

In terms of collaboration types, slightly more than half of the $25$ studies were authored by mixed collaborations $(56.0\%; 14/25)$ than purely academic collaborations $(44.0\%; 11/25)$. Almost all the papers had at least one author in the location studied $(92.0\%; 23/25)$.

Overall, vaccination was modelled as a single intervention for comparison in more than half of the studies $(56.0\%; 14/25)$, followed by vaccination in combination with other interventions $(28.0\%; 7/25)$, and no vaccination $(16.0\%; 4/25)$. Few of the first set of studies found vaccination to be the most impactful as a single intervention $(14.3\%; 2/14)$.

In general, the FMD models had more agent-based $(76.0\%; 19/25)$ and spatially explicit structure $(72.0\%; 18/25)$, largely used stochastic dynamics $(56.0\%; 14/25)$, and performed more sensitivity analyses $(56.0\%; 14/25)$.

In terms of model parametrization, the most common method was the combined use of literature sources and expert opinion $(28.0\%; 7/25)$, followed by fitting to data only $(20.0\%; 5/25)$, and the combined use of literature sources, expert opinion, and fitting to data $(16.0\%; 4/25)$. Here, mixed collaborations were more likely than purely academic collaborations to combine literature sources and expert opinion $(42.9\% 6/14)$. Furthermore, most of the FMD models were not validated $(72.0\%; 18/25)$.

\section*{Discussion}
For the period $1970-2019$, co-authorship by purely academic collaborations formed over $56\%$ of the outbreak response impact modelling studies of human vaccine-preventable diseases. Both collaboration types increased in absolute numbers over the past seven years. Regarding modelling practices between the two collaboration types, mixed collaborations were more likely to: (i) include authors affiliated through their institutions to the location studied, (ii) use more complex modelling practices including stochastic model dynamics, parametrization methods involving a combination of literature sources, expert opinion/assumptions, and fitting to data, and validate their models with data collected independent of the study. Even though this review was about human vaccine-preventable diseases, only 51.8\% of the studies modelled vaccination in some form. Moreover, only 10.1\% of the total studies modelled vaccination for comparison with other non-vaccination strategies in the same analysis. Influenza was disproportionately the most studied disease, followed by Ebola, and Dengue.

There were several differences in models and practices between the human disease literature and foot and mouth disease (FMD). Mixed collaborations dominated the FMD literature, with almost all papers having an author in the location studied. Furthermore, most of the FMD models and modelling practices were more complex involving the use of spatial, stochastic, agent-based models. However, the FMD models were less likely to be validated with real world data.

Collaborations, especially between authors from academic institutions, governmental, and non-governmental organizations responsible for outbreak response, could lead to knowledge transfer and improved decision-making \cite{Muscatello2017}. Moreover, such diversity in modelling collaborations could expand the skill sets needed to solve the complex real world outbreak response needs. However, it is well known that there is a weak link between academic research and decision-making in general, and research findings are often not easily translated into decisions \cite{Choi2005,Deelstra2003,Muscatello2017}. This gap in knowledge translation exists especially between outbreak response researchers and public health decision-makers \cite{Rivers2019,Muscatello2017}. There are examples of the commissioning of modelling by organisations such as the US Centers for Disease Control and Prevention (CDC) and the World Health Organization (WHO) to inform decision-making during past outbreaks of Influenza, Ebola, Zika, and Dengue \cite{Muscatello2017}. However, many decision-makers remain cautious about the uptake of modelling due, in part, to issues about transparency in assumptions, credibility and ease of use of modelling software, and adaptability of the results to other settings and existing policies \cite{Muscatello2017}.

To bridge this knowledge translation gap between modellers and decision-makers, modelling collaborations that deepen the interaction between model developers and decision-making have been proposed \cite{Choi2005,Rivers2019}. This could be achieved through the sharing of expertise so that the academics formulate, parametrize, and validate the models taking into account the expert opinions of the decision-makers so that the findings are more tailored towards implementation. Mixed or interdisciplinary collaborations have been reported to be strongly associated with research impact and translation to decision-making \cite{Deelstra2003}. Hence, outbreak response, which is broadly an operational field, would ideally have modelling groups/collaborations that are comprised of academics and decision-makers to bridge this gap. In this review, we observed an absolute increase in the number of papers published by mixed collaborations (Fig \ref{studies_per_collab_type}). This could suggest an increase in the uptake or recognition of modelling as an outbreak response decision-making tool. Future research to investigate and explain this increase could advance our understanding of the contribution of modelling to outbreak response decision-making.

The inclusion of local experts in outbreak response modelling teams helps with more tailored problem-solving and decision-making and better reception of the decisions made \cite{Abramowitz2015}. In that regard, mathematical modelling collaborations involving local experts or, in this review, locally affiliated co-authors are an important first step towards achieving this. We found that most of the human disease studies had authors with an institutional affiliation in the location studied. We observed the same pattern for FMD albeit at a much higher percentage. However, when the human disease data were disaggregated, the results showed that mixed collaborations had a much higher percentage of studies with at least one author in the studied location compared to purely academic collaborations. Coupling this with the absolute increase in publications by mixed collaborations in the past seven years could suggest an increase in the uptake of modelling as a public health decision-making tool. However, we did not measure this causality. Research that measures the direct impact of mathematical modelling in public health decision-making remains lacking in the literature \cite{Muscatello2017}. Future studies designed to investigate this uptake of models and whether it has had an impact on outbreak response would contribute meaningfully to the field of outbreak response modelling.

Three classes of interventions with respect to vaccination were modelled: non-vaccination (mostly antiviral use and non-pharmaceutical interventions), vaccination mixed with other complementary non-vaccination interventions, and vaccination as a single intervention for side-by-side comparison with other non-vaccination alternatives. The last class of interventions were the only eligible set for our analysis of the conclusions about whether vaccination is always the most impactful intervention when modelling is used as the assessment tool. Even though all the reviewed studies were about human vaccine-preventable diseases, only 10.1\% of the studies modelled vaccination as a single intervention for side-by-side comparison with non-vaccination interventions. This lack of studies assessing the sole impact of vaccination reflects the reality that vaccination is often  implemented alongside other interventions and never alone, making it difficult to assess its sole impact. Nevertheless, mathematical modelling is an ethically viable way to assess the sole impact of vaccination, and hence, an essential tool for decision-making.

Among the studies that modelled vaccination as a single intervention for comparison with other single non-vaccination interventions, vaccination was found to be the most impactful intervention in 82\% of the studies. Four studies out of the 23 that modelled influenza found case isolation \cite{Yasuda2009,Gao2016,Chen2020a} and antiviral prophylaxis and/or therapeutics \cite{Gumel2008} to be more impactful than vaccination assuming those interventions could be implemented immediately, given significantly efficient isolation and large antiviral stockpiles before the outbreak/pandemic. Among these four studies, some common assumptions that influenced how vaccination was implemented included: the late arrival of effective vaccines \cite{Yasuda2009}, low versus high vaccination rates \cite{Gao2016}, the use of partially effective pre-existing vaccines against the current strain reactively \cite{Gumel2009} or pre-emptively \cite{Chen2018}. In all four studies, it was, however, recommended that, vaccination be used in combination with the alternative interventions. Even though antivirals were found to be more impactful in some cases, its prolonged use was discouraged to prevent the development of antiviral resistance \cite{Gumel2009}. On the other hand, there was a high percentage of studies in the FMD literature about the use of vaccination as a single intervention and vaccination was rarely found to be the most impactful intervention.

We found some commonalities and differences in the choice of model structure and dynamics between the two collaboration types in the human disease literature. Mixed collaborations were more likely to use ``complex'' models and practices. We are not making any value judgements with regards to complexity but are only highlighting these differences that might require further investigation. Moreover, it is common to model an outbreak using alternative model choices and assumptions depending on the question being answered \cite{Basu2013}. However, the results must always be interpreted with cognisance of the limitations/assumptions of the model.  The use of more complex models and practices by mixed collaborations is likely due to the fact that often, real world public health policy-related decision-making is operational, requiring finer details in models and approaches to answer the questions posed in a practical way. Our definition of mixed collaborations meant that it may have involved decision-makers. It is, therefore, likely that their need for practical solutions could have influenced higher levels of model details or complexity.

The FMD models were generally more complex than the human disease models. This is not surprising because the nature of FMD spread often requires the inclusion of farm structure, farm connectivity, and demographics to capture the disease's dynamics accurately \cite{Kinsley2018}. Future studies designed to explain the differences in modelling practices of human outbreak response modelling groups might help to explain what we have observed in this review.

A little over half of the human disease papers used observed data for parametrization or validation. Additionally, only 4 studies shared their code in an easy to access form. On the other hand, the FMD models were generally not validated with observed data. Owing to this, it might be difficult to reproduce some of the results in these outbreak response modelling studies. We recognise that data sharing in public health raises a lot of debate regarding privacy and intellectual property, and often, authors are hindered by institutional data sharing policies \cite{Kim2016}. We, however, recommend that data and code be shared where possible to promote open science practices that help advance the field.

This review had several limitations. First, outbreak response models and analyses are not always published in peer-reviewed journals, but this systematic review only focussed on peer-reviewed articles. It is, therefore, possible that some relevant studies were missed by our search strategy. Second, we used the author list and affiliations to classify studies as either purely academic or mixed. However, this could cause some mixed collaborations to be misclassified as purely academic, especially in cases where non-academics contributed to papers classified as purely academic but were not included on the author list. It is, however, standard practice to include individuals who contributed substantially to a piece of scientific writing, hence, if that was not done for a paper, it could imply that the level of interaction was not high enough to warrant the credit of authorship. Third, in the absence of an explicit measure of contribution of mathematical modelling to outbreak response decision-making, we used mixed collaborations as a proxy. Thus, we may be under-estimating the number of mixed collaborations in the literature. Forth, we only surveyed the literature on a specific study design – mechanistic models. We excluded statistical models and other computational models, which are not mechanistic. Hence, the results of this systematic review should only be interpreted in the context of the mechanistic modelling landscape. Furthermore, it is also possible that some purely academic collaborations contribute to decision-making whereas some mixed collaborations are purely an academic exercise. Also, we  conducted our database searches in January 2020 and therefore do not reflect the literature, or any changes in practice, associated with the COVID-19 pandemic. Lastly, by only including papers published in English, we most certainly missed papers published in other languages.

Numerous factors could explain the patterns we have observed in this review, and we would recommend future studies that will use appropriate study designs, for example, interviews of modelling groups and public health decision-makers, to explain why certain model choices and modelling practices were made by the collaboration types. Future studies should investigate when modelling results directly impacted decision-making and what determined that to identify best practices that will strengthen the link between modelling and decision-making in the future. We expect that collaboration between academia, decision-makers, and local experts will enhance decision-making by accounting for aspects of policy and decision-making that might be overlooked in studies conducted mainly as a theoretical exercise.

\subsection*{Other information}
A protocol following the PRISMA guidelines for systematic review protocols and outlining the procedures for this systematic review was registered on PROSPERO with registration number CRD42020160803 and published through a peer-reviewed process~\cite{Azam2020}.

\section*{Supporting information}

\paragraph*{S1 File}
\label{S1_File}
{\bf Search strings and results, data items extracted, and questionnaire for data extraction.}

\paragraph*{S1 Fig}
\label{S1_Fig}
{\bf Collaboration patterns in time (proportions per year).}

\paragraph*{S2 File}
\label{S2_File}
{\bf Analysis of extracted data.}

\paragraph*{S3 Table}
\label{S3_Table}
{\bf PRISMA checklist.}

%\section*{Acknowledgments}

% Use the PLoS provided BiBTeX style
\bibliography{references.bib}
\bibliographystyle{vancouver}
\nolinenumbers
\end{document}

### 2023-03-02 scripts/orv_sys_rev_data_analysis.Rmd
added manuscript files

---
title: "Analysis of the included studies"
output:
  word_document:
    toc: yes
  pdf_document:
    toc: yes
    keep_tex: yes
    fig_crop: no
---

```{r echo=FALSE, include=FALSE}
#' load packages
library('tidyverse')
library('readr')
library('ggthemes')
library('mdthemes')
library('scales')
library('janitor')
library('forcats')
library('stringr')
library('countrycode')
library('bib2df')
library('conflicted')
library('Hmisc')
library('ggwordcloud')

#resolve package function conflicts
conflict_prefer('filter', 'dplyr')
conflict_prefer('select', 'dplyr')
conflict_prefer('kable', 'knitr')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(dev = 'jpeg')
knitr::opts_chunk$set(out.height = "\\textheight",  out.width = "\\textwidth")
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

#create a folder for storing the manuscript figures

if(!dir.exists('../figs_manuscript'))
    {
    dir.create('../figs_manuscript', 
               showWarnings = FALSE)
    }

#save figures in this folder
save_fig_here <- '../figs_manuscript'

save_thesis_fig_here <- "C:/Users/JAMESAZAM/Dropbox/My Academic Repository/_SACEMA/Academic/_PhD/__PhD_Thesis/_Thesis_LaTeX/figs/chapter_3"
```

```{r}
# Load the cleaned data 
long_data <- read_rds('../data/final_data/cleaned_data/review_data_long_cleaned.rds')

#The cleaned data without citations
compact_data_init <- read_rds('../data/final_data/cleaned_data/review_data_compact_cleaned.rds')

#a vector of shorter replacements for the original parametrization descriptions
parametrization_str_replacements <- c('values_from_literature' = 'literature', 
                  'values_from_guess_and_expert_opion' = 'expert_opinion', 
                  'values_fitted_to_ts' = 'fitted',
                  ' ' = ' and ' #replace space with 'and' to make it more readable
                  )

#a vector of shorter replacements for the original validation descriptions
validation_str_replacements <- c('compared_with_data' = 'data',
                                 'compared_with_other_model_output' = 'another_model',
                                 'model_not_validated' = 'none',
                                 ' ' = '_and_'
                                 )

# The data with citations 
compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/final_data/cleaned_data/compact_data_with_citation_keys_cleaned.rds'))

compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>% 
    mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
                               'yes', 
                               'no')
         ) %>% 
  mutate(intervention_type = case_when(
    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_combination_with_others', #when vax was modelled but not for comparison as a single intervention
    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
  )) %>% 
  mutate(publication_year = as.numeric(publication_year), 
         author_in_country_studied = as.character(author_in_country_studied)) %>% 
  arrange(publication_year) %>%
  mutate(
    author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + '),
    author_in_country_studied = if_else(author_in_country_studied == 'NA', 'not_applicable',
                                        author_in_country_studied
                                        )
    ) %>% 
  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, #An approach to aggregate the years before 2006 into one group because of the low number of papers
                                         2005, 
                                         publication_year
                                         )
                                  ), 
         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
                                         'purely_academic', 
                                         'mixed')
                                 )
         )

#replace the original descriptions of parametrization and validation with shorter strings
compact_data_with_citation_keys <- compact_data_with_citation_keys %>% 
  mutate(parametrization = str_replace_all(parametrization, 
                                           parametrization_str_replacements
                                           )
         ) %>% 
  mutate(validation = str_replace_all(validation, 
                                      validation_str_replacements
                                      )
         ) %>% 
  mutate(model_structure = str_replace(model_structure, 'deterministic stochastic', 'both'))

#Rearrange the columns
compact_data_with_citation_keys <- compact_data_with_citation_keys %>% 
  relocate(c(title, bibtexkey), .before = publication_year) %>% 
  relocate(publication_year, .before = bibtexkey) %>% 
  relocate(c(x0_reviewer, category, author:language), 
           .after = collab_type
           )

# Remove the FMD papers (NB: We only use the FMD papers for comparison)
long_data_no_fmd <- long_data %>% filter(disease != 'fmd')

compact_data_with_citation_keys_no_fmd <- compact_data_with_citation_keys %>% 
  filter(disease != 'fmd')

#Filter the FMD data
fmd_data <- compact_data_with_citation_keys %>% 
  filter(disease == 'fmd') 
```

# Human vaccine-preventable diseases

```{r eval=FALSE}
library(PRISMAstatement)

prisma_chart <- prisma(found = 12986,
       found_other = 0,
       no_dupes = 5012, 
       extra_dupes_box = TRUE,
       screened = 5012, 
       screen_exclusions = 4211, 
       full_text = 801,
       full_text_exclusions = 548, 
       qualitative = 253, 
       quantitative = 0,
       width = 800, height = 800,
       font_size = 12)

prisma_chart
```

<!-- ## Publications per year -->

<!-- ```{r} -->

<!-- publications_per_year <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   count(publication_year)  -->

<!-- publications_per_year_plot <- ggplot(data = publications_per_year) +  -->
<!--   geom_bar(aes(x = publication_year,  -->
<!--                y = n -->
<!--                ),  -->
<!--            stat = 'identity',  -->
<!--            color = 'black', -->
<!--            fill = 'tomato3' -->
<!--            ) + -->
<!--   scale_y_continuous(breaks = seq(0, 30, 2), -->
<!--                      labels = seq(0, 30, 2) -->
<!--                      ) + -->
<!--   labs(x = '**Year of publication**', y = '**Number of papers**') + -->
<!--   md_theme_minimal(base_size = 12) -->

<!-- plot(publications_per_year_plot) -->

<!-- ggsave(filename = 'publications_per_year.tiff',  -->
<!--        plot = publications_per_year_plot,  -->
<!--        device = 'tiff',  -->
<!--        path = save_fig_here -->
<!--        ) -->

<!-- ggsave(filename = 'publications_per_year.tiff',  -->
<!--        plot = publications_per_year_plot,  -->
<!--        device = 'tiff',  -->
<!--        path = save_thesis_fig_here -->
<!--        ) -->

<!-- ``` -->

<!-- ## Collaboration patterns in time -->

<!-- ### Number of studies per combinations of author affiliation types -->

<!-- ```{r echo=FALSE} -->
<!-- #' Count by collaboration types and make a bar plot -->
<!-- collab_types_count <- compact_data_with_citation_keys_no_fmd %>% -->
<!--     count(author_affiliation_type, sort = TRUE) %>%  -->
<!--     arrange(desc(n)) %>%  -->
<!--     adorn_totals() %>%  -->
<!--     adorn_percentages(denominator = 'col') %>%  -->
<!--     adorn_pct_formatting() %>%  -->
<!--     adorn_ns() -->

<!-- knitr::kable(collab_types_count,  -->
<!--              format = "latex", booktabs = TRUE,  -->
<!--              caption = 'Number of publications per author affiliation type combination') %>%  -->
<!--         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))  -->
<!-- ``` -->

<!-- ### Proportions of the total publications per year by collaboration type -->

<!-- ```{r echo=FALSE, fig.width=8} -->
<!-- #' Count the number of each author affiliation type per year (including FMD) -->
<!-- collap_types_by_year <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   count(year_aggreg,  -->
<!--         collab_type,  -->
<!--         name = 'total_publications' -->
<!--         ) -->

<!-- #The plot -->
<!-- # Modify the x-axis labels to account for the lumping of the years from 2005 and below -->
<!-- x_axis_labels <- as.character(seq(2005, 2020, 2)) -->

<!-- x_axis_labels[1] <- '1970-2005' -->

<!-- collab_proportions_plot <- ggplot(data = collap_types_by_year) +  -->
<!--   geom_bar(aes(x = year_aggreg, -->
<!--                y = total_publications, -->
<!--                fill = collab_type -->
<!--                ), -->
<!--            color = 'black', -->
<!--            stat = 'identity', -->
<!--            position = position_fill(reverse = TRUE)#, -->
<!--            #show.legend = FALSE -->
<!--              ) + -->
<!--   scale_fill_manual(values = c('tan3', 'turquoise2')) + -->
<!--   scale_x_continuous(breaks = seq(2005, 2020, 2), -->
<!--                      labels = x_axis_labels, -->
<!--                      expand = c(0, 0) -->
<!--                      ) + -->
<!--   #coord_flip() + -->
<!--   labs(#title = 'Publications per collaboration type over time', -->
<!--        x = '**Year**', -->
<!--        y = '**Proportion of total publications**', -->
<!--        fill = '**Collaboration type**'  -->
<!--          ) + -->
<!--   theme(legend.position = 'none') + -->
<!--  # md_theme_minimal(base_size = 16) #For Powerpoint -->
<!--   md_theme_minimal(base_size = 12) -->

<!-- plot(collab_proportions_plot) -->

<!-- ggsave(filename = 'collab_proportions.tiff',  -->
<!--        plot = collab_proportions_plot,  -->
<!--        device = 'tiff',  -->
<!--        path = save_fig_here -->
<!--        ) -->

<!-- ggsave(filename = 'collab_proportions.tiff',  -->
<!--        plot = collab_proportions_plot,  -->
<!--        device = 'tiff',  -->
<!--        path = save_thesis_fig_here -->
<!--        ) -->

<!-- ``` -->

<!-- ### Absolute number of publications per year by collaboration type -->

<!-- ```{r} -->
<!-- #' Count the number of each author affiliation type per year -->
<!-- collabs_per_year <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   count(year_aggreg,  -->
<!--         collab_type,  -->
<!--         name = 'total_publications' -->
<!--         )  -->

<!-- collabs_per_year_plot <- ggplot(data = collabs_per_year,  -->
<!--                                     aes(x = year_aggreg,  -->
<!--                                         y = total_publications -->
<!--                                         ),  -->
<!--                                     color = 'black') +  -->
<!--   geom_bar(aes(fill = collab_type),  -->
<!--            stat = 'identity',  -->
<!--            position = 'dodge' -->
<!--            ) +  -->
<!--   scale_fill_manual(values = c('tan3', 'turquoise2')) +  -->
<!--   scale_x_continuous(breaks = seq(2005, 2020, 2), -->
<!--                      labels = x_axis_labels, -->
<!--                      expand = c(0, 0) -->
<!--                      ) + -->
<!--   labs(x = '**Year**',  -->
<!--        y = '**Total publications**',  -->
<!--        fill = 'Collaboration type' -->
<!--        ) + -->
<!--   md_theme_minimal(base_size = 12) + -->
<!--   #md_theme_minimal(base_size = 16) + -->
<!--   theme(legend.position = 'bottom')  -->

<!-- plot(collabs_per_year_plot) -->

<!-- ggsave(filename = 'total_collabs_per_year_plot.tiff', -->
<!--        plot = collabs_per_year_plot,  -->
<!--        device = 'tiff', -->
<!--        path = save_fig_here -->
<!--        ) -->

<!-- ggsave(filename = 'total_collabs_per_year_plot.tiff', -->
<!--        plot = collabs_per_year_plot,  -->
<!--        device = 'tiff', -->
<!--        path = save_thesis_fig_here -->
<!--        ) -->

<!-- ``` -->

<!-- Even though non-academic collaborations increased over time, the share of total publications per year over time decreased. -->

<!-- ## Collaboration patterns in geographic space -->

## Collaboration types (aggregated)
```{r}
#' Count by collaboration types and make a bar plot
studies_per_collab_type <- compact_data_with_citation_keys_no_fmd %>%
    count(collab_type, sort = TRUE) %>% 
    arrange(desc(n)) %>% 
    adorn_totals() %>% 
    adorn_percentages(denominator = 'col') %>% 
    adorn_pct_formatting() %>% 
    adorn_ns()

knitr::kable(studies_per_collab_type, caption = 'Number of studies per collaboration type (Human VPDs)',
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

## Locations studied

### Real versus hypothetical

```{r}
location_types_tally <- compact_data_with_citation_keys_no_fmd %>% 
    separate_rows(country_studied, sep = ' ') %>%
    distinct(title, country_studied, .keep_all = TRUE) %>%
    mutate(location_type = ifelse(country_studied == 'none', 'none', 'real')) %>% 
    count(location_type) %>% 
  arrange(desc(n)) %>% 
   adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns()

knitr::kable(location_types_tally, 
             caption = 'Number of studies per location type', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))

```

### Larger than one country

```{r}
larger_geographies_tally <- compact_data_with_citation_keys_no_fmd %>% 
    separate_rows(country_studied, sep = ' ') %>%
    distinct(title, country_studied, .keep_all = TRUE) %>%
    filter(country_studied %in% c('west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
    count(country_studied) %>% 
  arrange(desc(n)) %>% 
   adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns()

knitr::kable(larger_geographies_tally, caption = 'Number of studies per location larger than one country', format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))

```

### Countries studied

```{r}
countries_studied_by_count <- compact_data_with_citation_keys_no_fmd %>% 
    separate_rows(country_studied, sep = ' ') %>%
    distinct(title, country_studied, .keep_all = TRUE) %>% 
    count(collab_type, country_studied, name = 'num_of_studies', sort = T)

#'Modify the data frame to lump together all countries with less than some number of studies as 'other' and recalculate the percentage studied
countries_studied_by_count_aggregated <- countries_studied_by_count %>% 
  group_by(country_studied) %>%
  summarise(num_of_studies = sum(num_of_studies),
            .groups = 'drop'
            ) %>% 
  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
  arrange(desc(num_of_studies)) %>% 
  adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns() %>% 
  ungroup()

#Print the results
knitr::kable(countries_studied_by_count_aggregated, 
             caption = 'Number of studies per country', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'), font_size = 7)
```

### Continents studied

```{r}
continents_studied_by_count <- countries_studied_by_count %>% 
  filter(country_studied %nin% c('none', 'northern_hemisphere', 'global')) %>% 
  mutate(continent_studied = countrycode(country_studied, 
                                          destination = 'continent',
                                          origin = 'iso2c',
                                          nomatch = NULL #if there is no match, keep the original
                                          )
         ) %>% 
  mutate(continent_studied = str_to_lower(continent_studied)
         ) %>% 
  mutate(continent_studied = case_when(str_detect(continent_studied, 'asia') == T ~ 'asia', 
                                         str_detect(continent_studied, 'africa') == T ~ 'africa', 
                                         TRUE ~ continent_studied
                                       )
           ) %>% 
  group_by(continent_studied) %>%
  summarise(num_of_studies = sum(num_of_studies), 
            .groups = 'drop'
            ) %>% 
  arrange(desc(num_of_studies)) %>% 
  adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns()

#Print the results
knitr::kable(continents_studied_by_count, 
             caption = 'Number of studies per continent', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

## Geographic connection of authors to the studied locations

```{r}
author_connectedness_top_5_countries <- compact_data_with_citation_keys_no_fmd %>% 
  filter(author_in_country_studied != 'not_applicable') %>% 
  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
separate_rows(country_studied,  sep = ' ') %>% 
  group_by(collab_type) %>% 
  count(country_studied, author_in_country_studied, sort = TRUE) %>% 
  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
  replace_na(list(yes = 0, no = 0)) %>% 
  arrange(collab_type, desc(yes)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no')) %>% 
  adorn_pct_formatting(... = c('yes', 'no')) %>% 
  adorn_ns(... = c('yes', 'no')) %>% 
  ungroup()

knitr::kable(author_connectedness_top_5_countries, caption = 'Studies with at least one author affiliation in the location studied', 
             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position', 'repeat_header'), font_size = 8)
```

### Author affiliation in the studied location (overall)

```{r}
author_connectedness_to_location_aggreg <- compact_data_with_citation_keys_no_fmd %>% 
  filter(author_in_country_studied != 'not_applicable') %>% 
  filter(country_studied %nin% c('other', 'none', 'northern_hemisphere', 'west_africa', 'global')) %>% 
  count(collab_type, author_in_country_studied, sort = TRUE) %>% 
  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
  replace_na(list(yes = 0, no = 0)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no')) %>% 
  adorn_pct_formatting(... = c('yes', 'no')) %>% 
  adorn_ns(... = c('yes', 'no'))

knitr::kable(author_connectedness_to_location_aggreg, caption = 'At least one author with an affiliation in the studied location', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

<!-- ## Diseases studied per collab type -->

<!-- ```{r echo=FALSE} -->
<!-- #count the number of unique diseases studied -->
<!-- disease_studied_by_collab_type <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   separate_rows(disease,  sep = ' ') %>%  -->
<!--   distinct(title, disease, .keep_all = TRUE) %>%  -->
<!--   count(collab_type, disease, sort = TRUE) %>% -->
<!--   pivot_wider(names_from = collab_type, values_from = n) %>%  -->
<!--   replace_na(list(purely_academic = 0, mixed = 0)) %>%  -->
<!--   adorn_totals(where = c('row', 'col')) %>%  -->
<!--   adorn_percentages(... = c('purely_academic', 'mixed')) %>%  -->
<!--   adorn_pct_formatting(... = c('purely_academic', 'mixed')) %>%  -->
<!--   adorn_ns(... = c('purely_academic', 'mixed')) %>%  -->
<!--   mutate(disease = str_to_sentence(str_replace(disease, '_', ' '))) %>%  -->
<!--   arrange(desc(Total)) -->

<!-- knitr::kable(disease_studied_by_collab_type, caption = 'Number of studies per disease and collaboration type', format = "latex", booktabs = TRUE) %>%  -->
<!--         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position')) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #tally the diseases by collaboration type -->
<!-- disease_by_collab_type_long <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   separate_rows(disease,  sep = ' ') %>%  -->
<!--   count(collab_type, disease, sort = TRUE)  -->

<!-- disease_by_collab_type_plot <- ggplot(disease_by_collab_type_long) +  -->
<!--   geom_bar(aes(x = reorder(disease, n),  -->
<!--                y = n,  -->
<!--                fill = collab_type -->
<!--                ),  -->
<!--            color = 'black', -->
<!--            stat = 'identity', -->
<!--            position = position_fill(reverse = TRUE) -->
<!--            ) +  -->
<!--   labs(x = '**Disease**', y = '**Number of studies**') +  -->
<!--   coord_flip() + -->
<!--   md_theme_minimal(base_size = 12) -->

<!-- print(disease_by_collab_type_plot) -->
<!-- ``` -->

## Interventions

### Types of interventions

```{r}
intervention_categories <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, intervention_type, sort = TRUE) %>% 
  pivot_wider(names_from = intervention_type, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
  adorn_pct_formatting(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
  adorn_ns(... = c('no_vax', 'vax_combination_with_others', 'vax_single'))

knitr::kable(intervention_categories, caption = 'Number of studies per intervention categories', format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

### Impact of vaccination

```{r}
vax_impact_conclusions <- compact_data_with_citation_keys_no_fmd %>% 
  filter(intervention_type == 'vax_single') %>% 
  count(collab_type, is_vax_effective, sort = T) %>% 
  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
    replace_na(list(yes = 0, n0 = 0, the_outcomes_were_inconclusive = 0)) %>% 
  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_ns(... = c('yes', 'no', 'inconclusive'))

#Print the results
knitr::kable(vax_impact_conclusions, 
             caption = 'Conclusions about impact of vaccination', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position')
                                  )
```

```{r eval=FALSE}
no_vax_modelled <- compact_data_with_citation_keys_no_fmd %>% 
    separate_rows(disease,  sep = ' ') %>% 
    filter(vax_modelled == 'no') %>% 
    count(disease, sort = TRUE, name = 'num_of_studies') %>% 
     adorn_totals(where = 'row') %>% 
    adorn_percentages(denominator = 'col') %>% 
    adorn_pct_formatting() %>% 
    adorn_ns()

knitr::kable(no_vax_modelled, caption = 'Number of studies per disease for which vaccination was not modelled', format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

```{r eval=FALSE}
vax_impact_by_disease <- compact_data_with_citation_keys_no_fmd %>% 
  filter(intervention_type == 'vax_single') %>% 
  count(disease, is_vax_effective, sort = T) %>% 
  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
    replace_na(list(yes = 0, no = 0, inconclusive = 0)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_ns(... = c('yes', 'no', 'inconclusive'))

#Print the results
knitr::kable(vax_impact_by_disease, 
             caption = 'Conclusions about impact of vaccination per disease', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

```{r eval=FALSE}
no_vax_impact_by_disease_citation_table <- compact_data_with_citation_keys_no_fmd %>% 
  filter(intervention_type == 'vax_single', is_vax_effective %in% c('no', 'the_outcomes_were_inconclusive')) %>% 
  select(title, disease, bibtexkey, publication_year, intervention_modelled, is_vax_effective)

#Print the results
# knitr::kable(no_vax_impact_by_disease_citation_table, 
#              caption = 'Studies that did not find vaccination as most impactful'
#              )

write.xlsx(no_vax_impact_by_disease_citation_table, file = '../citation_tables/no_vax_impact_by_disease_citation_table.xlsx')
```

```{r eval=FALSE}
vax_as_single_intervention_studies <- compact_data_with_citation_keys_no_fmd %>% 
  filter(intervention_type == 'vax_single') %>% 
  select(title, disease, bibtexkey, publication_year, intervention_modelled)

#Print the results
# knitr::kable(no_vax_impact_by_disease_citation_table, 
#              caption = 'Studies that did not find vaccination as most impactful'
#              )

write.xlsx(vax_as_single_intervention_studies, file = '../citation_tables/vax_as_single_intervention_studies.xlsx')
```

## Modelling objectives 
<!-- We grouped studies into whether they assessed the impact of a future intervention strategy (prospective), a past intervention, or both (dual).  -->

<!-- In general, there were more (73.2%; 167/228) studies about prospective intervention impact assessments than retrospective assessments (24.6%; 56/228), and the dual (2.2%; 5/228). A similar pattern was observed across the two collaboration types except that purely academic collaborations were more likely to perform the dual assessments.   -->

<!-- In terms of the outbreak types, there was an approximately equal number of papers about real and hypothetical outbreaks overall, and there was no clear difference between the two collaborations.   -->

```{r echo=FALSE}
#count the number of studies per objective type
modelling_objectives_count <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, objectives, name = 'num_of_studies') %>% 
  pivot_wider(names_from = objectives, values_from = num_of_studies) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('both', 'future', 'past')) %>% 
  adorn_pct_formatting(... = c('both', 'future', 'past')) %>% 
  adorn_ns(... = c('both', 'future', 'past'))

#Print a table of the results
knitr::kable(modelling_objectives_count,
             caption = 'Study objectives by collaboration type', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

## Outbreak types

```{r echo=FALSE}
#Outbreak types per collab type
outbreak_types_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, outbreak_type, name = 'num_of_studies') %>% 
  pivot_wider(names_from = outbreak_type, values_from = num_of_studies) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('hypothetical_outbreak', 'real_outbreak')) %>% 
  adorn_pct_formatting(... = c('hypothetical_outbreak', 'real_outbreak')) %>% 
  adorn_ns(... = c('hypothetical_outbreak', 'real_outbreak'))

#Print a table of the results
knitr::kable(outbreak_types_by_collab_type,
             caption = 'outbreak types by collaboration type', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

```{r eval=FALSE}
objectives_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
  count(objectives, collab_type, name = 'num_of_studies', sort = TRUE) %>% 
  pivot_wider(names_from = objectives, 
              values_from = num_of_studies
              ) %>% 
  replace_na(list(future = 0, past = 0, both = 0)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('future', 'past', 'both')) %>% 
  adorn_pct_formatting(... = c('future', 'past', 'both')) %>% 
  adorn_ns(... = c('future', 'past', 'both'))

knitr::kable(objectives_by_collab_type, 
             caption = 'Number of studies per objective by collaboration type', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

<!-- ## Model characteristics  -->

## Individual heterogeneity: agent-based versus compartmental models

```{r}
individual_representation <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, individual_representation, sort = TRUE) %>% 
  pivot_wider(names_from = individual_representation, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('compartments', 'agents', 'individuals_representation_other')) %>% 
  adorn_pct_formatting(... = c('compartments', 'agents', 'individuals_representation_other')) %>% 
  adorn_ns(... = c('compartments', 'agents', 'individuals_representation_other'))

knitr::kable(individual_representation, caption = 'How individuals were represented', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```
<!-- ### Individual representation by model structure -->
<!-- ```{r} -->
<!-- mod_structure_vs_individual_representation <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   group_by(collab_type) %>%  -->
<!--   count(model_structure, individual_representation, sort = TRUE) %>%  -->
<!--   pivot_wider(names_from = model_structure, values_from = n) %>%  -->
<!--   adorn_totals(where = c('col', 'row')) -->

<!-- knitr::kable(mod_structure_vs_individual_representation, caption = 'Model structure versus individual heterogeneity') -->
<!-- ``` -->

## Spatial heterogeneity

```{r}
space_representation <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, space_representation, sort = TRUE) %>% 
  pivot_wider(names_from = space_representation, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('no', 'yes')) %>% 
  adorn_pct_formatting(... = c('no', 'yes')) %>% 
  adorn_ns(... = c('no', 'yes'))

knitr::kable(space_representation, caption = 'Was space explicitly represented in the model',
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

<!-- ### Spatial models by model structure -->
<!-- ```{r} -->
<!-- mod_structure_vs_space_representation <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   group_by(collab_type) %>%  -->
<!--   count(model_structure, space_representation, sort = TRUE) %>%  -->
<!--   pivot_wider(names_from = model_structure, values_from = n) %>%  -->
<!--   adorn_totals(where = c('col', 'row')) -->

<!-- knitr::kable(mod_structure_vs_space_representation, caption = 'Model structure versus spatial heterogeneity') -->
<!-- ``` -->

## Model dynamics: deterministic vs stochastic

```{r}
stochastic_vs_deterministic <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, model_structure) %>% 
  pivot_wider(names_from = model_structure, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('both', 'deterministic', 'stochastic')) %>% 
  adorn_pct_formatting(... = c('both', 'deterministic', 'stochastic')) %>% 
  adorn_ns(... = c('both', 'deterministic', 'stochastic'))

knitr::kable(stochastic_vs_deterministic, caption = 'Model dynamics (deterministic versus stochastic)', format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

<!-- ## Modelling methods -->

## Outcomes measured

<!-- We tallied the overall top five outcomes most used between the two collaboration types.  -->

<!-- The top five most commonly used outcomes, irrespective of collaboration type, were: final epidemic size, attack rate, timing of epidemic peak, cases averted, and outbreak duration. -->

<!-- There was no difference in the two collaboration types as they were commonly used by both groups. -->

```{r}
outcomes_overall <- compact_data_with_citation_keys_no_fmd %>% 
mutate(outcome_measured = str_trim(outcome_measured)) %>% 
  separate_rows(outcome_measured, sep = ',') %>% 
  group_by(collab_type, outcome_measured) %>% 
  distinct(title, .keep_all = TRUE) %>% 
  filter(outcome_measured %nin% c('outcome_other', '', 's')) %>% 
  count(collab_type, outcome_measured, name = 'num_of_studies') %>% 
  ungroup(outcome_measured) %>% 
  arrange(desc(num_of_studies), .by_group = TRUE) %>% 
  ungroup() %>% 
  adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns()

knitr::kable(outcomes_overall, caption = 'Model outcomes by collaboration type', 
             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position', 'repeat_header'), font_size = 8)
```

```{r eval=FALSE}
outcomes_tally_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
  mutate(outcome_measured = str_trim(outcome_measured)) %>% 
  separate_rows(outcome_measured, sep = ',') %>% 
  group_by(outcome_measured) %>% 
  distinct(title, .keep_all = TRUE) %>% 
  ungroup(outcome_measured) %>% 
  filter(outcome_measured %nin% c('outcome_other', '')) %>% 
  group_by(collab_type) %>% 
  count(outcome_measured) %>% 
  arrange(desc(n), .by_group = TRUE) %>% 
  # slice(1:6) %>% 
  ungroup()

# outcomes_tally_plot <- ggplot(data = outcomes_tally_by_collab_type, 
#                               aes(x = reorder(outcome_measured, n), 
#                                   y = n
#                                   )
#                               ) + 
#   geom_bar(stat = 'identity') + 
#   labs(x = '**Outcome**', y = '**Number of times used**') +
#   coord_flip() +
#   facet_wrap('collab_type') +
#   md_theme_minimal()

collab_type_labels <- c('purely_academic' = 'Purely academic', 
                        'mixed' = 'Mixed'
                        )

outcomes_tally_plot <- ggplot(data = outcomes_tally_by_collab_type, 
                              aes(label = outcome_measured, 
                                  size = n
                                  )
                              ) + 
  geom_text_wordcloud_area() +
  scale_size_area(max_size = 10) + 
  facet_wrap(~ collab_type, 
             labeller = as_labeller(collab_type_labels),
             strip.position = 'top'
             ) +
  #theme_minimal() + 
  theme(strip.text = element_text(size = 15, face = 'bold'))

print(outcomes_tally_plot)

ggsave(filename = 'outcomes_tally_plot.tiff',
       plot = outcomes_tally_plot, 
       device = 'tiff',
       path = save_fig_here
       )

ggsave(filename = 'outcomes_tally_plot.tiff',
       plot = outcomes_tally_plot, 
       device = 'tiff',
       path = save_thesis_fig_here
       )
```

<!-- ### Parametrization methods -->

<!-- ```{r} -->
<!-- #wide data for table -->
<!-- model_parametrization_wide <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   count(collab_type, parametrization, sort = TRUE) %>%  -->
<!--   pivot_wider(names_from = parametrization, values_from = n) %>%  -->
<!--   adorn_totals(where = c('row', 'col')) %>%  -->
<!--   adorn_percentages(... = -c('Total', 'collab_type')) %>%  -->
<!--   adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%  -->
<!--   adorn_ns(... = -c('Total', 'collab_type'))  -->

<!-- #table -->
<!-- knitr::kable(model_parametrization_wide, caption = 'How model parameters are obtained',  -->
<!--              format = "latex", booktabs = TRUE) %>%  -->
<!--         kableExtra::kable_styling(latex_options = c('striped', 'scale_down', 'HOLD_position')) -->
<!-- ``` -->

<!-- ```{r eval=FALSE} -->
<!-- #long data for plotting -->
<!-- model_parametrization_long <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   group_by(collab_type) %>%  -->
<!--   count(parametrization, sort = TRUE) -->

<!-- #plotting -->
<!-- ggplot(data = model_parametrization_long,  -->
<!--        aes(fill = collab_type,  -->
<!--            area = n,  -->
<!--            label = parametrization, -->
<!--            subgroup = parametrization -->
<!--            ) -->
<!--        ) +  -->
<!--   geom_treemap() + -->
<!--   geom_treemap_text(colour = "white", -->
<!--                     place = "centre", -->
<!--                     size = 15, -->
<!--                     grow = TRUE -->
<!--                     ) + -->
<!--   md_theme_minimal(base_size = 12)  -->

<!-- ``` -->

<!-- ### Validation methods  -->

<!-- ```{r} -->
<!-- #wide data for table -->
<!-- model_validation_wide <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   count(collab_type, validation, sort = TRUE) %>%  -->
<!--   pivot_wider(names_from = validation, values_from = n) %>%  -->
<!--   replace_na(list(none = 0,  -->
<!--                   data = 0,  -->
<!--                   another_model = 0,  -->
<!--                   none_and_data = 0,  -->
<!--                   data_and_another_model = 0 -->
<!--                   ) -->
<!--              ) %>%  -->
<!--   adorn_totals(where = c('row', 'col')) %>%  -->
<!--   adorn_percentages(... = -c('Total', 'collab_type')) %>%  -->
<!--   adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%  -->
<!--   adorn_ns(... = -c('Total', 'collab_type'))  -->

<!-- #table -->
<!-- knitr::kable(model_validation_wide, caption = 'How the model\'s performance is assessed',  -->
<!--              format = "latex", booktabs = TRUE) %>%  -->
<!--         kableExtra::kable_styling(latex_options = c('striped', 'scale_down', 'HOLD_position')) -->
<!-- ``` -->

## Sensitivity analysis

<!-- Less than half (46.5%; 106/228) of the total studies performed sensitivity analyses. There was no clear difference between the collaborations.  -->

```{r eval=FALSE}
mod_structure_vs_sensitivity_analysis <- compact_data_with_citation_keys_no_fmd %>% 
  count(model_structure, sensitivity_analysis, sort = TRUE) %>% 
  pivot_wider(names_from = sensitivity_analysis, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('no', 'yes')) %>% 
  adorn_pct_formatting(... = c('no', 'yes')) %>% 
  adorn_ns(... = c('no', 'yes'))

knitr::kable(mod_structure_vs_sensitivity_analysis, 'Sensitivity analysis in relation to model structure', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))

```

```{r}
sensitivity_analysis <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, sensitivity_analysis, sort = TRUE) %>% 
  pivot_wider(names_from = sensitivity_analysis, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('no', 'yes')) %>% 
  adorn_pct_formatting(... = c('no', 'yes')) %>% 
  adorn_ns(... = c('no', 'yes'))

knitr::kable(sensitivity_analysis, caption = 'Sensitivity analysis', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))

```

## Data use and data availability

```{r}
data_use_and_availability <- compact_data_with_citation_keys_no_fmd %>% 
  filter(data_used == 'yes') %>%
  count(collab_type, data_available, sort = TRUE) %>% 
  pivot_wider(names_from = data_available, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('no', 'yes')) %>% 
  adorn_pct_formatting(... = c('no', 'yes')) %>% 
  adorn_ns(... = c('no', 'yes'))

knitr::kable(data_use_and_availability, 
             caption = 'Data accessibility', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))

```

## Code availability

```{r}
code_availability <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, simulation_code_available) %>% 
  pivot_wider(names_from = simulation_code_available, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('no', 'yes')) %>% 
  adorn_pct_formatting(... = c('no', 'yes')) %>% 
  adorn_ns(... = c('no', 'yes'))

knitr::kable(code_availability, caption = 'Code availability', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

```{r eval=FALSE}
papers_with_code_available <- compact_data_with_citation_keys_no_fmd %>% 
    filter(simulation_code_available == 'yes') %>% 
    as.data.frame()

openxlsx::write.xlsx(papers_with_code_available, file = '../citation_tables/papers_with_code_available.xlsx')

```

# Foot and mouth disease (FMD)

<!-- ## Collaboration patterns in time -->

## Unique combinations of author affiliation types

```{r}
#' Count by collaboration types and make a bar plot
author_affiliation_type_combos <- fmd_data %>%
    count(author_affiliation_type, sort = TRUE) %>% 
    mutate(author_affiliation_type = as_factor(author_affiliation_type)) %>% 
    arrange(desc(n)) %>% 
    adorn_totals() %>% 
    adorn_percentages(denominator = 'col') %>% 
    adorn_pct_formatting() %>% 
    adorn_ns()

knitr::kable(author_affiliation_type_combos, caption = 'Number of studies by author affiliation type combination',
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

## Collaboration types (aggregated)

```{r}
#' Count by collaboration types and make a bar plot
studies_per_collab_type <- fmd_data %>%
    count(collab_type, sort = TRUE) %>% 
    arrange(desc(n)) %>% 
    adorn_totals() %>% 
    adorn_percentages(denominator = 'col') %>% 
    adorn_pct_formatting() %>% 
    adorn_ns()

knitr::kable(studies_per_collab_type, caption = 'Number of studies per collaboration type',
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

### Proportions of the total publications per year by collaboration type

```{r echo=FALSE, fig.width=8}
#' Count the number of each author affiliation type per year (including FMD)
fmd_collab_types_per_year <- fmd_data %>% 
  count(year_aggreg, 
        collab_type, 
        name = 'total_publications'
        )

#The plot
# Modify the x-axis labels to account for the lumping of the years from 2005 and below
x_axis_labels <- as.character(seq(2005, 2020, 2))

x_axis_labels[1] <- '1970-2005'

fmd_collab_proportions_plot <- ggplot(data = fmd_collab_types_per_year) + 
  geom_bar(aes(x = year_aggreg,
               y = total_publications,
               fill = collab_type
               ),
           color = 'black',
           stat = 'identity',
           position = position_fill(reverse = TRUE)#,
           #show.legend = FALSE
             ) +
  scale_fill_manual(values = c('tan3', 'turquoise2')) +
  scale_x_continuous(breaks = seq(2005, 2020, 2),
                     labels = x_axis_labels,
                     expand = c(0, 0)
                     ) +
  #coord_flip() +
  labs(#title = 'Publications per collaboration type over time',
       x = '**Year**',
       y = '**Proportion of total publications**',
       fill = '**Collaboration type**' 
         ) +
  theme(legend.position = 'none') +
 # md_theme_minimal(base_size = 16) #For Powerpoint
  md_theme_minimal(base_size = 12)

plot(fmd_collab_proportions_plot)

```

### Absolute number of publications per year by collaboration type

```{r}
#' Count the number of each author affiliation type per year
fmd_collabs_per_year <- fmd_data %>% 
  count(year_aggreg, 
        collab_type, 
        name = 'total_publications'
        )

collabs_per_year_plot <- ggplot(data = fmd_collabs_per_year, 
                                    aes(x = year_aggreg, 
                                        y = total_publications
                                        ), 
                                    color = 'black') + 
  geom_bar(aes(fill = collab_type), 
           stat = 'identity', 
           position = 'dodge',
           width = 0.5
           ) + 
  scale_fill_manual(values = c('tan3', 'turquoise2')) + 
  scale_x_continuous(breaks = seq(2005, 2020, 2),
                     labels = x_axis_labels,
                     expand = c(0, 0)
                     ) +
  labs(x = '**Year**', 
       y = '**Total publications**', 
       fill = 'Collaboration type'
       ) +
  md_theme_minimal(base_size = 12) +
  #md_theme_minimal(base_size = 16) +
  theme(legend.position = 'bottom')

plot(collabs_per_year_plot)

```

<!-- ## Collaboration patterns in geographic space -->

## Geographic connection of authors to the studied locations 
```{r}
author_connectedness_to_location_fmd <- fmd_data %>% 
  filter(author_in_country_studied != 'not_applicable') %>% 
  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
  group_by(collab_type) %>% 
  count(country_studied, author_in_country_studied, sort = TRUE) %>% 
  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
  replace_na(list(yes = 0, no = 0)) %>% 
  arrange(collab_type, desc(yes)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no')) %>% 
  adorn_pct_formatting(... = c('yes', 'no')) %>% 
  adorn_ns(... = c('yes', 'no')) %>% 
  ungroup()

knitr::kable(author_connectedness_to_location_fmd, caption = 'Studies with at least one author affiliation in the location studied', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

### Aggregated

```{r}
author_connectedness_to_location_aggreg <- fmd_data %>% 
  filter(author_in_country_studied != 'not_applicable') %>% 
  filter(country_studied %nin% c('other', 'none', 'northern_hemisphere', 'west_africa', 'global')) %>% 
  count(collab_type, author_in_country_studied, sort = TRUE) %>% 
  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
  replace_na(list(yes = 0, no = 0)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no')) %>% 
  adorn_pct_formatting(... = c('yes', 'no')) %>% 
  adorn_ns(... = c('yes', 'no'))

knitr::kable(author_connectedness_to_location_aggreg, 
             caption = 'Studies with at least one author affiliation in the location studied', format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

## Interventions

### Types of interventions

```{r}
intervention_categories_fmd <- fmd_data %>% 
  count(collab_type, intervention_type, sort = TRUE) %>% 
  pivot_wider(names_from = intervention_type, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
  adorn_pct_formatting(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
  adorn_ns(... = c('no_vax', 'vax_combination_with_others', 'vax_single'))

knitr::kable(intervention_categories_fmd, caption = 'Number of studies per intervention type', format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

### Impact of vaccination

```{r}
fmd_vax_impact_conclusions <- fmd_data %>% 
  filter(intervention_type == 'vax_single') %>% 
  count(collab_type, is_vax_effective, sort = T) %>% 
  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
  replace_na(list(no = 0, inconclusive = 0, yes = 0)) %>% 
  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
  adorn_ns(... = c('yes', 'no', 'inconclusive'))

#Print the results
knitr::kable(fmd_vax_impact_conclusions, 
             caption = 'Conclusions about impact of vaccination', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

## Modelling objectives

```{r echo=FALSE}
#count the number of studies per objective type
modelling_objectives_fmd <- fmd_data %>% 
  count(collab_type, objectives, name = 'num_of_studies') %>% 
  pivot_wider(names_from = objectives, values_from = num_of_studies) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('future', 'past')) %>% 
  adorn_pct_formatting(... = c('future', 'past')) %>% 
  adorn_ns(... = c('future', 'past'))

#Print a table of the results
knitr::kable(modelling_objectives_fmd,
             caption = 'Study objectives by collaboration type', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

<!-- ### Modelling objectives and outbreak type by collaboration types -->

<!-- ```{r echo=FALSE} -->
<!-- objectives_and_outbreak_types_fmd <- fmd_data %>%  -->
<!--   count(objectives, outbreak_type, name = 'num_of_studies', sort = TRUE) %>%  -->
<!--   pivot_wider(names_from = objectives,  -->
<!--               values_from = num_of_studies -->
<!--               ) %>%  -->
<!--   replace_na(list(future = 0, past = 0, both = 0)) %>%  -->
<!--   adorn_totals(where = c('row', 'col')) %>%  -->
<!--   adorn_percentages(... = c('future', 'past')) %>%  -->
<!--   adorn_pct_formatting(... = c('future', 'past')) %>%  -->
<!--   adorn_ns(... = c('future', 'past'))  -->

<!-- knitr::kable(objectives_and_outbreak_types_fmd,  -->
<!--              caption = 'Number of studies per objective and outbreak type',  -->
<!--              format = "latex", booktabs = TRUE) %>%  -->
<!--         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position')) -->
<!-- ``` -->

## Outbreak types

```{r echo=FALSE}
#Outbreak types per collab type
outbreak_types_by_collab_type_fmd <- fmd_data %>% 
  count(collab_type, outbreak_type, name = 'num_of_studies') %>% 
  pivot_wider(names_from = outbreak_type, values_from = num_of_studies) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('hypothetical_outbreak', 'real_outbreak')) %>% 
  adorn_pct_formatting(... = c('hypothetical_outbreak', 'real_outbreak')) %>% 
  adorn_ns(... = c('hypothetical_outbreak', 'real_outbreak'))

#Print a table of the results
knitr::kable(outbreak_types_by_collab_type_fmd,
             caption = 'Study objectives by collaboration type', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

<!-- ## Model characteristics  -->

## Individual heterogeneity: agent-based versus compartmental models

```{r}
individual_representation_fmd <- fmd_data %>% 
  count(collab_type, individual_representation, sort = TRUE) %>% 
  pivot_wider(names_from = individual_representation, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('compartments', 'agents')) %>% 
  adorn_pct_formatting(... = c('compartments', 'agents')) %>% 
  adorn_ns(... = c('compartments', 'agents'))

knitr::kable(individual_representation_fmd, 
             caption = 'How individuals are represented', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

## Spatial heterogeneity

```{r}
space_representation_fmd <- fmd_data %>% 
  count(collab_type, space_representation, sort = TRUE) %>% 
  pivot_wider(names_from = space_representation, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('no', 'yes')) %>% 
  adorn_pct_formatting(... = c('no', 'yes')) %>% 
  adorn_ns(... = c('no', 'yes'))

knitr::kable(space_representation_fmd, caption = 'Models with spatial structure', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

## Model dynamics: deterministic vs stochastic

```{r}
stochastic_vs_deterministic_fmd <- fmd_data %>% 
  count(collab_type, model_structure) %>% 
  pivot_wider(names_from = model_structure, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('deterministic', 'stochastic')) %>% 
  adorn_pct_formatting(... = c('deterministic', 'stochastic')) %>% 
  adorn_ns(... = c('deterministic', 'stochastic'))

knitr::kable(stochastic_vs_deterministic_fmd, 
             caption = 'Model dynamics (deterministic versus stochastic)', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))

```

<!-- ## Modelling methods -->

## Outcomes measured
```{r}
outcomes_tally_by_collab_type <- fmd_data %>% 
  mutate(outcome_measured = str_trim(outcome_measured)) %>% 
  separate_rows(outcome_measured, sep = ',') %>% 
  group_by(collab_type, outcome_measured) %>% 
  distinct(title, .keep_all = TRUE) %>% 
  filter(outcome_measured %nin% c('outcome_other', '')) %>% 
  count(collab_type, outcome_measured, name = 'num_of_studies') %>% 
  ungroup(outcome_measured) %>% 
  arrange(desc(num_of_studies), .by_group = TRUE) %>% 
  ungroup() %>% 
  adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns()

knitr::kable(outcomes_tally_by_collab_type, 
             caption = 'Model outcomes by collaboration type', 
             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position', 'repeat_header'))
```

```{r eval=FALSE}
collab_type_labels <- c('purely_academic' = 'Purely academic', 
                        'mixed' = 'Mixed'
                        )

outcomes_tally_plot <- ggplot(data = outcomes_tally_by_collab_type, 
                              aes(label = outcome_measured, 
                                  size = n
                                  )
                              ) + 
  geom_text_wordcloud_area() +
  scale_size_area(max_size = 7) + 
  facet_wrap(~ collab_type, 
             labeller = as_labeller(collab_type_labels),
             strip.position = 'top'
             ) +
  #theme_minimal() + 
  theme(strip.text = element_text(size = 15, face = 'bold'))

#save the plot
ggsave(filename = 'outcomes_tally_fmd_plot.tiff',
       plot = outcomes_tally_plot, 
       device = 'tiff',
       path = save_fig_here
       )
```

## Parametrization methods

```{r}
#wide data for table
model_parametrization_fmd_wide <- fmd_data %>% 
  count(collab_type, parametrization, sort = TRUE) %>% 
  pivot_wider(names_from = parametrization, values_from = n) %>% 
  replace_na(list('expert_opinion and fitted' = 0, 'literature and fitted' = 0)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = -c('Total', 'collab_type')) %>% 
  adorn_pct_formatting(... = -c('Total', 'collab_type')) %>% 
  adorn_ns(... = -c('Total', 'collab_type')) 
#table
knitr::kable(model_parametrization_fmd_wide, 
             caption = 'Model parametrization methods', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'scale_down',  'HOLD_position'))
```

## Validation methods

```{r}
#wide data for table
model_validation_fmd_wide <- fmd_data %>% 
  count(collab_type, validation, sort = TRUE) %>% 
  pivot_wider(names_from = validation, values_from = n) %>% 
  replace_na(list(none = 0, 
                  data = 0, 
                  another_model = 0, 
                  data_and_another_model = 0
                  )
             ) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = -c('Total', 'collab_type')) %>% 
  adorn_pct_formatting(... = -c('Total', 'collab_type')) %>% 
  adorn_ns(... = -c('Total', 'collab_type'))

#table
knitr::kable(model_validation_fmd_wide, 
             caption = 'Model validation methods', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped',  'HOLD_position'))
```

## Sensitivity analysis

```{r}
sensitivity_analysis_fmd <- fmd_data %>% 
  count(collab_type, sensitivity_analysis, sort = TRUE) %>% 
  pivot_wider(names_from = sensitivity_analysis, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('no', 'yes')) %>% 
  adorn_pct_formatting(... = c('no', 'yes')) %>% 
  adorn_ns(... = c('no', 'yes'))

knitr::kable(sensitivity_analysis_fmd, caption = 'Sensitivity analysis', format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped',  'HOLD_position'))

```

## Data use and data availability

```{r}
data_use_and_availability_fmd <- fmd_data %>% 
  filter(data_used == 'yes') %>%
  count(collab_type, data_available, sort = TRUE) %>% 
  pivot_wider(names_from = data_available, values_from = n) %>% 
  replace_na(list(yes = 0, no = 0)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no')) %>% 
  adorn_pct_formatting(... = c('yes', 'no')) %>% 
  adorn_ns(... = c('yes', 'no'))

knitr::kable(data_use_and_availability_fmd, 
             caption = 'Data accessibility', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))

```

## Code availability

```{r}

code_availability_fmd <- fmd_data %>% 
  count(collab_type, simulation_code_available) %>% 
  pivot_wider(names_from = simulation_code_available, values_from = n) %>% 
  adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns()

knitr::kable(code_availability_fmd, caption = 'Code availability', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

### 2023-03-02 scripts/orv_sys_rev_data_analysis_old.Rmd
added manuscript files

---
title: "Systematic review of outbreak response models"
author: "James Azam"
date: "01/06/2021"
output:
  word_document:
    keep_md: yes
#  html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Sets the working directory for subsequent chunks, but not this chunk
#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

knitr::opts_chunk$set(fig.width = 8, fig.height = 6)
```

```{r echo=FALSE, message=FALSE}
#' load packages
library('tidyverse')
library('readr')
library('ggthemes')
library('scales')
library('janitor')
library('forcats')
library('stringr')
library('countrycode')
library('bib2df')
library('conflicted')

#resolve package function conflicts
conflict_prefer('filter', 'dplyr')
conflict_prefer('select', 'dplyr')
conflict_prefer('kable', 'knitr')
```

```{r echo=FALSE, include=FALSE, eval=FALSE}
# Source the script that cleans the raw data
# Load the script that cleans the data and saves it; 
# this should be run each time, just in case something has changed in the data cleaning process;
# The script clears the environment after cleaning the data
#source('./data_cleaning/orv_models_review_data_cleaning.R')
```

```{r echo=FALSE, include=FALSE}
# Load the cleaned data 
long_data <- read_rds('../data/final_data/cleaned_data/review_data_long_cleaned.rds')

#The cleaned data without citations
compact_data_init <- read_rds('../data/final_data/cleaned_data/review_data_compact_cleaned.rds')

compact_data <- compact_data_init %>% 
    mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
                               'yes', 
                               'no')
         ) %>% 
  mutate(intervention_type = case_when(
    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_alongside', #when vax was modelled but not for comparison as a single intervention
    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
  )) %>% 
  relocate(vax_modelled, intervention_type, .after = 'intervention_modelled')

# The data with citations 
compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/final_data/cleaned_data/compact_data_with_citation_keys_cleaned.rds'))

compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>% 
  mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
                               'yes', 
                               'no')
         ) %>% 
  mutate(intervention_type = case_when(
    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_alongside', #when vax was modelled but not for comparison as a single intervention
    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
  )) %>% 
  relocate(vax_modelled, intervention_type, .after = 'intervention_modelled')

# Remove the FMD papers (NB: We only use the FMD papers for comparison)
long_data_no_fmd <- long_data %>% filter(disease != 'fmd')

compact_data_no_fmd <- compact_data %>% filter(disease != 'fmd')

compact_data_with_citation_keys_no_fmd <- compact_data_with_citation_keys %>% filter(disease != 'fmd') 
```

# Exploratory Data Analysis
1. Publications per year
2. Distribution of collaborations across types (aggregated)
3. Countries/settings being studied (author affiliation vs country studied)

# What science is being inferred from models?

1. Impact of vaccination (human diseases vs FMD); analyse with and without Influenza
2. What diseases are being studied (to understand vaccine impact)
3. Which interventions are being studied?

```{r echo=FALSE}

pubs_per_year <- compact_data_no_fmd %>% 
  mutate(publication_year = as.numeric(publication_year)) %>% 
  count(publication_year)

pubs_per_year_bar_plot <- ggplot(data = pubs_per_year) + 
  geom_bar(aes(x = publication_year, 
               y = n
               ), 
           stat = 'identity', 
           color = 'black',
           fill = 'tomato3') +
  scale_y_continuous(breaks = seq(0, 30, 2),
                     labels = seq(0, 30, 2)
                     ) +
  labs(x = 'Year of publication', y = 'Number of papers') +
  theme_minimal()

plot(pubs_per_year_bar_plot)

```

# Modelling objectives

```{r echo=FALSE}
#Find the uniques entries
modelling_objectives_unique_entries <- long_data_no_fmd %>% 
  select(title, objectives) %>% 
  distinct()

#count the number of studies per objective type
modelling_objectives_count <- modelling_objectives_unique_entries %>% 
  count(objectives, name = 'num_of_studies')

#Print a table of the results
knitr::kable(modelling_objectives_count,
             col.names = c('Objective type',
                           'Number of studies'
                           ),
             caption = 'Number of studies per objective type'
             )
```

```{r echo=FALSE}
#Find the unique entries 
outbreak_types_unique_entries <- long_data_no_fmd %>% 
  select(title, outbreak_type) %>% 
  distinct()

#Count the number of studies per outbreak type  
outbreak_types_count <- outbreak_types_unique_entries %>% 
  count(outbreak_type, name = 'num_of_studies')

#Print a table of the results
knitr::kable(outbreak_types_count,
             col.names = c('Outbreak type',
                           'Number of studies'
                           ),
             caption = 'Number of studies per outbreak type'
             )
```

```{r echo=FALSE}
#Find the number of unique entries per objective type and outbreak type combination  
modelling_objectives_by_outbreak_type_unique_entries <- long_data_no_fmd %>% 
  select(title, objectives, outbreak_type) %>% 
  group_by(title) %>% 
  distinct() %>% 
  ungroup()

modelling_objectives_by_outbreak_type_count <- modelling_objectives_by_outbreak_type_unique_entries %>% 
  count(objectives, outbreak_type, name = 'num_of_studies') %>% 
  arrange(desc(num_of_studies)) %>% 
  pivot_wider(names_from = outbreak_type, 
              values_from = num_of_studies
              )

knitr::kable(modelling_objectives_by_outbreak_type_count, 
             # col.names = c('Objective type', 
             #               'Outbreak type', 
             #               'Number of studies'
             #               ),
             caption = 'Number of studies per objective and outbreak type'
             ) 
```

```{r echo=FALSE} 
#Year with the highest publications
max_pub_year <- compact_data_no_fmd %>% 
    count(publication_year, sort = T) %>% 
    filter(n == max(n))

print(max_pub_year)
```

## Number of studies per disease 
```{r echo=FALSE}
disease_studied_count <- long_data_no_fmd %>% 
  group_by(disease) %>% 
  distinct(title) %>% 
  count(disease, name = 'num_of_studies', sort = T) %>%
  ungroup()

knitr::kable(disease_studied_count, col.names = c('Disease', 'Number of studies'))
```

### Disease most studied
```{r echo=FALSE}
disease_studied_most <- disease_studied_count %>% 
  filter(num_of_studies == max(num_of_studies))

knitr::kable(disease_studied_most)
```

## Number of studies per country and continent

```{r echo=FALSE, warning=FALSE, message=FALSE}
#FIXME: I have to cross tabulate the countries studied with number of studies with at least one author located in the country being studied.

#Tally of how many times and percentage of times each COUNTRY has been studied
countries_studied_by_count <- long_data_no_fmd %>% 
    group_by(country_studied) %>%
    distinct(title) %>% 
    count(country_studied, name = 'num_of_studies', sort = T) %>% 
    ungroup(country_studied) %>% 
    mutate(country_studied = as_factor(country_studied), 
           percentage = round(num_of_studies/sum(num_of_studies)*100, 1)
           )

#'Modify the data frame to lump together all countries with less than some number of studies as 'other' and recalculate the percentage studied
countries_studied_by_count_aggregated <- countries_studied_by_count %>% 
  mutate(country_studied_aggreg = if_else(num_of_studies < 9, 
                                          'other', 
                                          as.character(country_studied)
                                          )
         ) %>% 
  group_by(country_studied_aggreg) %>%
  summarise(num_of_studies = sum(num_of_studies),
            percentage = sum(percentage),
            .groups = 'drop'
            ) %>% 
  arrange(desc(percentage)) %>% 
  mutate(country_studied_aggreg = as_factor(country_studied_aggreg))

#Print the results
knitr::kable(countries_studied_by_count_aggregated, 
             col.names = c('Country', 
                           'Number of studies', 
                           'Percentage'
                           ),
             caption = 'Number/percentage of studies per country'
             )
```

## Number and percentage of studies per continent
```{r echo=FALSE}
continents_studied_by_count <- countries_studied_by_count %>% 
  mutate(continent_studied = countrycode(country_studied, 
                                          destination = 'continent',
                                          origin = 'iso2c',
                                          nomatch = NULL #if there is no match, keep the original
                                          )
         ) %>% 
  mutate(continent_studied = str_to_lower(continent_studied)
         ) %>% 
  mutate(continent_studied = case_when(str_detect(continent_studied, 'asia') == T ~ 'asia', 
                                         str_detect(continent_studied, 'africa') == T ~ 'africa', 
                                         TRUE ~ continent_studied
                                       )
           ) %>% 
  group_by(continent_studied) %>%
  summarise(num_of_studies = sum(num_of_studies), 
            percentage = sum(percentage),
            .groups = 'drop'
            ) %>% 
  arrange(desc(percentage))

#Print the results
knitr::kable(continents_studied_by_count, 
             col.names = c('Continent', 
                           'Number of studies', 
                           'Percentage'
                           ),
             caption = 'Number/percentage of studies per continent'
             )
```

### Country most studied 
```{r echo=FALSE}
countries_studied_most <- countries_studied_by_count %>% 
    filter(country_studied != 'none') %>%
    filter(num_of_studies == max(num_of_studies))

#Print the result as a table    
knitr::kable(countries_studied_most, 
             col.names = c('Country', 
                           'Number of studies', 
                           'Percentage'
                           ),
             caption = 'Most studied country'
             )
```

### Continent most studied
```{r echo=FALSE}

continent_studied_most <- continents_studied_by_count %>% 
    dplyr::filter(continent_studied != 'none') %>% 
    filter(num_of_studies == max(num_of_studies))

#Print the result as a table      
knitr::kable(continent_studied_most,
             col.names = c('Continent', 
                           'Number of studies',
                           'Percentage'
                           ),
             caption = 'Most studied continent'
             )
```

## Number of studies per continent
```{r echo=FALSE}
continents_studied <- continents_studied_by_count %>% 
  filter(continent_studied != 'none') %>% 
  filter(continent_studied != 'global') %>% 
  filter(continent_studied != 'northern_hemisphere') %>% 
  group_by(continent_studied) %>% 
  summarise(num_of_studies = sum(num_of_studies )) %>% 
  ungroup() %>% 
  mutate(percentage = round(num_of_studies/sum(num_of_studies)*100, 1))

#Print table of results
knitr::kable(continents_studied_by_count %>% arrange(desc(percentage)),
             col.names = c('Continent',
                           'Number of papers',
                           'Percentage'
                           ),
             caption = 'Number/percent of studies by continent'
             )

```

### Highest number of studies per year and disease

```{r echo=FALSE}
knitr::kable(tibble(max_pub_year = max_pub_year$publication_year, 
                    disease_with_max_pubs = disease_studied_most$disease,
                    country_most_studied = countries_studied_most$country_studied
                    )
             )
```

# Primary objectives

## 1.A. Is modelling being used to inform outbreak response policy-making?

### I. How are the results distributed according to collaboration type?

Note that we do not include FMD in all the primary analyses. We only use it for comparisons, where necessary.

```{r echo=FALSE}
# 1B. Create the unique combinations of collaboration types and reword the string NA
collab_type_data <- compact_data_no_fmd %>%
  select(title, publication_year, author_affiliation_type, author_in_country_studied) %>% 
  mutate(publication_year = as.numeric(publication_year), 
         author_in_country_studied = as.character(author_in_country_studied)) %>% 
  arrange(publication_year) %>%
  mutate(
    author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + '),
    author_in_country_studied = if_else(author_in_country_studied == 'NA', 'not_applicable',
                                        author_in_country_studied
                                        )
    )

#' Count by collaboration types and make a bar plot
collab_types_count <- collab_type_data %>%
    count(author_affiliation_type) %>% 
    mutate(author_affiliation_type = as_factor(author_affiliation_type))

knitr::kable(collab_types_count %>% arrange(desc(n)))
```

### II. What has been the trend in collaboration over the years?

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

collap_types_count_barplot <- collab_types_count %>%
    ggplot() + geom_bar(aes(x = reorder(author_affiliation_type, n),
                            y = n
                            ),
                        stat = 'identity',
                        color = 'black'
                        ) +
    scale_y_continuous(breaks = seq(0, 140, 20),
                       labels = seq(0, 140, 20)
                       ) +
    labs(title = 'Number of studies per collaboration type', 
         x = '', 
         y = 'Number of studies') + 
  coord_flip() +
  theme_minimal() +
  theme(legend.position = 'none')

plot(collap_types_count_barplot)

knitr::kable(collab_types_count, 
             col.names = c('Collaboration type', 'Number of publications'),
             caption = 'Number of publications per collaboration type'
             )

```

### III. Proportions of the total publications per year shared by collaboration type (purely academic versus mixed).

```{r echo=FALSE}
#' Count the number of each author affiliation type per year (including FMD)
collap_types_by_year <- compact_data_no_fmd %>% 
  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 
                                         2005, 
                                         publication_year
                                         )
                                  ), 
         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
                                         'Purely academic', 
                                         'Mixed')
                                 )
         ) %>% 
  count(year_aggreg, 
        collab_type, 
        name = 'total_publications'
        )

#The plot
# Modify the x-axis labels to account for the lumping of the years from 2005 and below
x_axis_labels <- as.character(seq(2005, 2020, 2))

x_axis_labels[1] <- '1970-2005'

collab_type_by_year_plot <- ggplot(data = collap_types_by_year) + 
  geom_bar(aes(x = year_aggreg,
               y = total_publications,
               fill = collab_type
               ),
           color = 'black',
           stat = 'identity',
           position = position_fill(reverse = TRUE)  
             ) +
  scale_fill_manual(values = c('tan1', 'turquoise1')) +
  scale_x_continuous(breaks = seq(2005, 2020, 2),
                     labels = x_axis_labels
                     ) +
  labs(title = 'Publications per collaboration type over time',
       x = 'Year',
       y = 'Proportion of total publications in the year',
       fill = 'Collaboration type' 
         ) +
  theme_minimal(base_size = 12)

plot(collab_type_by_year_plot)

```
### IV. Number of studies by collaboration type (purely academic versus mixed).

```{r echo=FALSE}
#' Count the number of each author affiliation type per year (including FMD)
collap_types_by_year <- compact_data_no_fmd %>% 
  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 
                                         2005, 
                                         publication_year
                                         )
                                  ), 
         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
                                         'Purely academic', 
                                         'Mixed')
                                 )
         ) %>% 
  count(year_aggreg, 
        collab_type, 
        name = 'total_publications'
        ) %>% 
  pivot_wider(names_from = collab_type, values_from = total_publications)

knitr::kable(collap_types_by_year %>% clean_names() %>% adorn_totals(... = c(mixed, purely_academic)))

```

```{r echo=FALSE}
#' Count the number of each author affiliation type per year
collap_types_by_year <- compact_data_no_fmd %>% 
  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 
                                         2005, 
                                         publication_year
                                         )
                                  ), 
         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
                                         'Purely academic', 
                                         'Mixed')
                                 )
         ) %>% 
  count(year_aggreg, 
        collab_type, 
        name = 'total_publications'
        )

collap_types_by_year_plot <- ggplot(data = collap_types_by_year, 
                                    aes(x = year_aggreg, 
                                        y = total_publications
                                        ), 
                                    color = 'black') + 
  geom_bar(aes(fill = collab_type), 
           stat = 'identity', 
           position = 'dodge'
           ) +
  labs(x = 'Year', y = 'Total publications')

plot(collap_types_by_year_plot)

```

Even though non-academic collaborations increased over time, the share of total publications per year over time decreased.

### V. Academic collaborations versus other non-academic collaborations (excluding purely academic collaborations).

```{r echo=FALSE}

academic_collabs_versus_others <- compact_data_no_fmd %>% 
  filter(author_affiliation_type != 'academic_institutions') %>% 
  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 2005, publication_year
                                         )
                                  ), 
         collab_type = as_factor(if_else(str_detect(author_affiliation_type, 'academic_institutions'), 
                                         'Academic', 
                                         'Other'
                                         )
                                 )
         ) %>% 
  count(year_aggreg, 
        collab_type, 
        name = 'total_publications'
        )

#plot the result
academic_collabs_trend <- ggplot(data = academic_collabs_versus_others) + 
  geom_bar(aes(x = year_aggreg,
               y = total_publications,
               fill = collab_type
               ),
           color = 'black',
           stat = 'identity',
           position = position_fill(reverse = TRUE)  
             ) +
  scale_fill_manual(values = c('tan1', 'turquoise1')) +
  scale_x_continuous(breaks = seq(2005, 2020, 2),
                     labels = x_axis_labels
                     ) +
  labs(title = 'Academic and other collaborations over time',
       x = 'Year',
       y = 'Proportion of publications',
       fill = 'Collaboration type' 
         ) +
  theme_minimal(base_size = 12)

plot(academic_collabs_trend)

#Number of each collaboration type

```

# B. How often are papers authored by locals?
```{r}
author_location_count_by_disease_wide <- compact_data_no_fmd %>%
  separate_rows(disease, sep = ' ') %>% 
  mutate(author_in_country_studied = as_factor(author_in_country_studied), 
         disease = as_factor(disease)
         ) %>% 
  group_by(disease) %>%
  distinct(title, .keep_all = TRUE) %>% 
  count(author_in_country_studied) %>% 
  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
  replace_na(list(yes = 0, no = 0, not_applicable = 0)) %>% 
  mutate(total = not_applicable + no + yes) %>% 
  arrange(desc(total))

knitr::kable(author_location_count_by_disease_wide)
```

```{r}
author_location_count_by_disease_long <- author_location_count_by_disease_wide %>% 
  select(-c(not_applicable, total)) %>% 
  pivot_longer(cols = c(yes, no), 
               names_to = 'author_in_country_studied',
               values_to = 'n'
               )

author_location_count_by_disease_plot <- ggplot(data = author_location_count_by_disease_long, 
       aes(x = reorder(disease, n), 
           y = n
           )
       ) + geom_bar(aes(fill = author_in_country_studied),
                    stat = 'identity',
                    position = position_fill(reverse = TRUE)
                    ) +
  labs(x = 'Disease', y = 'Proportion of total studies') +
  coord_flip()

plot(author_location_count_by_disease_plot)
```

# 2. Is vaccination always the most impactful single intervention?

## Classification of interventions by inclusion/exclusion of vaccination

### Human diseases
```{r echo=FALSE}
intervention_categories_human_diseases <- compact_data_no_fmd %>% 
  group_by(intervention_type, vax_modelled_with_non_vax) %>% 
  count(is_vax_effective, sort = TRUE) %>% 
  pivot_wider(names_from = vax_modelled_with_non_vax, values_from = n) %>% 
  replace_na(list(no = 0, yes = 0))

knitr::kable(intervention_categories_human_diseases)
```
### FMD

```{r echo=FALSE}
intervention_categories_fmd <- compact_data %>% 
  filter(disease == 'fmd') %>% 
  group_by(intervention_type, vax_modelled_with_non_vax) %>% 
  count(is_vax_effective, sort = TRUE) %>% 
  filter(vax_modelled_with_non_vax == 'yes') %>% 
  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
  adorn_totals(where = 'col')

knitr::kable(intervention_categories_fmd)
```

## Classification of interventions by inclusion of vaccination 
```{r echo=FALSE}
study_categories_by_vax_single <- intervention_categories_human_diseases %>% 
  filter(intervention_type == 'vax_single')

knitr::kable(study_categories_by_vax_single)
```

## Citation table of studies that modelled vaccination as a single intervention
```{r echo=FALSE}
intervention_categories_citation_tbl <- compact_data_with_citation_keys_no_fmd %>%
  filter(intervention_type == 'vax_single') %>% 
  select(title, publication_year, bibtexkey, disease, intervention_modelled, vax_modelled, vax_modelled_with_non_vax, is_vax_effective)

knitr::kable(intervention_categories_citation_tbl %>% arrange(is_vax_effective
, disease))

```

# Is vaccination the most effective when compared to other single interventions?

## Vaccine impact categories (human diseases)
```{r echo=FALSE}
vax_impact_categories_no_fmd <- compact_data_no_fmd %>% 
  filter(vax_modelled_with_non_vax == 'yes') %>% 
  count(is_vax_effective, 
        name = 'num_of_studies', 
        sort = T
        )

#Print the results
knitr::kable(vax_impact_categories_no_fmd %>% adorn_totals, 
             col.names = c('Vaccination is most impactful', 
                           'Number of studies'
                           ),
             caption = 'Studies\' conclusions about impact of vaccination (Human diseases)'
             )
```

## Vaccine impact categories (FMD)
```{r echo=FALSE}
vax_impact_categories_fmd <- compact_data %>%
  filter(disease == 'fmd') %>% 
  filter(vax_modelled_with_non_vax == 'yes') %>% 
  count(is_vax_effective, 
        name = 'num_of_studies', 
        sort = T
        )

#Print the results
knitr::kable(vax_impact_categories_fmd %>% adorn_totals, 
             col.names = c('Vaccination is most impactful', 
                           'Number of studies'
                           ),
             caption = 'Studies\' conclusions about impact of vaccination (FMD)'
             )
```

## Citation table for human diseases
```{r echo=FALSE}
vax_impact_categories_citations_no_fmd <- compact_data_with_citation_keys %>% 
  filter(disease != 'fmd') %>% 
  filter(vax_modelled_with_non_vax == 'yes') %>% 
  select(title, publication_year, disease, objectives, is_vax_effective, bibtexkey) %>% 
  arrange(is_vax_effective)

#Print the results
knitr::kable(vax_impact_categories_citations_no_fmd,
             caption = 'Studies\' conclusions about impact of vaccination (citations for human diseases)'
             )
```

## Citation table for FMD
```{r echo=FALSE}
vax_impact_categories_citations_fmd <- compact_data_with_citation_keys %>% 
  filter(disease == 'fmd') %>% 
  filter(vax_modelled_with_non_vax == 'yes') %>% 
  select(title, publication_year, disease, objectives, is_vax_effective, bibtexkey) %>% 
  arrange(is_vax_effective)

#Print the results
knitr::kable(vax_impact_categories_citations_fmd,
             caption = 'Studies\' conclusions about impact of vaccination (citations for human diseases)'
             )

```

```{r echo=FALSE, eval=FALSE}
vax_impact_plot <- ggplot(data = vax_impact_categories) + 
  geom_bar(
    aes(x = is_vax_effective, 
        y = n,
        fill = is_vax_effective
        ),
    stat = 'identity',
    width = 0.25
    ) +
  scale_y_continuous(breaks = seq(0, 
                                  max(vax_impact_categories$n),
                                  2
                                  ),
                     labels = seq(0, 
                                max(vax_impact_categories$n),
                                2
                                )
                     ) +
  scale_x_discrete(breaks = c('no', 
                              'yes', 
                              'the_outcomes_were_inconclusive'
                              ), 
                   labels = c('no' = 'No', 
                              'yes' = 'Yes', 
                              'the_outcomes_were_inconclusive' = 'Inconclusive'
                              )
                   ) +
  scale_fill_discrete(name = 'Vaccine impact',
                      labels = c('No', 
                                 'Inconclusive',
                                 'Yes'
                      )
                      ) +
  labs(x = 'Vaccination is most impactful single intervention',
       y = 'Number of studies'
       ) +
  theme_minimal(base_size = 12)

plot(vax_impact_plot)

```

# Number of studies per disease

## By collaboration type

```{r echo=FALSE}
#count the number of unique diseases studied
disease_studied_by_collab_type <- compact_data_no_fmd %>% 
  separate_rows(disease,  sep = ' ') %>% 
  mutate(disease = as_factor(disease), 
         author_affiliation_type = as_factor(str_replace(author_affiliation_type, ' ', '+'))
         ) %>% 
    mutate(collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
                                         'purely_academic', 
                                         'mixed')
                                 )
         ) %>% 
  group_by(disease) %>% 
  distinct(title, .keep_all = TRUE) %>% 
  count(disease, collab_type, sort = TRUE) %>%
  pivot_wider(names_from = collab_type, values_from = n) %>% 
  replace_na(list(purely_academic = 0, mixed = 0)) %>% 
  mutate(total = purely_academic + mixed) %>% 
  arrange(desc(total))

knitr::kable(disease_studied_by_collab_type)
```

## By outbreak type

```{r echo=FALSE}
#count the number of unique diseases studied
disease_studied_by_outbreak_type <- compact_data_no_fmd %>% 
  separate_rows(disease,  sep = ' ') %>% 
  mutate(disease = as_factor(disease), 
         outbreak_type = as_factor(str_replace(outbreak_type, ' ', '+'))
         ) %>% 
  group_by(disease) %>% 
  distinct(title, .keep_all = TRUE) %>% 
  count(disease, outbreak_type, sort = TRUE) %>%
  pivot_wider(names_from = outbreak_type, values_from = n) %>% 
  replace_na(list(hypothetical_outbreak = 0, real_outbreak = 0)) %>% 
  mutate(total = hypothetical_outbreak + real_outbreak) %>% 
  arrange(desc(total))

knitr::kable(disease_studied_by_outbreak_type)
```

## By objective type

```{r echo=FALSE}
#count the number of unique diseases studied
disease_studied_by_objective_type <- compact_data_no_fmd %>% 
  separate_rows(disease,  sep = ' ') %>% 
  mutate(disease = as_factor(disease), 
         objectives = as_factor(objectives)
         ) %>% 
  group_by(disease) %>% 
  distinct(title, .keep_all = TRUE) %>% 
  count(disease, objectives) %>%
  pivot_wider(names_from = objectives, values_from = n) %>% 
  replace_na(list(future = 0, past = 0, both = 0)) %>% 
  mutate(total = future + past + both) %>% 
  arrange(desc(total))

knitr::kable(disease_studied_by_objective_type)
```

## FMD by collaboration type
```{r echo=FALSE}
fmd_studies_by_collab_type <- compact_data %>% 
  filter(disease == 'fmd') %>% 
  mutate(disease = as_factor(disease), 
         author_affiliation_type = as_factor(str_replace(author_affiliation_type, ' ', '+'))
         ) %>% 
  mutate(collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
                                         'purely_academic', 
                                         'mixed')
                                 )
         ) %>% 
  count(collab_type, sort = TRUE)

knitr::kable(fmd_studies_by_collab_type)
```
## FMD by objective type
```{r echo=FALSE}
fmd_studies_by_objective_and_outbreak_type <- compact_data %>% 
  filter(disease == 'fmd') %>% 
  count(objectives, outbreak_type) %>% 
  pivot_wider(names_from = outbreak_type, values_from = n)

knitr::kable(fmd_studies_by_objective_and_outbreak_type)
```

# Number of studies per disease and intervention.

```{r echo=FALSE}
#count the number of unique interventions modelled
interventions_unique_entries <- long_data_no_fmd %>% 
  group_by(title) %>% 
  distinct(intervention_modelled, .keep_all = TRUE) %>% 
  ungroup()

#interventions are disease specific
interventions_per_disease <- interventions_unique_entries %>% 
  mutate(intervention_modelled = str_trim(intervention_modelled)) %>% 
  filter(intervention_modelled != 'e.g.') %>% #remove false rows
  filter(intervention_modelled != 'various') %>% #remove false rows
  group_by(disease) %>% 
  count(intervention_modelled, name = 'num_of_studies') %>% 
  arrange(disease, desc(num_of_studies)) %>% 
  ungroup()

knitr::kable(interventions_per_disease)

```

# Number of studies per outcome

```{r echo=FALSE}
#count the number of unique outcomes measured
outcomes_unique_entries <- long_data_no_fmd %>% 
  group_by(title) %>% 
  distinct(outcome_measured, .keep_all = TRUE) %>% 
  ungroup()

#Count the number of studies 
outcomes_count <- outcomes_unique_entries %>% 
  group_by(outcome_measured) %>% 
  count(outcome_measured, name = 'num_of_studies', sort = T) %>% 
  ungroup() %>% 
  filter(outcome_measured != 's')

knitr::kable(outcomes_count)

#Plot the result
outcome_count_plot <- ggplot(data = outcomes_count) + 
  geom_point(aes(x = reorder(outcome_measured, 
                             num_of_studies), 
               y = num_of_studies
               ), 
           stat = 'identity',
           color = 'darkslategray4'
           ) +
  coord_flip() +
  theme_minimal()

plot(outcome_count_plot)

```

# Number of studies per model structure type

```{r echo=FALSE}
#Keep only the unique entries 
model_structure_unique_entries <- long_data_no_fmd %>% 
  group_by(title) %>% 
  distinct(model_structure) %>% 
  ungroup()

#Count the number of studies
model_structure_unique_count <- model_structure_unique_entries %>%
    group_by(model_structure) %>% 
    count(model_structure, name = 'num_of_studies')

#Print the table
knitr::kable(model_structure_unique_count)
```

# Number of studies by the model structure, parametrization, and validation types

```{r echo=FALSE}
#Cross tally the model structure with parametrization and validation categories
#FIXME: Check that studies are either not being under counted or double-counted. What do I want to count here? Is it the unique studies per method or combined method because most studies used a combination of parametrization methods especially
parametrization_and_validation_by_model_structure <- compact_data_no_fmd %>%
  mutate(parametrization = str_replace(parametrization, ' ', ' + '),
         validation = str_replace(validation, ' ', ' + ')
         ) %>% 
  count(model_structure, parametrization, validation) %>% 
  pivot_wider(names_from = model_structure, values_from = n)

#Print the table of results
knitr::kable(parametrization_and_validation_by_model_structure,
             caption = 'Parametrization and validation types per model structure')

```

# Model parametrization & validation

```{r echo=FALSE}
#Keep only the unique entries
parametrization_and_validation_count <- compact_data_no_fmd %>% 
  mutate(parametrization = str_replace(parametrization, ' ', ' + '), 
         validation = str_replace(validation, ' ', ' + ')
         ) %>% 
  count(parametrization, 
        validation, 
        name = 'num_of_studies'
        ) %>% 
  group_by(parametrization) %>% 
  arrange(desc(num_of_studies), .by_group = T)

#Print the table
knitr::kable(parametrization_and_validation_count)

```

# How is sensitivity analysis distributed by model structure?

```{r echo=FALSE}
#Keep only the unique entries
sensitivity_analysis_unique_entries <- long_data_no_fmd %>% 
  group_by(title) %>% 
  distinct(sensitivity_analysis, .keep_all = TRUE) %>% 
  ungroup()

#Count the number of studies
sensitivity_analysis_count <- sensitivity_analysis_unique_entries %>% 
  count(model_structure, sensitivity_analysis, name = 'num_of_studies')

#Print the table
knitr::kable(sensitivity_analysis_count)

```

# Data use and availability

```{r echo=FALSE}
#Keep only the unique entries
code_and_data_availability_count <- compact_data_no_fmd %>% 
  count(data_used, data_available) %>% 
  pivot_wider(names_from = data_available, values_from = n) %>% 
  replace_na(list(not_applicable = 0, 
                  yes = 0, 
                  no = 0
                  )
             )

#Print the results
knitr::kable(code_and_data_availability_count, caption = 'Data use and availability')

```
# Code availability

```{r echo=FALSE}
#Keep only the unique entries
code_availability_count <- compact_data_no_fmd %>% 
  count(simulation_code_available)

#Print the results
knitr::kable(code_availability_count, caption = 'Code availability')

```

# Secondary summaries
## Studies before 2006 (low frequency period) 
```{r echo=FALSE}
#Number of studies before 2005 (low frequency period)
n_studies_before_2006 <- compact_data_no_fmd %>% 
  filter(publication_year < 2006) %>% 
  summarise(n = n())

print(paste('Number of studies before 2006:', n_studies_before_2006))
```
## Number of studies between 2006-2019 (high frequency period)
```{r echo=FALSE}
n_studies_btwn_2006_2019 <- compact_data_no_fmd %>% 
  filter(publication_year >= 2006, publication_year <= 2019) %>% 
  summarise(n = n())

print(paste('Number of studies between 2006 and 2019:', n_studies_btwn_2006_2019))
```

# Exploration of the peak periods (2009-2011, 2015-2016, 2019)

## Citations of studies during 2009-2011
```{r echo=FALSE}
#Citation table of studies during 2009-2011 (Peak period)
studies_in_2009_2011_df <- compact_data_with_citation_keys_no_fmd %>%
  separate_rows(disease, sep = ' ') %>% 
  filter(publication_year >= 2009, publication_year <= 2011) %>%
  arrange(disease) %>%
  select(title, publication_year, disease, objectives, bibtexkey) %>% 
  mutate(disease = str_replace(disease, ' ', ' and '))

knitr::kable(studies_in_2009_2011_df, caption = 'Studies published during 2009-2011 (Peak period)')
```
### Number of studies during 2009-2011 per disease and objective type (Peak period)
```{r echo=FALSE}
n_studies_2009_2011_df <- studies_in_2009_2011_df %>%
  count(disease, objectives) %>% 
  arrange(disease, n) %>% 
  pivot_wider(names_from = objectives, values_from = n) %>% 
  replace_na(list(both = 0, future = 0, past = 0))

knitr::kable(n_studies_2009_2011_df, caption = 'Studies published during 2009-2011 (Peak period)')
```

## Citation table of studies during 2015-2016 per disease and objective type (Peak period)
```{r echo=FALSE}
studies_between_2015_2016_df <- compact_data_with_citation_keys_no_fmd %>%
  separate_rows(disease, sep = ' ') %>% 
  filter(publication_year >= 2015, publication_year <= 2016) %>%
  arrange(disease, publication_year) %>%
  select(title, publication_year, disease, objectives, bibtexkey) %>% 
  mutate(disease = str_replace(disease, ' ', ' and '))

knitr::kable(studies_between_2015_2016_df, caption = 'Studies published in 2015-2016 (Peak period)')
```

### Number of studies from 2015-2016 per disease and objective type (Peak period)
```{r echo=FALSE}
n_studies_between_2015_2016_df <- studies_between_2015_2016_df %>% 
  count(disease, objectives) %>% 
  arrange(desc(n))  %>% 
  pivot_wider(names_from = objectives, values_from = n) %>% 
  replace_na(list(both = 0, future = 0, past = 0))

knitr::kable(n_studies_between_2015_2016_df, caption = 'Papers published in 2015-2016 (Peak period)')
```

## Citation table of studies in 2019 (Peak period)
```{r echo=FALSE}
studies_in_2019_df <- compact_data_with_citation_keys_no_fmd %>%
  filter(publication_year == 2019) %>%
  arrange(disease) %>%
  select(title, publication_year, disease, objectives, bibtexkey) %>% 
  mutate(disease = str_replace(disease, ' ', ' and '))

knitr::kable(studies_in_2019_df, caption = 'Studies published in 2019 (Peak year)')
```
### Number of studies in 2019 per disease and objective type (Peak period)
```{r echo=FALSE}
n_studies_in_2019_df <- studies_in_2019_df %>% 
  count(disease, objectives) %>% 
  arrange(n)

knitr::kable(n_studies_in_2019_df, caption = 'Number of studies published in 2019 per disease and objective type (Peak year)')
```

### Total number of studies in 2019 (Peak period)
```{r echo=FALSE}
n_studies_in_2019 <- n_studies_in_2019_df %>%  
  summarise(n = n())

print(paste('Number of studies in 2019 (Peak year):', 
            n_studies_in_2019
            )
      )
```

## Number of diseases in the peak periods
```{r echo=FALSE}
peak_period_df <- bind_rows(studies_in_2009_2011_df, 
                            studies_between_2015_2016_df, 
                            studies_in_2019_df
                            ) %>% 
  arrange(disease, publication_year)

knitr::kable(peak_period_df , 
             caption = 'Studies published in peak period'
             )
```

```{r echo=FALSE}
n_studies_by_disease_and_objectives_peak_periods <- peak_period_df %>% 
  count(disease, objectives)

knitr::kable(n_studies_by_disease_and_objectives_peak_periods, 
             caption = 'Number of studies per disease and objective in peak periods'
             )
```

```{r echo=FALSE}
total_studies_by_disease_peak_period_df <- peak_period_df %>% 
  count(disease) %>% 
  arrange(n)

knitr::kable(total_studies_by_disease_peak_period_df, 
             caption = 'Number of studies per disease in peak periods'
             )
```

## Influenza during 2009 - 2011 peaks
```{r echo=FALSE}
n_Influenza_studies_by_objectives_2009_2011 <- peak_period_df %>% 
  filter(publication_year >= 2009, publication_year <= 2011) %>%
  filter(disease == 'influenza') %>% 
  count(objectives)

knitr::kable(n_Influenza_studies_by_objectives_2009_2011, 
             caption = 'Number of Influenza studies per objective type (2009 & 2011)'
             )
```
## Ebola in 2015-2016
```{r echo=FALSE}
n_ebola_studies_by_objectives_2015_2016 <- studies_between_2015_2016_df %>% 
  filter(disease == 'ebola') %>% 
  count(objectives)

knitr::kable(n_ebola_studies_by_objectives_2015_2016, 
             caption = 'Number of Ebola studies per objective type (2015-2016)'
             )
```
### Studies that used both retrospective and prospective assessments in peak periods
```{r echo=FALSE}
knitr::kable(peak_period_df %>% filter(objectives == 'both'), 
             caption = 'Studies with retrospective and prospective assessments'
             )

```

### 2023-03-02 analyses/scripts/full_data_extraction_citation_table.Rmd
moved analysis scripts and data into a folder

--- 2023-03-02 scripts/orv_sys_rev_data_analysis.Rmd
@@
 ---
-title: "Analysis of the included studies"
 output:
-  word_document:
-    toc: yes
   pdf_document:
-    toc: yes
     keep_tex: yes
-    fig_crop: no
 ---
@@
 library('readr')
-library('ggthemes')
-library('mdthemes')
+library('xlsx')
 library('scales')
-library('janitor')
-library('forcats')
 library('stringr')
-library('countrycode')
-library('bib2df')
 library('conflicted')
 library('Hmisc')
-library('ggwordcloud')
+library('kableExtra')
 
@@
 knitr::opts_chunk$set(dev = 'jpeg')
-knitr::opts_chunk$set(out.height = "\\textheight",  out.width = "\\textwidth")
+knitr::opts_chunk$set(fig.width = 8, fig.height = 6)
 knitr::opts_chunk$set(message = FALSE)
-knitr::opts_chunk$set(warning = FALSE)
 
@@
            )
-
-# Remove the FMD papers (NB: We only use the FMD papers for comparison)
-long_data_no_fmd <- long_data %>% filter(disease != 'fmd')
-
-compact_data_with_citation_keys_no_fmd <- compact_data_with_citation_keys %>% 
-  filter(disease != 'fmd')
-
-#Filter the FMD data
-fmd_data <- compact_data_with_citation_keys %>% 
-  filter(disease == 'fmd') 
 ```
 
-# Human vaccine-preventable diseases
-
-```{r eval=FALSE}
-library(PRISMAstatement)
-
-prisma_chart <- prisma(found = 12986,
-       found_other = 0,
-       no_dupes = 5012, 
-       extra_dupes_box = TRUE,
-       screened = 5012, 
-       screen_exclusions = 4211, 
-       full_text = 801,
-       full_text_exclusions = 548, 
-       qualitative = 253, 
-       quantitative = 0,
-       width = 800, height = 800,
-       font_size = 12)
-
-prisma_chart
-```
-
-<!-- ## Publications per year -->
-
-<!-- ```{r} -->
-
-<!-- publications_per_year <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(publication_year)  -->
-
-<!-- publications_per_year_plot <- ggplot(data = publications_per_year) +  -->
-<!--   geom_bar(aes(x = publication_year,  -->
-<!--                y = n -->
-<!--                ),  -->
-<!--            stat = 'identity',  -->
-<!--            color = 'black', -->
-<!--            fill = 'tomato3' -->
-<!--            ) + -->
-<!--   scale_y_continuous(breaks = seq(0, 30, 2), -->
-<!--                      labels = seq(0, 30, 2) -->
-<!--                      ) + -->
-<!--   labs(x = '**Year of publication**', y = '**Number of papers**') + -->
-<!--   md_theme_minimal(base_size = 12) -->
-
-<!-- plot(publications_per_year_plot) -->
-
-<!-- ggsave(filename = 'publications_per_year.tiff',  -->
-<!--        plot = publications_per_year_plot,  -->
-<!--        device = 'tiff',  -->
-<!--        path = save_fig_here -->
-<!--        ) -->
-
-<!-- ggsave(filename = 'publications_per_year.tiff',  -->
-<!--        plot = publications_per_year_plot,  -->
-<!--        device = 'tiff',  -->
-<!--        path = save_thesis_fig_here -->
-<!--        ) -->
-
-<!-- ``` -->
-
-<!-- ## Collaboration patterns in time -->
-
-<!-- ### Number of studies per combinations of author affiliation types -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- #' Count by collaboration types and make a bar plot -->
-<!-- collab_types_count <- compact_data_with_citation_keys_no_fmd %>% -->
-<!--     count(author_affiliation_type, sort = TRUE) %>%  -->
-<!--     arrange(desc(n)) %>%  -->
-<!--     adorn_totals() %>%  -->
-<!--     adorn_percentages(denominator = 'col') %>%  -->
-<!--     adorn_pct_formatting() %>%  -->
-<!--     adorn_ns() -->
-
-<!-- knitr::kable(collab_types_count,  -->
-<!--              format = "latex", booktabs = TRUE,  -->
-<!--              caption = 'Number of publications per author affiliation type combination') %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))  -->
-<!-- ``` -->
-
-<!-- ### Proportions of the total publications per year by collaboration type -->
-
-<!-- ```{r echo=FALSE, fig.width=8} -->
-<!-- #' Count the number of each author affiliation type per year (including FMD) -->
-<!-- collap_types_by_year <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(year_aggreg,  -->
-<!--         collab_type,  -->
-<!--         name = 'total_publications' -->
-<!--         ) -->
-
-<!-- #The plot -->
-<!-- # Modify the x-axis labels to account for the lumping of the years from 2005 and below -->
-<!-- x_axis_labels <- as.character(seq(2005, 2020, 2)) -->
-
-<!-- x_axis_labels[1] <- '1970-2005' -->
-
-<!-- collab_proportions_plot <- ggplot(data = collap_types_by_year) +  -->
-<!--   geom_bar(aes(x = year_aggreg, -->
-<!--                y = total_publications, -->
-<!--                fill = collab_type -->
-<!--                ), -->
-<!--            color = 'black', -->
-<!--            stat = 'identity', -->
-<!--            position = position_fill(reverse = TRUE)#, -->
-<!--            #show.legend = FALSE -->
-<!--              ) + -->
-<!--   scale_fill_manual(values = c('tan3', 'turquoise2')) + -->
-<!--   scale_x_continuous(breaks = seq(2005, 2020, 2), -->
-<!--                      labels = x_axis_labels, -->
-<!--                      expand = c(0, 0) -->
-<!--                      ) + -->
-<!--   #coord_flip() + -->
-<!--   labs(#title = 'Publications per collaboration type over time', -->
-<!--        x = '**Year**', -->
-<!--        y = '**Proportion of total publications**', -->
-<!--        fill = '**Collaboration type**'  -->
-<!--          ) + -->
-<!--   theme(legend.position = 'none') + -->
-<!--  # md_theme_minimal(base_size = 16) #For Powerpoint -->
-<!--   md_theme_minimal(base_size = 12) -->
-
-<!-- plot(collab_proportions_plot) -->
-
-<!-- ggsave(filename = 'collab_proportions.tiff',  -->
-<!--        plot = collab_proportions_plot,  -->
-<!--        device = 'tiff',  -->
-<!--        path = save_fig_here -->
-<!--        ) -->
-
-<!-- ggsave(filename = 'collab_proportions.tiff',  -->
-<!--        plot = collab_proportions_plot,  -->
-<!--        device = 'tiff',  -->
-<!--        path = save_thesis_fig_here -->
-<!--        ) -->
-
-<!-- ``` -->
-
-<!-- ### Absolute number of publications per year by collaboration type -->
-
-<!-- ```{r} -->
-<!-- #' Count the number of each author affiliation type per year -->
-<!-- collabs_per_year <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(year_aggreg,  -->
-<!--         collab_type,  -->
-<!--         name = 'total_publications' -->
-<!--         )  -->
-
-<!-- collabs_per_year_plot <- ggplot(data = collabs_per_year,  -->
-<!--                                     aes(x = year_aggreg,  -->
-<!--                                         y = total_publications -->
-<!--                                         ),  -->
-<!--                                     color = 'black') +  -->
-<!--   geom_bar(aes(fill = collab_type),  -->
-<!--            stat = 'identity',  -->
-<!--            position = 'dodge' -->
-<!--            ) +  -->
-<!--   scale_fill_manual(values = c('tan3', 'turquoise2')) +  -->
-<!--   scale_x_continuous(breaks = seq(2005, 2020, 2), -->
-<!--                      labels = x_axis_labels, -->
-<!--                      expand = c(0, 0) -->
-<!--                      ) + -->
-<!--   labs(x = '**Year**',  -->
-<!--        y = '**Total publications**',  -->
-<!--        fill = 'Collaboration type' -->
-<!--        ) + -->
-<!--   md_theme_minimal(base_size = 12) + -->
-<!--   #md_theme_minimal(base_size = 16) + -->
-<!--   theme(legend.position = 'bottom')  -->
-
-<!-- plot(collabs_per_year_plot) -->
-
-<!-- ggsave(filename = 'total_collabs_per_year_plot.tiff', -->
-<!--        plot = collabs_per_year_plot,  -->
-<!--        device = 'tiff', -->
-<!--        path = save_fig_here -->
-<!--        ) -->
-
-<!-- ggsave(filename = 'total_collabs_per_year_plot.tiff', -->
-<!--        plot = collabs_per_year_plot,  -->
-<!--        device = 'tiff', -->
-<!--        path = save_thesis_fig_here -->
-<!--        ) -->
-
-<!-- ``` -->
-
-<!-- Even though non-academic collaborations increased over time, the share of total publications per year over time decreased. -->
-
-<!-- ## Collaboration patterns in geographic space -->
-
-## Collaboration types (aggregated)
-```{r}
-#' Count by collaboration types and make a bar plot
-studies_per_collab_type <- compact_data_with_citation_keys_no_fmd %>%
-    count(collab_type, sort = TRUE) %>% 
-    arrange(desc(n)) %>% 
-    adorn_totals() %>% 
-    adorn_percentages(denominator = 'col') %>% 
-    adorn_pct_formatting() %>% 
-    adorn_ns()
-
-knitr::kable(studies_per_collab_type, caption = 'Number of studies per collaboration type (Human VPDs)',
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-## Locations studied
-
-### Real versus hypothetical
-
-```{r}
-location_types_tally <- compact_data_with_citation_keys_no_fmd %>% 
-    separate_rows(country_studied, sep = ' ') %>%
-    distinct(title, country_studied, .keep_all = TRUE) %>%
-    mutate(location_type = ifelse(country_studied == 'none', 'none', 'real')) %>% 
-    count(location_type) %>% 
-  arrange(desc(n)) %>% 
-   adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns()
-
-knitr::kable(location_types_tally, 
-             caption = 'Number of studies per location type', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
-```
-
-### Larger than one country
-
-```{r}
-larger_geographies_tally <- compact_data_with_citation_keys_no_fmd %>% 
-    separate_rows(country_studied, sep = ' ') %>%
-    distinct(title, country_studied, .keep_all = TRUE) %>%
-    filter(country_studied %in% c('west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
-    count(country_studied) %>% 
-  arrange(desc(n)) %>% 
-   adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns()
-
-knitr::kable(larger_geographies_tally, caption = 'Number of studies per location larger than one country', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
-```
-
-### Countries studied
-
-```{r}
-countries_studied_by_count <- compact_data_with_citation_keys_no_fmd %>% 
-    separate_rows(country_studied, sep = ' ') %>%
-    distinct(title, country_studied, .keep_all = TRUE) %>% 
-    count(collab_type, country_studied, name = 'num_of_studies', sort = T)
-
-#'Modify the data frame to lump together all countries with less than some number of studies as 'other' and recalculate the percentage studied
-countries_studied_by_count_aggregated <- countries_studied_by_count %>% 
-  group_by(country_studied) %>%
-  summarise(num_of_studies = sum(num_of_studies),
-            .groups = 'drop'
-            ) %>% 
-  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
-  arrange(desc(num_of_studies)) %>% 
-  adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns() %>% 
-  ungroup()
-
-#Print the results
-knitr::kable(countries_studied_by_count_aggregated, 
-             caption = 'Number of studies per country', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'), font_size = 7)
-```
-
-### Continents studied
-
-```{r}
-continents_studied_by_count <- countries_studied_by_count %>% 
-  filter(country_studied %nin% c('none', 'northern_hemisphere', 'global')) %>% 
-  mutate(continent_studied = countrycode(country_studied, 
-                                          destination = 'continent',
-                                          origin = 'iso2c',
-                                          nomatch = NULL #if there is no match, keep the original
+```{r results='asis'}
+final_citation_table <- compact_data_with_citation_keys %>% 
+    relocate(c('doi', 'year', 'bibtexkey'), .after = title) %>% 
+    select(-c(year_aggreg, x0_reviewer, category, 
+              number, pages, journal, publisher, 
+              volume, language, month, publication_type, 
+              modelling_timing, intervention_type, collab_type,
+              author, paper_doi, year, 
+              doi, bibtexkey
               )
            ) %>% 
-  mutate(continent_studied = str_to_lower(continent_studied)
-         ) %>% 
-  mutate(continent_studied = case_when(str_detect(continent_studied, 'asia') == T ~ 'asia', 
-                                         str_detect(continent_studied, 'africa') == T ~ 'africa', 
-                                         TRUE ~ continent_studied
-                                       )
-           ) %>% 
-  group_by(continent_studied) %>%
-  summarise(num_of_studies = sum(num_of_studies), 
-            .groups = 'drop'
-            ) %>% 
-  arrange(desc(num_of_studies)) %>% 
-  adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns()
-
-#Print the results
-knitr::kable(continents_studied_by_count, 
-             caption = 'Number of studies per continent', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-## Geographic connection of authors to the studied locations
-
-```{r}
-author_connectedness_top_5_countries <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(author_in_country_studied != 'not_applicable') %>% 
-  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
-separate_rows(country_studied,  sep = ' ') %>% 
-  group_by(collab_type) %>% 
-  count(country_studied, author_in_country_studied, sort = TRUE) %>% 
-  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
-  replace_na(list(yes = 0, no = 0)) %>% 
-  arrange(collab_type, desc(yes)) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('yes', 'no')) %>% 
-  adorn_pct_formatting(... = c('yes', 'no')) %>% 
-  adorn_ns(... = c('yes', 'no')) %>% 
-  ungroup()
-
-knitr::kable(author_connectedness_top_5_countries, caption = 'Studies with at least one author affiliation in the location studied', 
-             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position', 'repeat_header'), font_size = 8)
-```
-
-### Author affiliation in the studied location (overall)
-
-```{r}
-author_connectedness_to_location_aggreg <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(author_in_country_studied != 'not_applicable') %>% 
-  filter(country_studied %nin% c('other', 'none', 'northern_hemisphere', 'west_africa', 'global')) %>% 
-  count(collab_type, author_in_country_studied, sort = TRUE) %>% 
-  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
-  replace_na(list(yes = 0, no = 0)) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('yes', 'no')) %>% 
-  adorn_pct_formatting(... = c('yes', 'no')) %>% 
-  adorn_ns(... = c('yes', 'no'))
-
-knitr::kable(author_connectedness_to_location_aggreg, caption = 'At least one author with an affiliation in the studied location', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-<!-- ## Diseases studied per collab type -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- #count the number of unique diseases studied -->
-<!-- disease_studied_by_collab_type <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   separate_rows(disease,  sep = ' ') %>%  -->
-<!--   distinct(title, disease, .keep_all = TRUE) %>%  -->
-<!--   count(collab_type, disease, sort = TRUE) %>% -->
-<!--   pivot_wider(names_from = collab_type, values_from = n) %>%  -->
-<!--   replace_na(list(purely_academic = 0, mixed = 0)) %>%  -->
-<!--   adorn_totals(where = c('row', 'col')) %>%  -->
-<!--   adorn_percentages(... = c('purely_academic', 'mixed')) %>%  -->
-<!--   adorn_pct_formatting(... = c('purely_academic', 'mixed')) %>%  -->
-<!--   adorn_ns(... = c('purely_academic', 'mixed')) %>%  -->
-<!--   mutate(disease = str_to_sentence(str_replace(disease, '_', ' '))) %>%  -->
-<!--   arrange(desc(Total)) -->
-
-<!-- knitr::kable(disease_studied_by_collab_type, caption = 'Number of studies per disease and collaboration type', format = "latex", booktabs = TRUE) %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position')) -->
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- #tally the diseases by collaboration type -->
-<!-- disease_by_collab_type_long <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   separate_rows(disease,  sep = ' ') %>%  -->
-<!--   count(collab_type, disease, sort = TRUE)  -->
-
-<!-- disease_by_collab_type_plot <- ggplot(disease_by_collab_type_long) +  -->
-<!--   geom_bar(aes(x = reorder(disease, n),  -->
-<!--                y = n,  -->
-<!--                fill = collab_type -->
-<!--                ),  -->
-<!--            color = 'black', -->
-<!--            stat = 'identity', -->
-<!--            position = position_fill(reverse = TRUE) -->
-<!--            ) +  -->
-<!--   labs(x = '**Disease**', y = '**Number of studies**') +  -->
-<!--   coord_flip() + -->
-<!--   md_theme_minimal(base_size = 12) -->
-
-<!-- print(disease_by_collab_type_plot) -->
-<!-- ``` -->
-
-## Interventions
-
-### Types of interventions
-
-```{r}
-intervention_categories <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, intervention_type, sort = TRUE) %>% 
-  pivot_wider(names_from = intervention_type, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
-  adorn_pct_formatting(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
-  adorn_ns(... = c('no_vax', 'vax_combination_with_others', 'vax_single'))
-
-knitr::kable(intervention_categories, caption = 'Number of studies per intervention categories', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-### Impact of vaccination
-
-```{r}
-vax_impact_conclusions <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(intervention_type == 'vax_single') %>% 
-  count(collab_type, is_vax_effective, sort = T) %>% 
-  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
-    replace_na(list(yes = 0, n0 = 0, the_outcomes_were_inconclusive = 0)) %>% 
-  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
-  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
-  adorn_ns(... = c('yes', 'no', 'inconclusive'))
-
-#Print the results
-knitr::kable(vax_impact_conclusions, 
-             caption = 'Conclusions about impact of vaccination', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position')
-                                  )
-```
-
-```{r eval=FALSE}
-no_vax_modelled <- compact_data_with_citation_keys_no_fmd %>% 
-    separate_rows(disease,  sep = ' ') %>% 
-    filter(vax_modelled == 'no') %>% 
-    count(disease, sort = TRUE, name = 'num_of_studies') %>% 
-     adorn_totals(where = 'row') %>% 
-    adorn_percentages(denominator = 'col') %>% 
-    adorn_pct_formatting() %>% 
-    adorn_ns()
-
-knitr::kable(no_vax_modelled, caption = 'Number of studies per disease for which vaccination was not modelled', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-```{r eval=FALSE}
-vax_impact_by_disease <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(intervention_type == 'vax_single') %>% 
-  count(disease, is_vax_effective, sort = T) %>% 
-  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
-  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
-    replace_na(list(yes = 0, no = 0, inconclusive = 0)) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
-  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
-  adorn_ns(... = c('yes', 'no', 'inconclusive'))
-
-#Print the results
-knitr::kable(vax_impact_by_disease, 
-             caption = 'Conclusions about impact of vaccination per disease', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-```{r eval=FALSE}
-no_vax_impact_by_disease_citation_table <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(intervention_type == 'vax_single', is_vax_effective %in% c('no', 'the_outcomes_were_inconclusive')) %>% 
-  select(title, disease, bibtexkey, publication_year, intervention_modelled, is_vax_effective)
-
-#Print the results
-# knitr::kable(no_vax_impact_by_disease_citation_table, 
-#              caption = 'Studies that did not find vaccination as most impactful'
-#              )
-
-write.xlsx(no_vax_impact_by_disease_citation_table, file = '../citation_tables/no_vax_impact_by_disease_citation_table.xlsx')
-```
-
-```{r eval=FALSE}
-vax_as_single_intervention_studies <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(intervention_type == 'vax_single') %>% 
-  select(title, disease, bibtexkey, publication_year, intervention_modelled)
-
-#Print the results
-# knitr::kable(no_vax_impact_by_disease_citation_table, 
-#              caption = 'Studies that did not find vaccination as most impactful'
-#              )
-
-write.xlsx(vax_as_single_intervention_studies, file = '../citation_tables/vax_as_single_intervention_studies.xlsx')
-```
-
-## Modelling objectives 
-<!-- We grouped studies into whether they assessed the impact of a future intervention strategy (prospective), a past intervention, or both (dual).  -->
-
-<!-- In general, there were more (73.2%; 167/228) studies about prospective intervention impact assessments than retrospective assessments (24.6%; 56/228), and the dual (2.2%; 5/228).
-A similar pattern was observed across the two collaboration types except that purely academic collaborations were more likely to perform the dual assessments.
--->
-
-<!-- In terms of the outbreak types, there was an approximately equal number of papers about real and hypothetical outbreaks overall, and there was no clear difference between the two collaborations.
--->
-
-```{r echo=FALSE}
-#count the number of studies per objective type
-modelling_objectives_count <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, objectives, name = 'num_of_studies') %>% 
-  pivot_wider(names_from = objectives, values_from = num_of_studies) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('both', 'future', 'past')) %>% 
-  adorn_pct_formatting(... = c('both', 'future', 'past')) %>% 
-  adorn_ns(... = c('both', 'future', 'past'))
-
-#Print a table of the results
-knitr::kable(modelling_objectives_count,
-             caption = 'Study objectives by collaboration type', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-## Outbreak types
-
-```{r echo=FALSE}
-#Outbreak types per collab type
-outbreak_types_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, outbreak_type, name = 'num_of_studies') %>% 
-  pivot_wider(names_from = outbreak_type, values_from = num_of_studies) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('hypothetical_outbreak', 'real_outbreak')) %>% 
-  adorn_pct_formatting(... = c('hypothetical_outbreak', 'real_outbreak')) %>% 
-  adorn_ns(... = c('hypothetical_outbreak', 'real_outbreak'))
-
-#Print a table of the results
-knitr::kable(outbreak_types_by_collab_type,
-             caption = 'outbreak types by collaboration type', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-```{r eval=FALSE}
-objectives_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
-  count(objectives, collab_type, name = 'num_of_studies', sort = TRUE) %>% 
-  pivot_wider(names_from = objectives, 
-              values_from = num_of_studies
-              ) %>% 
-  replace_na(list(future = 0, past = 0, both = 0)) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('future', 'past', 'both')) %>% 
-  adorn_pct_formatting(... = c('future', 'past', 'both')) %>% 
-  adorn_ns(... = c('future', 'past', 'both'))
-
-knitr::kable(objectives_by_collab_type, 
-             caption = 'Number of studies per objective by collaboration type', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-<!-- ## Model characteristics  -->
-
-## Individual heterogeneity: agent-based versus compartmental models
-
-```{r}
-individual_representation <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, individual_representation, sort = TRUE) %>% 
-  pivot_wider(names_from = individual_representation, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('compartments', 'agents', 'individuals_representation_other')) %>% 
-  adorn_pct_formatting(... = c('compartments', 'agents', 'individuals_representation_other')) %>% 
-  adorn_ns(... = c('compartments', 'agents', 'individuals_representation_other'))
-
-knitr::kable(individual_representation, caption = 'How individuals were represented', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-<!-- ### Individual representation by model structure -->
-<!-- ```{r} -->
-<!-- mod_structure_vs_individual_representation <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   group_by(collab_type) %>%  -->
-<!--   count(model_structure, individual_representation, sort = TRUE) %>%  -->
-<!--   pivot_wider(names_from = model_structure, values_from = n) %>%  -->
-<!--   adorn_totals(where = c('col', 'row')) -->
-
-<!-- knitr::kable(mod_structure_vs_individual_representation, caption = 'Model structure versus individual heterogeneity') -->
-<!-- ``` -->
-
-## Spatial heterogeneity
-
-```{r}
-space_representation <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, space_representation, sort = TRUE) %>% 
-  pivot_wider(names_from = space_representation, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no', 'yes')) %>% 
-  adorn_pct_formatting(... = c('no', 'yes')) %>% 
-  adorn_ns(... = c('no', 'yes'))
-
-knitr::kable(space_representation, caption = 'Was space explicitly represented in the model',
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-<!-- ### Spatial models by model structure -->
-<!-- ```{r} -->
-<!-- mod_structure_vs_space_representation <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   group_by(collab_type) %>%  -->
-<!--   count(model_structure, space_representation, sort = TRUE) %>%  -->
-<!--   pivot_wider(names_from = model_structure, values_from = n) %>%  -->
-<!--   adorn_totals(where = c('col', 'row')) -->
-
-<!-- knitr::kable(mod_structure_vs_space_representation, caption = 'Model structure versus spatial heterogeneity') -->
-<!-- ``` -->
-
-## Model dynamics: deterministic vs stochastic
-
-```{r}
-stochastic_vs_deterministic <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, model_structure) %>% 
-  pivot_wider(names_from = model_structure, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('both', 'deterministic', 'stochastic')) %>% 
-  adorn_pct_formatting(... = c('both', 'deterministic', 'stochastic')) %>% 
-  adorn_ns(... = c('both', 'deterministic', 'stochastic'))
-
-knitr::kable(stochastic_vs_deterministic, caption = 'Model dynamics (deterministic versus stochastic)', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-<!-- ## Modelling methods -->
-
-## Outcomes measured
-
-<!-- We tallied the overall top five outcomes most used between the two collaboration types.  -->
-
-<!-- The top five most commonly used outcomes, irrespective of collaboration type, were: final epidemic size, attack rate, timing of epidemic peak, cases averted, and outbreak duration. -->
-
-<!-- There was no difference in the two collaboration types as they were commonly used by both groups. -->
-
-```{r}
-outcomes_overall <- compact_data_with_citation_keys_no_fmd %>% 
-mutate(outcome_measured = str_trim(outcome_measured)) %>% 
-  separate_rows(outcome_measured, sep = ',') %>% 
-  group_by(collab_type, outcome_measured) %>% 
-  distinct(title, .keep_all = TRUE) %>% 
-  filter(outcome_measured %nin% c('outcome_other', '', 's')) %>% 
-  count(collab_type, outcome_measured, name = 'num_of_studies') %>% 
-  ungroup(outcome_measured) %>% 
-  arrange(desc(num_of_studies), .by_group = TRUE) %>% 
-  ungroup() %>% 
-  adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns()
-
-knitr::kable(outcomes_overall, caption = 'Model outcomes by collaboration type', 
-             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position', 'repeat_header'), font_size = 8)
-```
-
-```{r eval=FALSE}
-outcomes_tally_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
-  mutate(outcome_measured = str_trim(outcome_measured)) %>% 
-  separate_rows(outcome_measured, sep = ',') %>% 
-  group_by(outcome_measured) %>% 
-  distinct(title, .keep_all = TRUE) %>% 
-  ungroup(outcome_measured) %>% 
-  filter(outcome_measured %nin% c('outcome_other', '')) %>% 
-  group_by(collab_type) %>% 
-  count(outcome_measured) %>% 
-  arrange(desc(n), .by_group = TRUE) %>% 
-  # slice(1:6) %>% 
-  ungroup()
-
-# outcomes_tally_plot <- ggplot(data = outcomes_tally_by_collab_type, 
-#                               aes(x = reorder(outcome_measured, n), 
-#                                   y = n
-#                                   )
-#                               ) + 
-#   geom_bar(stat = 'identity') + 
-#   labs(x = '**Outcome**', y = '**Number of times used**') +
-#   coord_flip() +
-#   facet_wrap('collab_type') +
-#   md_theme_minimal()
-
-collab_type_labels <- c('purely_academic' = 'Purely academic', 
-                        'mixed' = 'Mixed'
-                        )
-
-outcomes_tally_plot <- ggplot(data = outcomes_tally_by_collab_type, 
-                              aes(label = outcome_measured, 
-                                  size = n
-                                  )
-                              ) + 
-  geom_text_wordcloud_area() +
-  scale_size_area(max_size = 10) + 
-  facet_wrap(~ collab_type, 
-             labeller = as_labeller(collab_type_labels),
-             strip.position = 'top'
-             ) +
-  #theme_minimal() + 
-  theme(strip.text = element_text(size = 15, face = 'bold'))
-
-print(outcomes_tally_plot)
-
-ggsave(filename = 'outcomes_tally_plot.tiff',
-       plot = outcomes_tally_plot, 
-       device = 'tiff',
-       path = save_fig_here
-       )
-
-ggsave(filename = 'outcomes_tally_plot.tiff',
-       plot = outcomes_tally_plot, 
-       device = 'tiff',
-       path = save_thesis_fig_here
-       )
-```
-
-<!-- ### Parametrization methods -->
-
-<!-- ```{r} -->
-<!-- #wide data for table -->
-<!-- model_parametrization_wide <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(collab_type, parametrization, sort = TRUE) %>%  -->
-<!--   pivot_wider(names_from = parametrization, values_from = n) %>%  -->
-<!--   adorn_totals(where = c('row', 'col')) %>%  -->
-<!--   adorn_percentages(... = -c('Total', 'collab_type')) %>%  -->
-<!--   adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%  -->
-<!--   adorn_ns(... = -c('Total', 'collab_type'))  -->
-
-<!-- #table -->
-<!-- knitr::kable(model_parametrization_wide, caption = 'How model parameters are obtained',  -->
-<!--              format = "latex", booktabs = TRUE) %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'scale_down', 'HOLD_position')) -->
-<!-- ``` -->
-
-<!-- ```{r eval=FALSE} -->
-<!-- #long data for plotting -->
-<!-- model_parametrization_long <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   group_by(collab_type) %>%  -->
-<!--   count(parametrization, sort = TRUE) -->
-
-<!-- #plotting -->
-<!-- ggplot(data = model_parametrization_long,  -->
-<!--        aes(fill = collab_type,  -->
-<!--            area = n,  -->
-<!--            label = parametrization, -->
-<!--            subgroup = parametrization -->
-<!--            ) -->
-<!--        ) +  -->
-<!--   geom_treemap() + -->
-<!--   geom_treemap_text(colour = "white", -->
-<!--                     place = "centre", -->
-<!--                     size = 15, -->
-<!--                     grow = TRUE -->
-<!--                     ) + -->
-<!--   md_theme_minimal(base_size = 12)  -->
-
-<!-- ``` -->
-
-<!-- ### Validation methods  -->
-
-<!-- ```{r} -->
-<!-- #wide data for table -->
-<!-- model_validation_wide <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(collab_type, validation, sort = TRUE) %>%  -->
-<!--   pivot_wider(names_from = validation, values_from = n) %>%  -->
-<!--   replace_na(list(none = 0,  -->
-<!--                   data = 0,  -->
-<!--                   another_model = 0,  -->
-<!--                   none_and_data = 0,  -->
-<!--                   data_and_another_model = 0 -->
-<!--                   ) -->
-<!--              ) %>%  -->
-<!--   adorn_totals(where = c('row', 'col')) %>%  -->
-<!--   adorn_percentages(... = -c('Total', 'collab_type')) %>%  -->
-<!--   adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%  -->
-<!--   adorn_ns(... = -c('Total', 'collab_type'))  -->
-
-<!-- #table -->
-<!-- knitr::kable(model_validation_wide, caption = 'How the model\'s performance is assessed',  -->
-<!--              format = "latex", booktabs = TRUE) %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'scale_down', 'HOLD_position')) -->
-<!-- ``` -->
-
-## Sensitivity analysis
-
-<!-- Less than half (46.5%; 106/228) of the total studies performed sensitivity analyses. There was no clear difference between the collaborations.  -->
-
-```{r eval=FALSE}
-mod_structure_vs_sensitivity_analysis <- compact_data_with_citation_keys_no_fmd %>% 
-  count(model_structure, sensitivity_analysis, sort = TRUE) %>% 
-  pivot_wider(names_from = sensitivity_analysis, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no', 'yes')) %>% 
-  adorn_pct_formatting(... = c('no', 'yes')) %>% 
-  adorn_ns(... = c('no', 'yes'))
-
-knitr::kable(mod_structure_vs_sensitivity_analysis, 'Sensitivity analysis in relation to model structure', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
+    arrange(desc(publication_year))
 ```
@@
 ```{r}
-sensitivity_analysis <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, sensitivity_analysis, sort = TRUE) %>% 
-  pivot_wider(names_from = sensitivity_analysis, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no', 'yes')) %>% 
-  adorn_pct_formatting(... = c('no', 'yes')) %>% 
-  adorn_ns(... = c('no', 'yes'))
-
-knitr::kable(sensitivity_analysis, caption = 'Sensitivity analysis', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
+#columns 2-5 with paper titles
+knitr::kable(final_citation_table %>% 
+                 dplyr::select(1:5), 
+             format = "latex", booktabs = TRUE, 
+             longtable = TRUE#,
+             #caption = 'Extracted data per paper: publication_year, author_affiliation_type, country_studied, author_in_country_studied.'
+             ) %>% 
+    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
+    kableExtra::column_spec(column = c(1, 3), width = "5cm") %>% 
+    kableExtra::landscape()
 ```
 
-## Data use and data availability
+```{r}
+#columns 6-10 with paper titles
+knitr::kable(final_citation_table %>% 
+                 dplyr::select(1, 6:10), 
+             format = "latex", booktabs = TRUE, 
+             longtable = TRUE#,
+             #caption = 'Extracted data per paper: disease, objectives, individual_representation, space_representation, model_structure.'
+             ) %>% 
+    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
+    kableExtra::column_spec(column = c(1), width = "5cm") %>% 
+    kableExtra::landscape()
+```
 
 ```{r}
-data_use_and_availability <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(data_used == 'yes') %>%
-  count(collab_type, data_available, sort = TRUE) %>% 
-  pivot_wider(names_from = data_available, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no', 'yes')) %>% 
-  adorn_pct_formatting(... = c('no', 'yes')) %>% 
-  adorn_ns(... = c('no', 'yes'))
-
-knitr::kable(data_use_and_availability, 
-             caption = 'Data accessibility', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
+#columns 11-15 with paper titles
+knitr::kable(final_citation_table %>% 
+                 dplyr::select(1, 11:15), 
+             format = "latex", booktabs = TRUE, 
+             longtable = TRUE#,
+           #  caption = 'Extracted data per paper: parametrization, validation, outbreak_type, intervention_modelled, vax_modelled_with_non_vax.'
+             ) %>% 
+    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
+    kableExtra::column_spec(column = c(1, 2, 5), width = "4cm") %>% 
+    kableExtra::landscape()
 ```
 
-## Code availability
-
 ```{r}
-code_availability <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, simulation_code_available) %>% 
-  pivot_wider(names_from = simulation_code_available, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no', 'yes')) %>% 
-  adorn_pct_formatting(... = c('no', 'yes')) %>% 
-  adorn_ns(... = c('no', 'yes'))
-
-knitr::kable(code_availability, caption = 'Code availability', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+#columns 16-22 with paper titles
+knitr::kable(final_citation_table %>% 
+                 dplyr::select(1, 16:22), 
+             format = "latex", booktabs = TRUE, 
+             longtable = TRUE#,
+           #  caption = 'Extracted data per paper: is_vax_effective, outcome_measured, sensitivity_analysis, data_used, data_available, simulation_code_available, vax_modelled.'
+             ) %>% 
+    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
+    kableExtra::column_spec(column = c(1, 3), width = "5cm") %>% 
+    kableExtra::landscape()
 ```
-
-```{r eval=FALSE}
-papers_with_code_available <- compact_data_with_citation_keys_no_fmd %>% 
-    filter(simulation_code_available == 'yes') %>% 
-    as.data.frame()
-
-openxlsx::write.xlsx(papers_with_code_available, file = '../citation_tables/papers_with_code_available.xlsx')
-
-```
-
-# Foot and mouth disease (FMD)
-
-<!-- ## Collaboration patterns in time -->
-
-## Unique combinations of author affiliation types
-
-```{r}
-#' Count by collaboration types and make a bar plot
-author_affiliation_type_combos <- fmd_data %>%
-    count(author_affiliation_type, sort = TRUE) %>% 
-    mutate(author_affiliation_type = as_factor(author_affiliation_type)) %>% 
-    arrange(desc(n)) %>% 
-    adorn_totals() %>% 
-    adorn_percentages(denominator = 'col') %>% 
-    adorn_pct_formatting() %>% 
-    adorn_ns()
-
-knitr::kable(author_affiliation_type_combos, caption = 'Number of studies by author affiliation type combination',
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-## Collaboration types (aggregated)
-
-```{r}
-#' Count by collaboration types and make a bar plot
-studies_per_collab_type <- fmd_data %>%
-    count(collab_type, sort = TRUE) %>% 
-    arrange(desc(n)) %>% 
-    adorn_totals() %>% 
-    adorn_percentages(denominator = 'col') %>% 
-    adorn_pct_formatting() %>% 
-    adorn_ns()
-
-knitr::kable(studies_per_collab_type, caption = 'Number of studies per collaboration type',
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-### Proportions of the total publications per year by collaboration type
-
-```{r echo=FALSE, fig.width=8}
-#' Count the number of each author affiliation type per year (including FMD)
-fmd_collab_types_per_year <- fmd_data %>% 
-  count(year_aggreg, 
-        collab_type, 
-        name = 'total_publications'
-        )
-
-#The plot
-# Modify the x-axis labels to account for the lumping of the years from 2005 and below
-x_axis_labels <- as.character(seq(2005, 2020, 2))
-
-x_axis_labels[1] <- '1970-2005'
-
-fmd_collab_proportions_plot <- ggplot(data = fmd_collab_types_per_year) + 
-  geom_bar(aes(x = year_aggreg,
-               y = total_publications,
-               fill = collab_type
-               ),
-           color = 'black',
-           stat = 'identity',
-           position = position_fill(reverse = TRUE)#,
-           #show.legend = FALSE
-             ) +
-  scale_fill_manual(values = c('tan3', 'turquoise2')) +
-  scale_x_continuous(breaks = seq(2005, 2020, 2),
-                     labels = x_axis_labels,
-                     expand = c(0, 0)
-                     ) +
-  #coord_flip() +
-  labs(#title = 'Publications per collaboration type over time',
-       x = '**Year**',
-       y = '**Proportion of total publications**',
-       fill = '**Collaboration type**' 
-         ) +
-  theme(legend.position = 'none') +
- # md_theme_minimal(base_size = 16) #For Powerpoint
-  md_theme_minimal(base_size = 12)
-
-plot(fmd_collab_proportions_plot)
-
-```
-
-### Absolute number of publications per year by collaboration type
-
-```{r}
-#' Count the number of each author affiliation type per year
-fmd_collabs_per_year <- fmd_data %>% 
-  count(year_aggreg, 
-        collab_type, 
-        name = 'total_publications'
-        )
-
-collabs_per_year_plot <- ggplot(data = fmd_collabs_per_year, 
-                                    aes(x = year_aggreg, 
-                                        y = total_publications
-                                        ), 
-                                    color = 'black') + 
-  geom_bar(aes(fill = collab_type), 
-           stat = 'identity', 
-           position = 'dodge',
-           width = 0.5
-           ) + 
-  scale_fill_manual(values = c('tan3', 'turquoise2')) + 
-  scale_x_continuous(breaks = seq(2005, 2020, 2),
-                     labels = x_axis_labels,
-                     expand = c(0, 0)
-                     ) +
-  labs(x = '**Year**', 
-       y = '**Total publications**', 
-       fill = 'Collaboration type'
-       ) +
-  md_theme_minimal(base_size = 12) +
-  #md_theme_minimal(base_size = 16) +
-  theme(legend.position = 'bottom')
-
-plot(collabs_per_year_plot)
-
-```
-
-<!-- ## Collaboration patterns in geographic space -->
-
-## Geographic connection of authors to the studied locations 
-```{r}
-author_connectedness_to_location_fmd <- fmd_data %>% 
-  filter(author_in_country_studied != 'not_applicable') %>% 
-  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
-  group_by(collab_type) %>% 
-  count(country_studied, author_in_country_studied, sort = TRUE) %>% 
-  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
-  replace_na(list(yes = 0, no = 0)) %>% 
-  arrange(collab_type, desc(yes)) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('yes', 'no')) %>% 
-  adorn_pct_formatting(... = c('yes', 'no')) %>% 
-  adorn_ns(... = c('yes', 'no')) %>% 
-  ungroup()
-
-knitr::kable(author_connectedness_to_location_fmd, caption = 'Studies with at least one author affiliation in the location studied', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-### Aggregated
-
-```{r}
-author_connectedness_to_location_aggreg <- fmd_data %>% 
-  filter(author_in_country_studied != 'not_applicable') %>% 
-  filter(country_studied %nin% c('other', 'none', 'northern_hemisphere', 'west_africa', 'global')) %>% 
-  count(collab_type, author_in_country_studied, sort = TRUE) %>% 
-  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
-  replace_na(list(yes = 0, no = 0)) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('yes', 'no')) %>% 
-  adorn_pct_formatting(... = c('yes', 'no')) %>% 
-  adorn_ns(... = c('yes', 'no'))
-
-knitr::kable(author_connectedness_to_location_aggreg, 
-             caption = 'Studies with at least one author affiliation in the location studied', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-## Interventions
-
-### Types of interventions
-
-```{r}
-intervention_categories_fmd <- fmd_data %>% 
-  count(collab_type, intervention_type, sort = TRUE) %>% 
-  pivot_wider(names_from = intervention_type, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
-  adorn_pct_formatting(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
-  adorn_ns(... = c('no_vax', 'vax_combination_with_others', 'vax_single'))
-
-knitr::kable(intervention_categories_fmd, caption = 'Number of studies per intervention type', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-### Impact of vaccination
-
-```{r}
-fmd_vax_impact_conclusions <- fmd_data %>% 
-  filter(intervention_type == 'vax_single') %>% 
-  count(collab_type, is_vax_effective, sort = T) %>% 
-  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
-  replace_na(list(no = 0, inconclusive = 0, yes = 0)) %>% 
-  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
-  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
-  adorn_ns(... = c('yes', 'no', 'inconclusive'))
-
-#Print the results
-knitr::kable(fmd_vax_impact_conclusions, 
-             caption = 'Conclusions about impact of vaccination', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-## Modelling objectives
-
-```{r echo=FALSE}
-#count the number of studies per objective type
-modelling_objectives_fmd <- fmd_data %>% 
-  count(collab_type, objectives, name = 'num_of_studies') %>% 
-  pivot_wider(names_from = objectives, values_from = num_of_studies) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('future', 'past')) %>% 
-  adorn_pct_formatting(... = c('future', 'past')) %>% 
-  adorn_ns(... = c('future', 'past'))
-
-#Print a table of the results
-knitr::kable(modelling_objectives_fmd,
-             caption = 'Study objectives by collaboration type', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-<!-- ### Modelling objectives and outbreak type by collaboration types -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- objectives_and_outbreak_types_fmd <- fmd_data %>%  -->
-<!--   count(objectives, outbreak_type, name = 'num_of_studies', sort = TRUE) %>%  -->
-<!--   pivot_wider(names_from = objectives,  -->
-<!--               values_from = num_of_studies -->
-<!--               ) %>%  -->
-<!--   replace_na(list(future = 0, past = 0, both = 0)) %>%  -->
-<!--   adorn_totals(where = c('row', 'col')) %>%  -->
-<!--   adorn_percentages(... = c('future', 'past')) %>%  -->
-<!--   adorn_pct_formatting(... = c('future', 'past')) %>%  -->
-<!--   adorn_ns(... = c('future', 'past'))  -->
-
-<!-- knitr::kable(objectives_and_outbreak_types_fmd,  -->
-<!--              caption = 'Number of studies per objective and outbreak type',  -->
-<!--              format = "latex", booktabs = TRUE) %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position')) -->
-<!-- ``` -->
-
-## Outbreak types
-
-```{r echo=FALSE}
-#Outbreak types per collab type
-outbreak_types_by_collab_type_fmd <- fmd_data %>% 
-  count(collab_type, outbreak_type, name = 'num_of_studies') %>% 
-  pivot_wider(names_from = outbreak_type, values_from = num_of_studies) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('hypothetical_outbreak', 'real_outbreak')) %>% 
-  adorn_pct_formatting(... = c('hypothetical_outbreak', 'real_outbreak')) %>% 
-  adorn_ns(... = c('hypothetical_outbreak', 'real_outbreak'))
-
-#Print a table of the results
-knitr::kable(outbreak_types_by_collab_type_fmd,
-             caption = 'Study objectives by collaboration type', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-<!-- ## Model characteristics  -->
-
-## Individual heterogeneity: agent-based versus compartmental models
-
-```{r}
-individual_representation_fmd <- fmd_data %>% 
-  count(collab_type, individual_representation, sort = TRUE) %>% 
-  pivot_wider(names_from = individual_representation, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('compartments', 'agents')) %>% 
-  adorn_pct_formatting(... = c('compartments', 'agents')) %>% 
-  adorn_ns(... = c('compartments', 'agents'))
-
-knitr::kable(individual_representation_fmd, 
-             caption = 'How individuals are represented', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-## Spatial heterogeneity
-
-```{r}
-space_representation_fmd <- fmd_data %>% 
-  count(collab_type, space_representation, sort = TRUE) %>% 
-  pivot_wider(names_from = space_representation, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no', 'yes')) %>% 
-  adorn_pct_formatting(... = c('no', 'yes')) %>% 
-  adorn_ns(... = c('no', 'yes'))
-
-knitr::kable(space_representation_fmd, caption = 'Models with spatial structure', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-## Model dynamics: deterministic vs stochastic
-
-```{r}
-stochastic_vs_deterministic_fmd <- fmd_data %>% 
-  count(collab_type, model_structure) %>% 
-  pivot_wider(names_from = model_structure, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('deterministic', 'stochastic')) %>% 
-  adorn_pct_formatting(... = c('deterministic', 'stochastic')) %>% 
-  adorn_ns(... = c('deterministic', 'stochastic'))
-
-knitr::kable(stochastic_vs_deterministic_fmd, 
-             caption = 'Model dynamics (deterministic versus stochastic)', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
-```
-
-<!-- ## Modelling methods -->
-
-## Outcomes measured
-```{r}
-outcomes_tally_by_collab_type <- fmd_data %>% 
-  mutate(outcome_measured = str_trim(outcome_measured)) %>% 
-  separate_rows(outcome_measured, sep = ',') %>% 
-  group_by(collab_type, outcome_measured) %>% 
-  distinct(title, .keep_all = TRUE) %>% 
-  filter(outcome_measured %nin% c('outcome_other', '')) %>% 
-  count(collab_type, outcome_measured, name = 'num_of_studies') %>% 
-  ungroup(outcome_measured) %>% 
-  arrange(desc(num_of_studies), .by_group = TRUE) %>% 
-  ungroup() %>% 
-  adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns()
-
-knitr::kable(outcomes_tally_by_collab_type, 
-             caption = 'Model outcomes by collaboration type', 
-             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position', 'repeat_header'))
-```
-
-```{r eval=FALSE}
-collab_type_labels <- c('purely_academic' = 'Purely academic', 
-                        'mixed' = 'Mixed'
-                        )
-
-outcomes_tally_plot <- ggplot(data = outcomes_tally_by_collab_type, 
-                              aes(label = outcome_measured, 
-                                  size = n
-                                  )
-                              ) + 
-  geom_text_wordcloud_area() +
-  scale_size_area(max_size = 7) + 
-  facet_wrap(~ collab_type, 
-             labeller = as_labeller(collab_type_labels),
-             strip.position = 'top'
-             ) +
-  #theme_minimal() + 
-  theme(strip.text = element_text(size = 15, face = 'bold'))
-
-#save the plot
-ggsave(filename = 'outcomes_tally_fmd_plot.tiff',
-       plot = outcomes_tally_plot, 
-       device = 'tiff',
-       path = save_fig_here
-       )
-```
-
-## Parametrization methods
-
-```{r}
-#wide data for table
-model_parametrization_fmd_wide <- fmd_data %>% 
-  count(collab_type, parametrization, sort = TRUE) %>% 
-  pivot_wider(names_from = parametrization, values_from = n) %>% 
-  replace_na(list('expert_opinion and fitted' = 0, 'literature and fitted' = 0)) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = -c('Total', 'collab_type')) %>% 
-  adorn_pct_formatting(... = -c('Total', 'collab_type')) %>% 
-  adorn_ns(... = -c('Total', 'collab_type')) 
-#table
-knitr::kable(model_parametrization_fmd_wide, 
-             caption = 'Model parametrization methods', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'scale_down',  'HOLD_position'))
-```
-
-## Validation methods
-
-```{r}
-#wide data for table
-model_validation_fmd_wide <- fmd_data %>% 
-  count(collab_type, validation, sort = TRUE) %>% 
-  pivot_wider(names_from = validation, values_from = n) %>% 
-  replace_na(list(none = 0, 
-                  data = 0, 
-                  another_model = 0, 
-                  data_and_another_model = 0
-                  )
-             ) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = -c('Total', 'collab_type')) %>% 
-  adorn_pct_formatting(... = -c('Total', 'collab_type')) %>% 
-  adorn_ns(... = -c('Total', 'collab_type'))
-
-#table
-knitr::kable(model_validation_fmd_wide, 
-             caption = 'Model validation methods', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped',  'HOLD_position'))
-```
-
-## Sensitivity analysis
-
-```{r}
-sensitivity_analysis_fmd <- fmd_data %>% 
-  count(collab_type, sensitivity_analysis, sort = TRUE) %>% 
-  pivot_wider(names_from = sensitivity_analysis, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no', 'yes')) %>% 
-  adorn_pct_formatting(... = c('no', 'yes')) %>% 
-  adorn_ns(... = c('no', 'yes'))
-
-knitr::kable(sensitivity_analysis_fmd, caption = 'Sensitivity analysis', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped',  'HOLD_position'))
-
-```
-
-## Data use and data availability
-
-```{r}
-data_use_and_availability_fmd <- fmd_data %>% 
-  filter(data_used == 'yes') %>%
-  count(collab_type, data_available, sort = TRUE) %>% 
-  pivot_wider(names_from = data_available, values_from = n) %>% 
-  replace_na(list(yes = 0, no = 0)) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('yes', 'no')) %>% 
-  adorn_pct_formatting(... = c('yes', 'no')) %>% 
-  adorn_ns(... = c('yes', 'no'))
-
-knitr::kable(data_use_and_availability_fmd, 
-             caption = 'Data accessibility', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
-```
-
-## Code availability
-
-```{r}
-
-code_availability_fmd <- fmd_data %>% 
-  count(collab_type, simulation_code_available) %>% 
-  pivot_wider(names_from = simulation_code_available, values_from = n) %>% 
-  adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns()
-
-knitr::kable(code_availability_fmd, caption = 'Code availability', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```

### 2023-03-02 analyses/scripts/orv_sys_rev_supplementary.Rmd
moved analysis scripts and data into a folder

--- 2023-03-02 scripts/orv_sys_rev_data_analysis_old.Rmd
@@
 ---
-title: "Systematic review of outbreak response models"
+title: "Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)"
 author: "James Azam"
-date: "01/06/2021"
+date: '`r format(Sys.Date(), "%B %d, %Y")`'
 output:
@@
     keep_md: yes
-#  html_notebook
+    reference_docx: word-style.docx
+    toc: yes
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
-
-# Sets the working directory for subsequent chunks, but not this chunk
-#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
-
-knitr::opts_chunk$set(fig.width = 8, fig.height = 6)
-```
-
-```{r echo=FALSE, message=FALSE}
+```{r echo=FALSE, message=FALSE, include=FALSE}
 #' load packages
@@
 
-```{r echo=FALSE, include=FALSE, eval=FALSE}
-# Source the script that cleans the raw data
-# Load the script that cleans the data and saves it; 
-# this should be run each time, just in case something has changed in the data cleaning process;
-# The script clears the environment after cleaning the data
-#source('./data_cleaning/orv_models_review_data_cleaning.R')
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+
+# Sets the working directory for subsequent chunks, but not this chunk
+#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
 ```
@@
   )) %>% 
-  relocate(vax_modelled, intervention_type, .after = 'intervention_modelled')
-
-# The data with citations 
-compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/final_data/cleaned_data/compact_data_with_citation_keys_cleaned.rds'))
-
-compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>% 
-  mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
-                               'yes', 
-                               'no')
-         ) %>% 
-  mutate(intervention_type = case_when(
-    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_alongside', #when vax was modelled but not for comparison as a single intervention
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
-  )) %>% 
-  relocate(vax_modelled, intervention_type, .after = 'intervention_modelled')
-
-# Remove the FMD papers (NB: We only use the FMD papers for comparison)
-long_data_no_fmd <- long_data %>% filter(disease != 'fmd')
-
-compact_data_no_fmd <- compact_data %>% filter(disease != 'fmd')
-
-compact_data_with_citation_keys_no_fmd <- compact_data_with_citation_keys %>% filter(disease != 'fmd') 
-```
-
-# Exploratory Data Analysis
-1. Publications per year
-2. Distribution of collaborations across types (aggregated)
-3. Countries/settings being studied (author affiliation vs country studied)
-
-# What science is being inferred from models?
-
-1. Impact of vaccination (human diseases vs FMD); analyse with and without Influenza
-2. What diseases are being studied (to understand vaccine impact)
-3. Which interventions are being studied?
-
-```{r echo=FALSE}
-
-pubs_per_year <- compact_data_no_fmd %>% 
-  mutate(publication_year = as.numeric(publication_year)) %>% 
-  count(publication_year)
-
-pubs_per_year_bar_plot <- ggplot(data = pubs_per_year) + 
-  geom_bar(aes(x = publication_year, 
-               y = n
-               ), 
-           stat = 'identity', 
-           color = 'black',
-           fill = 'tomato3') +
-  scale_y_continuous(breaks = seq(0, 30, 2),
-                     labels = seq(0, 30, 2)
-                     ) +
-  labs(x = 'Year of publication', y = 'Number of papers') +
-  theme_minimal()
-
-plot(pubs_per_year_bar_plot)
-
-```
-
-# Modelling objectives
-
-```{r echo=FALSE}
-#Find the uniques entries
-modelling_objectives_unique_entries <- long_data_no_fmd %>% 
-  select(title, objectives) %>% 
-  distinct()
-
-#count the number of studies per objective type
-modelling_objectives_count <- modelling_objectives_unique_entries %>% 
-  count(objectives, name = 'num_of_studies')
-
-#Print a table of the results
-knitr::kable(modelling_objectives_count,
-             col.names = c('Objective type',
-                           'Number of studies'
-                           ),
-             caption = 'Number of studies per objective type'
-             )
-```
-
-```{r echo=FALSE}
-#Find the unique entries 
-outbreak_types_unique_entries <- long_data_no_fmd %>% 
-  select(title, outbreak_type) %>% 
-  distinct()
-
-#Count the number of studies per outbreak type  
-outbreak_types_count <- outbreak_types_unique_entries %>% 
-  count(outbreak_type, name = 'num_of_studies')
-
-#Print a table of the results
-knitr::kable(outbreak_types_count,
-             col.names = c('Outbreak type',
-                           'Number of studies'
-                           ),
-             caption = 'Number of studies per outbreak type'
-             )
-```
-
-```{r echo=FALSE}
-#Find the number of unique entries per objective type and outbreak type combination  
-modelling_objectives_by_outbreak_type_unique_entries <- long_data_no_fmd %>% 
-  select(title, objectives, outbreak_type) %>% 
-  group_by(title) %>% 
-  distinct() %>% 
-  ungroup()
-
-modelling_objectives_by_outbreak_type_count <- modelling_objectives_by_outbreak_type_unique_entries %>% 
-  count(objectives, outbreak_type, name = 'num_of_studies') %>% 
-  arrange(desc(num_of_studies)) %>% 
-  pivot_wider(names_from = outbreak_type, 
-              values_from = num_of_studies
-              )
-
-knitr::kable(modelling_objectives_by_outbreak_type_count, 
-             # col.names = c('Objective type', 
-             #               'Outbreak type', 
-             #               'Number of studies'
-             #               ),
-             caption = 'Number of studies per objective and outbreak type'
-             ) 
-```
-
-```{r echo=FALSE} 
-#Year with the highest publications
-max_pub_year <- compact_data_no_fmd %>% 
-    count(publication_year, sort = T) %>% 
-    filter(n == max(n))
-
-print(max_pub_year)
-```
-
-## Number of studies per disease 
-```{r echo=FALSE}
-disease_studied_count <- long_data_no_fmd %>% 
-  group_by(disease) %>% 
-  distinct(title) %>% 
-  count(disease, name = 'num_of_studies', sort = T) %>%
-  ungroup()
-
-knitr::kable(disease_studied_count, col.names = c('Disease', 'Number of studies'))
-```
-
-### Disease most studied
-```{r echo=FALSE}
-disease_studied_most <- disease_studied_count %>% 
-  filter(num_of_studies == max(num_of_studies))
-
-knitr::kable(disease_studied_most)
-```
-
-## Number of studies per country and continent
-
-```{r echo=FALSE, warning=FALSE, message=FALSE}
-#FIXME: I have to cross tabulate the countries studied with number of studies with at least one author located in the country being studied.
-
-#Tally of how many times and percentage of times each COUNTRY has been studied
-countries_studied_by_count <- long_data_no_fmd %>% 
-    group_by(country_studied) %>%
-    distinct(title) %>% 
-    count(country_studied, name = 'num_of_studies', sort = T) %>% 
-    ungroup(country_studied) %>% 
-    mutate(country_studied = as_factor(country_studied), 
-           percentage = round(num_of_studies/sum(num_of_studies)*100, 1)
-           )
-
-#'Modify the data frame to lump together all countries with less than some number of studies as 'other' and recalculate the percentage studied
-countries_studied_by_count_aggregated <- countries_studied_by_count %>% 
-  mutate(country_studied_aggreg = if_else(num_of_studies < 9, 
-                                          'other', 
-                                          as.character(country_studied)
-                                          )
-         ) %>% 
-  group_by(country_studied_aggreg) %>%
-  summarise(num_of_studies = sum(num_of_studies),
-            percentage = sum(percentage),
-            .groups = 'drop'
-            ) %>% 
-  arrange(desc(percentage)) %>% 
-  mutate(country_studied_aggreg = as_factor(country_studied_aggreg))
-
-#Print the results
-knitr::kable(countries_studied_by_count_aggregated, 
-             col.names = c('Country', 
-                           'Number of studies', 
-                           'Percentage'
-                           ),
-             caption = 'Number/percentage of studies per country'
-             )
-```
-
-## Number and percentage of studies per continent
-```{r echo=FALSE}
-continents_studied_by_count <- countries_studied_by_count %>% 
-  mutate(continent_studied = countrycode(country_studied, 
-                                          destination = 'continent',
-                                          origin = 'iso2c',
-                                          nomatch = NULL #if there is no match, keep the original
-                                          )
-         ) %>% 
-  mutate(continent_studied = str_to_lower(continent_studied)
-         ) %>% 
-  mutate(continent_studied = case_when(str_detect(continent_studied, 'asia') == T ~ 'asia', 
-                                         str_detect(continent_studied, 'africa') == T ~ 'africa', 
-                                         TRUE ~ continent_studied
-                                       )
-           ) %>% 
-  group_by(continent_studied) %>%
-  summarise(num_of_studies = sum(num_of_studies), 
-            percentage = sum(percentage),
-            .groups = 'drop'
-            ) %>% 
-  arrange(desc(percentage))
-
-#Print the results
-knitr::kable(continents_studied_by_count, 
-             col.names = c('Continent', 
-                           'Number of studies', 
-                           'Percentage'
-                           ),
-             caption = 'Number/percentage of studies per continent'
-             )
-```
-
-### Country most studied 
-```{r echo=FALSE}
-countries_studied_most <- countries_studied_by_count %>% 
-    filter(country_studied != 'none') %>%
-    filter(num_of_studies == max(num_of_studies))
-
-#Print the result as a table    
-knitr::kable(countries_studied_most, 
-             col.names = c('Country', 
-                           'Number of studies', 
-                           'Percentage'
-                           ),
-             caption = 'Most studied country'
-             )
-```
-
-### Continent most studied
-```{r echo=FALSE}
-
-continent_studied_most <- continents_studied_by_count %>% 
-    dplyr::filter(continent_studied != 'none') %>% 
-    filter(num_of_studies == max(num_of_studies))
-
-#Print the result as a table      
-knitr::kable(continent_studied_most,
-             col.names = c('Continent', 
-                           'Number of studies',
-                           'Percentage'
-                           ),
-             caption = 'Most studied continent'
-             )
-```
-
-## Number of studies per continent
-```{r echo=FALSE}
-continents_studied <- continents_studied_by_count %>% 
-  filter(continent_studied != 'none') %>% 
-  filter(continent_studied != 'global') %>% 
-  filter(continent_studied != 'northern_hemisphere') %>% 
-  group_by(continent_studied) %>% 
-  summarise(num_of_studies = sum(num_of_studies )) %>% 
-  ungroup() %>% 
-  mutate(percentage = round(num_of_studies/sum(num_of_studies)*100, 1))
-
-#Print table of results
-knitr::kable(continents_studied_by_count %>% arrange(desc(percentage)),
-             col.names = c('Continent',
-                           'Number of papers',
-                           'Percentage'
-                           ),
-             caption = 'Number/percent of studies by continent'
-             )
-
-```
-
-### Highest number of studies per year and disease
-
-```{r echo=FALSE}
-knitr::kable(tibble(max_pub_year = max_pub_year$publication_year, 
-                    disease_with_max_pubs = disease_studied_most$disease,
-                    country_most_studied = countries_studied_most$country_studied
-                    )
-             )
-```
-
-# Primary objectives
-
-## 1.A. Is modelling being used to inform outbreak response policy-making?
-
-### I. How are the results distributed according to collaboration type?
-
-Note that we do not include FMD in all the primary analyses. We only use it for comparisons, where necessary.
-
-```{r echo=FALSE}
-# 1B. Create the unique combinations of collaboration types and reword the string NA
-collab_type_data <- compact_data_no_fmd %>%
-  select(title, publication_year, author_affiliation_type, author_in_country_studied) %>% 
   mutate(publication_year = as.numeric(publication_year), 
@@
                                         )
-    )
-
+    ) %>% 
+  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, #An approach to aggregate the years before 2006 into one group because of the low number of papers
+                                         2005, 
+                                         publication_year
+                                         )
+                                  ), 
+         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
+                                         'purely_academic', 
+                                         'mixed')
+                                 )
+         )
+
+# The data with citations 
+compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/final_data/cleaned_data/compact_data_with_citation_keys_cleaned.rds'))
+
+compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>% 
+    mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
+                               'yes', 
+                               'no')
+         ) %>% 
+  mutate(intervention_type = case_when(
+    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
+    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_alongside', #when vax was modelled but not for comparison as a single intervention
+    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
+  )) %>% 
+  mutate(publication_year = as.numeric(publication_year), 
+         author_in_country_studied = as.character(author_in_country_studied)) %>% 
+  arrange(publication_year) %>%
+  mutate(
+    author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + '),
+    author_in_country_studied = if_else(author_in_country_studied == 'NA', 'not_applicable',
+                                        author_in_country_studied
+                                        )
+    ) %>% 
+  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, #An approach to aggregate the years before 2006 into one group because of the low number of papers
+                                         2005, 
+                                         publication_year
+                                         )
+                                  ), 
+         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
+                                         'purely_academic', 
+                                         'mixed')
+                                 )
+         )
+
+#Rearrange the columns
+compact_data_with_citation_keys <- compact_data_with_citation_keys %>% 
+  relocate(c(title, bibtexkey), .before = publication_year) %>% 
+  relocate(publication_year, .before = bibtexkey) %>% 
+  relocate(c(x0_reviewer, category, author:language), 
+           .after = collab_type
+           )
+
+# Remove the FMD papers (NB: We only use the FMD papers for comparison)
+long_data_no_fmd <- long_data %>% filter(disease != 'fmd')
+
+compact_data_no_fmd <- compact_data %>% filter(disease != 'fmd')
+
+compact_data_with_citation_keys_no_fmd <- compact_data_with_citation_keys %>% filter(disease != 'fmd') 
+```
+```{r echo=FALSE}
 #' Count by collaboration types and make a bar plot
-collab_types_count <- collab_type_data %>%
-    count(author_affiliation_type) %>% 
+collab_types_count <- compact_data_no_fmd %>%
+    count(author_affiliation_type, sort = TRUE) %>% 
     mutate(author_affiliation_type = as_factor(author_affiliation_type))
@@
 
-### II. What has been the trend in collaboration over the years?
+### Trend in collaboration over the years
 
@@
 ```
-
-### III. Proportions of the total publications per year shared by collaboration type (purely academic versus mixed).
+# Number of studies per disease and intervention.
+
+```{r echo=FALSE}
+#count the number of unique interventions modelled
+interventions_unique_entries <- long_data_no_fmd %>% 
+  group_by(title) %>% 
+  distinct(intervention_modelled, .keep_all = TRUE) %>% 
+  ungroup()
+
+#interventions are disease specific
+interventions_per_disease <- interventions_unique_entries %>% 
+  mutate(intervention_modelled = str_trim(intervention_modelled)) %>% 
+  filter(intervention_modelled != 'e.g.') %>% #remove false rows
+  filter(intervention_modelled != 'various') %>% #remove false rows
+  group_by(disease) %>% 
+  count(intervention_modelled, name = 'num_of_studies') %>% 
+  arrange(disease, desc(num_of_studies)) %>% 
+  ungroup()
+
+knitr::kable(interventions_per_disease)
+
+```
+
+# Number of studies per outcome
+
+```{r echo=FALSE}
+#count the number of unique outcomes measured
+outcomes_unique_entries <- long_data_no_fmd %>% 
+  group_by(title) %>% 
+  distinct(outcome_measured, .keep_all = TRUE) %>% 
+  ungroup()
+
+#Count the number of studies 
+outcomes_count <- outcomes_unique_entries %>% 
+  group_by(outcome_measured) %>% 
+  count(outcome_measured, name = 'num_of_studies', sort = T) %>% 
+  ungroup() %>% 
+  filter(outcome_measured != 's')
+
+knitr::kable(outcomes_count)
+
+#Plot the result
+outcome_count_plot <- ggplot(data = outcomes_count) + 
+  geom_point(aes(x = reorder(outcome_measured, 
+                             num_of_studies), 
+               y = num_of_studies
+               ), 
+           stat = 'identity',
+           color = 'darkslategray4'
+           ) +
+  coord_flip() +
+  theme_minimal()
+
+plot(outcome_count_plot)
+
+```
+
+# Number of studies per model structure type
+
+```{r echo=FALSE}
+#Keep only the unique entries 
+model_structure_unique_entries <- long_data_no_fmd %>% 
+  group_by(title) %>% 
+  distinct(model_structure) %>% 
+  ungroup()
+
+#Count the number of studies
+model_structure_unique_count <- model_structure_unique_entries %>%
+    group_by(model_structure) %>% 
+    count(model_structure, name = 'num_of_studies')
+
+#Print the table
+knitr::kable(model_structure_unique_count)
+```
+
+# Model structure, parametrization, and validation types
+
+```{r echo=FALSE}
+#Cross tally the model structure with parametrization and validation categories
+#FIXME: Check that studies are either not being under counted or double-counted.
+What do I want to count here?
+Is it the unique studies per method or combined method because most studies used a combination of parametrization methods especially
+parametrization_and_validation_by_model_structure <- compact_data_no_fmd %>%
+  mutate(parametrization = str_replace(parametrization, ' ', ' + '),
+         validation = str_replace(validation, ' ', ' + ')
+         ) %>% 
+  count(model_structure, parametrization, validation) %>% 
+  pivot_wider(names_from = model_structure, values_from = n)
+
+#Print the table of results
+knitr::kable(parametrization_and_validation_by_model_structure,
+             caption = 'Parametrization and validation types per model structure')
+
+```
+
+# Model parametrization & validation
+
+```{r echo=FALSE}
+#Keep only the unique entries
+parametrization_and_validation_count <- compact_data_no_fmd %>% 
+  mutate(parametrization = str_replace(parametrization, ' ', ' + '), 
+         validation = str_replace(validation, ' ', ' + ')
+         ) %>% 
+  count(parametrization, 
+        validation, 
+        name = 'num_of_studies'
+        ) %>% 
+  group_by(parametrization) %>% 
+  arrange(desc(num_of_studies), .by_group = T)
+
+#Print the table
+knitr::kable(parametrization_and_validation_count)
+
+```
+
+# How is sensitivity analysis distributed by model structure?
+
+```{r echo=FALSE}
+#Keep only the unique entries
+sensitivity_analysis_unique_entries <- long_data_no_fmd %>% 
+  group_by(title) %>% 
+  distinct(sensitivity_analysis, .keep_all = TRUE) %>% 
+  ungroup()
+
+#Count the number of studies
+sensitivity_analysis_count <- sensitivity_analysis_unique_entries %>% 
+  count(model_structure, sensitivity_analysis, name = 'num_of_studies')
+
+#Print the table
+knitr::kable(sensitivity_analysis_count)
+
+```
+
+# Data use and availability
+
+```{r echo=FALSE}
+#Keep only the unique entries
+code_and_data_availability_count <- compact_data_no_fmd %>% 
+  count(data_used, data_available) %>% 
+  pivot_wider(names_from = data_available, values_from = n) %>% 
+  replace_na(list(not_applicable = 0, 
+                  yes = 0, 
+                  no = 0
+                  )
+             )
+
+#Print the results
+knitr::kable(code_and_data_availability_count, caption = 'Data use and availability')
+
+```
+# Code availability
+
+```{r echo=FALSE}
+#Keep only the unique entries
+code_availability_count <- compact_data_no_fmd %>% 
+  count(simulation_code_available)
+
+#Print the results
+knitr::kable(code_availability_count, caption = 'Code availability')
+
+```
+
+# Number of studies per disease 
+## By outbreak type
+
+```{r echo=FALSE}
+#count the number of unique diseases studied
+disease_studied_by_outbreak_type <- compact_data_no_fmd %>% 
+  separate_rows(disease,  sep = ' ') %>% 
+  mutate(disease = as_factor(disease), 
+         outbreak_type = as_factor(str_replace(outbreak_type, ' ', '+'))
+         ) %>% 
+  group_by(disease) %>% 
+  distinct(title, .keep_all = TRUE) %>% 
+  count(disease, outbreak_type, sort = TRUE) %>%
+  pivot_wider(names_from = outbreak_type, values_from = n) %>% 
+  replace_na(list(hypothetical_outbreak = 0, real_outbreak = 0)) %>% 
+  mutate(total = hypothetical_outbreak + real_outbreak) %>% 
+  arrange(desc(total))
+
+knitr::kable(disease_studied_by_outbreak_type)
+```
+
+## By objective type
+
+```{r echo=FALSE}
+#count the number of unique diseases studied
+disease_studied_by_objective_type <- compact_data_no_fmd %>% 
+  separate_rows(disease,  sep = ' ') %>% 
+  mutate(disease = as_factor(disease), 
+         objectives = as_factor(objectives)
+         ) %>% 
+  group_by(disease) %>% 
+  distinct(title, .keep_all = TRUE) %>% 
+  count(disease, objectives) %>%
+  pivot_wider(names_from = objectives, values_from = n) %>% 
+  replace_na(list(future = 0, past = 0, both = 0)) %>% 
+  mutate(total = future + past + both) %>% 
+  arrange(desc(total))
+
+knitr::kable(disease_studied_by_objective_type)
+```
+
+## FMD by collaboration type
+```{r echo=FALSE}
+fmd_studies_by_collab_type <- compact_data %>% 
+  filter(disease == 'fmd') %>% 
+  mutate(disease = as_factor(disease), 
+         author_affiliation_type = as_factor(str_replace(author_affiliation_type, ' ', '+'))
+         ) %>% 
+  mutate(collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
+                                         'purely_academic', 
+                                         'mixed')
+                                 )
+         ) %>% 
+  count(collab_type, sort = TRUE)
+
+knitr::kable(fmd_studies_by_collab_type)
+```
+## FMD by objective type
+```{r echo=FALSE}
+fmd_studies_by_objective_and_outbreak_type <- compact_data %>% 
+  filter(disease == 'fmd') %>% 
+  count(objectives, outbreak_type) %>% 
+  pivot_wider(names_from = outbreak_type, values_from = n)
+
+knitr::kable(fmd_studies_by_objective_and_outbreak_type)
+```
+
+# Secondary summaries
+## Studies before 2006 (low frequency period) 
+```{r echo=FALSE}
+#Number of studies before 2005 (low frequency period)
+n_studies_before_2006 <- compact_data_no_fmd %>% 
+  filter(publication_year < 2006) %>% 
+  summarise(n = n())
+
+print(paste('Number of studies before 2006:', n_studies_before_2006))
+```
+## Number of studies between 2006-2019 (high frequency period)
+```{r echo=FALSE}
+n_studies_btwn_2006_2019 <- compact_data_no_fmd %>% 
+  filter(publication_year >= 2006, publication_year <= 2019) %>% 
+  summarise(n = n())
+
+print(paste('Number of studies between 2006 and 2019:', n_studies_btwn_2006_2019))
+```
+
+## Locations studied and connection of authors to the location
+
+### Countries studied
+
+```{r}
+#Tally of how many times and percentage of times each COUNTRY has been studied
+# countries_studied_by_count <- long_data_no_fmd %>% 
+#     group_by(country_studied) %>%
+#     distinct(title) %>% 
+#     count(country_studied, name = 'num_of_studies', sort = T) %>% 
+#     ungroup(country_studied) %>% 
+#     mutate(country_studied = as_factor(country_studied), 
+#            percentage = round(num_of_studies/sum(num_of_studies)*100, 1)
+#            )
+
+countries_studied_by_count <- compact_data_with_citation_keys_no_fmd %>% 
+    separate_rows(country_studied, sep = ' ') %>%
+    distinct(title, country_studied, .keep_all = TRUE) %>% 
+    count(collab_type, country_studied, name = 'num_of_studies', sort = T)
+
+#'Modify the data frame to lump together all countries with less than some number of studies as 'other' and recalculate the percentage studied
+countries_studied_by_count_aggregated <- countries_studied_by_count %>% 
+  group_by(country_studied) %>%
+  summarise(num_of_studies = sum(num_of_studies),
+            .groups = 'drop'
+            ) %>% 
+  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
+  arrange(desc(num_of_studies)) %>% 
+  adorn_totals(where = c('row')) %>% 
+  adorn_percentages(denominator = 'col') %>% 
+  adorn_pct_formatting() %>% 
+  adorn_ns() %>% 
+  ungroup()
+
+#Print the results
+knitr::kable(countries_studied_by_count_aggregated, 
+             caption = 'Number of studies per country'
+             )
+```
+
+### Continents studied
+```{r echo=FALSE}
+continents_studied_by_count <- countries_studied_by_count %>% 
+  mutate(continent_studied = countrycode(country_studied, 
+                                          destination = 'continent',
+                                          origin = 'iso2c',
+                                          nomatch = NULL #if there is no match, keep the original
+                                          )
+         ) %>% 
+  mutate(continent_studied = str_to_lower(continent_studied)
+         ) %>% 
+  mutate(continent_studied = case_when(str_detect(continent_studied, 'asia') == T ~ 'asia', 
+                                         str_detect(continent_studied, 'africa') == T ~ 'africa', 
+                                         TRUE ~ continent_studied
+                                       )
+           ) %>% 
+  group_by(continent_studied) %>%
+  summarise(num_of_studies = sum(num_of_studies), 
+            percentage = sum(percentage),
+            .groups = 'drop'
+            ) %>% 
+  arrange(desc(percentage))
+```
+
+### Country most studied
+```{r echo=FALSE}
+countries_studied_most <- countries_studied_by_count %>%
+    filter(country_studied != 'none') %>%
+    filter(num_of_studies == max(num_of_studies))
+
+#Print the result as a table
+knitr::kable(countries_studied_most,
+             col.names = c('Country',
+                           'Number of studies',
+                           'Percentage'
+                           ),
+             caption = 'Most studied country'
+             )
+```
+
+### Continent most studied
+```{r echo=FALSE}
+
+continent_studied_most <- continents_studied_by_count %>%
+    dplyr::filter(continent_studied != 'none') %>%
+    filter(num_of_studies == max(num_of_studies))
+
+#Print the result as a table
+knitr::kable(continent_studied_most,
+             col.names = c('Continent',
+                           'Number of studies',
+                           'Percentage'
+                           ),
+             caption = 'Most studied continent'
+             )
+```
+
+## Number of studies per continent
+```{r echo=FALSE}
+continents_studied <- continents_studied_by_count %>%
+  filter(continent_studied != 'none') %>%
+  filter(continent_studied != 'global') %>%
+  filter(continent_studied != 'northern_hemisphere') %>%
+  group_by(continent_studied) %>%
+  summarise(num_of_studies = sum(num_of_studies )) %>%
+  ungroup() %>%
+  mutate(percentage = round(num_of_studies/sum(num_of_studies)*100, 1))
+
+#Print table of results
+knitr::kable(continents_studied_by_count %>% arrange(desc(percentage)),
+             col.names = c('Continent',
+                           'Number of papers',
+                           'Percentage'
+                           ),
+             caption = 'Number/percent of studies by continent'
+             )
+
+```
+
+```{r echo=FALSE, include=FALSE}
+# Load the cleaned data 
+long_data <- read_rds('../data/final_data/cleaned_data/review_data_long_cleaned.rds')
+
+#The cleaned data without citations
+compact_data_init <- read_rds('../data/final_data/cleaned_data/review_data_compact_cleaned.rds')
+
+compact_data <- compact_data_init %>% 
+    mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
+                               'yes', 
+                               'no')
+         ) %>% 
+  mutate(intervention_type = case_when(
+    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
+    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_alongside', #when vax was modelled but not for comparison as a single intervention
+    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
+  )) %>% 
+  mutate(publication_year = as.numeric(publication_year), 
+         author_in_country_studied = as.character(author_in_country_studied)) %>% 
+  arrange(publication_year) %>%
+  mutate(
+    author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + '),
+    author_in_country_studied = if_else(author_in_country_studied == 'NA', 'not_applicable',
+                                        author_in_country_studied
+                                        )
+    ) %>% 
+  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, #An approach to aggregate the years before 2006 into one group because of the low number of papers
+                                         2005, 
+                                         publication_year
+                                         )
+                                  ), 
+         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
+                                         'purely_academic', 
+                                         'mixed')
+                                 )
+         )
+
+# The data with citations 
+compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/final_data/cleaned_data/compact_data_with_citation_keys_cleaned.rds'))
+
+compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>% 
+    mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
+                               'yes', 
+                               'no')
+         ) %>% 
+  mutate(intervention_type = case_when(
+    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
+    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_alongside', #when vax was modelled but not for comparison as a single intervention
+    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
+  )) %>% 
+  mutate(publication_year = as.numeric(publication_year), 
+         author_in_country_studied = as.character(author_in_country_studied)) %>% 
+  arrange(publication_year) %>%
+  mutate(
+    author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + '),
+    author_in_country_studied = if_else(author_in_country_studied == 'NA', 'not_applicable',
+                                        author_in_country_studied
+                                        )
+    ) %>% 
+  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, #An approach to aggregate the years before 2006 into one group because of the low number of papers
+                                         2005, 
+                                         publication_year
+                                         )
+                                  ), 
+         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
+                                         'purely_academic', 
+                                         'mixed')
+                                 )
+         )
+
+# Remove the FMD papers (NB: We only use the FMD papers for comparison)
+long_data_no_fmd <- long_data %>% filter(disease != 'fmd')
+
+compact_data_no_fmd <- compact_data %>% filter(disease != 'fmd')
+
+compact_data_with_citation_keys_no_fmd <- compact_data_with_citation_keys %>% filter(disease != 'fmd') 
+```
+
+### Interventions types (FMD)
+
+```{r echo=FALSE}
+intervention_categories_fmd <- compact_data %>% 
+  filter(disease == 'fmd') %>% 
+  group_by(intervention_type, vax_modelled_with_non_vax) %>% 
+  count(is_vax_effective, sort = TRUE) %>% 
+  filter(vax_modelled_with_non_vax == 'yes') %>% 
+  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
+  adorn_totals(where = 'col')
+
+knitr::kable(intervention_categories_fmd)
+```
+
+## Vaccine impact categories (FMD)
+```{r echo=FALSE}
+vax_impact_categories_fmd <- compact_data %>%
+  filter(disease == 'fmd') %>% 
+  filter(vax_modelled_with_non_vax == 'yes') %>% 
+  count(is_vax_effective, 
+        name = 'num_of_studies', 
+        sort = T
+        )
+
+#Print the results
+knitr::kable(vax_impact_categories_fmd %>% adorn_totals, 
+             col.names = c('Vaccination is most impactful', 
+                           'Number of studies'
+                           ),
+             caption = 'Studies\' conclusions about impact of vaccination (FMD)'
+             )
+```
+
+# Citation tables
+
+## Code availability
+```{r echo=FALSE}
+
+code_availability_citations <- compact_data_with_citation_keys %>% 
+  filter(simulation_code_available == 'yes')
+
+knitr::kable(code_availability_citations)
+```
+
+## Citation table for human diseases
+```{r echo=FALSE}
+vax_impact_categories_citations_no_fmd <- compact_data_with_citation_keys %>% 
+  filter(disease != 'fmd') %>% 
+  filter(vax_modelled_with_non_vax == 'yes') %>% 
+  select(title, publication_year, disease, objectives, is_vax_effective, bibtexkey) %>% 
+  arrange(is_vax_effective)
+
+#Print the results
+knitr::kable(vax_impact_categories_citations_no_fmd,
+             caption = 'Studies\' conclusions about impact of vaccination (citations for human diseases)'
+             )
+```
+
+## Citation table for FMD
+```{r echo=FALSE}
+vax_impact_categories_citations_fmd <- compact_data_with_citation_keys %>% 
+  filter(disease == 'fmd') %>% 
+  filter(vax_modelled_with_non_vax == 'yes') %>% 
+  select(title, publication_year, disease, objectives, is_vax_effective, bibtexkey) %>% 
+  arrange(is_vax_effective)
+
+#Print the results
+knitr::kable(vax_impact_categories_citations_fmd,
+             caption = 'Studies\' conclusions about impact of vaccination (citations for human diseases)'
+             )
+
+```
+
+# Exploration of the peak periods (2009-2011, 2015-2016, 2019)
+
+## Citations of studies during 2009-2011
+```{r echo=FALSE}
+#Citation table of studies during 2009-2011 (Peak period)
+studies_in_2009_2011_df <- compact_data_with_citation_keys_no_fmd %>%
+  separate_rows(disease, sep = ' ') %>% 
+  filter(publication_year >= 2009, publication_year <= 2011) %>%
+  arrange(disease) %>%
+  select(title, publication_year, disease, objectives, bibtexkey) %>% 
+  mutate(disease = str_replace(disease, ' ', ' and '))
+
+knitr::kable(studies_in_2009_2011_df, caption = 'Studies published during 2009-2011 (Peak period)')
+```
+### Number of studies during 2009-2011 per disease and objective type (Peak period)
+```{r echo=FALSE}
+n_studies_2009_2011_df <- studies_in_2009_2011_df %>%
+  count(disease, objectives) %>% 
+  arrange(disease, n) %>% 
+  pivot_wider(names_from = objectives, values_from = n) %>% 
+  replace_na(list(both = 0, future = 0, past = 0))
+
+knitr::kable(n_studies_2009_2011_df, caption = 'Studies published during 2009-2011 (Peak period)')
+```
+
+## Citation table of studies during 2015-2016 per disease and objective type (Peak period)
+```{r echo=FALSE}
+studies_between_2015_2016_df <- compact_data_with_citation_keys_no_fmd %>%
+  separate_rows(disease, sep = ' ') %>% 
+  filter(publication_year >= 2015, publication_year <= 2016) %>%
+  arrange(disease, publication_year) %>%
+  select(title, publication_year, disease, objectives, bibtexkey) %>% 
+  mutate(disease = str_replace(disease, ' ', ' and '))
+
+knitr::kable(studies_between_2015_2016_df, caption = 'Studies published in 2015-2016 (Peak period)')
+```
+
+### Number of studies from 2015-2016 per disease and objective type (Peak period)
+```{r echo=FALSE}
+n_studies_between_2015_2016_df <- studies_between_2015_2016_df %>% 
+  count(disease, objectives) %>% 
+  arrange(desc(n))  %>% 
+  pivot_wider(names_from = objectives, values_from = n) %>% 
+  replace_na(list(both = 0, future = 0, past = 0))
+
+knitr::kable(n_studies_between_2015_2016_df, caption = 'Papers published in 2015-2016 (Peak period)')
+```
+
+## Citation table of studies in 2019 (Peak period)
+```{r echo=FALSE}
+studies_in_2019_df <- compact_data_with_citation_keys_no_fmd %>%
+  filter(publication_year == 2019) %>%
+  arrange(disease) %>%
+  select(title, publication_year, disease, objectives, bibtexkey) %>% 
+  mutate(disease = str_replace(disease, ' ', ' and '))
+
+knitr::kable(studies_in_2019_df, caption = 'Studies published in 2019 (Peak year)')
+```
+### Number of studies in 2019 per disease and objective type (Peak period)
+```{r echo=FALSE}
+n_studies_in_2019_df <- studies_in_2019_df %>% 
+  count(disease, objectives) %>% 
+  arrange(n)
+
+knitr::kable(n_studies_in_2019_df, caption = 'Number of studies published in 2019 per disease and objective type (Peak year)')
+```
+
+### Total number of studies in 2019 (Peak period)
+```{r echo=FALSE}
+n_studies_in_2019 <- n_studies_in_2019_df %>%  
+  summarise(n = n())
+
+print(paste('Number of studies in 2019 (Peak year):', 
+            n_studies_in_2019
+            )
+      )
+```
+
+## Number of diseases in the peak periods
+```{r echo=FALSE}
+peak_period_df <- bind_rows(studies_in_2009_2011_df, 
+                            studies_between_2015_2016_df, 
+                            studies_in_2019_df
+                            ) %>% 
+  arrange(disease, publication_year)
+
+knitr::kable(peak_period_df , 
+             caption = 'Studies published in peak period'
+             )
+```
+
+```{r echo=FALSE}
+n_studies_by_disease_and_objectives_peak_periods <- peak_period_df %>% 
+  count(disease, objectives)
+
+knitr::kable(n_studies_by_disease_and_objectives_peak_periods, 
+             caption = 'Number of studies per disease and objective in peak periods'
+             )
+```
+
+```{r echo=FALSE}
+total_studies_by_disease_peak_period_df <- peak_period_df %>% 
+  count(disease) %>% 
+  arrange(n)
+
+knitr::kable(total_studies_by_disease_peak_period_df, 
+             caption = 'Number of studies per disease in peak periods'
+             )
+```
+
+## Influenza during 2009 - 2011 peaks
+```{r echo=FALSE}
+n_Influenza_studies_by_objectives_2009_2011 <- peak_period_df %>% 
+  filter(publication_year >= 2009, publication_year <= 2011) %>%
+  filter(disease == 'influenza') %>% 
+  count(objectives)
+
+knitr::kable(n_Influenza_studies_by_objectives_2009_2011, 
+             caption = 'Number of Influenza studies per objective type (2009 & 2011)'
+             )
+```
+## Ebola in 2015-2016
+```{r echo=FALSE}
+n_ebola_studies_by_objectives_2015_2016 <- studies_between_2015_2016_df %>% 
+  filter(disease == 'ebola') %>% 
+  count(objectives)
+
+knitr::kable(n_ebola_studies_by_objectives_2015_2016, 
+             caption = 'Number of Ebola studies per objective type (2015-2016)'
+             )
+```
+### Studies that used both retrospective and prospective assessments in peak periods
+```{r echo=FALSE}
+knitr::kable(peak_period_df %>% filter(objectives == 'both'), 
+             caption = 'Studies with retrospective and prospective assessments'
+             )
+
+```
+
+# Miscellaneous Analyses
+
+```{r echo=FALSE}
+disease_studied_count <- long_data_no_fmd %>% 
+  group_by(disease) %>% 
+  distinct(title) %>% 
+  count(disease, name = 'num_of_studies', sort = T) %>%
+  ungroup()
+
+knitr::kable(disease_studied_count, col.names = c('Disease', 'Number of studies'))
+```
+
+### Disease most studied
+```{r echo=FALSE}
+disease_studied_most <- disease_studied_count %>% 
+  filter(num_of_studies == max(num_of_studies))
+
+knitr::kable(disease_studied_most)
+```
+
+### Number of studies per collaboration type
 
@@
         name = 'total_publications'
+        ) %>% 
+  pivot_wider(names_from = collab_type, values_from = total_publications)
+
+knitr::kable(collap_types_by_year %>% clean_names() %>% adorn_totals(... = c(mixed, purely_academic)))
+
+```
+
+### Academic collaborations versus other non-academic collaborations (excluding purely academic collaborations).
+
+```{r echo=FALSE}
+academic_collabs_versus_others <- compact_data_no_fmd %>% 
+  filter(author_affiliation_type != 'academic_institutions') %>% 
+  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 2005, publication_year
+                                         )
+                                  ), 
+         collab_type = as_factor(if_else(str_detect(author_affiliation_type, 'academic_institutions'), 
+                                         'Academic', 
+                                         'Other'
+                                         )
+                                 )
+         ) %>% 
+  count(year_aggreg, 
+        collab_type, 
+        name = 'total_publications'
         )
@@
 x_axis_labels[1] <- '1970-2005'
-
-collab_type_by_year_plot <- ggplot(data = collap_types_by_year) + 
-  geom_bar(aes(x = year_aggreg,
-               y = total_publications,
-               fill = collab_type
-               ),
-           color = 'black',
-           stat = 'identity',
-           position = position_fill(reverse = TRUE)  
-             ) +
-  scale_fill_manual(values = c('tan1', 'turquoise1')) +
-  scale_x_continuous(breaks = seq(2005, 2020, 2),
-                     labels = x_axis_labels
-                     ) +
-  labs(title = 'Publications per collaboration type over time',
-       x = 'Year',
-       y = 'Proportion of total publications in the year',
-       fill = 'Collaboration type' 
-         ) +
-  theme_minimal(base_size = 12)
-
-plot(collab_type_by_year_plot)
-
-```
-### IV. Number of studies by collaboration type (purely academic versus mixed).
-
-```{r echo=FALSE}
-#' Count the number of each author affiliation type per year (including FMD)
-collap_types_by_year <- compact_data_no_fmd %>% 
-  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 
-                                         2005, 
-                                         publication_year
-                                         )
-                                  ), 
-         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
-                                         'Purely academic', 
-                                         'Mixed')
-                                 )
-         ) %>% 
-  count(year_aggreg, 
-        collab_type, 
-        name = 'total_publications'
-        ) %>% 
-  pivot_wider(names_from = collab_type, values_from = total_publications)
-
-knitr::kable(collap_types_by_year %>% clean_names() %>% adorn_totals(... = c(mixed, purely_academic)))
-
-```
-
-```{r echo=FALSE}
-#' Count the number of each author affiliation type per year
-collap_types_by_year <- compact_data_no_fmd %>% 
-  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 
-                                         2005, 
-                                         publication_year
-                                         )
-                                  ), 
-         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
-                                         'Purely academic', 
-                                         'Mixed')
-                                 )
-         ) %>% 
-  count(year_aggreg, 
-        collab_type, 
-        name = 'total_publications'
-        )
-
-collap_types_by_year_plot <- ggplot(data = collap_types_by_year, 
-                                    aes(x = year_aggreg, 
-                                        y = total_publications
-                                        ), 
-                                    color = 'black') + 
-  geom_bar(aes(fill = collab_type), 
-           stat = 'identity', 
-           position = 'dodge'
-           ) +
-  labs(x = 'Year', y = 'Total publications')
-
-plot(collap_types_by_year_plot)
-
-```
-
-Even though non-academic collaborations increased over time, the share of total publications per year over time decreased.
-
-### V. Academic collaborations versus other non-academic collaborations (excluding purely academic collaborations).
-
-```{r echo=FALSE}
-
-academic_collabs_versus_others <- compact_data_no_fmd %>% 
-  filter(author_affiliation_type != 'academic_institutions') %>% 
-  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 2005, publication_year
-                                         )
-                                  ), 
-         collab_type = as_factor(if_else(str_detect(author_affiliation_type, 'academic_institutions'), 
-                                         'Academic', 
-                                         'Other'
-                                         )
-                                 )
-         ) %>% 
-  count(year_aggreg, 
-        collab_type, 
-        name = 'total_publications'
-        )
 
@@
 
-# B. How often are papers authored by locals?
+# Connection of authors to the studied locations 
 ```{r}
-author_location_count_by_disease_wide <- compact_data_no_fmd %>%
+author_location_count_by_disease <- compact_data_no_fmd %>%
   separate_rows(disease, sep = ' ') %>% 
@@
          ) %>% 
-  group_by(disease) %>%
+  group_by(collab_type, disease) %>%
   distinct(title, .keep_all = TRUE) %>% 
-  count(author_in_country_studied) %>% 
+  count(author_in_country_studied, sort = TRUE) %>% 
+  complete(author_in_country_studied, fill = list(n = 0)) %>% 
   pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
@@
   mutate(total = not_applicable + no + yes) %>% 
+  ungroup(collab_type) %>% 
   arrange(desc(total))
 
-knitr::kable(author_location_count_by_disease_wide)
-```
-
-```{r}
-author_location_count_by_disease_long <- author_location_count_by_disease_wide %>% 
-  select(-c(not_applicable, total)) %>% 
-  pivot_longer(cols = c(yes, no), 
-               names_to = 'author_in_country_studied',
-               values_to = 'n'
-               )
-
-author_location_count_by_disease_plot <- ggplot(data = author_location_count_by_disease_long, 
-       aes(x = reorder(disease, n), 
-           y = n
-           )
-       ) + geom_bar(aes(fill = author_in_country_studied),
-                    stat = 'identity',
-                    position = position_fill(reverse = TRUE)
-                    ) +
-  labs(x = 'Disease', y = 'Proportion of total studies') +
-  coord_flip()
-
-plot(author_location_count_by_disease_plot)
-```
-
-# 2. Is vaccination always the most impactful single intervention?
-
-## Classification of interventions by inclusion/exclusion of vaccination
-
-### Human diseases
-```{r echo=FALSE}
-intervention_categories_human_diseases <- compact_data_no_fmd %>% 
-  group_by(intervention_type, vax_modelled_with_non_vax) %>% 
-  count(is_vax_effective, sort = TRUE) %>% 
-  pivot_wider(names_from = vax_modelled_with_non_vax, values_from = n) %>% 
-  replace_na(list(no = 0, yes = 0))
-
-knitr::kable(intervention_categories_human_diseases)
-```
-### FMD
-
-```{r echo=FALSE}
-intervention_categories_fmd <- compact_data %>% 
-  filter(disease == 'fmd') %>% 
-  group_by(intervention_type, vax_modelled_with_non_vax) %>% 
-  count(is_vax_effective, sort = TRUE) %>% 
-  filter(vax_modelled_with_non_vax == 'yes') %>% 
-  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
-  adorn_totals(where = 'col')
-
-knitr::kable(intervention_categories_fmd)
-```
-
-## Classification of interventions by inclusion of vaccination 
-```{r echo=FALSE}
-study_categories_by_vax_single <- intervention_categories_human_diseases %>% 
-  filter(intervention_type == 'vax_single')
-
-knitr::kable(study_categories_by_vax_single)
-```
-
-## Citation table of studies that modelled vaccination as a single intervention
-```{r echo=FALSE}
-intervention_categories_citation_tbl <- compact_data_with_citation_keys_no_fmd %>%
-  filter(intervention_type == 'vax_single') %>% 
-  select(title, publication_year, bibtexkey, disease, intervention_modelled, vax_modelled, vax_modelled_with_non_vax, is_vax_effective)
-
-knitr::kable(intervention_categories_citation_tbl %>% arrange(is_vax_effective
-, disease))
-
-```
-
-# Is vaccination the most effective when compared to other single interventions?
-
-## Vaccine impact categories (human diseases)
-```{r echo=FALSE}
-vax_impact_categories_no_fmd <- compact_data_no_fmd %>% 
-  filter(vax_modelled_with_non_vax == 'yes') %>% 
-  count(is_vax_effective, 
-        name = 'num_of_studies', 
-        sort = T
-        )
-
-#Print the results
-knitr::kable(vax_impact_categories_no_fmd %>% adorn_totals, 
-             col.names = c('Vaccination is most impactful', 
-                           'Number of studies'
-                           ),
-             caption = 'Studies\' conclusions about impact of vaccination (Human diseases)'
-             )
-```
-
-## Vaccine impact categories (FMD)
-```{r echo=FALSE}
-vax_impact_categories_fmd <- compact_data %>%
-  filter(disease == 'fmd') %>% 
-  filter(vax_modelled_with_non_vax == 'yes') %>% 
-  count(is_vax_effective, 
-        name = 'num_of_studies', 
-        sort = T
-        )
-
-#Print the results
-knitr::kable(vax_impact_categories_fmd %>% adorn_totals, 
-             col.names = c('Vaccination is most impactful', 
-                           'Number of studies'
-                           ),
-             caption = 'Studies\' conclusions about impact of vaccination (FMD)'
-             )
-```
-
-## Citation table for human diseases
-```{r echo=FALSE}
-vax_impact_categories_citations_no_fmd <- compact_data_with_citation_keys %>% 
-  filter(disease != 'fmd') %>% 
-  filter(vax_modelled_with_non_vax == 'yes') %>% 
-  select(title, publication_year, disease, objectives, is_vax_effective, bibtexkey) %>% 
-  arrange(is_vax_effective)
-
-#Print the results
-knitr::kable(vax_impact_categories_citations_no_fmd,
-             caption = 'Studies\' conclusions about impact of vaccination (citations for human diseases)'
-             )
-```
-
-## Citation table for FMD
-```{r echo=FALSE}
-vax_impact_categories_citations_fmd <- compact_data_with_citation_keys %>% 
-  filter(disease == 'fmd') %>% 
-  filter(vax_modelled_with_non_vax == 'yes') %>% 
-  select(title, publication_year, disease, objectives, is_vax_effective, bibtexkey) %>% 
-  arrange(is_vax_effective)
-
-#Print the results
-knitr::kable(vax_impact_categories_citations_fmd,
-             caption = 'Studies\' conclusions about impact of vaccination (citations for human diseases)'
-             )
-
-```
-
-```{r echo=FALSE, eval=FALSE}
-vax_impact_plot <- ggplot(data = vax_impact_categories) + 
-  geom_bar(
-    aes(x = is_vax_effective, 
-        y = n,
-        fill = is_vax_effective
-        ),
-    stat = 'identity',
-    width = 0.25
-    ) +
-  scale_y_continuous(breaks = seq(0, 
-                                  max(vax_impact_categories$n),
-                                  2
-                                  ),
-                     labels = seq(0, 
-                                max(vax_impact_categories$n),
-                                2
-                                )
-                     ) +
-  scale_x_discrete(breaks = c('no', 
-                              'yes', 
-                              'the_outcomes_were_inconclusive'
-                              ), 
-                   labels = c('no' = 'No', 
-                              'yes' = 'Yes', 
-                              'the_outcomes_were_inconclusive' = 'Inconclusive'
-                              )
-                   ) +
-  scale_fill_discrete(name = 'Vaccine impact',
-                      labels = c('No', 
-                                 'Inconclusive',
-                                 'Yes'
-                      )
-                      ) +
-  labs(x = 'Vaccination is most impactful single intervention',
-       y = 'Number of studies'
-       ) +
-  theme_minimal(base_size = 12)
-
-plot(vax_impact_plot)
-
-```
-
-# Number of studies per disease
-
-## By collaboration type
-
-```{r echo=FALSE}
-#count the number of unique diseases studied
-disease_studied_by_collab_type <- compact_data_no_fmd %>% 
-  separate_rows(disease,  sep = ' ') %>% 
-  mutate(disease = as_factor(disease), 
-         author_affiliation_type = as_factor(str_replace(author_affiliation_type, ' ', '+'))
-         ) %>% 
-    mutate(collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
-                                         'purely_academic', 
-                                         'mixed')
-                                 )
-         ) %>% 
-  group_by(disease) %>% 
-  distinct(title, .keep_all = TRUE) %>% 
-  count(disease, collab_type, sort = TRUE) %>%
-  pivot_wider(names_from = collab_type, values_from = n) %>% 
-  replace_na(list(purely_academic = 0, mixed = 0)) %>% 
-  mutate(total = purely_academic + mixed) %>% 
-  arrange(desc(total))
-
-knitr::kable(disease_studied_by_collab_type)
-```
-
-## By outbreak type
-
-```{r echo=FALSE}
-#count the number of unique diseases studied
-disease_studied_by_outbreak_type <- compact_data_no_fmd %>% 
-  separate_rows(disease,  sep = ' ') %>% 
-  mutate(disease = as_factor(disease), 
-         outbreak_type = as_factor(str_replace(outbreak_type, ' ', '+'))
-         ) %>% 
-  group_by(disease) %>% 
-  distinct(title, .keep_all = TRUE) %>% 
-  count(disease, outbreak_type, sort = TRUE) %>%
-  pivot_wider(names_from = outbreak_type, values_from = n) %>% 
-  replace_na(list(hypothetical_outbreak = 0, real_outbreak = 0)) %>% 
-  mutate(total = hypothetical_outbreak + real_outbreak) %>% 
-  arrange(desc(total))
-
-knitr::kable(disease_studied_by_outbreak_type)
-```
-
-## By objective type
-
-```{r echo=FALSE}
-#count the number of unique diseases studied
-disease_studied_by_objective_type <- compact_data_no_fmd %>% 
-  separate_rows(disease,  sep = ' ') %>% 
-  mutate(disease = as_factor(disease), 
-         objectives = as_factor(objectives)
-         ) %>% 
-  group_by(disease) %>% 
-  distinct(title, .keep_all = TRUE) %>% 
-  count(disease, objectives) %>%
-  pivot_wider(names_from = objectives, values_from = n) %>% 
-  replace_na(list(future = 0, past = 0, both = 0)) %>% 
-  mutate(total = future + past + both) %>% 
-  arrange(desc(total))
-
-knitr::kable(disease_studied_by_objective_type)
-```
-
-## FMD by collaboration type
-```{r echo=FALSE}
-fmd_studies_by_collab_type <- compact_data %>% 
-  filter(disease == 'fmd') %>% 
-  mutate(disease = as_factor(disease), 
-         author_affiliation_type = as_factor(str_replace(author_affiliation_type, ' ', '+'))
-         ) %>% 
-  mutate(collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
-                                         'purely_academic', 
-                                         'mixed')
-                                 )
-         ) %>% 
-  count(collab_type, sort = TRUE)
-
-knitr::kable(fmd_studies_by_collab_type)
-```
-## FMD by objective type
-```{r echo=FALSE}
-fmd_studies_by_objective_and_outbreak_type <- compact_data %>% 
-  filter(disease == 'fmd') %>% 
-  count(objectives, outbreak_type) %>% 
-  pivot_wider(names_from = outbreak_type, values_from = n)
-
-knitr::kable(fmd_studies_by_objective_and_outbreak_type)
-```
-
-# Number of studies per disease and intervention.
-
-```{r echo=FALSE}
-#count the number of unique interventions modelled
-interventions_unique_entries <- long_data_no_fmd %>% 
-  group_by(title) %>% 
-  distinct(intervention_modelled, .keep_all = TRUE) %>% 
-  ungroup()
-
-#interventions are disease specific
-interventions_per_disease <- interventions_unique_entries %>% 
-  mutate(intervention_modelled = str_trim(intervention_modelled)) %>% 
-  filter(intervention_modelled != 'e.g.') %>% #remove false rows
-  filter(intervention_modelled != 'various') %>% #remove false rows
-  group_by(disease) %>% 
-  count(intervention_modelled, name = 'num_of_studies') %>% 
-  arrange(disease, desc(num_of_studies)) %>% 
-  ungroup()
-
-knitr::kable(interventions_per_disease)
-
-```
-
-# Number of studies per outcome
-
-```{r echo=FALSE}
-#count the number of unique outcomes measured
-outcomes_unique_entries <- long_data_no_fmd %>% 
-  group_by(title) %>% 
-  distinct(outcome_measured, .keep_all = TRUE) %>% 
-  ungroup()
-
-#Count the number of studies 
-outcomes_count <- outcomes_unique_entries %>% 
-  group_by(outcome_measured) %>% 
-  count(outcome_measured, name = 'num_of_studies', sort = T) %>% 
-  ungroup() %>% 
-  filter(outcome_measured != 's')
-
-knitr::kable(outcomes_count)
-
-#Plot the result
-outcome_count_plot <- ggplot(data = outcomes_count) + 
-  geom_point(aes(x = reorder(outcome_measured, 
-                             num_of_studies), 
-               y = num_of_studies
-               ), 
-           stat = 'identity',
-           color = 'darkslategray4'
-           ) +
-  coord_flip() +
-  theme_minimal()
-
-plot(outcome_count_plot)
-
-```
-
-# Number of studies per model structure type
-
-```{r echo=FALSE}
-#Keep only the unique entries 
-model_structure_unique_entries <- long_data_no_fmd %>% 
-  group_by(title) %>% 
-  distinct(model_structure) %>% 
-  ungroup()
-
-#Count the number of studies
-model_structure_unique_count <- model_structure_unique_entries %>%
-    group_by(model_structure) %>% 
-    count(model_structure, name = 'num_of_studies')
-
-#Print the table
-knitr::kable(model_structure_unique_count)
-```
-
-# Number of studies by the model structure, parametrization, and validation types
-
-```{r echo=FALSE}
-#Cross tally the model structure with parametrization and validation categories
-#FIXME: Check that studies are either not being under counted or double-counted.
-What do I want to count here?
-Is it the unique studies per method or combined method because most studies used a combination of parametrization methods especially
-parametrization_and_validation_by_model_structure <- compact_data_no_fmd %>%
-  mutate(parametrization = str_replace(parametrization, ' ', ' + '),
-         validation = str_replace(validation, ' ', ' + ')
-         ) %>% 
-  count(model_structure, parametrization, validation) %>% 
-  pivot_wider(names_from = model_structure, values_from = n)
-
-#Print the table of results
-knitr::kable(parametrization_and_validation_by_model_structure,
-             caption = 'Parametrization and validation types per model structure')
-
-```
-
-# Model parametrization & validation
-
-```{r echo=FALSE}
-#Keep only the unique entries
-parametrization_and_validation_count <- compact_data_no_fmd %>% 
-  mutate(parametrization = str_replace(parametrization, ' ', ' + '), 
-         validation = str_replace(validation, ' ', ' + ')
-         ) %>% 
-  count(parametrization, 
-        validation, 
-        name = 'num_of_studies'
-        ) %>% 
-  group_by(parametrization) %>% 
-  arrange(desc(num_of_studies), .by_group = T)
-
-#Print the table
-knitr::kable(parametrization_and_validation_count)
-
-```
-
-# How is sensitivity analysis distributed by model structure?
-
-```{r echo=FALSE}
-#Keep only the unique entries
-sensitivity_analysis_unique_entries <- long_data_no_fmd %>% 
-  group_by(title) %>% 
-  distinct(sensitivity_analysis, .keep_all = TRUE) %>% 
-  ungroup()
-
-#Count the number of studies
-sensitivity_analysis_count <- sensitivity_analysis_unique_entries %>% 
-  count(model_structure, sensitivity_analysis, name = 'num_of_studies')
-
-#Print the table
-knitr::kable(sensitivity_analysis_count)
-
-```
-
-# Data use and availability
-
-```{r echo=FALSE}
-#Keep only the unique entries
-code_and_data_availability_count <- compact_data_no_fmd %>% 
-  count(data_used, data_available) %>% 
-  pivot_wider(names_from = data_available, values_from = n) %>% 
-  replace_na(list(not_applicable = 0, 
-                  yes = 0, 
-                  no = 0
-                  )
-             )
-
-#Print the results
-knitr::kable(code_and_data_availability_count, caption = 'Data use and availability')
-
-```
-# Code availability
-
-```{r echo=FALSE}
-#Keep only the unique entries
-code_availability_count <- compact_data_no_fmd %>% 
-  count(simulation_code_available)
-
-#Print the results
-knitr::kable(code_availability_count, caption = 'Code availability')
-
-```
-
-# Secondary summaries
-## Studies before 2006 (low frequency period) 
-```{r echo=FALSE}
-#Number of studies before 2005 (low frequency period)
-n_studies_before_2006 <- compact_data_no_fmd %>% 
-  filter(publication_year < 2006) %>% 
-  summarise(n = n())
-
-print(paste('Number of studies before 2006:', n_studies_before_2006))
-```
-## Number of studies between 2006-2019 (high frequency period)
-```{r echo=FALSE}
-n_studies_btwn_2006_2019 <- compact_data_no_fmd %>% 
-  filter(publication_year >= 2006, publication_year <= 2019) %>% 
-  summarise(n = n())
-
-print(paste('Number of studies between 2006 and 2019:', n_studies_btwn_2006_2019))
-```
-
-# Exploration of the peak periods (2009-2011, 2015-2016, 2019)
-
-## Citations of studies during 2009-2011
-```{r echo=FALSE}
-#Citation table of studies during 2009-2011 (Peak period)
-studies_in_2009_2011_df <- compact_data_with_citation_keys_no_fmd %>%
-  separate_rows(disease, sep = ' ') %>% 
-  filter(publication_year >= 2009, publication_year <= 2011) %>%
-  arrange(disease) %>%
-  select(title, publication_year, disease, objectives, bibtexkey) %>% 
-  mutate(disease = str_replace(disease, ' ', ' and '))
-
-knitr::kable(studies_in_2009_2011_df, caption = 'Studies published during 2009-2011 (Peak period)')
-```
-### Number of studies during 2009-2011 per disease and objective type (Peak period)
-```{r echo=FALSE}
-n_studies_2009_2011_df <- studies_in_2009_2011_df %>%
-  count(disease, objectives) %>% 
-  arrange(disease, n) %>% 
-  pivot_wider(names_from = objectives, values_from = n) %>% 
-  replace_na(list(both = 0, future = 0, past = 0))
-
-knitr::kable(n_studies_2009_2011_df, caption = 'Studies published during 2009-2011 (Peak period)')
-```
-
-## Citation table of studies during 2015-2016 per disease and objective type (Peak period)
-```{r echo=FALSE}
-studies_between_2015_2016_df <- compact_data_with_citation_keys_no_fmd %>%
-  separate_rows(disease, sep = ' ') %>% 
-  filter(publication_year >= 2015, publication_year <= 2016) %>%
-  arrange(disease, publication_year) %>%
-  select(title, publication_year, disease, objectives, bibtexkey) %>% 
-  mutate(disease = str_replace(disease, ' ', ' and '))
-
-knitr::kable(studies_between_2015_2016_df, caption = 'Studies published in 2015-2016 (Peak period)')
-```
-
-### Number of studies from 2015-2016 per disease and objective type (Peak period)
-```{r echo=FALSE}
-n_studies_between_2015_2016_df <- studies_between_2015_2016_df %>% 
-  count(disease, objectives) %>% 
-  arrange(desc(n))  %>% 
-  pivot_wider(names_from = objectives, values_from = n) %>% 
-  replace_na(list(both = 0, future = 0, past = 0))
-
-knitr::kable(n_studies_between_2015_2016_df, caption = 'Papers published in 2015-2016 (Peak period)')
-```
-
-## Citation table of studies in 2019 (Peak period)
-```{r echo=FALSE}
-studies_in_2019_df <- compact_data_with_citation_keys_no_fmd %>%
-  filter(publication_year == 2019) %>%
-  arrange(disease) %>%
-  select(title, publication_year, disease, objectives, bibtexkey) %>% 
-  mutate(disease = str_replace(disease, ' ', ' and '))
-
-knitr::kable(studies_in_2019_df, caption = 'Studies published in 2019 (Peak year)')
-```
-### Number of studies in 2019 per disease and objective type (Peak period)
-```{r echo=FALSE}
-n_studies_in_2019_df <- studies_in_2019_df %>% 
-  count(disease, objectives) %>% 
-  arrange(n)
-
-knitr::kable(n_studies_in_2019_df, caption = 'Number of studies published in 2019 per disease and objective type (Peak year)')
-```
-
-### Total number of studies in 2019 (Peak period)
-```{r echo=FALSE}
-n_studies_in_2019 <- n_studies_in_2019_df %>%  
-  summarise(n = n())
-
-print(paste('Number of studies in 2019 (Peak year):', 
-            n_studies_in_2019
-            )
-      )
-```
-
-## Number of diseases in the peak periods
-```{r echo=FALSE}
-peak_period_df <- bind_rows(studies_in_2009_2011_df, 
-                            studies_between_2015_2016_df, 
-                            studies_in_2019_df
-                            ) %>% 
-  arrange(disease, publication_year)
-
-knitr::kable(peak_period_df , 
-             caption = 'Studies published in peak period'
-             )
-```
-
-```{r echo=FALSE}
-n_studies_by_disease_and_objectives_peak_periods <- peak_period_df %>% 
-  count(disease, objectives)
-
-knitr::kable(n_studies_by_disease_and_objectives_peak_periods, 
-             caption = 'Number of studies per disease and objective in peak periods'
-             )
-```
-
-```{r echo=FALSE}
-total_studies_by_disease_peak_period_df <- peak_period_df %>% 
-  count(disease) %>% 
-  arrange(n)
-
-knitr::kable(total_studies_by_disease_peak_period_df, 
-             caption = 'Number of studies per disease in peak periods'
-             )
-```
-
-## Influenza during 2009 - 2011 peaks
-```{r echo=FALSE}
-n_Influenza_studies_by_objectives_2009_2011 <- peak_period_df %>% 
-  filter(publication_year >= 2009, publication_year <= 2011) %>%
-  filter(disease == 'influenza') %>% 
-  count(objectives)
-
-knitr::kable(n_Influenza_studies_by_objectives_2009_2011, 
-             caption = 'Number of Influenza studies per objective type (2009 & 2011)'
-             )
-```
-## Ebola in 2015-2016
-```{r echo=FALSE}
-n_ebola_studies_by_objectives_2015_2016 <- studies_between_2015_2016_df %>% 
-  filter(disease == 'ebola') %>% 
-  count(objectives)
-
-knitr::kable(n_ebola_studies_by_objectives_2015_2016, 
-             caption = 'Number of Ebola studies per objective type (2015-2016)'
-             )
-```
-### Studies that used both retrospective and prospective assessments in peak periods
-```{r echo=FALSE}
-knitr::kable(peak_period_df %>% filter(objectives == 'both'), 
-             caption = 'Studies with retrospective and prospective assessments'
-             )
-
-```
+knitr::kable(author_location_count_by_disease)
+```

### 2023-03-02 analyses/scripts/orv_models_review_data_cleaning.R

@@ -1,0 +1,195 @@
+#library('sjmisc')
+library('tidyverse')
+library('ggthemes')
+library('scales')
+library('janitor')
+library('forcats')
+library('stringr')
+library('bib2df')
+library('xlsx')
+
+#Check if the folder for saving the cleaned files exists, if not, create a folder
+if(!dir.exists('./data/final_data/cleaned_data'))
+    {
+    dir.create('./data/final_data/cleaned_data', 
+               showWarnings = FALSE)
+    }
+
+#load the review data extraction results and remove extraneous variables 
+review_data_compact <- read_delim('./data/final_data/raw_data/orv_review_compact_data.csv', 
+                                          delim = ';', 
+                                          na = c('', 'NA')
+                                          )
+
+#load the citation data for merging
+citation_data <- bib2df('./data/final_data/raw_data/included_studies.bib', 
+                        separate_names = FALSE
+                        ) %>% 
+    mutate(year = as.numeric(YEAR))
+
+############################################
+#Data cleaning
+############################################
+
+
+
+
+#Step 1
+#' Remove extraneous variables and clean the column names
+#' the compact data is the same as above except that there are multiple entries per cell;
+#' because that is how KoboToolbox saves multiple answer questions
+review_data_compact_cleaning_step1 <- review_data_compact %>% 
+    filter(publication_year < 2020) %>% #remove 2020 because the search was done in Jan 2020 so it gives the illusion that there were few papers in 2020.
+   # select(-'_index') %>% 
+    clean_names() %>% 
+    remove_empty('cols')
+
+#' Step 2
+#' Rename/shorten the entries and "merge" the entries in "other" and "multiple" columns into the "main" column
+review_data_compact_cleaning_step2 <- review_data_compact_cleaning_step1 %>% 
+    mutate(title = str_to_lower(paper_title), 
+           disease = str_to_lower(disease), 
+           objectives = case_when(objectives == 'assess_impact_future' ~ 'future', 
+                                  objectives == 'assess_impact_past' ~ 'past', 
+                                  objectives == 'assess_impact_past assess_impact_future' ~ 'both'
+                                  ),
+           author_in_country_studied = as_factor(if_else(is.na(author_in_country_studied), #if NA, change it to 'not_applicable' for easy analysis
+                                                         'not_applicable', 
+                                                         author_in_country_studied
+                                                         )
[…]

### 2023-03-02 epidemics_manuscript/outbreak_response_models_review_v2.tex
changed review title

--- 2023-03-02 Epidemics_submission/outbreak_response_models_review_v2.tex
@@
 {\Large
-\textbf\newline{Models and modelling practices for assessing the impact of outbreak response interventions to human vaccine-preventable diseases (1970-2019): A systematic review}
+\textbf\newline{Outbreak response interventions to human vaccine-preventable diseases: a systematic review of modelling practices before COVID-19}
 }

### 2023-03-15 analyses/scripts/full_data_extraction_citation_table.Rmd
updated the global chunk settings

@@
     keep_tex: yes
+  html_document:
+    df_print: paged
 ---
+```{r setup, include=FALSE}
+options(kableExtra.auto_format = FALSE)
 
-```{r echo=FALSE, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, 
+                      include = FALSE,
+                      dev = 'jpeg', 
+                      fig.width = 8, 
+                      fig.height = 6, 
+                      message = FALSE
+                      )
+```
+
+```{r}
 #' load packages
 library('tidyverse')
-library('readr')
-library('xlsx')
+# library('xlsx')
 library('scales')

### 2023-03-15 analyses/scripts/full_data_extraction_citation_table.Rmd
fixed the paths to the data

@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
-knitr::opts_chunk$set(dev = 'jpeg')
-knitr::opts_chunk$set(fig.width = 8, fig.height = 6)
-knitr::opts_chunk$set(message = FALSE)
-
+```{r}
 #create a folder for storing the manuscript figures
 
-if(!dir.exists('../figs_manuscript'))
-    {
-    dir.create('../figs_manuscript', 
-               showWarnings = FALSE)
+if (!dir.exists("../figs_manuscript")) {
+  dir.create("../figs_manuscript",
+    showWarnings = FALSE
+  )
 }
@@
 save_fig_here <- '../figs_manuscript'
-
-save_thesis_fig_here <- "C:/Users/JAMESAZAM/Dropbox/My Academic Repository/_SACEMA/Academic/_PhD/__PhD_Thesis/_Thesis_LaTeX/figs/chapter_3"
 ```
@@
 # Load the cleaned data 
-long_data <- read_rds('../data/final_data/cleaned_data/review_data_long_cleaned.rds')
+long_data <- read_rds('../data/review_data_long_cleaned.rds')
 
 #The cleaned data without citations
-compact_data_init <- read_rds('../data/final_data/cleaned_data/review_data_compact_cleaned.rds')
+compact_data_init <- read_rds('../data/review_data_compact_cleaned.rds')
+```
 
+```{r}
+# Data "cleaning"
 #a vector of shorter replacements for the original parametrization descriptions
@@
 # The data with citations 
-compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/final_data/cleaned_data/compact_data_with_citation_keys_cleaned.rds'))
+compact_data_with_citation_keys_init <- read_rds('../data/compact_data_with_citation_keys_cleaned.rds')
 

### 2023-03-15 analyses/scripts/full_data_extraction_citation_table.Rmd
removed explicit namespacing and turned off long table format

@@
 #columns 2-5 with paper titles
-knitr::kable(final_citation_table %>% 
+kable(final_citation_table %>% 
                  dplyr::select(1:5), 
-             format = "latex", booktabs = TRUE, 
-             longtable = TRUE#,
+             format = "latex", 
+             booktabs = TRUE, 
+             longtable = FALSE#,
              #caption = 'Extracted data per paper: publication_year, author_affiliation_type, country_studied, author_in_country_studied.'
@@
     kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
-    kableExtra::column_spec(column = c(1, 3), width = "5cm") %>% 
-    kableExtra::landscape()
+    column_spec(column = c(1, 3), width = "5cm") %>%
+    landscape()
 ```
@@
 #columns 6-10 with paper titles
-knitr::kable(final_citation_table %>% 
+kable(final_citation_table %>% 
                  dplyr::select(1, 6:10), 
              format = "latex", booktabs = TRUE, 
-             longtable = TRUE#,
+             longtable = FALSE#,
              #caption = 'Extracted data per paper: disease, objectives, individual_representation, space_representation, model_structure.'
@@
     kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
-    kableExtra::column_spec(column = c(1), width = "5cm") %>% 
-    kableExtra::landscape()
+    column_spec(column = c(1), width = "5cm") %>% 
+    landscape()
 ```
@@
 #columns 11-15 with paper titles
-knitr::kable(final_citation_table %>% 
+kable(final_citation_table %>% 
                  dplyr::select(1, 11:15), 
              format = "latex", booktabs = TRUE, 
-             longtable = TRUE#,
+             longtable = FALSE#,
            #  caption = 'Extracted data per paper: parametrization, validation, outbreak_type, intervention_modelled, vax_modelled_with_non_vax.'
@@
     kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
-    kableExtra::column_spec(column = c(1, 2, 5), width = "4cm") %>% 
-    kableExtra::landscape()
+    column_spec(column = c(1, 2, 5), width = "4cm") %>% 
+    landscape()
 ```
@@
 #columns 16-22 with paper titles
-knitr::kable(final_citation_table %>% 
+kable(final_citation_table %>% 
                  dplyr::select(1, 16:22), 
              format = "latex", booktabs = TRUE, 
-             longtable = TRUE#,
+             longtable = FALSE#,
            #  caption = 'Extracted data per paper: is_vax_effective, outcome_measured, sensitivity_analysis, data_used, data_available, simulation_code_available, vax_modelled.'
@@
     kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
-    kableExtra::column_spec(column = c(1, 3), width = "5cm") %>% 
-    kableExtra::landscape()
+    column_spec(column = c(1, 3), width = "5cm") %>% 
+    landscape()
 ```

### 2023-03-15 epidemics_manuscript/outbreak_response_models_review_v2.tex
changed review title

@@
 {\Large
-\textbf\newline{Outbreak response interventions to human vaccine-preventable diseases: a systematic review of modelling practices before COVID-19}
+\textbf\newline{Mechanistic modelling of outbreak response interventions to human vaccine-preventable diseases: a systematic review of modelling practices before COVID-19}
 }

### 2023-04-23 analyses/scripts/orv_models_review_data_cleaning.R
Refactored data cleaning script for readability

@@ -1,195 +1,246 @@
-#library('sjmisc')
-library('tidyverse')
-library('ggthemes')
-library('scales')
-library('janitor')
-library('forcats')
-library('stringr')
-library('bib2df')
-library('xlsx')
+suppressPackageStartupMessages({
+  library("tidyverse")
+  library("ggthemes")
+  library("scales")
+  library("janitor")
+  library("bib2df")
+  library("xlsx")
+})
 
-#Check if the folder for saving the cleaned files exists, if not, create a folder
-if(!dir.exists('./data/final_data/cleaned_data'))
-    {
-    dir.create('./data/final_data/cleaned_data', 
-               showWarnings = FALSE)
-    }
+# Define global variables
+data_dir <- "./data"
 
-#load the review data extraction results and remove extraneous variables 
-review_data_compact <- read_delim('./data/final_data/raw_data/orv_review_compact_data.csv', 
-                                          delim = ';', 
-                                          na = c('', 'NA')
-                                          )
 
-#load the citation data for merging
-citation_data <- bib2df('./data/final_data/raw_data/included_studies.bib', 
-                        separate_names = FALSE
-                        ) %>% 
-    mutate(year = as.numeric(YEAR))
+# load the review data extraction results and remove extraneous variables
+review_data_compact <- read_delim(
+  file.path(
+    data_dir,
+    "orv_review_compact_data.csv"
+  ),
+  delim = ";",
+  na = c("", "NA")
+)
+
+# load the citation data for merging
+citation_data <- bib2df(file.path(data_dir, "included_studies.bib"),
+  separate_names = FALSE
+) %>%
+  mutate(year = as.numeric(YEAR))
 
 ############################################
-#Data cleaning
+# Data cleaning
 ############################################
 
 
 
 
-#Step 1
+# Step 1
 #' Remove extraneous variables and clean the column names
-#' the compact data is the same as above except that there are multiple entries per cell;
+#' the compact data is the same as above except that there are multiple
+#' entries per cell;
 #' because that is how KoboToolbox saves multiple answer questions
-review_data_compact_cleaning_step1 <- review_data_compact %>% 
-    filter(publication_year < 2020) %>% #remove 2020 because the search was done in Jan 2020 so it gives the illusion that there were few papers in 2020.
-   # select(-'_index') %>% 
-    clean_names() %>% 
-    remove_empty('cols')
+review_data_compact_cleaning_step1 <- review_data_compact %>%
+  # remove 2020 because the search was
[…]

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Changed output to pdf
Removed redundant loaded packages and changed global chunk settings

--- 2023-03-02 scripts/orv_sys_rev_data_analysis.Rmd
@@
 output:
-  word_document:
-    toc: yes
+  # word_document:
+  #   toc: yes
   pdf_document:
@@
 library('tidyverse')
-library('readr')
 library('ggthemes')
@@
 library('janitor')
-library('forcats')
-library('stringr')
 library('countrycode')
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
-knitr::opts_chunk$set(dev = 'jpeg')
-knitr::opts_chunk$set(out.height = "\\textheight",  out.width = "\\textwidth")
-knitr::opts_chunk$set(message = FALSE)
-knitr::opts_chunk$set(warning = FALSE)
-
+knitr::opts_chunk$set(echo = FALSE, 
+                      dev = 'png', 
+                      out.height = "\\textheight",  
+                      out.width = "\\textwidth", 
+                      message = FALSE, 
+                      warning = FALSE
+                      )
+```
+
+```{r}
 #create a folder for storing the manuscript figures

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis_by_collab_type.Rmd
Revised the header (title, date, authors)

--- 2023-03-02 scripts/orv_sys_rev_data_analysis_old.Rmd
@@
 ---
-title: "Systematic review of outbreak response models"
-author: "James Azam"
-date: "01/06/2021"
+title: "Systematic review of outbreak response models: data analysis"
+author: "James M. Azam, Xiaoxi Pang, Elisha B. Are, Juliet R.C. Pulliam, Matthew J. Ferrari"
+date: today()
 output:

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Removed thesis path and commented out prisma chart code

@@
 # Load the cleaned data 
-long_data <- read_rds('../data/final_data/cleaned_data/review_data_long_cleaned.rds')
+long_data <- read_rds('../data/review_data_long_cleaned.rds')
 
 #The cleaned data without citations
-compact_data_init <- read_rds('../data/final_data/cleaned_data/review_data_compact_cleaned.rds')
-
-#a vector of shorter replacements for the original parametrization descriptions
-parametrization_str_replacements <- c('values_from_literature' = 'literature', 
+compact_data_init <- read_rds('../data/review_data_compact_cleaned.rds')
+```
+
+```{r}
+# Dictionary of parametrization methods descriptions
+parametrization_dict <- c('values_from_literature' = 'literature', 
                   'values_from_guess_and_expert_opion' = 'expert_opinion', 
@@
 
-#a vector of shorter replacements for the original validation descriptions
-validation_str_replacements <- c('compared_with_data' = 'data',
+# Dictionary of validation methods descriptions
+validation_dict <- c('compared_with_data' = 'data',
                                  'compared_with_other_model_output' = 'another_model',
@@
 
-```{r eval=FALSE}
-library(PRISMAstatement)
-
-prisma_chart <- prisma(found = 12986,
-       found_other = 0,
-       no_dupes = 5012, 
-       extra_dupes_box = TRUE,
-       screened = 5012, 
-       screen_exclusions = 4211, 
-       full_text = 801,
-       full_text_exclusions = 548, 
-       qualitative = 253, 
-       quantitative = 0,
-       width = 800, height = 800,
-       font_size = 12)
-
-prisma_chart
-```
+<!-- # ```{r eval=FALSE} -->
+<!-- # library(PRISMAstatement) -->
+<!-- #  -->
+<!-- # prisma_chart <- prisma(found = 12986, -->
+<!-- #        found_other = 0, -->
+<!-- #        no_dupes = 5012,  -->
+<!-- #        extra_dupes_box = TRUE, -->
+<!-- #        screened = 5012,  -->
+<!-- #        screen_exclusions = 4211,  -->
+<!-- #        full_text = 801, -->
+<!-- #        full_text_exclusions = 548,  -->
+<!-- #        qualitative = 253,  -->
+<!-- #        quantitative = 0, -->
+<!-- #        width = 800, height = 800, -->
+<!-- #        font_size = 12) -->
+<!-- #  -->
+<!-- # prisma_chart -->
+<!-- # ``` -->
 

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Shortened variable names

@@
   mutate(parametrization = str_replace_all(parametrization, 
-                                           parametrization_str_replacements
+                                           parametrization_dict
                                            )
@@
   mutate(validation = str_replace_all(validation, 
-                                      validation_str_replacements
+                                      validation_dict
                                       )

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Changed T to True.

@@
          ) %>% 
-  mutate(continent_studied = case_when(str_detect(continent_studied, 'asia') == T ~ 'asia', 
-                                         str_detect(continent_studied, 'africa') == T ~ 'africa', 
+  mutate(continent_studied = case_when(str_detect(continent_studied, 'asia') == TRUE ~ 'asia', 
+                                         str_detect(continent_studied, 'africa') == TRUE ~ 'africa', 
                                          TRUE ~ continent_studied

### 2023-04-23 analyses/scripts/orv_sys_rev_supplementary.Rmd
Updated some paths

@@
 # Load the cleaned data 
-long_data <- read_rds('../data/final_data/cleaned_data/review_data_long_cleaned.rds')
+long_data <- read_rds('../data/review_data_long_cleaned.rds')
 
 #The cleaned data without citations
-compact_data_init <- read_rds('../data/final_data/cleaned_data/review_data_compact_cleaned.rds')
+compact_data_init <- read_rds('../data/review_data_compact_cleaned.rds')
 
@@
 # The data with citations 
-compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/final_data/cleaned_data/compact_data_with_citation_keys_cleaned.rds'))
+compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/compact_data_with_citation_keys_cleaned.rds'))
 

### 2023-04-23 analyses/scripts/orv_sys_rev_supplementary.Rmd
Rephrased "articles" to "studies"

@@
              col.names = c('Continent',
-                           'Number of papers',
+                           'Number of studies',
                            'Percentage'

### 2023-04-23 analyses/scripts/orv_sys_rev_supplementary.Rmd
Replaced "%nin%" with !(%in%) to remove unneccesary package dependency

@@
             ) %>% 
-  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
+  filter(!(country_studied %in% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region'))) %>% 
   arrange(desc(num_of_studies)) %>% 

### 2023-04-23 analyses/scripts/orv_sys_rev_supplementary.Rmd
Combined two mutate calls and replaced "T" with TRUE

@@
          ) %>% 
-  mutate(continent_studied = str_to_lower(continent_studied)
-         ) %>% 
-  mutate(continent_studied = case_when(str_detect(continent_studied, 'asia') == T ~ 'asia', 
-                                         str_detect(continent_studied, 'africa') == T ~ 'africa', 
+  mutate(continent_studied = str_to_lower(continent_studied), 
+         continent_studied = case_when(str_detect(continent_studied, 'asia') == TRUE ~ 'asia', 
+                                         str_detect(continent_studied, 'africa') == TRUE ~ 'africa', 
                                          TRUE ~ continent_studied

### 2023-04-23 analyses/scripts/orv_sys_rev_supplementary.Rmd
Replaced a call to summarise() with mutate() to calculate a percentage

@@
   summarise(num_of_studies = sum(num_of_studies), 
-            percentage = sum(percentage),
             .groups = 'drop'
             ) %>% 
-  arrange(desc(percentage))
+mutate(percentage = round(num_of_studies/sum(num_of_studies), 2)*100) %>% 
+  arrange(desc(num_of_studies)) 
 ```

### 2023-04-23 analyses/scripts/orv_sys_rev_supplementary.Rmd
Added a table for studies by continent

--- 2023-04-23 analyses/scripts/orv_sys_rev_supplementary.Rmd
@@
   summarise(num_of_studies = sum(num_of_studies), 
-            percentage = sum(percentage),
             .groups = 'drop'
             ) %>% 
-  arrange(desc(percentage))
+mutate(percentage = round(num_of_studies/sum(num_of_studies), 2)*100) %>% 
+  arrange(desc(num_of_studies))
+
+#Print the results
+knitr::kable(continents_studied_by_count, 
+             caption = 'Number of studies per country'
+             )
 ```

### 2023-04-23 analyses/scripts/full_data_extraction_citation_table.Rmd
Removed redundant loaded packages

@@
 #' load packages
-library('tidyverse')
-# library('xlsx')
-library('scales')
-library('stringr')
-library('conflicted')
-library('Hmisc')
-library('kableExtra')
+library("tidyverse")
+library("scales")
+library("conflicted")
+library("knitr")
 
-#resolve package function conflicts
+# Resolve package function conflicts
 conflict_prefer('filter', 'dplyr')

### 2023-04-23 analyses/scripts/full_data_extraction_citation_table.Rmd
Turned on warnings in dir_create()
Updated global chunk settings

@@
 ```{r setup, include=FALSE}
-options(kableExtra.auto_format = FALSE)
+# options(kableExtra.auto_format = FALSE,
+#         knitr.table.format = "latex"
+#         )
 
@@
                       include = FALSE,
-                      dev = 'jpeg', 
+                      # dev = 'jpeg', 
                       fig.width = 8, 
                       fig.height = 6, 
-                      message = FALSE
+                      message = FALSE,
+                      warning = FALSE,
+                      cache = FALSE
                       )
@@
   dir.create("../figs_manuscript",
-    showWarnings = FALSE
+    showWarnings = TRUE
   )

### 2023-04-23 analyses/scripts/full_data_extraction_citation_table.Rmd
Revised the output settings to pdf

@@
   pdf_document:
-    keep_tex: yes
-  html_document:
-    df_print: paged
+    df_print: kable
+    latex_engine: xelatex
+    keep_tex: true
 ---

### 2023-04-23 analyses/scripts/full_data_extraction_citation_table.Rmd
Reformated the script to remove kable settings for beautifying the tables for the database

@@
 ```{r}
-# Data "cleaning"
-#a vector of shorter replacements for the original parametrization descriptions
-parametrization_str_replacements <- c('values_from_literature' = 'literature', 
-                  'values_from_guess_and_expert_opion' = 'expert_opinion', 
-                  'values_fitted_to_ts' = 'fitted',
-                  ' ' = ' and ' #replace space with 'and' to make it more readable
+# Load the data with citations
+compact_data_with_citation_keys_init <- read_rds("../data/compact_data_with_citation_keys_cleaned.rds")
+
+# Clean various variables
+compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>%
+  mutate(vax_modelled = ifelse(str_detect(intervention_modelled, "vaccination"),
+    "yes",
+    "no"
+  ), 
+  intervention_type = case_when(
+    vax_modelled == "no" & vax_modelled_with_non_vax == "no" ~ "no_vax", # Vaccination was not modelled
+    vax_modelled == "yes" & vax_modelled_with_non_vax == "no" ~ "vax_combination_with_others", # when vax was modelled but not for comparison as a single intervention
+    vax_modelled == "yes" & vax_modelled_with_non_vax == "yes" ~ "vax_single", # when vax was modelled as a single intervention
+  ),
+    publication_year = as.numeric(publication_year),
+    author_in_country_studied = as.character(author_in_country_studied)
+  ) %>%
+  arrange(publication_year) %>%
+  mutate(
+    author_affiliation_type = str_replace_all(author_affiliation_type, " ", " + "),
+    author_in_country_studied = if_else(author_in_country_studied == "NA", "not_applicable",
+      author_in_country_studied
+    ),
+    year_aggreg = as.numeric(ifelse(publication_year < 2006, # An approach to aggregate the years before 2006 into one group because of the low number of papers
+      2005,
+      publication_year
+    )),
+    collab_type = as_factor(if_else(author_affiliation_type == "academic_institutions",
+      "purely_academic",
+      "mixed"
+    ))
+  )
+```
+
+```{r}
+# Data dictionaries
+
+# parametrization description dictionary
+parametrization_str_replacements <- c(
+  "values_from_literature" = "literature",
+  "values_from_guess_and_expert_opion" = "expert_opinion",
+  "values_fitted_to_ts" = "fitted",
+  " " = " and " # replace space with 'and' to make it more readable
 )
 
-#a vector of shorter replacements for the original validation descriptions
-validation_str_replacements <- c('compared_with_data' = 'data',
-                                 'compared_with_other_model_output' = 'another_model',
-                                 'model_not_validated' = 'none',
-                                 ' ' = '_and_'
+# validation description dictionary
+validation_str_replacements <- c(
+  "compared_with_data" = "data",
+  "compared_with_other_model_output" = "another_model",
+  "model_not_validated" = "none",
+  " " = "_and_"
 )
 
-# The data with citations 
-compact_data_with_citation_keys_init <- read_rds('../data/compact_data_with_citation_keys_cleaned.rds')
-
-compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>% 
-    mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
-                               'yes', 
-                               'no')
-         ) %>% 
-  mutate(intervention_type = case_when(
-    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_combination_with_others', #when vax was modelled but not for comparison as a single intervention
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
+# Clean the parametrization and validation variables with dictionary
+compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
+  mutate(parametrization = str_replace_all(
+    parametrization,
+    parametrization_str_replacements
   )) %>%
-  mutate(publication_year = as.numeric(publication_year), 
-         author_in_country_studied = as.character(author_in_country_studied)) %>% 
-  arrange(publication_year) %>%
-  mutate(
-    author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + '),
-    author_in_country_studied = if_else(author_in_country_studied == 'NA', 'not_applicable',
-                                        author_in_country_studied
-                                        )
-    ) %>% 
-  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, #An approach to aggregate the years before 2006 into one group because of the low number of papers
-                                         2005, 
-                                         publication_year
-                                         )
-                                  ), 
-         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
-                                         'purely_academic', 
-                                         'mixed')
+  mutate(validation = str_replace_all(
+    validation,
+    validation_str_replacements
+  )) %>%
+  mutate(model_structure = str_replace(model_structure, 
+                                       "deterministic stochastic", 
+                                       "both"
                                        )
          )
+```
 
-#replace the original descriptions of parametrization and validation with shorter strings
-compact_data_with_citation_keys <- compact_data_with_citation_keys %>% 
-  mutate(parametrization = str_replace_all(parametrization, 
-                                           parametrization_str_replacements
-                                           )
-         ) %>% 
-  mutate(validation = str_replace_all(validation, 
-                                      validation_str_replacements
-                                      )
-         ) %>% 
-  mutate(model_structure = str_replace(model_structure, 'deterministic stochastic', 'both'))
-
-#Rearrange the columns
+```{r}
+# Rearrange the columns
 compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
@@
 
-```{r results='asis'}
+```{r}
+# Remove unneeded columns and rearrange the remainder
  final_citation_table <- compact_data_with_citation_keys %>% 
@@
 ```{r}
-#columns 2-5 with paper titles
-kable(final_citation_table %>% 
-                 dplyr::select(1:5), 
-             format = "latex", 
-             booktabs = TRUE, 
-             longtable = FALSE#,
-             #caption = 'Extracted data per paper: publication_year, author_affiliation_type, country_studied, author_in_country_studied.'
-             ) %>% 
-    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
-    column_spec(column = c(1, 3), width = "5cm") %>%
-    landscape()
+# Make a neat table of papers from columns 1(title)-5
+final_citation_table %>% 
+    select(1:5) %>% 
+    kable()
+
+# booktabs = TRUE,
+#       longtable = FALSE#,
+#       # caption = 'Extracted data per paper: publication_year, author_affiliation_type, country_studied, author_in_country_studied.'
+#          ) %>%
+#     kable_styling(latex_options = c('striped',
+#                                     'scale_down',
+#                                     'hold_position',
+#                                     'repeat_header'
+#                                     )
+#                   ) %>%
+#     column_spec(column = c(1, 3), width = "5cm") #%>%
+    # landscape()
 ```
 
-```{r}
-#columns 6-10 with paper titles
-kable(final_citation_table %>% 
-                 dplyr::select(1, 6:10), 
-             format = "latex", booktabs = TRUE, 
-             longtable = FALSE#,
-             #caption = 'Extracted data per paper: disease, objectives, individual_representation, space_representation, model_structure.'
-             ) %>% 
-    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
-    column_spec(column = c(1), width = "5cm") %>% 
-    landscape()
-```
+<!--  ```{r} -->
+<!-- # Make a neat table of papers from columns 1 (title), and 6-10  -->
+<!-- final_citation_table %>% -->
+<!--   select(c(1, 6:10)) %>% -->
+<!--   kable( -->
+<!--     booktabs = TRUE, -->
+<!--     longtable = FALSE, -->
+<!--     caption = "Extracted data per paper: disease, objectives, individual_representation, space_representation, model_structure." -->
+<!--   ) %>% -->
+<!--   kable_styling(latex_options = c("striped",  -->
+<!--                                   "scale_down",  -->
+<!--                                   "hold_position",  -->
+<!--                                   "repeat_header" -->
+<!--                                   ) -->
+<!--                 ) %>% -->
+<!--   column_spec(column = c(1), width = "5cm") %>% -->
+<!--   landscape() -->
+<!-- ``` -->
 
-```{r}
-#columns 11-15 with paper titles
-kable(final_citation_table %>% 
-                 dplyr::select(1, 11:15), 
-             format = "latex", booktabs = TRUE, 
-             longtable = FALSE#,
-           #  caption = 'Extracted data per paper: parametrization, validation, outbreak_type, intervention_modelled, vax_modelled_with_non_vax.'
-             ) %>% 
-    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
-    column_spec(column = c(1, 2, 5), width = "4cm") %>% 
-    landscape()
-```
+<!-- ```{r} -->
+<!-- # Make a neat table of papers from columns 1 (title) and 11-15  -->
+<!-- final_citation_table %>% -->
+<!--   select(1, 11:15) %>% -->
+<!--   kable( -->
+<!--     longtable = FALSE, -->
+<!--     caption = "Extracted data per paper: parametrization, validation, outbreak_type, intervention_modelled, vax_modelled_with_non_vax." -->
+<!--   ) %>% -->
+<!--   kable_styling(latex_options = c("striped",  -->
+<!--                                   "scale_down",  -->
+<!--                                   "hold_position",  -->
+<!--                                   "repeat_header" -->
+<!--                                   ) -->
+<!--                 ) %>% -->
+<!--   column_spec(column = c(1, 2, 5), width = "4cm") %>% -->
+<!--   landscape() -->
+<!-- ``` -->
 
-```{r}
-#columns 16-22 with paper titles
-kable(final_citation_table %>% 
-                 dplyr::select(1, 16:22), 
-             format = "latex", booktabs = TRUE, 
-             longtable = FALSE#,
-           #  caption = 'Extracted data per paper: is_vax_effective, outcome_measured, sensitivity_analysis, data_used, data_available, simulation_code_available, vax_modelled.'
-             ) %>% 
-    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
-    column_spec(column = c(1, 3), width = "5cm") %>% 
-    landscape()
-```
+<!--  ```{r} -->
+<!-- # Make a neat table of papers from columns 1 (title) and 16-22 -->
+<!-- final_citation_table %>% -->
+<!--   select(1, 16:22) %>% -->
+<!--   kable( -->
+<!--     booktabs = TRUE, -->
+<!--     longtable = FALSE, -->
+<!--     caption = "Extracted data per paper: is_vax_effective, outcome_measured, sensitivity_analysis, data_used, data_available, simulation_code_available, vax_modelled." -->
+<!--   ) %>% -->
+<!--   kable_styling(latex_options = c("striped", -->
+<!--                                   "scale_down",  -->
+<!--                                   "hold_position",  -->
+<!--                                   "repeat_header" -->
+<!--                                   ) -->
+<!--                 ) %>% -->
+<!--   column_spec(column = c(1, 3), width = "5cm") %>% -->
+<!--   landscape() -->
+<!-- ``` -->

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis_by_collab_type.Rmd
Changed output format to pdf
Removed redundant loaded packages

@@
 output:
-  word_document:
-    keep_md: yes
+  # word_document:
+  #   keep_md: yes
 #  html_notebook
+  pdf_document:
+    toc: yes
+    keep_tex: yes
+    fig_crop: no
 ---

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis_by_collab_type.Rmd
Fixed some paths

@@
 conflict_prefer('kable', 'knitr')
+
+data_dir <- "../data"
 ```
@@
 # The script clears the environment after cleaning the data
-#source('./data_cleaning/orv_models_review_data_cleaning.R')
+source(file.path('orv_models_review_data_cleaning.R'))
 ```
@@
 # Load the cleaned data 
-long_data <- read_rds('../data/final_data/cleaned_data/review_data_long_cleaned.rds')
+long_data <- read_rds(file.path(data_dir, 'review_data_long_cleaned.rds'))
 
 #The cleaned data without citations
-compact_data_init <- read_rds('../data/final_data/cleaned_data/review_data_compact_cleaned.rds')
+compact_data_init <- read_rds(file.path(data_dir, "review_data_compact_cleaned.rds"))
 
@@
 # The data with citations 
-compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/final_data/cleaned_data/compact_data_with_citation_keys_cleaned.rds'))
+compact_data_with_citation_keys_init <- read_rds(file.path(data_dir, "compact_data_with_citation_keys_cleaned.rds"))
 

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis_old.Rmd
Set up global chunk settings

--- 2023-03-02 scripts/orv_sys_rev_data_analysis_old.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
-
-# Sets the working directory for subsequent chunks, but not this chunk
-#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
-
-knitr::opts_chunk$set(fig.width = 8, fig.height = 6)
+knitr::opts_chunk$set(echo = FALSE, 
+                      warning = FALSE, 
+                      message = FALSE, 
+                      fig.width = 8, 
+                      fig.height = 6
+                      )
 ```

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis_old.Rmd
Fixed some paths

@@
 # Load the cleaned data 
-long_data <- read_rds('../data/final_data/cleaned_data/review_data_long_cleaned.rds')
+long_data <- read_rds(file.path(data_dir, 'review_data_long_cleaned.rds'))
 
 #The cleaned data without citations
-compact_data_init <- read_rds('../data/final_data/cleaned_data/review_data_compact_cleaned.rds')
+compact_data_init <- read_rds(file.path(data_dir, 'review_data_compact_cleaned.rds')
+                              )
 

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Removed Hmisc package and use of %nin% from Hmisc

--- 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
@@
 library('conflicted')
-library('Hmisc')
 library('ggwordcloud')
@@
             ) %>% 
-  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
+  filter(!country_studied %in% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
   arrange(desc(num_of_studies)) %>% 
@@
 continents_studied_by_count <- countries_studied_by_count %>% 
-  filter(country_studied %nin% c('none', 'northern_hemisphere', 'global')) %>% 
+  filter(!country_studied %in% c('none', 'northern_hemisphere', 'global')) %>% 
   mutate(continent_studied = countrycode(country_studied, 
@@
   filter(author_in_country_studied != 'not_applicable') %>% 
-  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
+  filter(!country_studied %in% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
 separate_rows(country_studied,  sep = ' ') %>% 
@@
   filter(author_in_country_studied != 'not_applicable') %>% 
-  filter(country_studied %nin% c('other', 'none', 'northern_hemisphere', 'west_africa', 'global')) %>% 
+  filter(!country_studied %in% c('other', 'none', 'northern_hemisphere', 'west_africa', 'global')) %>% 
   count(collab_type, author_in_country_studied, sort = TRUE) %>% 
@@
   distinct(title, .keep_all = TRUE) %>% 
-  filter(outcome_measured %nin% c('outcome_other', '', 's')) %>% 
+  filter(!outcome_measured %in% c('outcome_other', '', 's')) %>% 
   count(collab_type, outcome_measured, name = 'num_of_studies') %>% 
@@
   ungroup(outcome_measured) %>% 
-  filter(outcome_measured %nin% c('outcome_other', '')) %>% 
+  filter(!outcome_measured %in% c('outcome_other', '')) %>% 
   group_by(collab_type) %>% 
@@
   filter(author_in_country_studied != 'not_applicable') %>% 
-  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
+  filter(!country_studied %in% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
   group_by(collab_type) %>% 
@@
   filter(author_in_country_studied != 'not_applicable') %>% 
-  filter(country_studied %nin% c('other', 'none', 'northern_hemisphere', 'west_africa', 'global')) %>% 
+  filter(!country_studied %in% c('other', 'none', 'northern_hemisphere', 
+                                 'west_africa', 'global')
+         ) %>% 
   count(collab_type, author_in_country_studied, sort = TRUE) %>% 
@@
   distinct(title, .keep_all = TRUE) %>% 
-  filter(outcome_measured %nin% c('outcome_other', '')) %>% 
+  filter(!outcome_measured %in% c('outcome_other', '')) %>% 
   count(collab_type, outcome_measured, name = 'num_of_studies') %>% 

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Deleted commented out code

@@
 # Human vaccine-preventable diseases
-
-<!-- # ```{r eval=FALSE} -->
-<!-- # library(PRISMAstatement) -->
-<!-- #  -->
-<!-- # prisma_chart <- prisma(found = 12986, -->
-<!-- #        found_other = 0, -->
-<!-- #        no_dupes = 5012,  -->
-<!-- #        extra_dupes_box = TRUE, -->
-<!-- #        screened = 5012,  -->
-<!-- #        screen_exclusions = 4211,  -->
-<!-- #        full_text = 801, -->
-<!-- #        full_text_exclusions = 548,  -->
-<!-- #        qualitative = 253,  -->
-<!-- #        quantitative = 0, -->
-<!-- #        width = 800, height = 800, -->
-<!-- #        font_size = 12) -->
-<!-- #  -->
-<!-- # prisma_chart -->
-<!-- # ``` -->
-
-<!-- ## Publications per year -->
-
-<!-- ```{r} -->
-
-<!-- publications_per_year <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(publication_year)  -->
-
-<!-- publications_per_year_plot <- ggplot(data = publications_per_year) +  -->
-<!--   geom_bar(aes(x = publication_year,  -->
-<!--                y = n -->
-<!--                ),  -->
-<!--            stat = 'identity',  -->
-<!--            color = 'black', -->
-<!--            fill = 'tomato3' -->
-<!--            ) + -->
-<!--   scale_y_continuous(breaks = seq(0, 30, 2), -->
-<!--                      labels = seq(0, 30, 2) -->
-<!--                      ) + -->
-<!--   labs(x = '**Year of publication**', y = '**Number of papers**') + -->
-<!--   md_theme_minimal(base_size = 12) -->
-
-<!-- plot(publications_per_year_plot) -->
-
-<!-- ggsave(filename = 'publications_per_year.tiff',  -->
-<!--        plot = publications_per_year_plot,  -->
-<!--        device = 'tiff',  -->
-<!--        path = save_fig_here -->
-<!--        ) -->
-
-<!-- ggsave(filename = 'publications_per_year.tiff',  -->
-<!--        plot = publications_per_year_plot,  -->
-<!--        device = 'tiff',  -->
-<!--        path = save_thesis_fig_here -->
-<!--        ) -->
-
-<!-- ``` -->
-
-<!-- ## Collaboration patterns in time -->
-
-<!-- ### Number of studies per combinations of author affiliation types -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- #' Count by collaboration types and make a bar plot -->
-<!-- collab_types_count <- compact_data_with_citation_keys_no_fmd %>% -->
-<!--     count(author_affiliation_type, sort = TRUE) %>%  -->
-<!--     arrange(desc(n)) %>%  -->
-<!--     adorn_totals() %>%  -->
-<!--     adorn_percentages(denominator = 'col') %>%  -->
-<!--     adorn_pct_formatting() %>%  -->
-<!--     adorn_ns() -->
-
-<!-- knitr::kable(collab_types_count,  -->
-<!--              format = "latex", booktabs = TRUE,  -->
-<!--              caption = 'Number of publications per author affiliation type combination') %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))  -->
-<!-- ``` -->
-
-<!-- ### Proportions of the total publications per year by collaboration type -->
-
-<!-- ```{r echo=FALSE, fig.width=8} -->
-<!-- #' Count the number of each author affiliation type per year (including FMD) -->
-<!-- collap_types_by_year <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(year_aggreg,  -->
-<!--         collab_type,  -->
-<!--         name = 'total_publications' -->
-<!--         ) -->
-
-<!-- #The plot -->
-<!-- # Modify the x-axis labels to account for the lumping of the years from 2005 and below -->
-<!-- x_axis_labels <- as.character(seq(2005, 2020, 2)) -->
-
-<!-- x_axis_labels[1] <- '1970-2005' -->
-
-<!-- collab_proportions_plot <- ggplot(data = collap_types_by_year) +  -->
-<!--   geom_bar(aes(x = year_aggreg, -->
-<!--                y = total_publications, -->
-<!--                fill = collab_type -->
-<!--                ), -->
-<!--            color = 'black', -->
-<!--            stat = 'identity', -->
-<!--            position = position_fill(reverse = TRUE)#, -->
-<!--            #show.legend = FALSE -->
-<!--              ) + -->
-<!--   scale_fill_manual(values = c('tan3', 'turquoise2')) + -->
-<!--   scale_x_continuous(breaks = seq(2005, 2020, 2), -->
-<!--                      labels = x_axis_labels, -->
-<!--                      expand = c(0, 0) -->
-<!--                      ) + -->
-<!--   #coord_flip() + -->
-<!--   labs(#title = 'Publications per collaboration type over time', -->
-<!--        x = '**Year**', -->
-<!--        y = '**Proportion of total publications**', -->
-<!--        fill = '**Collaboration type**'  -->
-<!--          ) + -->
-<!--   theme(legend.position = 'none') + -->
-<!--  # md_theme_minimal(base_size = 16) #For Powerpoint -->
-<!--   md_theme_minimal(base_size = 12) -->
-
-<!-- plot(collab_proportions_plot) -->
-
-<!-- ggsave(filename = 'collab_proportions.tiff',  -->
-<!--        plot = collab_proportions_plot,  -->
-<!--        device = 'tiff',  -->
-<!--        path = save_fig_here -->
-<!--        ) -->
-
-<!-- ggsave(filename = 'collab_proportions.tiff',  -->
-<!--        plot = collab_proportions_plot,  -->
-<!--        device = 'tiff',  -->
-<!--        path = save_thesis_fig_here -->
-<!--        ) -->
-
-<!-- ``` -->
-
-<!-- ### Absolute number of publications per year by collaboration type -->
-
-<!-- ```{r} -->
-<!-- #' Count the number of each author affiliation type per year -->
-<!-- collabs_per_year <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(year_aggreg,  -->
-<!--         collab_type,  -->
-<!--         name = 'total_publications' -->
-<!--         )  -->
-
-<!-- collabs_per_year_plot <- ggplot(data = collabs_per_year,  -->
-<!--                                     aes(x = year_aggreg,  -->
-<!--                                         y = total_publications -->
-<!--                                         ),  -->
-<!--                                     color = 'black') +  -->
-<!--   geom_bar(aes(fill = collab_type),  -->
-<!--            stat = 'identity',  -->
-<!--            position = 'dodge' -->
-<!--            ) +  -->
-<!--   scale_fill_manual(values = c('tan3', 'turquoise2')) +  -->
-<!--   scale_x_continuous(breaks = seq(2005, 2020, 2), -->
-<!--                      labels = x_axis_labels, -->
-<!--                      expand = c(0, 0) -->
-<!--                      ) + -->
-<!--   labs(x = '**Year**',  -->
-<!--        y = '**Total publications**',  -->
-<!--        fill = 'Collaboration type' -->
-<!--        ) + -->
-<!--   md_theme_minimal(base_size = 12) + -->
-<!--   #md_theme_minimal(base_size = 16) + -->
-<!--   theme(legend.position = 'bottom')  -->
-
-<!-- plot(collabs_per_year_plot) -->
-
-<!-- ggsave(filename = 'total_collabs_per_year_plot.tiff', -->
-<!--        plot = collabs_per_year_plot,  -->
-<!--        device = 'tiff', -->
-<!--        path = save_fig_here -->
-<!--        ) -->
-
-<!-- ggsave(filename = 'total_collabs_per_year_plot.tiff', -->
-<!--        plot = collabs_per_year_plot,  -->
-<!--        device = 'tiff', -->
-<!--        path = save_thesis_fig_here -->
-<!--        ) -->
-
-<!-- ``` -->
-
-<!-- Even though non-academic collaborations increased over time, the share of total publications per year over time decreased. -->
-
-<!-- ## Collaboration patterns in geographic space -->
 

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Fixed some paths

@@
 ```{r}
-#create a folder for storing the manuscript figures
-
-if(!dir.exists('../figs_manuscript'))
+
+#directories
+# Figures
+figs_dir <- "../figs_manuscript"
+
+# Create a folder for storing the manuscript figures if it doesn't exist
+if (!dir.exists('../figs_manuscript'))
     {
@@
 
-#save figures in this folder
-save_fig_here <- '../figs_manuscript'
+data_dir <- "../data"
 ```
@@
 # Load the cleaned data 
-long_data <- read_rds('../data/review_data_long_cleaned.rds')
+long_data <- read_rds(file.path(data_dir, "review_data_long_cleaned.rds"))
 
 #The cleaned data without citations
-compact_data_init <- read_rds('../data/review_data_compact_cleaned.rds')
+compact_data_init <- read_rds(file.path(data_dir, 
+                                        "review_data_compact_cleaned.rds")
+                              )
 ```
@@
        device = 'tiff',
-       path = save_fig_here
+       path = figs_dir
        )

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Formatted the code

@@
 
-knitr::kable(studies_per_collab_type, caption = 'Number of studies per collaboration type (Human VPDs)',
+knitr::kable(studies_per_collab_type, 
+             caption = 'Number of studies per collaboration type (Human VPDs)',
              format = "latex", booktabs = TRUE) %>% 
@@
 fmd_collab_types_per_year <- fmd_data %>% 
-  count(year_aggreg, 
-        collab_type, 
-        name = 'total_publications'
-        )
+  count(year_aggreg, collab_type, name = 'total_publications')
 

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Removed md_theme dependency

@@
                      ) +
-  #coord_flip() +
-  labs(#title = 'Publications per collaboration type over time',
-       x = '**Year**',
-       y = '**Proportion of total publications**',
+  labs(x = 'Year',
+       y = 'Proportion of total publications',
        fill = '**Collaboration type**' 
          ) +
-  theme(legend.position = 'none') +
- # md_theme_minimal(base_size = 16) #For Powerpoint
-  md_theme_minimal(base_size = 12)
+  theme(legend.position = 'none')
 
@@
                      ) +
-  labs(x = '**Year**', 
-       y = '**Total publications**', 
+  labs(x = 'Year', 
+       y = 'Total publications', 
        fill = 'Collaboration type'
        ) +
-  md_theme_minimal(base_size = 12) +
-  #md_theme_minimal(base_size = 16) +
   theme(legend.position = 'bottom')

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Removed mdthemes package

@@
 library('ggthemes')
-library('mdthemes')
 library('scales')

### 2023-04-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Fixed some paths

@@
                               )
+
+# The data with citations 
+compact_data_with_citation_keys_init <- read_rds('../data/compact_data_with_citation_keys_cleaned.rds')
 ```
@@
                                  )
-
-# The data with citations 
-compact_data_with_citation_keys_init <- read_rds('../data/compact_data_with_citation_keys_cleaned.rds')
 

### 2023-04-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Moved up the setup chunk

@@
 
-```{r echo=FALSE, include=FALSE}
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, 
+                      dev = 'png', 
+                      out.height = "\\textheight",  
+                      out.width = "\\textwidth", 
+                      message = FALSE, 
+                      warning = FALSE
+                      )
+```
+
+```{r}
 #' load packages
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, 
-                      dev = 'png', 
-                      out.height = "\\textheight",  
-                      out.width = "\\textwidth", 
-                      message = FALSE, 
-                      warning = FALSE
-                      )
-```
-
-```{r}
-
+```{r}
 #directories

### 2023-04-25 analyses/scripts/orv_models_review_data_cleaning.R
Fixed a path

@@ -1,14 +1,12 @@
 suppressPackageStartupMessages({
   library("tidyverse")
-  library("ggthemes")
-  library("scales")
   library("janitor")
   library("bib2df")
   library("xlsx")
 })
 
 # Define global variables
-data_dir <- "./data"
+data_dir <- "./analyses/data"
 
 
 # load the review data extraction results and remove extraneous variables

### 2023-04-26 analyses/scripts/orv_models_review_data_cleaning.R
Fixed a path

@@ -6,7 +6,7 @@ suppressPackageStartupMessages({
 })
 
 # Define global variables
-data_dir <- "./analyses/data"
+data_dir <- "./data"
 
 
 # load the review data extraction results and remove extraneous variables

### 2023-04-26 analyses/scripts/orv_models_review_data_cleaning.R
Moved the extra data cleaning steps from the main analysis script here

@@ -226,11 +226,95 @@ citation_data_cleaned <- citation_data %>%
     year = as.numeric(year)
   )
 
-# COmbine the citation database and cleaned dataset
+# Combine the citation database and cleaned dataset
 compact_data_with_citation_keys <- left_join(review_data_compact_cleaned,
   citation_data_cleaned,
   by = c("title")
 )
+
+
+# Clean individual variables
+compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
+  mutate(publication_year = as.numeric(publication_year),
+         author_in_country_studied = as.character(author_in_country_studied)
+         ) %>%
+  arrange(publication_year) %>%
+  mutate(vax_modelled = ifelse(
+    str_detect(intervention_modelled, 'vaccination'), 'yes', 'no')) %>%
+  mutate(
+    intervention_type = case_when(
+    # When vax was not modelled at all
+    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax',
+    # When vax was modelled but not for comparison as a single intervention
+    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_combination_with_others',
+    # When vax was modelled as a single intervention to be compared with others
+    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single'
+    )
+    ) %>%
+  mutate(
+    author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + ')
+    ) |>
+  mutate(
+    author_in_country_studied = if_else(author_in_country_studied == 'NA',
+                                        'not_applicable',
+                                        author_in_country_studied
+                                        )
+    ) %>%
+  #Aggregate years before 2006 into one group because of the low number of papers
+  mutate(year_aggreg = as.numeric(
+    ifelse(publication_year < 2006, 2005, publication_year)
+    )
+    ) |>
+  mutate(
+  collab_type = as_factor(
+    if_else(author_affiliation_type == 'academic_institutions',
+            'purely_academic',
+            'mixed')
+    ),
+  purely_academic_collab = if_else(
+    author_affiliation_type == 'academic_institutions', TRUE, FALSE)
+  ) |>
+  relocate(purely_academic_collab, .after = author_affiliation_type)
+
+# Clean descriptions of parametrization and validation with shorter labels
+
+#' First create dictionary of parametrization methods descriptions and shorter
+#' replacements
+
+parametrization_dict <- c('values_from_literature' = 'literature',
[…]

### 2023-04-26 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Now sourcing the data cleaning script in the main analysis

@@
 ```{r}
+#' re-run the data cleaning step, in case something has changed 
+#' TO DO: Use GNU make for this
+
+source("./orv_models_review_data_cleaning.R")
+
 # Load the cleaned data 

### 2023-04-26 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Moved the extra data cleaning steps to the data cleaning script

@@
 #The cleaned data without citations
-compact_data_init <- read_rds(file.path(data_dir, 
-                                        "review_data_compact_cleaned.rds")
+compact_data_init <- read_rds(
+  file.path(data_dir, "review_data_compact_cleaned.rds")
   )
@@
 # The data with citations 
-compact_data_with_citation_keys_init <- read_rds('../data/compact_data_with_citation_keys_cleaned.rds')
-```
-
-```{r}
-# Dictionary of parametrization methods descriptions
-parametrization_dict <- c('values_from_literature' = 'literature', 
-                  'values_from_guess_and_expert_opion' = 'expert_opinion', 
-                  'values_fitted_to_ts' = 'fitted',
-                  ' ' = ' and ' #replace space with 'and' to make it more readable
-                  )
-
-# Dictionary of validation methods descriptions
-validation_dict <- c('compared_with_data' = 'data',
-                                 'compared_with_other_model_output' = 'another_model',
-                                 'model_not_validated' = 'none',
-                                 ' ' = '_and_'
-                                 )
-
-compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>% 
-    mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
-                               'yes', 
-                               'no')
-         ) %>% 
-  mutate(intervention_type = case_when(
-    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_combination_with_others', #when vax was modelled but not for comparison as a single intervention
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
-  )) %>% 
-  mutate(publication_year = as.numeric(publication_year), 
-         author_in_country_studied = as.character(author_in_country_studied)) %>% 
-  arrange(publication_year) %>%
-  mutate(
-    author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + '),
-    author_in_country_studied = if_else(author_in_country_studied == 'NA', 'not_applicable',
-                                        author_in_country_studied
-                                        )
-    ) %>% 
-  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, #An approach to aggregate the years before 2006 into one group because of the low number of papers
-                                         2005, 
-                                         publication_year
-                                         )
-                                  ), 
-         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
-                                         'purely_academic', 
-                                         'mixed')
-                                 )
-         )
-
-#replace the original descriptions of parametrization and validation with shorter strings
-compact_data_with_citation_keys <- compact_data_with_citation_keys %>% 
-  mutate(parametrization = str_replace_all(parametrization, 
-                                           parametrization_dict
-                                           )
-         ) %>% 
-  mutate(validation = str_replace_all(validation, 
-                                      validation_dict
-                                      )
-         ) %>% 
-  mutate(model_structure = str_replace(model_structure, 'deterministic stochastic', 'both'))
-
-#Rearrange the columns
-compact_data_with_citation_keys <- compact_data_with_citation_keys %>% 
-  relocate(c(title, bibtexkey), .before = publication_year) %>% 
-  relocate(publication_year, .before = bibtexkey) %>% 
-  relocate(c(x0_reviewer, category, author:language), 
-           .after = collab_type
-           )
-
-# Remove the FMD papers (NB: We only use the FMD papers for comparison)
+compact_data_with_citation_keys <- read_rds(
+  '../data/compact_data_with_citation_keys_cleaned.rds'
+  )
+
+# Keep the human disease studies (NB: We only use the FMD papers for comparison)
 long_data_no_fmd <- long_data %>% filter(disease != 'fmd')
@@
 
-#Filter the FMD data
+# Filter the FMD data
 fmd_data <- compact_data_with_citation_keys %>% 

### 2023-05-15 analyses/scripts/archive/orv_sys_rev_data_analysis_FMD.Rmd
Moved redundant scripts into archive directory

--- 2023-03-02 scripts/orv_sys_rev_data_analysis.Rmd
@@
 ---
-title: "Analysis of the included studies"
+title: "Outbreak response models of foot and mouth disease (1970-2019) - A primary analysis"
+author: "James Azam"
+date: '`r format(Sys.Date(), "%B %d, %Y")`'
 output:
   word_document:
+    keep_md: yes
+    reference_docx: word-style.docx
     toc: yes
-  pdf_document:
-    toc: yes
-    keep_tex: yes
-    fig_crop: no
 ---
@@
 library('Hmisc')
+library('treemapify')
 library('ggwordcloud')
@@
 ```{r}
-# Load the cleaned data 
-long_data <- read_rds('../data/final_data/cleaned_data/review_data_long_cleaned.rds')
-
-#The cleaned data without citations
-compact_data_init <- read_rds('../data/final_data/cleaned_data/review_data_compact_cleaned.rds')
-
-#a vector of shorter replacements for the original parametrization descriptions
-parametrization_str_replacements <- c('values_from_literature' = 'literature', 
-                  'values_from_guess_and_expert_opion' = 'expert_opinion', 
-                  'values_fitted_to_ts' = 'fitted',
-                  ' ' = ' and ' #replace space with 'and' to make it more readable
-                  )
-
-#a vector of shorter replacements for the original validation descriptions
-validation_str_replacements <- c('compared_with_data' = 'data',
-                                 'compared_with_other_model_output' = 'another_model',
-                                 'model_not_validated' = 'none',
-                                 ' ' = '_and_'
-                                 )
-
 # The data with citations 
@@
     vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_combination_with_others', #when vax was modelled but not for comparison as a single intervention
+    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_alongside', #when vax was modelled but not for comparison as a single intervention
     vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
@@
 
+#a vector of shorter replacements for the original parametrization descriptions
+parametrization_str_replacements <- c('values_from_literature' = 'literature', 
+                  'values_from_guess_and_expert_opion' = 'expert_opinion', 
+                  'values_fitted_to_ts' = 'fitted',
+                  ' ' = ' and ' #replace space with 'and' to make it more readable
+                  )
+
+#a vector of shorter replacements for the original validation descriptions
+validation_str_replacements <- c('compared_with_data' = 'data',
+                                 'compared_with_other_model_output' = 'another_model',
+                                 'model_not_validated' = 'none',
+                                 ' ' = '_and_'
+                                 )
+
 #replace the original descriptions of parametrization and validation with shorter strings
@@
 
-# Remove the FMD papers (NB: We only use the FMD papers for comparison)
-long_data_no_fmd <- long_data %>% filter(disease != 'fmd')
-
-compact_data_with_citation_keys_no_fmd <- compact_data_with_citation_keys %>% 
-  filter(disease != 'fmd')
-
 #Filter the FMD data
@@
 
-# Human vaccine-preventable diseases
+# Primary objectives of review
 
-```{r eval=FALSE}
-library(PRISMAstatement)
+## Collaboration patterns in time
 
-prisma_chart <- prisma(found = 12986,
-       found_other = 0,
-       no_dupes = 5012, 
-       extra_dupes_box = TRUE,
-       screened = 5012, 
-       screen_exclusions = 4211, 
-       full_text = 801,
-       full_text_exclusions = 548, 
-       qualitative = 253, 
-       quantitative = 0,
-       width = 800, height = 800,
-       font_size = 12)
-
-prisma_chart
-```
-
-<!-- ## Publications per year -->
-
-<!-- ```{r} -->
-
-<!-- publications_per_year <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(publication_year)  -->
-
-<!-- publications_per_year_plot <- ggplot(data = publications_per_year) +  -->
-<!--   geom_bar(aes(x = publication_year,  -->
-<!--                y = n -->
-<!--                ),  -->
-<!--            stat = 'identity',  -->
-<!--            color = 'black', -->
-<!--            fill = 'tomato3' -->
-<!--            ) + -->
-<!--   scale_y_continuous(breaks = seq(0, 30, 2), -->
-<!--                      labels = seq(0, 30, 2) -->
-<!--                      ) + -->
-<!--   labs(x = '**Year of publication**', y = '**Number of papers**') + -->
-<!--   md_theme_minimal(base_size = 12) -->
-
-<!-- plot(publications_per_year_plot) -->
-
-<!-- ggsave(filename = 'publications_per_year.tiff',  -->
-<!--        plot = publications_per_year_plot,  -->
-<!--        device = 'tiff',  -->
-<!--        path = save_fig_here -->
-<!--        ) -->
-
-<!-- ggsave(filename = 'publications_per_year.tiff',  -->
-<!--        plot = publications_per_year_plot,  -->
-<!--        device = 'tiff',  -->
-<!--        path = save_thesis_fig_here -->
-<!--        ) -->
-
-<!-- ``` -->
-
-<!-- ## Collaboration patterns in time -->
-
-<!-- ### Number of studies per combinations of author affiliation types -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- #' Count by collaboration types and make a bar plot -->
-<!-- collab_types_count <- compact_data_with_citation_keys_no_fmd %>% -->
-<!--     count(author_affiliation_type, sort = TRUE) %>%  -->
-<!--     arrange(desc(n)) %>%  -->
-<!--     adorn_totals() %>%  -->
-<!--     adorn_percentages(denominator = 'col') %>%  -->
-<!--     adorn_pct_formatting() %>%  -->
-<!--     adorn_ns() -->
-
-<!-- knitr::kable(collab_types_count,  -->
-<!--              format = "latex", booktabs = TRUE,  -->
-<!--              caption = 'Number of publications per author affiliation type combination') %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))  -->
-<!-- ``` -->
-
-<!-- ### Proportions of the total publications per year by collaboration type -->
-
-<!-- ```{r echo=FALSE, fig.width=8} -->
-<!-- #' Count the number of each author affiliation type per year (including FMD) -->
-<!-- collap_types_by_year <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(year_aggreg,  -->
-<!--         collab_type,  -->
-<!--         name = 'total_publications' -->
-<!--         ) -->
-
-<!-- #The plot -->
-<!-- # Modify the x-axis labels to account for the lumping of the years from 2005 and below -->
-<!-- x_axis_labels <- as.character(seq(2005, 2020, 2)) -->
-
-<!-- x_axis_labels[1] <- '1970-2005' -->
-
-<!-- collab_proportions_plot <- ggplot(data = collap_types_by_year) +  -->
-<!--   geom_bar(aes(x = year_aggreg, -->
-<!--                y = total_publications, -->
-<!--                fill = collab_type -->
-<!--                ), -->
-<!--            color = 'black', -->
-<!--            stat = 'identity', -->
-<!--            position = position_fill(reverse = TRUE)#, -->
-<!--            #show.legend = FALSE -->
-<!--              ) + -->
-<!--   scale_fill_manual(values = c('tan3', 'turquoise2')) + -->
-<!--   scale_x_continuous(breaks = seq(2005, 2020, 2), -->
-<!--                      labels = x_axis_labels, -->
-<!--                      expand = c(0, 0) -->
-<!--                      ) + -->
-<!--   #coord_flip() + -->
-<!--   labs(#title = 'Publications per collaboration type over time', -->
-<!--        x = '**Year**', -->
-<!--        y = '**Proportion of total publications**', -->
-<!--        fill = '**Collaboration type**'  -->
-<!--          ) + -->
-<!--   theme(legend.position = 'none') + -->
-<!--  # md_theme_minimal(base_size = 16) #For Powerpoint -->
-<!--   md_theme_minimal(base_size = 12) -->
-
-<!-- plot(collab_proportions_plot) -->
-
-<!-- ggsave(filename = 'collab_proportions.tiff',  -->
-<!--        plot = collab_proportions_plot,  -->
-<!--        device = 'tiff',  -->
-<!--        path = save_fig_here -->
-<!--        ) -->
-
-<!-- ggsave(filename = 'collab_proportions.tiff',  -->
-<!--        plot = collab_proportions_plot,  -->
-<!--        device = 'tiff',  -->
-<!--        path = save_thesis_fig_here -->
-<!--        ) -->
-
-<!-- ``` -->
-
-<!-- ### Absolute number of publications per year by collaboration type -->
-
-<!-- ```{r} -->
-<!-- #' Count the number of each author affiliation type per year -->
-<!-- collabs_per_year <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(year_aggreg,  -->
-<!--         collab_type,  -->
-<!--         name = 'total_publications' -->
-<!--         )  -->
-
-<!-- collabs_per_year_plot <- ggplot(data = collabs_per_year,  -->
-<!--                                     aes(x = year_aggreg,  -->
-<!--                                         y = total_publications -->
-<!--                                         ),  -->
-<!--                                     color = 'black') +  -->
-<!--   geom_bar(aes(fill = collab_type),  -->
-<!--            stat = 'identity',  -->
-<!--            position = 'dodge' -->
-<!--            ) +  -->
-<!--   scale_fill_manual(values = c('tan3', 'turquoise2')) +  -->
-<!--   scale_x_continuous(breaks = seq(2005, 2020, 2), -->
-<!--                      labels = x_axis_labels, -->
-<!--                      expand = c(0, 0) -->
-<!--                      ) + -->
-<!--   labs(x = '**Year**',  -->
-<!--        y = '**Total publications**',  -->
-<!--        fill = 'Collaboration type' -->
-<!--        ) + -->
-<!--   md_theme_minimal(base_size = 12) + -->
-<!--   #md_theme_minimal(base_size = 16) + -->
-<!--   theme(legend.position = 'bottom')  -->
-
-<!-- plot(collabs_per_year_plot) -->
-
-<!-- ggsave(filename = 'total_collabs_per_year_plot.tiff', -->
-<!--        plot = collabs_per_year_plot,  -->
-<!--        device = 'tiff', -->
-<!--        path = save_fig_here -->
-<!--        ) -->
-
-<!-- ggsave(filename = 'total_collabs_per_year_plot.tiff', -->
-<!--        plot = collabs_per_year_plot,  -->
-<!--        device = 'tiff', -->
-<!--        path = save_thesis_fig_here -->
-<!--        ) -->
-
-<!-- ``` -->
-
-<!-- Even though non-academic collaborations increased over time, the share of total publications per year over time decreased. -->
-
-<!-- ## Collaboration patterns in geographic space -->
-
-## Collaboration types (aggregated)
-```{r}
-#' Count by collaboration types and make a bar plot
-studies_per_collab_type <- compact_data_with_citation_keys_no_fmd %>%
-    count(collab_type, sort = TRUE) %>% 
-    arrange(desc(n)) %>% 
-    adorn_totals() %>% 
-    adorn_percentages(denominator = 'col') %>% 
-    adorn_pct_formatting() %>% 
-    adorn_ns()
-
-knitr::kable(studies_per_collab_type, caption = 'Number of studies per collaboration type (Human VPDs)',
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-## Locations studied
-
-### Real versus hypothetical
-
-```{r}
-location_types_tally <- compact_data_with_citation_keys_no_fmd %>% 
-    separate_rows(country_studied, sep = ' ') %>%
-    distinct(title, country_studied, .keep_all = TRUE) %>%
-    mutate(location_type = ifelse(country_studied == 'none', 'none', 'real')) %>% 
-    count(location_type) %>% 
-  arrange(desc(n)) %>% 
-   adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns()
-
-knitr::kable(location_types_tally, 
-             caption = 'Number of studies per location type', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
-```
-
-### Larger than one country
-
-```{r}
-larger_geographies_tally <- compact_data_with_citation_keys_no_fmd %>% 
-    separate_rows(country_studied, sep = ' ') %>%
-    distinct(title, country_studied, .keep_all = TRUE) %>%
-    filter(country_studied %in% c('west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
-    count(country_studied) %>% 
-  arrange(desc(n)) %>% 
-   adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns()
-
-knitr::kable(larger_geographies_tally, caption = 'Number of studies per location larger than one country', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
-```
-
-### Countries studied
-
-```{r}
-countries_studied_by_count <- compact_data_with_citation_keys_no_fmd %>% 
-    separate_rows(country_studied, sep = ' ') %>%
-    distinct(title, country_studied, .keep_all = TRUE) %>% 
-    count(collab_type, country_studied, name = 'num_of_studies', sort = T)
-
-#'Modify the data frame to lump together all countries with less than some number of studies as 'other' and recalculate the percentage studied
-countries_studied_by_count_aggregated <- countries_studied_by_count %>% 
-  group_by(country_studied) %>%
-  summarise(num_of_studies = sum(num_of_studies),
-            .groups = 'drop'
-            ) %>% 
-  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
-  arrange(desc(num_of_studies)) %>% 
-  adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns() %>% 
-  ungroup()
-
-#Print the results
-knitr::kable(countries_studied_by_count_aggregated, 
-             caption = 'Number of studies per country', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'), font_size = 7)
-```
-
-### Continents studied
-
-```{r}
-continents_studied_by_count <- countries_studied_by_count %>% 
-  filter(country_studied %nin% c('none', 'northern_hemisphere', 'global')) %>% 
-  mutate(continent_studied = countrycode(country_studied, 
-                                          destination = 'continent',
-                                          origin = 'iso2c',
-                                          nomatch = NULL #if there is no match, keep the original
-                                          )
-         ) %>% 
-  mutate(continent_studied = str_to_lower(continent_studied)
-         ) %>% 
-  mutate(continent_studied = case_when(str_detect(continent_studied, 'asia') == T ~ 'asia', 
-                                         str_detect(continent_studied, 'africa') == T ~ 'africa', 
-                                         TRUE ~ continent_studied
-                                       )
-           ) %>% 
-  group_by(continent_studied) %>%
-  summarise(num_of_studies = sum(num_of_studies), 
-            .groups = 'drop'
-            ) %>% 
-  arrange(desc(num_of_studies)) %>% 
-  adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns()
-
-#Print the results
-knitr::kable(continents_studied_by_count, 
-             caption = 'Number of studies per continent', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-## Geographic connection of authors to the studied locations
-
-```{r}
-author_connectedness_top_5_countries <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(author_in_country_studied != 'not_applicable') %>% 
-  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
-separate_rows(country_studied,  sep = ' ') %>% 
-  group_by(collab_type) %>% 
-  count(country_studied, author_in_country_studied, sort = TRUE) %>% 
-  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
-  replace_na(list(yes = 0, no = 0)) %>% 
-  arrange(collab_type, desc(yes)) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('yes', 'no')) %>% 
-  adorn_pct_formatting(... = c('yes', 'no')) %>% 
-  adorn_ns(... = c('yes', 'no')) %>% 
-  ungroup()
-
-knitr::kable(author_connectedness_top_5_countries, caption = 'Studies with at least one author affiliation in the location studied', 
-             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position', 'repeat_header'), font_size = 8)
-```
-
-### Author affiliation in the studied location (overall)
-
-```{r}
-author_connectedness_to_location_aggreg <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(author_in_country_studied != 'not_applicable') %>% 
-  filter(country_studied %nin% c('other', 'none', 'northern_hemisphere', 'west_africa', 'global')) %>% 
-  count(collab_type, author_in_country_studied, sort = TRUE) %>% 
-  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
-  replace_na(list(yes = 0, no = 0)) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('yes', 'no')) %>% 
-  adorn_pct_formatting(... = c('yes', 'no')) %>% 
-  adorn_ns(... = c('yes', 'no'))
-
-knitr::kable(author_connectedness_to_location_aggreg, caption = 'At least one author with an affiliation in the studied location', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-<!-- ## Diseases studied per collab type -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- #count the number of unique diseases studied -->
-<!-- disease_studied_by_collab_type <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   separate_rows(disease,  sep = ' ') %>%  -->
-<!--   distinct(title, disease, .keep_all = TRUE) %>%  -->
-<!--   count(collab_type, disease, sort = TRUE) %>% -->
-<!--   pivot_wider(names_from = collab_type, values_from = n) %>%  -->
-<!--   replace_na(list(purely_academic = 0, mixed = 0)) %>%  -->
-<!--   adorn_totals(where = c('row', 'col')) %>%  -->
-<!--   adorn_percentages(... = c('purely_academic', 'mixed')) %>%  -->
-<!--   adorn_pct_formatting(... = c('purely_academic', 'mixed')) %>%  -->
-<!--   adorn_ns(... = c('purely_academic', 'mixed')) %>%  -->
-<!--   mutate(disease = str_to_sentence(str_replace(disease, '_', ' '))) %>%  -->
-<!--   arrange(desc(Total)) -->
-
-<!-- knitr::kable(disease_studied_by_collab_type, caption = 'Number of studies per disease and collaboration type', format = "latex", booktabs = TRUE) %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position')) -->
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- #tally the diseases by collaboration type -->
-<!-- disease_by_collab_type_long <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   separate_rows(disease,  sep = ' ') %>%  -->
-<!--   count(collab_type, disease, sort = TRUE)  -->
-
-<!-- disease_by_collab_type_plot <- ggplot(disease_by_collab_type_long) +  -->
-<!--   geom_bar(aes(x = reorder(disease, n),  -->
-<!--                y = n,  -->
-<!--                fill = collab_type -->
-<!--                ),  -->
-<!--            color = 'black', -->
-<!--            stat = 'identity', -->
-<!--            position = position_fill(reverse = TRUE) -->
-<!--            ) +  -->
-<!--   labs(x = '**Disease**', y = '**Number of studies**') +  -->
-<!--   coord_flip() + -->
-<!--   md_theme_minimal(base_size = 12) -->
-
-<!-- print(disease_by_collab_type_plot) -->
-<!-- ``` -->
-
-## Interventions
-
-### Types of interventions
-
-```{r}
-intervention_categories <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, intervention_type, sort = TRUE) %>% 
-  pivot_wider(names_from = intervention_type, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
-  adorn_pct_formatting(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
-  adorn_ns(... = c('no_vax', 'vax_combination_with_others', 'vax_single'))
-
-knitr::kable(intervention_categories, caption = 'Number of studies per intervention categories', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-### Impact of vaccination
-
-```{r}
-vax_impact_conclusions <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(intervention_type == 'vax_single') %>% 
-  count(collab_type, is_vax_effective, sort = T) %>% 
-  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
-    replace_na(list(yes = 0, n0 = 0, the_outcomes_were_inconclusive = 0)) %>% 
-  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
-  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
-  adorn_ns(... = c('yes', 'no', 'inconclusive'))
-
-#Print the results
-knitr::kable(vax_impact_conclusions, 
-             caption = 'Conclusions about impact of vaccination', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position')
-                                  )
-```
-
-```{r eval=FALSE}
-no_vax_modelled <- compact_data_with_citation_keys_no_fmd %>% 
-    separate_rows(disease,  sep = ' ') %>% 
-    filter(vax_modelled == 'no') %>% 
-    count(disease, sort = TRUE, name = 'num_of_studies') %>% 
-     adorn_totals(where = 'row') %>% 
-    adorn_percentages(denominator = 'col') %>% 
-    adorn_pct_formatting() %>% 
-    adorn_ns()
-
-knitr::kable(no_vax_modelled, caption = 'Number of studies per disease for which vaccination was not modelled', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-```{r eval=FALSE}
-vax_impact_by_disease <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(intervention_type == 'vax_single') %>% 
-  count(disease, is_vax_effective, sort = T) %>% 
-  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
-  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
-    replace_na(list(yes = 0, no = 0, inconclusive = 0)) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('yes', 'no', 'inconclusive')) %>% 
-  adorn_pct_formatting(... = c('yes', 'no', 'inconclusive')) %>% 
-  adorn_ns(... = c('yes', 'no', 'inconclusive'))
-
-#Print the results
-knitr::kable(vax_impact_by_disease, 
-             caption = 'Conclusions about impact of vaccination per disease', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-```{r eval=FALSE}
-no_vax_impact_by_disease_citation_table <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(intervention_type == 'vax_single', is_vax_effective %in% c('no', 'the_outcomes_were_inconclusive')) %>% 
-  select(title, disease, bibtexkey, publication_year, intervention_modelled, is_vax_effective)
-
-#Print the results
-# knitr::kable(no_vax_impact_by_disease_citation_table, 
-#              caption = 'Studies that did not find vaccination as most impactful'
-#              )
-
-write.xlsx(no_vax_impact_by_disease_citation_table, file = '../citation_tables/no_vax_impact_by_disease_citation_table.xlsx')
-```
-
-```{r eval=FALSE}
-vax_as_single_intervention_studies <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(intervention_type == 'vax_single') %>% 
-  select(title, disease, bibtexkey, publication_year, intervention_modelled)
-
-#Print the results
-# knitr::kable(no_vax_impact_by_disease_citation_table, 
-#              caption = 'Studies that did not find vaccination as most impactful'
-#              )
-
-write.xlsx(vax_as_single_intervention_studies, file = '../citation_tables/vax_as_single_intervention_studies.xlsx')
-```
-
-## Modelling objectives 
-<!-- We grouped studies into whether they assessed the impact of a future intervention strategy (prospective), a past intervention, or both (dual).  -->
-
-<!-- In general, there were more (73.2%; 167/228) studies about prospective intervention impact assessments than retrospective assessments (24.6%; 56/228), and the dual (2.2%; 5/228).
-A similar pattern was observed across the two collaboration types except that purely academic collaborations were more likely to perform the dual assessments.
--->
-
-<!-- In terms of the outbreak types, there was an approximately equal number of papers about real and hypothetical outbreaks overall, and there was no clear difference between the two collaborations.
--->
+### Number of FMD studies per collaboration types
 
 ```{r echo=FALSE}
-#count the number of studies per objective type
-modelling_objectives_count <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, objectives, name = 'num_of_studies') %>% 
-  pivot_wider(names_from = objectives, values_from = num_of_studies) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('both', 'future', 'past')) %>% 
-  adorn_pct_formatting(... = c('both', 'future', 'past')) %>% 
-  adorn_ns(... = c('both', 'future', 'past'))
-
-#Print a table of the results
-knitr::kable(modelling_objectives_count,
-             caption = 'Study objectives by collaboration type', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-## Outbreak types
-
-```{r echo=FALSE}
-#Outbreak types per collab type
-outbreak_types_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, outbreak_type, name = 'num_of_studies') %>% 
-  pivot_wider(names_from = outbreak_type, values_from = num_of_studies) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('hypothetical_outbreak', 'real_outbreak')) %>% 
-  adorn_pct_formatting(... = c('hypothetical_outbreak', 'real_outbreak')) %>% 
-  adorn_ns(... = c('hypothetical_outbreak', 'real_outbreak'))
-
-#Print a table of the results
-knitr::kable(outbreak_types_by_collab_type,
-             caption = 'outbreak types by collaboration type', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-```{r eval=FALSE}
-objectives_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
-  count(objectives, collab_type, name = 'num_of_studies', sort = TRUE) %>% 
-  pivot_wider(names_from = objectives, 
-              values_from = num_of_studies
-              ) %>% 
-  replace_na(list(future = 0, past = 0, both = 0)) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('future', 'past', 'both')) %>% 
-  adorn_pct_formatting(... = c('future', 'past', 'both')) %>% 
-  adorn_ns(... = c('future', 'past', 'both'))
-
-knitr::kable(objectives_by_collab_type, 
-             caption = 'Number of studies per objective by collaboration type', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-<!-- ## Model characteristics  -->
-
-## Individual heterogeneity: agent-based versus compartmental models
-
-```{r}
-individual_representation <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, individual_representation, sort = TRUE) %>% 
-  pivot_wider(names_from = individual_representation, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('compartments', 'agents', 'individuals_representation_other')) %>% 
-  adorn_pct_formatting(... = c('compartments', 'agents', 'individuals_representation_other')) %>% 
-  adorn_ns(... = c('compartments', 'agents', 'individuals_representation_other'))
-
-knitr::kable(individual_representation, caption = 'How individuals were represented', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-<!-- ### Individual representation by model structure -->
-<!-- ```{r} -->
-<!-- mod_structure_vs_individual_representation <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   group_by(collab_type) %>%  -->
-<!--   count(model_structure, individual_representation, sort = TRUE) %>%  -->
-<!--   pivot_wider(names_from = model_structure, values_from = n) %>%  -->
-<!--   adorn_totals(where = c('col', 'row')) -->
-
-<!-- knitr::kable(mod_structure_vs_individual_representation, caption = 'Model structure versus individual heterogeneity') -->
-<!-- ``` -->
-
-## Spatial heterogeneity
-
-```{r}
-space_representation <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, space_representation, sort = TRUE) %>% 
-  pivot_wider(names_from = space_representation, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no', 'yes')) %>% 
-  adorn_pct_formatting(... = c('no', 'yes')) %>% 
-  adorn_ns(... = c('no', 'yes'))
-
-knitr::kable(space_representation, caption = 'Was space explicitly represented in the model',
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-<!-- ### Spatial models by model structure -->
-<!-- ```{r} -->
-<!-- mod_structure_vs_space_representation <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   group_by(collab_type) %>%  -->
-<!--   count(model_structure, space_representation, sort = TRUE) %>%  -->
-<!--   pivot_wider(names_from = model_structure, values_from = n) %>%  -->
-<!--   adorn_totals(where = c('col', 'row')) -->
-
-<!-- knitr::kable(mod_structure_vs_space_representation, caption = 'Model structure versus spatial heterogeneity') -->
-<!-- ``` -->
-
-## Model dynamics: deterministic vs stochastic
-
-```{r}
-stochastic_vs_deterministic <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, model_structure) %>% 
-  pivot_wider(names_from = model_structure, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('both', 'deterministic', 'stochastic')) %>% 
-  adorn_pct_formatting(... = c('both', 'deterministic', 'stochastic')) %>% 
-  adorn_ns(... = c('both', 'deterministic', 'stochastic'))
-
-knitr::kable(stochastic_vs_deterministic, caption = 'Model dynamics (deterministic versus stochastic)', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-<!-- ## Modelling methods -->
-
-## Outcomes measured
-
-<!-- We tallied the overall top five outcomes most used between the two collaboration types.  -->
-
-<!-- The top five most commonly used outcomes, irrespective of collaboration type, were: final epidemic size, attack rate, timing of epidemic peak, cases averted, and outbreak duration. -->
-
-<!-- There was no difference in the two collaboration types as they were commonly used by both groups. -->
-
-```{r}
-outcomes_overall <- compact_data_with_citation_keys_no_fmd %>% 
-mutate(outcome_measured = str_trim(outcome_measured)) %>% 
-  separate_rows(outcome_measured, sep = ',') %>% 
-  group_by(collab_type, outcome_measured) %>% 
-  distinct(title, .keep_all = TRUE) %>% 
-  filter(outcome_measured %nin% c('outcome_other', '', 's')) %>% 
-  count(collab_type, outcome_measured, name = 'num_of_studies') %>% 
-  ungroup(outcome_measured) %>% 
-  arrange(desc(num_of_studies), .by_group = TRUE) %>% 
-  ungroup() %>% 
-  adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns()
-
-knitr::kable(outcomes_overall, caption = 'Model outcomes by collaboration type', 
-             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position', 'repeat_header'), font_size = 8)
-```
-
-```{r eval=FALSE}
-outcomes_tally_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
-  mutate(outcome_measured = str_trim(outcome_measured)) %>% 
-  separate_rows(outcome_measured, sep = ',') %>% 
-  group_by(outcome_measured) %>% 
-  distinct(title, .keep_all = TRUE) %>% 
-  ungroup(outcome_measured) %>% 
-  filter(outcome_measured %nin% c('outcome_other', '')) %>% 
-  group_by(collab_type) %>% 
-  count(outcome_measured) %>% 
-  arrange(desc(n), .by_group = TRUE) %>% 
-  # slice(1:6) %>% 
-  ungroup()
-
-# outcomes_tally_plot <- ggplot(data = outcomes_tally_by_collab_type, 
-#                               aes(x = reorder(outcome_measured, n), 
-#                                   y = n
-#                                   )
-#                               ) + 
-#   geom_bar(stat = 'identity') + 
-#   labs(x = '**Outcome**', y = '**Number of times used**') +
-#   coord_flip() +
-#   facet_wrap('collab_type') +
-#   md_theme_minimal()
-
-collab_type_labels <- c('purely_academic' = 'Purely academic', 
-                        'mixed' = 'Mixed'
-                        )
-
-outcomes_tally_plot <- ggplot(data = outcomes_tally_by_collab_type, 
-                              aes(label = outcome_measured, 
-                                  size = n
-                                  )
-                              ) + 
-  geom_text_wordcloud_area() +
-  scale_size_area(max_size = 10) + 
-  facet_wrap(~ collab_type, 
-             labeller = as_labeller(collab_type_labels),
-             strip.position = 'top'
-             ) +
-  #theme_minimal() + 
-  theme(strip.text = element_text(size = 15, face = 'bold'))
-
-print(outcomes_tally_plot)
-
-ggsave(filename = 'outcomes_tally_plot.tiff',
-       plot = outcomes_tally_plot, 
-       device = 'tiff',
-       path = save_fig_here
-       )
-
-ggsave(filename = 'outcomes_tally_plot.tiff',
-       plot = outcomes_tally_plot, 
-       device = 'tiff',
-       path = save_thesis_fig_here
-       )
-```
-
-<!-- ### Parametrization methods -->
-
-<!-- ```{r} -->
-<!-- #wide data for table -->
-<!-- model_parametrization_wide <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(collab_type, parametrization, sort = TRUE) %>%  -->
-<!--   pivot_wider(names_from = parametrization, values_from = n) %>%  -->
-<!--   adorn_totals(where = c('row', 'col')) %>%  -->
-<!--   adorn_percentages(... = -c('Total', 'collab_type')) %>%  -->
-<!--   adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%  -->
-<!--   adorn_ns(... = -c('Total', 'collab_type'))  -->
-
-<!-- #table -->
-<!-- knitr::kable(model_parametrization_wide, caption = 'How model parameters are obtained',  -->
-<!--              format = "latex", booktabs = TRUE) %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'scale_down', 'HOLD_position')) -->
-<!-- ``` -->
-
-<!-- ```{r eval=FALSE} -->
-<!-- #long data for plotting -->
-<!-- model_parametrization_long <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   group_by(collab_type) %>%  -->
-<!--   count(parametrization, sort = TRUE) -->
-
-<!-- #plotting -->
-<!-- ggplot(data = model_parametrization_long,  -->
-<!--        aes(fill = collab_type,  -->
-<!--            area = n,  -->
-<!--            label = parametrization, -->
-<!--            subgroup = parametrization -->
-<!--            ) -->
-<!--        ) +  -->
-<!--   geom_treemap() + -->
-<!--   geom_treemap_text(colour = "white", -->
-<!--                     place = "centre", -->
-<!--                     size = 15, -->
-<!--                     grow = TRUE -->
-<!--                     ) + -->
-<!--   md_theme_minimal(base_size = 12)  -->
-
-<!-- ``` -->
-
-<!-- ### Validation methods  -->
-
-<!-- ```{r} -->
-<!-- #wide data for table -->
-<!-- model_validation_wide <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(collab_type, validation, sort = TRUE) %>%  -->
-<!--   pivot_wider(names_from = validation, values_from = n) %>%  -->
-<!--   replace_na(list(none = 0,  -->
-<!--                   data = 0,  -->
-<!--                   another_model = 0,  -->
-<!--                   none_and_data = 0,  -->
-<!--                   data_and_another_model = 0 -->
-<!--                   ) -->
-<!--              ) %>%  -->
-<!--   adorn_totals(where = c('row', 'col')) %>%  -->
-<!--   adorn_percentages(... = -c('Total', 'collab_type')) %>%  -->
-<!--   adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%  -->
-<!--   adorn_ns(... = -c('Total', 'collab_type'))  -->
-
-<!-- #table -->
-<!-- knitr::kable(model_validation_wide, caption = 'How the model\'s performance is assessed',  -->
-<!--              format = "latex", booktabs = TRUE) %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'scale_down', 'HOLD_position')) -->
-<!-- ``` -->
-
-## Sensitivity analysis
-
-<!-- Less than half (46.5%; 106/228) of the total studies performed sensitivity analyses. There was no clear difference between the collaborations.  -->
-
-```{r eval=FALSE}
-mod_structure_vs_sensitivity_analysis <- compact_data_with_citation_keys_no_fmd %>% 
-  count(model_structure, sensitivity_analysis, sort = TRUE) %>% 
-  pivot_wider(names_from = sensitivity_analysis, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no', 'yes')) %>% 
-  adorn_pct_formatting(... = c('no', 'yes')) %>% 
-  adorn_ns(... = c('no', 'yes'))
-
-knitr::kable(mod_structure_vs_sensitivity_analysis, 'Sensitivity analysis in relation to model structure', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
-```
-
-```{r}
-sensitivity_analysis <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, sensitivity_analysis, sort = TRUE) %>% 
-  pivot_wider(names_from = sensitivity_analysis, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no', 'yes')) %>% 
-  adorn_pct_formatting(... = c('no', 'yes')) %>% 
-  adorn_ns(... = c('no', 'yes'))
-
-knitr::kable(sensitivity_analysis, caption = 'Sensitivity analysis', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
-```
-
-## Data use and data availability
-
-```{r}
-data_use_and_availability <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(data_used == 'yes') %>%
-  count(collab_type, data_available, sort = TRUE) %>% 
-  pivot_wider(names_from = data_available, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no', 'yes')) %>% 
-  adorn_pct_formatting(... = c('no', 'yes')) %>% 
-  adorn_ns(... = c('no', 'yes'))
-
-knitr::kable(data_use_and_availability, 
-             caption = 'Data accessibility', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
-```
-
-## Code availability
-
-```{r}
-code_availability <- compact_data_with_citation_keys_no_fmd %>% 
-  count(collab_type, simulation_code_available) %>% 
-  pivot_wider(names_from = simulation_code_available, values_from = n) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no', 'yes')) %>% 
-  adorn_pct_formatting(... = c('no', 'yes')) %>% 
-  adorn_ns(... = c('no', 'yes'))
-
-knitr::kable(code_availability, caption = 'Code availability', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-```{r eval=FALSE}
-papers_with_code_available <- compact_data_with_citation_keys_no_fmd %>% 
-    filter(simulation_code_available == 'yes') %>% 
-    as.data.frame()
-
-openxlsx::write.xlsx(papers_with_code_available, file = '../citation_tables/papers_with_code_available.xlsx')
-
-```
-
-# Foot and mouth disease (FMD)
-
-<!-- ## Collaboration patterns in time -->
-
-## Unique combinations of author affiliation types
-
-```{r}
 #' Count by collaboration types and make a bar plot
-author_affiliation_type_combos <- fmd_data %>%
+studies_per_collab_type <- fmd_data %>%
     count(author_affiliation_type, sort = TRUE) %>% 
     mutate(author_affiliation_type = as_factor(author_affiliation_type)) %>% 
-    arrange(desc(n)) %>% 
-    adorn_totals() %>% 
-    adorn_percentages(denominator = 'col') %>% 
-    adorn_pct_formatting() %>% 
-    adorn_ns()
+  arrange(desc(n))
 
-knitr::kable(author_affiliation_type_combos, caption = 'Number of studies by author affiliation type combination',
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-## Collaboration types (aggregated)
-
-```{r}
-#' Count by collaboration types and make a bar plot
-studies_per_collab_type <- fmd_data %>%
-    count(collab_type, sort = TRUE) %>% 
-    arrange(desc(n)) %>% 
-    adorn_totals() %>% 
-    adorn_percentages(denominator = 'col') %>% 
-    adorn_pct_formatting() %>% 
-    adorn_ns()
-
-knitr::kable(studies_per_collab_type, caption = 'Number of studies per collaboration type',
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+knitr::kable(studies_per_collab_type)
 ```
@@
 
-<!-- ## Collaboration patterns in geographic space -->
+## Collaboration patterns in geographic space
 
-## Geographic connection of authors to the studied locations 
+### Geographic connection of authors to the studied locations
+
+#### Top 5 countries
 ```{r}
@@
   replace_na(list(yes = 0, no = 0)) %>% 
-  arrange(collab_type, desc(yes)) %>% 
+  slice(n = 1:5) %>% 
   adorn_totals(where = c('row', 'col')) %>% 
@@
 
-knitr::kable(author_connectedness_to_location_fmd, caption = 'Studies with at least one author affiliation in the location studied', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+knitr::kable(author_connectedness_to_location_fmd)
 ```
-
-### Aggregated
+#### Aggregated
 
@@
 
-knitr::kable(author_connectedness_to_location_aggreg, 
-             caption = 'Studies with at least one author affiliation in the location studied', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+knitr::kable(author_connectedness_to_location_aggreg)
 ```
@@
   adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
-  adorn_pct_formatting(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
-  adorn_ns(... = c('no_vax', 'vax_combination_with_others', 'vax_single'))
+  adorn_percentages(... = c('no_vax', 'vax_alongside', 'vax_single')) %>% 
+  adorn_pct_formatting(... = c('no_vax', 'vax_alongside', 'vax_single')) %>% 
+  adorn_ns(... = c('no_vax', 'vax_alongside', 'vax_single'))
 
-knitr::kable(intervention_categories_fmd, caption = 'Number of studies per intervention type', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+knitr::kable(intervention_categories_fmd)
 ```
@@
 knitr::kable(fmd_vax_impact_conclusions, 
-             caption = 'Conclusions about impact of vaccination', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+             caption = 'Conclusions about impact of vaccination'
+             )
 ```
+
+# Secondary objectives of review
 
@@
 knitr::kable(modelling_objectives_fmd,
-             caption = 'Study objectives by collaboration type', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+             caption = 'Study objectives by collaboration type'
+             )
 ```
-
-<!-- ### Modelling objectives and outbreak type by collaboration types -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- objectives_and_outbreak_types_fmd <- fmd_data %>%  -->
-<!--   count(objectives, outbreak_type, name = 'num_of_studies', sort = TRUE) %>%  -->
-<!--   pivot_wider(names_from = objectives,  -->
-<!--               values_from = num_of_studies -->
-<!--               ) %>%  -->
-<!--   replace_na(list(future = 0, past = 0, both = 0)) %>%  -->
-<!--   adorn_totals(where = c('row', 'col')) %>%  -->
-<!--   adorn_percentages(... = c('future', 'past')) %>%  -->
-<!--   adorn_pct_formatting(... = c('future', 'past')) %>%  -->
-<!--   adorn_ns(... = c('future', 'past'))  -->
-
-<!-- knitr::kable(objectives_and_outbreak_types_fmd,  -->
-<!--              caption = 'Number of studies per objective and outbreak type',  -->
-<!--              format = "latex", booktabs = TRUE) %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position')) -->
-<!-- ``` -->
 
@@
 knitr::kable(outbreak_types_by_collab_type_fmd,
-             caption = 'Study objectives by collaboration type', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+             caption = 'Study objectives by collaboration type'
+             )
 ```
 
-<!-- ## Model characteristics  -->
+## Modelling objectives and outbreak type by collaboration types
 
-## Individual heterogeneity: agent-based versus compartmental models
+```{r echo=FALSE}
+objectives_and_outbreak_types_fmd <- fmd_data %>% 
+  count(objectives, outbreak_type, name = 'num_of_studies', sort = TRUE) %>% 
+  pivot_wider(names_from = objectives, 
+              values_from = num_of_studies
+              ) %>% 
+  replace_na(list(future = 0, past = 0, both = 0)) %>% 
+  adorn_totals(where = c('row', 'col')) %>% 
+  adorn_percentages(... = c('future', 'past')) %>% 
+  adorn_pct_formatting(... = c('future', 'past')) %>% 
+  adorn_ns(... = c('future', 'past'))
+
+knitr::kable(objectives_and_outbreak_types_fmd, 
+             caption = 'Number of studies per objective and outbreak type'
+             ) 
+```
+
+## Model characteristics
+
+### Individual heterogeneity: agent-based versus compartmental models
 
@@
 
-knitr::kable(individual_representation_fmd, 
-             caption = 'How individuals are represented', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+knitr::kable(individual_representation_fmd)
 ```
 
-## Spatial heterogeneity
+### Spatial heterogeneity
 
@@
 
-knitr::kable(space_representation_fmd, caption = 'Models with spatial structure', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+knitr::kable(space_representation_fmd, caption = 'Spatial models')
 ```
 
-## Model dynamics: deterministic vs stochastic
+### Model dynamics: deterministic vs stochastic
 
@@
 knitr::kable(stochastic_vs_deterministic_fmd, 
-             caption = 'Model dynamics (deterministic versus stochastic)', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
+             caption = 'Model dynamics (deterministic versus stochastic)'
+             )
 ```
 
-<!-- ## Modelling methods -->
-
-## Outcomes measured
+## Modelling methods
+### Outcomes measured
 ```{r}
@@
   separate_rows(outcome_measured, sep = ',') %>% 
-  group_by(collab_type, outcome_measured) %>% 
+  group_by(outcome_measured) %>% 
   distinct(title, .keep_all = TRUE) %>% 
+  ungroup(outcome_measured) %>% 
   filter(outcome_measured %nin% c('outcome_other', '')) %>% 
-  count(collab_type, outcome_measured, name = 'num_of_studies') %>% 
-  ungroup(outcome_measured) %>% 
-  arrange(desc(num_of_studies), .by_group = TRUE) %>% 
-  ungroup() %>% 
-  adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns()
+  group_by(collab_type) %>% 
+  count(outcome_measured) %>% 
+  arrange(desc(n), .by_group = TRUE) %>% 
+  slice(1:6) %>% 
+  ungroup()
 
-knitr::kable(outcomes_tally_by_collab_type, 
-             caption = 'Model outcomes by collaboration type', 
-             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position', 'repeat_header'))
-```
-
-```{r eval=FALSE}
 collab_type_labels <- c('purely_academic' = 'Purely academic', 
@@
 #save the plot
-ggsave(filename = 'outcomes_tally_fmd_plot.tiff',
+ggsave(filename = 'outcomes_tally_fmd_plot.png',
        plot = outcomes_tally_plot, 
-       device = 'tiff',
+       device = 'png',
        path = save_fig_here
        )
+
+print(outcomes_tally_plot)
 ```
 
-## Parametrization methods
+### Parametrization methods
 
@@
 knitr::kable(model_parametrization_fmd_wide, 
-             caption = 'Model parametrization methods', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'scale_down',  'HOLD_position'))
+             caption = 'How model parameters are obtained'
+             )
 ```
 
-## Validation methods
+### Validation methods
 
@@
 knitr::kable(model_validation_fmd_wide, 
-             caption = 'Model validation methods', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped',  'HOLD_position'))
+             caption = 'How the model\'s performance is assessed'
+             )
 ```
 
-## Sensitivity analysis
+### Sensitivity analysis
 
@@
 
-knitr::kable(sensitivity_analysis_fmd, caption = 'Sensitivity analysis', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped',  'HOLD_position'))
+knitr::kable(sensitivity_analysis_fmd)
 
@@
 
-## Data use and data availability
+### Data use and data availability
 
@@
 knitr::kable(data_use_and_availability_fmd, 
-             caption = 'Data accessibility', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+             caption = 'How often is the data used available for public access')
 
@@
 
-## Code availability
+### Code availability
 
@@
 
-knitr::kable(code_availability_fmd, caption = 'Code availability', 
-             format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+knitr::kable(code_availability_fmd)
 ```

### 2023-05-15 analyses/scripts/orv_models_review_data_cleaning.R
Replaced the base pipes with the dplyr pipe

@@ -56,13 +56,13 @@ review_data_compact_cleaning_step2 <- review_data_compact_cleaning_step1 %>%
   mutate(
     country_studied_other =
       str_replace_all(country_studied_other, " ", "_")
-  ) |>
+  ) %>%
   #' make titles lower case
   mutate(
     title = str_to_lower(paper_title),
     disease = str_to_lower(disease),
     country_studied_other = str_to_lower(country_studied_other)
-  ) |>
+  ) %>%
   #' contract long entries
   mutate(
     objectives = case_when(
@@ -90,7 +90,7 @@ review_data_compact_cleaning_step2 <- review_data_compact_cleaning_step1 %>%
         "not_applicable",
         data_available
       )
-  ) |>
+  ) %>%
   mutate(
     country_studied = case_when(
       country_studied == "none" ~ "none",
@@ -100,7 +100,7 @@ review_data_compact_cleaning_step2 <- review_data_compact_cleaning_step1 %>%
         country_studied != "multiple" &
         country_studied != "other" ~ country_studied
     )
-  ) |>
+  ) %>%
   mutate(
     intervention_modelled = str_replace_all(
       intervention_modelled,
@@ -112,7 +112,7 @@ review_data_compact_cleaning_step2 <- review_data_compact_cleaning_step1 %>%
       " ",
       ","
     )
-  ) |>
+  ) %>%
   # make some columns factors
   mutate(across(
     .cols = c(
@@ -253,7 +253,7 @@ compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
     ) %>%
   mutate(
     author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + ')
-    ) |>
+    ) %>%
   mutate(
     author_in_country_studied = if_else(author_in_country_studied == 'NA',
                                         'not_applicable',
@@ -264,7 +264,7 @@ compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
   mutate(year_aggreg = as.numeric(
     ifelse(publication_year < 2006, 2005, publication_year)
     )
-    ) |>
+    ) %>%
   mutate(
   collab_type = as_factor(
     if_else(author_affiliation_type == 'academic_institutions',
@@ -273,7 +273,7 @@ compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
     ),
   purely_academic_collab = if_else(
     author_affiliation_type == 'academic_institutions', TRUE, FALSE)
-  ) |>
+  ) %>%
[…]

### 2023-05-15 analyses/scripts/orv_models_review_data_cleaning.R
Replaced native pipe with dplyr pipe

@@ -70,7 +70,7 @@ review_data_compact_cleaning_step2 <- review_data_compact_cleaning_step1 %>%
       objectives == "assess_impact_past" ~ "past",
       objectives == "assess_impact_past assess_impact_future" ~ "both"
     )
-  ) |>
+  ) %>%
   # if entry is NA, change it to 'not_applicable' for easy analysis in R
   mutate(
     author_in_country_studied =

### 2023-05-15 analyses/scripts/orv_models_review_data_cleaning.R
Now using here package for managing paths

@@ -1,26 +1,23 @@
 suppressPackageStartupMessages({
-  library("tidyverse")
-  library("janitor")
-  library("bib2df")
-  library("xlsx")
+  library(tidyverse)
+  library(janitor)
+  library(bib2df)
+  library(xlsx)
+  library(here)
 })
 
-# Define global variables
-data_dir <- "./data"
-
+# I/O paths
+data_dir <- "analyses/data"
 
 # load the review data extraction results and remove extraneous variables
 review_data_compact <- read_delim(
-  file.path(
-    data_dir,
-    "orv_review_compact_data.csv"
-  ),
+  here(data_dir, "orv_review_compact_data.csv"),
   delim = ";",
   na = c("", "NA")
 )
 
 # load the citation data for merging
-citation_data <- bib2df(file.path(data_dir, "included_studies.bib"),
+citation_data <- bib2df(here(data_dir, "included_studies.bib"),
   separate_names = FALSE
 ) %>%
   mutate(year = as.numeric(YEAR))
@@ -173,7 +170,7 @@ review_data_compact_cleaned <- review_data_compact_cleaning_step3 %>%
 
 # save the cleaned compact dataset
 saveRDS(review_data_compact_cleaned,
-  file = file.path(data_dir, "review_data_compact_cleaned.rds")
+  file = here(data_dir, "review_data_compact_cleaned.rds")
 )
 
 
@@ -195,7 +192,7 @@ review_data_wide_to_long <- review_data_compact_cleaned %>%
 
 # save the cleaned data
 saveRDS(review_data_wide_to_long,
-  file = file.path(data_dir, "review_data_long_cleaned.rds")
+  file = here(data_dir, "review_data_long_cleaned.rds")
 )
 
 # Clean the citation database

### 2023-05-15 analyses/scripts/full_data_extraction_citation_table.Rmd
Now using the here package to manage paths

@@
 #' load packages
+suppressPackageStartupMessages({
   library("tidyverse")
@@
   library("knitr")
+  library("here")
+  library("kableExtra")
+  })
 
@@
 ```{r}
-#create a folder for storing the manuscript figures
+here::i_am("analyses/scripts/full_data_extraction_citation_table.Rmd")
+#I/O paths
+figs_dir <- "analyses/figs"
+data_dir <- "analyses/data"
+scripts_dir <- "analyses/scripts"
 
-if (!dir.exists("../figs_manuscript")) {
-  dir.create("../figs_manuscript",
+# Create a folder for storing the figures
+
+if (!dir.exists(here::here(figs_dir))) {
+  dir.create(here::here(figs_dir),
     showWarnings = TRUE
@@
 }
-
-#save figures in this folder
-save_fig_here <- '../figs_manuscript'
 ```
 
-```{r}
-# Load the cleaned data 
-long_data <- read_rds('../data/review_data_long_cleaned.rds')
+```{r load_data}
+#' re-run the data cleaning step, in case something has changed 
+#' TO DO: Use GNU make for this
 
-#The cleaned data without citations
-compact_data_init <- read_rds('../data/review_data_compact_cleaned.rds')
-```
+source(here::here(scripts_dir, "orv_models_review_data_cleaning.R"))
 
-```{r}
-# Load the data with citations
-compact_data_with_citation_keys_init <- read_rds("../data/compact_data_with_citation_keys_cleaned.rds")
-
-# Clean various variables
-compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>%
-  mutate(vax_modelled = ifelse(str_detect(intervention_modelled, "vaccination"),
-    "yes",
-    "no"
-  ), 
-  intervention_type = case_when(
-    vax_modelled == "no" & vax_modelled_with_non_vax == "no" ~ "no_vax", # Vaccination was not modelled
-    vax_modelled == "yes" & vax_modelled_with_non_vax == "no" ~ "vax_combination_with_others", # when vax was modelled but not for comparison as a single intervention
-    vax_modelled == "yes" & vax_modelled_with_non_vax == "yes" ~ "vax_single", # when vax was modelled as a single intervention
-  ),
-    publication_year = as.numeric(publication_year),
-    author_in_country_studied = as.character(author_in_country_studied)
-  ) %>%
-  arrange(publication_year) %>%
-  mutate(
-    author_affiliation_type = str_replace_all(author_affiliation_type, " ", " + "),
-    author_in_country_studied = if_else(author_in_country_studied == "NA", "not_applicable",
-      author_in_country_studied
-    ),
-    year_aggreg = as.numeric(ifelse(publication_year < 2006, # An approach to aggregate the years before 2006 into one group because of the low number of papers
-      2005,
-      publication_year
-    )),
-    collab_type = as_factor(if_else(author_affiliation_type == "academic_institutions",
-      "purely_academic",
-      "mixed"
+# The data with citations 
+compact_data_with_citation_keys <- read_rds(
+  here::here(data_dir, 'compact_data_with_citation_keys_cleaned.rds'
   ))
-  )
-```
-
-```{r}
-# Data dictionaries
-
-# parametrization description dictionary
-parametrization_str_replacements <- c(
-  "values_from_literature" = "literature",
-  "values_from_guess_and_expert_opion" = "expert_opinion",
-  "values_fitted_to_ts" = "fitted",
-  " " = " and " # replace space with 'and' to make it more readable
-)
-
-# validation description dictionary
-validation_str_replacements <- c(
-  "compared_with_data" = "data",
-  "compared_with_other_model_output" = "another_model",
-  "model_not_validated" = "none",
-  " " = "_and_"
-)
-
-# Clean the parametrization and validation variables with dictionary
-compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
-  mutate(parametrization = str_replace_all(
-    parametrization,
-    parametrization_str_replacements
-  )) %>%
-  mutate(validation = str_replace_all(
-    validation,
-    validation_str_replacements
-  )) %>%
-  mutate(model_structure = str_replace(model_structure, 
-                                       "deterministic stochastic", 
-                                       "both"
-                                       )
-         )
 ```

### 2023-05-15 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Now using the here package to manage paths

@@
 #' load packages
+suppressPackageStartupMessages({
   library('tidyverse')
@@
   library('ggwordcloud')
+  library('here')
+  })
 
@@
 ```{r}
-#directories
-# Figures
-figs_dir <- "../figs_manuscript"
-
-# Create a folder for storing the manuscript figures if it doesn't exist
-if (!dir.exists('../figs_manuscript'))
-    {
-    dir.create('../figs_manuscript', 
-               showWarnings = FALSE)
+#I/O directories
+figs_dir <- "analyses/figs"
+data_dir <- "analyses/data"
+scripts_dir <- "analyses/scripts"
+
+here::i_am("analyses/scripts/orv_sys_rev_data_analysis.Rmd")
+# Create a folder for storing the figures
+
+if (!dir.exists(here::here(figs_dir))) {
+  dir.create(here::here(figs_dir),
+    showWarnings = TRUE
+  )
 }
-
-data_dir <- "../data"
 ```
@@
 
-source("./orv_models_review_data_cleaning.R")
+source(here::here(scripts_dir, "orv_models_review_data_cleaning.R"))
 
 # Load the cleaned data 
-long_data <- read_rds(file.path(data_dir, "review_data_long_cleaned.rds"))
+long_data <- read_rds(here::here(data_dir, "review_data_long_cleaned.rds"))
 
@@
 compact_data_init <- read_rds(
-  file.path(data_dir, "review_data_compact_cleaned.rds")
+  here::here(data_dir, "review_data_compact_cleaned.rds")
   )
@@
 compact_data_with_citation_keys <- read_rds(
-  '../data/compact_data_with_citation_keys_cleaned.rds'
-  )
+  here::here(data_dir, 'compact_data_with_citation_keys_cleaned.rds'))
 

### 2023-05-15 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Remove word_output
Styled the script

@@
 output:
-  # word_document:
-  #   toc: yes
   pdf_document:
@@
              caption = 'Number of studies per collaboration type (Human VPDs)',
-             format = "latex", booktabs = TRUE) %>% 
+             format = "latex", 
+             booktabs = TRUE
+             ) %>% 
         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))

### 2023-05-15 analyses/scripts/full_data_extraction_citation_table.Rmd
Finally, a working version of the supplementary tables

@@
 ---
+title: "Supplementary material"
 output:
   pdf_document:
-    df_print: kable
-    latex_engine: xelatex
-    keep_tex: true
+    fig_crop: no
 ---
 ```{r setup, include=FALSE}
-# options(kableExtra.auto_format = FALSE,
-#         knitr.table.format = "latex"
-#         )
+knitr::opts_chunk$set(echo = FALSE, 
+                      dev = 'png', 
+                      out.height = "\\textheight",  
+                      out.width = "\\textwidth", 
+                      message = FALSE, 
+                      warning = FALSE
+                      )
 
-knitr::opts_chunk$set(echo = FALSE, 
-                      include = FALSE,
-                      # dev = 'jpeg', 
-                      fig.width = 8, 
-                      fig.height = 6, 
-                      message = FALSE,
-                      warning = FALSE,
-                      cache = FALSE
-                      )
+options(kableExtra.auto_format = FALSE)
 ```
@@
             ) %>% 
-     arrange(desc(publication_year))
+     arrange(desc(publication_year)) %>% 
+  mutate(num = seq_len(nrow(.))) %>% 
+  relocate(num, .before = "title")
+
+# Shorten names
+
+names_dict <- c(year = "publication_year",
+                affiliation_type = "author_affiliation_type",
+                academic_collab = "purely_academic_collab",
+                location = "country_studied",
+                interventions = "intervention_modelled"
+                )
+
+ final_citation_table <-  final_citation_table %>% 
+  rename(names_dict)
 ```
 
-```{r}
+```{r helper_functions}
+#' Function to print the table caption using a template 
+#' It extracts the column names and combines them into a comma-separated
+#' list and attaches a preceding sentence, which defaults to 
+#' ""List of included studies by:""
+make_table_caption <- function(df, preceding_sentence = "List of included studies by:"){
+  paste(preceding_sentence, paste(names(df)[-c(1)], collapse = ", "))
+} 
+```
+The following table contains information on the data extracted from
+each of the included studies.
+
+Technical note: Due to the large number of 
+rows, the table could not be printed in one go and was instead printed a few columns 
+at a time. In actual fact, it is just a repetition of the title column along with
+the presented columns.
+
+```{r cols_1_to_6}
 # Make a neat table of papers from columns 1(title)-5
-final_citation_table %>% 
-    select(1:5) %>% 
-    kable()
+cols_1_to_6 <- final_citation_table %>% 
+    select(1:6)
 
-# booktabs = TRUE,
-#       longtable = FALSE#,
-#       # caption = 'Extracted data per paper: publication_year, author_affiliation_type, country_studied, author_in_country_studied.'
-#          ) %>%
-#     kable_styling(latex_options = c('striped',
-#                                     'scale_down',
-#                                     'hold_position',
-#                                     'repeat_header'
-#                                     )
-#                   ) %>%
-#     column_spec(column = c(1, 3), width = "5cm") #%>%
-    # landscape()
+knitr::kable(cols_1_to_6, 
+    format = "latex", 
+    booktabs = TRUE,
+    longtable = TRUE
+    # caption = make_table_caption(cols_1_to_6)
+    ) %>% 
+  kableExtra::kable_styling(latex_options = c("striped", 
+                                  "scale_down", 
+                                  "hold_position", 
+                                  "repeat_header"),
+                            font_size = 9
+                ) %>% 
+  kableExtra::column_spec(column = c(2), width = "4cm") %>% 
+  kableExtra::landscape() 
 ```
 
-<!--  ```{r} -->
-<!-- # Make a neat table of papers from columns 1 (title), and 6-10  -->
-<!-- final_citation_table %>% -->
-<!--   select(c(1, 6:10)) %>% -->
-<!--   kable( -->
-<!--     booktabs = TRUE, -->
-<!--     longtable = FALSE, -->
-<!--     caption = "Extracted data per paper: disease, objectives, individual_representation, space_representation, model_structure." -->
-<!--   ) %>% -->
-<!--   kable_styling(latex_options = c("striped",  -->
-<!--                                   "scale_down",  -->
-<!--                                   "hold_position",  -->
-<!--                                   "repeat_header" -->
-<!--                                   ) -->
-<!--                 ) %>% -->
-<!--   column_spec(column = c(1), width = "5cm") %>% -->
-<!--   landscape() -->
-<!-- ``` -->
+```{r cols_7_to_10}
+# Make a neat table of papers from columns 1, 2 (title), and 7-10
+cols_7_to_10 <- final_citation_table %>% 
+    select(c(1, 2, 7:10))
 
-<!-- ```{r} -->
-<!-- # Make a neat table of papers from columns 1 (title) and 11-15  -->
-<!-- final_citation_table %>% -->
-<!--   select(1, 11:15) %>% -->
-<!--   kable( -->
-<!--     longtable = FALSE, -->
-<!--     caption = "Extracted data per paper: parametrization, validation, outbreak_type, intervention_modelled, vax_modelled_with_non_vax." -->
-<!--   ) %>% -->
-<!--   kable_styling(latex_options = c("striped",  -->
-<!--                                   "scale_down",  -->
-<!--                                   "hold_position",  -->
-<!--                                   "repeat_header" -->
-<!--                                   ) -->
-<!--                 ) %>% -->
-<!--   column_spec(column = c(1, 2, 5), width = "4cm") %>% -->
-<!--   landscape() -->
-<!-- ``` -->
+knitr::kable(cols_7_to_10, 
+    format = "latex", 
+    booktabs = TRUE,
+    longtable = TRUE
+    # caption = make_table_caption(cols_7_to_10)
+    ) %>% 
+  kableExtra::kable_styling(latex_options = c("striped", 
+                                  "scale_down", 
+                                  "hold_position", 
+                                  "repeat_header"),
+                            font_size = 9
+                ) %>% 
+  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
+  kableExtra::landscape() 
+```
 
-<!--  ```{r} -->
-<!-- # Make a neat table of papers from columns 1 (title) and 16-22 -->
-<!-- final_citation_table %>% -->
-<!--   select(1, 16:22) %>% -->
-<!--   kable( -->
-<!--     booktabs = TRUE, -->
-<!--     longtable = FALSE, -->
-<!--     caption = "Extracted data per paper: is_vax_effective, outcome_measured, sensitivity_analysis, data_used, data_available, simulation_code_available, vax_modelled." -->
-<!--   ) %>% -->
-<!--   kable_styling(latex_options = c("striped", -->
-<!--                                   "scale_down",  -->
-<!--                                   "hold_position",  -->
-<!--                                   "repeat_header" -->
-<!--                                   ) -->
-<!--                 ) %>% -->
-<!--   column_spec(column = c(1, 3), width = "5cm") %>% -->
-<!--   landscape() -->
-<!-- ``` -->
+```{r cols_11_to_14}
+# Make a neat table of papers from columns 1, 2 (title) and 11-15
+cols_11_to_14 <- final_citation_table %>% 
+    select(c(1, 2, 11:14))
+
+knitr::kable(cols_11_to_14, 
+    format = "latex", 
+    booktabs = TRUE,
+    longtable = TRUE
+    # caption = make_table_caption(cols_11_to_14)
+    ) %>% 
+  kableExtra::kable_styling(latex_options = c("striped", 
+                                  "scale_down", 
+                                  "hold_position", 
+                                  "repeat_header"),
+                            font_size = 9
+                ) %>% 
+  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
+  kableExtra::landscape() 
+```
+
+```{r cols_15_to_16}
+# Make a neat table of papers from columns 1, 2 (title) and 15-18
+cols_15_to_16 <- final_citation_table %>% 
+    select(c(1, 2, 15:16))
+
+knitr::kable(cols_15_to_16, 
+    format = "latex", 
+    booktabs = TRUE,
+    longtable = TRUE
+    ) %>% 
+  kableExtra::kable_styling(latex_options = c("striped", 
+                                  "scale_down", 
+                                  "hold_position", 
+                                  "repeat_header"),
+                            font_size = 9
+                ) %>% 
+  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
+  kableExtra::landscape() 
+```
+
+```{r cols_17_to_18}
+# Make a neat table of papers from columns 1, 2 (title) and 19-24
+cols_17_to_18 <- final_citation_table %>% 
+    select(c(1, 2, 17:18))
+
+knitr::kable(cols_17_to_18, 
+    format = "latex", 
+    booktabs = TRUE,
+    longtable = TRUE
+    # caption = make_table_caption(cols_1_to_6)
+    ) %>% 
+  kableExtra::kable_styling(latex_options = c("striped", 
+                                  "scale_down", 
+                                  "hold_position", 
+                                  "repeat_header"),
+                            font_size = 9
+                ) %>% 
+  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
+  kableExtra::landscape() 
+```
+
+```{r cols_19_to_20}
+# Make a neat table of papers from columns 1, 2 (title) and 19-24
+cols_19_to_20 <- final_citation_table %>% 
+    select(c(1, 2, 19:20))
+
+knitr::kable(cols_19_to_20, 
+    format = "latex", 
+    booktabs = TRUE,
+    longtable = TRUE
+    # caption = make_table_caption(cols_1_to_6)
+    ) %>% 
+  kableExtra::kable_styling(latex_options = c("striped", 
+                                  "scale_down", 
+                                  "hold_position", 
+                                  "repeat_header"),
+                            font_size = 9
+                ) %>% 
+  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
+  kableExtra::landscape() 
+```
+
+```{r cols_21_to_22}
+# Make a neat table of papers from columns 1, 2 (title) and 19-24
+cols_21_to_22 <- final_citation_table %>% 
+    select(c(1, 2, 21:22))
+
+knitr::kable(cols_21_to_22, 
+    format = "latex", 
+    booktabs = TRUE,
+    longtable = TRUE
+    ) %>% 
+  kableExtra::kable_styling(latex_options = c("striped", 
+                                  "scale_down", 
+                                  "hold_position", 
+                                  "repeat_header"),
+                            font_size = 9
+                ) %>% 
+  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
+  kableExtra::landscape() 
+```
+
+```{r cols_23_to_24}
+# Make a neat table of papers from columns 1, 2 (title) and 19-24
+cols_23_to_24 <- final_citation_table %>% 
+    select(c(1, 2, 23:24))
+
+knitr::kable(cols_23_to_24, 
+     format = "latex",
+     booktabs = TRUE,
+     longtable = TRUE
+   ) %>% 
+  kableExtra::kable_styling(latex_options = c("striped", 
+                                  "scale_down", 
+                                  "hold_position", 
+                                  "repeat_header"),
+                            font_size = 9
+                ) %>% 
+  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
+  kableExtra::landscape() 
+```

### 2023-05-20 analyses/scripts/orv_models_review_data_cleaning.R
modified script to work from terminal

@@ -1,3 +1,17 @@
+# I/O paths
+data_dir <- "data"
+
+.args <- if (interactive()) {
+  c(
+    file.path(data_dir, "orv_review_compact_data.csv"),
+    file.path(data_dir, "included_studies.bib"),
+    file.path(data_dir, "compact_data_with_citation_keys_cleaned.rds")
+  )
+} else {
+  commandArgs(trailingOnly = TRUE)
+}
+
+
 suppressPackageStartupMessages({
   library(tidyverse)
   library(janitor)
@@ -6,18 +20,15 @@ suppressPackageStartupMessages({
   library(here)
 })
 
-# I/O paths
-data_dir <- "analyses/data"
-
 # load the review data extraction results and remove extraneous variables
 review_data_compact <- read_delim(
-  here(data_dir, "orv_review_compact_data.csv"),
+  here(.args[1]),
   delim = ";",
   na = c("", "NA")
 )
 
 # load the citation data for merging
-citation_data <- bib2df(here(data_dir, "included_studies.bib"),
+citation_data <- bib2df(here(.args[2]),
   separate_names = FALSE
 ) %>%
   mutate(year = as.numeric(YEAR))
@@ -316,11 +327,6 @@ compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
 
 
 # save the cleaned data
-saveRDS(compact_data_with_citation_keys,
-  file = here(data_dir, "compact_data_with_citation_keys_cleaned.rds")
-)
+saveRDS(compact_data_with_citation_keys, tail(.args, 1))
 
-openxlsx::write.xlsx(x = compact_data_with_citation_keys,
-                     file = here(data_dir, "included_studies_database.xlsx")
-                     )
 

### 2023-05-21 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Adapted the scripts to use use the command line

@@
 ```{r}
-#I/O directories
-figs_dir <- "analyses/figs"
-data_dir <- "analyses/data"
-scripts_dir <- "analyses/scripts"
-
-here::i_am("analyses/scripts/orv_sys_rev_data_analysis.Rmd")
+#' if sourced, re-run the data cleaning step, in case something has changed 
+#' else if through the terminal, use the arguments passed through the
+#' commandline/make
+if (is_null(getOption('knitr.in.progress'))) {
+source(here::here('./scripts/orv_models_review_data_cleaning.R'))
+args <- c(
+  here::here("data", "review_data_long_cleaned.rds"),
+  here::here("data", "review_data_compact_cleaned.rds"),
+  here::here("data", "compact_data_with_citation_keys_cleaned.rds")
+  )
+} else {
+ args <- commandArgs(trailingOnly = TRUE)
+}
+```
+
+```{r}
 # Create a folder for storing the figures
@@
 ```{r}
-#' re-run the data cleaning step, in case something has changed 
-#' TO DO: Use GNU make for this
-
-source(here::here(scripts_dir, "orv_models_review_data_cleaning.R"))
-
 # Load the cleaned data 
-long_data <- read_rds(here::here(data_dir, "review_data_long_cleaned.rds"))
+long_data <- read_rds(args[1])
 
 #The cleaned data without citations
-compact_data_init <- read_rds(
-  here::here(data_dir, "review_data_compact_cleaned.rds")
-  )
+compact_data_init <- read_rds(args[2])
 
 # The data with citations 
-compact_data_with_citation_keys <- read_rds(
-  here::here(data_dir, 'compact_data_with_citation_keys_cleaned.rds'))
+compact_data_with_citation_keys <- read_rds(args[3])
 

### 2023-05-21 analyses/scripts/orv_models_review_data_cleaning.R

@@ -1,11 +1,11 @@
 # I/O paths
-data_dir <- "data"
+data_dir <- "./data"
 
 .args <- if (interactive()) {
   c(
-    file.path(data_dir, "orv_review_compact_data.csv"),
-    file.path(data_dir, "included_studies.bib"),
-    file.path(data_dir, "compact_data_with_citation_keys_cleaned.rds")
+    here::here(data_dir, "orv_review_compact_data.csv"),
+    here::here(data_dir, "included_studies.bib"),
+    here::here(data_dir, "compact_data_with_citation_keys_cleaned.rds")
   )
 } else {
   commandArgs(trailingOnly = TRUE)

### 2023-05-23 analyses/scripts/orv_models_review_data_cleaning.R
removed commented out code for viewing the data

@@ -163,12 +163,6 @@ review_data_compact_cleaning_step3 <- review_data_compact_cleaning_step2 %>%
     )
   )
 
-# View(review_data_compact_cleaning_step3)
-
-
-
-# View(review_data_compact_cleaning_step3)
-
 #' Step 3A
 # Remove the "other" and "multiple" columns
 review_data_compact_cleaned <- review_data_compact_cleaning_step3 %>%
@@ -177,7 +171,6 @@ review_data_compact_cleaned <- review_data_compact_cleaning_step3 %>%
     #' instead of "other"
     -c(paper_title, country_studied_multiple)
   )
-# View(review_data_compact_cleaned)
 
 # save the cleaned compact dataset
 saveRDS(review_data_compact_cleaned,

### 2023-05-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
commented out the chunk to check if knitting is interactive as it's not working

@@
 ```{r}
-#' if sourced, re-run the data cleaning step, in case something has changed 
-#' else if through the terminal, use the arguments passed through the
-#' commandline/make
-if (is_null(getOption('knitr.in.progress'))) {
-source(here::here('./scripts/orv_models_review_data_cleaning.R'))
-args <- c(
-  here::here("data", "review_data_long_cleaned.rds"),
-  here::here("data", "review_data_compact_cleaned.rds"),
-  here::here("data", "compact_data_with_citation_keys_cleaned.rds")
-  )
-} else {
- args <- commandArgs(trailingOnly = TRUE)
-}
-```
-
-```{r}
-# Create a folder for storing the figures
+# if the figs folder doesn't exist, create it for storing the figures
+figs_dir <- "figs"
 

### 2023-05-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
replaced read_rds with readRDS

@@
 
+```{r rerun_data_cleaning_if_interactive}
+#' if this script is being knit interactively, re-run the data cleaning step,
+#' and assign the generated cleaned data (in case something has changed) 
+#' else if through the terminal, use the 
+#' arguments passed through the commandline/make
+# knitting_interactively <- isFALSE(is.null(getOption('knitr.in.progress')))
+# 
+# if (knitting_interactively) {
+#   source(here::here("scripts", "orv_models_review_data_cleaning.R"))
+# args <- c(
+#   here::here("data", "review_data_long_cleaned.rds"),
+#   here::here("data", "review_data_compact_cleaned.rds"),
+#   here::here("data", "compact_data_with_citation_keys_cleaned.rds")
+#   )
+# } else {
+#  args <- commandArgs(trailingOnly = TRUE)
+# }
+```
+
+```{r}
+args <- c(
+  here::here("data", "review_data_long_cleaned.rds"),
+  here::here("data", "review_data_compact_cleaned.rds"),
+  here::here("data", "compact_data_with_citation_keys_cleaned.rds")
+  )
+```
+
 ```{r}
 # Load the cleaned data 
-long_data <- read_rds(args[1])
+long_data <- readRDS(args[1])
 
 #The cleaned data without citations
-compact_data_init <- read_rds(args[2])
+compact_data_init <- readRDS(args[2])
 
 # The data with citations 
-compact_data_with_citation_keys <- read_rds(args[3])
+compact_data_with_citation_keys <- readRDS(args[3])
 

### 2023-06-16 analyses/scripts/orv_models_review_data_cleaning.R
Shortened "the_outcomes_were_inconclusive" to "inconclusive"

@@ -49,8 +49,13 @@ citation_data <- bib2df(here(.args[2]),
 # Data cleaning
 ############################################
 
-
-
+# Initialize steps; shorten some variables and entries
+review_data_compact <- review_data_compact %>%
+  mutate(is_vax_effective = ifelse(
+    is_vax_effective == "the_outcomes_were_inconclusive",
+    "inconclusive",
+    is_vax_effective),
+    )
 
 # Step 1
 #' Remove extraneous variables and clean the column names

### 2023-06-16 analyses/scripts/orv_models_review_data_cleaning.R
Added "immunization" to the pattern for detecting if vaccination was modelled

@@ -304,7 +304,9 @@ compact_data_with_citation_keys <- left_join(review_data_compact_cleaned,
 compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
   arrange(publication_year) %>%
   mutate(vax_modelled = ifelse(
-    str_detect(intervention_modelled, 'vaccination'), 'yes', 'no')) %>%
+    str_detect(intervention_modelled, 'vaccination|immunization|immunisation'),
+    'yes', 'no')
+    ) %>%
   mutate(
     intervention_type = case_when(
     # When vax was not modelled at all

### 2023-06-16 analyses/scripts/orv_models_review_data_cleaning.R
Modified the names of the categories of vaccination modelling

@@ -307,14 +307,15 @@ compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
     str_detect(intervention_modelled, 'vaccination|immunization|immunisation'),
     'yes', 'no')
     ) %>%
+  # Vaccination modelling categories
   mutate(
     intervention_type = case_when(
     # When vax was not modelled at all
     vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax',
     # When vax was modelled but not for comparison as a single intervention
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_combination_with_others',
+    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_as_mixed_intervention',
     # When vax was modelled as a single intervention to be compared with others
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_single'
+    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_compared_to_others'
     )
     ) %>%
   mutate(

### 2023-06-16 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Updated analysis script with new vaccination modelling category names

@@
   adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
-  adorn_pct_formatting(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
-  adorn_ns(... = c('no_vax', 'vax_combination_with_others', 'vax_single'))
-
-knitr::kable(intervention_categories, caption = 'Number of studies per intervention categories', format = "latex", booktabs = TRUE) %>% 
+  adorn_percentages(... = c('no_vax', 
+                            'vax_as_mixed_intervention', 
+                            'vax_compared_to_others')
+                    ) %>% 
+  adorn_pct_formatting(... = c('no_vax', 
+                               'vax_as_mixed_intervention', 
+                               'vax_compared_to_others')
+                       ) %>% 
+  adorn_ns(... = c('no_vax', 
+                   'vax_as_mixed_intervention', 
+                   'vax_compared_to_others'
+                   )
+           )
+
+knitr::kable(intervention_categories, 
+             caption = 'Number of studies per intervention categories', 
+             format = "latex", booktabs = TRUE) %>% 
         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
@@
 vax_impact_conclusions <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(intervention_type == 'vax_single') %>% 
-  count(collab_type, is_vax_effective, sort = T) %>% 
+  filter(intervention_type == 'vax_compared_to_others') %>% 
+  count(collab_type, is_vax_effective, sort = TRUE) %>% 
   pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
     replace_na(list(yes = 0, n0 = 0, the_outcomes_were_inconclusive = 0)) %>% 
-  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
   adorn_totals(where = c('row', 'col')) %>% 
@@
 vax_impact_by_disease <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(intervention_type == 'vax_single') %>% 
+  filter(intervention_type == 'vax_compared_to_others') %>% 
   count(disease, is_vax_effective, sort = T) %>% 
   pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
-  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
     replace_na(list(yes = 0, no = 0, inconclusive = 0)) %>% 
@@
 vax_as_single_intervention_studies <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(intervention_type == 'vax_single') %>% 
-  select(title, disease, bibtexkey, publication_year, intervention_modelled)
+  filter(intervention_type == 'vax_compared_to_others') %>% 
+  select(title, author, publication_year, disease, paper_doi, 
+         intervention_modelled)
 
@@
   adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
-  adorn_pct_formatting(... = c('no_vax', 'vax_combination_with_others', 'vax_single')) %>% 
-  adorn_ns(... = c('no_vax', 'vax_combination_with_others', 'vax_single'))
+  adorn_percentages(... = c('no_vax', 'vax_as_mixed_intervention', 'vax_compared_to_others')) %>% 
+  adorn_pct_formatting(... = c('no_vax', 'vax_as_mixed_intervention', 'vax_compared_to_others')) %>% 
+  adorn_ns(... = c('no_vax', 'vax_as_mixed_intervention', 'vax_compared_to_others'))
 
@@
 fmd_vax_impact_conclusions <- fmd_data %>% 
-  filter(intervention_type == 'vax_single') %>% 
+  filter(intervention_type == 'vax_compared_to_others') %>% 
   count(collab_type, is_vax_effective, sort = T) %>% 
@@
   replace_na(list(no = 0, inconclusive = 0, yes = 0)) %>% 
-  rename('inconclusive' = 'the_outcomes_were_inconclusive') %>% 
   adorn_totals(where = c('row', 'col')) %>% 

### 2023-06-16 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Loaded jsonlite

@@
   library('here')
+  library("jsonlite")
   })

### 2023-06-16 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Uncommented old analyses

@@
 
-<!-- ## Diseases studied per collab type -->
-
-<!-- ```{r echo=FALSE} -->
-<!-- #count the number of unique diseases studied -->
-<!-- disease_studied_by_collab_type <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   separate_rows(disease,  sep = ' ') %>%  -->
-<!--   distinct(title, disease, .keep_all = TRUE) %>%  -->
-<!--   count(collab_type, disease, sort = TRUE) %>% -->
-<!--   pivot_wider(names_from = collab_type, values_from = n) %>%  -->
-<!--   replace_na(list(purely_academic = 0, mixed = 0)) %>%  -->
-<!--   adorn_totals(where = c('row', 'col')) %>%  -->
-<!--   adorn_percentages(... = c('purely_academic', 'mixed')) %>%  -->
-<!--   adorn_pct_formatting(... = c('purely_academic', 'mixed')) %>%  -->
-<!--   adorn_ns(... = c('purely_academic', 'mixed')) %>%  -->
-<!--   mutate(disease = str_to_sentence(str_replace(disease, '_', ' '))) %>%  -->
-<!--   arrange(desc(Total)) -->
-
-<!-- knitr::kable(disease_studied_by_collab_type, caption = 'Number of studies per disease and collaboration type', format = "latex", booktabs = TRUE) %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position')) -->
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- #tally the diseases by collaboration type -->
-<!-- disease_by_collab_type_long <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   separate_rows(disease,  sep = ' ') %>%  -->
-<!--   count(collab_type, disease, sort = TRUE)  -->
-
-<!-- disease_by_collab_type_plot <- ggplot(disease_by_collab_type_long) +  -->
-<!--   geom_bar(aes(x = reorder(disease, n),  -->
-<!--                y = n,  -->
-<!--                fill = collab_type -->
-<!--                ),  -->
-<!--            color = 'black', -->
-<!--            stat = 'identity', -->
-<!--            position = position_fill(reverse = TRUE) -->
-<!--            ) +  -->
-<!--   labs(x = '**Disease**', y = '**Number of studies**') +  -->
-<!--   coord_flip() + -->
-<!--   md_theme_minimal(base_size = 12) -->
-
-<!-- print(disease_by_collab_type_plot) -->
-<!-- ``` -->
+## Diseases studied per collab type
+
+```{r echo=FALSE}
+#count the number of unique diseases studied
+disease_studied_by_collab_type <- compact_data_with_citation_keys_no_fmd %>%
+  separate_rows(disease,  sep = ' ') %>%
+  distinct(title, disease, .keep_all = TRUE) %>%
+  count(collab_type, disease, sort = TRUE) %>%
+  pivot_wider(names_from = collab_type, values_from = n) %>%
+  replace_na(list(purely_academic = 0, mixed = 0)) %>%
+  adorn_totals(where = c('row', 'col')) %>%
+  adorn_percentages(... = c('purely_academic', 'mixed')) %>%
+  adorn_pct_formatting(... = c('purely_academic', 'mixed')) %>%
+  adorn_ns(... = c('purely_academic', 'mixed')) %>%
+  mutate(disease = str_to_sentence(str_replace(disease, '_', ' '))) %>%
+  arrange(desc(Total))
+
+disease_studied_by_collab_type_mod <- rbind(disease_studied_by_collab_type[-1, ], 
+                   disease_studied_by_collab_type[1, ])
+
+knitr::kable(disease_studied_by_collab_type_mod, 
+             caption = 'Number of studies per disease and collaboration type', 
+             format = "latex", booktabs = TRUE) %>%
+        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+```
+
+```{r}
+#tally the diseases by collaboration type
+disease_by_collab_type_long <- compact_data_with_citation_keys_no_fmd %>%
+  separate_rows(disease,  sep = ' ') %>%
+  count(collab_type, disease, sort = TRUE)
+
+disease_by_collab_type_plot <- ggplot(disease_by_collab_type_long) +
+  geom_bar(aes(x = reorder(disease, n),
+               y = n,
+               fill = collab_type
+               ),
+           color = 'black',
+           stat = 'identity',
+           position = position_fill(reverse = TRUE)
+           ) +
+  labs(x = 'Disease', y = 'Number of studies') +
+  coord_flip() +
+  theme_minimal(base_size = 12)
+
+print(disease_by_collab_type_plot)
+```
 
@@
 
-<!-- ### Parametrization methods -->
-
-<!-- ```{r} -->
-<!-- #wide data for table -->
-<!-- model_parametrization_wide <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(collab_type, parametrization, sort = TRUE) %>%  -->
-<!--   pivot_wider(names_from = parametrization, values_from = n) %>%  -->
-<!--   adorn_totals(where = c('row', 'col')) %>%  -->
-<!--   adorn_percentages(... = -c('Total', 'collab_type')) %>%  -->
-<!--   adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%  -->
-<!--   adorn_ns(... = -c('Total', 'collab_type'))  -->
-
-<!-- #table -->
-<!-- knitr::kable(model_parametrization_wide, caption = 'How model parameters are obtained',  -->
-<!--              format = "latex", booktabs = TRUE) %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'scale_down', 'HOLD_position')) -->
-<!-- ``` -->
-
-<!-- ```{r eval=FALSE} -->
-<!-- #long data for plotting -->
-<!-- model_parametrization_long <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   group_by(collab_type) %>%  -->
-<!--   count(parametrization, sort = TRUE) -->
-
-<!-- #plotting -->
-<!-- ggplot(data = model_parametrization_long,  -->
-<!--        aes(fill = collab_type,  -->
-<!--            area = n,  -->
-<!--            label = parametrization, -->
-<!--            subgroup = parametrization -->
-<!--            ) -->
-<!--        ) +  -->
-<!--   geom_treemap() + -->
-<!--   geom_treemap_text(colour = "white", -->
-<!--                     place = "centre", -->
-<!--                     size = 15, -->
-<!--                     grow = TRUE -->
-<!--                     ) + -->
-<!--   md_theme_minimal(base_size = 12)  -->
-
-<!-- ``` -->
-
-<!-- ### Validation methods  -->
-
-<!-- ```{r} -->
-<!-- #wide data for table -->
-<!-- model_validation_wide <- compact_data_with_citation_keys_no_fmd %>%  -->
-<!--   count(collab_type, validation, sort = TRUE) %>%  -->
-<!--   pivot_wider(names_from = validation, values_from = n) %>%  -->
-<!--   replace_na(list(none = 0,  -->
-<!--                   data = 0,  -->
-<!--                   another_model = 0,  -->
-<!--                   none_and_data = 0,  -->
-<!--                   data_and_another_model = 0 -->
-<!--                   ) -->
-<!--              ) %>%  -->
-<!--   adorn_totals(where = c('row', 'col')) %>%  -->
-<!--   adorn_percentages(... = -c('Total', 'collab_type')) %>%  -->
-<!--   adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%  -->
-<!--   adorn_ns(... = -c('Total', 'collab_type'))  -->
-
-<!-- #table -->
-<!-- knitr::kable(model_validation_wide, caption = 'How the model\'s performance is assessed',  -->
-<!--              format = "latex", booktabs = TRUE) %>%  -->
-<!--         kableExtra::kable_styling(latex_options = c('striped', 'scale_down', 'HOLD_position')) -->
-<!-- ``` -->
+### Parametrization methods
+
+```{r}
+#wide data for table
+model_parametrization_wide <- compact_data_with_citation_keys_no_fmd %>%
+  count(collab_type, parametrization, sort = TRUE) %>%
+  pivot_wider(names_from = parametrization, values_from = n) %>%
+  adorn_totals(where = c('row', 'col')) %>%
+  adorn_percentages(... = -c('Total', 'collab_type')) %>%
+  adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%
+  adorn_ns(... = -c('Total', 'collab_type'))
+
+#table
+knitr::kable(model_parametrization_wide, 
+             caption = 'How model parameters are obtained',
+             format = "latex", booktabs = TRUE) %>%
+        kableExtra::kable_styling(latex_options = c('striped', 
+                                                    'scale_down', 
+                                                    'HOLD_position')
+                                  )
+```
+
+### Validation methods
+
+```{r}
+#wide data for table
+model_validation_wide <- compact_data_with_citation_keys_no_fmd %>%
+  count(collab_type, validation, sort = TRUE) %>%
+  pivot_wider(names_from = validation, values_from = n) %>%
+  replace_na(list(none = 0,
+                  data = 0,
+                  another_model = 0,
+                  none_and_data = 0,
+                  data_and_another_model = 0
+                  )
+             ) %>%
+  adorn_totals(where = c('row', 'col')) %>%
+  adorn_percentages(... = -c('Total', 'collab_type')) %>%
+  adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%
+  adorn_ns(... = -c('Total', 'collab_type'))
+
+#table
+knitr::kable(model_validation_wide, 
+             caption = 'How the model\'s performance is assessed',
+             format = "latex", booktabs = TRUE) %>%
+        kableExtra::kable_styling(latex_options = c('striped', 
+                                                    'scale_down', 
+                                                    'HOLD_position')
+                                  )
+```
 

### 2023-06-16 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Deleted the chunk for exporting papers that concluded vax was not the most impactful

@@
         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-```
-
-```{r eval=FALSE}
-no_vax_impact_by_disease_citation_table <- compact_data_with_citation_keys_no_fmd %>% 
-  filter(intervention_type == 'vax_single', is_vax_effective %in% c('no', 'the_outcomes_were_inconclusive')) %>% 
-  select(title, disease, bibtexkey, publication_year, intervention_modelled, is_vax_effective)
-
-#Print the results
-# knitr::kable(no_vax_impact_by_disease_citation_table, 
-#              caption = 'Studies that did not find vaccination as most impactful'
-#              )
-
-write.xlsx(no_vax_impact_by_disease_citation_table, file = '../citation_tables/no_vax_impact_by_disease_citation_table.xlsx')
 ```

### 2023-06-16 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Styling: broke long lines into multiple lines, etc

@@
 
-knitr::kable(no_vax_modelled, caption = 'Number of studies per disease for which vaccination was not modelled', format = "latex", booktabs = TRUE) %>% 
+knitr::kable(no_vax_modelled, 
+             caption = sprintf("%s %s", 
+                               'Number of studies per disease for',
+                               'which vaccination was not modelled'
+                               ), 
+             format = "latex", booktabs = TRUE) %>% 
         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
@@
 
-write.xlsx(vax_as_single_intervention_studies, file = '../citation_tables/vax_as_single_intervention_studies.xlsx')
+writexl::write_xlsx(vax_as_single_intervention_studies, 
+          path = file.path("citation_tables", 
+                           "studies_modelling_vax_for_comparison.xlsx"
+                           )
+           )
 ```
@@
 ## Modelling objectives 
-<!-- We grouped studies into whether they assessed the impact of a future intervention strategy (prospective), a past intervention, or both (dual).  -->
-
-<!-- In general, there were more (73.2%; 167/228) studies about prospective intervention impact assessments than retrospective assessments (24.6%; 56/228), and the dual (2.2%; 5/228).
-A similar pattern was observed across the two collaboration types except that purely academic collaborations were more likely to perform the dual assessments.
--->
-
-<!-- In terms of the outbreak types, there was an approximately equal number of papers about real and hypothetical outbreaks overall, and there was no clear difference between the two collaborations.
--->
+<!-- We grouped studies into whether they assessed the impact of a future 
+intervention strategy (prospective), a past intervention, or both (dual).  -->
+
+<!-- In general, there were more (73.2%; 167/228) studies about prospective 
+intervention impact assessments than retrospective assessments (24.6%; 56/228), 
+and the dual (2.2%; 5/228). A similar pattern was observed across the two 
+collaboration types except that purely academic collaborations were more 
+likely to perform the dual assessments.   -->
+
+<!-- In terms of the outbreak types, there was an approximately equal number 
+of papers about real and hypothetical outbreaks overall, and there was no 
+clear difference between the two collaborations.   -->
 
@@
   adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('compartments', 'agents', 'individuals_representation_other')) %>% 
-  adorn_pct_formatting(... = c('compartments', 'agents', 'individuals_representation_other')) %>% 
-  adorn_ns(... = c('compartments', 'agents', 'individuals_representation_other'))
-
-knitr::kable(individual_representation, caption = 'How individuals were represented', 
+  adorn_percentages(... = c('compartments', 'agents', 
+                            'individuals_representation_other')
+                    ) %>% 
+  adorn_pct_formatting(... = c('compartments', 'agents', 
+                               'individuals_representation_other')
+                       ) %>% 
+  adorn_ns(... = c('compartments', 'agents', 
+                   'individuals_representation_other')
+           )
+
+knitr::kable(individual_representation, 
+             caption = 'How individuals were represented', 
              format = "latex", booktabs = TRUE) %>% 
@@
 
-knitr::kable(space_representation, caption = 'Was space explicitly represented in the model',
+knitr::kable(space_representation, 
+             caption = 'Was space explicitly represented in the model',
              format = "latex", booktabs = TRUE) %>% 
@@
 
-knitr::kable(stochastic_vs_deterministic, caption = 'Model dynamics (deterministic versus stochastic)', format = "latex", booktabs = TRUE) %>% 
+knitr::kable(stochastic_vs_deterministic, 
+             caption = 'Model dynamics (deterministic versus stochastic)', 
+             format = "latex", booktabs = TRUE) %>% 
         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
@@
 
-<!-- We tallied the overall top five outcomes most used between the two collaboration types.  -->
-
-<!-- The top five most commonly used outcomes, irrespective of collaboration type, were: final epidemic size, attack rate, timing of epidemic peak, cases averted, and outbreak duration. -->
-
-<!-- There was no difference in the two collaboration types as they were commonly used by both groups. -->
+<!-- We tallied the overall top five outcomes most used between the 
+two collaboration types.  -->
+
+<!-- The top five most commonly used outcomes, irrespective of collaboration 
+type, were: final epidemic size, attack rate, timing of epidemic peak, 
+cases averted, and outbreak duration. -->
+
+<!-- There was no difference in the two collaboration types as they were 
+commonly used by both groups. -->
 
@@
 
-knitr::kable(mod_structure_vs_sensitivity_analysis, 'Sensitivity analysis in relation to model structure', 
+knitr::kable(mod_structure_vs_sensitivity_analysis, 
+             caption = 'Sensitivity analysis in relation to model structure', 
              format = "latex", booktabs = TRUE) %>% 
@@
     filter(simulation_code_available == 'yes') %>% 
-    as.data.frame()
-
-openxlsx::write.xlsx(papers_with_code_available, file = '../citation_tables/papers_with_code_available.xlsx')
-
+  select(title, author, publication_year, paper_doi, publication_type, journal)
+
+writexl::write_xlsx(papers_with_code_available, 
+                     path = file.path("citation_tables", 
+                                      "papers_with_code_available.xlsx")
+                    )
 ```

### 2023-06-19 analyses/scripts/orv_models_review_data_cleaning.R
Added section titles

@@ -45,9 +45,8 @@ citation_data <- bib2df(here(.args[2]),
 ) %>%
   mutate(year = as.numeric(YEAR))
 
-############################################
-# Data cleaning
-############################################
+
+# Data cleaning ----
 
 # Initialize steps; shorten some variables and entries
 review_data_compact <- review_data_compact %>%
@@ -228,6 +227,7 @@ review_data_compact_cleaning_step4 <- review_data_compact_cleaning_step3 %>%
     )
   )
 
+# compact dataset (cleaned) ====
 #' Step 3A
 # Remove the "other" and "multiple" columns
 review_data_compact_cleaned <- review_data_compact_cleaning_step4 %>%
@@ -260,6 +260,7 @@ review_data_wide_to_long <- review_data_compact_cleaned %>%
   filter(outcome_measured != "outcome_other") %>%
   filter(intervention_modelled != "intervention_other")
 
+# long dataset (cleaned) ====
 # save the cleaned data
 saveRDS(review_data_wide_to_long,
   file = here(data_dir, "review_data_long_cleaned.rds")
@@ -384,7 +385,7 @@ compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
   arrange(title)
 
 
-
+# full dataset with citation information (cleaned) ====
 # save the cleaned data
 saveRDS(compact_data_with_citation_keys, tail(.args, 1))
 

### 2023-06-19 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Combined the two data loading chunks

@@
   )
-```
-
-```{r}
+
 # Load the cleaned data 

### 2023-06-19 analyses/scripts/orv_sys_rev_supplementary.Rmd
Loaded here package

@@
 library('conflicted')
+library('here')
 

### 2023-06-19 analyses/scripts/orv_sys_rev_supplementary.Rmd
Shortened the no-fmd data object name

@@
 #' Count by collaboration types and make a bar plot
-collab_types_count <- compact_data_no_fmd %>%
+collab_types_count <- data_without_fmd %>%
     count(author_affiliation_type, sort = TRUE) %>% 
@@
 
-countries_studied_by_count <- compact_data_with_citation_keys_no_fmd %>% 
+countries_studied_by_count <- data_without_fmd %>% 
     separate_rows(country_studied, sep = ' ') %>%
@@
 
-compact_data_with_citation_keys_no_fmd <- compact_data_with_citation_keys %>% filter(disease != 'fmd') 
+data_without_fmd <- compact_data_with_citation_keys %>% filter(disease != 'fmd') 
 ```
@@
 #Citation table of studies during 2009-2011 (Peak period)
-studies_in_2009_2011_df <- compact_data_with_citation_keys_no_fmd %>%
+studies_in_2009_2011_df <- data_without_fmd %>%
   separate_rows(disease, sep = ' ') %>% 
@@
 ```{r echo=FALSE}
-studies_between_2015_2016_df <- compact_data_with_citation_keys_no_fmd %>%
+studies_between_2015_2016_df <- data_without_fmd %>%
   separate_rows(disease, sep = ' ') %>% 
@@
 ```{r echo=FALSE}
-studies_in_2019_df <- compact_data_with_citation_keys_no_fmd %>%
+studies_in_2019_df <- data_without_fmd %>%
   filter(publication_year == 2019) %>%

### 2023-06-19 analyses/scripts/orv_sys_rev_supplementary.Rmd
Shortened the old chunk for loading and cleaning data

@@
 
-```{r echo=FALSE, include=FALSE}
+```{r}
+#Paths to the datasets
+args <- c(
+  here::here("data", "review_data_long_cleaned.rds"),
+  here::here("data", "compact_data_with_citation_keys_cleaned.rds")
+  )
 # Load the cleaned data 
-long_data <- read_rds('../data/review_data_long_cleaned.rds')
-
-#The cleaned data without citations
-compact_data_init <- read_rds('../data/review_data_compact_cleaned.rds')
-
-compact_data <- compact_data_init %>% 
-    mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
-                               'yes', 
-                               'no')
-         ) %>% 
-  mutate(intervention_type = case_when(
-    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_alongside', #when vax was modelled but not for comparison as a single intervention
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
-  )) %>% 
-  mutate(publication_year = as.numeric(publication_year), 
-         author_in_country_studied = as.character(author_in_country_studied)) %>% 
-  arrange(publication_year) %>%
-  mutate(
-    author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + '),
-    author_in_country_studied = if_else(author_in_country_studied == 'NA', 'not_applicable',
-                                        author_in_country_studied
-                                        )
-    ) %>% 
-  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, #An approach to aggregate the years before 2006 into one group because of the low number of papers
-                                         2005, 
-                                         publication_year
-                                         )
-                                  ), 
-         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
-                                         'purely_academic', 
-                                         'mixed')
-                                 )
-         )
+long_data <- readRDS(args[1])
 
 # The data with citations 
-compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/compact_data_with_citation_keys_cleaned.rds'))
+compact_data_with_citation_keys <- readRDS(args[2])
 
-compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>% 
-    mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
-                               'yes', 
-                               'no')
-         ) %>% 
-  mutate(intervention_type = case_when(
-    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_alongside', #when vax was modelled but not for comparison as a single intervention
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
-  )) %>% 
-  mutate(publication_year = as.numeric(publication_year), 
-         author_in_country_studied = as.character(author_in_country_studied)) %>% 
-  arrange(publication_year) %>%
-  mutate(
-    author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + '),
-    author_in_country_studied = if_else(author_in_country_studied == 'NA', 'not_applicable',
-                                        author_in_country_studied
-                                        )
-    ) %>% 
-  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, #An approach to aggregate the years before 2006 into one group because of the low number of papers
-                                         2005, 
-                                         publication_year
-                                         )
-                                  ), 
-         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
-                                         'purely_academic', 
-                                         'mixed')
-                                 )
-         )
-
-#Rearrange the columns
-compact_data_with_citation_keys <- compact_data_with_citation_keys %>% 
-  relocate(c(title, bibtexkey), .before = publication_year) %>% 
-  relocate(publication_year, .before = bibtexkey) %>% 
-  relocate(c(x0_reviewer, category, author:language), 
-           .after = collab_type
-           )
-
-# Remove the FMD papers (NB: We only use the FMD papers for comparison)
+# Keep the human disease studies (NB: We only use the FMD papers for comparison)
 long_data_no_fmd <- long_data %>% filter(disease != 'fmd')
 
-compact_data_no_fmd <- compact_data %>% filter(disease != 'fmd')
+data_without_fmd <- compact_data_with_citation_keys %>% 
+  filter(disease != 'fmd')
 
-compact_data_with_citation_keys_no_fmd <- compact_data_with_citation_keys %>% filter(disease != 'fmd') 
+# Filter the FMD data
+fmd_data <- compact_data_with_citation_keys %>% 
+  filter(disease == 'fmd') 
 ```
+
 ```{r echo=FALSE}

### 2023-06-19 analyses/scripts/orv_sys_rev_supplementary.Rmd
Expanded the setup chunk

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
-
-# Sets the working directory for subsequent chunks, but not this chunk
-#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
+knitr::opts_chunk$set(echo = FALSE, 
+                      dev = 'png', 
+                      out.height = "\\textheight",  
+                      out.width = "\\textwidth", 
+                      message = FALSE, 
+                      warning = FALSE
+                      )
 ```

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed wordstyle document

@@
     keep_md: yes
-    reference_docx: word-style.docx
     toc: yes

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Renamed the data object

@@
 # Filter the FMD data
-fmd_data <- compact_data_with_citation_keys %>% 
+data_fmd_only <- compact_data_with_citation_keys %>% 
   filter(disease == 'fmd') 
@@
 Is it the unique studies per method or combined method because most studies used a combination of parametrization methods especially
-parametrization_and_validation_by_model_structure <- compact_data_no_fmd %>%
+parametrization_and_validation_by_model_structure <- data_without_fmd %>%
   mutate(parametrization = str_replace(parametrization, ' ', ' + '),
@@
 #Keep only the unique entries
-parametrization_and_validation_count <- compact_data_no_fmd %>% 
+parametrization_and_validation_count <- data_without_fmd %>% 
   mutate(parametrization = str_replace(parametrization, ' ', ' + '), 
@@
 #Keep only the unique entries
-code_and_data_availability_count <- compact_data_no_fmd %>% 
+code_and_data_availability_count <- data_without_fmd %>% 
   count(data_used, data_available) %>% 
@@
 #Keep only the unique entries
-code_availability_count <- compact_data_no_fmd %>% 
+code_availability_count <- data_without_fmd %>% 
   count(simulation_code_available)
@@
 #count the number of unique diseases studied
-disease_studied_by_outbreak_type <- compact_data_no_fmd %>% 
+disease_studied_by_outbreak_type <- data_without_fmd %>% 
   separate_rows(disease,  sep = ' ') %>% 
@@
 #count the number of unique diseases studied
-disease_studied_by_objective_type <- compact_data_no_fmd %>% 
+disease_studied_by_objective_type <- data_without_fmd %>% 
   separate_rows(disease,  sep = ' ') %>% 
@@
 ```{r echo=FALSE}
-fmd_studies_by_collab_type <- compact_data %>% 
-  filter(disease == 'fmd') %>% 
+fmd_studies_by_collab_type <- data_fmd_only %>% 
   mutate(disease = as_factor(disease), 
@@
 ```{r echo=FALSE}
-fmd_studies_by_objective_and_outbreak_type <- compact_data %>% 
-  filter(disease == 'fmd') %>% 
+fmd_studies_by_objective_and_outbreak_type <- data_fmd_only %>% 
   count(objectives, outbreak_type) %>% 
@@
 ```{r echo=FALSE}
-vax_impact_categories_fmd <- compact_data %>%
-  filter(disease == 'fmd') %>% 
+vax_impact_categories_fmd <- data_fmd_only %>%
   filter(vax_modelled_with_non_vax == 'yes') %>% 
@@
 #' Count the number of each author affiliation type per year (including FMD)
-collap_types_by_year <- compact_data_no_fmd %>% 
+collap_types_by_year <- data_without_fmd %>% 
   mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 
@@
 ```{r echo=FALSE}
-academic_collabs_versus_others <- compact_data_no_fmd %>% 
+academic_collabs_versus_others <- data_without_fmd %>% 
   filter(author_affiliation_type != 'academic_institutions') %>% 
@@
 ```{r}
-author_location_count_by_disease <- compact_data_no_fmd %>%
+author_location_count_by_disease <- data_without_fmd %>%
   separate_rows(disease, sep = ' ') %>% 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Renamed the data object

@@
 ```{r echo=FALSE}
-intervention_categories_fmd <- compact_data %>% 
-  filter(disease == 'fmd') %>% 
+intervention_categories_fmd <- data_fmd_only %>% 
   group_by(intervention_type, vax_modelled_with_non_vax) %>% 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed the data loading and cleaning steps as now being handled by data cleaning script

@@
 
-```{r echo=FALSE, include=FALSE}
-# Load the cleaned data 
-long_data <- read_rds('../data/review_data_long_cleaned.rds')
-
-#The cleaned data without citations
-compact_data_init <- read_rds('../data/review_data_compact_cleaned.rds')
-
-compact_data <- compact_data_init %>% 
-    mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
-                               'yes', 
-                               'no')
-         ) %>% 
-  mutate(intervention_type = case_when(
-    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_alongside', #when vax was modelled but not for comparison as a single intervention
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
-  )) %>% 
-  mutate(publication_year = as.numeric(publication_year), 
-         author_in_country_studied = as.character(author_in_country_studied)) %>% 
-  arrange(publication_year) %>%
-  mutate(
-    author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + '),
-    author_in_country_studied = if_else(author_in_country_studied == 'NA', 'not_applicable',
-                                        author_in_country_studied
-                                        )
-    ) %>% 
-  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, #An approach to aggregate the years before 2006 into one group because of the low number of papers
-                                         2005, 
-                                         publication_year
-                                         )
-                                  ), 
-         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
-                                         'purely_academic', 
-                                         'mixed')
-                                 )
-         )
-
-# The data with citations 
-compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/compact_data_with_citation_keys_cleaned.rds'))
-
-compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>% 
-    mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
-                               'yes', 
-                               'no')
-         ) %>% 
-  mutate(intervention_type = case_when(
-    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_alongside', #when vax was modelled but not for comparison as a single intervention
-    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
-  )) %>% 
-  mutate(publication_year = as.numeric(publication_year), 
-         author_in_country_studied = as.character(author_in_country_studied)) %>% 
-  arrange(publication_year) %>%
-  mutate(
-    author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + '),
-    author_in_country_studied = if_else(author_in_country_studied == 'NA', 'not_applicable',
-                                        author_in_country_studied
-                                        )
-    ) %>% 
-  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, #An approach to aggregate the years before 2006 into one group because of the low number of papers
-                                         2005, 
-                                         publication_year
-                                         )
-                                  ), 
-         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
-                                         'purely_academic', 
-                                         'mixed')
-                                 )
-         )
-
-# Remove the FMD papers (NB: We only use the FMD papers for comparison)
-long_data_no_fmd <- long_data %>% filter(disease != 'fmd')
-
-compact_data_no_fmd <- compact_data %>% filter(disease != 'fmd')
-
-data_without_fmd <- compact_data_with_citation_keys %>% filter(disease != 'fmd') 
-```
-
 ### Interventions types (FMD)

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Styling: removed unnecessary new lines

@@
 plot(outcome_count_plot)
-
 ```
@@
 knitr::kable(parametrization_and_validation_count)
-
 ```
@@
 knitr::kable(sensitivity_analysis_count)
-
 ```
@@
 knitr::kable(code_and_data_availability_count, caption = 'Data use and availability')
-
 ```
@@
 knitr::kable(code_availability_count, caption = 'Code availability')
-
 ```
@@
 # Number of studies per disease
+
 ## By outbreak type
@@
              )
-
 ```

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Deleted all chunks for printing citation tables

@@
 
-# Secondary summaries
-## Studies before 2006 (low frequency period) 
-```{r echo=FALSE}
-#Number of studies before 2005 (low frequency period)
-n_studies_before_2006 <- compact_data_no_fmd %>% 
-  filter(publication_year < 2006) %>% 
-  summarise(n = n())
-
-print(paste('Number of studies before 2006:', n_studies_before_2006))
-```
-## Number of studies between 2006-2019 (high frequency period)
-```{r echo=FALSE}
-n_studies_btwn_2006_2019 <- compact_data_no_fmd %>% 
-  filter(publication_year >= 2006, publication_year <= 2019) %>% 
-  summarise(n = n())
-
-print(paste('Number of studies between 2006 and 2019:', n_studies_btwn_2006_2019))
-```
-
 ## Locations studied and connection of authors to the location
@@
 
-# Citation tables
-
-## Code availability
-```{r echo=FALSE}
-
-code_availability_citations <- compact_data_with_citation_keys %>% 
-  filter(simulation_code_available == 'yes')
-
-knitr::kable(code_availability_citations)
-```
-
-## Citation table for human diseases
-```{r echo=FALSE}
-vax_impact_categories_citations_no_fmd <- compact_data_with_citation_keys %>% 
-  filter(disease != 'fmd') %>% 
-  filter(vax_modelled_with_non_vax == 'yes') %>% 
-  select(title, publication_year, disease, objectives, is_vax_effective, bibtexkey) %>% 
-  arrange(is_vax_effective)
-
-#Print the results
-knitr::kable(vax_impact_categories_citations_no_fmd,
-             caption = 'Studies\' conclusions about impact of vaccination (citations for human diseases)'
-             )
-```
-
-## Citation table for FMD
-```{r echo=FALSE}
-vax_impact_categories_citations_fmd <- compact_data_with_citation_keys %>% 
-  filter(disease == 'fmd') %>% 
-  filter(vax_modelled_with_non_vax == 'yes') %>% 
-  select(title, publication_year, disease, objectives, is_vax_effective, bibtexkey) %>% 
-  arrange(is_vax_effective)
-
-#Print the results
-knitr::kable(vax_impact_categories_citations_fmd,
-             caption = 'Studies\' conclusions about impact of vaccination (citations for human diseases)'
-             )
-
-```
-
-# Exploration of the peak periods (2009-2011, 2015-2016, 2019)
-
-## Citations of studies during 2009-2011
-```{r echo=FALSE}
-#Citation table of studies during 2009-2011 (Peak period)
-studies_in_2009_2011_df <- data_without_fmd %>%
-  separate_rows(disease, sep = ' ') %>% 
-  filter(publication_year >= 2009, publication_year <= 2011) %>%
-  arrange(disease) %>%
-  select(title, publication_year, disease, objectives, bibtexkey) %>% 
-  mutate(disease = str_replace(disease, ' ', ' and '))
-
-knitr::kable(studies_in_2009_2011_df, caption = 'Studies published during 2009-2011 (Peak period)')
-```
-### Number of studies during 2009-2011 per disease and objective type (Peak period)
-```{r echo=FALSE}
-n_studies_2009_2011_df <- studies_in_2009_2011_df %>%
-  count(disease, objectives) %>% 
-  arrange(disease, n) %>% 
-  pivot_wider(names_from = objectives, values_from = n) %>% 
-  replace_na(list(both = 0, future = 0, past = 0))
-
-knitr::kable(n_studies_2009_2011_df, caption = 'Studies published during 2009-2011 (Peak period)')
-```
-
-## Citation table of studies during 2015-2016 per disease and objective type (Peak period)
-```{r echo=FALSE}
-studies_between_2015_2016_df <- data_without_fmd %>%
-  separate_rows(disease, sep = ' ') %>% 
-  filter(publication_year >= 2015, publication_year <= 2016) %>%
-  arrange(disease, publication_year) %>%
-  select(title, publication_year, disease, objectives, bibtexkey) %>% 
-  mutate(disease = str_replace(disease, ' ', ' and '))
-
-knitr::kable(studies_between_2015_2016_df, caption = 'Studies published in 2015-2016 (Peak period)')
-```
-
-### Number of studies from 2015-2016 per disease and objective type (Peak period)
-```{r echo=FALSE}
-n_studies_between_2015_2016_df <- studies_between_2015_2016_df %>% 
-  count(disease, objectives) %>% 
-  arrange(desc(n))  %>% 
-  pivot_wider(names_from = objectives, values_from = n) %>% 
-  replace_na(list(both = 0, future = 0, past = 0))
-
-knitr::kable(n_studies_between_2015_2016_df, caption = 'Papers published in 2015-2016 (Peak period)')
-```
-
-## Citation table of studies in 2019 (Peak period)
-```{r echo=FALSE}
-studies_in_2019_df <- data_without_fmd %>%
-  filter(publication_year == 2019) %>%
-  arrange(disease) %>%
-  select(title, publication_year, disease, objectives, bibtexkey) %>% 
-  mutate(disease = str_replace(disease, ' ', ' and '))
-
-knitr::kable(studies_in_2019_df, caption = 'Studies published in 2019 (Peak year)')
-```
-### Number of studies in 2019 per disease and objective type (Peak period)
-```{r echo=FALSE}
-n_studies_in_2019_df <- studies_in_2019_df %>% 
-  count(disease, objectives) %>% 
-  arrange(n)
-
-knitr::kable(n_studies_in_2019_df, caption = 'Number of studies published in 2019 per disease and objective type (Peak year)')
-```
-
-### Total number of studies in 2019 (Peak period)
-```{r echo=FALSE}
-n_studies_in_2019 <- n_studies_in_2019_df %>%  
-  summarise(n = n())
-
-print(paste('Number of studies in 2019 (Peak year):', 
-            n_studies_in_2019
-            )
-      )
-```
-
-## Number of diseases in the peak periods
-```{r echo=FALSE}
-peak_period_df <- bind_rows(studies_in_2009_2011_df, 
-                            studies_between_2015_2016_df, 
-                            studies_in_2019_df
-                            ) %>% 
-  arrange(disease, publication_year)
-
-knitr::kable(peak_period_df , 
-             caption = 'Studies published in peak period'
-             )
-```
-
-```{r echo=FALSE}
-n_studies_by_disease_and_objectives_peak_periods <- peak_period_df %>% 
-  count(disease, objectives)
-
-knitr::kable(n_studies_by_disease_and_objectives_peak_periods, 
-             caption = 'Number of studies per disease and objective in peak periods'
-             )
-```
-
-```{r echo=FALSE}
-total_studies_by_disease_peak_period_df <- peak_period_df %>% 
-  count(disease) %>% 
-  arrange(n)
-
-knitr::kable(total_studies_by_disease_peak_period_df, 
-             caption = 'Number of studies per disease in peak periods'
-             )
-```
-
-## Influenza during 2009 - 2011 peaks
-```{r echo=FALSE}
-n_Influenza_studies_by_objectives_2009_2011 <- peak_period_df %>% 
-  filter(publication_year >= 2009, publication_year <= 2011) %>%
-  filter(disease == 'influenza') %>% 
-  count(objectives)
-
-knitr::kable(n_Influenza_studies_by_objectives_2009_2011, 
-             caption = 'Number of Influenza studies per objective type (2009 & 2011)'
-             )
-```
-## Ebola in 2015-2016
-```{r echo=FALSE}
-n_ebola_studies_by_objectives_2015_2016 <- studies_between_2015_2016_df %>% 
-  filter(disease == 'ebola') %>% 
-  count(objectives)
-
-knitr::kable(n_ebola_studies_by_objectives_2015_2016, 
-             caption = 'Number of Ebola studies per objective type (2015-2016)'
-             )
-```
-### Studies that used both retrospective and prospective assessments in peak periods
-```{r echo=FALSE}
-knitr::kable(peak_period_df %>% filter(objectives == 'both'), 
-             caption = 'Studies with retrospective and prospective assessments'
-             )
-
-```
-
 # Miscellaneous Analyses

### 2023-06-21 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Revised the YAML headers to be uniform

@@
 ---
-title: "Analysis of the included studies"
+title: "Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review"
+subtitle: "Supplementary file (analysis for main manuscript)"
+author: "James M. Azam, Xiaoxi Pang, Elisha B. Are, Juliet R.C. Pulliam, Matthew J. Ferrari"
 output:
@@
     toc: yes
-    keep_tex: yes
     fig_crop: no

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Revised the YAML headers to be uniform

@@
 ---
-title: "Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)"
-author: "James Azam"
-date: '`r format(Sys.Date(), "%B %d, %Y")`'
+title: "Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review"
+subtitle: "Supplementary file"
+author: "James M. Azam, Xiaoxi Pang, Elisha B. Are, Juliet R.C. Pulliam, Matthew J. Ferrari"
 output:
-  word_document:
-    keep_md: yes
+  pdf_document:
     toc: yes
+    fig_crop: no
 ---

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed plot of outcomes measured

@@
 
-knitr::kable(outcomes_count)
-
-#Plot the result
-outcome_count_plot <- ggplot(data = outcomes_count) + 
-  geom_point(aes(x = reorder(outcome_measured, 
-                             num_of_studies), 
-               y = num_of_studies
-               ), 
-           stat = 'identity',
-           color = 'darkslategray4'
-           ) +
-  coord_flip() +
-  theme_minimal()
-
-plot(outcome_count_plot)
+knitr::kable(outcomes_count,
+             caption = "Count of outcomes measured")
 ```

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Moved the arrange operation out of the kable function

@@
   count(author_affiliation_type, sort = TRUE) %>% 
-    mutate(author_affiliation_type = as_factor(author_affiliation_type))
+  mutate(author_affiliation_type = as_factor(author_affiliation_type)) %>% 
+  arrange(desc(n))
 
-knitr::kable(collab_types_count %>% arrange(desc(n)))
+knitr::kable(collab_types_count )
 ```

### 2023-06-21 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Removed chunk for checking if script is being knit interactively

@@
 }
-```
-
-```{r rerun_data_cleaning_if_interactive}
-#' if this script is being knit interactively, re-run the data cleaning step,
-#' and assign the generated cleaned data (in case something has changed) 
-#' else if through the terminal, use the 
-#' arguments passed through the commandline/make
-# knitting_interactively <- isFALSE(is.null(getOption('knitr.in.progress')))
-# 
-# if (knitting_interactively) {
-#   source(here::here("scripts", "orv_models_review_data_cleaning.R"))
-# args <- c(
-#   here::here("data", "review_data_long_cleaned.rds"),
-#   here::here("data", "review_data_compact_cleaned.rds"),
-#   here::here("data", "compact_data_with_citation_keys_cleaned.rds")
-#   )
-# } else {
-#  args <- commandArgs(trailingOnly = TRUE)
-# }
 ```

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Cleaned up plotting code

@@
 ```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
-
-collap_types_count_barplot <- collab_types_count %>%
-    ggplot() + geom_bar(aes(x = reorder(author_affiliation_type, n),
-                            y = n
-                            ),
+collap_types_count_barplot <- ggplot(data = collab_types_count) + 
+  geom_bar(aes(x = reorder(author_affiliation_type, n), y = n),
            stat = 'identity',
-                        color = 'black'
-                        ) +
+           color = 'black') +
     scale_y_continuous(breaks = seq(0, 140, 20),
@@
     labs(title = 'Number of studies per collaboration type', 
-         x = '', 
+         x = ' ', 
          y = 'Number of studies') + 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed the plot of aggregated collaboration types over time

--- 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
@@
 
-### Trend in collaboration over the years
-
-```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
-
-collap_types_count_barplot <- collab_types_count %>%
-    ggplot() + geom_bar(aes(x = reorder(author_affiliation_type, n),
-                            y = n
-                            ),
-                        stat = 'identity',
-                        color = 'black'
-                        ) +
-    scale_y_continuous(breaks = seq(0, 140, 20),
-                       labels = seq(0, 140, 20)
-                       ) +
-    labs(title = 'Number of studies per collaboration type', 
-         x = '', 
-         y = 'Number of studies') + 
-  coord_flip() +
-  theme_minimal() +
-  theme(legend.position = 'none')
-
-plot(collap_types_count_barplot)
-
-knitr::kable(collab_types_count, 
-             col.names = c('Collaboration type', 'Number of publications'),
-             caption = 'Number of publications per collaboration type'
-             )
-
-```
 # Number of studies per disease and intervention.

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed group_by operations and mvoed variable into count

@@
   filter(intervention_modelled != 'various') %>% #remove false rows
-  group_by(disease) %>% 
-  count(intervention_modelled, name = 'num_of_studies') %>% 
+  count(disease, intervention_modelled, name = 'num_of_studies') %>% 
   arrange(disease, desc(num_of_studies)) %>% 
@@
 knitr::kable(interventions_per_disease)
-
 ```
@@
 outcomes_count <- outcomes_unique_entries %>% 
-  group_by(outcome_measured) %>% 
   count(outcome_measured, name = 'num_of_studies', sort = T) %>% 
@@
 model_structure_unique_count <- model_structure_unique_entries %>%
-    group_by(model_structure) %>% 
-    count(model_structure, name = 'num_of_studies')
+    count(model_structure, model_structure, name = 'num_of_studies')
 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed renaming of the parametrization and validation entries

@@
 parametrization_and_validation_by_model_structure <- data_without_fmd %>%
-  mutate(parametrization = str_replace(parametrization, ' ', ' + '),
-         validation = str_replace(validation, ' ', ' + ')
-         ) %>% 
   count(model_structure, parametrization, validation) %>% 
@@
 parametrization_and_validation_count <- data_without_fmd %>% 
-  mutate(parametrization = str_replace(parametrization, ' ', ' + '), 
-         validation = str_replace(validation, ' ', ' + ')
-         ) %>% 
   count(parametrization, 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Replaced the default col "n" from count() with "num_of_studies"

@@
 collab_types_count <- data_without_fmd %>%
-  count(author_affiliation_type, sort = TRUE) %>% 
+  count(author_affiliation_type, sort = TRUE, name = "num_of_studies") %>% 
   mutate(author_affiliation_type = as_factor(author_affiliation_type)) %>% 
-  arrange(desc(n))
+  arrange(desc(num_of_studies))
 
@@
 code_and_data_availability_count <- data_without_fmd %>% 
-  count(data_used, data_available) %>% 
+  count(data_used, data_available, name = 'num_of_studies') 
   pivot_wider(names_from = data_available, values_from = n) %>% 
@@
 code_availability_count <- data_without_fmd %>% 
-  count(simulation_code_available)
+  count(simulation_code_available, name = 'num_of_studies')
 
@@
   distinct(title, .keep_all = TRUE) %>% 
-  count(disease, outbreak_type, sort = TRUE) %>%
-  pivot_wider(names_from = outbreak_type, values_from = n) %>% 
+  count(disease, outbreak_type, sort = TRUE, name = 'num_of_studies') %>%
+  pivot_wider(names_from = outbreak_type, values_from = 'num_of_studies') %>% 
   replace_na(list(hypothetical_outbreak = 0, real_outbreak = 0)) %>% 
@@
   distinct(title, .keep_all = TRUE) %>% 
-  count(disease, objectives) %>%
-  pivot_wider(names_from = objectives, values_from = n) %>% 
+  count(disease, objectives, name = 'num_of_studies') %>%
+  pivot_wider(names_from = objectives, values_from = num_of_studies) %>% 
   replace_na(list(future = 0, past = 0, both = 0)) %>% 
@@
          ) %>% 
-  count(collab_type, sort = TRUE)
+  count(collab_type, sort = TRUE, name = 'num_of_studies')
 
@@
 fmd_studies_by_objective_and_outbreak_type <- data_fmd_only %>% 
-  count(objectives, outbreak_type) %>% 
-  pivot_wider(names_from = outbreak_type, values_from = n)
+  count(objectives, outbreak_type, name = 'num_of_studies') %>% 
+  pivot_wider(names_from = outbreak_type, values_from = num_of_studies)
 
@@
   group_by(intervention_type, vax_modelled_with_non_vax) %>% 
-  count(is_vax_effective, sort = TRUE) %>% 
+  count(is_vax_effective, sort = TRUE, name = 'num_of_studies') %>% 
   filter(vax_modelled_with_non_vax == 'yes') %>% 
-  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
+  pivot_wider(names_from = is_vax_effective, values_from = num_of_studies) %>% 
   adorn_totals(where = 'col')
@@
          ) %>% 
-  count(year_aggreg, 
-        collab_type, 
+  count(year_aggreg, collab_type, , name = 'num_of_studies') %>% 
+  pivot_wider(names_from = collab_type, values_from = num_of_studies)
         name = 'total_publications'
@@
         collab_type, 
-        name = 'total_publications'
+        name = 'num_of_studies'
         )
@@
   geom_bar(aes(x = year_aggreg,
-               y = total_publications,
+               y = num_of_studies,
                fill = collab_type
@@
   distinct(title, .keep_all = TRUE) %>% 
-  count(author_in_country_studied, sort = TRUE) %>% 
-  complete(author_in_country_studied, fill = list(n = 0)) %>% 
-  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
+  count(author_in_country_studied, sort = TRUE, name = "num_of_studies") %>% 
+  complete(author_in_country_studied, fill = list(num_of_studies = 0)) %>% 
+  pivot_wider(names_from = author_in_country_studied, values_from = num_of_studies) %>% 
   replace_na(list(yes = 0, no = 0, not_applicable = 0)) %>% 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed analysis of model validation and parametrization cross-tabulation

@@
 knitr::kable(model_structure_unique_count)
-```
-
-# Model structure, parametrization, and validation types
-
-```{r echo=FALSE}
-#Cross tally the model structure with parametrization and validation categories
-#FIXME: Check that studies are either not being under counted or double-counted.
-What do I want to count here?
-Is it the unique studies per method or combined method because most studies used a combination of parametrization methods especially
-parametrization_and_validation_by_model_structure <- data_without_fmd %>%
-  count(model_structure, parametrization, validation) %>% 
-  pivot_wider(names_from = model_structure, values_from = n)
-
-#Print the table of results
-knitr::kable(parametrization_and_validation_by_model_structure,
-             caption = 'Parametrization and validation types per model structure')
-
-```
-
-# Model parametrization & validation
-
-```{r echo=FALSE}
-#Keep only the unique entries
-parametrization_and_validation_count <- data_without_fmd %>% 
-  count(parametrization, 
-        validation, 
-        name = 'num_of_studies'
-        ) %>% 
-  group_by(parametrization) %>% 
-  arrange(desc(num_of_studies), .by_group = T)
-
-#Print the table
-knitr::kable(parametrization_and_validation_count)
 ```

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed separate rows operations as now being handled by data cleaning script

@@
 disease_studied_by_outbreak_type <- data_without_fmd %>% 
-  separate_rows(disease,  sep = ' ') %>% 
   mutate(disease = as_factor(disease), 
@@
 disease_studied_by_objective_type <- data_without_fmd %>% 
-  separate_rows(disease,  sep = ' ') %>% 
   mutate(disease = as_factor(disease), 
@@
 countries_studied_by_count <- data_without_fmd %>% 
-    separate_rows(country_studied, sep = ' ') %>%
     distinct(title, country_studied, .keep_all = TRUE) %>% 
@@
 author_location_count_by_disease <- data_without_fmd %>%
-  separate_rows(disease, sep = ' ') %>% 
   mutate(author_in_country_studied = as_factor(author_in_country_studied), 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed pivoting as table made less sense

@@
   count(data_used, data_available, name = 'num_of_studies')
-  pivot_wider(names_from = data_available, values_from = n) %>% 
-  replace_na(list(not_applicable = 0, 
-                  yes = 0, 
-                  no = 0
-                  )
-             )
 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed redundant code

@@
   pivot_wider(names_from = collab_type, values_from = num_of_studies)
-        name = 'total_publications'
-        ) %>% 
-  pivot_wider(names_from = collab_type, values_from = total_publications)
 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Counted collab types per year and made a table

@@
   filter(disease == 'fmd') 
+```
+
+# Human vaccine-preventable diseases
+
+## Studies per collaboration type
+
+```{r echo=FALSE}
+#' Count the number of each author affiliation type per year (including FMD)
+collap_types_by_year <- data_without_fmd %>% 
+  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 
+                                         2005, 
+                                         publication_year
+                                         )
+                                  ), 
+         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
+                                         'Purely academic', 
+                                         'Mixed')
+                                 )
+         ) %>% 
+  count(year_aggreg, collab_type, name = 'num_of_studies') %>% 
+  pivot_wider(names_from = collab_type, values_from = num_of_studies)
+
+knitr::kable(collap_types_by_year %>% 
+               clean_names() %>% 
+               adorn_totals(... = c(mixed, purely_academic), 
+                            where = c("row", "col")
+                            )
+             )
 ```

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Made a table of the unique number of studies per disease

@@
 # Number of studies per disease and intervention.
+## Diseases studied
+```{r echo=FALSE}
+disease_studied_count <- long_data_no_fmd %>% 
+  group_by(disease) %>% 
+  distinct(title) %>% 
+  count(disease, name = 'num_of_studies', sort = TRUE) %>%
+  ungroup()
 
+knitr::kable(disease_studied_count, col.names = c('Disease', 'Number of studies'))
+```
 ```{r echo=FALSE}

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Cleaned up the section headings and hierarchy

--- 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
@@
 # Number of studies per disease and intervention.
+## Diseases studied
+```{r echo=FALSE}
+disease_studied_count <- long_data_no_fmd %>% 
+  group_by(disease) %>% 
+  distinct(title) %>% 
+  count(disease, name = 'num_of_studies', sort = TRUE) %>%
+  ungroup()
+
+knitr::kable(disease_studied_count, col.names = c('Disease', 'Number of studies'))
+```
+
+## Diseases and interventions
 
@@
 
-# Number of studies per outcome
+## Outcomes studied
 
@@
 
-# Number of studies per model structure type
+## Model structure type
 
@@
 
-# How is sensitivity analysis distributed by model structure?
+## Model structure and sensitivity analysis
 
@@
 
-# Data use and availability
+## Data use and availability
 
@@
 ```
-# Code availability
 
+## Code availability
 ```{r echo=FALSE}
@@
 
-# Number of studies per disease
-
-## By outbreak type
+## Outbreak type
 
@@
 
-## By objective type
+## Objective types
 
@@
 
-## FMD by collaboration type
+## Geographic analyses
 ```{r echo=FALSE}
@@
 ```
-
-## Locations studied and connection of authors to the location
 
@@
 
-## Number of studies per continent
+#### Studies per continent
 ```{r echo=FALSE}
@@
 
-### Interventions types (FMD)
+### Connection of authors to the studied locations
 
+## Interventions types 
 ```{r echo=FALSE}
@@
 
-## Vaccine impact categories (FMD)
+## Vaccine impact categories 
 ```{r echo=FALSE}

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Changed T to TRUE

@@
 outcomes_count <- outcomes_unique_entries %>% 
-  count(outcome_measured, name = 'num_of_studies', sort = T) %>% 
+  count(outcome_measured, name = 'num_of_studies', sort = TRUE) %>% 
   ungroup() %>% 
@@
     distinct(title, country_studied, .keep_all = TRUE) %>% 
-    count(collab_type, country_studied, name = 'num_of_studies', sort = T)
+    count(collab_type, country_studied, name = 'num_of_studies', sort = TRUE)
 
@@
         name = 'num_of_studies', 
-        sort = T
+        sort = TRUE
         )

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Rearranged some code chunks

@@
 ```
-
-# Miscellaneous Analyses
-
-```{r echo=FALSE}
-disease_studied_count <- long_data_no_fmd %>% 
-  group_by(disease) %>% 
-  distinct(title) %>% 
-  count(disease, name = 'num_of_studies', sort = T) %>%
-  ungroup()
-
-knitr::kable(disease_studied_count, col.names = c('Disease', 'Number of studies'))
-```
-
-### Disease most studied
-```{r echo=FALSE}
-disease_studied_most <- disease_studied_count %>% 
-  filter(num_of_studies == max(num_of_studies))
-
-knitr::kable(disease_studied_most)
-```
-
-### Number of studies per collaboration type
-
-```{r echo=FALSE}
-#' Count the number of each author affiliation type per year (including FMD)
-collap_types_by_year <- data_without_fmd %>% 
-  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 
-                                         2005, 
-                                         publication_year
-                                         )
-                                  ), 
-         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
-                                         'Purely academic', 
-                                         'Mixed')
-                                 )
-         ) %>% 
-  count(year_aggreg, collab_type, , name = 'num_of_studies') %>% 
-  pivot_wider(names_from = collab_type, values_from = num_of_studies)
-
-knitr::kable(collap_types_by_year %>% clean_names() %>% adorn_totals(... = c(mixed, purely_academic)))
-
-```
-
-### Academic collaborations versus other non-academic collaborations (excluding purely academic collaborations).
-
-```{r echo=FALSE}
-academic_collabs_versus_others <- data_without_fmd %>% 
-  filter(author_affiliation_type != 'academic_institutions') %>% 
-  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 2005, publication_year
-                                         )
-                                  ), 
-         collab_type = as_factor(if_else(str_detect(author_affiliation_type, 'academic_institutions'), 
-                                         'Academic', 
-                                         'Other'
-                                         )
-                                 )
-         ) %>% 
-  count(year_aggreg, 
-        collab_type, 
-        name = 'num_of_studies'
-        )
-
-#The plot
-# Modify the x-axis labels to account for the lumping of the years from 2005 and below
-x_axis_labels <- as.character(seq(2005, 2020, 2))
-
-x_axis_labels[1] <- '1970-2005'
-
-#plot the result
-academic_collabs_trend <- ggplot(data = academic_collabs_versus_others) + 
-  geom_bar(aes(x = year_aggreg,
-               y = num_of_studies,
-               fill = collab_type
-               ),
-           color = 'black',
-           stat = 'identity',
-           position = position_fill(reverse = TRUE)  
-             ) +
-  scale_fill_manual(values = c('tan1', 'turquoise1')) +
-  scale_x_continuous(breaks = seq(2005, 2020, 2),
-                     labels = x_axis_labels
-                     ) +
-  labs(title = 'Academic and other collaborations over time',
-       x = 'Year',
-       y = 'Proportion of publications',
-       fill = 'Collaboration type' 
-         ) +
-  theme_minimal(base_size = 12)
-
-plot(academic_collabs_trend)
-
-#Number of each collaboration type
-
-```
-
-# Connection of authors to the studied locations 
-```{r}
-author_location_count_by_disease <- data_without_fmd %>%
-  mutate(author_in_country_studied = as_factor(author_in_country_studied), 
-         disease = as_factor(disease)
-         ) %>% 
-  group_by(collab_type, disease) %>%
-  distinct(title, .keep_all = TRUE) %>% 
-  count(author_in_country_studied, sort = TRUE, name = "num_of_studies") %>% 
-  complete(author_in_country_studied, fill = list(num_of_studies = 0)) %>% 
-  pivot_wider(names_from = author_in_country_studied, values_from = num_of_studies) %>% 
-  replace_na(list(yes = 0, no = 0, not_applicable = 0)) %>% 
-  mutate(total = not_applicable + no + yes) %>% 
-  ungroup(collab_type) %>% 
-  arrange(desc(total))
-
-knitr::kable(author_location_count_by_disease)
-```

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Added a section for FMD

@@
 ### Connection of authors to the studied locations 
+# Foot and mouth disease
+
+## Collaboration types
+```{r echo=FALSE}
+fmd_studies_by_collab_type <- data_fmd_only %>% 
+  mutate(disease = as_factor(disease), 
+         author_affiliation_type = as_factor(str_replace(author_affiliation_type, ' ', '+'))
+         ) %>% 
+  mutate(collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
+                                         'purely_academic', 
+                                         'mixed')
+                                 )
+         ) %>% 
+  count(collab_type, sort = TRUE, name = 'num_of_studies')
+
+knitr::kable(fmd_studies_by_collab_type)
+```
+## Objective types
+```{r echo=FALSE}
+fmd_studies_by_objective_and_outbreak_type <- data_fmd_only %>% 
+  count(objectives, outbreak_type, name = 'num_of_studies') %>% 
+  pivot_wider(names_from = outbreak_type, values_from = num_of_studies)
+
+knitr::kable(fmd_studies_by_objective_and_outbreak_type)
+```
 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed an unnecessary space before a bracket
Moved FMD analyses to the dedicated section

@@
 
-knitr::kable(collab_types_count )
+knitr::kable(collab_types_count)
 ```
@@
 ## Geographic analyses
-```{r echo=FALSE}
-fmd_studies_by_collab_type <- data_fmd_only %>% 
-  mutate(disease = as_factor(disease), 
-         author_affiliation_type = as_factor(str_replace(author_affiliation_type, ' ', '+'))
-         ) %>% 
-  mutate(collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
-                                         'purely_academic', 
-                                         'mixed')
-                                 )
-         ) %>% 
-  count(collab_type, sort = TRUE, name = 'num_of_studies')
-
-knitr::kable(fmd_studies_by_collab_type)
-```
-## FMD by objective type
-```{r echo=FALSE}
-fmd_studies_by_objective_and_outbreak_type <- data_fmd_only %>% 
-  count(objectives, outbreak_type, name = 'num_of_studies') %>% 
-  pivot_wider(names_from = outbreak_type, values_from = num_of_studies)
-
-knitr::kable(fmd_studies_by_objective_and_outbreak_type)
-```
 
@@
 ```{r}
-#Tally of how many times and percentage of times each COUNTRY has been studied
-# countries_studied_by_count <- long_data_no_fmd %>% 
-#     group_by(country_studied) %>%
-#     distinct(title) %>% 
-#     count(country_studied, name = 'num_of_studies', sort = T) %>% 
-#     ungroup(country_studied) %>% 
-#     mutate(country_studied = as_factor(country_studied), 
-#            percentage = round(num_of_studies/sum(num_of_studies)*100, 1)
-#            )
-
 countries_studied_by_count <- data_without_fmd %>% 
@@
 
-#'Modify the data frame to lump together all countries with less than some number of studies as 'other' and recalculate the percentage studied
+#' Modify the data frame to lump together all countries with less than some 
+#' number of studies as 'other' and recalculate the percentage studied
 countries_studied_by_count_aggregated <- countries_studied_by_count %>% 
@@
             ) %>% 
-  filter(!(country_studied %in% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region'))) %>% 
+  filter(!(country_studied %in% c('none', 'west_africa', 'global', 
+                                  'northern_hemisphere', 'southeast_asia', 
+                                  'who_southeast_asia_region'))) %>% 
   arrange(desc(num_of_studies)) %>% 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Moved a piped operation out of the kable function

@@
   ungroup() %>%
-  mutate(percentage = round(num_of_studies/sum(num_of_studies)*100, 1))
+  mutate(percentage = round(num_of_studies/sum(num_of_studies)*100, 1)) %>% 
+  arrange(desc(percentage))
 
 #Print table of results
-knitr::kable(continents_studied_by_count %>% arrange(desc(percentage)),
+knitr::kable(continents_studied,
              col.names = c('Continent',

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Made a plot of proportions per year of mixed collaborations including and excluding academics

@@
 
-# Number of studies per disease and intervention.
+### Mixed collaborations with and without academics
+
+```{r echo=FALSE}
+academic_collabs_versus_others <- data_without_fmd %>% 
+  filter(author_affiliation_type != 'academic_institutions') %>% 
+  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 2005, publication_year
+                                         )
+                                  ), 
+         collab_type = as_factor(if_else(str_detect(author_affiliation_type, 
+                                                    'academic_institutions'),
+                                         'including_academics', 
+                                         'excluding_academics')
+                                 )
+         ) %>% 
+  count(year_aggreg, collab_type, name = 'num_of_studies')
+
+#The plot
+# Modify the x-axis labels to account for the lumping of the years from 2005 and below
+x_axis_labels <- as.character(seq(2005, 2020, 2))
+
+x_axis_labels[1] <- '1970-2005'
+
+#plot the result
+academic_collabs_trend <- ggplot(data = academic_collabs_versus_others) + 
+  geom_bar(aes(x = year_aggreg,
+               y = num_of_studies,
+               fill = collab_type
+               ),
+           color = 'black',
+           stat = 'identity',
+           position = position_fill(reverse = TRUE)  
+             ) +
+  scale_fill_manual(values = c("tan1", "turquoise1")) +
+  scale_x_continuous(breaks = seq(2005, 2020, 2),
+                     labels = x_axis_labels
+                     ) +
+  coord_flip() +
+  labs(title = 'Proportion of mixed collaborations per year',
+       x = 'Year',
+       y = 'Proportion of publications',
+       fill = 'Mixed collaboration type' 
+         ) +
+  theme_minimal(base_size = 12)
+
+plot(academic_collabs_trend)
+```
+
 ## Diseases studied

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Minor: formatted the code

@@
   group_by(continent_studied) %>%
-  summarise(num_of_studies = sum(num_of_studies), 
-            .groups = 'drop'
-            ) %>% 
+  summarise(num_of_studies = sum(num_of_studies), .groups = 'drop') %>% 
   mutate(percentage = round(num_of_studies/sum(num_of_studies), 2)*100) %>% 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed the analysis of country and continent most studied as they can be gotten from the table of counts

@@
 knitr::kable(continents_studied_by_count, 
-             caption = 'Number of studies per country'
-             )
-```
-
-### Country most studied
-```{r echo=FALSE}
-countries_studied_most <- countries_studied_by_count %>%
-    filter(country_studied != 'none') %>%
-    filter(num_of_studies == max(num_of_studies))
-
-#Print the result as a table
-knitr::kable(countries_studied_most,
-             col.names = c('Country',
-                           'Number of studies',
-                           'Percentage'
-                           ),
-             caption = 'Most studied country'
-             )
-```
-
-### Continent most studied
-```{r echo=FALSE}
-
-continent_studied_most <- continents_studied_by_count %>%
-    dplyr::filter(continent_studied != 'none') %>%
-    filter(num_of_studies == max(num_of_studies))
-
-#Print the result as a table
-knitr::kable(continent_studied_most,
-             col.names = c('Continent',
-                           'Number of studies',
-                           'Percentage'
-                           ),
-             caption = 'Most studied continent'
-             )
 ```

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Split the countries before counting their unique occurrences

@@
 countries_studied_by_count <- data_without_fmd %>% 
+  separate_rows(country_studied, sep = " ") %>%
     distinct(title, country_studied, .keep_all = TRUE) %>% 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Fixed a function call which had no closing brackets

@@
 #Print the results
-knitr::kable(vax_impact_categories_fmd %>% adorn_totals, 
+knitr::kable(vax_impact_categories_fmd %>% adorn_totals(), 
              col.names = c('Vaccination is most impactful', 

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Cleaned up the code for counting the continents studied

@@
   mutate(continent_studied = str_to_lower(continent_studied), 
-         continent_studied = case_when(str_detect(continent_studied, 'asia') == TRUE ~ 'asia', 
+         continent_studied = case_when(
+           str_detect(continent_studied, 'asia') == TRUE ~ 'asia',
            str_detect(continent_studied, 'africa') == TRUE ~ 'africa',
-                                         TRUE ~ continent_studied
-                                       )
+           TRUE ~ continent_studied)
            ) %>% 
@@
   summarise(num_of_studies = sum(num_of_studies), .groups = 'drop') %>% 
-  mutate(percentage = round(num_of_studies/sum(num_of_studies), 2)*100) %>% 
-  arrange(desc(num_of_studies))
+  arrange(desc(num_of_studies)) %>% 
+  filter(!(continent_studied %in% c('none', 'northern_hemisphere', 'global')))
 
 #Print the results
-knitr::kable(continents_studied_by_count, 
+knitr::kable(continents_studied_by_count %>% adorn_totals(), 
+             caption = "Number of studies per continent studied")
 ```

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Added a new line

@@
 ```
+
 ## Objective types

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Made a table of counts of author affiliation to the location studied by disease

@@
 ### Connection of authors to the studied locations 
+```{r}
+author_location_count_by_disease <- data_without_fmd %>%
+  mutate(author_in_country_studied = as_factor(author_in_country_studied), 
+         disease = as_factor(disease)
+         ) %>% 
+  group_by(disease) %>%
+  distinct(title, .keep_all = TRUE) %>% 
+  count(author_in_country_studied, sort = TRUE, name = "num_of_studies") %>% 
+  complete(author_in_country_studied, fill = list(num_of_studies = 0)) %>% 
+  pivot_wider(names_from = author_in_country_studied, values_from = num_of_studies) %>% 
+  replace_na(list(yes = 0, no = 0, not_applicable = 0)) %>% 
+  mutate(total = not_applicable + no + yes) %>% 
+  ungroup(disease) %>% 
+  arrange(desc(total))
+
+knitr::kable(author_location_count_by_disease,
+             caption = "Author connection to the location studied by disease")
+```
+
 # Foot and mouth disease

### 2023-06-22 analyses/scripts/orv_models_review_data_cleaning.R
Renamed the objective types

@@ -146,7 +146,11 @@ review_data_compact_cleaning_step2 <- review_data_compact_cleaning_step1 %>%
       data_available
     ),
     .fns = ~ as.factor(.x)
-  ))
+  )) %>%
+  mutate(objectives = ifelse(objectives == "future",
+                             "prospective_analysis",
+                             "retrospective_analysis")
+         )
 
 
 #' step 2a. Convert string columns to factor

### 2023-06-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Modified the table of objective types to reflect the new names
Broke up long lines

@@
     distinct(title, country_studied, .keep_all = TRUE) %>%
-    filter(country_studied %in% c('west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
+    filter(country_studied %in% c('west_africa', 'global', 
+                                  'northern_hemisphere', 'southeast_asia', 
+                                  'who_southeast_asia_region')
+           ) %>% 
     count(country_studied) %>% 
@@
 
-knitr::kable(larger_geographies_tally, caption = 'Number of studies per location larger than one country', format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
-
+knitr::kable(larger_geographies_tally, 
+             caption = 'Number of studies per location larger than one country', 
+             format = "latex", booktabs = TRUE) %>% 
+        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
 ```
@@
             ) %>% 
-  filter(!country_studied %in% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
+  filter(!country_studied %in% c('none', 'west_africa', 'global', 
+                                 'northern_hemisphere', 'southeast_asia', 
+                                 'who_southeast_asia_region')
+         ) %>% 
   arrange(desc(num_of_studies)) %>% 
@@
              format = "latex", booktabs = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'), font_size = 7)
+        kableExtra::kable_styling(latex_options = c('striped', 
+                                                    'HOLD_position'), 
+                                  font_size = 7)
 ```
@@
          ) %>% 
-  mutate(continent_studied = case_when(str_detect(continent_studied, 'asia') == TRUE ~ 'asia', 
-                                         str_detect(continent_studied, 'africa') == TRUE ~ 'africa', 
+  mutate(continent_studied = case_when(str_detect(continent_studied, 
+                                                  'asia') == TRUE ~ 'asia', 
+                                         str_detect(continent_studied, 
+                                                    'africa') == TRUE ~ 'africa', 
                                          TRUE ~ continent_studied
@@
   filter(author_in_country_studied != 'not_applicable') %>% 
-  filter(!country_studied %in% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
+  filter(!country_studied %in% c('none', 'west_africa', 'global', 
+                                 'northern_hemisphere', 'southeast_asia', 
+                                 'who_southeast_asia_region')) %>% 
 separate_rows(country_studied,  sep = ' ') %>% 
@@
 
-knitr::kable(author_connectedness_top_5_countries, caption = 'Studies with at least one author affiliation in the location studied', 
+knitr::kable(author_connectedness_top_5_countries, 
+             caption = 'Studies with at least one author affiliation in the location studied', 
              format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position', 'repeat_header'), font_size = 8)
+        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position', 
+                                                    'repeat_header'), 
+                                  font_size = 8)
 ```
@@
   filter(author_in_country_studied != 'not_applicable') %>% 
-  filter(!country_studied %in% c('other', 'none', 'northern_hemisphere', 'west_africa', 'global')) %>% 
+  filter(!country_studied %in% c('other', 'none', 'northern_hemisphere', 
+                                 'west_africa', 'global')) %>% 
   count(collab_type, author_in_country_studied, sort = TRUE) %>% 
@@
 
-knitr::kable(author_connectedness_to_location_aggreg, caption = 'At least one author with an affiliation in the studied location', 
+knitr::kable(author_connectedness_to_location_aggreg, 
+             caption = 'At least one author with an affiliation in the studied location', 
              format = "latex", booktabs = TRUE) %>% 
@@
   adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('both', 'future', 'past')) %>% 
-  adorn_pct_formatting(... = c('both', 'future', 'past')) %>% 
-  adorn_ns(... = c('both', 'future', 'past'))
+  adorn_percentages(... = c('prospective_analysis', 'retrospective_analysis')) %>% 
+  adorn_pct_formatting(... = c('prospective_analysis', 'retrospective_analysis')) %>% 
+  adorn_ns(... = c('prospective_analysis', 'retrospective_analysis'),
+           position = "front")
 

### 2023-06-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Fixed section headers
Replaced objective types with new names

@@
 
-## Locations studied
-
-### Real versus hypothetical
+## Geographic analyses
+
+### Location studied
+
+#### Real versus hypothetical
 
@@
 
-### Larger than one country
+#### Larger than one country
 
@@
 
-### Countries studied
+#### Countries studied
 
@@
 
-### Continents studied
+#### Continents studied
 
@@
 
-## Geographic connection of authors to the studied locations
+## Connection of authors to the studied locations
 
@@
               ) %>% 
-  replace_na(list(future = 0, past = 0, both = 0)) %>% 
-  adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('future', 'past', 'both')) %>% 
-  adorn_pct_formatting(... = c('future', 'past', 'both')) %>% 
-  adorn_ns(... = c('future', 'past', 'both'))
+  replace_na(list(prospective_analysis = 0, retrospective_analysis = 0, both = 0)) %>% 
+  adorn_totals(where = c('row', 'col')) %>% 
+  adorn_percentages(... = c('prospective_analysis', 'retrospective_analysis', 'both')) %>% 
+  adorn_pct_formatting(... = c('prospective_analysis', 'retrospective_analysis', 'both')) %>% 
+  adorn_ns(... = c('prospective_analysis', 'retrospective_analysis', 'both'))
 
@@
   adorn_totals(where = c('row', 'col')) %>% 
-  adorn_percentages(... = c('future', 'past')) %>% 
-  adorn_pct_formatting(... = c('future', 'past')) %>% 
-  adorn_ns(... = c('future', 'past'))
+  adorn_percentages(... = c('prospective_analysis', 'retrospective_analysis')) %>% 
+  adorn_pct_formatting(... = c('prospective_analysis', 'retrospective_analysis')) %>% 
+  adorn_ns(... = c('prospective_analysis', 'retrospective_analysis'))
 
@@
 <!--               ) %>%  -->
-<!--   replace_na(list(future = 0, past = 0, both = 0)) %>%  -->
+<!--   replace_na(list(prospective_analysis = 0, retrospective_analysis = 0, both = 0)) %>%  -->
 <!--   adorn_totals(where = c('row', 'col')) %>%  -->
-<!--   adorn_percentages(... = c('future', 'past')) %>%  -->
-<!--   adorn_pct_formatting(... = c('future', 'past')) %>%  -->
-<!--   adorn_ns(... = c('future', 'past'))  -->
+<!--   adorn_percentages(... = c('prospective_analysis', 'retrospective_analysis')) %>%  -->
+<!--   adorn_pct_formatting(... = c('prospective_analysis', 'retrospective_analysis')) %>%  -->
+<!--   adorn_ns(... = c('prospective_analysis', 'retrospective_analysis'))  -->
 

### 2023-06-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Fixed a heading

@@
 
-<!-- ## Collaboration patterns in geographic space -->
-
-## Geographic connection of authors to the studied locations 
+## Geographic analyses
+
+### Connection of authors to the studied locations 
 ```{r}

### 2023-06-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Minor: broke long lines into new lines
Added paths to the figs folders in the repo and Dropbox folders

@@
 # if the figs folder doesn't exist, create it for storing the figures
-figs_dir <- "figs"
+gh_figs_dir <- "../figs/"
+dropbox_figs_dir <- "~/Dropbox/My Academic Repository/Manuscripts/First author/In review/2022 - Systematic review of ORV models/Epidemics/submission2/manuscript_writeup/figs/"
 
@@
   filter(author_in_country_studied != 'not_applicable') %>% 
-  filter(!country_studied %in% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
+  filter(!country_studied %in% c('none', 'west_africa', 'global', 
+                                 'northern_hemisphere', 'southeast_asia',
+                                 'who_southeast_asia_region')) %>% 
   group_by(collab_type) %>% 
@@
 
-knitr::kable(author_connectedness_to_location_fmd, caption = 'Studies with at least one author affiliation in the location studied', 
+knitr::kable(author_connectedness_to_location_fmd, 
+             caption = 'Studies with at least one author affiliation in the location studied', 
              format = "latex", booktabs = TRUE) %>% 

### 2023-06-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Added code for general analyses: number of studies and plot of publications per year

@@
   filter(disease == 'fmd') 
+```
+# General analyses
+
+## Number of studied included
+Number of studies included `r nrow(compact_data_with_citation_keys)` in review.
+
+## Breakdown of studies before and after 2005
+```{r}
+before_2005 <- data_without_fmd %>% 
+  select(publication_year) %>% 
+  mutate(before_2005 = ifelse(publication_year <= 2005, "yes", "no")) %>% 
+  count(before_2005) %>% 
+  adorn_percentages(denominator = 'col') %>% 
+  adorn_pct_formatting() %>% 
+  adorn_ns(position = "front")
+
+knitr::kable(before_2005)
+```
+
+## Publications per year
+```{r}
+publications_per_year <- data_without_fmd %>%
+  count(publication_year)
+
+publications_per_year_plot <- ggplot(data = publications_per_year) +
+  geom_bar(aes(x = publication_year,
+               y = n
+               ),
+           stat = 'identity',
+           color = 'black',
+           fill = 'tomato3'
+           ) +
+  scale_y_continuous(breaks = seq(0, 30, 2),
+                     labels = seq(0, 30, 2)
+                     ) +
+  labs(x = "Year of publication", y = "Number of papers") +
+  theme_minimal(base_size = 12)
+
+plot(publications_per_year_plot)
+
+# Save to github
+ggsave(filename = "publications_per_year.tiff",
+       plot = publications_per_year_plot,
+       device = 'tiff',
+       path = figs_dir
+       )
+
+# Save to dropbox folder
+ggsave(filename = "fig2_publications_per_year.png",
+       plot = publications_per_year_plot,
+       device = 'tiff',
+       path = dropbox_figs_dir
+       )
 ```

### 2023-06-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Removed the device in ggsave to prevent confusion

@@
        plot = publications_per_year_plot,
-       device = 'tiff',
        path = figs_dir
@@
        plot = publications_per_year_plot,
-       device = 'tiff',
        path = dropbox_figs_dir

### 2023-06-25 analyses/scripts/orv_sys_rev_supplementary.Rmd
Moved some analyses from here to the main script

@@
 
-## Studies per collaboration type
-
-```{r echo=FALSE}
-#' Count the number of each author affiliation type per year (including FMD)
-collap_types_by_year <- data_without_fmd %>% 
-  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 
-                                         2005, 
-                                         publication_year
-                                         )
-                                  ), 
-         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
-                                         'Purely academic', 
-                                         'Mixed')
-                                 )
-         ) %>% 
-  count(year_aggreg, collab_type, name = 'num_of_studies') %>% 
-  pivot_wider(names_from = collab_type, values_from = num_of_studies)
-
-knitr::kable(collap_types_by_year %>% 
-               clean_names() %>% 
-               adorn_totals(... = c(mixed, purely_academic), 
-                            where = c("row", "col")
-                            )
-             )
-```
-
-```{r echo=FALSE}
-#' Count by collaboration types and make a bar plot
-collab_types_count <- data_without_fmd %>%
-  count(author_affiliation_type, sort = TRUE, name = "num_of_studies") %>% 
-  mutate(author_affiliation_type = as_factor(author_affiliation_type)) %>% 
-  arrange(desc(num_of_studies))
-
-knitr::kable(collab_types_count)
-```
-
-### Mixed collaborations with and without academics
-
-```{r echo=FALSE}
-academic_collabs_versus_others <- data_without_fmd %>% 
-  filter(author_affiliation_type != 'academic_institutions') %>% 
-  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 2005, publication_year
-                                         )
-                                  ), 
-         collab_type = as_factor(if_else(str_detect(author_affiliation_type, 
-                                                    'academic_institutions'),
-                                         'including_academics', 
-                                         'excluding_academics')
-                                 )
-         ) %>% 
-  count(year_aggreg, collab_type, name = 'num_of_studies')
-
-#The plot
-# Modify the x-axis labels to account for the lumping of the years from 2005 and below
-x_axis_labels <- as.character(seq(2005, 2020, 2))
-
-x_axis_labels[1] <- '1970-2005'
-
-#plot the result
-academic_collabs_trend <- ggplot(data = academic_collabs_versus_others) + 
-  geom_bar(aes(x = year_aggreg,
-               y = num_of_studies,
-               fill = collab_type
-               ),
-           color = 'black',
-           stat = 'identity',
-           position = position_fill(reverse = TRUE)  
-             ) +
-  scale_fill_manual(values = c("tan1", "turquoise1")) +
-  scale_x_continuous(breaks = seq(2005, 2020, 2),
-                     labels = x_axis_labels
-                     ) +
-  coord_flip() +
-  labs(title = 'Proportion of mixed collaborations per year',
-       x = 'Year',
-       y = 'Proportion of publications',
-       fill = 'Mixed collaboration type' 
-         ) +
-  theme_minimal(base_size = 12)
-
-plot(academic_collabs_trend)
-```
-
 ## Diseases studied
@@
 knitr::kable(disease_studied_count, col.names = c('Disease', 'Number of studies'))
-```
-
-## Diseases and interventions
-
-```{r echo=FALSE}
-#count the number of unique interventions modelled
-interventions_unique_entries <- long_data_no_fmd %>% 
-  group_by(title) %>% 
-  distinct(intervention_modelled, .keep_all = TRUE) %>% 
-  ungroup()
-
-#interventions are disease specific
-interventions_per_disease <- interventions_unique_entries %>% 
-  mutate(intervention_modelled = str_trim(intervention_modelled)) %>% 
-  filter(intervention_modelled != 'e.g.') %>% #remove false rows
-  filter(intervention_modelled != 'various') %>% #remove false rows
-  count(disease, intervention_modelled, name = 'num_of_studies') %>% 
-  arrange(disease, desc(num_of_studies)) %>% 
-  ungroup()
-
-knitr::kable(interventions_per_disease)
 ```

### 2023-06-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Fixed the paths for saving the figures
Revised the general analyses paragraph

@@
 
-if (!dir.exists(here::here(figs_dir))) {
-  dir.create(here::here(figs_dir),
+if (!dir.exists(here::here(gh_figs_dir))) {
+  dir.create(here::here(gh_figs_dir),
     showWarnings = TRUE
@@
 
-## Number of studied included
-Number of studies included `r nrow(compact_data_with_citation_keys)` in review.
+## Number of studies included
+
+The review involved `r nrow(compact_data_with_citation_keys)` published between
+`r min(compact_data_with_citation_keys$publication_year)` and `r max(compact_data_with_citation_keys$publication_year)`.
 

### 2023-06-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Used the right dataset name

@@
 ```{r}
-before_2005 <- data_without_fmd %>% 
+before_2005 <- compact_data_with_citation_keys_no_fmd %>% 
   select(publication_year) %>% 
@@
 ```{r}
-publications_per_year <- data_without_fmd %>%
+publications_per_year <- compact_data_with_citation_keys_no_fmd %>%
   count(publication_year)

### 2023-06-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Renamed the count variable to "num_of_studies"

@@
   mutate(before_2005 = ifelse(publication_year <= 2005, "yes", "no")) %>% 
-  count(before_2005) %>% 
+  count(before_2005, name = "num_of_studies") %>% 
   adorn_percentages(denominator = 'col') %>% 

### 2023-06-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Removed the awkward space between the x-axis and main plot

@@
   scale_y_continuous(breaks = seq(0, 30, 2),
-                     labels = seq(0, 30, 2)
+                     labels = seq(0, 30, 2),
+                     expand = c(0, 0)
+                     ) +
+    scale_x_continuous(breaks = seq(1970, 2020, 5),
+                     labels = seq(1970, 2020, 5)
                      ) +

### 2023-06-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Fixed a path
Fixed some section headings

@@
        plot = publications_per_year_plot,
-       path = figs_dir
+       path = gh_figs_dir
        )
@@
 
-## Collaboration types (aggregated)
+## Analysis of collaboration type compositions
+
+### Aggregated
 ```{r}

### 2023-06-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Added more break downs of the collaboration type analyses

@@
 
+### Number of studies per year and broken down by collaboration types
+
+```{r echo=FALSE}
+#' Count the number of each author affiliation type per year (including FMD)
+collap_types_by_year <- compact_data_with_citation_keys_no_fmd %>% 
+  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 
+                                         2005, 
+                                         publication_year
+                                         )
+                                  ), 
+         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
+                                         'Purely academic', 
+                                         'Mixed')
+                                 )
+         ) %>% 
+  count(year_aggreg, collab_type, name = 'num_of_studies') %>% 
+  pivot_wider(names_from = collab_type, values_from = num_of_studies) %>% 
+  clean_names() %>% 
+  adorn_totals(... = c(mixed, purely_academic), where = c("row", "col"))
+
+knitr::kable(collap_types_by_year,
+             caption = "Breakdown of studies per year by collaboration types")
+```
+
+```{r echo=FALSE}
+#' Count by collaboration types and make a bar plot
+collab_types_count <- compact_data_with_citation_keys_no_fmd %>%
+  count(author_affiliation_type, sort = TRUE, name = "num_of_studies") %>% 
+  mutate(author_affiliation_type = as_factor(author_affiliation_type)) %>% 
+  arrange(desc(num_of_studies)) %>% 
+  adorn_totals() %>% 
+  adorn_percentages(denominator = 'col') %>% 
+  adorn_pct_formatting() %>% 
+  adorn_ns(position = "front")
+
+knitr::kable(collab_types_count)
+```
+
+### Number of publications per year by collaboration type
+
+```{r} 
+ #' Count the number of each author affiliation type per year
+ collabs_per_year <- compact_data_with_citation_keys_no_fmd %>%
+   count(year_aggreg,
+     collab_type,
+     name = "total_publications"
+   )
+ x_axis_labels <- as.character(seq(2005, 2020, 2))
+
+ collabs_per_year_plot <- ggplot(
+   data = collabs_per_year,
+   aes(
+     x = year_aggreg,
+     y = total_publications
+   ),
+   color = "black"
+ ) +
+   geom_bar(aes(fill = collab_type),
+     stat = "identity",
+     position = "dodge"
+   ) +
+   scale_fill_manual(values = c("tan3", "turquoise2")) +
+   scale_x_continuous(
+     breaks = seq(2005, 2020, 2),
+     labels = x_axis_labels,
+     expand = c(0, 0)
+   ) +
+   scale_y_continuous(
+     breaks = seq(0, 20, 2),
+     labels = seq(0, 20, 2)
+   ) +
+   labs(
+     x = "Year",
+     y = "Total publications",
+     fill = "Collaboration type"
+   ) +
+   theme_minimal(base_size = 12) +
+   theme(legend.position = "bottom")
+
+ plot(collabs_per_year_plot)
+
+ ggsave(
+   filename = "total_collabs_per_year_plot.tiff",
+   plot = collabs_per_year_plot,
+   path = gh_figs_dir
+ )
+
+ ggsave(
+   filename = "total_collabs_per_year_plot.tiff",
+   plot = collabs_per_year_plot,
+   path = dropbox_figs_dir
+ )
+```
+
+Even though non-academic collaborations increased over time, the share of 
+total publications per year over time decreased.
+
+### Proportion of the total publications per year by collaboration type
+
+```{r echo=FALSE, fig.width=8} 
+#' Count the number of each author affiliation type per year (including FMD) 
+collap_types_by_year <- compact_data_with_citation_keys_no_fmd %>%
+  count(year_aggreg,
+    collab_type,
+    name = "total_publications"
+  )
+
+# The plot
+# Modify the x-axis labels to account for the lumping of the years from 2005 and below
+x_axis_labels <- as.character(seq(2005, 2020, 2))
+
+x_axis_labels[1] <- "1970-2005"
+
+collab_proportions_plot <- ggplot(data = collap_types_by_year) +
+  geom_bar(
+    aes(
+      x = year_aggreg,
+      y = total_publications,
+      fill = collab_type
+    ),
+    color = "black",
+    stat = "identity",
+    position = position_fill(reverse = TRUE) # ,
+    # show.legend = FALSE
+  ) +
+  scale_fill_manual(values = c("tan3", "turquoise2")) +
+  scale_x_continuous(
+    breaks = seq(2005, 2020, 2),
+    labels = x_axis_labels,
+    expand = c(0, 0)
+  ) +
+  labs(
+    x = "Year",
+    y = "Proportion of total publications",
+    fill = "Collaboration type"
+  ) +
+  theme(legend.position = "none") +
+  theme_minimal(base_size = 12)
+
+plot(collab_proportions_plot)
+
+ggsave(
+  filename = "collab_proportions.tiff",
+  plot = collab_proportions_plot,
+  path = gh_figs_dir
+)
+
+ggsave(
+  filename = "collab_proportions.tiff",
+  plot = collab_proportions_plot,
+  path = dropbox_figs_dir
+)
+```
+
+### Mixed collaborations with and without academics
+
+```{r echo=FALSE}
+academic_collabs_versus_others <- compact_data_with_citation_keys_no_fmd %>%
+  filter(author_affiliation_type != "academic_institutions") %>%
+  mutate(
+    year_aggreg = as.numeric(ifelse(publication_year < 2006, 2005, publication_year)),
+    collab_type = as_factor(if_else(str_detect(
+      author_affiliation_type,
+      "academic_institutions"
+    ),
+    "including_academics",
+    "excluding_academics"
+    ))
+  ) %>%
+  count(year_aggreg, collab_type, name = "num_of_studies")
+
+# The plot
+# Modify the x-axis labels to account for the lumping of the years from 2005 and below
+x_axis_labels <- as.character(seq(2005, 2020, 2))
+
+x_axis_labels[1] <- "1970-2005"
+
+# plot the result
+academic_collabs_trend <- ggplot(data = academic_collabs_versus_others) +
+  geom_bar(
+    aes(
+      x = year_aggreg,
+      y = num_of_studies,
+      fill = collab_type
+    ),
+    color = "black",
+    stat = "identity",
+    position = position_fill(reverse = TRUE)
+  ) +
+  scale_fill_manual(values = c("tan1", "turquoise1")) +
+  scale_x_continuous(
+    breaks = seq(2005, 2020, 2),
+    labels = x_axis_labels
+  ) +
+  coord_flip() +
+  labs(
+    title = "Proportion of mixed collaborations per year",
+    x = "Year",
+    y = "Proportion of publications",
+    fill = "Mixed collaboration type"
+  ) +
+  theme_minimal(base_size = 12)
+
+plot(academic_collabs_trend)
+```
+
 ## Geographic analyses
@@
         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
+```
+
+## Diseases and interventions
+
+```{r echo=FALSE}
+#count the number of unique interventions modelled
+interventions_unique_entries <- long_data_no_fmd %>% 
+  group_by(title) %>% 
+  distinct(intervention_modelled, .keep_all = TRUE) %>% 
+  ungroup()
+
+#interventions are disease specific
+interventions_per_disease <- interventions_unique_entries %>% 
+  mutate(intervention_modelled = str_trim(intervention_modelled)) %>% 
+  filter(intervention_modelled != 'e.g.') %>% #remove false rows
+  filter(intervention_modelled != 'various') %>% #remove false rows
+  count(disease, intervention_modelled, name = 'num_of_studies') %>% 
+  arrange(disease, desc(num_of_studies)) %>% 
+  ungroup()
+
+knitr::kable(interventions_per_disease)
+```
+### Diseases and interventions (top 2 per disease)
+
+```{r echo=FALSE}
+#count the number of unique interventions modelled
+interventions_per_disease_top2 <- long_data_no_fmd %>% 
+  group_by(title) %>% 
+  distinct(intervention_modelled, .keep_all = TRUE) %>% 
+  ungroup() %>% 
+  count(disease, intervention_modelled, name = 'num_of_studies') %>% 
+  arrange(disease, desc(num_of_studies)) %>% 
+  group_by(disease) %>% 
+  slice_head(n = 2) %>% #keep only top 2 per group 
+  ungroup()
+
+knitr::kable(interventions_per_disease_top2,
+             caption = "Top 2 most studied intervention per disease")
 ```

### 2023-06-26 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Styled the code
Removed a commented out section
Styled the code chunk and reworded the caption

@@
 ```
-
-<!-- ## Modelling methods -->
 
@@
 
-knitr::kable(outcomes_overall, caption = 'Model outcomes by collaboration type', 
+knitr::kable(outcomes_overall, 
+             caption = 'Outcomes studied by the collaboration types', 
              format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
-        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position', 'repeat_header'), font_size = 8)
+        kableExtra::kable_styling(latex_options = c('striped', 
+                                                    'HOLD_position', 
+                                                    'repeat_header'), 
+                                  font_size = 8)
 ```

### 2023-06-26 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Made the section H2 instead of H3
Separated the multiple countries entry into single rows

@@
 
-### Validation methods
+## Validation methods
 
@@
                                  'who_southeast_asia_region')) %>% 
+  separate_rows(country_studied,  sep = ' ') %>% 
   group_by(collab_type) %>% 

### 2023-06-26 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Made the section heading H2 instead of H3

@@
 
+## Parametrization methods
 ```{r eval=FALSE}
@@
 ```
-
-### Parametrization methods
 

### 2023-06-26 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Removed the wordcloud plot of the outcomes measured

@@
 ## Parametrization methods
-```{r eval=FALSE}
-outcomes_tally_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
-  mutate(outcome_measured = str_trim(outcome_measured)) %>% 
-  separate_rows(outcome_measured, sep = ',') %>% 
-  group_by(outcome_measured) %>% 
-  distinct(title, .keep_all = TRUE) %>% 
-  ungroup(outcome_measured) %>% 
-  filter(!outcome_measured %in% c('outcome_other', '')) %>% 
-  group_by(collab_type) %>% 
-  count(outcome_measured) %>% 
-  arrange(desc(n), .by_group = TRUE) %>% 
-  # slice(1:6) %>% 
-  ungroup()
-
-# outcomes_tally_plot <- ggplot(data = outcomes_tally_by_collab_type, 
-#                               aes(x = reorder(outcome_measured, n), 
-#                                   y = n
-#                                   )
-#                               ) + 
-#   geom_bar(stat = 'identity') + 
-#   labs(x = '**Outcome**', y = '**Number of times used**') +
-#   coord_flip() +
-#   facet_wrap('collab_type') +
-#   md_theme_minimal()
-
-collab_type_labels <- c('purely_academic' = 'Purely academic', 
-                        'mixed' = 'Mixed'
-                        )
-
-outcomes_tally_plot <- ggplot(data = outcomes_tally_by_collab_type, 
-                              aes(label = outcome_measured, 
-                                  size = n
-                                  )
-                              ) + 
-  geom_text_wordcloud_area() +
-  scale_size_area(max_size = 10) + 
-  facet_wrap(~ collab_type, 
-             labeller = as_labeller(collab_type_labels),
-             strip.position = 'top'
-             ) +
-  #theme_minimal() + 
-  theme(strip.text = element_text(size = 15, face = 'bold'))
-
-print(outcomes_tally_plot)
-
-ggsave(filename = 'outcomes_tally_plot.tiff',
-       plot = outcomes_tally_plot, 
-       device = 'tiff',
-       path = figs_dir
-       )
-
-ggsave(filename = 'outcomes_tally_plot.tiff',
-       plot = outcomes_tally_plot, 
-       device = 'tiff',
-       path = save_thesis_fig_here
-       )
-```
 

### 2023-06-26 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Split the outcomes measured analysis into overall and top 6 per collab type

@@
 ```{r}
-outcomes_overall <- compact_data_with_citation_keys_no_fmd %>% 
+outcomes_measured_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
   mutate(outcome_measured = str_trim(outcome_measured)) %>% 
@@
   ungroup(outcome_measured) %>% 
-  arrange(desc(num_of_studies), .by_group = TRUE) %>% 
-  ungroup() %>% 
-  adorn_totals(where = c('row')) %>% 
-  adorn_percentages(denominator = 'col') %>% 
-  adorn_pct_formatting() %>% 
-  adorn_ns()
-
-knitr::kable(outcomes_overall, 
+  arrange(desc(num_of_studies), .by_group = TRUE)
+
+knitr::kable(outcomes_measured_by_collab_type, 
              caption = 'Outcomes studied by the collaboration types', 
@@
                                                     'HOLD_position', 
-                                                    'repeat_header'), 
-                                  font_size = 8)
+                                                    'repeat_header')
+                                  )
+```
+
+### Top 6 outcomes measured by collaboration type
+```{r}
+outcomes_measured_by_collab_type_top6 <- outcomes_measured_by_collab_type %>% 
+  group_map(~ {
+    .x %>% 
+      adorn_totals() %>% 
+      adorn_percentages(denominator = "col") %>%
+      adorn_pct_formatting() %>%
+      adorn_ns()},
+    .keep = TRUE) %>% 
+  map(head, n = 6) %>% 
+  list_rbind()
+
+knitr::kable(outcomes_measured_by_collab_type_top6, 
+             caption = 'Top 6 outcomes studied by the collaboration types', 
+             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
+        kableExtra::kable_styling(latex_options = c('striped', 
+                                                    'HOLD_position', 
+                                                    'repeat_header')
+                                  )
 ```

### 2023-06-26 analyses/scripts/S4_Table.Rmd
Renamed the Rmarkdown supplementary scripts

--- 2023-05-15 analyses/scripts/full_data_extraction_citation_table.Rmd
@@
 
+## Table 1
+
+This section presents extracted data on the author affiliation type (affiliation_type), 
+whether it is a purely academic collaboration (academic_collab), and the location
+that was studied.
+
 ```{r cols_1_to_6}
@@
 
+## Table 2
+
+This section presents extracted data on the disease studied (disease), 
+type of objective studied (objectives), whether the paper had an author in
+the location studied (author_in_country_studied), and how individuals were 
+represented (individual_representation).
+
 ```{r cols_7_to_10}
@@
 ```
+## Table 3
+
+This section presents extracted data on whether spatial heterogeneity was
+represented (space_representation), the type of model structure 
+(model_structure), the type of parametrization and validation method used.
 
@@
 ```
+## Table 4
+
+This section presents extracted data on the type of outbreak and the interventions 
+studied.
 
@@
 ```
+## Table 5
+
+This section presents extracted data on whether vaccination was modelled as 
+a sole intervention for comparison against other interventions 
+(vax_modelled_with_non_vax) and the studies' conclusion on the impact of 
+vaccination (is_vax_effective).
 
@@
 
+## Table 6
+
+This section presents extracted data on the outcomes measured and whether a 
+sensitivity analysis was conducted.
+
 ```{r cols_19_to_20}
@@
 
+## Table 7
+
+This section presents extracted data on whether observed data was used for 
+model validation (data_used), and whether the data was made available 
+(data_available).
+
 ```{r cols_21_to_22}
@@
 ```
+## Table 8
+
+This section presents extracted data on whether the simulation code was made 
+available (simulation_code_available) and whether vaccination was modelled 
+(vax_modelled).
 

### 2023-06-26 analyses/scripts/S2_File.Rmd
Removed unused packages

--- 2023-06-26 analyses/scripts/orv_sys_rev_data_analysis.Rmd
@@
   library('conflicted')
-  library('ggwordcloud')
   library('here')
-  library("jsonlite")
   })

### 2023-06-26 analyses/scripts/S4_Table.Rmd
Fixed some path issues

@@
 ```{r}
-here::i_am("analyses/scripts/full_data_extraction_citation_table.Rmd")
-#I/O paths
-figs_dir <- "analyses/figs"
-data_dir <- "analyses/data"
-scripts_dir <- "analyses/scripts"
+# Paths
+figs_dir <- "../figs/"
+data_dir <- "../data"
+scripts_dir <- "../scripts"
 
@@
 ```{r load_data}
-#' re-run the data cleaning step, in case something has changed 
-#' TO DO: Use GNU make for this
-
-source(here::here(scripts_dir, "orv_models_review_data_cleaning.R"))
-
+.args <- c(here::here("data", "compact_data_with_citation_keys_cleaned.rds"))
 # The data with citations 
-compact_data_with_citation_keys <- read_rds(
-  here::here(data_dir, 'compact_data_with_citation_keys_cleaned.rds'
-  ))
+compact_data_with_citation_keys <- readRDS(.args[1])
 ```

### 2023-09-02 manuscript/submission2/outbreak_response_models_review_v2.tex
Added v1 and v2 of submitted manuscripts and associated files

--- 2023-03-02 epidemics_manuscript/outbreak_response_models_review_v2.tex
@@
 {\Large
-\textbf\newline{Outbreak response interventions to human vaccine-preventable diseases: a systematic review of modelling practices before COVID-19}
+\textbf\newline{Modelling outbreak response impact in human vaccine-preventable diseases: A systematic review of differences in practices between collaboration types before COVID19}
 }
@@
 \\
-James M. Azam\textsuperscript{1*},
-Xiaoxi Pang\textsuperscript{2},
-Elisha B. Are\textsuperscript{1, 3},
-Juliet R.C. Pulliam\textsuperscript{1},
-Matthew J. Ferrari\textsuperscript{4}
+James M. Azam\textsuperscript{1, 2*},
+Xiaoxi Pang\textsuperscript{3},
+Elisha B. Are\textsuperscript{2, 4},
+Juliet R.C. Pulliam\textsuperscript{2},
+Matthew J. Ferrari\textsuperscript{5}
 \\
 \bigskip
-\textbf{1} DSI-NRF Centre of Excellence in Epidemiological Modelling and Analysis (SACEMA), Stellenbosch University, Stellenbosch 7600, South Africa
+\textbf{1} Department of Infectious Disease Epidemiology, London School of Hygiene and Tropical Medicine, London, United Kingdom
 \\
-\textbf{2} Department of Mathematics, The University of Manchester, Manchester, UK
+\textbf{2} DSI-NRF Centre of Excellence in Epidemiological Modelling and Analysis (SACEMA), Stellenbosch University, Stellenbosch 7600, South Africa
 \\
-\textbf{3} Department of Mathematics, Simon Fraser University, Burnaby, BC, Canada
+\textbf{3} Department of Mathematics, The University of Manchester, Manchester, United Kingdom
 \\
-\textbf{4} Center for Infectious Disease Dynamics, Department of Biology, The Pennsylvania
+\textbf{4} Department of Mathematics, Simon Fraser University, Burnaby, BC, Canada
+\\
+\textbf{5} Center for Infectious Disease Dynamics, Department of Biology, The Pennsylvania
 State University, University Park, Pennsylvania, USA
@@
 
-* jamesazam@sun.ac.za
+* james.azam@lshtm.ac.uk
 
@@
 \subsection*{Background}
-Mathematical modelling can aid outbreak response decision-making.
-However, this would require collaboration among model developers, decision-makers, and local experts to incorporate appropriate realism.
-We conducted a systematic review of modelling studies on human vaccine-preventable disease (VPD) outbreaks to identify patterns in modelling practices among collaborations.
-We complemented this with a mini review of eligible studies from the foot-and-mouth disease (FMD) literature.
+Outbreak response modelling often involves collaboration among academics, and experts from governmental and non-governmental organisations.
+We conducted a systematic review of modelling studies on human vaccine-preventable disease (VPD) outbreaks to identify patterns in modelling practices between two collaboration types.
+We complemented this with a mini comparison of foot-and-mouth disease (FMD), a veterinary disease that is controllable by vaccination.
 \subsection*{Methods}
-Three databases were searched for studies published during 1970-2019 that applied models to assess the impact of an outbreak response.
-Per included study, we extracted data on author affiliation type (academic institution, governmental, and non-governmental organizations), whether at least one author was affiliated to the country studied, interventions, and model characteristics.
-Furthermore, the studies were grouped into two collaboration types: purely academic (papers with only academic affiliations), and mixed (all other combinations) to help investigate differences in modelling patterns between collaboration types in the human disease literature.
-Additionally, we compared modelling practices between the human VPD and FMD literature.
+We searched three databases for modelling studies that assessed the impact of an outbreak response.
+We extracted data on author affiliation type (academic institution, governmental, and non-governmental organizations), location studied, and whether at least one author was affiliated to the studied location.
+We also extracted the outcomes and interventions studied, and model characteristics.
+Included studies were grouped into two collaboration types: purely academic (papers with only academic affiliations), and mixed (all other combinations) to help investigate differences in modelling patterns between collaboration types in the human disease literature and overall differences with FMD collaboration practices.
 \subsection*{Results}
-Human VPDs formed 228 of 253 included studies.
+Human VPDs formed 227 of 252 included studies.
 Purely academic collaborations dominated the human disease studies (56\%).
 Notably, mixed collaborations increased in the last seven years (2013 - 2019).
-Most studies had an author in the country studied (75.2\%) but this was more likely among the mixed collaborations.
+Most studies had an author affiliated to an institution in the country studied (75.2\%) but this was more likely among the mixed collaborations.
 Contrasted to the human VPDs, mixed collaborations dominated the FMD literature (56\%).
-Furthermore, FMD studies more often had an author affiliated to the country studied (92\%) and used complex model design, including stochasticity, and model parametrization and validation.
+Furthermore, FMD studies more often had an author with an affiliation to the country studied (92\%) and used complex model design, including stochasticity, and model parametrization and validation.
 \subsection*{Conclusion}
@@
 \begin{enumerate}
-	\item We explored the nature of collaborative modelling in the human-vaccine preventable disease outbreak response literature.
-	\item Author collaborations were grouped into purely academic and mixed types.
+	\item We explored differences in collaborative modelling practices in the human-vaccine preventable disease outbreak response literature.
+	\item Collaborations were grouped into purely academic and mixed.
+	\item The collaboration types differed in terms of their model choices and practices.
 	\item Purely academic collaborations dominated the human vaccine-preventable diseases literature.
 	\item Mixed collaborations were more likely to involve local experts and use complex methods.
-	\item Mixed collaborations have more potential to lead to decision-making and are recommended.
 \end{enumerate}
 
-%\subsection*{Registration}
-%A protocol following the PRISMA guidelines for systematic review protocols and outlining the procedures for this systematic review was registered on PROSPERO with registration number CRD42020160803 and published through a peer-reviewed process.
 \linenumbers
@@
 Furthermore, involving local experts in the design of interventions has been found to boost the success of outbreak response efforts ~\cite{Sigfrid2020}.
-Consequently, outbreak response teams should ideally involve at least one local expert to provide more context~\cite{Sigfrid2020}.
+Consequently, outbreak response should ideally involve at least one local expert to provide more context~\cite{Sigfrid2020}.
 
 Mathematical modelling can support outbreak response decision-making~\cite{Lofgren2015}.
-Modelling is a proven tool for revealing insights about the extent of disease spread, and impact of interventions, while drawing on lessons learnt to provide recommendations for decision-making during outbreaks~\cite{Kretzschmar2020,Whitty2014,Lofgren2015}.
+Modelling is a proven tool for revealing insights about the extent of disease spread, and impact of interventions, and providing recommendations for decision-making during outbreaks~\cite{Kretzschmar2020,Whitty2014,Lofgren2015}.
 Insights from mathematical modelling, though often useful, only form part of the larger context (socio-economic, political, and so forth) to be considered during an outbreak, making it difficult to determine the extent to which it contributes to outbreak response decision-making ~\cite{Kretzschmar2020,Kerkhove2012}.
-One way to help ensure that modelling contributes to decision-making could be through the conduct of interdisciplinary research between model developers and decision-makers.
+One way to help ensure that modelling contributes to decision-making is the conduct of interdisciplinary research  --- that is, research conducted by authors with diverse scientific backgrounds --- between model developers and decision-makers.
 
-The link between interdisciplinarity in scientific research --- that is, research conducted by authors with diverse scientific backgrounds --- and research impact, for example, number of citations has been well-researched~\cite{Abramo2017,Wagner2011}.
+The link between interdisciplinarity in scientific research and research impact, for example, number of citations has been well-researched~\cite{Abramo2017,Wagner2011}.
 However, few studies have investigated the impact of interdisciplinary collaborations on the conduct of scientific research.
@@
 The study found that the methods used in the reviewed studies differed according to the nature of the scientific backgrounds of the authors who conducted the research.
-Our preliminary searches of the literature did not reveal any of such review studies investigating differences in research practices among collaborations in the outbreak response modelling literature.
-We, therefore, conducted a systematic review of outbreak response modelling studies of human vaccine-preventable diseases with the goal to explore the time and geographic (countries) patterns of collaboration types, and to ascertain differences in practices between the collaboration types in terms of the choice of model characteristics, modelling methods, and other topics.
 
-We sought to answer the following questions with respect to the collaboration landscape in the human disease outbreak response modelling literature: (1) How are the studies distributed in time and geographic locations, and how often is at least one of the collaborators geographically connected to the location being studied?
-(2) What types of interventions are generally modelled and is there a difference between the conclusions drawn about the impact of interventions, especially, vaccination in comparison with other non-vaccination interventions during outbreaks?
-(3) Do the model characteristics (structure and dynamics) and modelling practices (parametrization, validation, and so forth) differ between the collaboration types?
+Our preliminary search of the literature did not reveal any systematic reviews investigating differences in research practices among collaborations in the outbreak response modelling literature.
+We, therefore, conducted this systematic review of outbreak response modelling studies of human vaccine-preventable diseases with the aim to explore the time and geographic patterns in the collaboration landscape, and to investigate differences in model choices and modelling practices.
+We categorised the collaboration landscape into two types: (1) purely academic collaborations: papers with all authors affiliated to academic institutions, and (2) mixed collaborations, that is, papers with authors affiliated to a mixture of academic, government and NGO affiliations.
+Using this classification, we investigated differences in the choice of model structure, dynamics, individual and spatial heterogeneity, and modelling methods such as model parametrization, validation, sensitivity analysis, the use of data and provision of data and code for reproducibility.
 
-We acknowledge that there is a parallel body of relevant modelling work in the livestock literature.
-Specifically, the outbreak response effort that resulted from the 2001 foot-and-mouth disease (FMD) virus outbreak in the United Kingdom has been a foundational example of the application of mathematical modelling for decision-making.
+We sought to answer the following questions with respect to the two collaboration types in the human disease outbreak response modelling literature: (1) How are the studies distributed in time (years) and geographic locations, (2) Is there a difference in the practice of including local experts in modelling exercises?
+(3) Do the choice of model characteristics (structure and dynamics) and modelling methods/approaches (model parametrization and validation, outcomes of interest, sensitivity analyses, use of data, and code availability) differ between the collaboration types?
+
+Even though this review is about human VPDs, we acknowledge and include the modelling work done in the veterinary literature and in particular, for foot-and-mouth disease (FMD).
+Specifically, the outbreak response modelling effort resulting from the 2001 (FMD) outbreak in the United Kingdom has been a foundational example of the application of mathematical modelling to decision-making.
 Subsequent work based on this outbreak has been instrumental in the development of FMD outbreak intervention strategies around the world.
-Hence, even though the primary scope of this review is the application of models to inform outbreak response for human infectious diseases, we include the relevant FMD references for comparison.
-In the end, we, therefore, study the differences in terms of collaborations in the human disease modelling literature, and compare our observations to that of the FMD modelling literature to further ascertain any differences in approaches and practices between the human and livestock literature.
+We, therefore, include some relevant FMD references for comparison.
+Essentially, in this review, we study the differences in terms of collaboration types in the human disease modelling literature, and compare our observations to some parallel results from the FMD modelling literature.
+This is useful for investigating any differences in approaches and practices between the human and livestock literature and opens up opportunities for future work.
 
-%The following were the objectives of the systematic review:
-%\begin{enumerate}
-%	\item To ascertain differences in model characteristics and modelling methods between collaboration types. 
-%	\item To determine the distribution of outbreak response modelling studies over time (years) overall and in terms of collaboration types, 
-%	\item To determine how often at least one of the authors on a paper was geographically connected to the country/location studied and whether there were differences between collaboration types,
-%	\item To investigate types of interventions modelled and differences between the conclusions drawn about the impact of interventions.
-%\end{enumerate}
+The following were the objectives of the systematic review:
+\begin{enumerate}
+	\item To characterise the nature of collaboration types through geographic space and time,
+	\item To investigate if there were differences between the collaboration types regarding the inclusion of local experts,
+	\item To report differences between the collaboration types in terms of the choice of model structure, dynamics and heterogeneity, and
+	\item To investigate and report differences in modelling methods/approaches (model parametrization, validation, sensitivity analyses, code availability, and so forth) between collaboration types.
+	\item To report on miscellaneous interesting aspects captured by each study including the disease, interventions, and outcomes studied.
+\end{enumerate}
 
@@
 
-We included studies that used a mechanistic model to investigate the impact of interventions triggered by the outbreak of any of the human vaccine-preventable diseases we considered (Table 1 in \nameref{S1_File}), Ebola, or foot-and-mouth disease.
+We included studies that used a mechanistic model to investigate the impact of interventions triggered by the outbreak of any of the human vaccine-preventable diseases listed by the World Health Organization as of 2019 (Table 1 in \nameref{S1_File}).
+Aside from the WHO list, we also included Ebola because at the time of conducting this review, a vaccine had been approved for outbreak response purposes.
+We also included foot-and-mouth disease for comparison as a candidate veterinary disease that is manageable by vaccination and has been well modelled in the past.
+
 Studies were considered unique even if they had a duplicated author list or a slight variation in the author list, probably representing the same modelling group, so far as the content of the paper was different.
@@
 	\item Study used a model that is not mechanistic,
-	\item Study is not about an outbreak as defined,
+	\item Study is not about an outbreak as defined above,
 	\item Disease studied is not a human vaccine-preventable disease (Table 1 in \nameref{S1_File}), Ebola or foot-and-mouth disease,
@@
 To extract the data from the studies, we used the data extraction questionnaire implemented with the KoboToolbox web application (Section 3 in \nameref{S1_File}).
-The questionnaire was first piloted with 10 papers among the three reviewers, who worked in duplicate.
-All conflicts in terms of extracted data were resolved.
+The questionnaire was first piloted with $10$ papers among the three reviewers, who worked in duplicate.
+All conflicts in terms of extracted data were resolved through discussion and mutual agreement.
 
@@
 
-We extracted data on the type of publication, author affiliation type (academic/government/non-governmental), country/setting studied, whether at least one author affiliation was situated in the country studied, disease studied, the study objectives (retrospective/prospective impact assessment, timing of the modelling practice with respect to the outbreak (retrospective/prospective/real-time), interventions studied, and whether vaccination was the most impactful intervention when compared as a single intervention (yes/no/inconclusive).
+From each paper, we extracted data on the type of publication (original research, preprint, and so forth), author affiliation type (academic/government/non-governmental), country/setting studied, whether at least one author affiliation was situated in the country studied, disease studied, study objectives (retrospective/prospective impact assessment, timing of the modelling practice with respect to the outbreak (retrospective/prospective/real-time), interventions studied, and whether vaccination was the most impactful intervention when compared as a single intervention (yes/no/inconclusive).
 A full list of the extracted data items are provided (Section 2 in \nameref{S1_File}).
 
-From the model in each paper, we extracted data on the representation of individuals (compartmental vs individual-based), whether spatial structure was represented (yes/no), model structure (deterministic vs stochastic), model parameterization, and validation.
-We also extracted a predefined list of outcomes (cases averted, final epidemic size, etc) measured with the models.
-If an outcome was reported that was not on the pre-defined list, we collected it separately as free text for further analysis.
-We also extracted data on whether the studies included sensitivity analysis or not.
+From each model described in the methods section, we extracted data on the representation of individuals (compartmental vs individual-based), whether spatial structure was represented (yes/no), model structure (deterministic vs stochastic), model parametrization, and validation.
+We also extracted a predefined list of outcomes (final epidemic size, attack rate, cases averted, ad a host of others) measured with the models.
+If the outcome measured was not on the pre-defined list, we collected it separately as free text for further analysis.
+We collected data on whether the studies included sensitivity analysis or not.
 This was to understand how uncertainties in the model inputs were dealt with.
-We collected data on whether the studies used real world data, that is, excluding simulated data, and whether the data was openly available for download.
-We also extracted information on whether the code used for the analysis and visualization were made openly available.
+We collected data on whether the studies used observed data, that is, excluding simulated data, and whether the data was openly accessible.
+Lastly, we noted whether the code used for the analysis was openly available.
+In this regard, we classified code that was only available upon request as not available because of the barrier to access that this approach often introduces.
 
@@
 
-To summarize the conclusions drawn about the impact of vaccination as a single intervention, we grouped the studies into three categories, that is, studies that modelled non-vaccination interventions, those that modelled vaccination in combination with other interventions, and those that modelled vaccination as a single intervention for comparison with other interventions.
-The question was only applicable to the last category of interventions, so we counted the number of studies that found vaccination to be the most impactful or not.
-Where vaccination was not found to be the most impactful, we briefly summarised the reasons and modelling assumptions.
+We summarized the interventions studied by grouping the studies into three categories, that is, studies that modelled non-vaccination interventions, those that modelled vaccination in combination with other interventions, and those that modelled vaccination as a single intervention for comparison with other interventions.
+We also summarised the top two most studied intervention for each disease by counting the number of times each disease was studied per paper.
 
-For the disease studied, model characteristics (structure, dynamics, and spatial heterogeneity), and modelling practices (parametrization, validation, sensitivity analysis, data and code use and availability), we counted the number of studies per collaboration type and reported the results as percentages and fractions of the total.
+For the disease studied, model characteristics (structure, dynamics, and spatial heterogeneity), and modelling practices (parametrization, validation, sensitivity analysis, data use and available, and code use and availability), we counted the number of studies per collaboration type and reported the results as percentages and fractions of the total.
 In counting the number of papers per disease studied and outcome measured, if a study had more than one outcome measured or disease, we treated each instance as unique and counted them separately.
@@
 
-All analyses were perform in R 4.0.5 ~\cite{R2021}.
-We have provided a database of all the screened papers and their associated extracted data in a csv file, which can be accessed at \url{https://osf.io/dmvst/?view_only=b50a8d3ec21b4a07b7977d0f56e79fc3}.
-Additionally, all the analysis tables are provided as a supplement (\nameref{S2_File}).
+All analyses were perform in R version 4.3.0 ~\cite{R2023}.
+The raw analysis of the results presented in the main text have been provided as a supplement (\nameref{S2_File}).
+We have also supplied as supplementary files a pdf of tables with the database of the included studies and extracted data (\nameref{S4_Table}).
+The R code and data for this analysis can be found in a public Github repository accessible at \url{https://github.com/jamesmbaazam/orv_modelling_review_epidemics}.
 
@@
 \subsection*{Study selection}
-We retrieved a total of $12, 986$ bibliographic records from Scopus, PubMed, and Web of Science (Fig \ref{PRISMA_flowchart}).
-Using Endnote and Rayyan, we identified and removed $7, 974$ duplicates, resulting in $5, 012$ unique records for title, abstract, and full text screening.
-We exported the unique records into Rayyan for the screening in two stages.
-Stage 1 involved a title and abstract screening in duplicate by the three reviewers and resulted $4, 211$ excluded studies.
-The stage 2 screening, which involved screening the full text, led to $548$ excluded studies.
+We retrieved a total of $12, 986$ bibliographic records from Scopus, PubMed, and Web of Science (Fig \ref{fig:fig1prismaflowchart}).
+Using Endnote and Rayyan, we identified and removed $7, 974$ duplicates, resulting in $5, 012$ unique records.
+We exported the unique records into Rayyan for screening in two stages.
 
-After the full text screening, $253$ studies remained for the data extraction stage of which $228$ on human vaccine-preventable diseases and $25$ studies were on FMD.
-The FMD studies were only used for comparisons.
+Stage one involved screening titles and abstracts in duplicate by the three reviewers.
+After this stage, $4, 211$ studies were excluded.
+At stage two, we screened the full text of the remaining studies, and this led to $549$ exclusions.
 
-\begin{figure}[!h]
-	\includegraphics[scale=0.85]{figs/fig1_PRISMA_flowchart}
+After stage two, $252$ studies remained for the data extraction stage.
+Of the $252$ studies, $227$ were about human vaccine-preventable diseases and $25$ studies about foot-and-mouth disease (FMD).
+The FMD studies were not used in the main analysis but only for comparisons in the dedicated section for FMD.
+
+\begin{figure}[h!]
+	\includegraphics[scale=0.65]{figs/fig1_PRISMA_flowchart}
 	\caption{\bf The PRISMA flow chart. Numbers described here include studies for both the human vaccine-preventable diseases and foot-and-mouth disease.}
-	\label{PRISMA_flowchart}
+	\label{fig:fig1prismaflowchart}
 \end{figure}
@@
 \subsection*{Publications over time}
-Overall, a few outbreak response modelling papers were published between 1970-2005 $(3.9\%; 9/228)$, followed by a marked increase in publications until 2019 $(96.1\%; 220/228)$ (Fig \ref{publications_per_year}).
+Overall, a few relevant papers were published between 1970-2005 $(4.0\%; 9/227)$, followed by a marked increase in publications until 2019 $(96.0\%; 218/227)$ (Fig \ref{publications_per_year}).
 
 \begin{figure}[!h]	
- \includegraphics[scale=0.65]{figs/fig2_publications_per_year.png}
+ \includegraphics[scale=0.70]{figs/fig2_publications_per_year.png}
 	\caption{\bf Number of publications per year (1970-2019).}
@@
 
-Overall, papers with only authors from academic institution affiliations were the most common (56.1\%; 128/228).
-Papers with author affiliations from academic and governmental organization affiliations were the second most common (25.0\%; 57/228), and followed by those with academic and NGO affiliations (7.5\%; 17/228).
-The least common were those with governmental and NGO affiliations (0.9\%; 2/228).
+Overall, papers with all authors from academic institution affiliations were the most common (56.8\%; 129/227).
+Papers with author affiliations from academic and governmental organizations were the second most common (24.2\%; 55/227), and followed by those from academic and NGO affiliations (7.5\%; 17/227).
+The least common were those from governmental and NGO affiliations (0.9\%; 2/227).
 
-As explained earlier, we ultimately grouped the author affiliation combinations into two collaboration types.
-There were more purely academic collaborations (56.1\%; 128/228) than mixed collaborations (43.9\%; 100/228).
+As explained earlier in the methods section, for the analyses moving forward, we grouped the author affiliation combinations into two collaboration types: purely academic and mixed.
+There were more purely academic collaborations (56.8\%; 129/227) than mixed collaborations (43.2\%; 98/227).
 
@@
 \caption{\bf Number of studies per unique combination of author affiliations (human diseases).
-Here, we also show the grouping of author affiliation combinations into purely academic and mixed collaborations.
-Purely academic collaborations refer to those authored by only authors with academic institution affiliations whereas mixed collaborations include those authored by a mixture of authors with academic institution affiliations, government institutions, and NGOs or only one of the last two.}
+Here, we also show the categorization of the author affiliation combinations into purely academic and mixed collaborations.
+Papers authored by purely academic collaborations have all authors being affiliated to academic institutions whereas those authored by mixed collaborations have authors being affiliated to a combination of academic institutions, government institutions, and NGOs or only one of the last two.}
 \setlength\arrayrulewidth{1pt} 
@@
 \textbf{Collaboration type} & \textbf{Author affiliation combination} & \textbf{Number of publications} \\ \hline
-Purely academic & academic only  & 128 \\ \hline
-Mixed & academic + governmental   & 57 \\ \hline
+Purely academic & academic only  & 129 \\ \hline
+Mixed & academic + governmental   & 55 \\ \hline
 Mixed & academic + NGO                 & 17  \\ \hline
@@
 Mixed & governmental + NGO               & 2 \\ \hline  \rowcolor{gray!20}
-\textbf{Total} &  & \textbf{228} \\  \hline 
+\textbf{Total} &  & \textbf{227} \\  \hline 
 \end{tabular}
@@
 The period from 1970-2005 has been lumped up due to the lack of publications.
-Academic collaborations refer to those authored by only authors with academic institution affiliations whereas mixed collaborations include those authored by a mixture of authors with academic institution affiliations, government institutions, and NGOs.
+Academic collaborations refer papers with all authors affiliated to academic institutions whereas mixed collaborations include papers authored by a mixture of authors who are affiliated with academic institutions, government institutions, and/or NGOs.
 Mixed collaborations are represented by the turquoise bars and purely academic collaborations by the brown bars.}
@@
 \subsection*{Locations studied}
-Overall, most of the papers were about actual locations $(78.6\%; 195/248)$.
-Among these, some studied a geographic location spanning more than one country but not classifiable as a continent $(9.7\%; 19/195)$.
-Among those 19 studies, West Africa was studied the most $(47.4\%; 9/19)$, followed by the whole globe $(36.8\%; 7/19)$, Southeast Asia $(10.5\%; 2/19)$, and the Northern Hemisphere $(5.3\%; 1/19)$.
+Overall, most of the papers were about actual geographic locations $(78.9\%; 195/247)$ as compared to hypothetical locations $(21.1\%; 52/247)$.
+Among the former, some studied a geographic location spanning more than one country but not classifiable as a continent $(9.7\%; 19/195)$.
+Moreover, among those $19$ studies, West Africa was the most studied $(47.4\%; 9/19)$, followed by the whole globe $(36.8\%; 7/19)$, Southeast Asia $(10.6\%; 2/19)$, and the Northern Hemisphere $(5.3\%; 1/19)$.
 
@@
 
-When disaggregated into countries, the United States was the most studied $(21.1\%; 37/176)$, followed by China $(10.8\%; 19/176)$, Canada $(6.2\%; 11/176)$, and Sierra Leone $(5.7\%; 10/176)$.
+When disaggregated into countries, the United States was the most studied $(21.6\%; 38/176)$, followed by China $(10.8\%; 19/176)$, Canada $(6.2\%; 11/176)$, and Sierra Leone $(5.7\%; 10/176)$.
 
@@
 
-When stratified by collaboration types, mixed collaborations were more likely to have studies with at least one author in the location studied $(83.1\%; 63/77)$ compared with the purely academic collaborations $(67.5\%; 54/80)$.
+When stratified by collaboration types, mixed collaborations were more likely to have studies with at least one author in the location studied $(84.0\%; 63/75)$ compared with the purely academic collaborations $(67.1\%; 55/82)$.
 
@@
 Overall, the number of studies per disease was disproportionately distributed (Table \ref{studies_per_disease_and_collaboration_type}).
-Influenza was the most studied $(57.2\%; 135/236)$, followed by Ebola $(14.4\%; 34/236)$, Dengue $(5.1\%; 12/236)$, and a tie between Cholera $(4.7\%; 11/236)$, and Measles $(4.7\%; 11/236)$.
+Influenza was the most studied $(57.4\%; 135/235)$, followed by Ebola $(14.5\%; 34/235)$, Dengue $(5.1\%; 12/236)$, and a tie between Cholera $(4.7\%; 11/235)$, and Measles $(4.7\%; 11/235)$.
 
-When the diseases were broken down in terms of collaboration type, there were clear differences in their distribution.
+When the diseases were broken down in terms of which collaboration types studied them, there were clear differences in their distribution.
 Influenza, Dengue, and Measles were more studied by mixed collaborations whereas Ebola and Cholera were more studied by purely academic collaborations.
@@
 In counting the number of papers per disease studied, if a study was about more than one disease, we treated each instance as unique and counted them separately, leading to a total greater than the reported number of studies.}
-	\label{chap3-table: Number of studies per disease and collaboration type}
 	\begin{tabular}{|l c c c|}
@@
 		\textbf{Disease}         & \textbf{Purely academic} & \textbf{Mixed} & \textbf{Total} \\ \hline
-		Influenza                & 52.6\% (71)     & 47.4\% (64) & 135   \\ \hline
-		Ebola                    & 70.6\% (24)     & 29.4\% (10) & 35    \\ \hline
+		Influenza                & 54.1\% (73)     & 45.9\% (62) & 135   \\ \hline
+		Ebola                    & 70.6\% (24)     & 29.4\% (10) & 34    \\ \hline
 		Dengue                   & 50.0\% (6)      & 50.0\% (6)  & 12    \\ \hline
@@
 		Measles                  & 36.4\% (4)      & 63.6\% (7)  & 11    \\ \hline
-		Tuberculosis             & 85.7\% (6)      & 14.3\% (1)  & 7     \\ \hline
 		Poliomyelitis            & 28.6\% (2)      & 71.4\% (5)  & 7     \\ \hline
+		Tuberculosis             & 83.3\% (5)      & 16.7\% (1)  & 6     \\ \hline
 		Varicella                & 50.0\% (2)      & 50.0\% (2)  & 4     \\ \hline
@@
 		Mumps                    & 0.0\% (0)       & 100.0\% (1) & 1    \\ \hline \rowcolor{gray!20}
-		\textbf{Overall}			&	\textbf{55.5\% (131)}   			& \textbf{44.5\% (105)}   & \textbf{100\% (236)} \\
+		\textbf{Overall}			&	\textbf{56.2\% (132)}   			& \textbf{43.8\% (103)}   & \textbf{100\% (235)} \\
 		\hline
@@
 
-\subsection*{Intervention types and impact of vaccination}
-There were more papers about non-vaccination interventions $(48.2\%; 110/228)$, followed by those that modelled vaccination as part of a mix of interventions or do-nothing counterfactuals $(41.7\%; 95/228)$, and those that modelled vaccination as a single intervention for side-by-side comparison with other non-vaccination interventions $(10.1\%; 23/228)$.
+\subsection*{Intervention types}
+There were more papers about non-vaccination interventions $(47.6\%; 108/227)$, followed by those that modelled vaccination in combination with other interventions or do-nothing counterfactuals $(41.0\%; 93/227)$, and those that modelled vaccination as a single intervention for side-by-side comparison with other non-vaccination interventions $(11.5\%; 26/227)$.
 
-The third group of papers that modelled vaccination as a single intervention allowed us to collate conclusions on the sole impact of vaccination.
-There were approximately the same number of studies in this set of studies belonging to the two collaborations types.
+We also tabulated the top 2 interventions studied per disease (Table \ref{top2_interventions_per_disease}).
 
-Concerning the conclusions about the sole impact of vaccination as a single intervention, most of the studies found vaccination to be the most impactful single intervention in side-by-side comparison with other non-vaccination interventions $(82.6\%; 19/23)$.
-Few studies found the vaccination to be less impactful compared to other interventions and for various reasons $(17.4\%; 4/23)$.
-Influenza was the disease studied in these latter four cases.
-Isolation, and antivirals were found to be more impactful than vaccination due to reasons including the delay until a strain-specific vaccine is developed to control the disease.
+\begin{table}
+	\setlength\arrayrulewidth{1pt} 
+	\centering
+	\caption{\bf Top 2 most studied interventions per disease. We counted the unique number of times an intervention was studied per disease and reported the top two.}
+		\begin{tabular}{| l | l |}
+			\hline
+			\textbf{Disease} & \textbf{Intervention modelled} \\ \hline
+			Cholera & vaccination \\ \hline
+			Cholera & hygiene \\ \hline
+			Dengue & vaccination \\ \hline
+			Dengue & larvicides \\ \hline
+			Ebola & isolation \\ \hline
+			Ebola & safe burial \\ \hline
+			Hepatitis a & vaccination \\ \hline
+			Hepatitis b & vaccination \\ \hline
+			Influenza & vaccination \\ \hline
+			Influenza & school closure \\ \hline
+			Malaria & drugs \\ \hline
+			Malaria & treatment \\ \hline
+			Measles & vaccination \\ \hline
+			Measles & behavioural change \\ \hline
+			Meningococcal meningitis & vaccination \\ \hline
+			Meningococcal meningitis & PPE \\ \hline
+			Pertussis & vaccination \\ \hline
+			Pertussis & contact tracing \\ \hline
+			Pneumococcal disease & treatment \\ \hline
+			Poliomyelitis & vaccination \\ \hline
+			Poliomyelitis & school closure \\ \hline
+			Rubella & vaccination \\ \hline
+			Tuberculosis & treatment \\ \hline
+			Tuberculosis & vaccination \\ \hline
+			Typhoid & screening \\ \hline
+			Varicella & vaccination \\ \hline
+			Varicella & isolation \\ \hline
+			Yellow fever & vaccination \\ \hline
+		\end{tabular}
+			\label{top2_interventions_per_disease}
+	\end{table}
 
 \subsection*{Model structure, spatial heterogeneity, and model dynamics}
-There were more compartmental models $(78.5\%; 179/228)$ than agent-based models $(20.2\%; 46/228)$ with no clear difference in preference between the two collaboration types.
+There were more compartmental models $(78.9\%; 179/227)$ than agent-based models $(19.8\%; 45/227)$ with no clear difference in preference between the two collaboration types.
 
-Approximately a third of the papers included spatial heterogeneity $(28.9\%; 66/228)$ with no clear difference between the two collaboration types.
+Approximately a third of the papers included spatial heterogeneity $(28.6\%; 65/227)$ with no clear difference between the two collaboration types.
 
-Deterministic models were the most common $(62.3\%; 142/228)$ compared to stochastic $(31.6\%; 72/228)$ and hybrid models $(6.1\%; 14/228)$, that is models with both deterministic and stochastic components.
-Here, mixed collaborations were more likely to use stochastic models $(40.0\%; 40/100)$ than purely academic collaborations $(25.0\%; 32/128)$.
+Deterministic models were the most common $(63.4\%; 144/227)$ compared to stochastic $(30.4\%; 69/227)$ and hybrid models $(6.2\%; 14/227)$, that is models with both deterministic and stochastic components.
+Mixed collaborations were more likely to use stochastic models $(39.8\%; 39/100)$ than purely academic collaborations $(23.3\%; 30/128)$.
+
+\subsection*{Outcomes measured}
+We counted the unique number of times an outcome was studied by each collaboration type (Table \ref{top 6 outcomes studied by collab types}).
+Final epidemic size was the top outcome of interest in both groups.
+The top 6 outcomes were common between both groups except for intervention cost, which was more of interest to purely academic collaborations but not to mixed collaborations.
+On the other hand, number of hospitalizations was more of interest to mixed collaborations than purely academic collaborations.
+
+\begin{table}[h!]
+	 \caption{\textbf{Top 6 outcomes studied per collaboration type. Percentages are calculated from the total of studies within each collaboration type. Actual numbers are provided in brackets.}}
+	 \centering
+	 \begin{tabular}{| l | l | l |}\hline
+	 	\textbf{Collaboration type} & \textbf{Outcome measured} & \textbf{number of studies} \\ \hline
+	 	Purely academic & final epidemic size & 22.0\%  (55)\\ \hline
+	 	 & attack rate & 11.6\%  (29)\\ \hline
+	 	 & timing of peak & 8.0\%  (20)\\ \hline
+	 	 & cost & 7.2\%  (18)\\ \hline
+	 	 & outbreak duration and timing & 6.0\%  (15)\\ \hline
+	 	 & cases averted & 4.8\%  (12)\\ \hline
+	 	Mixed & final epidemic size & 14.4\%  (31)\\ \hline
+	 	 & attack rate & 13.4\%  (29)\\ \hline
+	 	 & cases averted & 10.2\%  (22)\\ \hline
+	 	 & timing of peak & 7.,4\%  (16)\\ \hline
+	 	 & outbreak duration and timing & 6.0\%  (13)\\ \hline
+	 	 & hospitalizations & 4.2\%   (9)\\ \hline
+ 	\end{tabular}
+ 	\label{top 6 outcomes studied by collab types}
+ 	\end{table}
 
 \subsection*{Model parametrization and validation}
-The top three most commonly used parametrization methods included: combining literature sources and expert opinion/assumptions, literature sources and fitting to data, and literature sources only (Table \ref{model_parametrization_results}).
+The top three most commonly used parametrization methods, that is, how model parameter values were obtained, included: combining literature sources and expert opinion/assumptions, literature sources and fitting to data, and literature sources only (Table \ref{model_parametrization_results}).
 
-The most common parametrization method among mixed collaborations was the combination of literature sources and fitting $(27.3 \%; 35/128)$, whereas the combination of literature and expert opinion was the most common among purely academic collaborations $(28.0\%; 28/100)$.
+The most common parametrization method among mixed collaborations was the combination of literature sources and fitting $(28.6 \%; 28/98)$, whereas the combination of literature and expert opinion was the most common among purely academic collaborations $(27.1\%; 35/129)$.
 
@@
 \caption{\bf Model parametrization methods.
-We define parametrization as the method of determining the parameter values for the model.
+We define model parametrization as the method of determining the parameter values for the model.
 In the table, ``Literature'' means the model's parameters were obtained from literature sources.
@@
 \begin{tabular}{| p{0.17\textwidth}  p{0.14\textwidth}  p{0.14\textwidth}  p{0.12\textwidth}  p{0.13\textwidth}  p{0.13\textwidth}  p{0.12\textwidth}  p{0.1\textwidth}  p{0.07\textwidth} |} \hline 
-\textbf{Collaboration type} & \textbf{Literature and expert opinion} & \textbf{Literature and fitted} & \textbf{Literature} & \textbf{Expert opinion} & \textbf{Literature, expert opinion, and fitted} & \textbf{Fitted} & \textbf{Expert opinion and fitted} & \textbf{Total} \\ \hline
-Academic & 27.3\% (35) & 22.7\% (29) & 18.0\% (23) & 13.3\% (17) & 9.4\% (12)  & 7.0\% (9) & 2.3\% (3) & 128 \\ \hline
-Mixed & 25.0\% (25) & 28.0\% (28) & 15.0\% (15) & 7.0\% (7) & 19.0\% (19) & 5.0\% (5) & 1.0\% (1) & 100 \\ \hline \rowcolor{gray!20}
-Overall & 26.3\% (60) & 25.0\% (57) & 16.7\% (38) & 10.5\% (24) & 13.6\% (31) & 6.1\% (14) & 1.8\% (4) & 228 \\ \hline 
+\textbf{Collaboration type} & \textbf{Literature and expert opinion} & \textbf{Literature and fitted} & \textbf{Literature} &  \textbf{Literature, expert opinion, and fitted} & \textbf{Expert opinion} & \textbf{Fitted} & \textbf{Expert opinion and fitted} & \textbf{Total} \\ \hline
+Academic & 27.1\% (35) & 21.7\% (28) & 17.8\% (23) & 10.1\% (13) & 14.0\% (18)  & 7.0\% (9) & 2.3\% (3) & 129 \\ \hline
+Mixed & 24.5\% (24) & 28.6\% (28) & 14.3\% (14) & 19.4\% (19) & 7.1\% (7) & 5.1\% (5) & 1.0\% (1) & 98 \\ \hline \rowcolor{gray!20}
+Overall & 26.3\% (59) & 24.7\% (56) & 16.3\% (37) & 14.1\% (32) & 11.0\% (25) & 6.2\% (14) & 1.8\% (4) & 227 \\ \hline 
 \end{tabular}
@@
 
-Most studies did not perform any form of validation $(63.2\%; 144/228)$.
-Approximately a third used data to validate their models $(34.6\%; 79/228)$ (Table \ref{model_validation_results}).
-Mixed collaborations were more likely to validate their model with data or the output of an independent model.
+We defined model validation as the method by which the model's performance was measured.
+Four categories of model validation were established for the purpose of this review.
+In Table \ref{model_validation_results}, we present the results.
+If the model was not validated with observed data or another model's output, we classified its validation as ``none''.
+``Data'' means the model's output was compared to independently observed data.
+``Another model’s output'' means the model's output was compared to an independent model's output.
+Some studies also used data and another model's output.
+We classified these as ``data and another model".
+
+Most studies were classified as none $(63.2\%; 144/227)$. Approximately a third used data to validate their models $(34.6\%; 79/227)$ (Table \ref{model_validation_results}).
+
+In terms of differences between the collaboration types, mixed collaborations were more likely to validate their model with data or the output of an independent model.
 
@@
 	\setlength\arrayrulewidth{1pt} 
-	\caption{\bf Model validation methods.
-We define model validation as the method by which the model's performance was measured.
-``None'' means no validation was performed, or the model’s output was compared to another output from the same model.
-``Data'' means the model was compared to independently observed data.
-``Another model’s output'' means the model's output was compared to an independent model's output.}
+	\caption{\bf Model validation methods.}
 	\begin{adjustwidth}{-0.00in}{0in}
@@
 			\textbf{Collaboration type} & \textbf{None} & \textbf{Data} & \textbf{Another model's output} & \textbf{Data and another model} & \textbf{Total} \\ \hline
-			Academic & 70.3\% (90) & 28.9\% (37) & 0.8\% (1) & 0.0\% (0) & 128 \\ \hline
-			Mixed & 54.0\% (54) & 42.0\% (42) & 3.0\% (3) & 1.0\% (1) & 100 \\ \hline \rowcolor{gray!20}
-			Overall & 63.2\% (144) & 34.6\% (79) & 1.8\% (4) & 0.4\% (1) & 228\\ \hline
+			Academic & 71.3\% (92) & 27.9\% (36) & 0.8\% (1) & 0.0\% (0) & 129 \\ \hline
+			Mixed & 53.1\% (52) & 42.9\% (42) & 3.1\% (3) & 1.0\% (1) & 98 \\ \hline \rowcolor{gray!20}
+			Overall & 63.4\% (144) & 34.4\% (79) & 1.8\% (4) & 0.4\% (1) & 227\\ \hline
 		\end{tabular}
@@
 \subsection*{Data and model simulation code}
-More than half of the papers used datasets collected independent of the study for either the model parametrization or validation process $(56.1\%; 128/228)$.
-These papers were split approximately equally between the two collaboration types.
+More than half of the papers used datasets collected independent of the study for either the model parametrization or validation process $(55.5\%; 126/227)$.
+These papers were split equally between the two collaboration types.
 
 The use of accessible data was, however, different between the two groups.
-Purely academic collaborations were more likely to use data that could be accessed in the public domain $(81.0\%; 51/63)$ compared to mixed collaborations $(56.9\%; 37/65)$.
+Purely academic collaborations were more likely to use data that could be accessed in the public domain $(82.5\%; 52/63)$ compared to mixed collaborations $(58.7\%; 37/63)$.
 
-Few papers provided access to the model simulation code $(1.7\%; 4/228)$.
+Few papers provided access to the model simulation code $(1.7\%; 4/227)$.
 Here, if a paper indicated that the authors could be contacted for the code, it was deemed as inaccessible due to the many hurdles with getting the code in time.
-Some papers reported the computer application/software/program/package used (R, Python, C++, Matlab, and so forth) but we did not collect that information.
+Additionally, some papers reported the computer application/software/program/package used (R, Python, C++, Matlab, and so forth) but we did not collect that information.
 
 \subsection*{Patterns in the foot and mouth disease (FMD) literature}
-There were $25$ studies about foot and mouth disease outbreaks.
+We included $25$ foot and mouth disease modelling studies for comparison with the human disease literature.
 Due to the small number of studies, the absolute differences between the two collaboration types were generally not large enough to be considered (\nameref{S2_File}), hence, we report on the aggregated patterns.
 
-In terms of collaboration types, slightly more than half of the $25$ studies were authored by mixed collaborations $(56.0\%; 14/25)$ than purely academic collaborations $(44.0\%; 11/25)$.
-Almost all the papers had at least one author in the location studied $(92.0\%; 23/25)$.
+Slightly more than half of the $25$ studies were authored by mixed collaborations $(56.0\%; 14/25)$.
+In terms of how connected the authors were to the locations studied, almost all the papers had at least one author affiliated to an institution in the location studied $(92.0\%; 23/25)$.
 
 Overall, vaccination was modelled as a single intervention for comparison in more than half of the studies $(56.0\%; 14/25)$, followed by vaccination in combination with other interventions $(28.0\%; 7/25)$, and no vaccination $(16.0\%; 4/25)$.
-Few of the first set of studies found vaccination to be the most impactful as a single intervention $(14.3\%; 2/14)$.
 
@@
 
+Outbreak duration and timing, final epidemic size, and intervention costs were the top three outcomes of interest overall.
+
 In terms of model parametrization, the most common method was the combined use of literature sources and expert opinion $(28.0\%; 7/25)$, followed by fitting to data only $(20.0\%; 5/25)$, and the combined use of literature sources, expert opinion, and fitting to data $(16.0\%; 4/25)$.
-Here, mixed collaborations were more likely than purely academic collaborations to combine literature sources and expert opinion $(42.9\% 6/14)$.
-Furthermore, most of the FMD models were not validated $(72.0\%; 18/25)$.
+In terms of model validation, most of the FMD models were not compared to observed data or the output of independent models $(72.0\%; 18/25)$.
 
 \section*{Discussion}
-For the period $1970-2019$, co-authorship by purely academic collaborations formed over $56\%$ of the outbreak response impact modelling studies of human vaccine-preventable diseases.
-Both collaboration types increased in absolute numbers over the past seven years.
-Regarding modelling practices between the two collaboration types, mixed collaborations were more likely to: (i) include authors affiliated through their institutions to the location studied, (ii) use more complex modelling practices including stochastic model dynamics, parametrization methods involving a combination of literature sources, expert opinion/assumptions, and fitting to data, and validate their models with data collected independent of the study.
-Even though this review was about human vaccine-preventable diseases, only 51.8\% of the studies modelled vaccination in some form.
-Moreover, only 10.1\% of the total studies modelled vaccination for comparison with other non-vaccination strategies in the same analysis.
+For the period $1970-2019$, the outbreak response intervention impact modelling literature for human vaccine-preventable diseases was dominated by purely academic collaborations.
+This collaboration type, which we defined as papers with all authors affiliated to academic institutions, formed over $56\%$ of the literature.
+Both purely academic and mixed collaborations increased in absolute numbers in the last seven years of the review period (2013-2019).
+Regarding modelling practices between the two collaboration types, mixed collaborations were more likely to: (i) include authors who were affiliated to an institutions in the location studied, (ii) use more complex modelling practices including stochastic model dynamics, parametrization methods involving a combination of literature sources, expert opinion/assumptions, and fitting to data, and validate their models with data collected independent of the study.
+Even though this review was about human vaccine-preventable diseases, only 52.5\% of the studies modelled vaccination in some form.
 Influenza was disproportionately the most studied disease, followed by Ebola, and Dengue.
+Final epidemic size and attack rate were a commonly preferred modelling outcome of interest.
+Lastly, even though all the studies conducted simulation studies, code availability was rare as only $1.8\%$ of the studies $(4/227)$ made them readily accessible.
 
-There were several differences in models and practices between the human disease literature and foot and mouth disease (FMD).
-Mixed collaborations dominated the FMD literature, with almost all papers having an author in the location studied.
+There were several differences in models and modelling practices/approaches between the human disease literature and foot and mouth disease (FMD).
+Mixed collaborations dominated the FMD literature and almost all the papers had an author in the location studied.
 Furthermore, most of the FMD models and modelling practices were more complex involving the use of spatial, stochastic, agent-based models.
@@
 
-Collaborations, especially between authors from academic institutions, governmental, and non-governmental organizations responsible for outbreak response, could lead to knowledge transfer and improved decision-making \cite{Muscatello2017}.
-Moreover, such diversity in modelling collaborations could expand the skill sets needed to solve the complex real world outbreak response needs.
-However, it is well known that there is a weak link between academic research and decision-making in general, and research findings are often not easily translated into decisions \cite{Choi2005,Deelstra2003,Muscatello2017}.
-This gap in knowledge translation exists especially between outbreak response researchers and public health decision-makers \cite{Rivers2019,Muscatello2017}.
-There are examples of the commissioning of modelling by organisations such as the US Centers for Disease Control and Prevention (CDC) and the World Health Organization (WHO) to inform decision-making during past outbreaks of Influenza, Ebola, Zika, and Dengue \cite{Muscatello2017}.
-However, many decision-makers remain cautious about the uptake of modelling due, in part, to issues about transparency in assumptions, credibility and ease of use of modelling software, and adaptability of the results to other settings and existing policies \cite{Muscatello2017}.
+We quantified the presence of mixed collaborations in outbreak response modelling between $1970$ and $2019$ (Fig \ref{studies_per_collab_type}).
+Our results show an absolute increase in the number of papers published by mixed collaborations during the period.
+Mixed or interdisciplinary collaborations have been reported to be strongly associated with research impact and translation to decision-making \cite{Deelstra2003}.
+We, however, did not measure the impact of mixed collaborations in outbreak response decision-making and therefore recommend that future studies consider pursuing this.
+Outbreak response, which is broadly an operational field, should ideally have modelling groups/collaborations that impact decision-making.
 
-To bridge this knowledge translation gap between modellers and decision-makers, modelling collaborations that deepen the interaction between model developers and decision-making have been proposed \cite{Choi2005,Rivers2019}.
-This could be achieved through the sharing of expertise so that the academics formulate, parametrize, and validate the models taking into account the expert opinions of the decision-makers so that the findings are more tailored towards implementation.
-Mixed or interdisciplinary collaborations have been reported to be strongly associated with research impact and translation to decision-making \cite{Deelstra2003}.
-Hence, outbreak response, which is broadly an operational field, would ideally have modelling groups/collaborations that are comprised of academics and decision-makers to bridge this gap.
-In this review, we observed an absolute increase in the number of papers published by mixed collaborations (Fig \ref{studies_per_collab_type}).
-This could suggest an increase in the uptake or recognition of modelling as an outbreak response decision-making tool.
-Future research to investigate and explain this increase could advance our understanding of the contribution of modelling to outbreak response decision-making.
+The increase in mixed collaborations could suggest an increase in the uptake or recognition of modelling by decision-makers in governmental and non-governmental organizations as an outbreak response decision-making tool.
+There are examples of the commissioning of modelling by organisations such as the US Centers for Disease Control and Prevention (CDC) and the World Health Organization (WHO) to support decision-making during past outbreaks of Influenza, Ebola, Zika, and Dengue \cite{Muscatello2017}.
+However, research that measures the direct impact and contributions of such collaborations to decision-making remains lacking in the literature and calls for future research \cite{Muscatello2017}.
 
@@
 We observed the same pattern for FMD albeit at a much higher percentage.
-However, when the human disease data were disaggregated, the results showed that mixed collaborations had a much higher percentage of studies with at least one author in the studied location compared to purely academic collaborations.
-Coupling this with the absolute increase in publications by mixed collaborations in the past seven years could suggest an increase in the uptake of modelling as a public health decision-making tool.
-However, we did not measure this causality.
-Research that measures the direct impact of mathematical modelling in public health decision-making remains lacking in the literature \cite{Muscatello2017}.
-Future studies designed to investigate this uptake of models and whether it has had an impact on outbreak response would contribute meaningfully to the field of outbreak response modelling.
-
-Three classes of interventions with respect to vaccination were modelled: non-vaccination (mostly antiviral use and non-pharmaceutical interventions), vaccination mixed with other complementary non-vaccination interventions, and vaccination as a single intervention for side-by-side comparison with other non-vaccination alternatives.
-The last class of interventions were the only eligible set for our analysis of the conclusions about whether vaccination is always the most impactful intervention when modelling is used as the assessment tool.
-Even though all the reviewed studies were about human vaccine-preventable diseases, only 10.1\% of the studies modelled vaccination as a single intervention for side-by-side comparison with non-vaccination interventions.
-This lack of studies assessing the sole impact of vaccination reflects the reality that vaccination is often  implemented alongside other interventions and never alone, making it difficult to assess its sole impact.
-Nevertheless, mathematical modelling is an ethically viable way to assess the sole impact of vaccination, and hence, an essential tool for decision-making.
-
-Among the studies that modelled vaccination as a single intervention for comparison with other single non-vaccination interventions, vaccination was found to be the most impactful intervention in 82\% of the studies.
-Four studies out of the 23 that modelled influenza found case isolation \cite{Yasuda2009,Gao2016,Chen2020a} and antiviral prophylaxis and/or therapeutics \cite{Gumel2008} to be more impactful than vaccination assuming those interventions could be implemented immediately, given significantly efficient isolation and large antiviral stockpiles before the outbreak/pandemic.
-Among these four studies, some common assumptions that influenced how vaccination was implemented included: the late arrival of effective vaccines \cite{Yasuda2009}, low versus high vaccination rates \cite{Gao2016}, the use of partially effective pre-existing vaccines against the current strain reactively \cite{Gumel2009} or pre-emptively \cite{Chen2018}.
-In all four studies, it was, however, recommended that, vaccination be used in combination with the alternative interventions.
-Even though antivirals were found to be more impactful in some cases, its prolonged use was discouraged to prevent the development of antiviral resistance \cite{Gumel2009}.
-On the other hand, there was a high percentage of studies in the FMD literature about the use of vaccination as a single intervention and vaccination was rarely found to be the most impactful intervention.
+When the human disease data was disaggregated, the results showed that mixed collaborations had a much higher percentage.
 
 We found some commonalities and differences in the choice of model structure and dynamics between the two collaboration types in the human disease literature.
-Mixed collaborations were more likely to use ``complex'' models and practices.
+Mixed collaborations were more likely to use agent-based model structures and model validation methods like comparing model outputs to observed data.
+These are often difficult to implement in practice and tend to lead to complex outcomes.
 We are not making any value judgements with regards to complexity but are only highlighting these differences that might require further investigation.
@@
 Our definition of mixed collaborations meant that it may have involved decision-makers.
-It is, therefore, likely that their need for practical solutions could have influenced higher levels of model details or complexity.
+It is, therefore, likely that their need for practical solutions could have influenced higher levels of model complexity.
 
 The FMD models were generally more complex than the human disease models.
-This is not surprising because the nature of FMD spread often requires the inclusion of farm structure, farm connectivity, and demographics to capture the disease's dynamics accurately \cite{Kinsley2018}.
+This is not surprising because the nature of FMD spread often requires the inclusion of farm structure, farm connectivity, and demographics to capture the disease's dynamics accurately and to capture the complex nature of the responses to outbreaks in terms of movement control and depopulations of farms \cite{Kinsley2018}.
+These levels of detail and complexity are often required in human disease outbreak models, but we observed a more frequent use among the FMD studies.
 Future studies designed to explain the differences in modelling practices of human outbreak response modelling groups might help to explain what we have observed in this review.
@@
 Additionally, only 4 studies shared their code in an easy to access form.
-On the other hand, the FMD models were generally not validated with observed data.
 Owing to this, it might be difficult to reproduce some of the results in these outbreak response modelling studies.
@@
 We, however, recommend that data and code be shared where possible to promote open science practices that help advance the field.
+The FMD models were generally not validated with observed data.
+This is most likely due to the lack of data on FMD outbreaks as most areas in the world are free of FMD outbreaks.
+The lack of data seems to have constrained FMD outbreak model validation and might serve as an opportunity to use data-free model validation techniques.
+However, these techniques were not captured in this review.
 
 This review had several limitations.
-First, outbreak response models and analyses are not always published in peer-reviewed journals, but this systematic review only focussed on peer-reviewed articles.
+First, outbreak response models and analyses are not always published in peer-reviewed journals, but this systematic review only focused on peer-reviewed articles.
 It is, therefore, possible that some relevant studies were missed by our search strategy.
@@
 Thus, we may be under-estimating the number of mixed collaborations in the literature.
-Forth, we only surveyed the literature on a specific study design – mechanistic models.
+Fourth, we only surveyed the literature on a specific study design – mechanistic models.
 We excluded statistical models and other computational models, which are not mechanistic.
@@
 Also, we  conducted our database searches in January 2020 and therefore do not reflect the literature, or any changes in practice, associated with the COVID-19 pandemic.
+This study, however, provides a baseline for comparing practices before and after the COVID-19 pandemic.
 Lastly, by only including papers published in English, we most certainly missed papers published in other languages.
@@
 
+\paragraph*{S4 Table}
+\label{S4_Table}
+{\bf Database of included studies and extracted data per paper.}
+
 %\section*{Acknowledgments}

### 2023-09-02 manuscript/submission2/submission_files/supplementary/S1 File.tex
Added v1 and v2 of submitted manuscripts and associated files

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{float}
\usepackage{rotating}
\usepackage{pdfpages}

% Title must be 250 characters or less.
\title{S1 File }

\begin{document}
\maketitle

\section{Human vaccine-preventable diseases considered}

\begin{table}[H]
	\centering
	\caption{The World Health Organization (WHO) list of diseases with an available vaccine as of Jan 1, 2020.}
	\begin{tabular}{ll}
		\toprule
		Cholera	& Mumps \\
		Dengue	&  Pertussis\\
		%	\hline
		Diphtheria	& Pneumococcal disease \\
		%	\hline
		Hepatitis A		&  Poliomyelitis\\
		%	\hline
		Hepatitis B		& Rabies \\
		%	\hline
		Hepatitis E	& 	Rotavirus \\
		%	\hline
		Haemophilus influenzae type b (Hib)		& Rubella \\
		%	\hline
		Human papillomavirus (HPV)	&  	Tetanus\\
		%	\hline
		Influenza	&  Tick-borne encephalitis	\\
		%	\hline
		Japanese encephalitis		&  Tuberculosis\\
		%	\hline
		Malaria		&  Typhoid\\
		%	\hline
		Measles		& Varicella \\
		%	\hline
		Meningococcal meningitis		&  Yellow Fever\\
		\bottomrule
	\end{tabular}
	\label{chap2-table: The World Health Organization (WHO) list of diseases with an available vaccine}
\end{table}

\section{Data items}
The following information will be extracted from each of the included studies:
\begin{enumerate}
		\item Disease(s) modelled
		\item Study's main objective(s)
		\item Location studied and whether the first or last author has an affiliation in the location
		\item Model dynamics: deterministic, stochastic, or a hybrid
		\item How individuals are represented in model: individual-bases or compartmental
		\item Whether spatial structure was included
		\item Interventions modelled: vaccination (ring, mass, targeted, prophylactic, pulse) or non-vaccination (movement restrictions, palliative care, quarantine, isolation, treatment, other(s) as indicated)
		\item Model parametrisation (We define model parametrization as the process of obtaining the model's parameter values either from literature or through some kind of mathematical or statistical technique)
		\item Method of model validation with some form of data. (We define model validation as any procedure used to evaluate the model’s suitability for the data and problem being studied)
		\item Outcome measured with model
		\item Authors’ conclusion on the predicted or potential impact of the intervention
		\item Timing of modelling practice: retrospective, real-time, other(s) as indicated
		\item Sensitivity analysis performed or not
		\item Data and code availability
	\end{enumerate}

\section{Questionnaire for data extraction}
	\subsection{Citation information}
	\begin{enumerate}
		\item What is the title of this paper?
		\item What is the year of publication? 
		\item What is the DOI of the paper? 
	\end{enumerate}

	\subsection{Collaboration }
	\begin{enumerate}[resume]
		\item Which of the following describe the nature of the author affiliations? 
		\begin{itemize}
			\item Academic institutions (universities, research institutions, etc)
			\item Government institutions (government ministries or departments, etc)
			\item Non-governmental institutions 
		\end{itemize}
		\item Which country is this study based on? [Dropdown menu of all countries including an option for hypothetical, and other, if multiple. Please specify]
		\item Are any of the author affiliations situated in the country being studied? 
		\begin{itemize}
			\item Yes 
			\item No
		\end{itemize}
	\end{enumerate}

	\subsection{Introduction}
	\subsubsection{Disease}
	\begin{enumerate}[resume]
		\item Which disease(s) was modelled in this study?
		\item Which of the following will describe the study’s broad objective(s)? 
		\begin{itemize}
			\item Assessing the potential impact/effectiveness of past interventions
			\item Assessing the potential impact/effectiveness of future/proposed interventions
			\item Other. Please indicate.
		\end{itemize}
	\end{enumerate}

\subsection{Methods}
	\subsubsection{Model structure }
	\begin{enumerate}[resume]
		\item How are individuals represented in the model? 
		\begin{itemize}
			\item Compartments, where identical individuals are grouped according to disease state
			\item Agent/Individual-based, where each agent is captured individually
		\end{itemize}
		\item Is space explicitly represented in the model? 
		\begin{itemize}
			\item Yes
			\item No
			\item Unclear. Please indicate why.
		\end{itemize}
		\item Which of the following describes the model structure?
		\begin{itemize}
			\item Deterministic
			\item Stochastic
			\item Other. Please indicate
		\end{itemize}
	\end{enumerate}

	\subsubsection{Calibration and validation}
	\begin{enumerate}[resume]
		\item How were the model’s parameter values determined? 
		\begin{itemize}
			\item Values were sourced from various literature sources, including, systematic reviews studies reporting on primary data
			\item Values were assumed/guessed based on a plausible range (expert opinion)
			\item Values were fitted to a time series 
		\end{itemize}
		\item Which of the following best describe the model validation process, that is, the process of evaluating the model’s ability to describe the dynamics of the disease?
		\begin{itemize}
			\item The model was not validated. (This includes where one set of the model’s runs were compared to another set of runs from the same model.)
			\item The model's output was compared to an independently observed dataset
			\item The model's output was compared to at least one other model's output
			\item Other. Please indicate
		\end{itemize}
	\end{enumerate}

	\subsubsection{Outbreak and intervention }
	\begin{enumerate}[resume]
		\item What type of outbreak was this study based on? 
		\begin{itemize}
			\item A real outbreak that occurred 
			\item A hypothetical outbreak
		\end{itemize}
		\item Which of the following would describe the type of intervention modelled? 
		\begin{multicols}{2}
			\begin{itemize}
				\item Antiviral prophylaxis
				\item Bednets
				\item Behaviour change
				\item Contact tracing
				\item Culling
				\item Education
				\item Face masks
				\item Handwashing
				\item Hospital bed capacity
				\item Improved hygiene
				\item Indoor/outdoor spraying
				\item Isolation
				\item Larvicides
				\item Media campaign
				\item Palliative care
				\item Protective clothing (PPE, other than face masks)
				\item Quarantine
				\item Safe burial
				\item Social/physical distancing
				\item School closure
				\item Testing/screening
				\item Travel restriction/border control
				\item Treatment
				\item Travel screening
				\item Vaccination
				\item Ventilation
				\item Workplace closure
				\item 	Other. Please indicate.
			\end{itemize}
		\end{multicols}
	\end{enumerate}

	\subsubsection{Impact of interventions}
	\begin{enumerate}[resume]
		\item Was vaccination modelled for comparison with other interventions? 
		\begin{itemize}
			\item Yes 
			\item No
		\end{itemize}
	\end{enumerate}

	\begin{enumerate}[resume]
		\item If yes, was vaccination found to be the most effective strategy in terms of the stated objective? 
		\begin{itemize}
			\item 	Yes
			\item 	No
			\item 	The outcomes were inconclusive
		\end{itemize}
		\item What was the timing of the modelling practice? 
		\begin{itemize}
			\item Prospective
			\item Retrospective
			\item In real-time during the outbreak
		\end{itemize}
		\item Which outcome was measured?
		\begin{multicols}{2}
			\begin{itemize}
				\item Cases averted
				\item Intervention coverage
				\item Lives saved
				\item Deaths prevented/averted
				\item Campaign duration
				\item Outbreak duration/timing
				\item Final epidemic size/Outbreak size/Total cases
				\item Cost (direct cost/cost-effectiveness/cost-benefit)
				\item Timing of peak
				\item Attack rate
				\item Hospitalizations
				\item QUALYS
				\item DALYs
				\item Case-fatality
				\item Other. Please indicate
			\end{itemize}
		\end{multicols}
	\end{enumerate}

	\subsubsection{Sensitivity analysis}
	\begin{enumerate}[resume]
		\item Was a sensitivity analysis performed? 
		\begin{itemize}
			\item Yes
			\item No
		\end{itemize}
	\end{enumerate}

	\subsubsection{Reproducibility/transparency}
	\textbf{Data}
	\begin{enumerate}[resume]
		\item	Was any independently observed data used in this modelling study? (Independently observed data implies data that was not simulated with the model being used for evaluation in this study.)
		\begin{itemize}
			\item No
			\item	Yes 
		\end{itemize}
		\item	If Yes, Is the independently observed data openly available? 
		\begin{itemize}
			\item	Yes
			\item	No
			\item	Nothing about this was mentioned
		\end{itemize}
	\end{enumerate}

	\subsubsection{Code}
	\begin{enumerate}[resume]
		\item	Is the simulation code openly available?
		\begin{itemize}
			\item Yes (supplementary materials, git, zenodo, google drive, etc)
			\item No, including studies in where the authors indicated they could be emailed for the simulation code
		\end{itemize}
	\end{enumerate}

\newpage	
\section{Search strings and results}
Below are the detailed search strategies and results for the three bibliographic databases used:

\begin{sidewaysfigure}
	\begin{table}[H]
		\centering
		\caption{Scopus search strings and results.}
		\begin{tabular}{lp{0.85\textwidth}l}
			\toprule
			\textbf{Search} & \textbf{Query} & \textbf{Records found} \\
			\midrule
			\#1 & TITLE-ABS-KEY ( epidemic  OR    outbreak  OR  emergency    OR  reactive  OR    crisis ) & 1,834,598 \\
			\#2 & TITLE-ABS-KEY ( respon*  OR    manage*  OR  control    OR  interven*  OR    strateg* ) & 19,366,062 \\
			\#3 & TITLE-ABS-KEY ( stochastic  OR    transmission  OR  computational  OR    mathematical  OR  mechanistic    OR  statistical  OR    simulation  OR  "In silico"  OR    dynamic* ) & 11\,890\,240 \\
			\#4 & TITLE-ABS-KEY ( model* ) & 12\,504\,649 \\
			\#5 & TITLE-ABS-KEY ( cholera  OR    dengue  OR  diphtheria    OR  ebola  OR    "Foot-and-mouth"    OR  "foot and mouth"  OR    fmd  OR  "Hepatitis A"  OR    "Hepatitis B"  OR  "Hepatitis E"  OR  "Haemophilus   influenzae type b"  OR  hib    OR  "Human   papillomavirus"  OR  hpv    OR  influenza ) )  OR   (   TITLE-ABS-KEY ( "Japanese encephalitis"  OR    malaria  OR  measles    OR  "Meningococcal   meningitis"   OR  mumps    OR  pertussis  OR    "Whooping cough"    OR  "Pneumococcal   disease"  OR  poliomyelitis  OR    polio  OR  rabies    OR  rotavirus  OR    rubella ) )  OR  ( TITLE-ABS-KEY ( tetanus  OR    "Tick-borne encephalitis"    OR  tuberculosis  OR    typhoid  OR  varicella    OR  chickenpox  OR    "Yellow Fever"    OR    "vaccine-preventable" ) )& 1\,123\,110 \\
			\#6 & TITLE-ABS-KEY ( epidemic  OR    outbreak  OR  emergency    OR  reactive  OR    crisis ) )  AND  ( TITLE-ABS-KEY ( respon*  OR    manage*  OR  control    OR  interven*  OR    strateg* ) )  AND   ( TITLE-ABS-KEY ( stochastic  OR    transmission  OR  computational  OR    mathematical  OR  mechanistic    OR  statistical  OR    simulation  OR  "In silico"  OR    dynamic* ) )  AND  ( TITLE-ABS-KEY ( model* ) )  AND    ( ( TITLE-ABS-KEY ( cholera    OR  dengue  OR    diphtheria  OR  ebola    OR    "Foot-and-mouth"    OR   "foot and   mouth"  OR  fmd    OR  "Hepatitis A"  OR    "Hepatitis B"  OR  "Hepatitis E"  OR    "Haemophilus influenzae type b"  OR    hib  OR  "Human papillomavirus"  OR    hpv  OR  influenza ) )  OR  (   TITLE-ABS-KEY ( "Japanese encephalitis"  OR    malaria  OR  measles    OR  "Meningococcal meningitis"  OR    mumps  OR  pertussis    OR  "Whooping   cough"  OR  "Pneumococcal disease"  OR    poliomyelitis  OR  polio    OR  rabies  OR    rotavirus  OR  rubella ) )    OR  ( TITLE-ABS-KEY ( tetanus  OR    "Tick-borne encephalitis"    OR  tuberculosis  OR    typhoid  OR  varicella     OR  chickenpox  OR    "Yellow Fever"    OR    "vaccine-preventable" ) ) ) & 5\,253 (5\, 095*) \\
			\multicolumn{3}{l}{*Scopus returned 5\,253 records but we could not retrieve 158 records after several attempts.}\\ \bottomrule
			\hline
		\end{tabular}
	\end{table}
\end{sidewaysfigure}

\begin{sidewaysfigure}
	\begin{table}[H]
		\centering
		\caption{PubMed search strings and results.}
		\begin{tabular}{lp{0.85\textwidth}l}
			\toprule
			\textbf{Search} & \textbf{Query} & \textbf{Records found} \\
			\midrule
			\#1 & Search (Epidemic OR Outbreak OR   Emergency OR Reactive OR Crisis) & 1\,021\,994 \\
			\#2 & Search (respon*  OR    manage*  OR  control    OR  interven*  OR    strateg*) & 9\,134\,363 \\
			\#3 & Search (Stochastic OR Transmission   OR Computational OR Mathematical OR Mechanistic OR Statistical OR Simulation   OR "In silico" OR Dynamic*) & 2\,563\,238 \\
			\#4 & Search (model*) & 2\,222\,906 \\
			\#5 & Search (Cholera OR Dengue OR   Diphtheria OR Ebola OR  "Foot-and-mouth" OR "foot and   mouth" OR FMD OR "Hepatitis A" OR "Hepatitis B" OR   "Hepatitis E" OR "Haemophilus influenzae type b" OR Hib   OR "Human papillomavirus" OR HPV OR Influenza OR "Japanese   encephalitis" OR Malaria OR Measles OR "Meningococcal   meningitis" OR Mumps OR Pertussis OR "Whooping cough" OR   "Pneumococcal disease" OR Poliomyelitis OR Polio OR Rabies OR Rotavirus   OR Rubella OR Tetanus OR "Tick-borne encephalitis" OR Tuberculosis   OR Typhoid OR Varicella OR Chickenpox OR "Yellow Fever" OR   "vaccine-preventable") & 887\,440 \\
			\#6 & Search ((((((Epidemic OR Outbreak   OR Emergency OR Reactive OR Crisis)))  AND ((Response OR Management OR Control   OR Intervention OR Strategies))) AND ((Stochastic OR Transmission OR   Computational OR Mathematical OR Mechanistic OR Statistical OR Simulation OR   "In silico" OR Dynamic*))) AND model*) AND ((Cholera OR Dengue OR   Diphtheria OR Ebola OR  "Foot-and-mouth" OR "foot and   mouth" OR FMD OR "Hepatitis A" OR  "Hepatitis B" OR   "Hepatitis E" OR "Haemophilus influenzae type b" OR Hib  OR "Human papillomavirus" OR HPV OR Influenza OR "Japanese   encephalitis" OR Malaria OR Measles OR "Meningococcal   meningitis" OR Mumps OR Pertussis OR "Whooping cough" OR   "Pneumococcal disease" OR Poliomyelitis OR Polio OR Rabies OR   Rotavirus OR Rubella OR Tetanus OR "Tick-borne encephalitis" OR   Tuberculosis OR Typhoid OR Varicella OR Chickenpox OR "Yellow Fever" OR "vaccine-preventable")) & 3\,088 \\
			\bottomrule
		\end{tabular}
	\end{table}
\end{sidewaysfigure}

\begin{sidewaysfigure}
	\begin{table}[H]
		\centering
		\caption{Web of Science search strings and results}
		\begin{tabular}{lp{0.85\textwidth}l}
			\toprule
			\textbf{Search} & \textbf{Query} & \textbf{Records found} \\
			\midrule
			\# 1 & TOPIC: (Epidemic OR Outbreak OR   Emergency OR Reactive OR Crisis) & 1\,241\,675 \\
			\# 2 & TOPIC: (respon* OR  manage*    OR  control  OR    interven*  OR  strateg*) & 13\,791\,565 \\
			\# 3 & TOPIC: (Stochastic OR Transmission   OR Computational OR Mathematical OR Mechanistic OR Statistical OR Simulat* OR    "In silico" OR Dynamic*) & 7\,869\,289 \\
			\# 4 & TOPIC: (model*) & 705\,715 \\
			\# 5 & TOPIC: (Cholera OR Dengue OR Diphtheria   OR Ebola OR "Foot-and-mouth" OR "foot and mouth" OR FMD   OR "Hepatitis A" OR "Hepatitis B" OR "Hepatitis   E" OR "Haemophilus influenzae type b" OR Hib OR "Human   papillomavirus" OR HPV OR Influenza OR "Japanese encephalitis" OR Malaria OR Measles OR "Meningococcal meningitis" OR Mumps OR  Pertussis OR "Whooping cough" OR "Pneumococcal disease"   OR Poliomyelitis OR Polio OR Rabies OR Rotavirus OR Rubella OR Tetanus OR   "Tick-borne encephalitis" OR Tuberculosis OR Typhoid OR Varicella   OR Chickenpox OR "Yellow Fever" OR "vaccine-preventable") & 8\,790\,133 \\
			\#6 & TOPIC: (Epidemic OR Outbreak OR   Emergency OR Reactive OR Crisis) AND TOPIC: (Respon* OR  Manage* OR  Control  OR    Interven*  OR  Strateg*)) AND TOPIC: (Stochastic OR   Transmission OR Computational OR Mathematical OR Mechanistic OR Statistical   OR Simulation OR In silico OR Dynamic*) AND TOPIC: (model*) AND TOPIC:   (Cholera OR Dengue OR Diphtheria OR Ebola OR  "Foot-and-mouth" OR   "foot and mouth" OR FMD OR "Hepatitis A" OR   "Hepatitis B" OR "Hepatitis E" OR "Haemophilus   influenzae type b" OR Hib OR "Human papillomavirus" OR HPV OR   Influenza OR "Japanese encephalitis" OR Malaria OR Measles OR   "Meningococcal meningitis" OR Mumps OR Pertussis OR "Whooping   cough" OR "Pneumococcal disease" OR Poliomyelitis OR Polio OR   Rabies OR Rotavirus OR Rubella OR Tetanus OR "Tick-borne   encephalitis" OR Tuberculosis OR Typhoid OR  Varicella OR Chickenpox OR   "Yellow Fever" OR "vaccine-preventable") & 4\,803 \\
			\bottomrule
		\end{tabular}
	\end{table}
\end{sidewaysfigure}

%\newpage		
%\section{Collaboration patterns in time}
%\begin{figure}[H]
%		\centering
%		\includegraphics[scale=0.75]{figs/collab_proportions.png}
%		\caption[Relative proportion (purely academic versus mixed collaborations) of studies per year.]{Relative proportion (purely academic versus mixed collaborations) of studies per year. Academic collaborations refer to those authored by only authors with academic institution affiliations whereas mixed collaborations include those authored by a mixture of authors with academic institution affiliations, government institutions, and NGOs. Mixed collaborations are represented by the turquoise bars and purely academic collaborations by the brown bars.} 
%	\end{figure}
\end{document}

### 2023-10-18 analyses/scripts/S4_Table.Rmd
Save the tex versions as well

@@
     fig_crop: no
+    keep_tex: yes
 ---

### 2023-10-18 analyses/scripts/S4_Table.tex
Generate latex version of files

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Supplementary material},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Supplementary material}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

The following table contains information on the data extracted from each
of the included studies.

Technical note: Due to the large number of rows, the table could not be
printed in one go and was instead printed a few columns at a time. In
actual fact, it is just a repetition of the title column along with the
presented columns.

\hypertarget{table-1}{%
\subsection{Table 1}\label{table-1}}

This section presents extracted data on the author affiliation type
(affiliation\_type), whether it is a purely academic collaboration
(academic\_collab), and the location that was studied.

\begin{landscape}\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}{l>{\raggedright\arraybackslash}p{4cm}l>{\raggedright\arraybackslash}p{3.5cm}l>{\raggedright\arraybackslash}p{1.5cm}}
\toprule
num & title & year & affiliation\_type & academic\_collab & location\\
\midrule
\endfirsthead
\multicolumn{6}{@{}l}{\textit{(continued)}}\\
\toprule
num & title & year & affiliation\_type & academic\_collab & location\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{a cholera metapopulation model interlinking migration with intervention strategies - a case study of zimbabwe (2008-2009)} & \cellcolor{gray!6}{2019} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{ZW}\\
2 & a theoretical single-parameter model for urbanisation to study infectious disease spread and interventions & 2019 & academic institutions + government institutions & FALSE & DK FR IS IT NL NO GB\\
\cellcolor{gray!6}{3} & \cellcolor{gray!6}{assessing the effects of modeling the spectrum of clinical symptoms on the dynamics and control of ebola} & \cellcolor{gray!6}{2019} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{LY}\\
4 & dynamical analysis and control strategies in modelling ebola virus disease & 2019 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{5} & \cellcolor{gray!6}{effect of a hepatitis a vaccination campaign during a hepatitis a outbreak in taiwan, 2015–2017: a modeling study} & \cellcolor{gray!6}{2019} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{TW}\\
\addlinespace
6 & evaluating strategies for control of tuberculosis in prisons and prevention of spillover into communities: an observational and modeling study from brazil & 2019 & academic institutions & TRUE & BR\\
\cellcolor{gray!6}{7} & \cellcolor{gray!6}{evaluating the effects of control interventions and estimating the inapparent infections for dengue outbreak in hangzhou, china} & \cellcolor{gray!6}{2019} & \cellcolor{gray!6}{government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{CN}\\
8 & incidence dynamics and investigation of key interventions in a dengue outbreak in ningbo city, china & 2019 & academic institutions + government institutions & FALSE & CN\\
\cellcolor{gray!6}{9} & \cellcolor{gray!6}{incorporating media data into a model of infectious disease transmission} & \cellcolor{gray!6}{2019} & \cellcolor{gray!6}{NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{MX US}\\
10 & influence of asymptomatic infections for the effectiveness of facemasks during pandemic influenza & 2019 & academic institutions & TRUE & none\\
\addlinespace
\cellcolor{gray!6}{11} & \cellcolor{gray!6}{mathematical analysis of a cholera infection model with vaccination strategy} & \cellcolor{gray!6}{2019} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{CN}\\
12 & modeling and stability analysis of epidemic expansion disease ebola virus with implications prevention in population & 2019 & academic institutions & TRUE & west africa\\
\cellcolor{gray!6}{13} & \cellcolor{gray!6}{modeling the effectiveness of respiratory protective devices in reducing influenza outbreak} & \cellcolor{gray!6}{2019} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{none}\\
14 & modeling the effects of vaccination and treatment on tuberculosis transmission dynamics & 2019 & academic institutions & TRUE & ET\\
\cellcolor{gray!6}{15} & \cellcolor{gray!6}{optimal control and cost-effective analysis of the 2017 meningitis outbreak in nigeria} & \cellcolor{gray!6}{2019} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{NG}\\
\addlinespace
16 & optimal control strategies for a two-group epidemic model with vaccination-resource constraints & 2019 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{17} & \cellcolor{gray!6}{optimal media reporting intensity on mitigating spread of an emerging infectious disease} & \cellcolor{gray!6}{2019} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{CN}\\
18 & school dismissal as a pandemic influenza response: when, where and for how long? & 2019 & academic institutions + government institutions & FALSE & US\\
\cellcolor{gray!6}{19} & \cellcolor{gray!6}{study on modeling simulation and optimal control method for the transmission risk of the ebola virus} & \cellcolor{gray!6}{2019} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{west africa}\\
20 & transmission dynamics of cholera with hyperinfectious and hypoinfectious vibrios: mathematical modelling and control strategies & 2019 & academic institutions & TRUE & HT\\
\addlinespace
\cellcolor{gray!6}{21} & \cellcolor{gray!6}{a new epidemics–logistics model: insights into controlling the ebola virus disease in west africa} & \cellcolor{gray!6}{2018} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{GN LR SL}\\
22 & contact reductions from live poultry market closures limit the epidemic of human infections with h7n9 influenza & 2018 & academic institutions + NGO & FALSE & CN\\
\cellcolor{gray!6}{23} & \cellcolor{gray!6}{disparities in spread and control of influenza in slums of delhi: findings from an agent-based modelling study} & \cellcolor{gray!6}{2018} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{IN}\\
24 & efficacy of control measures in the control of ebola, liberia 2014–2015 & 2018 & academic institutions & TRUE & LR\\
\cellcolor{gray!6}{25} & \cellcolor{gray!6}{epidemiology of the silent polio outbreak in rahat, israel, based on modeling of environmental surveillance data} & \cellcolor{gray!6}{2018} & \cellcolor{gray!6}{academic institutions + government institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{IL}\\
\addlinespace
26 & evaluating costs and health consequences of sick leave strategies against pandemic and seasonal influenza in norway using a dynamic model & 2018 & academic institutions & TRUE & NO\\
\cellcolor{gray!6}{27} & \cellcolor{gray!6}{evaluating vaccination strategies to control foot-and-mouth disease: a country comparison study} & \cellcolor{gray!6}{2018} & \cellcolor{gray!6}{academic institutions + government institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{AU CA NZ GB US}\\
28 & impact of public health responses during a measles outbreak in an amish community in ohio: modeling the dynamics of transmission & 2018 & academic institutions + government institutions & FALSE & US\\
\cellcolor{gray!6}{29} & \cellcolor{gray!6}{initial validation of a simulation model for estimating the impact of serogroup a neisseria meningitidis vaccination in the african meningitis belt} & \cellcolor{gray!6}{2018} & \cellcolor{gray!6}{government institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{BF}\\
30 & logistical constraints lead to an intermediate optimum in outbreak response vaccination & 2018 & academic institutions & TRUE & none\\
\addlinespace
\cellcolor{gray!6}{31} & \cellcolor{gray!6}{manipulation of contact network structure and the impact on foot-and-mouth disease transmission} & \cellcolor{gray!6}{2018} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{GB}\\
32 & mathematical model and intervention strategies for mitigating tuberculosis in the philippines & 2018 & academic institutions & TRUE & PH\\
\cellcolor{gray!6}{33} & \cellcolor{gray!6}{measles outbreak response decision-making under uncertainty: a retrospective analysis} & \cellcolor{gray!6}{2018} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{BR}\\
34 & modeling the heterogeneity of dengue transmission in a city & 2018 & academic institutions + government institutions + NGO & FALSE & CN\\
\cellcolor{gray!6}{35} & \cellcolor{gray!6}{modelling the large-scale yellow fever outbreak in luanda, angola, and the impact of vaccination} & \cellcolor{gray!6}{2018} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{AO}\\
\addlinespace
36 & quantifying the impact of early-stage contact tracing on controlling ebola diffusion & 2018 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{37} & \cellcolor{gray!6}{simulation of key interventions for seasonal influenza outbreak control at school in changsha, china} & \cellcolor{gray!6}{2018} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{CN}\\
38 & the impact of regular school closure on seasonal influenza epidemics: a data-driven spatial transmission model for belgium & 2018 & academic institutions + government institutions & FALSE & BE\\
\cellcolor{gray!6}{39} & \cellcolor{gray!6}{the potential impact of case-area targeted interventions in response to cholera outbreaks: a modeling study} & \cellcolor{gray!6}{2018} & \cellcolor{gray!6}{academic institutions + government institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{TD}\\
40 & value of inventory information in allocating a limited supply of influenza vaccine during a pandemic & 2018 & academic institutions & TRUE & US\\
\addlinespace
\cellcolor{gray!6}{41} & \cellcolor{gray!6}{an age-structured model for cholera control with vaccination} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
42 & an approach to and web-based tool for infectious disease outbreak intervention analysis & 2017 & government institutions & FALSE & none\\
\cellcolor{gray!6}{43} & \cellcolor{gray!6}{an economic assessment of foot and mouth disease in japan} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{JP}\\
44 & analysis of an seriv epidemic model of human influenza & 2017 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{45} & \cellcolor{gray!6}{control strategies of avian influenza pandemic model with time delay} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
\addlinespace
46 & costs and benefits of including inactivated in addition to oral poliovirus vaccine in outbreak response after cessation of oral poliovirus vaccine use & 2017 & NGO & FALSE & NG\\
\cellcolor{gray!6}{47} & \cellcolor{gray!6}{deriving effective vaccine allocation strategies for pandemic influenza: comparison of an agent-based simulation and a compartmental model} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{US}\\
48 & early rigorous control interventions can largely reduce dengue outbreak magnitude: experience from chaozhou, china & 2017 & academic institutions & TRUE & CN\\
\cellcolor{gray!6}{49} & \cellcolor{gray!6}{effects of reactive social distancing on the 1918 influenza pandemic} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{GB}\\
50 & epidemiological and economic impact of pandemic influenza in chicago: priorities for vaccine interventions & 2017 & academic institutions & TRUE & US\\
\addlinespace
\cellcolor{gray!6}{51} & \cellcolor{gray!6}{estimating direct and indirect protective effect of influenza vaccination in the united states} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{US}\\
52 & evaluating the effects of common control measures for influenza a (h1n1) outbreak at school in china: a modeling study & 2017 & academic institutions + government institutions & FALSE & CN\\
\cellcolor{gray!6}{53} & \cellcolor{gray!6}{evaluation of strategies to control a potential outbreak of foot-and-mouth disease in sweden} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{SE}\\
54 & impact of a waning vaccine and altered behavior on the spread of influenza & 2017 & academic institutions + government institutions & FALSE & none\\
\cellcolor{gray!6}{55} & \cellcolor{gray!6}{mathematical models for devising the optimal ebola virus disease eradication} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{LR}\\
\addlinespace
56 & modeling the role of public health education in ebola virus disease outbreaks in sudan & 2017 & academic institutions & TRUE & SD\\
\cellcolor{gray!6}{57} & \cellcolor{gray!6}{modelling the transmission and control strategies of varicella among school children in shenzhen, china} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{CN}\\
58 & optimal and adaptive control of an epidemic model of influenza with unknown parameters & 2017 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{59} & \cellcolor{gray!6}{simulating endogenous dynamics of intervention-capacity deployment: ebola outbreak in liberia} & \cellcolor{gray!6}{2017} & \cellcolor{gray!6}{academic institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{LR}\\
60 & simulating the potential role of media coverage and infected bats in the 2014 ebola outbreak & 2017 & academic institutions & TRUE & west africa\\
\addlinespace
\cellcolor{gray!6}{61} & \cellcolor{gray!6}{a mathematical model of ebola virus disease: using sensitivity analysis to determine effective intervention targets} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
62 & a multi-agent model for adaptive vaccination during infectious disease outbreaks & 2016 & academic institutions + government institutions & FALSE & US\\
\cellcolor{gray!6}{63} & \cellcolor{gray!6}{assessing the efficiency of movement restriction as a control strategy of ebola} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
64 & characterization of outbreak response strategies and potential vaccine stockpile needs for the polio endgame & 2016 & government institutions + NGO & FALSE & global\\
\cellcolor{gray!6}{65} & \cellcolor{gray!6}{designing public health policies to mitigate the adverse consequences of rural-urban migration via meta-population modeling} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
\addlinespace
66 & dynamic model of influenza with age-structured and media coverage & 2016 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{67} & \cellcolor{gray!6}{economic evaluation of individual school closure strategies: the hong kong 2009 h1n1 pandemic} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{HK}\\
68 & efficient vaccine distribution based on a hybrid compartmental model & 2016 & academic institutions & TRUE & HK\\
\cellcolor{gray!6}{69} & \cellcolor{gray!6}{epidemiological evaluation of different fmd control strategies in two selected regions in austria} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{AT}\\
70 & evaluating targeted interventions via meta-population models with multi-level mixing & 2016 & academic institutions + government institutions & FALSE & US\\
\addlinespace
\cellcolor{gray!6}{71} & \cellcolor{gray!6}{evaluation of outbreak response immunization in the control of pertussis using agent-based modeling} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{CA}\\
72 & global stability and optimal control for a tuberculosis model with vaccination and treatment & 2016 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{73} & \cellcolor{gray!6}{impact on epidemic measles of vaccination campaigns triggered by disease outbreaks or serosurveys: a modeling study} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{NP NE YE ZM}\\
74 & metapopulation and non-proportional vaccination models overview & 2016 & academic institutions & TRUE & MX\\
\cellcolor{gray!6}{75} & \cellcolor{gray!6}{model-based comprehensive analysis of school closure policies for mitigating influenza epidemics and pandemics} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions + government institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{GB}\\
\addlinespace
76 & modeling ring-vaccination strategies to control ebola virus disease epidemics & 2016 & academic institutions & TRUE & west africa\\
\cellcolor{gray!6}{77} & \cellcolor{gray!6}{modeling the effect of public health resources and alerting on the dynamics of pertussis spread*} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{US}\\
78 & modeling the impact of behavior change on the spread of ebola & 2016 & academic institutions & TRUE & LY\\
\cellcolor{gray!6}{79} & \cellcolor{gray!6}{modeling the spread of polio in an ipv-vaccinated population: lessons learned from the 2013 silent outbreak in southern israel} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{IL}\\
80 & modelling weekly vector control against dengue in the guangdong province of china & 2016 & academic institutions & TRUE & CN\\
\addlinespace
\cellcolor{gray!6}{81} & \cellcolor{gray!6}{optimal control strategies for the spread of ebola in west africa} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{west africa}\\
82 & potential impact of a ventilation intervention for influenza in the context of a dense indoor contact network in hong kong & 2016 & academic institutions & TRUE & HK\\
\cellcolor{gray!6}{83} & \cellcolor{gray!6}{predicting and evaluating the epidemic trend of ebola virus disease in the 2014-2015 outbreak and the effects of intervention measures} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{west africa}\\
84 & projected impact of dengue vaccination in yucatán, mexico & 2016 & academic institutions + government institutions & FALSE & MX\\
\cellcolor{gray!6}{85} & \cellcolor{gray!6}{seasonality and the effectiveness of mass vaccination} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{none}\\
\addlinespace
86 & simulation optimization for an age-based vaccines distribution strategy against the spread of influenza epidemic & 2016 & academic institutions & TRUE & MX\\
\cellcolor{gray!6}{87} & \cellcolor{gray!6}{spatiotemporal dynamics of the ebola epidemic in guinea and implications for vaccination and disease elimination: a computational modeling analysis} & \cellcolor{gray!6}{2016} & \cellcolor{gray!6}{academic institutions + government institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{GN}\\
88 & the interplay of vaccination and vector control on small dengue networks & 2016 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{89} & \cellcolor{gray!6}{an epidemic patchy model with entry–exit screening} & \cellcolor{gray!6}{2015} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
90 & assessing the role of voluntary self-isolation in the control of pandemic influenza using a household epidemic model & 2015 & academic institutions & TRUE & none\\
\addlinespace
\cellcolor{gray!6}{91} & \cellcolor{gray!6}{be-codis: a mathematical model to predict the risk of human diseases spread between countries—validation and application to the 2014–2015 ebola virus disease epidemic} & \cellcolor{gray!6}{2015} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{global}\\
92 & dengue in madeira island & 2015 & academic institutions & TRUE & PT\\
\cellcolor{gray!6}{93} & \cellcolor{gray!6}{dynamic simulation of a seiqr-v epidemic model based on cellular automata} & \cellcolor{gray!6}{2015} & \cellcolor{gray!6}{academic institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{MX}\\
94 & early vaccine availability represents an important public health advance for the control of pandemic influenza & 2015 & academic institutions & TRUE & CA\\
\cellcolor{gray!6}{95} & \cellcolor{gray!6}{effectiveness of ebola treatment units and community care centers — liberia, september 23–october 31, 2014} & \cellcolor{gray!6}{2015} & \cellcolor{gray!6}{government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{LR}\\
\addlinespace
96 & evaluation of the benefts and risks of introducing ebola community care centers, sierra leone & 2015 & academic institutions + NGO & FALSE & SL\\
\cellcolor{gray!6}{97} & \cellcolor{gray!6}{evidence for emergency vaccination having played a crucial role to control the 1965/66 foot-and-mouth disease outbreak in switzerland} & \cellcolor{gray!6}{2015} & \cellcolor{gray!6}{academic institutions + government institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{CH}\\
98 & measuring the impact of ebola control measures in sierra leone & 2015 & academic institutions & TRUE & SL\\
\cellcolor{gray!6}{99} & \cellcolor{gray!6}{media impact switching surface during an infectious disease outbreak} & \cellcolor{gray!6}{2015} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{CN}\\
100 & modeling options to manage type 1 wild poliovirus imported into israel in 2013 & 2015 & academic institutions + government institutions & FALSE & IL\\
\addlinespace
\cellcolor{gray!6}{101} & \cellcolor{gray!6}{modeling the effect of comprehensive interventions on ebola virus transmission} & \cellcolor{gray!6}{2015} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{GN LR SL}\\
102 & modeling the effect of school closures in a pandemic scenario: exploring two different contact matrices & 2015 & academic institutions + government institutions & FALSE & US\\
\cellcolor{gray!6}{103} & \cellcolor{gray!6}{modelling the effect of early detection of ebola} & \cellcolor{gray!6}{2015} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{west africa}\\
104 & multi-scale modeling for the transmission of influenza and the evaluation of interventions toward it & 2015 & academic institutions & TRUE & US\\
\cellcolor{gray!6}{105} & \cellcolor{gray!6}{optimal intervention strategies for a seir control model of ebola epidemics} & \cellcolor{gray!6}{2015} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
\addlinespace
106 & predicting the extinction of ebola spreading in liberia due to mitigation strategies & 2015 & academic institutions & TRUE & LR\\
\cellcolor{gray!6}{107} & \cellcolor{gray!6}{school closure strategies for the 2009 hong kong hini influenza pandemic} & \cellcolor{gray!6}{2015} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{HK}\\
108 & spatiotemporal spread of the 2014 outbreak of ebola virus disease in liberia and the effectiveness of non-pharmaceutical interventions: a computational modelling analysis & 2015 & academic institutions + NGO & FALSE & LR\\
\cellcolor{gray!6}{109} & \cellcolor{gray!6}{strategies for early vaccination during novel influenza outbreaks} & \cellcolor{gray!6}{2015} & \cellcolor{gray!6}{academic institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{CA}\\
110 & the effects of media reports on disease spread and important public health measurements & 2015 & academic institutions + NGO & FALSE & CA\\
\addlinespace
\cellcolor{gray!6}{111} & \cellcolor{gray!6}{the impact of human behavioral changes in 2014 west africa ebola outbreak} & \cellcolor{gray!6}{2015} & \cellcolor{gray!6}{NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{GN LR SL}\\
112 & transmission dynamics and final epidemic size of ebola virus disease outbreaks with varying interventions & 2015 & academic institutions & TRUE & west africa\\
\cellcolor{gray!6}{113} & \cellcolor{gray!6}{treatment–donation-stockpile dynamics in ebola convalescent blood transfusion therapy} & \cellcolor{gray!6}{2015} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{west africa}\\
114 & vaccine prioritization for effective pandemic response & 2015 & academic institutions + government institutions & FALSE & US\\
\cellcolor{gray!6}{115} & \cellcolor{gray!6}{a mathematical study of a tb model with treatment interruptions and two latent periods} & \cellcolor{gray!6}{2014} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
\addlinespace
116 & antiviral prophylaxis and isolation for the control of pandemic influenza & 2014 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{117} & \cellcolor{gray!6}{assessing the impact of travel restrictions on international spread of the 2014 west african ebola epidemic} & \cellcolor{gray!6}{2014} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{global}\\
118 & assessing the use of antiviral treatment to control influenza & 2014 & academic institutions & TRUE & CA\\
\cellcolor{gray!6}{119} & \cellcolor{gray!6}{behavior in the time of cholera: evidence from the 2008-2009 cholera outbreak in zimbabwe} & \cellcolor{gray!6}{2014} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{ZW}\\
120 & behavioural response in educated young adults towards influenza a(h1n1)pdm09 & 2014 & academic institutions + government institutions & FALSE & none\\
\addlinespace
\cellcolor{gray!6}{121} & \cellcolor{gray!6}{cover your cough! quantifying the benefits of a localized healthy behavior intervention on flu epidemics in washington dc} & \cellcolor{gray!6}{2014} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{US}\\
122 & dynamics and control of ebola virus transmission in montserrado, liberia: a mathematical modelling analysis & 2014 & academic institutions + government institutions & FALSE & LR\\
\cellcolor{gray!6}{123} & \cellcolor{gray!6}{estimating the effectiveness of early control measures through school absenteeism surveillance in observed outbreaks at rural schools in hubei, china} & \cellcolor{gray!6}{2014} & \cellcolor{gray!6}{academic institutions + government institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{CN}\\
124 & evaluation of the benefit of emergency vaccination in a foot-and-mouth disease free country with low livestock density & 2014 & academic institutions + government institutions & FALSE & CH\\
\cellcolor{gray!6}{125} & \cellcolor{gray!6}{modeling the dynamics of oral poliovirus vaccine cessation} & \cellcolor{gray!6}{2014} & \cellcolor{gray!6}{academic institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{none}\\
\addlinespace
126 & modeling the impact of optimal screening on typhoid dynamics & 2014 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{127} & \cellcolor{gray!6}{modeling the influence of environment and intervention oncholera in haiti} & \cellcolor{gray!6}{2014} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{HT}\\
128 & sequential bayesian inference in hidden markov stochastic kinetic models with application to detection and response to seasonal epidemics & 2014 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{129} & \cellcolor{gray!6}{simulating optimal vaccination times during cholera outbreaks} & \cellcolor{gray!6}{2014} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
130 & the role of vaccination coverage, individual behaviors, and the public health response in the control of measles epidemics: an agent-based simulation for california & 2014 & academic institutions & TRUE & US\\
\addlinespace
\cellcolor{gray!6}{131} & \cellcolor{gray!6}{time is (still) of the essence: quantifying the impact of emergency meningitis vaccination response in katsina state, nigeria} & \cellcolor{gray!6}{2014} & \cellcolor{gray!6}{academic institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{NG}\\
132 & a perspective on multiple waves of influenza pandemics & 2013 & academic institutions & TRUE & US\\
\cellcolor{gray!6}{133} & \cellcolor{gray!6}{an optimal control problem arising from a dengue disease transmission model} & \cellcolor{gray!6}{2013} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
134 & cholera in haiti: reproductive numbers and vaccination coverage estimates & 2013 & academic institutions + government institutions & FALSE & HT\\
\cellcolor{gray!6}{135} & \cellcolor{gray!6}{comparing control strategies against foot-and-mouth disease: will vaccination be cost-effective in denmark?} & \cellcolor{gray!6}{2013} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{DK}\\
\addlinespace
136 & cost-effectiveness of influenza control measures: a dynamic transmission model-based analysis & 2013 & academic institutions & TRUE & TW\\
\cellcolor{gray!6}{137} & \cellcolor{gray!6}{cost-effectiveness of workplace closure and travel restriction for mitigating influenza outbreaks: a network-based simulation} & \cellcolor{gray!6}{2013} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
138 & decisions on control of foot-and-mouth disease informed using model predictions & 2013 & academic institutions & TRUE & DK\\
\cellcolor{gray!6}{139} & \cellcolor{gray!6}{dengue in cape verde: vector control and vaccination} & \cellcolor{gray!6}{2013} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{CV}\\
140 & enhancement of collective immunity in tokyo metropolitan area by selective vaccination against an emerging influenza pandemic & 2013 & academic institutions & TRUE & JP\\
\addlinespace
\cellcolor{gray!6}{141} & \cellcolor{gray!6}{estimated impact of aggressive empirical antiviral treatment in containing an outbreak of pandemic influenza h1n1 in an isolated first nations community} & \cellcolor{gray!6}{2013} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{CA}\\
142 & multiregional dynamic vaccine allocation during an influenza epidemic & 2013 & academic institutions & TRUE & US\\
\cellcolor{gray!6}{143} & \cellcolor{gray!6}{policies to reduce influenza in the workplace: impact assessments using an agent-based model} & \cellcolor{gray!6}{2013} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{US}\\
144 & transmission dynamics of the 2009 influenza a (h1n1) pandemic in india: the impact of holiday-related school closure & 2013 & academic institutions & TRUE & IN\\
\cellcolor{gray!6}{145} & \cellcolor{gray!6}{vaccination against foot-and-mouth disease: do initial conditions affect its benefit?} & \cellcolor{gray!6}{2013} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{GB}\\
\addlinespace
146 & was mandatory quarantine necessary in china for controlling the 2009 h1n1 pandemic? & 2013 & academic institutions + NGO & FALSE & CN\\
\cellcolor{gray!6}{147} & \cellcolor{gray!6}{a contact-network-based simulation model for evaluating interventions under 'what-if' scenarios in epidemic} & \cellcolor{gray!6}{2012} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{SG}\\
148 & campus quarantine (fengxiao) for curbing emergent infectious diseases: lessons from mitigating a/h1n1 in xi'an, china & 2012 & academic institutions + NGO & FALSE & CN\\
\cellcolor{gray!6}{149} & \cellcolor{gray!6}{dynamic modelling of costs and health consequences of school closure during an influenza pandemic} & \cellcolor{gray!6}{2012} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{NO}\\
150 & effect of vaccines and antivirals during the major 2009 a(h1n1) pandemic wave in norway - and the influence of vaccination timing & 2012 & academic institutions + government institutions + NGO & FALSE & NO\\
\addlinespace
\cellcolor{gray!6}{151} & \cellcolor{gray!6}{estimating the value of containment strategies in delaying the arrival time of an influenza pandemic: a case study of travel restriction and patient isolation} & \cellcolor{gray!6}{2012} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
152 & how to minimize the attack rate during multiple influenza outbreaks in a heterogeneous population & 2012 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{153} & \cellcolor{gray!6}{modeling strategies for controlling h1n1 outbreaks in china} & \cellcolor{gray!6}{2012} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{CN}\\
154 & modeling the effects of h1n1 influenza vaccine distribution in the united states & 2012 & academic institutions & TRUE & US\\
\cellcolor{gray!6}{155} & \cellcolor{gray!6}{modeling the impact of air, sea, and land travel restrictions supplemented by other interventions on the emergence of a new influenza pandemic virus} & \cellcolor{gray!6}{2012} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{HK}\\
\addlinespace
156 & simulating school closure policies for cost effective pandemic decision making & 2012 & academic institutions + government institutions & FALSE & none\\
\cellcolor{gray!6}{157} & \cellcolor{gray!6}{the impact of school closures on pandemic influenza: assessing potential repercussions using a seasonal sir model} & \cellcolor{gray!6}{2012} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
158 & vaccination against foot-and-mouth disease i: epidemiological consequences & 2012 & academic institutions & TRUE & NL\\
\cellcolor{gray!6}{159} & \cellcolor{gray!6}{a deterministic resource scheduling model in epidemic control: a case study} & \cellcolor{gray!6}{2011} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{GR}\\
160 & a model for the a(h1n1) epidemic in mexico, including social isolation & 2011 & academic institutions & TRUE & MX\\
\addlinespace
\cellcolor{gray!6}{161} & \cellcolor{gray!6}{a model to evaluate mass vaccination against pneumococcus as a countermeasure against pandemic influenza} & \cellcolor{gray!6}{2011} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{GB}\\
162 & a multilayer framework to assess influenza intervention policies & 2011 & academic institutions & TRUE & TW\\
\cellcolor{gray!6}{163} & \cellcolor{gray!6}{a note on the use of optimal control on a discrete time model of influenza dynamics} & \cellcolor{gray!6}{2011} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
164 & a simulation-based assessment of school closure strategies during an influenza epidemic & 2011 & academic institutions & TRUE & CN\\
\cellcolor{gray!6}{165} & \cellcolor{gray!6}{agent-based modeling of the spread of influenza-like illness in an emergency department: a simulation study} & \cellcolor{gray!6}{2011} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{CA}\\
\addlinespace
166 & antiviral treatment for pandemic influenza: assessing potential repercussions using a seasonally forced sir model & 2011 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{167} & \cellcolor{gray!6}{can antiviral drugs contain pandemic influenza transmission?} & \cellcolor{gray!6}{2011} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{none}\\
168 & characterizing the epidemiology of the 2009 influenza a/h1n1 pandemic in mexico & 2011 & academic institutions + government institutions & FALSE & MX\\
\cellcolor{gray!6}{169} & \cellcolor{gray!6}{cholera epidemic in haiti, 2010: using a transmission model to explain spatial spread of disease and identify optimal control interventions} & \cellcolor{gray!6}{2011} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{HT}\\
170 & controlling an influenza outbreak in deterministic and stochastic models with the emergence and evolution of drug resistance (model 1) & 2011 & academic institutions & TRUE & none\\
\addlinespace
\cellcolor{gray!6}{171} & \cellcolor{gray!6}{modeling control strategies for concurrent epidemics of seasonal and pandemic h1n1 influenza} & \cellcolor{gray!6}{2011} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{US}\\
172 & modeling the impact of behavior changes on the spread of pandemic influenza & 2011 & academic institutions + government institutions & FALSE & none\\
\cellcolor{gray!6}{173} & \cellcolor{gray!6}{modelling and analysis of influenza a (h1n1) on networks} & \cellcolor{gray!6}{2011} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{CN}\\
174 & modelling the strategies for age specific vaccination scheduling during influenza pandemic outbreaks & 2011 & academic institutions & TRUE & HU\\
\cellcolor{gray!6}{175} & \cellcolor{gray!6}{modelling the transmission dynamics and control of the novel 2009 swine influenza (h1n1) pandemic} & \cellcolor{gray!6}{2011} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{CA}\\
\addlinespace
176 & planning for the control of pandemic influenza a (h1n1) in los angeles county and the united states & 2011 & academic institutions + government institutions + NGO & FALSE & US\\
\cellcolor{gray!6}{177} & \cellcolor{gray!6}{prioritization of delayed vaccination for pandemic influenza} & \cellcolor{gray!6}{2011} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{US}\\
178 & temporal factors in school closure policy for mitigating the spread of influenza & 2011 & academic institutions + government institutions & FALSE & SG\\
\cellcolor{gray!6}{179} & \cellcolor{gray!6}{the global transmission and control of influenza} & \cellcolor{gray!6}{2011} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{global}\\
180 & toward effective vaccine deployment: a systematic study & 2011 & academic institutions & TRUE & HK\\
\addlinespace
\cellcolor{gray!6}{181} & \cellcolor{gray!6}{vaccination against 2009 pandemic h1n1 in a population dynamical model of vancouver, canada: timing is everything} & \cellcolor{gray!6}{2011} & \cellcolor{gray!6}{academic institutions + government institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{CA}\\
182 & a simulation model for the potential spread of foot-and-mouth disease in the castile and leon region of spain & 2010 & academic institutions & TRUE & ES\\
\cellcolor{gray!6}{183} & \cellcolor{gray!6}{community-based measures for mitigating the 2009 h1n1 pandemic in china} & \cellcolor{gray!6}{2010} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{CN}\\
184 & effective real-time allocation of pandemic interventions & 2010 & NGO & FALSE & US\\
\cellcolor{gray!6}{185} & \cellcolor{gray!6}{efficient mitigation strategies for epidemics in rural regions} & \cellcolor{gray!6}{2010} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{US}\\
\addlinespace
186 & influenza pandemic waves under various mitigation strategies with 2009 h1n1 as a case study & 2010 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{187} & \cellcolor{gray!6}{is a mass immunization program for pandemic (h1n1) 2009 good value for money? early evidence from the canadian experience} & \cellcolor{gray!6}{2010} & \cellcolor{gray!6}{academic institutions + government institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{CA}\\
188 & optimal control for pandemic influenza: the role of limited antiviral treatment and isolation & 2010 & academic institutions + NGO & FALSE & none\\
\cellcolor{gray!6}{189} & \cellcolor{gray!6}{optimizing vaccine allocation at different points in time during an epidemic} & \cellcolor{gray!6}{2010} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{none}\\
190 & simulating school closure strategies to mitigate an influenza epidemic & 2010 & academic institutions + government institutions + NGO & FALSE & US\\
\addlinespace
\cellcolor{gray!6}{191} & \cellcolor{gray!6}{the effect of mask use on the spread of influenza during a pandemic} & \cellcolor{gray!6}{2010} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{none}\\
192 & transmission dynamics of an influenza model with age of infection and antiviral treatment & 2010 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{193} & \cellcolor{gray!6}{transmission risks and control of foot-and-mouth disease in the netherlands: spatial patterns} & \cellcolor{gray!6}{2010} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{NL}\\
194 & when should we intervene to control the 2009 influenza a(h1n1) pandemic? & 2010 & academic institutions + government institutions & FALSE & JP\\
\cellcolor{gray!6}{195} & \cellcolor{gray!6}{adaptive vaccination strategies to mitigate pandemic influenza} & \cellcolor{gray!6}{2009} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{MX}\\
\addlinespace
196 & antiviral resistance and the control of pandemic influenza: the roles of stochasticity, evolution and model details & 2009 & academic institutions & TRUE & US\\
\cellcolor{gray!6}{197} & \cellcolor{gray!6}{economic evaluation of influenza pandemic mitigation strategies in the united states using a stochastic microsimulation transmission model} & \cellcolor{gray!6}{2009} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{US}\\
198 & effectiveness and cost-effectiveness of expanded antiviral prophylaxis and adjuvanted vaccination strategies for an influenza a (h5n1) pandemic & 2009 & academic institutions & TRUE & US\\
\cellcolor{gray!6}{199} & \cellcolor{gray!6}{engineering responses to pandemics} & \cellcolor{gray!6}{2009} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{HK}\\
200 & epidemiological benefits of more-effective tuberculosis vaccines, drugs, and diagnostics & 2009 & academic institutions + government institutions + NGO & FALSE & who southeast asia region\\
\addlinespace
\cellcolor{gray!6}{201} & \cellcolor{gray!6}{household epidemics: modelling effects of early stage vaccination} & \cellcolor{gray!6}{2009} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{SE TZ}\\
202 & measures against transmission of pandemic h1n1 influenza in japan in 2009: simulation model & 2009 & academic institutions + government institutions & FALSE & JP\\
\cellcolor{gray!6}{203} & \cellcolor{gray!6}{modeling vaccination campaigns and the fall/winter 2009 activity of the new a(h1n1) influenza in the northern hemisphere} & \cellcolor{gray!6}{2009} & \cellcolor{gray!6}{academic institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{northern hemisphere}\\
204 & modelling foot and mouth disease & 2009 & academic institutions & TRUE & GB\\
\cellcolor{gray!6}{205} & \cellcolor{gray!6}{modelling of the influenza a(h1n1)v outbreak in mexico city, april-may 2009, with control sanitary measures} & \cellcolor{gray!6}{2009} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{MX}\\
\addlinespace
206 & post-exposure prophylaxis during pandemic outbreaks & 2009 & academic institutions + government institutions & FALSE & none\\
\cellcolor{gray!6}{207} & \cellcolor{gray!6}{potential for a global dynamic of influenza a (h1n1)} & \cellcolor{gray!6}{2009} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{global}\\
208 & reducing the impact of the next influenza pandemic using householdbased public health interventions & 2009 & academic institutions & TRUE & HK\\
\cellcolor{gray!6}{209} & \cellcolor{gray!6}{seasonal transmission potential and activity peaks of the new influenza a(h1n1): a monte carlo likelihood analysis based on human mobility} & \cellcolor{gray!6}{2009} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{global}\\
210 & simulation of foot-and-mouth disease spread within an integrated livestock system in texas, usa & 2009 & academic institutions & TRUE & US\\
\addlinespace
\cellcolor{gray!6}{211} & \cellcolor{gray!6}{the transmissibility and control of pandemic influenza a (h1n1) virus} & \cellcolor{gray!6}{2009} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{US}\\
212 & bayesian analysis of severe acute respiratory syndrome: the 2003 hong kong epidemic & 2008 & academic institutions & TRUE & HK\\
\cellcolor{gray!6}{213} & \cellcolor{gray!6}{hepatitis b vaccination and changes in sexual risk behaviour among men who have sex with men in amsterdam} & \cellcolor{gray!6}{2008} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{NL}\\
214 & mathematical assessment of canada's pandemic influenza preparedness plan & 2008 & academic institutions + government institutions & FALSE & CA\\
\cellcolor{gray!6}{215} & \cellcolor{gray!6}{modeling targeted layered containment of an influenza pandemic in the united states} & \cellcolor{gray!6}{2008} & \cellcolor{gray!6}{academic institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{US}\\
\addlinespace
216 & optimal allocation of pandemic influenza vaccine depends on age, risk and timing & 2008 & academic institutions + government institutions & FALSE & NL\\
\cellcolor{gray!6}{217} & \cellcolor{gray!6}{pandemic simulation of antivirals plus school closures: buying time until strain-specific vaccine is available} & \cellcolor{gray!6}{2008} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{US}\\
218 & preparedness for the spread of influenza: prohibition of traffic, school closure, and vaccination of children in the commuter towns of tokyo & 2008 & academic institutions + government institutions + NGO & FALSE & JP\\
\cellcolor{gray!6}{219} & \cellcolor{gray!6}{scenarios of diffusion and control of an influenza pandemic in italy} & \cellcolor{gray!6}{2008} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{IT}\\
220 & time is of the essence: exploring a measles outbreak response vaccination in niamey, niger & 2008 & academic institutions + government institutions + NGO & FALSE & NE\\
\addlinespace
\cellcolor{gray!6}{221} & \cellcolor{gray!6}{a stochastic equation-based model of the value of international air-travel restrictions for controlling pandemic flu} & \cellcolor{gray!6}{2007} & \cellcolor{gray!6}{NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{global}\\
222 & assessing the role of basic control measures, antivirals and vaccine in curtailing pandemic influenza: scenarios for the us, uk and the netherlands & 2007 & academic institutions & TRUE & NL GB US\\
\cellcolor{gray!6}{223} & \cellcolor{gray!6}{deterministic sir (susceptible–infected–removed) models applied to varicella outbreaks} & \cellcolor{gray!6}{2007} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{CO}\\
224 & effectiveness of movement-prevention regulations to reduce the spread of foot-and-mouth disease in the netherlands & 2007 & academic institutions & TRUE & NL\\
\cellcolor{gray!6}{225} & \cellcolor{gray!6}{effects of internal border control on spread of pandemic influenza} & \cellcolor{gray!6}{2007} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{AU}\\
\addlinespace
226 & simple models of influenza progression within a heterogeneous population & 2007 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{227} & \cellcolor{gray!6}{stochastic model of an influenza epidemic with drug resistance} & \cellcolor{gray!6}{2007} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{none}\\
228 & the effect of public health measures on the 1918 influenza pandemic in u.s. cities & 2007 & academic institutions & TRUE & US\\
\cellcolor{gray!6}{229} & \cellcolor{gray!6}{vaccinating in disease-free regions: a vaccine model with application to yellow fever} & \cellcolor{gray!6}{2007} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{BR}\\
230 & a 'small-world-like' model for comparing interventions aimed at preventing and controlling influenza pandemics & 2006 & academic institutions + NGO & FALSE & none\\
\addlinespace
\cellcolor{gray!6}{231} & \cellcolor{gray!6}{containing pandemic influenza with antiviral agents: analytical commentary} & \cellcolor{gray!6}{2006} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{US}\\
232 & critical response to post-outbreak vaccination against foot-and-mouth disease & 2006 & academic institutions + government institutions & FALSE & UY\\
\cellcolor{gray!6}{233} & \cellcolor{gray!6}{mitigation strategies for pandemic influenza in the united states} & \cellcolor{gray!6}{2006} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{US}\\
234 & simple models for containment of a pandemic & 2006 & academic institutions & TRUE & none\\
\cellcolor{gray!6}{235} & \cellcolor{gray!6}{statistical inference in a stochastic epidemic seir model with control intervention: ebola as a case study} & \cellcolor{gray!6}{2006} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{CD}\\
\addlinespace
236 & strategies for containing an emerging influenza pandemic in southeast asia & 2005 & academic institutions + government institutions & FALSE & southeast asia\\
\cellcolor{gray!6}{237} & \cellcolor{gray!6}{modeling alternative mitigation strategies for a hypothetical outbreak of foot-and-mouth disease in the united states} & \cellcolor{gray!6}{2003} & \cellcolor{gray!6}{government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{US}\\
238 & modelling vaccination strategies against foot-and-mouth disease & 2003 & academic institutions & TRUE & GB\\
\cellcolor{gray!6}{239} & \cellcolor{gray!6}{a decision-tree to optimise control measures during the early stage of a foot-and-mouth disease epidemic} & \cellcolor{gray!6}{2002} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{NL}\\
240 & effect of control measures on the course of simulated foot and mouth disease epidemics that started on different farm types in various dutch areas & 2002 & academic institutions & TRUE & NL\\
\addlinespace
\cellcolor{gray!6}{241} & \cellcolor{gray!6}{dynamics of the 2001 uk foot and mouth epidemic: stochastic dispersal in a heterogeneous landscape} & \cellcolor{gray!6}{2001} & \cellcolor{gray!6}{academic institutions + government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{GB}\\
242 & an extended state-transition model for foot-and-mouth disease epidemics in france & 2000 & government institutions & FALSE & FR\\
\cellcolor{gray!6}{243} & \cellcolor{gray!6}{simulated economic consequences of foot-and-mouth disease epidemics and their public control in france} & \cellcolor{gray!6}{2000} & \cellcolor{gray!6}{government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{FR}\\
244 & effect of chemotherapy on malaria transmission among yanomami amerindians: simulated consequences of placebo treatment & 1999 & academic institutions + government institutions & FALSE & VE\\
\cellcolor{gray!6}{245} & \cellcolor{gray!6}{modelling vaccination strategy against directly transmitted diseases using a series of pulses} & \cellcolor{gray!6}{1998} & \cellcolor{gray!6}{academic institutions} & \cellcolor{gray!6}{TRUE} & \cellcolor{gray!6}{BR}\\
\addlinespace
246 & mass vaccination to control chickenpox: the influence of zoster & 1996 & academic institutions & TRUE & DK FO\\
\cellcolor{gray!6}{247} & \cellcolor{gray!6}{an evaluation of alternate control strategies for foot-and-mouth disease in australia: a regional approach} & \cellcolor{gray!6}{1995} & \cellcolor{gray!6}{government institutions + NGO} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{AU}\\
248 & analysis of a measles epidemic & 1993 & academic institutions + government institutions & FALSE & US\\
\cellcolor{gray!6}{249} & \cellcolor{gray!6}{a model of the transmission of dengue fever with an evaluation of the impact of ultra-low volume (ulv) insecticide applications on dengue epidemics} & \cellcolor{gray!6}{1992} & \cellcolor{gray!6}{government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{none}\\
250 & a discrete-time model with vaccination for a measles epidemic & 1991 & academic institutions & TRUE & US\\
\addlinespace
\cellcolor{gray!6}{251} & \cellcolor{gray!6}{a stochastic model of epidemics in military recruits} & \cellcolor{gray!6}{1982} & \cellcolor{gray!6}{government institutions} & \cellcolor{gray!6}{FALSE} & \cellcolor{gray!6}{US}\\
252 & stochastic two-agent epidemic simulation models for a community of families & 1971 & academic institutions & TRUE & none\\*
\end{longtable}
\endgroup{}
\end{landscape}

\hypertarget{table-2}{%
\subsection{Table 2}\label{table-2}}

This section presents extracted data on the disease studied (disease),
type of objective studied (objectives), whether the paper had an author
in the location studied (author\_in\_country\_studied), and how
individuals were represented (individual\_representation).

\begin{landscape}\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}{l>{\raggedright\arraybackslash}p{3.3cm}l>{\raggedright\arraybackslash}p{3.3cm}>{\raggedright\arraybackslash}p{2cm}l}
\toprule
num & title & author\_in\_country\_studied & disease & objectives & individual\_representation\\
\midrule
\endfirsthead
\multicolumn{6}{@{}l}{\textit{(continued)}}\\
\toprule
num & title & author\_in\_country\_studied & disease & objectives & individual\_representation\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{a cholera metapopulation model interlinking migration with intervention strategies - a case study of zimbabwe (2008-2009)} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{cholera} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
2 & a theoretical single-parameter model for urbanisation to study infectious disease spread and interventions & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{3} & \cellcolor{gray!6}{assessing the effects of modeling the spectrum of clinical symptoms on the dynamics and control of ebola} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
4 & dynamical analysis and control strategies in modelling ebola virus disease & not applicable & ebola & prospective analysis & compartments\\
\cellcolor{gray!6}{5} & \cellcolor{gray!6}{effect of a hepatitis a vaccination campaign during a hepatitis a outbreak in taiwan, 2015–2017: a modeling study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{hepatitis a} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{agents}\\
\addlinespace
6 & evaluating strategies for control of tuberculosis in prisons and prevention of spillover into communities: an observational and modeling study from brazil & yes & tuberculosis & prospective analysis & compartments\\
\cellcolor{gray!6}{7} & \cellcolor{gray!6}{evaluating the effects of control interventions and estimating the inapparent infections for dengue outbreak in hangzhou, china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{dengue} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
8 & incidence dynamics and investigation of key interventions in a dengue outbreak in ningbo city, china & yes & dengue & retrospective analysis & compartments\\
\cellcolor{gray!6}{9} & \cellcolor{gray!6}{incorporating media data into a model of infectious disease transmission} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{agents}\\
10 & influence of asymptomatic infections for the effectiveness of facemasks during pandemic influenza & not applicable & influenza & prospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{11} & \cellcolor{gray!6}{mathematical analysis of a cholera infection model with vaccination strategy} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{cholera} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
12 & modeling and stability analysis of epidemic expansion disease ebola virus with implications prevention in population & no & ebola & prospective analysis & compartments\\
\cellcolor{gray!6}{13} & \cellcolor{gray!6}{modeling the effectiveness of respiratory protective devices in reducing influenza outbreak} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
14 & modeling the effects of vaccination and treatment on tuberculosis transmission dynamics & no & tuberculosis & prospective analysis & compartments\\
\cellcolor{gray!6}{15} & \cellcolor{gray!6}{optimal control and cost-effective analysis of the 2017 meningitis outbreak in nigeria} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{meningococcal meningitis} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
16 & optimal control strategies for a two-group epidemic model with vaccination-resource constraints & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{17} & \cellcolor{gray!6}{optimal media reporting intensity on mitigating spread of an emerging infectious disease} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
18 & school dismissal as a pandemic influenza response: when, where and for how long? & yes & influenza & prospective analysis & agents\\
\cellcolor{gray!6}{19} & \cellcolor{gray!6}{study on modeling simulation and optimal control method for the transmission risk of the ebola virus} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
20 & transmission dynamics of cholera with hyperinfectious and hypoinfectious vibrios: mathematical modelling and control strategies & no & cholera & prospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{21} & \cellcolor{gray!6}{a new epidemics–logistics model: insights into controlling the ebola virus disease in west africa} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
22 & contact reductions from live poultry market closures limit the epidemic of human infections with h7n9 influenza & yes & influenza & retrospective analysis & compartments\\
\cellcolor{gray!6}{23} & \cellcolor{gray!6}{disparities in spread and control of influenza in slums of delhi: findings from an agent-based modelling study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
24 & efficacy of control measures in the control of ebola, liberia 2014–2015 & no & ebola & retrospective analysis & compartments\\
\cellcolor{gray!6}{25} & \cellcolor{gray!6}{epidemiology of the silent polio outbreak in rahat, israel, based on modeling of environmental surveillance data} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{poliomyelitis} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
26 & evaluating costs and health consequences of sick leave strategies against pandemic and seasonal influenza in norway using a dynamic model & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{27} & \cellcolor{gray!6}{evaluating vaccination strategies to control foot-and-mouth disease: a country comparison study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
28 & impact of public health responses during a measles outbreak in an amish community in ohio: modeling the dynamics of transmission & yes & measles & retrospective analysis & compartments\\
\cellcolor{gray!6}{29} & \cellcolor{gray!6}{initial validation of a simulation model for estimating the impact of serogroup a neisseria meningitidis vaccination in the african meningitis belt} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{meningococcal meningitis} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
30 & logistical constraints lead to an intermediate optimum in outbreak response vaccination & not applicable & cholera ebola influenza measles & prospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{31} & \cellcolor{gray!6}{manipulation of contact network structure and the impact on foot-and-mouth disease transmission} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
32 & mathematical model and intervention strategies for mitigating tuberculosis in the philippines & yes & tuberculosis & prospective analysis & compartments\\
\cellcolor{gray!6}{33} & \cellcolor{gray!6}{measles outbreak response decision-making under uncertainty: a retrospective analysis} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{measles} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
34 & modeling the heterogeneity of dengue transmission in a city & yes & dengue & prospective analysis & compartments\\
\cellcolor{gray!6}{35} & \cellcolor{gray!6}{modelling the large-scale yellow fever outbreak in luanda, angola, and the impact of vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yellow fever} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
36 & quantifying the impact of early-stage contact tracing on controlling ebola diffusion & no & ebola & prospective analysis & agents\\
\cellcolor{gray!6}{37} & \cellcolor{gray!6}{simulation of key interventions for seasonal influenza outbreak control at school in changsha, china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
38 & the impact of regular school closure on seasonal influenza epidemics: a data-driven spatial transmission model for belgium & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{39} & \cellcolor{gray!6}{the potential impact of case-area targeted interventions in response to cholera outbreaks: a modeling study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{cholera} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
40 & value of inventory information in allocating a limited supply of influenza vaccine during a pandemic & yes & influenza & prospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{41} & \cellcolor{gray!6}{an age-structured model for cholera control with vaccination} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{cholera} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
42 & an approach to and web-based tool for infectious disease outbreak intervention analysis & not applicable & influenza measles & prospective analysis & compartments\\
\cellcolor{gray!6}{43} & \cellcolor{gray!6}{an economic assessment of foot and mouth disease in japan} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
44 & analysis of an seriv epidemic model of human influenza & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{45} & \cellcolor{gray!6}{control strategies of avian influenza pandemic model with time delay} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
46 & costs and benefits of including inactivated in addition to oral poliovirus vaccine in outbreak response after cessation of oral poliovirus vaccine use & no & poliomyelitis & prospective analysis & compartments\\
\cellcolor{gray!6}{47} & \cellcolor{gray!6}{deriving effective vaccine allocation strategies for pandemic influenza: comparison of an agent-based simulation and a compartmental model} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{individuals representation other}\\
48 & early rigorous control interventions can largely reduce dengue outbreak magnitude: experience from chaozhou, china & yes & dengue & retrospective analysis & compartments\\
\cellcolor{gray!6}{49} & \cellcolor{gray!6}{effects of reactive social distancing on the 1918 influenza pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
50 & epidemiological and economic impact of pandemic influenza in chicago: priorities for vaccine interventions & yes & influenza & prospective analysis & agents\\
\addlinespace
\cellcolor{gray!6}{51} & \cellcolor{gray!6}{estimating direct and indirect protective effect of influenza vaccination in the united states} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
52 & evaluating the effects of common control measures for influenza a (h1n1) outbreak at school in china: a modeling study & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{53} & \cellcolor{gray!6}{evaluation of strategies to control a potential outbreak of foot-and-mouth disease in sweden} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
54 & impact of a waning vaccine and altered behavior on the spread of influenza & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{55} & \cellcolor{gray!6}{mathematical models for devising the optimal ebola virus disease eradication} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
56 & modeling the role of public health education in ebola virus disease outbreaks in sudan & no & ebola & prospective analysis & compartments\\
\cellcolor{gray!6}{57} & \cellcolor{gray!6}{modelling the transmission and control strategies of varicella among school children in shenzhen, china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{varicella} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
58 & optimal and adaptive control of an epidemic model of influenza with unknown parameters & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{59} & \cellcolor{gray!6}{simulating endogenous dynamics of intervention-capacity deployment: ebola outbreak in liberia} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
60 & simulating the potential role of media coverage and infected bats in the 2014 ebola outbreak & no & ebola & retrospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{61} & \cellcolor{gray!6}{a mathematical model of ebola virus disease: using sensitivity analysis to determine effective intervention targets} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
62 & a multi-agent model for adaptive vaccination during infectious disease outbreaks & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{63} & \cellcolor{gray!6}{assessing the efficiency of movement restriction as a control strategy of ebola} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
64 & characterization of outbreak response strategies and potential vaccine stockpile needs for the polio endgame & not applicable & poliomyelitis & prospective analysis & compartments\\
\cellcolor{gray!6}{65} & \cellcolor{gray!6}{designing public health policies to mitigate the adverse consequences of rural-urban migration via meta-population modeling} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{measles} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
66 & dynamic model of influenza with age-structured and media coverage & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{67} & \cellcolor{gray!6}{economic evaluation of individual school closure strategies: the hong kong 2009 h1n1 pandemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
68 & efficient vaccine distribution based on a hybrid compartmental model & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{69} & \cellcolor{gray!6}{epidemiological evaluation of different fmd control strategies in two selected regions in austria} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{agents}\\
70 & evaluating targeted interventions via meta-population models with multi-level mixing & yes & influenza & retrospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{71} & \cellcolor{gray!6}{evaluation of outbreak response immunization in the control of pertussis using agent-based modeling} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{pertussis} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
72 & global stability and optimal control for a tuberculosis model with vaccination and treatment & not applicable & tuberculosis & prospective analysis & compartments\\
\cellcolor{gray!6}{73} & \cellcolor{gray!6}{impact on epidemic measles of vaccination campaigns triggered by disease outbreaks or serosurveys: a modeling study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{measles} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
74 & metapopulation and non-proportional vaccination models overview & no & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{75} & \cellcolor{gray!6}{model-based comprehensive analysis of school closure policies for mitigating influenza epidemics and pandemics} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
\addlinespace
76 & modeling ring-vaccination strategies to control ebola virus disease epidemics & no & ebola & prospective analysis & compartments\\
\cellcolor{gray!6}{77} & \cellcolor{gray!6}{modeling the effect of public health resources and alerting on the dynamics of pertussis spread*} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{pertussis} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
78 & modeling the impact of behavior change on the spread of ebola & no & ebola & prospective analysis & compartments\\
\cellcolor{gray!6}{79} & \cellcolor{gray!6}{modeling the spread of polio in an ipv-vaccinated population: lessons learned from the 2013 silent outbreak in southern israel} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{poliomyelitis} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
80 & modelling weekly vector control against dengue in the guangdong province of china & yes & dengue & retrospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{81} & \cellcolor{gray!6}{optimal control strategies for the spread of ebola in west africa} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
82 & potential impact of a ventilation intervention for influenza in the context of a dense indoor contact network in hong kong & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{83} & \cellcolor{gray!6}{predicting and evaluating the epidemic trend of ebola virus disease in the 2014-2015 outbreak and the effects of intervention measures} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
84 & projected impact of dengue vaccination in yucatán, mexico & yes & dengue & retrospective analysis & agents\\
\cellcolor{gray!6}{85} & \cellcolor{gray!6}{seasonality and the effectiveness of mass vaccination} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{dengue influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
86 & simulation optimization for an age-based vaccines distribution strategy against the spread of influenza epidemic & yes & influenza & prospective analysis & agents\\
\cellcolor{gray!6}{87} & \cellcolor{gray!6}{spatiotemporal dynamics of the ebola epidemic in guinea and implications for vaccination and disease elimination: a computational modeling analysis} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{agents}\\
88 & the interplay of vaccination and vector control on small dengue networks & not applicable & dengue & prospective analysis & compartments\\
\cellcolor{gray!6}{89} & \cellcolor{gray!6}{an epidemic patchy model with entry–exit screening} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
90 & assessing the role of voluntary self-isolation in the control of pandemic influenza using a household epidemic model & not applicable & influenza & prospective analysis & individuals representation other\\
\addlinespace
\cellcolor{gray!6}{91} & \cellcolor{gray!6}{be-codis: a mathematical model to predict the risk of human diseases spread between countries—validation and application to the 2014–2015 ebola virus disease epidemic} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
92 & dengue in madeira island & yes & dengue & prospective analysis & compartments\\
\cellcolor{gray!6}{93} & \cellcolor{gray!6}{dynamic simulation of a seiqr-v epidemic model based on cellular automata} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
94 & early vaccine availability represents an important public health advance for the control of pandemic influenza & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{95} & \cellcolor{gray!6}{effectiveness of ebola treatment units and community care centers — liberia, september 23–october 31, 2014} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
96 & evaluation of the benefts and risks of introducing ebola community care centers, sierra leone & no & ebola & prospective analysis & compartments\\
\cellcolor{gray!6}{97} & \cellcolor{gray!6}{evidence for emergency vaccination having played a crucial role to control the 1965/66 foot-and-mouth disease outbreak in switzerland} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{agents}\\
98 & measuring the impact of ebola control measures in sierra leone & no & ebola & retrospective analysis & compartments\\
\cellcolor{gray!6}{99} & \cellcolor{gray!6}{media impact switching surface during an infectious disease outbreak} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
100 & modeling options to manage type 1 wild poliovirus imported into israel in 2013 & yes & poliomyelitis & retrospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{101} & \cellcolor{gray!6}{modeling the effect of comprehensive interventions on ebola virus transmission} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
102 & modeling the effect of school closures in a pandemic scenario: exploring two different contact matrices & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{103} & \cellcolor{gray!6}{modelling the effect of early detection of ebola} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
104 & multi-scale modeling for the transmission of influenza and the evaluation of interventions toward it & yes & influenza & prospective analysis & agents\\
\cellcolor{gray!6}{105} & \cellcolor{gray!6}{optimal intervention strategies for a seir control model of ebola epidemics} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
106 & predicting the extinction of ebola spreading in liberia due to mitigation strategies & no & ebola & retrospective analysis & compartments\\
\cellcolor{gray!6}{107} & \cellcolor{gray!6}{school closure strategies for the 2009 hong kong hini influenza pandemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
108 & spatiotemporal spread of the 2014 outbreak of ebola virus disease in liberia and the effectiveness of non-pharmaceutical interventions: a computational modelling analysis & no & ebola & retrospective analysis & agents\\
\cellcolor{gray!6}{109} & \cellcolor{gray!6}{strategies for early vaccination during novel influenza outbreaks} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
110 & the effects of media reports on disease spread and important public health measurements & yes & influenza & prospective analysis & agents\\
\addlinespace
\cellcolor{gray!6}{111} & \cellcolor{gray!6}{the impact of human behavioral changes in 2014 west africa ebola outbreak} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
112 & transmission dynamics and final epidemic size of ebola virus disease outbreaks with varying interventions & no & ebola & prospective analysis & compartments\\
\cellcolor{gray!6}{113} & \cellcolor{gray!6}{treatment–donation-stockpile dynamics in ebola convalescent blood transfusion therapy} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
114 & vaccine prioritization for effective pandemic response & yes & influenza & prospective analysis & individuals representation other\\
\cellcolor{gray!6}{115} & \cellcolor{gray!6}{a mathematical study of a tb model with treatment interruptions and two latent periods} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{tuberculosis} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
116 & antiviral prophylaxis and isolation for the control of pandemic influenza & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{117} & \cellcolor{gray!6}{assessing the impact of travel restrictions on international spread of the 2014 west african ebola epidemic} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
118 & assessing the use of antiviral treatment to control influenza & no & influenza & prospective analysis & agents\\
\cellcolor{gray!6}{119} & \cellcolor{gray!6}{behavior in the time of cholera: evidence from the 2008-2009 cholera outbreak in zimbabwe} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{cholera} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
120 & behavioural response in educated young adults towards influenza a(h1n1)pdm09 & not applicable & influenza & prospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{121} & \cellcolor{gray!6}{cover your cough! quantifying the benefits of a localized healthy behavior intervention on flu epidemics in washington dc} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
122 & dynamics and control of ebola virus transmission in montserrado, liberia: a mathematical modelling analysis & yes & ebola & prospective analysis & compartments\\
\cellcolor{gray!6}{123} & \cellcolor{gray!6}{estimating the effectiveness of early control measures through school absenteeism surveillance in observed outbreaks at rural schools in hubei, china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza mumps varicella} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
124 & evaluation of the benefit of emergency vaccination in a foot-and-mouth disease free country with low livestock density & yes & fmd & prospective analysis & agents\\
\cellcolor{gray!6}{125} & \cellcolor{gray!6}{modeling the dynamics of oral poliovirus vaccine cessation} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{poliomyelitis} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
126 & modeling the impact of optimal screening on typhoid dynamics & not applicable & typhoid & prospective analysis & compartments\\
\cellcolor{gray!6}{127} & \cellcolor{gray!6}{modeling the influence of environment and intervention oncholera in haiti} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{cholera} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
128 & sequential bayesian inference in hidden markov stochastic kinetic models with application to detection and response to seasonal epidemics & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{129} & \cellcolor{gray!6}{simulating optimal vaccination times during cholera outbreaks} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{cholera} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
130 & the role of vaccination coverage, individual behaviors, and the public health response in the control of measles epidemics: an agent-based simulation for california & yes & measles & prospective analysis & agents\\
\addlinespace
\cellcolor{gray!6}{131} & \cellcolor{gray!6}{time is (still) of the essence: quantifying the impact of emergency meningitis vaccination response in katsina state, nigeria} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{meningococcal meningitis} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
132 & a perspective on multiple waves of influenza pandemics & yes & influenza & retrospective analysis & agents\\
\cellcolor{gray!6}{133} & \cellcolor{gray!6}{an optimal control problem arising from a dengue disease transmission model} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{dengue} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
134 & cholera in haiti: reproductive numbers and vaccination coverage estimates & no & cholera & prospective analysis & agents\\
\cellcolor{gray!6}{135} & \cellcolor{gray!6}{comparing control strategies against foot-and-mouth disease: will vaccination be cost-effective in denmark?} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
\addlinespace
136 & cost-effectiveness of influenza control measures: a dynamic transmission model-based analysis & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{137} & \cellcolor{gray!6}{cost-effectiveness of workplace closure and travel restriction for mitigating influenza outbreaks: a network-based simulation} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
138 & decisions on control of foot-and-mouth disease informed using model predictions & yes & fmd & prospective analysis & agents\\
\cellcolor{gray!6}{139} & \cellcolor{gray!6}{dengue in cape verde: vector control and vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{dengue} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
140 & enhancement of collective immunity in tokyo metropolitan area by selective vaccination against an emerging influenza pandemic & yes & influenza & prospective analysis & agents\\
\addlinespace
\cellcolor{gray!6}{141} & \cellcolor{gray!6}{estimated impact of aggressive empirical antiviral treatment in containing an outbreak of pandemic influenza h1n1 in an isolated first nations community} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
142 & multiregional dynamic vaccine allocation during an influenza epidemic & yes & influenza & prospective analysis & agents\\
\cellcolor{gray!6}{143} & \cellcolor{gray!6}{policies to reduce influenza in the workplace: impact assessments using an agent-based model} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
144 & transmission dynamics of the 2009 influenza a (h1n1) pandemic in india: the impact of holiday-related school closure & yes & influenza & retrospective analysis & compartments\\
\cellcolor{gray!6}{145} & \cellcolor{gray!6}{vaccination against foot-and-mouth disease: do initial conditions affect its benefit?} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{agents}\\
\addlinespace
146 & was mandatory quarantine necessary in china for controlling the 2009 h1n1 pandemic? & yes & influenza & retrospective analysis & compartments\\
\cellcolor{gray!6}{147} & \cellcolor{gray!6}{a contact-network-based simulation model for evaluating interventions under 'what-if' scenarios in epidemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
148 & campus quarantine (fengxiao) for curbing emergent infectious diseases: lessons from mitigating a/h1n1 in xi'an, china & yes & influenza & retrospective analysis & compartments\\
\cellcolor{gray!6}{149} & \cellcolor{gray!6}{dynamic modelling of costs and health consequences of school closure during an influenza pandemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
150 & effect of vaccines and antivirals during the major 2009 a(h1n1) pandemic wave in norway - and the influence of vaccination timing & yes & influenza & retrospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{151} & \cellcolor{gray!6}{estimating the value of containment strategies in delaying the arrival time of an influenza pandemic: a case study of travel restriction and patient isolation} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
152 & how to minimize the attack rate during multiple influenza outbreaks in a heterogeneous population & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{153} & \cellcolor{gray!6}{modeling strategies for controlling h1n1 outbreaks in china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
154 & modeling the effects of h1n1 influenza vaccine distribution in the united states & yes & influenza & retrospective analysis & compartments\\
\cellcolor{gray!6}{155} & \cellcolor{gray!6}{modeling the impact of air, sea, and land travel restrictions supplemented by other interventions on the emergence of a new influenza pandemic virus} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
156 & simulating school closure policies for cost effective pandemic decision making & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{157} & \cellcolor{gray!6}{the impact of school closures on pandemic influenza: assessing potential repercussions using a seasonal sir model} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
158 & vaccination against foot-and-mouth disease i: epidemiological consequences & yes & fmd & prospective analysis & agents\\
\cellcolor{gray!6}{159} & \cellcolor{gray!6}{a deterministic resource scheduling model in epidemic control: a case study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
160 & a model for the a(h1n1) epidemic in mexico, including social isolation & yes & influenza & retrospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{161} & \cellcolor{gray!6}{a model to evaluate mass vaccination against pneumococcus as a countermeasure against pandemic influenza} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
162 & a multilayer framework to assess influenza intervention policies & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{163} & \cellcolor{gray!6}{a note on the use of optimal control on a discrete time model of influenza dynamics} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
164 & a simulation-based assessment of school closure strategies during an influenza epidemic & yes & influenza & prospective analysis & agents\\
\cellcolor{gray!6}{165} & \cellcolor{gray!6}{agent-based modeling of the spread of influenza-like illness in an emergency department: a simulation study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
\addlinespace
166 & antiviral treatment for pandemic influenza: assessing potential repercussions using a seasonally forced sir model & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{167} & \cellcolor{gray!6}{can antiviral drugs contain pandemic influenza transmission?} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
168 & characterizing the epidemiology of the 2009 influenza a/h1n1 pandemic in mexico & yes & influenza & retrospective analysis & compartments\\
\cellcolor{gray!6}{169} & \cellcolor{gray!6}{cholera epidemic in haiti, 2010: using a transmission model to explain spatial spread of disease and identify optimal control interventions} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{cholera} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
170 & controlling an influenza outbreak in deterministic and stochastic models with the emergence and evolution of drug resistance (model 1) & not applicable & influenza & prospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{171} & \cellcolor{gray!6}{modeling control strategies for concurrent epidemics of seasonal and pandemic h1n1 influenza} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
172 & modeling the impact of behavior changes on the spread of pandemic influenza & not applicable & influenza & retrospective analysis & compartments\\
\cellcolor{gray!6}{173} & \cellcolor{gray!6}{modelling and analysis of influenza a (h1n1) on networks} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
174 & modelling the strategies for age specific vaccination scheduling during influenza pandemic outbreaks & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{175} & \cellcolor{gray!6}{modelling the transmission dynamics and control of the novel 2009 swine influenza (h1n1) pandemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
176 & planning for the control of pandemic influenza a (h1n1) in los angeles county and the united states & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{177} & \cellcolor{gray!6}{prioritization of delayed vaccination for pandemic influenza} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
178 & temporal factors in school closure policy for mitigating the spread of influenza & yes & influenza & prospective analysis & agents\\
\cellcolor{gray!6}{179} & \cellcolor{gray!6}{the global transmission and control of influenza} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
180 & toward effective vaccine deployment: a systematic study & yes & influenza & prospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{181} & \cellcolor{gray!6}{vaccination against 2009 pandemic h1n1 in a population dynamical model of vancouver, canada: timing is everything} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
182 & a simulation model for the potential spread of foot-and-mouth disease in the castile and leon region of spain & yes & fmd & prospective analysis & compartments\\
\cellcolor{gray!6}{183} & \cellcolor{gray!6}{community-based measures for mitigating the 2009 h1n1 pandemic in china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{agents}\\
184 & effective real-time allocation of pandemic interventions & yes & influenza & prospective analysis & agents\\
\cellcolor{gray!6}{185} & \cellcolor{gray!6}{efficient mitigation strategies for epidemics in rural regions} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
186 & influenza pandemic waves under various mitigation strategies with 2009 h1n1 as a case study & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{187} & \cellcolor{gray!6}{is a mass immunization program for pandemic (h1n1) 2009 good value for money? early evidence from the canadian experience} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
188 & optimal control for pandemic influenza: the role of limited antiviral treatment and isolation & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{189} & \cellcolor{gray!6}{optimizing vaccine allocation at different points in time during an epidemic} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
190 & simulating school closure strategies to mitigate an influenza epidemic & yes & influenza & prospective analysis & agents\\
\addlinespace
\cellcolor{gray!6}{191} & \cellcolor{gray!6}{the effect of mask use on the spread of influenza during a pandemic} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
192 & transmission dynamics of an influenza model with age of infection and antiviral treatment & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{193} & \cellcolor{gray!6}{transmission risks and control of foot-and-mouth disease in the netherlands: spatial patterns} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{agents}\\
194 & when should we intervene to control the 2009 influenza a(h1n1) pandemic? & yes & influenza & retrospective analysis & compartments\\
\cellcolor{gray!6}{195} & \cellcolor{gray!6}{adaptive vaccination strategies to mitigate pandemic influenza} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
196 & antiviral resistance and the control of pandemic influenza: the roles of stochasticity, evolution and model details & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{197} & \cellcolor{gray!6}{economic evaluation of influenza pandemic mitigation strategies in the united states using a stochastic microsimulation transmission model} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
198 & effectiveness and cost-effectiveness of expanded antiviral prophylaxis and adjuvanted vaccination strategies for an influenza a (h5n1) pandemic & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{199} & \cellcolor{gray!6}{engineering responses to pandemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{agents}\\
200 & epidemiological benefits of more-effective tuberculosis vaccines, drugs, and diagnostics & no & tuberculosis & prospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{201} & \cellcolor{gray!6}{household epidemics: modelling effects of early stage vaccination} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
202 & measures against transmission of pandemic h1n1 influenza in japan in 2009: simulation model & yes & influenza & prospective analysis & agents\\
\cellcolor{gray!6}{203} & \cellcolor{gray!6}{modeling vaccination campaigns and the fall/winter 2009 activity of the new a(h1n1) influenza in the northern hemisphere} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
204 & modelling foot and mouth disease & no & fmd & prospective analysis & compartments\\
\cellcolor{gray!6}{205} & \cellcolor{gray!6}{modelling of the influenza a(h1n1)v outbreak in mexico city, april-may 2009, with control sanitary measures} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
206 & post-exposure prophylaxis during pandemic outbreaks & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{207} & \cellcolor{gray!6}{potential for a global dynamic of influenza a (h1n1)} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
208 & reducing the impact of the next influenza pandemic using householdbased public health interventions & yes & influenza & prospective analysis & agents\\
\cellcolor{gray!6}{209} & \cellcolor{gray!6}{seasonal transmission potential and activity peaks of the new influenza a(h1n1): a monte carlo likelihood analysis based on human mobility} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
210 & simulation of foot-and-mouth disease spread within an integrated livestock system in texas, usa & yes & fmd & prospective analysis & agents\\
\addlinespace
\cellcolor{gray!6}{211} & \cellcolor{gray!6}{the transmissibility and control of pandemic influenza a (h1n1) virus} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
212 & bayesian analysis of severe acute respiratory syndrome: the 2003 hong kong epidemic & no & pneumococcal disease & retrospective analysis & compartments\\
\cellcolor{gray!6}{213} & \cellcolor{gray!6}{hepatitis b vaccination and changes in sexual risk behaviour among men who have sex with men in amsterdam} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{hepatitis b} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
214 & mathematical assessment of canada's pandemic influenza preparedness plan & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{215} & \cellcolor{gray!6}{modeling targeted layered containment of an influenza pandemic in the united states} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
\addlinespace
216 & optimal allocation of pandemic influenza vaccine depends on age, risk and timing & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{217} & \cellcolor{gray!6}{pandemic simulation of antivirals plus school closures: buying time until strain-specific vaccine is available} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza pneumococcal disease} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
218 & preparedness for the spread of influenza: prohibition of traffic, school closure, and vaccination of children in the commuter towns of tokyo & yes & influenza & prospective analysis & agents\\
\cellcolor{gray!6}{219} & \cellcolor{gray!6}{scenarios of diffusion and control of an influenza pandemic in italy} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
220 & time is of the essence: exploring a measles outbreak response vaccination in niamey, niger & yes & measles & retrospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{221} & \cellcolor{gray!6}{a stochastic equation-based model of the value of international air-travel restrictions for controlling pandemic flu} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
222 & assessing the role of basic control measures, antivirals and vaccine in curtailing pandemic influenza: scenarios for the us, uk and the netherlands & yes & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{223} & \cellcolor{gray!6}{deterministic sir (susceptible–infected–removed) models applied to varicella outbreaks} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{varicella} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{agents}\\
224 & effectiveness of movement-prevention regulations to reduce the spread of foot-and-mouth disease in the netherlands & yes & fmd & retrospective analysis & agents\\
\cellcolor{gray!6}{225} & \cellcolor{gray!6}{effects of internal border control on spread of pandemic influenza} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
226 & simple models of influenza progression within a heterogeneous population & not applicable & influenza & retrospective analysis & compartments\\
\cellcolor{gray!6}{227} & \cellcolor{gray!6}{stochastic model of an influenza epidemic with drug resistance} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
228 & the effect of public health measures on the 1918 influenza pandemic in u.s. cities & no & influenza & retrospective analysis & compartments\\
\cellcolor{gray!6}{229} & \cellcolor{gray!6}{vaccinating in disease-free regions: a vaccine model with application to yellow fever} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yellow fever} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
230 & a 'small-world-like' model for comparing interventions aimed at preventing and controlling influenza pandemics & not applicable & influenza & prospective analysis & agents\\
\addlinespace
\cellcolor{gray!6}{231} & \cellcolor{gray!6}{containing pandemic influenza with antiviral agents: analytical commentary} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
232 & critical response to post-outbreak vaccination against foot-and-mouth disease & no & fmd & prospective analysis & agents\\
\cellcolor{gray!6}{233} & \cellcolor{gray!6}{mitigation strategies for pandemic influenza in the united states} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{influenza} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
234 & simple models for containment of a pandemic & not applicable & influenza & prospective analysis & compartments\\
\cellcolor{gray!6}{235} & \cellcolor{gray!6}{statistical inference in a stochastic epidemic seir model with control intervention: ebola as a case study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{ebola} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
236 & strategies for containing an emerging influenza pandemic in southeast asia & yes & influenza & prospective analysis & agents\\
\cellcolor{gray!6}{237} & \cellcolor{gray!6}{modeling alternative mitigation strategies for a hypothetical outbreak of foot-and-mouth disease in the united states} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
238 & modelling vaccination strategies against foot-and-mouth disease & yes & fmd & prospective analysis & agents\\
\cellcolor{gray!6}{239} & \cellcolor{gray!6}{a decision-tree to optimise control measures during the early stage of a foot-and-mouth disease epidemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
240 & effect of control measures on the course of simulated foot and mouth disease epidemics that started on different farm types in various dutch areas & yes & fmd & retrospective analysis & agents\\
\addlinespace
\cellcolor{gray!6}{241} & \cellcolor{gray!6}{dynamics of the 2001 uk foot and mouth epidemic: stochastic dispersal in a heterogeneous landscape} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
242 & an extended state-transition model for foot-and-mouth disease epidemics in france & yes & fmd & retrospective analysis & compartments\\
\cellcolor{gray!6}{243} & \cellcolor{gray!6}{simulated economic consequences of foot-and-mouth disease epidemics and their public control in france} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{retrospective analysis} & \cellcolor{gray!6}{compartments}\\
244 & effect of chemotherapy on malaria transmission among yanomami amerindians: simulated consequences of placebo treatment & yes & malaria & retrospective analysis & compartments\\
\cellcolor{gray!6}{245} & \cellcolor{gray!6}{modelling vaccination strategy against directly transmitted diseases using a series of pulses} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{rubella} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
\addlinespace
246 & mass vaccination to control chickenpox: the influence of zoster & no & varicella & retrospective analysis & compartments\\
\cellcolor{gray!6}{247} & \cellcolor{gray!6}{an evaluation of alternate control strategies for foot-and-mouth disease in australia: a regional approach} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{fmd} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{agents}\\
248 & analysis of a measles epidemic & yes & measles & prospective analysis & compartments\\
\cellcolor{gray!6}{249} & \cellcolor{gray!6}{a model of the transmission of dengue fever with an evaluation of the impact of ultra-low volume (ulv) insecticide applications on dengue epidemics} & \cellcolor{gray!6}{not applicable} & \cellcolor{gray!6}{dengue} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
250 & a discrete-time model with vaccination for a measles epidemic & yes & measles & retrospective analysis & compartments\\
\addlinespace
\cellcolor{gray!6}{251} & \cellcolor{gray!6}{a stochastic model of epidemics in military recruits} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{measles} & \cellcolor{gray!6}{prospective analysis} & \cellcolor{gray!6}{compartments}\\
252 & stochastic two-agent epidemic simulation models for a community of families & not applicable & poliomyelitis & prospective analysis & agents\\*
\end{longtable}
\endgroup{}
\end{landscape}

\hypertarget{table-3}{%
\subsection{Table 3}\label{table-3}}

This section presents extracted data on whether spatial heterogeneity
was represented (space\_representation), the type of model structure
(model\_structure), the type of parametrization and validation method
used.

\begin{landscape}\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}{l>{\raggedright\arraybackslash}p{3cm}l>{\raggedright\arraybackslash}p{3cm}ll}
\toprule
num & title & space\_representation & model\_structure & parametrization & validation\\
\midrule
\endfirsthead
\multicolumn{6}{@{}l}{\textit{(continued)}}\\
\toprule
num & title & space\_representation & model\_structure & parametrization & validation\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{a cholera metapopulation model interlinking migration with intervention strategies - a case study of zimbabwe (2008-2009)} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{fitted} & \cellcolor{gray!6}{none}\\
2 & a theoretical single-parameter model for urbanisation to study infectious disease spread and interventions & yes & deterministic & expert opinion & none\\
\cellcolor{gray!6}{3} & \cellcolor{gray!6}{assessing the effects of modeling the spectrum of clinical symptoms on the dynamics and control of ebola} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{fitted} & \cellcolor{gray!6}{none}\\
4 & dynamical analysis and control strategies in modelling ebola virus disease & yes & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{5} & \cellcolor{gray!6}{effect of a hepatitis a vaccination campaign during a hepatitis a outbreak in taiwan, 2015–2017: a modeling study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
\addlinespace
6 & evaluating strategies for control of tuberculosis in prisons and prevention of spillover into communities: an observational and modeling study from brazil & no & stochastic & literature and fitted & data\\
\cellcolor{gray!6}{7} & \cellcolor{gray!6}{evaluating the effects of control interventions and estimating the inapparent infections for dengue outbreak in hangzhou, china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{none}\\
8 & incidence dynamics and investigation of key interventions in a dengue outbreak in ningbo city, china & no & deterministic & literature and fitted & data\\
\cellcolor{gray!6}{9} & \cellcolor{gray!6}{incorporating media data into a model of infectious disease transmission} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
10 & influence of asymptomatic infections for the effectiveness of facemasks during pandemic influenza & no & deterministic & literature and expert opinion & none\\
\addlinespace
\cellcolor{gray!6}{11} & \cellcolor{gray!6}{mathematical analysis of a cholera infection model with vaccination strategy} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
12 & modeling and stability analysis of epidemic expansion disease ebola virus with implications prevention in population & no & deterministic & expert opinion & none\\
\cellcolor{gray!6}{13} & \cellcolor{gray!6}{modeling the effectiveness of respiratory protective devices in reducing influenza outbreak} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
14 & modeling the effects of vaccination and treatment on tuberculosis transmission dynamics & no & deterministic & literature and fitted & data\\
\cellcolor{gray!6}{15} & \cellcolor{gray!6}{optimal control and cost-effective analysis of the 2017 meningitis outbreak in nigeria} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{none}\\
\addlinespace
16 & optimal control strategies for a two-group epidemic model with vaccination-resource constraints & no & deterministic & literature & none\\
\cellcolor{gray!6}{17} & \cellcolor{gray!6}{optimal media reporting intensity on mitigating spread of an emerging infectious disease} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{none}\\
18 & school dismissal as a pandemic influenza response: when, where and for how long? & no & stochastic & literature and expert opinion & none\\
\cellcolor{gray!6}{19} & \cellcolor{gray!6}{study on modeling simulation and optimal control method for the transmission risk of the ebola virus} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
20 & transmission dynamics of cholera with hyperinfectious and hypoinfectious vibrios: mathematical modelling and control strategies & no & deterministic & literature and expert opinion & data\\
\addlinespace
\cellcolor{gray!6}{21} & \cellcolor{gray!6}{a new epidemics–logistics model: insights into controlling the ebola virus disease in west africa} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{data}\\
22 & contact reductions from live poultry market closures limit the epidemic of human infections with h7n9 influenza & no & deterministic & expert opinion & none\\
\cellcolor{gray!6}{23} & \cellcolor{gray!6}{disparities in spread and control of influenza in slums of delhi: findings from an agent-based modelling study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
24 & efficacy of control measures in the control of ebola, liberia 2014–2015 & no & deterministic & literature and fitted & data\\
\cellcolor{gray!6}{25} & \cellcolor{gray!6}{epidemiology of the silent polio outbreak in rahat, israel, based on modeling of environmental surveillance data} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{fitted} & \cellcolor{gray!6}{none}\\
\addlinespace
26 & evaluating costs and health consequences of sick leave strategies against pandemic and seasonal influenza in norway using a dynamic model & no & deterministic & literature and fitted & none\\
\cellcolor{gray!6}{27} & \cellcolor{gray!6}{evaluating vaccination strategies to control foot-and-mouth disease: a country comparison study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{another model}\\
28 & impact of public health responses during a measles outbreak in an amish community in ohio: modeling the dynamics of transmission & no & stochastic & literature and fitted & data\\
\cellcolor{gray!6}{29} & \cellcolor{gray!6}{initial validation of a simulation model for estimating the impact of serogroup a neisseria meningitidis vaccination in the african meningitis belt} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
30 & logistical constraints lead to an intermediate optimum in outbreak response vaccination & no & stochastic & expert opinion & none\\
\addlinespace
\cellcolor{gray!6}{31} & \cellcolor{gray!6}{manipulation of contact network structure and the impact on foot-and-mouth disease transmission} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
32 & mathematical model and intervention strategies for mitigating tuberculosis in the philippines & no & deterministic & literature and expert opinion and fitted & data\\
\cellcolor{gray!6}{33} & \cellcolor{gray!6}{measles outbreak response decision-making under uncertainty: a retrospective analysis} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{data}\\
34 & modeling the heterogeneity of dengue transmission in a city & no & deterministic & literature and expert opinion and fitted & data\\
\cellcolor{gray!6}{35} & \cellcolor{gray!6}{modelling the large-scale yellow fever outbreak in luanda, angola, and the impact of vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{expert opinion and fitted} & \cellcolor{gray!6}{none}\\
\addlinespace
36 & quantifying the impact of early-stage contact tracing on controlling ebola diffusion & no & stochastic & literature and expert opinion & none\\
\cellcolor{gray!6}{37} & \cellcolor{gray!6}{simulation of key interventions for seasonal influenza outbreak control at school in changsha, china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
38 & the impact of regular school closure on seasonal influenza epidemics: a data-driven spatial transmission model for belgium & yes & stochastic & literature and fitted & data\\
\cellcolor{gray!6}{39} & \cellcolor{gray!6}{the potential impact of case-area targeted interventions in response to cholera outbreaks: a modeling study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
40 & value of inventory information in allocating a limited supply of influenza vaccine during a pandemic & no & deterministic & expert opinion & none\\
\addlinespace
\cellcolor{gray!6}{41} & \cellcolor{gray!6}{an age-structured model for cholera control with vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
42 & an approach to and web-based tool for infectious disease outbreak intervention analysis & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{43} & \cellcolor{gray!6}{an economic assessment of foot and mouth disease in japan} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
44 & analysis of an seriv epidemic model of human influenza & no & deterministic & expert opinion & none\\
\cellcolor{gray!6}{45} & \cellcolor{gray!6}{control strategies of avian influenza pandemic model with time delay} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{expert opinion} & \cellcolor{gray!6}{none}\\
\addlinespace
46 & costs and benefits of including inactivated in addition to oral poliovirus vaccine in outbreak response after cessation of oral poliovirus vaccine use & no & deterministic & literature and fitted & data\\
\cellcolor{gray!6}{47} & \cellcolor{gray!6}{deriving effective vaccine allocation strategies for pandemic influenza: comparison of an agent-based simulation and a compartmental model} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{both} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{another model}\\
48 & early rigorous control interventions can largely reduce dengue outbreak magnitude: experience from chaozhou, china & no & deterministic & literature and fitted & data\\
\cellcolor{gray!6}{49} & \cellcolor{gray!6}{effects of reactive social distancing on the 1918 influenza pandemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
50 & epidemiological and economic impact of pandemic influenza in chicago: priorities for vaccine interventions & no & stochastic & literature and expert opinion and fitted & none\\
\addlinespace
\cellcolor{gray!6}{51} & \cellcolor{gray!6}{estimating direct and indirect protective effect of influenza vaccination in the united states} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
52 & evaluating the effects of common control measures for influenza a (h1n1) outbreak at school in china: a modeling study & no & deterministic & literature and fitted & data\\
\cellcolor{gray!6}{53} & \cellcolor{gray!6}{evaluation of strategies to control a potential outbreak of foot-and-mouth disease in sweden} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{none}\\
54 & impact of a waning vaccine and altered behavior on the spread of influenza & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{55} & \cellcolor{gray!6}{mathematical models for devising the optimal ebola virus disease eradication} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
\addlinespace
56 & modeling the role of public health education in ebola virus disease outbreaks in sudan & no & deterministic & fitted & data\\
\cellcolor{gray!6}{57} & \cellcolor{gray!6}{modelling the transmission and control strategies of varicella among school children in shenzhen, china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{none}\\
58 & optimal and adaptive control of an epidemic model of influenza with unknown parameters & no & deterministic & expert opinion & none\\
\cellcolor{gray!6}{59} & \cellcolor{gray!6}{simulating endogenous dynamics of intervention-capacity deployment: ebola outbreak in liberia} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{data}\\
60 & simulating the potential role of media coverage and infected bats in the 2014 ebola outbreak & no & deterministic & literature and fitted & data\\
\addlinespace
\cellcolor{gray!6}{61} & \cellcolor{gray!6}{a mathematical model of ebola virus disease: using sensitivity analysis to determine effective intervention targets} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
62 & a multi-agent model for adaptive vaccination during infectious disease outbreaks & no & stochastic & literature and expert opinion and fitted & data\\
\cellcolor{gray!6}{63} & \cellcolor{gray!6}{assessing the efficiency of movement restriction as a control strategy of ebola} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
64 & characterization of outbreak response strategies and potential vaccine stockpile needs for the polio endgame & yes & both & literature and expert opinion & none\\
\cellcolor{gray!6}{65} & \cellcolor{gray!6}{designing public health policies to mitigate the adverse consequences of rural-urban migration via meta-population modeling} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{both} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
\addlinespace
66 & dynamic model of influenza with age-structured and media coverage & no & deterministic & literature & none\\
\cellcolor{gray!6}{67} & \cellcolor{gray!6}{economic evaluation of individual school closure strategies: the hong kong 2009 h1n1 pandemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{both} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
68 & efficient vaccine distribution based on a hybrid compartmental model & yes & deterministic & literature and expert opinion & data\\
\cellcolor{gray!6}{69} & \cellcolor{gray!6}{epidemiological evaluation of different fmd control strategies in two selected regions in austria} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
70 & evaluating targeted interventions via meta-population models with multi-level mixing & yes & deterministic & literature & none\\
\addlinespace
\cellcolor{gray!6}{71} & \cellcolor{gray!6}{evaluation of outbreak response immunization in the control of pertussis using agent-based modeling} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{data}\\
72 & global stability and optimal control for a tuberculosis model with vaccination and treatment & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{73} & \cellcolor{gray!6}{impact on epidemic measles of vaccination campaigns triggered by disease outbreaks or serosurveys: a modeling study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
74 & metapopulation and non-proportional vaccination models overview & yes & deterministic & literature & none\\
\cellcolor{gray!6}{75} & \cellcolor{gray!6}{model-based comprehensive analysis of school closure policies for mitigating influenza epidemics and pandemics} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{another model}\\
\addlinespace
76 & modeling ring-vaccination strategies to control ebola virus disease epidemics & yes & stochastic & literature & none\\
\cellcolor{gray!6}{77} & \cellcolor{gray!6}{modeling the effect of public health resources and alerting on the dynamics of pertussis spread*} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{data}\\
78 & modeling the impact of behavior change on the spread of ebola & no & deterministic & expert opinion and fitted & none\\
\cellcolor{gray!6}{79} & \cellcolor{gray!6}{modeling the spread of polio in an ipv-vaccinated population: lessons learned from the 2013 silent outbreak in southern israel} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{both} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{data}\\
80 & modelling weekly vector control against dengue in the guangdong province of china & no & deterministic & literature & none\\
\addlinespace
\cellcolor{gray!6}{81} & \cellcolor{gray!6}{optimal control strategies for the spread of ebola in west africa} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{expert opinion} & \cellcolor{gray!6}{none}\\
82 & potential impact of a ventilation intervention for influenza in the context of a dense indoor contact network in hong kong & no & stochastic & literature and expert opinion and fitted & none\\
\cellcolor{gray!6}{83} & \cellcolor{gray!6}{predicting and evaluating the epidemic trend of ebola virus disease in the 2014-2015 outbreak and the effects of intervention measures} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
84 & projected impact of dengue vaccination in yucatán, mexico & no & deterministic & literature and fitted & none\\
\cellcolor{gray!6}{85} & \cellcolor{gray!6}{seasonality and the effectiveness of mass vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
\addlinespace
86 & simulation optimization for an age-based vaccines distribution strategy against the spread of influenza epidemic & no & stochastic & literature & none\\
\cellcolor{gray!6}{87} & \cellcolor{gray!6}{spatiotemporal dynamics of the ebola epidemic in guinea and implications for vaccination and disease elimination: a computational modeling analysis} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
88 & the interplay of vaccination and vector control on small dengue networks & yes & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{89} & \cellcolor{gray!6}{an epidemic patchy model with entry–exit screening} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{none}\\
90 & assessing the role of voluntary self-isolation in the control of pandemic influenza using a household epidemic model & yes & deterministic & literature & none\\
\addlinespace
\cellcolor{gray!6}{91} & \cellcolor{gray!6}{be-codis: a mathematical model to predict the risk of human diseases spread between countries—validation and application to the 2014–2015 ebola virus disease epidemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{both} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{data}\\
92 & dengue in madeira island & no & deterministic & literature & none\\
\cellcolor{gray!6}{93} & \cellcolor{gray!6}{dynamic simulation of a seiqr-v epidemic model based on cellular automata} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{expert opinion} & \cellcolor{gray!6}{data}\\
94 & early vaccine availability represents an important public health advance for the control of pandemic influenza & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{95} & \cellcolor{gray!6}{effectiveness of ebola treatment units and community care centers — liberia, september 23–october 31, 2014} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
\addlinespace
96 & evaluation of the benefts and risks of introducing ebola community care centers, sierra leone & no & stochastic & literature and expert opinion and fitted & data\\
\cellcolor{gray!6}{97} & \cellcolor{gray!6}{evidence for emergency vaccination having played a crucial role to control the 1965/66 foot-and-mouth disease outbreak in switzerland} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{data}\\
98 & measuring the impact of ebola control measures in sierra leone & yes & stochastic & literature and fitted & data\\
\cellcolor{gray!6}{99} & \cellcolor{gray!6}{media impact switching surface during an infectious disease outbreak} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
100 & modeling options to manage type 1 wild poliovirus imported into israel in 2013 & no & deterministic & literature & none\\
\addlinespace
\cellcolor{gray!6}{101} & \cellcolor{gray!6}{modeling the effect of comprehensive interventions on ebola virus transmission} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
102 & modeling the effect of school closures in a pandemic scenario: exploring two different contact matrices & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{103} & \cellcolor{gray!6}{modelling the effect of early detection of ebola} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
104 & multi-scale modeling for the transmission of influenza and the evaluation of interventions toward it & yes & stochastic & fitted & data\\
\cellcolor{gray!6}{105} & \cellcolor{gray!6}{optimal intervention strategies for a seir control model of ebola epidemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
\addlinespace
106 & predicting the extinction of ebola spreading in liberia due to mitigation strategies & yes & both & literature and fitted & data\\
\cellcolor{gray!6}{107} & \cellcolor{gray!6}{school closure strategies for the 2009 hong kong hini influenza pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{expert opinion} & \cellcolor{gray!6}{none}\\
108 & spatiotemporal spread of the 2014 outbreak of ebola virus disease in liberia and the effectiveness of non-pharmaceutical interventions: a computational modelling analysis & yes & stochastic & literature and fitted & data\\
\cellcolor{gray!6}{109} & \cellcolor{gray!6}{strategies for early vaccination during novel influenza outbreaks} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{none}\\
110 & the effects of media reports on disease spread and important public health measurements & no & both & literature and expert opinion and fitted & data\\
\addlinespace
\cellcolor{gray!6}{111} & \cellcolor{gray!6}{the impact of human behavioral changes in 2014 west africa ebola outbreak} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
112 & transmission dynamics and final epidemic size of ebola virus disease outbreaks with varying interventions & no & deterministic & literature and fitted & data\\
\cellcolor{gray!6}{113} & \cellcolor{gray!6}{treatment–donation-stockpile dynamics in ebola convalescent blood transfusion therapy} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
114 & vaccine prioritization for effective pandemic response & no & both & literature and expert opinion & data and another model\\
\cellcolor{gray!6}{115} & \cellcolor{gray!6}{a mathematical study of a tb model with treatment interruptions and two latent periods} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
\addlinespace
116 & antiviral prophylaxis and isolation for the control of pandemic influenza & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{117} & \cellcolor{gray!6}{assessing the impact of travel restrictions on international spread of the 2014 west african ebola epidemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{none}\\
118 & assessing the use of antiviral treatment to control influenza & no & deterministic & expert opinion & none\\
\cellcolor{gray!6}{119} & \cellcolor{gray!6}{behavior in the time of cholera: evidence from the 2008-2009 cholera outbreak in zimbabwe} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{fitted} & \cellcolor{gray!6}{data}\\
120 & behavioural response in educated young adults towards influenza a(h1n1)pdm09 & no & deterministic & literature and fitted & data\\
\addlinespace
\cellcolor{gray!6}{121} & \cellcolor{gray!6}{cover your cough! quantifying the benefits of a localized healthy behavior intervention on flu epidemics in washington dc} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
122 & dynamics and control of ebola virus transmission in montserrado, liberia: a mathematical modelling analysis & no & stochastic & literature and fitted & data\\
\cellcolor{gray!6}{123} & \cellcolor{gray!6}{estimating the effectiveness of early control measures through school absenteeism surveillance in observed outbreaks at rural schools in hubei, china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
124 & evaluation of the benefit of emergency vaccination in a foot-and-mouth disease free country with low livestock density & yes & deterministic & fitted & none\\
\cellcolor{gray!6}{125} & \cellcolor{gray!6}{modeling the dynamics of oral poliovirus vaccine cessation} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
\addlinespace
126 & modeling the impact of optimal screening on typhoid dynamics & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{127} & \cellcolor{gray!6}{modeling the influence of environment and intervention oncholera in haiti} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{none}\\
128 & sequential bayesian inference in hidden markov stochastic kinetic models with application to detection and response to seasonal epidemics & no & stochastic & expert opinion & none\\
\cellcolor{gray!6}{129} & \cellcolor{gray!6}{simulating optimal vaccination times during cholera outbreaks} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
130 & the role of vaccination coverage, individual behaviors, and the public health response in the control of measles epidemics: an agent-based simulation for california & no & deterministic & literature & none\\
\addlinespace
\cellcolor{gray!6}{131} & \cellcolor{gray!6}{time is (still) of the essence: quantifying the impact of emergency meningitis vaccination response in katsina state, nigeria} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{data}\\
132 & a perspective on multiple waves of influenza pandemics & no & deterministic & literature and fitted & none\\
\cellcolor{gray!6}{133} & \cellcolor{gray!6}{an optimal control problem arising from a dengue disease transmission model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{expert opinion} & \cellcolor{gray!6}{none}\\
134 & cholera in haiti: reproductive numbers and vaccination coverage estimates & yes & deterministic & fitted & none\\
\cellcolor{gray!6}{135} & \cellcolor{gray!6}{comparing control strategies against foot-and-mouth disease: will vaccination be cost-effective in denmark?} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{none}\\
\addlinespace
136 & cost-effectiveness of influenza control measures: a dynamic transmission model-based analysis & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{137} & \cellcolor{gray!6}{cost-effectiveness of workplace closure and travel restriction for mitigating influenza outbreaks: a network-based simulation} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
138 & decisions on control of foot-and-mouth disease informed using model predictions & no & deterministic & expert opinion and fitted & none\\
\cellcolor{gray!6}{139} & \cellcolor{gray!6}{dengue in cape verde: vector control and vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
140 & enhancement of collective immunity in tokyo metropolitan area by selective vaccination against an emerging influenza pandemic & yes & stochastic & literature and expert opinion & none\\
\addlinespace
\cellcolor{gray!6}{141} & \cellcolor{gray!6}{estimated impact of aggressive empirical antiviral treatment in containing an outbreak of pandemic influenza h1n1 in an isolated first nations community} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{fitted} & \cellcolor{gray!6}{none}\\
142 & multiregional dynamic vaccine allocation during an influenza epidemic & no & deterministic & expert opinion & none\\
\cellcolor{gray!6}{143} & \cellcolor{gray!6}{policies to reduce influenza in the workplace: impact assessments using an agent-based model} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
144 & transmission dynamics of the 2009 influenza a (h1n1) pandemic in india: the impact of holiday-related school closure & yes & stochastic & literature and expert opinion and fitted & data\\
\cellcolor{gray!6}{145} & \cellcolor{gray!6}{vaccination against foot-and-mouth disease: do initial conditions affect its benefit?} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
\addlinespace
146 & was mandatory quarantine necessary in china for controlling the 2009 h1n1 pandemic? & no & deterministic & literature & data\\
\cellcolor{gray!6}{147} & \cellcolor{gray!6}{a contact-network-based simulation model for evaluating interventions under 'what-if' scenarios in epidemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
148 & campus quarantine (fengxiao) for curbing emergent infectious diseases: lessons from mitigating a/h1n1 in xi'an, china & no & deterministic & literature and fitted & none\\
\cellcolor{gray!6}{149} & \cellcolor{gray!6}{dynamic modelling of costs and health consequences of school closure during an influenza pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
150 & effect of vaccines and antivirals during the major 2009 a(h1n1) pandemic wave in norway - and the influence of vaccination timing & no & deterministic & literature and expert opinion and fitted & data\\
\addlinespace
\cellcolor{gray!6}{151} & \cellcolor{gray!6}{estimating the value of containment strategies in delaying the arrival time of an influenza pandemic: a case study of travel restriction and patient isolation} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{expert opinion} & \cellcolor{gray!6}{none}\\
152 & how to minimize the attack rate during multiple influenza outbreaks in a heterogeneous population & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{153} & \cellcolor{gray!6}{modeling strategies for controlling h1n1 outbreaks in china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{none}\\
154 & modeling the effects of h1n1 influenza vaccine distribution in the united states & yes & deterministic & expert opinion and fitted & data\\
\cellcolor{gray!6}{155} & \cellcolor{gray!6}{modeling the impact of air, sea, and land travel restrictions supplemented by other interventions on the emergence of a new influenza pandemic virus} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{none}\\
\addlinespace
156 & simulating school closure policies for cost effective pandemic decision making & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{157} & \cellcolor{gray!6}{the impact of school closures on pandemic influenza: assessing potential repercussions using a seasonal sir model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
158 & vaccination against foot-and-mouth disease i: epidemiological consequences & yes & stochastic & literature and fitted & none\\
\cellcolor{gray!6}{159} & \cellcolor{gray!6}{a deterministic resource scheduling model in epidemic control: a case study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
160 & a model for the a(h1n1) epidemic in mexico, including social isolation & no & deterministic & literature and fitted & data\\
\addlinespace
\cellcolor{gray!6}{161} & \cellcolor{gray!6}{a model to evaluate mass vaccination against pneumococcus as a countermeasure against pandemic influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{fitted} & \cellcolor{gray!6}{none}\\
162 & a multilayer framework to assess influenza intervention policies & yes & deterministic & expert opinion & none\\
\cellcolor{gray!6}{163} & \cellcolor{gray!6}{a note on the use of optimal control on a discrete time model of influenza dynamics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{expert opinion} & \cellcolor{gray!6}{none}\\
164 & a simulation-based assessment of school closure strategies during an influenza epidemic & no & stochastic & literature and expert opinion & none\\
\cellcolor{gray!6}{165} & \cellcolor{gray!6}{agent-based modeling of the spread of influenza-like illness in an emergency department: a simulation study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
\addlinespace
166 & antiviral treatment for pandemic influenza: assessing potential repercussions using a seasonally forced sir model & no & deterministic & literature and fitted & none\\
\cellcolor{gray!6}{167} & \cellcolor{gray!6}{can antiviral drugs contain pandemic influenza transmission?} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
168 & characterizing the epidemiology of the 2009 influenza a/h1n1 pandemic in mexico & yes & stochastic & fitted & none\\
\cellcolor{gray!6}{169} & \cellcolor{gray!6}{cholera epidemic in haiti, 2010: using a transmission model to explain spatial spread of disease and identify optimal control interventions} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{data}\\
170 & controlling an influenza outbreak in deterministic and stochastic models with the emergence and evolution of drug resistance (model 1) & no & both & literature and expert opinion & none\\
\addlinespace
\cellcolor{gray!6}{171} & \cellcolor{gray!6}{modeling control strategies for concurrent epidemics of seasonal and pandemic h1n1 influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{none}\\
172 & modeling the impact of behavior changes on the spread of pandemic influenza & no & deterministic & expert opinion & none\\
\cellcolor{gray!6}{173} & \cellcolor{gray!6}{modelling and analysis of influenza a (h1n1) on networks} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
174 & modelling the strategies for age specific vaccination scheduling during influenza pandemic outbreaks & no & deterministic & literature and expert opinion and fitted & data\\
\cellcolor{gray!6}{175} & \cellcolor{gray!6}{modelling the transmission dynamics and control of the novel 2009 swine influenza (h1n1) pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{none}\\
\addlinespace
176 & planning for the control of pandemic influenza a (h1n1) in los angeles county and the united states & no & both & literature and fitted & data\\
\cellcolor{gray!6}{177} & \cellcolor{gray!6}{prioritization of delayed vaccination for pandemic influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
178 & temporal factors in school closure policy for mitigating the spread of influenza & yes & stochastic & literature and expert opinion & none\\
\cellcolor{gray!6}{179} & \cellcolor{gray!6}{the global transmission and control of influenza} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{data}\\
180 & toward effective vaccine deployment: a systematic study & no & deterministic & literature and fitted & data\\
\addlinespace
\cellcolor{gray!6}{181} & \cellcolor{gray!6}{vaccination against 2009 pandemic h1n1 in a population dynamical model of vancouver, canada: timing is everything} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
182 & a simulation model for the potential spread of foot-and-mouth disease in the castile and leon region of spain & yes & stochastic & literature and expert opinion and fitted & none\\
\cellcolor{gray!6}{183} & \cellcolor{gray!6}{community-based measures for mitigating the 2009 h1n1 pandemic in china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{fitted} & \cellcolor{gray!6}{none}\\
184 & effective real-time allocation of pandemic interventions & yes & stochastic & literature & none\\
\cellcolor{gray!6}{185} & \cellcolor{gray!6}{efficient mitigation strategies for epidemics in rural regions} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{fitted} & \cellcolor{gray!6}{none}\\
\addlinespace
186 & influenza pandemic waves under various mitigation strategies with 2009 h1n1 as a case study & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{187} & \cellcolor{gray!6}{is a mass immunization program for pandemic (h1n1) 2009 good value for money? early evidence from the canadian experience} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{expert opinion} & \cellcolor{gray!6}{none}\\
188 & optimal control for pandemic influenza: the role of limited antiviral treatment and isolation & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{189} & \cellcolor{gray!6}{optimizing vaccine allocation at different points in time during an epidemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{data}\\
190 & simulating school closure strategies to mitigate an influenza epidemic & yes & stochastic & literature and fitted & none\\
\addlinespace
\cellcolor{gray!6}{191} & \cellcolor{gray!6}{the effect of mask use on the spread of influenza during a pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
192 & transmission dynamics of an influenza model with age of infection and antiviral treatment & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{193} & \cellcolor{gray!6}{transmission risks and control of foot-and-mouth disease in the netherlands: spatial patterns} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
194 & when should we intervene to control the 2009 influenza a(h1n1) pandemic? & no & deterministic & literature & none\\
\cellcolor{gray!6}{195} & \cellcolor{gray!6}{adaptive vaccination strategies to mitigate pandemic influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{data}\\
\addlinespace
196 & antiviral resistance and the control of pandemic influenza: the roles of stochasticity, evolution and model details & no & stochastic & literature and expert opinion & none\\
\cellcolor{gray!6}{197} & \cellcolor{gray!6}{economic evaluation of influenza pandemic mitigation strategies in the united states using a stochastic microsimulation transmission model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
198 & effectiveness and cost-effectiveness of expanded antiviral prophylaxis and adjuvanted vaccination strategies for an influenza a (h5n1) pandemic & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{199} & \cellcolor{gray!6}{engineering responses to pandemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
200 & epidemiological benefits of more-effective tuberculosis vaccines, drugs, and diagnostics & no & deterministic & literature and expert opinion and fitted & data\\
\addlinespace
\cellcolor{gray!6}{201} & \cellcolor{gray!6}{household epidemics: modelling effects of early stage vaccination} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
202 & measures against transmission of pandemic h1n1 influenza in japan in 2009: simulation model & no & stochastic & literature and expert opinion and fitted & none\\
\cellcolor{gray!6}{203} & \cellcolor{gray!6}{modeling vaccination campaigns and the fall/winter 2009 activity of the new a(h1n1) influenza in the northern hemisphere} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
204 & modelling foot and mouth disease & yes & deterministic & literature and expert opinion & data\\
\cellcolor{gray!6}{205} & \cellcolor{gray!6}{modelling of the influenza a(h1n1)v outbreak in mexico city, april-may 2009, with control sanitary measures} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{expert opinion and fitted} & \cellcolor{gray!6}{none}\\
\addlinespace
206 & post-exposure prophylaxis during pandemic outbreaks & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{207} & \cellcolor{gray!6}{potential for a global dynamic of influenza a (h1n1)} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
208 & reducing the impact of the next influenza pandemic using householdbased public health interventions & no & deterministic & expert opinion & none\\
\cellcolor{gray!6}{209} & \cellcolor{gray!6}{seasonal transmission potential and activity peaks of the new influenza a(h1n1): a monte carlo likelihood analysis based on human mobility} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
210 & simulation of foot-and-mouth disease spread within an integrated livestock system in texas, usa & yes & deterministic & fitted & none\\
\addlinespace
\cellcolor{gray!6}{211} & \cellcolor{gray!6}{the transmissibility and control of pandemic influenza a (h1n1) virus} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{data}\\
212 & bayesian analysis of severe acute respiratory syndrome: the 2003 hong kong epidemic & no & stochastic & fitted & none\\
\cellcolor{gray!6}{213} & \cellcolor{gray!6}{hepatitis b vaccination and changes in sexual risk behaviour among men who have sex with men in amsterdam} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
214 & mathematical assessment of canada's pandemic influenza preparedness plan & no & deterministic & fitted & none\\
\cellcolor{gray!6}{215} & \cellcolor{gray!6}{modeling targeted layered containment of an influenza pandemic in the united states} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
\addlinespace
216 & optimal allocation of pandemic influenza vaccine depends on age, risk and timing & no & deterministic & literature & data\\
\cellcolor{gray!6}{217} & \cellcolor{gray!6}{pandemic simulation of antivirals plus school closures: buying time until strain-specific vaccine is available} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{expert opinion} & \cellcolor{gray!6}{none}\\
218 & preparedness for the spread of influenza: prohibition of traffic, school closure, and vaccination of children in the commuter towns of tokyo & yes & stochastic & literature and expert opinion and fitted & data\\
\cellcolor{gray!6}{219} & \cellcolor{gray!6}{scenarios of diffusion and control of an influenza pandemic in italy} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{both} & \cellcolor{gray!6}{literature and expert opinion and fitted} & \cellcolor{gray!6}{none}\\
220 & time is of the essence: exploring a measles outbreak response vaccination in niamey, niger & yes & stochastic & literature and fitted & data\\
\addlinespace
\cellcolor{gray!6}{221} & \cellcolor{gray!6}{a stochastic equation-based model of the value of international air-travel restrictions for controlling pandemic flu} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
222 & assessing the role of basic control measures, antivirals and vaccine in curtailing pandemic influenza: scenarios for the us, uk and the netherlands & no & deterministic & literature & none\\
\cellcolor{gray!6}{223} & \cellcolor{gray!6}{deterministic sir (susceptible infected removed) models applied to varicella outbreaks} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{both} & \cellcolor{gray!6}{literature and fitted} & \cellcolor{gray!6}{data}\\
224 & effectiveness of movement-prevention regulations to reduce the spread of foot-and-mouth disease in the netherlands & yes & stochastic & literature and expert opinion and fitted & none\\
\cellcolor{gray!6}{225} & \cellcolor{gray!6}{effects of internal border control on spread of pandemic influenza} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
\addlinespace
226 & simple models of influenza progression within a heterogeneous population & no & stochastic & expert opinion & none\\
\cellcolor{gray!6}{227} & \cellcolor{gray!6}{stochastic model of an influenza epidemic with drug resistance} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{another model}\\
228 & the effect of public health measures on the 1918 influenza pandemic in u.s. cities & yes & deterministic & literature and expert opinion and fitted & data\\
\cellcolor{gray!6}{229} & \cellcolor{gray!6}{vaccinating in disease-free regions: a vaccine model with application to yellow fever} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
230 & a 'small-world-like' model for comparing interventions aimed at preventing and controlling influenza pandemics & yes & stochastic & literature and expert opinion & data\\
\addlinespace
\cellcolor{gray!6}{231} & \cellcolor{gray!6}{containing pandemic influenza with antiviral agents: analytical commentary} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{another model}\\
232 & critical response to post-outbreak vaccination against foot-and-mouth disease & yes & deterministic & fitted & data\\
\cellcolor{gray!6}{233} & \cellcolor{gray!6}{mitigation strategies for pandemic influenza in the united states} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
234 & simple models for containment of a pandemic & no & deterministic & literature & none\\
\cellcolor{gray!6}{235} & \cellcolor{gray!6}{statistical inference in a stochastic epidemic seir model with control intervention: ebola as a case study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{data}\\
\addlinespace
236 & strategies for containing an emerging influenza pandemic in southeast asia & yes & stochastic & literature and expert opinion and fitted & none\\
\cellcolor{gray!6}{237} & \cellcolor{gray!6}{modeling alternative mitigation strategies for a hypothetical outbreak of foot-and-mouth disease in the united states} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
238 & modelling vaccination strategies against foot-and-mouth disease & yes & stochastic & fitted & data\\
\cellcolor{gray!6}{239} & \cellcolor{gray!6}{a decision-tree to optimise control measures during the early stage of a foot-and-mouth disease epidemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{expert opinion} & \cellcolor{gray!6}{none}\\
240 & effect of control measures on the course of simulated foot and mouth disease epidemics that started on different farm types in various dutch areas & yes & stochastic & expert opinion & none\\
\addlinespace
\cellcolor{gray!6}{241} & \cellcolor{gray!6}{dynamics of the 2001 uk foot and mouth epidemic: stochastic dispersal in a heterogeneous landscape} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{fitted} & \cellcolor{gray!6}{data}\\
242 & an extended state-transition model for foot-and-mouth disease epidemics in france & no & deterministic & literature and expert opinion & none\\
\cellcolor{gray!6}{243} & \cellcolor{gray!6}{simulated economic consequences of foot-and-mouth disease epidemics and their public control in france} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
244 & effect of chemotherapy on malaria transmission among yanomami amerindians: simulated consequences of placebo treatment & no & deterministic & literature and expert opinion and fitted & data\\
\cellcolor{gray!6}{245} & \cellcolor{gray!6}{modelling vaccination strategy against directly transmitted diseases using a series of pulses} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
\addlinespace
246 & mass vaccination to control chickenpox: the influence of zoster & no & deterministic & literature and fitted & data\\
\cellcolor{gray!6}{247} & \cellcolor{gray!6}{an evaluation of alternate control strategies for foot-and-mouth disease in australia: a regional approach} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{literature} & \cellcolor{gray!6}{none}\\
248 & analysis of a measles epidemic & no & both & literature and expert opinion and fitted & data\\
\cellcolor{gray!6}{249} & \cellcolor{gray!6}{a model of the transmission of dengue fever with an evaluation of the impact of ultra-low volume (ulv) insecticide applications on dengue epidemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{deterministic} & \cellcolor{gray!6}{literature and expert opinion} & \cellcolor{gray!6}{none}\\
250 & a discrete-time model with vaccination for a measles epidemic & no & deterministic & literature and fitted & data\\
\addlinespace
\cellcolor{gray!6}{251} & \cellcolor{gray!6}{a stochastic model of epidemics in military recruits} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{stochastic} & \cellcolor{gray!6}{expert opinion} & \cellcolor{gray!6}{none}\\
252 & stochastic two-agent epidemic simulation models for a community of families & no & stochastic & expert opinion & none\\*
\end{longtable}
\endgroup{}
\end{landscape}

\hypertarget{table-4}{%
\subsection{Table 4}\label{table-4}}

This section presents extracted data on the type of outbreak and the
interventions studied.

\begin{landscape}\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}{l>{\raggedright\arraybackslash}p{3cm}l>{\raggedright\arraybackslash}p{8cm}}
\toprule
num & title & outbreak\_type & interventions\\
\midrule
\endfirsthead
\multicolumn{4}{@{}l}{\textit{(continued)}}\\
\toprule
num & title & outbreak\_type & interventions\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{a cholera metapopulation model interlinking migration with intervention strategies - a case study of zimbabwe (2008-2009)} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
2 & a theoretical single-parameter model for urbanisation to study infectious disease spread and interventions & hypothetical outbreak & travel restriction,vaccination\\
\cellcolor{gray!6}{3} & \cellcolor{gray!6}{assessing the effects of modeling the spectrum of clinical symptoms on the dynamics and control of ebola} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{contact tracing,ppe other 1,quarantine,safe burial,distancing,social mobilisation}\\
4 & dynamical analysis and control strategies in modelling ebola virus disease & hypothetical outbreak & education\\
\cellcolor{gray!6}{5} & \cellcolor{gray!6}{effect of a hepatitis a vaccination campaign during a hepatitis a outbreak in taiwan, 2015–2017: a modeling study} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
\addlinespace
6 & evaluating strategies for control of tuberculosis in prisons and prevention of spillover into communities: an observational and modeling study from brazil & real outbreak & prison: entry screening,exit screening,secondary ipt,passive diagnosis active diagnosis and combined above\\
\cellcolor{gray!6}{7} & \cellcolor{gray!6}{evaluating the effects of control interventions and estimating the inapparent infections for dengue outbreak in hangzhou, china} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{larvicides}\\
8 & incidence dynamics and investigation of key interventions in a dengue outbreak in ningbo city, china & real outbreak & isolation,adult vector control,larva control\\
\cellcolor{gray!6}{9} & \cellcolor{gray!6}{incorporating media data into a model of infectious disease transmission} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{media campaign}\\
10 & influence of asymptomatic infections for the effectiveness of facemasks during pandemic influenza & hypothetical outbreak & face masks\\
\addlinespace
\cellcolor{gray!6}{11} & \cellcolor{gray!6}{mathematical analysis of a cholera infection model with vaccination strategy} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
12 & modeling and stability analysis of epidemic expansion disease ebola virus with implications prevention in population & hypothetical outbreak & vaccination\\
\cellcolor{gray!6}{13} & \cellcolor{gray!6}{modeling the effectiveness of respiratory protective devices in reducing influenza outbreak} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{face masks,respiratory protective devices}\\
14 & modeling the effects of vaccination and treatment on tuberculosis transmission dynamics & real outbreak & treatment,vaccination\\
\cellcolor{gray!6}{15} & \cellcolor{gray!6}{optimal control and cost-effective analysis of the 2017 meningitis outbreak in nigeria} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{PPE other 1,vaccination}\\
\addlinespace
16 & optimal control strategies for a two-group epidemic model with vaccination-resource constraints & hypothetical outbreak & vaccination\\
\cellcolor{gray!6}{17} & \cellcolor{gray!6}{optimal media reporting intensity on mitigating spread of an emerging infectious disease} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{media campaign}\\
18 & school dismissal as a pandemic influenza response: when, where and for how long? & real outbreak & school closure\\
\cellcolor{gray!6}{19} & \cellcolor{gray!6}{study on modeling simulation and optimal control method for the transmission risk of the ebola virus} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{isolation,quarantine,treatment}\\
20 & transmission dynamics of cholera with hyperinfectious and hypoinfectious vibrios: mathematical modelling and control strategies & real outbreak & hygiene,quarantine,treatment,vaccination\\
\addlinespace
\cellcolor{gray!6}{21} & \cellcolor{gray!6}{a new epidemics–logistics model: insights into controlling the ebola virus disease in west africa} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{ebola treatment units}\\
22 & contact reductions from live poultry market closures limit the epidemic of human infections with h7n9 influenza & real outbreak & close live poultry market\\
\cellcolor{gray!6}{23} & \cellcolor{gray!6}{disparities in spread and control of influenza in slums of delhi: findings from an agent-based modelling study} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{isolation,school closure,vaccination,stay home}\\
24 & efficacy of control measures in the control of ebola, liberia 2014–2015 & real outbreak & education,isolation,quarantine,safe burial,distancing\\
\cellcolor{gray!6}{25} & \cellcolor{gray!6}{epidemiology of the silent polio outbreak in rahat, israel, based on modeling of environmental surveillance data} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
\addlinespace
26 & evaluating costs and health consequences of sick leave strategies against pandemic and seasonal influenza in norway using a dynamic model & hypothetical outbreak & sick leave strategy\\
\cellcolor{gray!6}{27} & \cellcolor{gray!6}{evaluating vaccination strategies to control foot-and-mouth disease: a country comparison study} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination,stomping out}\\
28 & impact of public health responses during a measles outbreak in an amish community in ohio: modeling the dynamics of transmission & real outbreak & vaccination\\
\cellcolor{gray!6}{29} & \cellcolor{gray!6}{initial validation of a simulation model for estimating the impact of serogroup a neisseria meningitidis vaccination in the african meningitis belt} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
30 & logistical constraints lead to an intermediate optimum in outbreak response vaccination & hypothetical outbreak & vaccination\\
\addlinespace
\cellcolor{gray!6}{31} & \cellcolor{gray!6}{manipulation of contact network structure and the impact on foot-and-mouth disease transmission} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{rewiring}\\
32 & mathematical model and intervention strategies for mitigating tuberculosis in the philippines & real outbreak & distancing from infectious individuals,latent case finding,case holding,active case finding\\
\cellcolor{gray!6}{33} & \cellcolor{gray!6}{measles outbreak response decision-making under uncertainty: a retrospective analysis} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
34 & modeling the heterogeneity of dengue transmission in a city & real outbreak & vaccination,vector control\\
\cellcolor{gray!6}{35} & \cellcolor{gray!6}{modelling the large-scale yellow fever outbreak in luanda, angola, and the impact of vaccination} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
\addlinespace
36 & quantifying the impact of early-stage contact tracing on controlling ebola diffusion & real outbreak & contact tracing,hospitalization\\
\cellcolor{gray!6}{37} & \cellcolor{gray!6}{simulation of key interventions for seasonal influenza outbreak control at school in changsha, china} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{antiviral prophylaxis,isolation,school closure,vaccination,antiviral treatment}\\
38 & the impact of regular school closure on seasonal influenza epidemics: a data-driven spatial transmission model for belgium & real outbreak & school closure\\
\cellcolor{gray!6}{39} & \cellcolor{gray!6}{the potential impact of case-area targeted interventions in response to cholera outbreaks: a modeling study} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination,antibiotic prophylaxis,point-of-use water treatment}\\
40 & value of inventory information in allocating a limited supply of influenza vaccine during a pandemic & hypothetical outbreak & vaccination\\
\addlinespace
\cellcolor{gray!6}{41} & \cellcolor{gray!6}{an age-structured model for cholera control with vaccination} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
42 & an approach to and web-based tool for infectious disease outbreak intervention analysis & hypothetical outbreak & unclear\\
\cellcolor{gray!6}{43} & \cellcolor{gray!6}{an economic assessment of foot and mouth disease in japan} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{culling,vaccination,early detection}\\
44 & analysis of an seriv epidemic model of human influenza & real outbreak & media campaign,vaccination\\
\cellcolor{gray!6}{45} & \cellcolor{gray!6}{control strategies of avian influenza pandemic model with time delay} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{disease control}\\
\addlinespace
46 & costs and benefits of including inactivated in addition to oral poliovirus vaccine in outbreak response after cessation of oral poliovirus vaccine use & hypothetical outbreak & vaccination\\
\cellcolor{gray!6}{47} & \cellcolor{gray!6}{deriving effective vaccine allocation strategies for pandemic influenza: comparison of an agent-based simulation and a compartmental model} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
48 & early rigorous control interventions can largely reduce dengue outbreak magnitude: experience from chaozhou, china & real outbreak & reducing mosquito density\\
\cellcolor{gray!6}{49} & \cellcolor{gray!6}{effects of reactive social distancing on the 1918 influenza pandemic} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{behavioural change}\\
50 & epidemiological and economic impact of pandemic influenza in chicago: priorities for vaccine interventions & hypothetical outbreak & vaccination\\
\addlinespace
\cellcolor{gray!6}{51} & \cellcolor{gray!6}{estimating direct and indirect protective effect of influenza vaccination in the united states} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
52 & evaluating the effects of common control measures for influenza a (h1n1) outbreak at school in china: a modeling study & real outbreak & antiviral prophylaxis,isolation,school closure,vaccination,therapeutics\\
\cellcolor{gray!6}{53} & \cellcolor{gray!6}{evaluation of strategies to control a potential outbreak of foot-and-mouth disease in sweden} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{culling,vaccination,movement restriction,national standstill,protection zones,surveillance zones}\\
54 & impact of a waning vaccine and altered behavior on the spread of influenza & hypothetical outbreak & behavioural change,vaccination\\
\cellcolor{gray!6}{55} & \cellcolor{gray!6}{mathematical models for devising the optimal ebola virus disease eradication} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{isolation,treatment,vaccination}\\
\addlinespace
56 & modeling the role of public health education in ebola virus disease outbreaks in sudan & hypothetical outbreak & education\\
\cellcolor{gray!6}{57} & \cellcolor{gray!6}{modelling the transmission and control strategies of varicella among school children in shenzhen, china} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
58 & optimal and adaptive control of an epidemic model of influenza with unknown parameters & hypothetical outbreak & vaccination\\
\cellcolor{gray!6}{59} & \cellcolor{gray!6}{simulating endogenous dynamics of intervention-capacity deployment: ebola outbreak in liberia} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{isolation,quarantine,safe burial,treatment,vaccination}\\
60 & simulating the potential role of media coverage and infected bats in the 2014 ebola outbreak & real outbreak & media campaign,capturing infected bats\\
\addlinespace
\cellcolor{gray!6}{61} & \cellcolor{gray!6}{a mathematical model of ebola virus disease: using sensitivity analysis to determine effective intervention targets} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{isolation,quarantine,safe burial}\\
62 & a multi-agent model for adaptive vaccination during infectious disease outbreaks & real outbreak & vaccination\\
\cellcolor{gray!6}{63} & \cellcolor{gray!6}{assessing the efficiency of movement restriction as a control strategy of ebola} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{travel restriction}\\
64 & characterization of outbreak response strategies and potential vaccine stockpile needs for the polio endgame & hypothetical outbreak & vaccination\\
\cellcolor{gray!6}{65} & \cellcolor{gray!6}{designing public health policies to mitigate the adverse consequences of rural-urban migration via meta-population modeling} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
\addlinespace
66 & dynamic model of influenza with age-structured and media coverage & hypothetical outbreak & media campaign\\
\cellcolor{gray!6}{67} & \cellcolor{gray!6}{economic evaluation of individual school closure strategies: the hong kong 2009 h1n1 pandemic} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{school closure}\\
68 & efficient vaccine distribution based on a hybrid compartmental model & real outbreak & vaccination\\
\cellcolor{gray!6}{69} & \cellcolor{gray!6}{epidemiological evaluation of different fmd control strategies in two selected regions in austria} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{culling,vaccination,ring culling,and combinations of above}\\
70 & evaluating targeted interventions via meta-population models with multi-level mixing & real outbreak & vaccination\\
\addlinespace
\cellcolor{gray!6}{71} & \cellcolor{gray!6}{evaluation of outbreak response immunization in the control of pertussis using agent-based modeling} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
72 & global stability and optimal control for a tuberculosis model with vaccination and treatment & hypothetical outbreak & treatment,vaccination\\
\cellcolor{gray!6}{73} & \cellcolor{gray!6}{impact on epidemic measles of vaccination campaigns triggered by disease outbreaks or serosurveys: a modeling study} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
74 & metapopulation and non-proportional vaccination models overview & hypothetical outbreak & distancing,school closure,vaccination\\
\cellcolor{gray!6}{75} & \cellcolor{gray!6}{model-based comprehensive analysis of school closure policies for mitigating influenza epidemics and pandemics} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{school closure}\\
\addlinespace
76 & modeling ring-vaccination strategies to control ebola virus disease epidemics & real outbreak & vaccination\\
\cellcolor{gray!6}{77} & \cellcolor{gray!6}{modeling the effect of public health resources and alerting on the dynamics of pertussis spread*} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{contact tracing,vaccination}\\
78 & modeling the impact of behavior change on the spread of ebola & real outbreak & behavioural change\\
\cellcolor{gray!6}{79} & \cellcolor{gray!6}{modeling the spread of polio in an ipv-vaccinated population: lessons learned from the 2013 silent outbreak in southern israel} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
80 & modelling weekly vector control against dengue in the guangdong province of china & hypothetical outbreak & larvicides\\
\addlinespace
\cellcolor{gray!6}{81} & \cellcolor{gray!6}{optimal control strategies for the spread of ebola in west africa} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{education,treatment,control the propagation,reduce the number of susceptible and infected and simultaneously increase recovered}\\
82 & potential impact of a ventilation intervention for influenza in the context of a dense indoor contact network in hong kong & hypothetical outbreak & face masks,isolation,school closure,vaccination,ventilation\\
\cellcolor{gray!6}{83} & \cellcolor{gray!6}{predicting and evaluating the epidemic trend of ebola virus disease in the 2014-2015 outbreak and the effects of intervention measures} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{isolation,safe burial,vaccination,protected sex with condoms,early detection and diagnosis,preventing importation}\\
84 & projected impact of dengue vaccination in yucatán, mexico & hypothetical outbreak & vaccination\\
\cellcolor{gray!6}{85} & \cellcolor{gray!6}{seasonality and the effectiveness of mass vaccination} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
\addlinespace
86 & simulation optimization for an age-based vaccines distribution strategy against the spread of influenza epidemic & hypothetical outbreak & vaccination\\
\cellcolor{gray!6}{87} & \cellcolor{gray!6}{spatiotemporal dynamics of the ebola epidemic in guinea and implications for vaccination and disease elimination: a computational modeling analysis} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{contact tracing,safe burial,vaccination,ebola treatment units}\\
88 & the interplay of vaccination and vector control on small dengue networks & hypothetical outbreak & vaccination,sterile insect technique\\
\cellcolor{gray!6}{89} & \cellcolor{gray!6}{an epidemic patchy model with entry–exit screening} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{screening}\\
90 & assessing the role of voluntary self-isolation in the control of pandemic influenza using a household epidemic model & hypothetical outbreak & antiviral prophylaxis,isolation\\
\addlinespace
\cellcolor{gray!6}{91} & \cellcolor{gray!6}{be-codis: a mathematical model to predict the risk of human diseases spread between countries—validation and application to the 2014–2015 ebola virus disease epidemic} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{hygiene,isolation,hospitalization}\\
92 & dengue in madeira island & hypothetical outbreak & education,larvicides\\
\cellcolor{gray!6}{93} & \cellcolor{gray!6}{dynamic simulation of a seiqr-v epidemic model based on cellular automata} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{quarantine,vaccination}\\
94 & early vaccine availability represents an important public health advance for the control of pandemic influenza & hypothetical outbreak & vaccination\\
\cellcolor{gray!6}{95} & \cellcolor{gray!6}{effectiveness of ebola treatment units and community care centers — liberia, september 23–october 31, 2014} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{ebola treatment units,community care centers}\\
\addlinespace
96 & evaluation of the benefts and risks of introducing ebola community care centers, sierra leone & hypothetical outbreak & beds,ebola treatment units,community care centers\\
\cellcolor{gray!6}{97} & \cellcolor{gray!6}{evidence for emergency vaccination having played a crucial role to control the 1965/66 foot-and-mouth disease outbreak in switzerland} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{contact tracing,culling,travel restriction,vaccination,surveillance}\\
98 & measuring the impact of ebola control measures in sierra leone & real outbreak & beds\\
\cellcolor{gray!6}{99} & \cellcolor{gray!6}{media impact switching surface during an infectious disease outbreak} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{media campaign}\\
100 & modeling options to manage type 1 wild poliovirus imported into israel in 2013 & real outbreak & vaccination\\
\addlinespace
\cellcolor{gray!6}{101} & \cellcolor{gray!6}{modeling the effect of comprehensive interventions on ebola virus transmission} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{isolation,media campaign,safe burial,vaccination}\\
102 & modeling the effect of school closures in a pandemic scenario: exploring two different contact matrices & hypothetical outbreak & school closure\\
\cellcolor{gray!6}{103} & \cellcolor{gray!6}{modelling the effect of early detection of ebola} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{isolation}\\
104 & multi-scale modeling for the transmission of influenza and the evaluation of interventions toward it & real outbreak & school closure,vaccination\\
\cellcolor{gray!6}{105} & \cellcolor{gray!6}{optimal intervention strategies for a seir control model of ebola epidemics} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{reducing transmission}\\
\addlinespace
106 & predicting the extinction of ebola spreading in liberia due to mitigation strategies & real outbreak & safe burial,effective hospitalization\\
\cellcolor{gray!6}{107} & \cellcolor{gray!6}{school closure strategies for the 2009 hong kong hini influenza pandemic} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{school closure}\\
108 & spatiotemporal spread of the 2014 outbreak of ebola virus disease in liberia and the effectiveness of non-pharmaceutical interventions: a computational modelling analysis & real outbreak & beds,PPE other 1,safe burial\\
\cellcolor{gray!6}{109} & \cellcolor{gray!6}{strategies for early vaccination during novel influenza outbreaks} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
110 & the effects of media reports on disease spread and important public health measurements & real outbreak & media campaign,distancing,vaccination\\
\addlinespace
\cellcolor{gray!6}{111} & \cellcolor{gray!6}{the impact of human behavioral changes in 2014 west africa ebola outbreak} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{behavioural change}\\
112 & transmission dynamics and final epidemic size of ebola virus disease outbreaks with varying interventions & real outbreak & several interventions to reduce transmission\\
\cellcolor{gray!6}{113} & \cellcolor{gray!6}{treatment–donation-stockpile dynamics in ebola convalescent blood transfusion therapy} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{treatment}\\
114 & vaccine prioritization for effective pandemic response & hypothetical outbreak & vaccination\\
\cellcolor{gray!6}{115} & \cellcolor{gray!6}{a mathematical study of a tb model with treatment interruptions and two latent periods} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{treatment}\\
\addlinespace
116 & antiviral prophylaxis and isolation for the control of pandemic influenza & hypothetical outbreak & antiviral prophylaxis,isolation\\
\cellcolor{gray!6}{117} & \cellcolor{gray!6}{assessing the impact of travel restrictions on international spread of the 2014 west african ebola epidemic} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{travel restriction}\\
118 & assessing the use of antiviral treatment to control influenza & hypothetical outbreak & antiviral prophylaxis,vaccination\\
\cellcolor{gray!6}{119} & \cellcolor{gray!6}{behavior in the time of cholera: evidence from the 2008-2009 cholera outbreak in zimbabwe} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{water treatment}\\
120 & behavioural response in educated young adults towards influenza a(h1n1)pdm09 & hypothetical outbreak & behavioural change\\
\addlinespace
\cellcolor{gray!6}{121} & \cellcolor{gray!6}{cover your cough! quantifying the benefits of a localized healthy behavior intervention on flu epidemics in washington dc} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{behavioural change,vaccination}\\
122 & dynamics and control of ebola virus transmission in montserrado, liberia: a mathematical modelling analysis & real outbreak & contact tracing,beds,household protective kits\\
\cellcolor{gray!6}{123} & \cellcolor{gray!6}{estimating the effectiveness of early control measures through school absenteeism surveillance in observed outbreaks at rural schools in hubei, china} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{school absenteeism surveillance}\\
124 & evaluation of the benefit of emergency vaccination in a foot-and-mouth disease free country with low livestock density & hypothetical outbreak & vaccination\\
\cellcolor{gray!6}{125} & \cellcolor{gray!6}{modeling the dynamics of oral poliovirus vaccine cessation} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
\addlinespace
126 & modeling the impact of optimal screening on typhoid dynamics & hypothetical outbreak & screening\\
\cellcolor{gray!6}{127} & \cellcolor{gray!6}{modeling the influence of environment and intervention oncholera in haiti} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
128 & sequential bayesian inference in hidden markov stochastic kinetic models with application to detection and response to seasonal epidemics & hypothetical outbreak & direct measures to reduce infectiousness,e.g.,quarantine,prophylactic measures to mitigate outbreak seasonality and morbidity\\
\cellcolor{gray!6}{129} & \cellcolor{gray!6}{simulating optimal vaccination times during cholera outbreaks} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
130 & the role of vaccination coverage, individual behaviors, and the public health response in the control of measles epidemics: an agent-based simulation for california & hypothetical outbreak & behavioural change,contact tracing,vaccination\\
\addlinespace
\cellcolor{gray!6}{131} & \cellcolor{gray!6}{time is (still) of the essence: quantifying the impact of emergency meningitis vaccination response in katsina state, nigeria} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
132 & a perspective on multiple waves of influenza pandemics & real outbreak & travel restriction,vaccination\\
\cellcolor{gray!6}{133} & \cellcolor{gray!6}{an optimal control problem arising from a dengue disease transmission model} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{treatment,mosquito repellent}\\
134 & cholera in haiti: reproductive numbers and vaccination coverage estimates & real outbreak & vaccination\\
\cellcolor{gray!6}{135} & \cellcolor{gray!6}{comparing control strategies against foot-and-mouth disease: will vaccination be cost-effective in denmark?} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination,depopulation of detected herds,protection,surveillance zones,movement tracing,national standstill}\\
\addlinespace
136 & cost-effectiveness of influenza control measures: a dynamic transmission model-based analysis & real outbreak & face masks,handwashing,isolation,vaccination,ventilation,high efficiency particulate air filtration,ultraviolet germicidal irradiation\\
\cellcolor{gray!6}{137} & \cellcolor{gray!6}{cost-effectiveness of workplace closure and travel restriction for mitigating influenza outbreaks: a network-based simulation} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{antiviral prophylaxis,distancing,school closure,travel restriction}\\
138 & decisions on control of foot-and-mouth disease informed using model predictions & hypothetical outbreak & vaccination\\
\cellcolor{gray!6}{139} & \cellcolor{gray!6}{dengue in cape verde: vector control and vaccination} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{larvicides,vaccination}\\
140 & enhancement of collective immunity in tokyo metropolitan area by selective vaccination against an emerging influenza pandemic & hypothetical outbreak & vaccination\\
\addlinespace
\cellcolor{gray!6}{141} & \cellcolor{gray!6}{estimated impact of aggressive empirical antiviral treatment in containing an outbreak of pandemic influenza h1n1 in an isolated first nations community} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{antiviral prophylaxis,distancing}\\
142 & multiregional dynamic vaccine allocation during an influenza epidemic & real outbreak & vaccination\\
\cellcolor{gray!6}{143} & \cellcolor{gray!6}{policies to reduce influenza in the workplace: impact assessments using an agent-based model} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{paid sick days,stay-at-home behaviour}\\
144 & transmission dynamics of the 2009 influenza a (h1n1) pandemic in india: the impact of holiday-related school closure & real outbreak & school closure\\
\cellcolor{gray!6}{145} & \cellcolor{gray!6}{vaccination against foot-and-mouth disease: do initial conditions affect its benefit?} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
\addlinespace
146 & was mandatory quarantine necessary in china for controlling the 2009 h1n1 pandemic? & real outbreak & quarantine\\
\cellcolor{gray!6}{147} & \cellcolor{gray!6}{a contact-network-based simulation model for evaluating interventions under 'what-if' scenarios in epidemic} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{school closure}\\
148 & campus quarantine (fengxiao) for curbing emergent infectious diseases: lessons from mitigating a/h1n1 in xi'an, china & real outbreak & school closure\\
\cellcolor{gray!6}{149} & \cellcolor{gray!6}{dynamic modelling of costs and health consequences of school closure during an influenza pandemic} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{school closure}\\
150 & effect of vaccines and antivirals during the major 2009 a(h1n1) pandemic wave in norway - and the influence of vaccination timing & real outbreak & antiviral prophylaxis,vaccination\\
\addlinespace
\cellcolor{gray!6}{151} & \cellcolor{gray!6}{estimating the value of containment strategies in delaying the arrival time of an influenza pandemic: a case study of travel restriction and patient isolation} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{isolation,travel restriction}\\
152 & how to minimize the attack rate during multiple influenza outbreaks in a heterogeneous population & hypothetical outbreak & unclear\\
\cellcolor{gray!6}{153} & \cellcolor{gray!6}{modeling strategies for controlling h1n1 outbreaks in china} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{isolation,quarantine}\\
154 & modeling the effects of h1n1 influenza vaccine distribution in the united states & real outbreak & vaccination\\
\cellcolor{gray!6}{155} & \cellcolor{gray!6}{modeling the impact of air, sea, and land travel restrictions supplemented by other interventions on the emergence of a new influenza pandemic virus} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{travel restriction,hospitalization,antiviral treatment}\\
\addlinespace
156 & simulating school closure policies for cost effective pandemic decision making & hypothetical outbreak & school closure\\
\cellcolor{gray!6}{157} & \cellcolor{gray!6}{the impact of school closures on pandemic influenza: assessing potential repercussions using a seasonal sir model} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{school closure}\\
158 & vaccination against foot-and-mouth disease i: epidemiological consequences & hypothetical outbreak & culling,vaccination\\
\cellcolor{gray!6}{159} & \cellcolor{gray!6}{a deterministic resource scheduling model in epidemic control: a case study} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
160 & a model for the a(h1n1) epidemic in mexico, including social isolation & real outbreak & isolation\\
\addlinespace
\cellcolor{gray!6}{161} & \cellcolor{gray!6}{a model to evaluate mass vaccination against pneumococcus as a countermeasure against pandemic influenza} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
162 & a multilayer framework to assess influenza intervention policies & real outbreak & treatment,hospitalization\\
\cellcolor{gray!6}{163} & \cellcolor{gray!6}{a note on the use of optimal control on a discrete time model of influenza dynamics} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{distancing,antiviral treatment}\\
164 & a simulation-based assessment of school closure strategies during an influenza epidemic & hypothetical outbreak & school closure\\
\cellcolor{gray!6}{165} & \cellcolor{gray!6}{agent-based modeling of the spread of influenza-like illness in an emergency department: a simulation study} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{face masks,pallative care,treatment}\\
\addlinespace
166 & antiviral treatment for pandemic influenza: assessing potential repercussions using a seasonally forced sir model & hypothetical outbreak & treatment\\
\cellcolor{gray!6}{167} & \cellcolor{gray!6}{can antiviral drugs contain pandemic influenza transmission?} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{antiviral prophylaxis}\\
168 & characterizing the epidemiology of the 2009 influenza a/h1n1 pandemic in mexico & real outbreak & distancing,school closure\\
\cellcolor{gray!6}{169} & \cellcolor{gray!6}{cholera epidemic in haiti, 2010: using a transmission model to explain spatial spread of disease and identify optimal control interventions} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{hygiene,vaccination}\\
170 & controlling an influenza outbreak in deterministic and stochastic models with the emergence and evolution of drug resistance (model 1) & hypothetical outbreak & antiviral prophylaxis,treatment\\
\addlinespace
\cellcolor{gray!6}{171} & \cellcolor{gray!6}{modeling control strategies for concurrent epidemics of seasonal and pandemic h1n1 influenza} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{distancing,treatment}\\
172 & modeling the impact of behavior changes on the spread of pandemic influenza & hypothetical outbreak & isolation,school closure,vaccination\\
\cellcolor{gray!6}{173} & \cellcolor{gray!6}{modelling and analysis of influenza a (h1n1) on networks} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
174 & modelling the strategies for age specific vaccination scheduling during influenza pandemic outbreaks & real outbreak & vaccination\\
\cellcolor{gray!6}{175} & \cellcolor{gray!6}{modelling the transmission dynamics and control of the novel 2009 swine influenza (h1n1) pandemic} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
\addlinespace
176 & planning for the control of pandemic influenza a (h1n1) in los angeles county and the united states & real outbreak & vaccination\\
\cellcolor{gray!6}{177} & \cellcolor{gray!6}{prioritization of delayed vaccination for pandemic influenza} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
178 & temporal factors in school closure policy for mitigating the spread of influenza & hypothetical outbreak & school closure\\
\cellcolor{gray!6}{179} & \cellcolor{gray!6}{the global transmission and control of influenza} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
180 & toward effective vaccine deployment: a systematic study & hypothetical outbreak & vaccination\\
\addlinespace
\cellcolor{gray!6}{181} & \cellcolor{gray!6}{vaccination against 2009 pandemic h1n1 in a population dynamical model of vancouver, canada: timing is everything} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
182 & a simulation model for the potential spread of foot-and-mouth disease in the castile and leon region of spain & hypothetical outbreak & vaccination,preventive depopulation\\
\cellcolor{gray!6}{183} & \cellcolor{gray!6}{community-based measures for mitigating the 2009 h1n1 pandemic in china} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{quarantine,school closure,hygiene precaution}\\
184 & effective real-time allocation of pandemic interventions & hypothetical outbreak & vaccination\\
\cellcolor{gray!6}{185} & \cellcolor{gray!6}{efficient mitigation strategies for epidemics in rural regions} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
\addlinespace
186 & influenza pandemic waves under various mitigation strategies with 2009 h1n1 as a case study & hypothetical outbreak & school closure,vaccination,antiviral treatment\\
\cellcolor{gray!6}{187} & \cellcolor{gray!6}{is a mass immunization program for pandemic (h1n1) 2009 good value for money? early evidence from the canadian experience} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{mass immunization program}\\
188 & optimal control for pandemic influenza: the role of limited antiviral treatment and isolation & hypothetical outbreak & isolation,antiviral treatment\\
\cellcolor{gray!6}{189} & \cellcolor{gray!6}{optimizing vaccine allocation at different points in time during an epidemic} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
190 & simulating school closure strategies to mitigate an influenza epidemic & real outbreak & school closure\\
\addlinespace
\cellcolor{gray!6}{191} & \cellcolor{gray!6}{the effect of mask use on the spread of influenza during a pandemic} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{face masks}\\
192 & transmission dynamics of an influenza model with age of infection and antiviral treatment & hypothetical outbreak & antiviral prophylaxis\\
\cellcolor{gray!6}{193} & \cellcolor{gray!6}{transmission risks and control of foot-and-mouth disease in the netherlands: spatial patterns} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{culling}\\
194 & when should we intervene to control the 2009 influenza a(h1n1) pandemic? & real outbreak & isolation,onboard quarantine inspection\\
\cellcolor{gray!6}{195} & \cellcolor{gray!6}{adaptive vaccination strategies to mitigate pandemic influenza} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
\addlinespace
196 & antiviral resistance and the control of pandemic influenza: the roles of stochasticity, evolution and model details & hypothetical outbreak & antiviral prophylaxis\\
\cellcolor{gray!6}{197} & \cellcolor{gray!6}{economic evaluation of influenza pandemic mitigation strategies in the united states using a stochastic microsimulation transmission model} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{antiviral prophylaxis,distancing,vaccination}\\
198 & effectiveness and cost-effectiveness of expanded antiviral prophylaxis and adjuvanted vaccination strategies for an influenza a (h5n1) pandemic & hypothetical outbreak & antiviral prophylaxis,vaccination\\
\cellcolor{gray!6}{199} & \cellcolor{gray!6}{engineering responses to pandemics} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{behavioural change,travel restriction}\\
200 & epidemiological benefits of more-effective tuberculosis vaccines, drugs, and diagnostics & real outbreak & treatment,vaccination,diagnostics\\
\addlinespace
\cellcolor{gray!6}{201} & \cellcolor{gray!6}{household epidemics: modelling effects of early stage vaccination} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
202 & measures against transmission of pandemic h1n1 influenza in japan in 2009: simulation model & hypothetical outbreak & antiviral prophylaxis,isolation,school closure,vaccination\\
\cellcolor{gray!6}{203} & \cellcolor{gray!6}{modeling vaccination campaigns and the fall/winter 2009 activity of the new a(h1n1) influenza in the northern hemisphere} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{antiviral prophylaxis,vaccination}\\
204 & modelling foot and mouth disease & hypothetical outbreak & culling,vaccination,movement restriction,surveillance\\
\cellcolor{gray!6}{205} & \cellcolor{gray!6}{modelling of the influenza a(h1n1)v outbreak in mexico city, april-may 2009, with control sanitary measures} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{handwashing,sanitary measures}\\
\addlinespace
206 & post-exposure prophylaxis during pandemic outbreaks & real outbreak & treatment,post-exposure prophylaxis\\
\cellcolor{gray!6}{207} & \cellcolor{gray!6}{potential for a global dynamic of influenza a (h1n1)} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
208 & reducing the impact of the next influenza pandemic using householdbased public health interventions & hypothetical outbreak & contact tracing,isolation,quarantine\\
\cellcolor{gray!6}{209} & \cellcolor{gray!6}{seasonal transmission potential and activity peaks of the new influenza a(h1n1): a monte carlo likelihood analysis based on human mobility} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{treatment}\\
210 & simulation of foot-and-mouth disease spread within an integrated livestock system in texas, usa & hypothetical outbreak & early detection\\
\addlinespace
\cellcolor{gray!6}{211} & \cellcolor{gray!6}{the transmissibility and control of pandemic influenza a (h1n1) virus} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{vaccination}\\
212 & bayesian analysis of severe acute respiratory syndrome: the 2003 hong kong epidemic & real outbreak & treatment\\
\cellcolor{gray!6}{213} & \cellcolor{gray!6}{hepatitis b vaccination and changes in sexual risk behaviour among men who have sex with men in amsterdam} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
214 & mathematical assessment of canada's pandemic influenza preparedness plan & hypothetical outbreak & antiviral prophylaxis,face masks,hygiene,school closure,vaccination,work closure,antiviral treatment\\
\cellcolor{gray!6}{215} & \cellcolor{gray!6}{modeling targeted layered containment of an influenza pandemic in the united states} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{antiviral prophylaxis,quarantine,distancing,school closure,screening,work closure}\\
\addlinespace
216 & optimal allocation of pandemic influenza vaccine depends on age, risk and timing & real outbreak & vaccination\\
\cellcolor{gray!6}{217} & \cellcolor{gray!6}{pandemic simulation of antivirals plus school closures: buying time until strain-specific vaccine is available} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{antiviral prophylaxis,school closure,vaccination}\\
218 & preparedness for the spread of influenza: prohibition of traffic, school closure, and vaccination of children in the commuter towns of tokyo & real outbreak & school closure,vaccination,prohibition of traffic\\
\cellcolor{gray!6}{219} & \cellcolor{gray!6}{scenarios of diffusion and control of an influenza pandemic in italy} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{antiviral prophylaxis,distancing,school closure,vaccination,work closure,closure of public places}\\
220 & time is of the essence: exploring a measles outbreak response vaccination in niamey, niger & real outbreak & vaccination\\
\addlinespace
\cellcolor{gray!6}{221} & \cellcolor{gray!6}{a stochastic equation-based model of the value of international air-travel restrictions for controlling pandemic flu} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{travel restriction}\\
222 & assessing the role of basic control measures, antivirals and vaccine in curtailing pandemic influenza: scenarios for the us, uk and the netherlands & hypothetical outbreak & antiviral prophylaxis,treatment,vaccination,reduction of hospital transmission,reduction of community transmission\\
\cellcolor{gray!6}{223} & \cellcolor{gray!6}{deterministic sir (susceptible infected removed) models applied to varicella outbreaks} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{isolation,vaccination}\\
224 & effectiveness of movement-prevention regulations to reduce the spread of foot-and-mouth disease in the netherlands & real outbreak & culling,vaccination,surveillance,preventive slaughter of dangerous contacts,movement restriction\\
\cellcolor{gray!6}{225} & \cellcolor{gray!6}{effects of internal border control on spread of pandemic influenza} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{travel restriction}\\
\addlinespace
226 & simple models of influenza progression within a heterogeneous population & hypothetical outbreak & distancing\\
\cellcolor{gray!6}{227} & \cellcolor{gray!6}{stochastic model of an influenza epidemic with drug resistance} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{treatment}\\
228 & the effect of public health measures on the 1918 influenza pandemic in u.s. cities & real outbreak & face masks,hygiene,isolation,quarantine,distancing,school closure,work closure,prevention of mass gatherings,several combinations of interventions\\
\cellcolor{gray!6}{229} & \cellcolor{gray!6}{vaccinating in disease-free regions: a vaccine model with application to yellow fever} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
230 & a 'small-world-like' model for comparing interventions aimed at preventing and controlling influenza pandemics & hypothetical outbreak & antiviral prophylaxis,school closure,treatment,vaccination,work closure,stay-at-home\\
\addlinespace
\cellcolor{gray!6}{231} & \cellcolor{gray!6}{containing pandemic influenza with antiviral agents: analytical commentary} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{antiviral prophylaxis,vaccination}\\
232 & critical response to post-outbreak vaccination against foot-and-mouth disease & real outbreak & vaccination\\
\cellcolor{gray!6}{233} & \cellcolor{gray!6}{mitigation strategies for pandemic influenza in the united states} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{antiviral prophylaxis,distancing,school closure,travel restriction,vaccination}\\
234 & simple models for containment of a pandemic & hypothetical outbreak & antiviral prophylaxis,vaccination\\
\cellcolor{gray!6}{235} & \cellcolor{gray!6}{statistical inference in a stochastic epidemic seir model with control intervention: ebola as a case study} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{interventions to reduce transmission}\\
\addlinespace
236 & strategies for containing an emerging influenza pandemic in southeast asia & hypothetical outbreak & antiviral prophylaxis,quarantine,distancing,school closure,work closure\\
\cellcolor{gray!6}{237} & \cellcolor{gray!6}{modeling alternative mitigation strategies for a hypothetical outbreak of foot-and-mouth disease in the united states} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{culling,vaccination}\\
238 & modelling vaccination strategies against foot-and-mouth disease & real outbreak & vaccination\\
\cellcolor{gray!6}{239} & \cellcolor{gray!6}{a decision-tree to optimise control measures during the early stage of a foot-and-mouth disease epidemic} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{culling,vaccination,stomping out,movement control}\\
240 & effect of control measures on the course of simulated foot and mouth disease epidemics that started on different farm types in various dutch areas & hypothetical outbreak & culling,vaccination\\
\addlinespace
\cellcolor{gray!6}{241} & \cellcolor{gray!6}{dynamics of the 2001 uk foot and mouth epidemic: stochastic dispersal in a heterogeneous landscape} & \cellcolor{gray!6}{real outbreak} & \cellcolor{gray!6}{culling,vaccination}\\
242 & an extended state-transition model for foot-and-mouth disease epidemics in france & real outbreak & vaccination,stamping-out and slaughter of contact herds\\
\cellcolor{gray!6}{243} & \cellcolor{gray!6}{simulated economic consequences of foot-and-mouth disease epidemics and their public control in france} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{stamping out}\\
244 & effect of chemotherapy on malaria transmission among yanomami amerindians: simulated consequences of placebo treatment & real outbreak & treatment,drugs\\
\cellcolor{gray!6}{245} & \cellcolor{gray!6}{modelling vaccination strategy against directly transmitted diseases using a series of pulses} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination}\\
\addlinespace
246 & mass vaccination to control chickenpox: the influence of zoster & real outbreak & vaccination\\
\cellcolor{gray!6}{247} & \cellcolor{gray!6}{an evaluation of alternate control strategies for foot-and-mouth disease in australia: a regional approach} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{vaccination,stamping out,dangerous contact slaughter}\\
248 & analysis of a measles epidemic & real outbreak & vaccination\\
\cellcolor{gray!6}{249} & \cellcolor{gray!6}{a model of the transmission of dengue fever with an evaluation of the impact of ultra-low volume (ulv) insecticide applications on dengue epidemics} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{ultra-low volume (ulv) insecticide applications}\\
250 & a discrete-time model with vaccination for a measles epidemic & real outbreak & vaccination\\
\addlinespace
\cellcolor{gray!6}{251} & \cellcolor{gray!6}{a stochastic model of epidemics in military recruits} & \cellcolor{gray!6}{hypothetical outbreak} & \cellcolor{gray!6}{isolation,quarantine}\\
252 & stochastic two-agent epidemic simulation models for a community of families & hypothetical outbreak & school closure,vaccination\\*
\end{longtable}
\endgroup{}
\end{landscape}

\hypertarget{table-5}{%
\subsection{Table 5}\label{table-5}}

This section presents extracted data on whether vaccination was modelled
as a sole intervention for comparison against other interventions
(vax\_modelled\_with\_non\_vax) and the studies' conclusion on the
impact of vaccination (is\_vax\_effective).

\begin{landscape}\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}{l>{\raggedright\arraybackslash}p{4cm}l>{\raggedright\arraybackslash}p{4cm}}
\toprule
num & title & vax\_modelled\_with\_non\_vax & is\_vax\_effective\\
\midrule
\endfirsthead
\multicolumn{4}{@{}l}{\textit{(continued)}}\\
\toprule
num & title & vax\_modelled\_with\_non\_vax & is\_vax\_effective\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{a cholera metapopulation model interlinking migration with intervention strategies - a case study of zimbabwe (2008-2009)} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
2 & a theoretical single-parameter model for urbanisation to study infectious disease spread and interventions & no & not applicable\\
\cellcolor{gray!6}{3} & \cellcolor{gray!6}{assessing the effects of modeling the spectrum of clinical symptoms on the dynamics and control of ebola} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
4 & dynamical analysis and control strategies in modelling ebola virus disease & no & not applicable\\
\cellcolor{gray!6}{5} & \cellcolor{gray!6}{effect of a hepatitis a vaccination campaign during a hepatitis a outbreak in taiwan, 2015–2017: a modeling study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
6 & evaluating strategies for control of tuberculosis in prisons and prevention of spillover into communities: an observational and modeling study from brazil & no & not applicable\\
\cellcolor{gray!6}{7} & \cellcolor{gray!6}{evaluating the effects of control interventions and estimating the inapparent infections for dengue outbreak in hangzhou, china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
8 & incidence dynamics and investigation of key interventions in a dengue outbreak in ningbo city, china & no & not applicable\\
\cellcolor{gray!6}{9} & \cellcolor{gray!6}{incorporating media data into a model of infectious disease transmission} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
10 & influence of asymptomatic infections for the effectiveness of facemasks during pandemic influenza & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{11} & \cellcolor{gray!6}{mathematical analysis of a cholera infection model with vaccination strategy} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
12 & modeling and stability analysis of epidemic expansion disease ebola virus with implications prevention in population & no & not applicable\\
\cellcolor{gray!6}{13} & \cellcolor{gray!6}{modeling the effectiveness of respiratory protective devices in reducing influenza outbreak} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
14 & modeling the effects of vaccination and treatment on tuberculosis transmission dynamics & no & not applicable\\
\cellcolor{gray!6}{15} & \cellcolor{gray!6}{optimal control and cost-effective analysis of the 2017 meningitis outbreak in nigeria} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
\addlinespace
16 & optimal control strategies for a two-group epidemic model with vaccination-resource constraints & no & not applicable\\
\cellcolor{gray!6}{17} & \cellcolor{gray!6}{optimal media reporting intensity on mitigating spread of an emerging infectious disease} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
18 & school dismissal as a pandemic influenza response: when, where and for how long? & no & not applicable\\
\cellcolor{gray!6}{19} & \cellcolor{gray!6}{study on modeling simulation and optimal control method for the transmission risk of the ebola virus} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
20 & transmission dynamics of cholera with hyperinfectious and hypoinfectious vibrios: mathematical modelling and control strategies & yes & yes\\
\addlinespace
\cellcolor{gray!6}{21} & \cellcolor{gray!6}{a new epidemics–logistics model: insights into controlling the ebola virus disease in west africa} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
22 & contact reductions from live poultry market closures limit the epidemic of human infections with h7n9 influenza & no & not applicable\\
\cellcolor{gray!6}{23} & \cellcolor{gray!6}{disparities in spread and control of influenza in slums of delhi: findings from an agent-based modelling study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
24 & efficacy of control measures in the control of ebola, liberia 2014–2015 & no & not applicable\\
\cellcolor{gray!6}{25} & \cellcolor{gray!6}{epidemiology of the silent polio outbreak in rahat, israel, based on modeling of environmental surveillance data} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
26 & evaluating costs and health consequences of sick leave strategies against pandemic and seasonal influenza in norway using a dynamic model & no & not applicable\\
\cellcolor{gray!6}{27} & \cellcolor{gray!6}{evaluating vaccination strategies to control foot-and-mouth disease: a country comparison study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
28 & impact of public health responses during a measles outbreak in an amish community in ohio: modeling the dynamics of transmission & no & not applicable\\
\cellcolor{gray!6}{29} & \cellcolor{gray!6}{initial validation of a simulation model for estimating the impact of serogroup a neisseria meningitidis vaccination in the african meningitis belt} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
30 & logistical constraints lead to an intermediate optimum in outbreak response vaccination & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{31} & \cellcolor{gray!6}{manipulation of contact network structure and the impact on foot-and-mouth disease transmission} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
32 & mathematical model and intervention strategies for mitigating tuberculosis in the philippines & no & not applicable\\
\cellcolor{gray!6}{33} & \cellcolor{gray!6}{measles outbreak response decision-making under uncertainty: a retrospective analysis} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
34 & modeling the heterogeneity of dengue transmission in a city & no & not applicable\\
\cellcolor{gray!6}{35} & \cellcolor{gray!6}{modelling the large-scale yellow fever outbreak in luanda, angola, and the impact of vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
36 & quantifying the impact of early-stage contact tracing on controlling ebola diffusion & no & not applicable\\
\cellcolor{gray!6}{37} & \cellcolor{gray!6}{simulation of key interventions for seasonal influenza outbreak control at school in changsha, china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
38 & the impact of regular school closure on seasonal influenza epidemics: a data-driven spatial transmission model for belgium & no & not applicable\\
\cellcolor{gray!6}{39} & \cellcolor{gray!6}{the potential impact of case-area targeted interventions in response to cholera outbreaks: a modeling study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
40 & value of inventory information in allocating a limited supply of influenza vaccine during a pandemic & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{41} & \cellcolor{gray!6}{an age-structured model for cholera control with vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
42 & an approach to and web-based tool for infectious disease outbreak intervention analysis & no & not applicable\\
\cellcolor{gray!6}{43} & \cellcolor{gray!6}{an economic assessment of foot and mouth disease in japan} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
44 & analysis of an seriv epidemic model of human influenza & no & not applicable\\
\cellcolor{gray!6}{45} & \cellcolor{gray!6}{control strategies of avian influenza pandemic model with time delay} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
46 & costs and benefits of including inactivated in addition to oral poliovirus vaccine in outbreak response after cessation of oral poliovirus vaccine use & no & not applicable\\
\cellcolor{gray!6}{47} & \cellcolor{gray!6}{deriving effective vaccine allocation strategies for pandemic influenza: comparison of an agent-based simulation and a compartmental model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
48 & early rigorous control interventions can largely reduce dengue outbreak magnitude: experience from chaozhou, china & no & not applicable\\
\cellcolor{gray!6}{49} & \cellcolor{gray!6}{effects of reactive social distancing on the 1918 influenza pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
50 & epidemiological and economic impact of pandemic influenza in chicago: priorities for vaccine interventions & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{51} & \cellcolor{gray!6}{estimating direct and indirect protective effect of influenza vaccination in the united states} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
52 & evaluating the effects of common control measures for influenza a (h1n1) outbreak at school in china: a modeling study & yes & yes\\
\cellcolor{gray!6}{53} & \cellcolor{gray!6}{evaluation of strategies to control a potential outbreak of foot-and-mouth disease in sweden} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
54 & impact of a waning vaccine and altered behavior on the spread of influenza & yes & yes\\
\cellcolor{gray!6}{55} & \cellcolor{gray!6}{mathematical models for devising the optimal ebola virus disease eradication} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
56 & modeling the role of public health education in ebola virus disease outbreaks in sudan & no & not applicable\\
\cellcolor{gray!6}{57} & \cellcolor{gray!6}{modelling the transmission and control strategies of varicella among school children in shenzhen, china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
58 & optimal and adaptive control of an epidemic model of influenza with unknown parameters & no & not applicable\\
\cellcolor{gray!6}{59} & \cellcolor{gray!6}{simulating endogenous dynamics of intervention-capacity deployment: ebola outbreak in liberia} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
60 & simulating the potential role of media coverage and infected bats in the 2014 ebola outbreak & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{61} & \cellcolor{gray!6}{a mathematical model of ebola virus disease: using sensitivity analysis to determine effective intervention targets} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
62 & a multi-agent model for adaptive vaccination during infectious disease outbreaks & no & not applicable\\
\cellcolor{gray!6}{63} & \cellcolor{gray!6}{assessing the efficiency of movement restriction as a control strategy of ebola} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
64 & characterization of outbreak response strategies and potential vaccine stockpile needs for the polio endgame & no & not applicable\\
\cellcolor{gray!6}{65} & \cellcolor{gray!6}{designing public health policies to mitigate the adverse consequences of rural-urban migration via meta-population modeling} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
66 & dynamic model of influenza with age-structured and media coverage & no & not applicable\\
\cellcolor{gray!6}{67} & \cellcolor{gray!6}{economic evaluation of individual school closure strategies: the hong kong 2009 h1n1 pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
68 & efficient vaccine distribution based on a hybrid compartmental model & no & not applicable\\
\cellcolor{gray!6}{69} & \cellcolor{gray!6}{epidemiological evaluation of different fmd control strategies in two selected regions in austria} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{inconclusive}\\
70 & evaluating targeted interventions via meta-population models with multi-level mixing & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{71} & \cellcolor{gray!6}{evaluation of outbreak response immunization in the control of pertussis using agent-based modeling} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
72 & global stability and optimal control for a tuberculosis model with vaccination and treatment & no & not applicable\\
\cellcolor{gray!6}{73} & \cellcolor{gray!6}{impact on epidemic measles of vaccination campaigns triggered by disease outbreaks or serosurveys: a modeling study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
74 & metapopulation and non-proportional vaccination models overview & no & not applicable\\
\cellcolor{gray!6}{75} & \cellcolor{gray!6}{model-based comprehensive analysis of school closure policies for mitigating influenza epidemics and pandemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
76 & modeling ring-vaccination strategies to control ebola virus disease epidemics & no & not applicable\\
\cellcolor{gray!6}{77} & \cellcolor{gray!6}{modeling the effect of public health resources and alerting on the dynamics of pertussis spread*} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
78 & modeling the impact of behavior change on the spread of ebola & no & not applicable\\
\cellcolor{gray!6}{79} & \cellcolor{gray!6}{modeling the spread of polio in an ipv-vaccinated population: lessons learned from the 2013 silent outbreak in southern israel} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
80 & modelling weekly vector control against dengue in the guangdong province of china & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{81} & \cellcolor{gray!6}{optimal control strategies for the spread of ebola in west africa} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
82 & potential impact of a ventilation intervention for influenza in the context of a dense indoor contact network in hong kong & yes & no\\
\cellcolor{gray!6}{83} & \cellcolor{gray!6}{predicting and evaluating the epidemic trend of ebola virus disease in the 2014-2015 outbreak and the effects of intervention measures} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
84 & projected impact of dengue vaccination in yucatán, mexico & no & not applicable\\
\cellcolor{gray!6}{85} & \cellcolor{gray!6}{seasonality and the effectiveness of mass vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
86 & simulation optimization for an age-based vaccines distribution strategy against the spread of influenza epidemic & no & not applicable\\
\cellcolor{gray!6}{87} & \cellcolor{gray!6}{spatiotemporal dynamics of the ebola epidemic in guinea and implications for vaccination and disease elimination: a computational modeling analysis} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
88 & the interplay of vaccination and vector control on small dengue networks & no & not applicable\\
\cellcolor{gray!6}{89} & \cellcolor{gray!6}{an epidemic patchy model with entry–exit screening} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
90 & assessing the role of voluntary self-isolation in the control of pandemic influenza using a household epidemic model & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{91} & \cellcolor{gray!6}{be-codis: a mathematical model to predict the risk of human diseases spread between countries—validation and application to the 2014–2015 ebola virus disease epidemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
92 & dengue in madeira island & no & not applicable\\
\cellcolor{gray!6}{93} & \cellcolor{gray!6}{dynamic simulation of a seiqr-v epidemic model based on cellular automata} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{inconclusive}\\
94 & early vaccine availability represents an important public health advance for the control of pandemic influenza & no & not applicable\\
\cellcolor{gray!6}{95} & \cellcolor{gray!6}{effectiveness of ebola treatment units and community care centers — liberia, september 23–october 31, 2014} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
96 & evaluation of the benefts and risks of introducing ebola community care centers, sierra leone & no & not applicable\\
\cellcolor{gray!6}{97} & \cellcolor{gray!6}{evidence for emergency vaccination having played a crucial role to control the 1965/66 foot-and-mouth disease outbreak in switzerland} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
98 & measuring the impact of ebola control measures in sierra leone & no & not applicable\\
\cellcolor{gray!6}{99} & \cellcolor{gray!6}{media impact switching surface during an infectious disease outbreak} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
100 & modeling options to manage type 1 wild poliovirus imported into israel in 2013 & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{101} & \cellcolor{gray!6}{modeling the effect of comprehensive interventions on ebola virus transmission} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
102 & modeling the effect of school closures in a pandemic scenario: exploring two different contact matrices & no & not applicable\\
\cellcolor{gray!6}{103} & \cellcolor{gray!6}{modelling the effect of early detection of ebola} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
104 & multi-scale modeling for the transmission of influenza and the evaluation of interventions toward it & no & not applicable\\
\cellcolor{gray!6}{105} & \cellcolor{gray!6}{optimal intervention strategies for a seir control model of ebola epidemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
106 & predicting the extinction of ebola spreading in liberia due to mitigation strategies & no & not applicable\\
\cellcolor{gray!6}{107} & \cellcolor{gray!6}{school closure strategies for the 2009 hong kong hini influenza pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
108 & spatiotemporal spread of the 2014 outbreak of ebola virus disease in liberia and the effectiveness of non-pharmaceutical interventions: a computational modelling analysis & no & not applicable\\
\cellcolor{gray!6}{109} & \cellcolor{gray!6}{strategies for early vaccination during novel influenza outbreaks} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
110 & the effects of media reports on disease spread and important public health measurements & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{111} & \cellcolor{gray!6}{the impact of human behavioral changes in 2014 west africa ebola outbreak} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
112 & transmission dynamics and final epidemic size of ebola virus disease outbreaks with varying interventions & no & not applicable\\
\cellcolor{gray!6}{113} & \cellcolor{gray!6}{treatment–donation-stockpile dynamics in ebola convalescent blood transfusion therapy} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
114 & vaccine prioritization for effective pandemic response & no & not applicable\\
\cellcolor{gray!6}{115} & \cellcolor{gray!6}{a mathematical study of a tb model with treatment interruptions and two latent periods} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
116 & antiviral prophylaxis and isolation for the control of pandemic influenza & no & not applicable\\
\cellcolor{gray!6}{117} & \cellcolor{gray!6}{assessing the impact of travel restrictions on international spread of the 2014 west african ebola epidemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
118 & assessing the use of antiviral treatment to control influenza & yes & inconclusive\\
\cellcolor{gray!6}{119} & \cellcolor{gray!6}{behavior in the time of cholera: evidence from the 2008-2009 cholera outbreak in zimbabwe} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
120 & behavioural response in educated young adults towards influenza a(h1n1)pdm09 & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{121} & \cellcolor{gray!6}{cover your cough! quantifying the benefits of a localized healthy behavior intervention on flu epidemics in washington dc} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
122 & dynamics and control of ebola virus transmission in montserrado, liberia: a mathematical modelling analysis & no & not applicable\\
\cellcolor{gray!6}{123} & \cellcolor{gray!6}{estimating the effectiveness of early control measures through school absenteeism surveillance in observed outbreaks at rural schools in hubei, china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
124 & evaluation of the benefit of emergency vaccination in a foot-and-mouth disease free country with low livestock density & no & not applicable\\
\cellcolor{gray!6}{125} & \cellcolor{gray!6}{modeling the dynamics of oral poliovirus vaccine cessation} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
126 & modeling the impact of optimal screening on typhoid dynamics & no & not applicable\\
\cellcolor{gray!6}{127} & \cellcolor{gray!6}{modeling the influence of environment and intervention oncholera in haiti} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
128 & sequential bayesian inference in hidden markov stochastic kinetic models with application to detection and response to seasonal epidemics & no & not applicable\\
\cellcolor{gray!6}{129} & \cellcolor{gray!6}{simulating optimal vaccination times during cholera outbreaks} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
130 & the role of vaccination coverage, individual behaviors, and the public health response in the control of measles epidemics: an agent-based simulation for california & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{131} & \cellcolor{gray!6}{time is (still) of the essence: quantifying the impact of emergency meningitis vaccination response in katsina state, nigeria} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
132 & a perspective on multiple waves of influenza pandemics & no & not applicable\\
\cellcolor{gray!6}{133} & \cellcolor{gray!6}{an optimal control problem arising from a dengue disease transmission model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
134 & cholera in haiti: reproductive numbers and vaccination coverage estimates & no & not applicable\\
\cellcolor{gray!6}{135} & \cellcolor{gray!6}{comparing control strategies against foot-and-mouth disease: will vaccination be cost-effective in denmark?} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{inconclusive}\\
\addlinespace
136 & cost-effectiveness of influenza control measures: a dynamic transmission model-based analysis & yes & no\\
\cellcolor{gray!6}{137} & \cellcolor{gray!6}{cost-effectiveness of workplace closure and travel restriction for mitigating influenza outbreaks: a network-based simulation} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
138 & decisions on control of foot-and-mouth disease informed using model predictions & no & not applicable\\
\cellcolor{gray!6}{139} & \cellcolor{gray!6}{dengue in cape verde: vector control and vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
140 & enhancement of collective immunity in tokyo metropolitan area by selective vaccination against an emerging influenza pandemic & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{141} & \cellcolor{gray!6}{estimated impact of aggressive empirical antiviral treatment in containing an outbreak of pandemic influenza h1n1 in an isolated first nations community} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
142 & multiregional dynamic vaccine allocation during an influenza epidemic & no & not applicable\\
\cellcolor{gray!6}{143} & \cellcolor{gray!6}{policies to reduce influenza in the workplace: impact assessments using an agent-based model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
144 & transmission dynamics of the 2009 influenza a (h1n1) pandemic in india: the impact of holiday-related school closure & no & not applicable\\
\cellcolor{gray!6}{145} & \cellcolor{gray!6}{vaccination against foot-and-mouth disease: do initial conditions affect its benefit?} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
146 & was mandatory quarantine necessary in china for controlling the 2009 h1n1 pandemic? & no & not applicable\\
\cellcolor{gray!6}{147} & \cellcolor{gray!6}{a contact-network-based simulation model for evaluating interventions under 'what-if' scenarios in epidemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
148 & campus quarantine (fengxiao) for curbing emergent infectious diseases: lessons from mitigating a/h1n1 in xi'an, china & no & not applicable\\
\cellcolor{gray!6}{149} & \cellcolor{gray!6}{dynamic modelling of costs and health consequences of school closure during an influenza pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
150 & effect of vaccines and antivirals during the major 2009 a(h1n1) pandemic wave in norway - and the influence of vaccination timing & yes & no\\
\addlinespace
\cellcolor{gray!6}{151} & \cellcolor{gray!6}{estimating the value of containment strategies in delaying the arrival time of an influenza pandemic: a case study of travel restriction and patient isolation} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
152 & how to minimize the attack rate during multiple influenza outbreaks in a heterogeneous population & no & not applicable\\
\cellcolor{gray!6}{153} & \cellcolor{gray!6}{modeling strategies for controlling h1n1 outbreaks in china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
154 & modeling the effects of h1n1 influenza vaccine distribution in the united states & no & not applicable\\
\cellcolor{gray!6}{155} & \cellcolor{gray!6}{modeling the impact of air, sea, and land travel restrictions supplemented by other interventions on the emergence of a new influenza pandemic virus} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
156 & simulating school closure policies for cost effective pandemic decision making & no & not applicable\\
\cellcolor{gray!6}{157} & \cellcolor{gray!6}{the impact of school closures on pandemic influenza: assessing potential repercussions using a seasonal sir model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
158 & vaccination against foot-and-mouth disease i: epidemiological consequences & yes & no\\
\cellcolor{gray!6}{159} & \cellcolor{gray!6}{a deterministic resource scheduling model in epidemic control: a case study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
160 & a model for the a(h1n1) epidemic in mexico, including social isolation & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{161} & \cellcolor{gray!6}{a model to evaluate mass vaccination against pneumococcus as a countermeasure against pandemic influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
162 & a multilayer framework to assess influenza intervention policies & no & not applicable\\
\cellcolor{gray!6}{163} & \cellcolor{gray!6}{a note on the use of optimal control on a discrete time model of influenza dynamics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
164 & a simulation-based assessment of school closure strategies during an influenza epidemic & no & not applicable\\
\cellcolor{gray!6}{165} & \cellcolor{gray!6}{agent-based modeling of the spread of influenza-like illness in an emergency department: a simulation study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
166 & antiviral treatment for pandemic influenza: assessing potential repercussions using a seasonally forced sir model & no & not applicable\\
\cellcolor{gray!6}{167} & \cellcolor{gray!6}{can antiviral drugs contain pandemic influenza transmission?} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
168 & characterizing the epidemiology of the 2009 influenza a/h1n1 pandemic in mexico & no & not applicable\\
\cellcolor{gray!6}{169} & \cellcolor{gray!6}{cholera epidemic in haiti, 2010: using a transmission model to explain spatial spread of disease and identify optimal control interventions} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
170 & controlling an influenza outbreak in deterministic and stochastic models with the emergence and evolution of drug resistance (model 1) & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{171} & \cellcolor{gray!6}{modeling control strategies for concurrent epidemics of seasonal and pandemic h1n1 influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
172 & modeling the impact of behavior changes on the spread of pandemic influenza & no & not applicable\\
\cellcolor{gray!6}{173} & \cellcolor{gray!6}{modelling and analysis of influenza a (h1n1) on networks} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
174 & modelling the strategies for age specific vaccination scheduling during influenza pandemic outbreaks & no & not applicable\\
\cellcolor{gray!6}{175} & \cellcolor{gray!6}{modelling the transmission dynamics and control of the novel 2009 swine influenza (h1n1) pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
176 & planning for the control of pandemic influenza a (h1n1) in los angeles county and the united states & yes & yes\\
\cellcolor{gray!6}{177} & \cellcolor{gray!6}{prioritization of delayed vaccination for pandemic influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
178 & temporal factors in school closure policy for mitigating the spread of influenza & no & not applicable\\
\cellcolor{gray!6}{179} & \cellcolor{gray!6}{the global transmission and control of influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
180 & toward effective vaccine deployment: a systematic study & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{181} & \cellcolor{gray!6}{vaccination against 2009 pandemic h1n1 in a population dynamical model of vancouver, canada: timing is everything} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
182 & a simulation model for the potential spread of foot-and-mouth disease in the castile and leon region of spain & yes & no\\
\cellcolor{gray!6}{183} & \cellcolor{gray!6}{community-based measures for mitigating the 2009 h1n1 pandemic in china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
184 & effective real-time allocation of pandemic interventions & no & not applicable\\
\cellcolor{gray!6}{185} & \cellcolor{gray!6}{efficient mitigation strategies for epidemics in rural regions} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
186 & influenza pandemic waves under various mitigation strategies with 2009 h1n1 as a case study & no & not applicable\\
\cellcolor{gray!6}{187} & \cellcolor{gray!6}{is a mass immunization program for pandemic (h1n1) 2009 good value for money? early evidence from the canadian experience} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
188 & optimal control for pandemic influenza: the role of limited antiviral treatment and isolation & no & not applicable\\
\cellcolor{gray!6}{189} & \cellcolor{gray!6}{optimizing vaccine allocation at different points in time during an epidemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
190 & simulating school closure strategies to mitigate an influenza epidemic & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{191} & \cellcolor{gray!6}{the effect of mask use on the spread of influenza during a pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
192 & transmission dynamics of an influenza model with age of infection and antiviral treatment & no & not applicable\\
\cellcolor{gray!6}{193} & \cellcolor{gray!6}{transmission risks and control of foot-and-mouth disease in the netherlands: spatial patterns} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
194 & when should we intervene to control the 2009 influenza a(h1n1) pandemic? & no & not applicable\\
\cellcolor{gray!6}{195} & \cellcolor{gray!6}{adaptive vaccination strategies to mitigate pandemic influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
196 & antiviral resistance and the control of pandemic influenza: the roles of stochasticity, evolution and model details & no & not applicable\\
\cellcolor{gray!6}{197} & \cellcolor{gray!6}{economic evaluation of influenza pandemic mitigation strategies in the united states using a stochastic microsimulation transmission model} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
198 & effectiveness and cost-effectiveness of expanded antiviral prophylaxis and adjuvanted vaccination strategies for an influenza a (h5n1) pandemic & yes & yes\\
\cellcolor{gray!6}{199} & \cellcolor{gray!6}{engineering responses to pandemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
200 & epidemiological benefits of more-effective tuberculosis vaccines, drugs, and diagnostics & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{201} & \cellcolor{gray!6}{household epidemics: modelling effects of early stage vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
202 & measures against transmission of pandemic h1n1 influenza in japan in 2009: simulation model & yes & no\\
\cellcolor{gray!6}{203} & \cellcolor{gray!6}{modeling vaccination campaigns and the fall/winter 2009 activity of the new a(h1n1) influenza in the northern hemisphere} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
204 & modelling foot and mouth disease & no & not applicable\\
\cellcolor{gray!6}{205} & \cellcolor{gray!6}{modelling of the influenza a(h1n1)v outbreak in mexico city, april-may 2009, with control sanitary measures} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
206 & post-exposure prophylaxis during pandemic outbreaks & no & not applicable\\
\cellcolor{gray!6}{207} & \cellcolor{gray!6}{potential for a global dynamic of influenza a (h1n1)} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
208 & reducing the impact of the next influenza pandemic using householdbased public health interventions & no & not applicable\\
\cellcolor{gray!6}{209} & \cellcolor{gray!6}{seasonal transmission potential and activity peaks of the new influenza a(h1n1): a monte carlo likelihood analysis based on human mobility} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
210 & simulation of foot-and-mouth disease spread within an integrated livestock system in texas, usa & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{211} & \cellcolor{gray!6}{the transmissibility and control of pandemic influenza a (h1n1) virus} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
212 & bayesian analysis of severe acute respiratory syndrome: the 2003 hong kong epidemic & no & not applicable\\
\cellcolor{gray!6}{213} & \cellcolor{gray!6}{hepatitis b vaccination and changes in sexual risk behaviour among men who have sex with men in amsterdam} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
214 & mathematical assessment of canada's pandemic influenza preparedness plan & yes & no\\
\cellcolor{gray!6}{215} & \cellcolor{gray!6}{modeling targeted layered containment of an influenza pandemic in the united states} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
216 & optimal allocation of pandemic influenza vaccine depends on age, risk and timing & no & not applicable\\
\cellcolor{gray!6}{217} & \cellcolor{gray!6}{pandemic simulation of antivirals plus school closures: buying time until strain-specific vaccine is available} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
218 & preparedness for the spread of influenza: prohibition of traffic, school closure, and vaccination of children in the commuter towns of tokyo & yes & yes\\
\cellcolor{gray!6}{219} & \cellcolor{gray!6}{scenarios of diffusion and control of an influenza pandemic in italy} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
220 & time is of the essence: exploring a measles outbreak response vaccination in niamey, niger & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{221} & \cellcolor{gray!6}{a stochastic equation-based model of the value of international air-travel restrictions for controlling pandemic flu} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
222 & assessing the role of basic control measures, antivirals and vaccine in curtailing pandemic influenza: scenarios for the us, uk and the netherlands & yes & inconclusive\\
\cellcolor{gray!6}{223} & \cellcolor{gray!6}{deterministic sir (susceptible–infected–removed) models applied to varicella outbreaks} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
224 & effectiveness of movement-prevention regulations to reduce the spread of foot-and-mouth disease in the netherlands & no & not applicable\\
\cellcolor{gray!6}{225} & \cellcolor{gray!6}{effects of internal border control on spread of pandemic influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
226 & simple models of influenza progression within a heterogeneous population & no & not applicable\\
\cellcolor{gray!6}{227} & \cellcolor{gray!6}{stochastic model of an influenza epidemic with drug resistance} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
228 & the effect of public health measures on the 1918 influenza pandemic in u.s. cities & no & not applicable\\
\cellcolor{gray!6}{229} & \cellcolor{gray!6}{vaccinating in disease-free regions: a vaccine model with application to yellow fever} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
230 & a 'small-world-like' model for comparing interventions aimed at preventing and controlling influenza pandemics & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{231} & \cellcolor{gray!6}{containing pandemic influenza with antiviral agents: analytical commentary} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
232 & critical response to post-outbreak vaccination against foot-and-mouth disease & no & not applicable\\
\cellcolor{gray!6}{233} & \cellcolor{gray!6}{mitigation strategies for pandemic influenza in the united states} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
234 & simple models for containment of a pandemic & no & not applicable\\
\cellcolor{gray!6}{235} & \cellcolor{gray!6}{statistical inference in a stochastic epidemic seir model with control intervention: ebola as a case study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
236 & strategies for containing an emerging influenza pandemic in southeast asia & no & not applicable\\
\cellcolor{gray!6}{237} & \cellcolor{gray!6}{modeling alternative mitigation strategies for a hypothetical outbreak of foot-and-mouth disease in the united states} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{inconclusive}\\
238 & modelling vaccination strategies against foot-and-mouth disease & no & not applicable\\
\cellcolor{gray!6}{239} & \cellcolor{gray!6}{a decision-tree to optimise control measures during the early stage of a foot-and-mouth disease epidemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
240 & effect of control measures on the course of simulated foot and mouth disease epidemics that started on different farm types in various dutch areas & yes & inconclusive\\
\addlinespace
\cellcolor{gray!6}{241} & \cellcolor{gray!6}{dynamics of the 2001 uk foot and mouth epidemic: stochastic dispersal in a heterogeneous landscape} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
242 & an extended state-transition model for foot-and-mouth disease epidemics in france & yes & no\\
\cellcolor{gray!6}{243} & \cellcolor{gray!6}{simulated economic consequences of foot-and-mouth disease epidemics and their public control in france} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
244 & effect of chemotherapy on malaria transmission among yanomami amerindians: simulated consequences of placebo treatment & no & not applicable\\
\cellcolor{gray!6}{245} & \cellcolor{gray!6}{modelling vaccination strategy against directly transmitted diseases using a series of pulses} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
246 & mass vaccination to control chickenpox: the influence of zoster & no & not applicable\\
\cellcolor{gray!6}{247} & \cellcolor{gray!6}{an evaluation of alternate control strategies for foot-and-mouth disease in australia: a regional approach} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
248 & analysis of a measles epidemic & no & not applicable\\
\cellcolor{gray!6}{249} & \cellcolor{gray!6}{a model of the transmission of dengue fever with an evaluation of the impact of ultra-low volume (ulv) insecticide applications on dengue epidemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
250 & a discrete-time model with vaccination for a measles epidemic & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{251} & \cellcolor{gray!6}{a stochastic model of epidemics in military recruits} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
252 & stochastic two-agent epidemic simulation models for a community of families & no & not applicable\\*
\end{longtable}
\endgroup{}
\end{landscape}

\hypertarget{table-6}{%
\subsection{Table 6}\label{table-6}}

This section presents extracted data on the outcomes measured and
whether a sensitivity analysis was conducted.

\begin{landscape}\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}{l>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{6cm}l}
\toprule
num & title & outcome\_measured & sensitivity\_analysis\\
\midrule
\endfirsthead
\multicolumn{4}{@{}l}{\textit{(continued)}}\\
\toprule
num & title & outcome\_measured & sensitivity\_analysis\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{a cholera metapopulation model interlinking migration with intervention strategies - a case study of zimbabwe (2008-2009)} & \cellcolor{gray!6}{cases averted,final epidemic size,cost,case fatality} & \cellcolor{gray!6}{no}\\
2 & a theoretical single-parameter model for urbanisation to study infectious disease spread and interventions & final epidemic size & yes\\
\cellcolor{gray!6}{3} & \cellcolor{gray!6}{assessing the effects of modeling the spectrum of clinical symptoms on the dynamics and control of ebola} & \cellcolor{gray!6}{final epidemic size} & \cellcolor{gray!6}{yes}\\
4 & dynamical analysis and control strategies in modelling ebola virus disease & final epidemic size,cost & no\\
\cellcolor{gray!6}{5} & \cellcolor{gray!6}{effect of a hepatitis a vaccination campaign during a hepatitis a outbreak in taiwan, 2015–2017: a modeling study} & \cellcolor{gray!6}{cases averted} & \cellcolor{gray!6}{yes}\\
\addlinespace
6 & evaluating strategies for control of tuberculosis in prisons and prevention of spillover into communities: an observational and modeling study from brazil & cases averted & yes\\
\cellcolor{gray!6}{7} & \cellcolor{gray!6}{evaluating the effects of control interventions and estimating the inapparent infections for dengue outbreak in hangzhou, china} & \cellcolor{gray!6}{cases averted,final epidemic size} & \cellcolor{gray!6}{yes}\\
8 & incidence dynamics and investigation of key interventions in a dengue outbreak in ningbo city, china & attack rate & yes\\
\cellcolor{gray!6}{9} & \cellcolor{gray!6}{incorporating media data into a model of infectious disease transmission} & \cellcolor{gray!6}{final epidemic size} & \cellcolor{gray!6}{yes}\\
10 & influence of asymptomatic infections for the effectiveness of facemasks during pandemic influenza & final epidemic size,control reproduction number, & yes\\
\addlinespace
\cellcolor{gray!6}{11} & \cellcolor{gray!6}{mathematical analysis of a cholera infection model with vaccination strategy} & \cellcolor{gray!6}{intervention coverage,outbreak duration and timing,final epidemic size,attack rate} & \cellcolor{gray!6}{yes}\\
12 & modeling and stability analysis of epidemic expansion disease ebola virus with implications prevention in population & final epidemic size & no\\
\cellcolor{gray!6}{13} & \cellcolor{gray!6}{modeling the effectiveness of respiratory protective devices in reducing influenza outbreak} & \cellcolor{gray!6}{attack rate,prevalence of infection} & \cellcolor{gray!6}{yes}\\
14 & modeling the effects of vaccination and treatment on tuberculosis transmission dynamics & incidence & yes\\
\cellcolor{gray!6}{15} & \cellcolor{gray!6}{optimal control and cost-effective analysis of the 2017 meningitis outbreak in nigeria} & \cellcolor{gray!6}{cases averted,cost} & \cellcolor{gray!6}{yes}\\
\addlinespace
16 & optimal control strategies for a two-group epidemic model with vaccination-resource constraints & outbreak duration and timing,final epidemic size,cost & no\\
\cellcolor{gray!6}{17} & \cellcolor{gray!6}{optimal media reporting intensity on mitigating spread of an emerging infectious disease} & \cellcolor{gray!6}{final epidemic size,peak magnitude} & \cellcolor{gray!6}{yes}\\
18 & school dismissal as a pandemic influenza response: when, where and for how long? & cases averted,timing of peak,cumulative attack rate & yes\\
\cellcolor{gray!6}{19} & \cellcolor{gray!6}{study on modeling simulation and optimal control method for the transmission risk of the ebola virus} & \cellcolor{gray!6}{number of individuals in s,number of susceptible individuals,number of latently infected individuals,isolated or quarantined individuals,and the individuals that have recovered and are immune to evd} & \cellcolor{gray!6}{yes}\\
20 & transmission dynamics of cholera with hyperinfectious and hypoinfectious vibrios: mathematical modelling and control strategies & final epidemic size,cost & no\\
\addlinespace
\cellcolor{gray!6}{21} & \cellcolor{gray!6}{a new epidemics–logistics model: insights into controlling the ebola virus disease in west africa} & \cellcolor{gray!6}{funerals,cumulative infections} & \cellcolor{gray!6}{yes}\\
22 & contact reductions from live poultry market closures limit the epidemic of human infections with h7n9 influenza & cases averted,outbreak duration and timing,final epidemic size & no\\
\cellcolor{gray!6}{23} & \cellcolor{gray!6}{disparities in spread and control of influenza in slums of delhi: findings from an agent-based modelling study} & \cellcolor{gray!6}{attack rate} & \cellcolor{gray!6}{no}\\
24 & efficacy of control measures in the control of ebola, liberia 2014–2015 & cumulative deaths,cumulative cases & yes\\
\cellcolor{gray!6}{25} & \cellcolor{gray!6}{epidemiology of the silent polio outbreak in rahat, israel, based on modeling of environmental surveillance data} & \cellcolor{gray!6}{cases averted} & \cellcolor{gray!6}{no}\\
\addlinespace
26 & evaluating costs and health consequences of sick leave strategies against pandemic and seasonal influenza in norway using a dynamic model & cost & no\\
\cellcolor{gray!6}{27} & \cellcolor{gray!6}{evaluating vaccination strategies to control foot-and-mouth disease: a country comparison study} & \cellcolor{gray!6}{outbreak duration and timing,total number of infected premises} & \cellcolor{gray!6}{no}\\
28 & impact of public health responses during a measles outbreak in an amish community in ohio: modeling the dynamics of transmission & outbreak duration and timing,final epidemic size,instantaneous reproduction number,case reproduction number & yes\\
\cellcolor{gray!6}{29} & \cellcolor{gray!6}{initial validation of a simulation model for estimating the impact of serogroup a neisseria meningitidis vaccination in the african meningitis belt} & \cellcolor{gray!6}{incidence} & \cellcolor{gray!6}{yes}\\
30 & logistical constraints lead to an intermediate optimum in outbreak response vaccination & intervention coverage & no\\
\addlinespace
\cellcolor{gray!6}{31} & \cellcolor{gray!6}{manipulation of contact network structure and the impact on foot-and-mouth disease transmission} & \cellcolor{gray!6}{final epidemic size} & \cellcolor{gray!6}{no}\\
32 & mathematical model and intervention strategies for mitigating tuberculosis in the philippines & cost,number of exposed and infectious individuals & yes\\
\cellcolor{gray!6}{33} & \cellcolor{gray!6}{measles outbreak response decision-making under uncertainty: a retrospective analysis} & \cellcolor{gray!6}{immunization threshold} & \cellcolor{gray!6}{yes}\\
34 & modeling the heterogeneity of dengue transmission in a city & final epidemic size,timing of peak,peak size & no\\
\cellcolor{gray!6}{35} & \cellcolor{gray!6}{modelling the large-scale yellow fever outbreak in luanda, angola, and the impact of vaccination} & \cellcolor{gray!6}{deaths averted,final epidemic size,attack rate,case fatality} & \cellcolor{gray!6}{yes}\\
\addlinespace
36 & quantifying the impact of early-stage contact tracing on controlling ebola diffusion & attack rate & no\\
\cellcolor{gray!6}{37} & \cellcolor{gray!6}{simulation of key interventions for seasonal influenza outbreak control at school in changsha, china} & \cellcolor{gray!6}{outbreak duration and timing,attack rate} & \cellcolor{gray!6}{no}\\
38 & the impact of regular school closure on seasonal influenza epidemics: a data-driven spatial transmission model for belgium & timing of peak,peak difference,incidence & no\\
\cellcolor{gray!6}{39} & \cellcolor{gray!6}{the potential impact of case-area targeted interventions in response to cholera outbreaks: a modeling study} & \cellcolor{gray!6}{cases averted,outbreak duration and timing,incidence} & \cellcolor{gray!6}{yes}\\
40 & value of inventory information in allocating a limited supply of influenza vaccine during a pandemic & intervention coverage & no\\
\addlinespace
\cellcolor{gray!6}{41} & \cellcolor{gray!6}{an age-structured model for cholera control with vaccination} & \cellcolor{gray!6}{final epidemic size} & \cellcolor{gray!6}{no}\\
42 & an approach to and web-based tool for infectious disease outbreak intervention analysis & cumulative infected & yes\\
\cellcolor{gray!6}{43} & \cellcolor{gray!6}{an economic assessment of foot and mouth disease in japan} & \cellcolor{gray!6}{outbreak duration and timing,final epidemic size,cost} & \cellcolor{gray!6}{no}\\
44 & analysis of an seriv epidemic model of human influenza & timing of peak,peak size,transmission & yes\\
\cellcolor{gray!6}{45} & \cellcolor{gray!6}{control strategies of avian influenza pandemic model with time delay} & \cellcolor{gray!6}{cases averted} & \cellcolor{gray!6}{no}\\
\addlinespace
46 & costs and benefits of including inactivated in addition to oral poliovirus vaccine in outbreak response after cessation of oral poliovirus vaccine use & cost,dalys,incremental cost effectiveness ratio,incremental net benefits & yes\\
\cellcolor{gray!6}{47} & \cellcolor{gray!6}{deriving effective vaccine allocation strategies for pandemic influenza: comparison of an agent-based simulation and a compartmental model} & \cellcolor{gray!6}{final epidemic size,cost,total deaths,years of life lost} & \cellcolor{gray!6}{yes}\\
48 & early rigorous control interventions can largely reduce dengue outbreak magnitude: experience from chaozhou, china & outbreak duration and timing,final epidemic size & no\\
\cellcolor{gray!6}{49} & \cellcolor{gray!6}{effects of reactive social distancing on the 1918 influenza pandemic} & \cellcolor{gray!6}{final epidemic size} & \cellcolor{gray!6}{no}\\
50 & epidemiological and economic impact of pandemic influenza in chicago: priorities for vaccine interventions & cost,attack rate,total deaths,risk of death,net benefits,return on investment & yes\\
\addlinespace
\cellcolor{gray!6}{51} & \cellcolor{gray!6}{estimating direct and indirect protective effect of influenza vaccination in the united states} & \cellcolor{gray!6}{cases averted} & \cellcolor{gray!6}{no}\\
52 & evaluating the effects of common control measures for influenza a (h1n1) outbreak at school in china: a modeling study & outbreak duration and timing,attack rate & yes\\
\cellcolor{gray!6}{53} & \cellcolor{gray!6}{evaluation of strategies to control a potential outbreak of foot-and-mouth disease in sweden} & \cellcolor{gray!6}{outbreak duration and timing,final epidemic size,total number of herds surveilled,total number of herds culled,total number of herds vaccinated} & \cellcolor{gray!6}{yes}\\
54 & impact of a waning vaccine and altered behavior on the spread of influenza & final epidemic size,timing of peak & no\\
\cellcolor{gray!6}{55} & \cellcolor{gray!6}{mathematical models for devising the optimal ebola virus disease eradication} & \cellcolor{gray!6}{infection rate} & \cellcolor{gray!6}{no}\\
\addlinespace
56 & modeling the role of public health education in ebola virus disease outbreaks in sudan & final epidemic size,cumulative incidence & yes\\
\cellcolor{gray!6}{57} & \cellcolor{gray!6}{modelling the transmission and control strategies of varicella among school children in shenzhen, china} & \cellcolor{gray!6}{cases averted,intervention coverage,final epidemic size,peak size} & \cellcolor{gray!6}{no}\\
58 & optimal and adaptive control of an epidemic model of influenza with unknown parameters & final epidemic size,cost & no\\
\cellcolor{gray!6}{59} & \cellcolor{gray!6}{simulating endogenous dynamics of intervention-capacity deployment: ebola outbreak in liberia} & \cellcolor{gray!6}{effective reproduction number} & \cellcolor{gray!6}{no}\\
60 & simulating the potential role of media coverage and infected bats in the 2014 ebola outbreak & timing of peak,cumulative cases,cumulative deaths,peak magnitude & yes\\
\addlinespace
\cellcolor{gray!6}{61} & \cellcolor{gray!6}{a mathematical model of ebola virus disease: using sensitivity analysis to determine effective intervention targets} & \cellcolor{gray!6}{r0} & \cellcolor{gray!6}{yes}\\
62 & a multi-agent model for adaptive vaccination during infectious disease outbreaks & hospitalizations,case fatality & no\\
\cellcolor{gray!6}{63} & \cellcolor{gray!6}{assessing the efficiency of movement restriction as a control strategy of ebola} & \cellcolor{gray!6}{final epidemic size} & \cellcolor{gray!6}{no}\\
64 & characterization of outbreak response strategies and potential vaccine stockpile needs for the polio endgame & paralytic incidence,average expected number of cases & yes\\
\cellcolor{gray!6}{65} & \cellcolor{gray!6}{designing public health policies to mitigate the adverse consequences of rural-urban migration via meta-population modeling} & \cellcolor{gray!6}{final epidemic size,vaccine doses,peak magnitude} & \cellcolor{gray!6}{no}\\
\addlinespace
66 & dynamic model of influenza with age-structured and media coverage & intervention coverage & no\\
\cellcolor{gray!6}{67} & \cellcolor{gray!6}{economic evaluation of individual school closure strategies: the hong kong 2009 h1n1 pandemic} & \cellcolor{gray!6}{cost,attack rate} & \cellcolor{gray!6}{yes}\\
68 & efficient vaccine distribution based on a hybrid compartmental model & final epidemic size,attack rate & no\\
\cellcolor{gray!6}{69} & \cellcolor{gray!6}{epidemiological evaluation of different fmd control strategies in two selected regions in austria} & \cellcolor{gray!6}{intervention coverage,outbreak duration and timing,final epidemic size} & \cellcolor{gray!6}{yes}\\
70 & evaluating targeted interventions via meta-population models with multi-level mixing & intervention coverage,final epidemic size & no\\
\addlinespace
\cellcolor{gray!6}{71} & \cellcolor{gray!6}{evaluation of outbreak response immunization in the control of pertussis using agent-based modeling} & \cellcolor{gray!6}{cases averted,cumulative incidence} & \cellcolor{gray!6}{yes}\\
72 & global stability and optimal control for a tuberculosis model with vaccination and treatment & incidence,basic reproduction number & no\\
\cellcolor{gray!6}{73} & \cellcolor{gray!6}{impact on epidemic measles of vaccination campaigns triggered by disease outbreaks or serosurveys: a modeling study} & \cellcolor{gray!6}{cases averted} & \cellcolor{gray!6}{yes}\\
74 & metapopulation and non-proportional vaccination models overview & outbreak duration and timing,final epidemic size & no\\
\cellcolor{gray!6}{75} & \cellcolor{gray!6}{model-based comprehensive analysis of school closure policies for mitigating influenza epidemics and pandemics} & \cellcolor{gray!6}{timing of peak,attack rate,peak incidence,average number of weeks lost} & \cellcolor{gray!6}{yes}\\
\addlinespace
76 & modeling ring-vaccination strategies to control ebola virus disease epidemics & outbreak duration and timing,final epidemic size & no\\
\cellcolor{gray!6}{77} & \cellcolor{gray!6}{modeling the effect of public health resources and alerting on the dynamics of pertussis spread*} & \cellcolor{gray!6}{outbreak duration and timing,final epidemic size,number of contacts traced} & \cellcolor{gray!6}{yes}\\
78 & modeling the impact of behavior change on the spread of ebola & outbreak duration and timing,final epidemic size,timing of peak & yes\\
\cellcolor{gray!6}{79} & \cellcolor{gray!6}{modeling the spread of polio in an ipv-vaccinated population: lessons learned from the 2013 silent outbreak in southern israel} & \cellcolor{gray!6}{outbreak duration and timing,cumulative incidence} & \cellcolor{gray!6}{yes}\\
80 & modelling weekly vector control against dengue in the guangdong province of china & final epidemic size,attack rate & yes\\
\addlinespace
\cellcolor{gray!6}{81} & \cellcolor{gray!6}{optimal control strategies for the spread of ebola in west africa} & \cellcolor{gray!6}{s,i and r curve} & \cellcolor{gray!6}{no}\\
82 & potential impact of a ventilation intervention for influenza in the context of a dense indoor contact network in hong kong & timing of peak,peak infection rate & yes\\
\cellcolor{gray!6}{83} & \cellcolor{gray!6}{predicting and evaluating the epidemic trend of ebola virus disease in the 2014-2015 outbreak and the effects of intervention measures} & \cellcolor{gray!6}{final epidemic size,total deaths} & \cellcolor{gray!6}{yes}\\
84 & projected impact of dengue vaccination in yucatán, mexico & intervention coverage,effectiveness of vaccination strategies & no\\
\cellcolor{gray!6}{85} & \cellcolor{gray!6}{seasonality and the effectiveness of mass vaccination} & \cellcolor{gray!6}{cases averted} & \cellcolor{gray!6}{no}\\
\addlinespace
86 & simulation optimization for an age-based vaccines distribution strategy against the spread of influenza epidemic & outbreak duration and timing & no\\
\cellcolor{gray!6}{87} & \cellcolor{gray!6}{spatiotemporal dynamics of the ebola epidemic in guinea and implications for vaccination and disease elimination: a computational modeling analysis} & \cellcolor{gray!6}{cumulative cases,incidence} & \cellcolor{gray!6}{yes}\\
88 & the interplay of vaccination and vector control on small dengue networks & geometric mean number of infected hosts,basic reproduction number & yes\\
\cellcolor{gray!6}{89} & \cellcolor{gray!6}{an epidemic patchy model with entry–exit screening} & \cellcolor{gray!6}{basic reproduction number} & \cellcolor{gray!6}{yes}\\
90 & assessing the role of voluntary self-isolation in the control of pandemic influenza using a household epidemic model & household reproduction number & no\\
\addlinespace
\cellcolor{gray!6}{91} & \cellcolor{gray!6}{be-codis: a mathematical model to predict the risk of human diseases spread between countries—validation and application to the 2014–2015 ebola virus disease epidemic} & \cellcolor{gray!6}{cumulative incidence,cumulative deaths} & \cellcolor{gray!6}{yes}\\
92 & dengue in madeira island & final epidemic size & no\\
\cellcolor{gray!6}{93} & \cellcolor{gray!6}{dynamic simulation of a seiqr-v epidemic model based on cellular automata} & \cellcolor{gray!6}{cases averted,final epidemic size} & \cellcolor{gray!6}{no}\\
94 & early vaccine availability represents an important public health advance for the control of pandemic influenza & attack rate & no\\
\cellcolor{gray!6}{95} & \cellcolor{gray!6}{effectiveness of ebola treatment units and community care centers — liberia, september 23–october 31, 2014} & \cellcolor{gray!6}{cases averted,cumulative incidence} & \cellcolor{gray!6}{no}\\
\addlinespace
96 & evaluation of the benefts and risks of introducing ebola community care centers, sierra leone & final epidemic size & no\\
\cellcolor{gray!6}{97} & \cellcolor{gray!6}{evidence for emergency vaccination having played a crucial role to control the 1965/66 foot-and-mouth disease outbreak in switzerland} & \cellcolor{gray!6}{outbreak duration and timing,number of animals culled,number of premises culled} & \cellcolor{gray!6}{yes}\\
98 & measuring the impact of ebola control measures in sierra leone & cases averted & yes\\
\cellcolor{gray!6}{99} & \cellcolor{gray!6}{media impact switching surface during an infectious disease outbreak} & \cellcolor{gray!6}{timing of peak,hospital notifications} & \cellcolor{gray!6}{yes}\\
100 & modeling options to manage type 1 wild poliovirus imported into israel in 2013 & intervention coverage,final epidemic size & no\\
\addlinespace
\cellcolor{gray!6}{101} & \cellcolor{gray!6}{modeling the effect of comprehensive interventions on ebola virus transmission} & \cellcolor{gray!6}{final epidemic size,basic reproduction number} & \cellcolor{gray!6}{yes}\\
102 & modeling the effect of school closures in a pandemic scenario: exploring two different contact matrices & timing of peak & yes\\
\cellcolor{gray!6}{103} & \cellcolor{gray!6}{modelling the effect of early detection of ebola} & \cellcolor{gray!6}{attack rate} & \cellcolor{gray!6}{no}\\
104 & multi-scale modeling for the transmission of influenza and the evaluation of interventions toward it & attack rate & yes\\
\cellcolor{gray!6}{105} & \cellcolor{gray!6}{optimal intervention strategies for a seir control model of ebola epidemics} & \cellcolor{gray!6}{cost,total fraction of infected and exposed} & \cellcolor{gray!6}{no}\\
\addlinespace
106 & predicting the extinction of ebola spreading in liberia due to mitigation strategies & outbreak duration and timing,final epidemic size & yes\\
\cellcolor{gray!6}{107} & \cellcolor{gray!6}{school closure strategies for the 2009 hong kong hini influenza pandemic} & \cellcolor{gray!6}{outbreak duration and timing,final epidemic size,timing of peak,attack rate} & \cellcolor{gray!6}{yes}\\
108 & spatiotemporal spread of the 2014 outbreak of ebola virus disease in liberia and the effectiveness of non-pharmaceutical interventions: a computational modelling analysis & cases averted,final epidemic size,number of deaths & yes\\
\cellcolor{gray!6}{109} & \cellcolor{gray!6}{strategies for early vaccination during novel influenza outbreaks} & \cellcolor{gray!6}{attack rate,hospitalizations} & \cellcolor{gray!6}{no}\\
110 & the effects of media reports on disease spread and important public health measurements & outbreak duration and timing,final epidemic size,timing of peak,peak magnitude,total vaccinated & yes\\
\addlinespace
\cellcolor{gray!6}{111} & \cellcolor{gray!6}{the impact of human behavioral changes in 2014 west africa ebola outbreak} & \cellcolor{gray!6}{r0} & \cellcolor{gray!6}{yes}\\
112 & transmission dynamics and final epidemic size of ebola virus disease outbreaks with varying interventions & final epidemic size & yes\\
\cellcolor{gray!6}{113} & \cellcolor{gray!6}{treatment–donation-stockpile dynamics in ebola convalescent blood transfusion therapy} & \cellcolor{gray!6}{case fatality} & \cellcolor{gray!6}{no}\\
114 & vaccine prioritization for effective pandemic response & attack rate,mortality rate & yes\\
\cellcolor{gray!6}{115} & \cellcolor{gray!6}{a mathematical study of a tb model with treatment interruptions and two latent periods} & \cellcolor{gray!6}{control reproduction number} & \cellcolor{gray!6}{no}\\
\addlinespace
116 & antiviral prophylaxis and isolation for the control of pandemic influenza & control reproduction number & yes\\
\cellcolor{gray!6}{117} & \cellcolor{gray!6}{assessing the impact of travel restrictions on international spread of the 2014 west african ebola epidemic} & \cellcolor{gray!6}{risk of case importation} & \cellcolor{gray!6}{yes}\\
118 & assessing the use of antiviral treatment to control influenza & intervention coverage,attack rate & no\\
\cellcolor{gray!6}{119} & \cellcolor{gray!6}{behavior in the time of cholera: evidence from the 2008-2009 cholera outbreak in zimbabwe} & \cellcolor{gray!6}{incidence} & \cellcolor{gray!6}{yes}\\
120 & behavioural response in educated young adults towards influenza a(h1n1)pdm09 & r0 & no\\
\addlinespace
\cellcolor{gray!6}{121} & \cellcolor{gray!6}{cover your cough! quantifying the benefits of a localized healthy behavior intervention on flu epidemics in washington dc} & \cellcolor{gray!6}{final epidemic size,timing of peak,number of simulations with epidemic outbreak,peak infections} & \cellcolor{gray!6}{no}\\
122 & dynamics and control of ebola virus transmission in montserrado, liberia: a mathematical modelling analysis & cases averted,deaths averted & no\\
\cellcolor{gray!6}{123} & \cellcolor{gray!6}{estimating the effectiveness of early control measures through school absenteeism surveillance in observed outbreaks at rural schools in hubei, china} & \cellcolor{gray!6}{attack rate,extra protective rate} & \cellcolor{gray!6}{no}\\
124 & evaluation of the benefit of emergency vaccination in a foot-and-mouth disease free country with low livestock density & outbreak duration and timing & no\\
\cellcolor{gray!6}{125} & \cellcolor{gray!6}{modeling the dynamics of oral poliovirus vaccine cessation} & \cellcolor{gray!6}{incidence,vaccine-derived virus prevalence,population immunity} & \cellcolor{gray!6}{no}\\
\addlinespace
126 & modeling the impact of optimal screening on typhoid dynamics & final epidemic size & no\\
\cellcolor{gray!6}{127} & \cellcolor{gray!6}{modeling the influence of environment and intervention oncholera in haiti} & \cellcolor{gray!6}{final epidemic size} & \cellcolor{gray!6}{no}\\
128 & sequential bayesian inference in hidden markov stochastic kinetic models with application to detection and response to seasonal epidemics & campaign duration,final epidemic size,cost,peak magnitude,number of times countermeasures are started,proportion of time that infected size is above a threshold number of infecteds & no\\
\cellcolor{gray!6}{129} & \cellcolor{gray!6}{simulating optimal vaccination times during cholera outbreaks} & \cellcolor{gray!6}{final epidemic size} & \cellcolor{gray!6}{no}\\
130 & the role of vaccination coverage, individual behaviors, and the public health response in the control of measles epidemics: an agent-based simulation for california & intervention coverage,final epidemic size & yes\\
\addlinespace
\cellcolor{gray!6}{131} & \cellcolor{gray!6}{time is (still) of the essence: quantifying the impact of emergency meningitis vaccination response in katsina state, nigeria} & \cellcolor{gray!6}{cases averted,outbreak duration and timing} & \cellcolor{gray!6}{yes}\\
132 & a perspective on multiple waves of influenza pandemics & outbreak duration and timing,final epidemic size,attack rate & no\\
\cellcolor{gray!6}{133} & \cellcolor{gray!6}{an optimal control problem arising from a dengue disease transmission model} & \cellcolor{gray!6}{final epidemic size} & \cellcolor{gray!6}{yes}\\
134 & cholera in haiti: reproductive numbers and vaccination coverage estimates & intervention coverage,attack rate & yes\\
\cellcolor{gray!6}{135} & \cellcolor{gray!6}{comparing control strategies against foot-and-mouth disease: will vaccination be cost-effective in denmark?} & \cellcolor{gray!6}{outbreak duration and timing,cost,number of infected herds,number of depopulated herds,export losses} & \cellcolor{gray!6}{yes}\\
\addlinespace
136 & cost-effectiveness of influenza control measures: a dynamic transmission model-based analysis & cost,basic reproduction number & no\\
\cellcolor{gray!6}{137} & \cellcolor{gray!6}{cost-effectiveness of workplace closure and travel restriction for mitigating influenza outbreaks: a network-based simulation} & \cellcolor{gray!6}{cost} & \cellcolor{gray!6}{yes}\\
138 & decisions on control of foot-and-mouth disease informed using model predictions & outbreak duration and timing,final epidemic size,cost & yes\\
\cellcolor{gray!6}{139} & \cellcolor{gray!6}{dengue in cape verde: vector control and vaccination} & \cellcolor{gray!6}{campaign duration,final epidemic size,timing of peak} & \cellcolor{gray!6}{no}\\
140 & enhancement of collective immunity in tokyo metropolitan area by selective vaccination against an emerging influenza pandemic & attack rate & no\\
\addlinespace
\cellcolor{gray!6}{141} & \cellcolor{gray!6}{estimated impact of aggressive empirical antiviral treatment in containing an outbreak of pandemic influenza h1n1 in an isolated first nations community} & \cellcolor{gray!6}{cases averted,intervention coverage,attack rate} & \cellcolor{gray!6}{no}\\
142 & multiregional dynamic vaccine allocation during an influenza epidemic & cases averted & no\\
\cellcolor{gray!6}{143} & \cellcolor{gray!6}{policies to reduce influenza in the workplace: impact assessments using an agent-based model} & \cellcolor{gray!6}{final epidemic size,attack rate} & \cellcolor{gray!6}{yes}\\
144 & transmission dynamics of the 2009 influenza a (h1n1) pandemic in india: the impact of holiday-related school closure & reproduction number & no\\
\cellcolor{gray!6}{145} & \cellcolor{gray!6}{vaccination against foot-and-mouth disease: do initial conditions affect its benefit?} & \cellcolor{gray!6}{intervention coverage} & \cellcolor{gray!6}{yes}\\
\addlinespace
146 & was mandatory quarantine necessary in china for controlling the 2009 h1n1 pandemic? & outbreak duration and timing,cost,timing of peak,cumulative incidence & no\\
\cellcolor{gray!6}{147} & \cellcolor{gray!6}{a contact-network-based simulation model for evaluating interventions under 'what-if' scenarios in epidemic} & \cellcolor{gray!6}{attack rate,peak incidence,peak day} & \cellcolor{gray!6}{no}\\
148 & campus quarantine (fengxiao) for curbing emergent infectious diseases: lessons from mitigating a/h1n1 in xi'an, china & hospitalizations & yes\\
\cellcolor{gray!6}{149} & \cellcolor{gray!6}{dynamic modelling of costs and health consequences of school closure during an influenza pandemic} & \cellcolor{gray!6}{attack rate,qualys} & \cellcolor{gray!6}{yes}\\
150 & effect of vaccines and antivirals during the major 2009 a(h1n1) pandemic wave in norway - and the influence of vaccination timing & final epidemic size & yes\\
\addlinespace
\cellcolor{gray!6}{151} & \cellcolor{gray!6}{estimating the value of containment strategies in delaying the arrival time of an influenza pandemic: a case study of travel restriction and patient isolation} & \cellcolor{gray!6}{first arrival time} & \cellcolor{gray!6}{no}\\
152 & how to minimize the attack rate during multiple influenza outbreaks in a heterogeneous population & cumulative attack rate & no\\
\cellcolor{gray!6}{153} & \cellcolor{gray!6}{modeling strategies for controlling h1n1 outbreaks in china} & \cellcolor{gray!6}{attack rate} & \cellcolor{gray!6}{no}\\
154 & modeling the effects of h1n1 influenza vaccine distribution in the united states & cases averted & no\\
\cellcolor{gray!6}{155} & \cellcolor{gray!6}{modeling the impact of air, sea, and land travel restrictions supplemented by other interventions on the emergence of a new influenza pandemic virus} & \cellcolor{gray!6}{timing of peak,attack rate} & \cellcolor{gray!6}{yes}\\
\addlinespace
156 & simulating school closure policies for cost effective pandemic decision making & cost,qualys,incremental cost effectiveness ratio (icer),cumulative attack rate & yes\\
\cellcolor{gray!6}{157} & \cellcolor{gray!6}{the impact of school closures on pandemic influenza: assessing potential repercussions using a seasonal sir model} & \cellcolor{gray!6}{final epidemic size,timing of peak} & \cellcolor{gray!6}{no}\\
158 & vaccination against foot-and-mouth disease i: epidemiological consequences & outbreak duration and timing,final epidemic size & no\\
\cellcolor{gray!6}{159} & \cellcolor{gray!6}{a deterministic resource scheduling model in epidemic control: a case study} & \cellcolor{gray!6}{final epidemic size} & \cellcolor{gray!6}{yes}\\
160 & a model for the a(h1n1) epidemic in mexico, including social isolation & timing of peak & no\\
\addlinespace
\cellcolor{gray!6}{161} & \cellcolor{gray!6}{a model to evaluate mass vaccination against pneumococcus as a countermeasure against pandemic influenza} & \cellcolor{gray!6}{campaign duration,hospitalizations,case fatality} & \cellcolor{gray!6}{yes}\\
162 & a multilayer framework to assess influenza intervention policies & timing of peak,peak magnitude & no\\
\cellcolor{gray!6}{163} & \cellcolor{gray!6}{a note on the use of optimal control on a discrete time model of influenza dynamics} & \cellcolor{gray!6}{final epidemic size,cost,incidence} & \cellcolor{gray!6}{yes}\\
164 & a simulation-based assessment of school closure strategies during an influenza epidemic & timing of peak,attack rate,peak daily infection & no\\
\cellcolor{gray!6}{165} & \cellcolor{gray!6}{agent-based modeling of the spread of influenza-like illness in an emergency department: a simulation study} & \cellcolor{gray!6}{final epidemic size} & \cellcolor{gray!6}{yes}\\
\addlinespace
166 & antiviral treatment for pandemic influenza: assessing potential repercussions using a seasonally forced sir model & final epidemic size,timing of peak,peak size & no\\
\cellcolor{gray!6}{167} & \cellcolor{gray!6}{can antiviral drugs contain pandemic influenza transmission?} & \cellcolor{gray!6}{final epidemic size,attack rate} & \cellcolor{gray!6}{no}\\
168 & characterizing the epidemiology of the 2009 influenza a/h1n1 pandemic in mexico & cases averted,attack rate & no\\
\cellcolor{gray!6}{169} & \cellcolor{gray!6}{cholera epidemic in haiti, 2010: using a transmission model to explain spatial spread of disease and identify optimal control interventions} & \cellcolor{gray!6}{outbreak duration and timing,final epidemic size,timing of peak,cumulative hospital cases,date of first reported cases} & \cellcolor{gray!6}{no}\\
170 & controlling an influenza outbreak in deterministic and stochastic models with the emergence and evolution of drug resistance (model 1) & attack rate & no\\
\addlinespace
\cellcolor{gray!6}{171} & \cellcolor{gray!6}{modeling control strategies for concurrent epidemics of seasonal and pandemic h1n1 influenza} & \cellcolor{gray!6}{final epidemic size,cost} & \cellcolor{gray!6}{no}\\
172 & modeling the impact of behavior changes on the spread of pandemic influenza & intervention coverage,outbreak duration and timing,attack rate,case fatality & no\\
\cellcolor{gray!6}{173} & \cellcolor{gray!6}{modelling and analysis of influenza a (h1n1) on networks} & \cellcolor{gray!6}{final epidemic size} & \cellcolor{gray!6}{no}\\
174 & modelling the strategies for age specific vaccination scheduling during influenza pandemic outbreaks & final epidemic size,attack rate,total deaths & yes\\
\cellcolor{gray!6}{175} & \cellcolor{gray!6}{modelling the transmission dynamics and control of the novel 2009 swine influenza (h1n1) pandemic} & \cellcolor{gray!6}{final epidemic size,hospitalizations,case fatality} & \cellcolor{gray!6}{no}\\
\addlinespace
176 & planning for the control of pandemic influenza a (h1n1) in los angeles county and the united states & cases averted,final epidemic size,timing of peak,hospitalizations & no\\
\cellcolor{gray!6}{177} & \cellcolor{gray!6}{prioritization of delayed vaccination for pandemic influenza} & \cellcolor{gray!6}{deaths averted,attack rate,hospitalizations} & \cellcolor{gray!6}{yes}\\
178 & temporal factors in school closure policy for mitigating the spread of influenza & timing of peak,attack rate,peak incidence & no\\
\cellcolor{gray!6}{179} & \cellcolor{gray!6}{the global transmission and control of influenza} & \cellcolor{gray!6}{attack rate,prevalence} & \cellcolor{gray!6}{yes}\\
180 & toward effective vaccine deployment: a systematic study & cumulative infections & no\\
\addlinespace
\cellcolor{gray!6}{181} & \cellcolor{gray!6}{vaccination against 2009 pandemic h1n1 in a population dynamical model of vancouver, canada: timing is everything} & \cellcolor{gray!6}{campaign duration,attack rate,case fatality} & \cellcolor{gray!6}{yes}\\
182 & a simulation model for the potential spread of foot-and-mouth disease in the castile and leon region of spain & outbreak duration and timing,number of infected premises,number of depopulated premises,number of quarantined premises & yes\\
\cellcolor{gray!6}{183} & \cellcolor{gray!6}{community-based measures for mitigating the 2009 h1n1 pandemic in china} & \cellcolor{gray!6}{timing of peak} & \cellcolor{gray!6}{no}\\
184 & effective real-time allocation of pandemic interventions & morbidity,indirect protection & yes\\
\cellcolor{gray!6}{185} & \cellcolor{gray!6}{efficient mitigation strategies for epidemics in rural regions} & \cellcolor{gray!6}{cases averted} & \cellcolor{gray!6}{yes}\\
\addlinespace
186 & influenza pandemic waves under various mitigation strategies with 2009 h1n1 as a case study & final epidemic size,timing of peak,cumulative attack rate,peak magnitude & no\\
\cellcolor{gray!6}{187} & \cellcolor{gray!6}{is a mass immunization program for pandemic (h1n1) 2009 good value for money? early evidence from the canadian experience} & \cellcolor{gray!6}{cost,hospitalizations,qualys} & \cellcolor{gray!6}{no}\\
188 & optimal control for pandemic influenza: the role of limited antiviral treatment and isolation & attack rate,cumulative incidence & yes\\
\cellcolor{gray!6}{189} & \cellcolor{gray!6}{optimizing vaccine allocation at different points in time during an epidemic} & \cellcolor{gray!6}{attack rate,hospitalizations,case fatality} & \cellcolor{gray!6}{yes}\\
190 & simulating school closure strategies to mitigate an influenza epidemic & attack rate,incidence & yes\\
\addlinespace
\cellcolor{gray!6}{191} & \cellcolor{gray!6}{the effect of mask use on the spread of influenza during a pandemic} & \cellcolor{gray!6}{attack rate,r0} & \cellcolor{gray!6}{no}\\
192 & transmission dynamics of an influenza model with age of infection and antiviral treatment & final epidemic size,attack rate & no\\
\cellcolor{gray!6}{193} & \cellcolor{gray!6}{transmission risks and control of foot-and-mouth disease in the netherlands: spatial patterns} & \cellcolor{gray!6}{effective reproduction number} & \cellcolor{gray!6}{yes}\\
194 & when should we intervene to control the 2009 influenza a(h1n1) pandemic? & time of detection,maximum number of symptomatic cases per day & no\\
\cellcolor{gray!6}{195} & \cellcolor{gray!6}{adaptive vaccination strategies to mitigate pandemic influenza} & \cellcolor{gray!6}{timing of peak,hospitalizations,deaths} & \cellcolor{gray!6}{no}\\
\addlinespace
196 & antiviral resistance and the control of pandemic influenza: the roles of stochasticity, evolution and model details & attack rate & no\\
\cellcolor{gray!6}{197} & \cellcolor{gray!6}{economic evaluation of influenza pandemic mitigation strategies in the united states using a stochastic microsimulation transmission model} & \cellcolor{gray!6}{outbreak duration and timing,cost} & \cellcolor{gray!6}{yes}\\
198 & effectiveness and cost-effectiveness of expanded antiviral prophylaxis and adjuvanted vaccination strategies for an influenza a (h5n1) pandemic & cases averted,deaths averted,cost,qualys,incremental cost effectiveness ratio & yes\\
\cellcolor{gray!6}{199} & \cellcolor{gray!6}{engineering responses to pandemics} & \cellcolor{gray!6}{final epidemic size} & \cellcolor{gray!6}{no}\\
200 & epidemiological benefits of more-effective tuberculosis vaccines, drugs, and diagnostics & incidence,cumulative cases,cumulative deaths & yes\\
\addlinespace
\cellcolor{gray!6}{201} & \cellcolor{gray!6}{household epidemics: modelling effects of early stage vaccination} & \cellcolor{gray!6}{household reproduction number for} & \cellcolor{gray!6}{yes}\\
202 & measures against transmission of pandemic h1n1 influenza in japan in 2009: simulation model & final epidemic size & no\\
\cellcolor{gray!6}{203} & \cellcolor{gray!6}{modeling vaccination campaigns and the fall/winter 2009 activity of the new a(h1n1) influenza in the northern hemisphere} & \cellcolor{gray!6}{final epidemic size,attack rate,peak size} & \cellcolor{gray!6}{yes}\\
204 & modelling foot and mouth disease & number of infected farms,basic reproduction number & no\\
\cellcolor{gray!6}{205} & \cellcolor{gray!6}{modelling of the influenza a(h1n1)v outbreak in mexico city, april-may 2009, with control sanitary measures} & \cellcolor{gray!6}{attack rate} & \cellcolor{gray!6}{no}\\
\addlinespace
206 & post-exposure prophylaxis during pandemic outbreaks & final epidemic size,total deaths & yes\\
\cellcolor{gray!6}{207} & \cellcolor{gray!6}{potential for a global dynamic of influenza a (h1n1)} & \cellcolor{gray!6}{final epidemic size,attack rate,mortality rate} & \cellcolor{gray!6}{no}\\
208 & reducing the impact of the next influenza pandemic using householdbased public health interventions & attack rate & no\\
\cellcolor{gray!6}{209} & \cellcolor{gray!6}{seasonal transmission potential and activity peaks of the new influenza a(h1n1): a monte carlo likelihood analysis based on human mobility} & \cellcolor{gray!6}{final epidemic size,timing of peak,incidence} & \cellcolor{gray!6}{yes}\\
210 & simulation of foot-and-mouth disease spread within an integrated livestock system in texas, usa & lives saved,outbreak duration and timing & no\\
\addlinespace
\cellcolor{gray!6}{211} & \cellcolor{gray!6}{the transmissibility and control of pandemic influenza a (h1n1) virus} & \cellcolor{gray!6}{attack rate,r0} & \cellcolor{gray!6}{yes}\\
212 & bayesian analysis of severe acute respiratory syndrome: the 2003 hong kong epidemic & attack rate & no\\
\cellcolor{gray!6}{213} & \cellcolor{gray!6}{hepatitis b vaccination and changes in sexual risk behaviour among men who have sex with men in amsterdam} & \cellcolor{gray!6}{cases averted} & \cellcolor{gray!6}{no}\\
214 & mathematical assessment of canada's pandemic influenza preparedness plan & final epidemic size,hospitalizations,cumulative deaths & no\\
\cellcolor{gray!6}{215} & \cellcolor{gray!6}{modeling targeted layered containment of an influenza pandemic in the united states} & \cellcolor{gray!6}{cases averted,attack rate} & \cellcolor{gray!6}{yes}\\
\addlinespace
216 & optimal allocation of pandemic influenza vaccine depends on age, risk and timing & cases averted,hospitalizations & yes\\
\cellcolor{gray!6}{217} & \cellcolor{gray!6}{pandemic simulation of antivirals plus school closures: buying time until strain-specific vaccine is available} & \cellcolor{gray!6}{final epidemic size,timing of peak,attack rate,case fatality} & \cellcolor{gray!6}{no}\\
218 & preparedness for the spread of influenza: prohibition of traffic, school closure, and vaccination of children in the commuter towns of tokyo & final epidemic size,timing of peak,peak magnitude & no\\
\cellcolor{gray!6}{219} & \cellcolor{gray!6}{scenarios of diffusion and control of an influenza pandemic in italy} & \cellcolor{gray!6}{outbreak duration and timing,timing of peak,cumulative attack rate} & \cellcolor{gray!6}{yes}\\
220 & time is of the essence: exploring a measles outbreak response vaccination in niamey, niger & cases averted & no\\
\addlinespace
\cellcolor{gray!6}{221} & \cellcolor{gray!6}{a stochastic equation-based model of the value of international air-travel restrictions for controlling pandemic flu} & \cellcolor{gray!6}{timing of peak,peak magnitude} & \cellcolor{gray!6}{no}\\
222 & assessing the role of basic control measures, antivirals and vaccine in curtailing pandemic influenza: scenarios for the us, uk and the netherlands & final epidemic size,hospitalizations,deaths & no\\
\cellcolor{gray!6}{223} & \cellcolor{gray!6}{deterministic sir (susceptible–infected–removed) models applied to varicella outbreaks} & \cellcolor{gray!6}{cases averted} & \cellcolor{gray!6}{no}\\
224 & effectiveness of movement-prevention regulations to reduce the spread of foot-and-mouth disease in the netherlands & outbreak duration and timing,number of infected farms,the number of pre-emptively slaughtered farms,number of farms in control zones & yes\\
\cellcolor{gray!6}{225} & \cellcolor{gray!6}{effects of internal border control on spread of pandemic influenza} & \cellcolor{gray!6}{delay between epidemics} & \cellcolor{gray!6}{yes}\\
\addlinespace
226 & simple models of influenza progression within a heterogeneous population & final epidemic size,timing of peak,peak magnitude & no\\
\cellcolor{gray!6}{227} & \cellcolor{gray!6}{stochastic model of an influenza epidemic with drug resistance} & \cellcolor{gray!6}{final epidemic size,attack rate,resistant cases} & \cellcolor{gray!6}{no}\\
228 & the effect of public health measures on the 1918 influenza pandemic in u.s. cities & final epidemic size,mortality & no\\
\cellcolor{gray!6}{229} & \cellcolor{gray!6}{vaccinating in disease-free regions: a vaccine model with application to yellow fever} & \cellcolor{gray!6}{final epidemic size,r0,vaccination coverage} & \cellcolor{gray!6}{no}\\
230 & a 'small-world-like' model for comparing interventions aimed at preventing and controlling influenza pandemics & outbreak duration and timing,final epidemic size,attack rate,cumulative incidence & yes\\
\addlinespace
\cellcolor{gray!6}{231} & \cellcolor{gray!6}{containing pandemic influenza with antiviral agents: analytical commentary} & \cellcolor{gray!6}{attack rate} & \cellcolor{gray!6}{yes}\\
232 & critical response to post-outbreak vaccination against foot-and-mouth disease & final epidemic size & no\\
\cellcolor{gray!6}{233} & \cellcolor{gray!6}{mitigation strategies for pandemic influenza in the united states} & \cellcolor{gray!6}{attack rate,cumulative incidence} & \cellcolor{gray!6}{yes}\\
234 & simple models for containment of a pandemic & final epidemic size & no\\
\cellcolor{gray!6}{235} & \cellcolor{gray!6}{statistical inference in a stochastic epidemic seir model with control intervention: ebola as a case study} & \cellcolor{gray!6}{outbreak duration and timing,final epidemic size} & \cellcolor{gray!6}{no}\\
\addlinespace
236 & strategies for containing an emerging influenza pandemic in southeast asia & probability of preventing a large outbreak,number of courses of drug required to achieve containment & yes\\
\cellcolor{gray!6}{237} & \cellcolor{gray!6}{modeling alternative mitigation strategies for a hypothetical outbreak of foot-and-mouth disease in the united states} & \cellcolor{gray!6}{outbreak duration and timing,cost,number of herds slaughtered,number of herds vaccinated} & \cellcolor{gray!6}{no}\\
238 & modelling vaccination strategies against foot-and-mouth disease & outbreak duration and timing,final epidemic size & yes\\
\cellcolor{gray!6}{239} & \cellcolor{gray!6}{a decision-tree to optimise control measures during the early stage of a foot-and-mouth disease epidemic} & \cellcolor{gray!6}{final epidemic size,cost,export losses} & \cellcolor{gray!6}{no}\\
240 & effect of control measures on the course of simulated foot and mouth disease epidemics that started on different farm types in various dutch areas & outbreak duration and timing,final epidemic size,attack rate & no\\
\addlinespace
\cellcolor{gray!6}{241} & \cellcolor{gray!6}{dynamics of the 2001 uk foot and mouth epidemic: stochastic dispersal in a heterogeneous landscape} & \cellcolor{gray!6}{outbreak duration and timing,final epidemic size,total number of animals culled} & \cellcolor{gray!6}{no}\\
242 & an extended state-transition model for foot-and-mouth disease epidemics in france & outbreak duration and timing,final epidemic size & yes\\
\cellcolor{gray!6}{243} & \cellcolor{gray!6}{simulated economic consequences of foot-and-mouth disease epidemics and their public control in france} & \cellcolor{gray!6}{cost} & \cellcolor{gray!6}{no}\\
244 & effect of chemotherapy on malaria transmission among yanomami amerindians: simulated consequences of placebo treatment & duration of infection & yes\\
\cellcolor{gray!6}{245} & \cellcolor{gray!6}{modelling vaccination strategy against directly transmitted diseases using a series of pulses} & \cellcolor{gray!6}{force of infection,proportion of susceptible individuals} & \cellcolor{gray!6}{yes}\\
\addlinespace
246 & mass vaccination to control chickenpox: the influence of zoster & mortality rate,incidence & no\\
\cellcolor{gray!6}{247} & \cellcolor{gray!6}{an evaluation of alternate control strategies for foot-and-mouth disease in australia: a regional approach} & \cellcolor{gray!6}{outbreak duration and timing,final epidemic size,cost,compensation,control costs,output effects,income effects,employment effects} & \cellcolor{gray!6}{no}\\
248 & analysis of a measles epidemic & cumulative cases & no\\
\cellcolor{gray!6}{249} & \cellcolor{gray!6}{a model of the transmission of dengue fever with an evaluation of the impact of ultra-low volume (ulv) insecticide applications on dengue epidemics} & \cellcolor{gray!6}{cases averted,timing of peak,peak magnitude,population immunity} & \cellcolor{gray!6}{yes}\\
250 & a discrete-time model with vaccination for a measles epidemic & cumulative incidence & no\\
\addlinespace
\cellcolor{gray!6}{251} & \cellcolor{gray!6}{a stochastic model of epidemics in military recruits} & \cellcolor{gray!6}{outbreak duration and timing} & \cellcolor{gray!6}{no}\\
252 & stochastic two-agent epidemic simulation models for a community of families & intervention coverage,outbreak duration and timing,timing of peak & no\\*
\end{longtable}
\endgroup{}
\end{landscape}

\hypertarget{table-7}{%
\subsection{Table 7}\label{table-7}}

This section presents extracted data on whether observed data was used
for model validation (data\_used), and whether the data was made
available (data\_available).

\begin{landscape}\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}{l>{\raggedright\arraybackslash}p{9cm}ll}
\toprule
num & title & data\_used & data\_available\\
\midrule
\endfirsthead
\multicolumn{4}{@{}l}{\textit{(continued)}}\\
\toprule
num & title & data\_used & data\_available\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{a cholera metapopulation model interlinking migration with intervention strategies - a case study of zimbabwe (2008-2009)} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
2 & a theoretical single-parameter model for urbanisation to study infectious disease spread and interventions & no & not applicable\\
\cellcolor{gray!6}{3} & \cellcolor{gray!6}{assessing the effects of modeling the spectrum of clinical symptoms on the dynamics and control of ebola} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
4 & dynamical analysis and control strategies in modelling ebola virus disease & no & not applicable\\
\cellcolor{gray!6}{5} & \cellcolor{gray!6}{effect of a hepatitis a vaccination campaign during a hepatitis a outbreak in taiwan, 2015–2017: a modeling study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
\addlinespace
6 & evaluating strategies for control of tuberculosis in prisons and prevention of spillover into communities: an observational and modeling study from brazil & yes & yes\\
\cellcolor{gray!6}{7} & \cellcolor{gray!6}{evaluating the effects of control interventions and estimating the inapparent infections for dengue outbreak in hangzhou, china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
8 & incidence dynamics and investigation of key interventions in a dengue outbreak in ningbo city, china & yes & no\\
\cellcolor{gray!6}{9} & \cellcolor{gray!6}{incorporating media data into a model of infectious disease transmission} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
10 & influence of asymptomatic infections for the effectiveness of facemasks during pandemic influenza & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{11} & \cellcolor{gray!6}{mathematical analysis of a cholera infection model with vaccination strategy} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
12 & modeling and stability analysis of epidemic expansion disease ebola virus with implications prevention in population & no & not applicable\\
\cellcolor{gray!6}{13} & \cellcolor{gray!6}{modeling the effectiveness of respiratory protective devices in reducing influenza outbreak} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
14 & modeling the effects of vaccination and treatment on tuberculosis transmission dynamics & yes & no\\
\cellcolor{gray!6}{15} & \cellcolor{gray!6}{optimal control and cost-effective analysis of the 2017 meningitis outbreak in nigeria} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
\addlinespace
16 & optimal control strategies for a two-group epidemic model with vaccination-resource constraints & no & not applicable\\
\cellcolor{gray!6}{17} & \cellcolor{gray!6}{optimal media reporting intensity on mitigating spread of an emerging infectious disease} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
18 & school dismissal as a pandemic influenza response: when, where and for how long? & yes & yes\\
\cellcolor{gray!6}{19} & \cellcolor{gray!6}{study on modeling simulation and optimal control method for the transmission risk of the ebola virus} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
20 & transmission dynamics of cholera with hyperinfectious and hypoinfectious vibrios: mathematical modelling and control strategies & yes & no\\
\addlinespace
\cellcolor{gray!6}{21} & \cellcolor{gray!6}{a new epidemics–logistics model: insights into controlling the ebola virus disease in west africa} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
22 & contact reductions from live poultry market closures limit the epidemic of human infections with h7n9 influenza & no & not applicable\\
\cellcolor{gray!6}{23} & \cellcolor{gray!6}{disparities in spread and control of influenza in slums of delhi: findings from an agent-based modelling study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
24 & efficacy of control measures in the control of ebola, liberia 2014–2015 & yes & yes\\
\cellcolor{gray!6}{25} & \cellcolor{gray!6}{epidemiology of the silent polio outbreak in rahat, israel, based on modeling of environmental surveillance data} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
\addlinespace
26 & evaluating costs and health consequences of sick leave strategies against pandemic and seasonal influenza in norway using a dynamic model & no & not applicable\\
\cellcolor{gray!6}{27} & \cellcolor{gray!6}{evaluating vaccination strategies to control foot-and-mouth disease: a country comparison study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
28 & impact of public health responses during a measles outbreak in an amish community in ohio: modeling the dynamics of transmission & yes & no\\
\cellcolor{gray!6}{29} & \cellcolor{gray!6}{initial validation of a simulation model for estimating the impact of serogroup a neisseria meningitidis vaccination in the african meningitis belt} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
30 & logistical constraints lead to an intermediate optimum in outbreak response vaccination & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{31} & \cellcolor{gray!6}{manipulation of contact network structure and the impact on foot-and-mouth disease transmission} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
32 & mathematical model and intervention strategies for mitigating tuberculosis in the philippines & yes & yes\\
\cellcolor{gray!6}{33} & \cellcolor{gray!6}{measles outbreak response decision-making under uncertainty: a retrospective analysis} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
34 & modeling the heterogeneity of dengue transmission in a city & yes & no\\
\cellcolor{gray!6}{35} & \cellcolor{gray!6}{modelling the large-scale yellow fever outbreak in luanda, angola, and the impact of vaccination} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
\addlinespace
36 & quantifying the impact of early-stage contact tracing on controlling ebola diffusion & no & not applicable\\
\cellcolor{gray!6}{37} & \cellcolor{gray!6}{simulation of key interventions for seasonal influenza outbreak control at school in changsha, china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
38 & the impact of regular school closure on seasonal influenza epidemics: a data-driven spatial transmission model for belgium & yes & no\\
\cellcolor{gray!6}{39} & \cellcolor{gray!6}{the potential impact of case-area targeted interventions in response to cholera outbreaks: a modeling study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
40 & value of inventory information in allocating a limited supply of influenza vaccine during a pandemic & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{41} & \cellcolor{gray!6}{an age-structured model for cholera control with vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
42 & an approach to and web-based tool for infectious disease outbreak intervention analysis & no & not applicable\\
\cellcolor{gray!6}{43} & \cellcolor{gray!6}{an economic assessment of foot and mouth disease in japan} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
44 & analysis of an seriv epidemic model of human influenza & no & not applicable\\
\cellcolor{gray!6}{45} & \cellcolor{gray!6}{control strategies of avian influenza pandemic model with time delay} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
46 & costs and benefits of including inactivated in addition to oral poliovirus vaccine in outbreak response after cessation of oral poliovirus vaccine use & yes & no\\
\cellcolor{gray!6}{47} & \cellcolor{gray!6}{deriving effective vaccine allocation strategies for pandemic influenza: comparison of an agent-based simulation and a compartmental model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
48 & early rigorous control interventions can largely reduce dengue outbreak magnitude: experience from chaozhou, china & yes & no\\
\cellcolor{gray!6}{49} & \cellcolor{gray!6}{effects of reactive social distancing on the 1918 influenza pandemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
50 & epidemiological and economic impact of pandemic influenza in chicago: priorities for vaccine interventions & yes & yes\\
\addlinespace
\cellcolor{gray!6}{51} & \cellcolor{gray!6}{estimating direct and indirect protective effect of influenza vaccination in the united states} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
52 & evaluating the effects of common control measures for influenza a (h1n1) outbreak at school in china: a modeling study & yes & yes\\
\cellcolor{gray!6}{53} & \cellcolor{gray!6}{evaluation of strategies to control a potential outbreak of foot-and-mouth disease in sweden} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
54 & impact of a waning vaccine and altered behavior on the spread of influenza & no & not applicable\\
\cellcolor{gray!6}{55} & \cellcolor{gray!6}{mathematical models for devising the optimal ebola virus disease eradication} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
\addlinespace
56 & modeling the role of public health education in ebola virus disease outbreaks in sudan & yes & yes\\
\cellcolor{gray!6}{57} & \cellcolor{gray!6}{modelling the transmission and control strategies of varicella among school children in shenzhen, china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
58 & optimal and adaptive control of an epidemic model of influenza with unknown parameters & no & not applicable\\
\cellcolor{gray!6}{59} & \cellcolor{gray!6}{simulating endogenous dynamics of intervention-capacity deployment: ebola outbreak in liberia} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
60 & simulating the potential role of media coverage and infected bats in the 2014 ebola outbreak & yes & yes\\
\addlinespace
\cellcolor{gray!6}{61} & \cellcolor{gray!6}{a mathematical model of ebola virus disease: using sensitivity analysis to determine effective intervention targets} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
62 & a multi-agent model for adaptive vaccination during infectious disease outbreaks & yes & yes\\
\cellcolor{gray!6}{63} & \cellcolor{gray!6}{assessing the efficiency of movement restriction as a control strategy of ebola} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
64 & characterization of outbreak response strategies and potential vaccine stockpile needs for the polio endgame & no & not applicable\\
\cellcolor{gray!6}{65} & \cellcolor{gray!6}{designing public health policies to mitigate the adverse consequences of rural-urban migration via meta-population modeling} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
66 & dynamic model of influenza with age-structured and media coverage & no & not applicable\\
\cellcolor{gray!6}{67} & \cellcolor{gray!6}{economic evaluation of individual school closure strategies: the hong kong 2009 h1n1 pandemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
68 & efficient vaccine distribution based on a hybrid compartmental model & yes & yes\\
\cellcolor{gray!6}{69} & \cellcolor{gray!6}{epidemiological evaluation of different fmd control strategies in two selected regions in austria} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
70 & evaluating targeted interventions via meta-population models with multi-level mixing & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{71} & \cellcolor{gray!6}{evaluation of outbreak response immunization in the control of pertussis using agent-based modeling} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
72 & global stability and optimal control for a tuberculosis model with vaccination and treatment & no & not applicable\\
\cellcolor{gray!6}{73} & \cellcolor{gray!6}{impact on epidemic measles of vaccination campaigns triggered by disease outbreaks or serosurveys: a modeling study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
74 & metapopulation and non-proportional vaccination models overview & yes & yes\\
\cellcolor{gray!6}{75} & \cellcolor{gray!6}{model-based comprehensive analysis of school closure policies for mitigating influenza epidemics and pandemics} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
\addlinespace
76 & modeling ring-vaccination strategies to control ebola virus disease epidemics & no & not applicable\\
\cellcolor{gray!6}{77} & \cellcolor{gray!6}{modeling the effect of public health resources and alerting on the dynamics of pertussis spread*} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
78 & modeling the impact of behavior change on the spread of ebola & yes & yes\\
\cellcolor{gray!6}{79} & \cellcolor{gray!6}{modeling the spread of polio in an ipv-vaccinated population: lessons learned from the 2013 silent outbreak in southern israel} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
80 & modelling weekly vector control against dengue in the guangdong province of china & yes & yes\\
\addlinespace
\cellcolor{gray!6}{81} & \cellcolor{gray!6}{optimal control strategies for the spread of ebola in west africa} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
82 & potential impact of a ventilation intervention for influenza in the context of a dense indoor contact network in hong kong & yes & yes\\
\cellcolor{gray!6}{83} & \cellcolor{gray!6}{predicting and evaluating the epidemic trend of ebola virus disease in the 2014-2015 outbreak and the effects of intervention measures} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
84 & projected impact of dengue vaccination in yucatán, mexico & no & not applicable\\
\cellcolor{gray!6}{85} & \cellcolor{gray!6}{seasonality and the effectiveness of mass vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
86 & simulation optimization for an age-based vaccines distribution strategy against the spread of influenza epidemic & no & not applicable\\
\cellcolor{gray!6}{87} & \cellcolor{gray!6}{spatiotemporal dynamics of the ebola epidemic in guinea and implications for vaccination and disease elimination: a computational modeling analysis} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
88 & the interplay of vaccination and vector control on small dengue networks & no & not applicable\\
\cellcolor{gray!6}{89} & \cellcolor{gray!6}{an epidemic patchy model with entry–exit screening} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
90 & assessing the role of voluntary self-isolation in the control of pandemic influenza using a household epidemic model & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{91} & \cellcolor{gray!6}{be-codis: a mathematical model to predict the risk of human diseases spread between countries—validation and application to the 2014–2015 ebola virus disease epidemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
92 & dengue in madeira island & no & not applicable\\
\cellcolor{gray!6}{93} & \cellcolor{gray!6}{dynamic simulation of a seiqr-v epidemic model based on cellular automata} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
94 & early vaccine availability represents an important public health advance for the control of pandemic influenza & yes & yes\\
\cellcolor{gray!6}{95} & \cellcolor{gray!6}{effectiveness of ebola treatment units and community care centers — liberia, september 23–october 31, 2014} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
\addlinespace
96 & evaluation of the benefts and risks of introducing ebola community care centers, sierra leone & yes & no\\
\cellcolor{gray!6}{97} & \cellcolor{gray!6}{evidence for emergency vaccination having played a crucial role to control the 1965/66 foot-and-mouth disease outbreak in switzerland} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
98 & measuring the impact of ebola control measures in sierra leone & yes & yes\\
\cellcolor{gray!6}{99} & \cellcolor{gray!6}{media impact switching surface during an infectious disease outbreak} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
100 & modeling options to manage type 1 wild poliovirus imported into israel in 2013 & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{101} & \cellcolor{gray!6}{modeling the effect of comprehensive interventions on ebola virus transmission} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
102 & modeling the effect of school closures in a pandemic scenario: exploring two different contact matrices & yes & yes\\
\cellcolor{gray!6}{103} & \cellcolor{gray!6}{modelling the effect of early detection of ebola} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
104 & multi-scale modeling for the transmission of influenza and the evaluation of interventions toward it & yes & yes\\
\cellcolor{gray!6}{105} & \cellcolor{gray!6}{optimal intervention strategies for a seir control model of ebola epidemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
106 & predicting the extinction of ebola spreading in liberia due to mitigation strategies & yes & yes\\
\cellcolor{gray!6}{107} & \cellcolor{gray!6}{school closure strategies for the 2009 hong kong hini influenza pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
108 & spatiotemporal spread of the 2014 outbreak of ebola virus disease in liberia and the effectiveness of non-pharmaceutical interventions: a computational modelling analysis & yes & yes\\
\cellcolor{gray!6}{109} & \cellcolor{gray!6}{strategies for early vaccination during novel influenza outbreaks} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
110 & the effects of media reports on disease spread and important public health measurements & yes & no\\
\addlinespace
\cellcolor{gray!6}{111} & \cellcolor{gray!6}{the impact of human behavioral changes in 2014 west africa ebola outbreak} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
112 & transmission dynamics and final epidemic size of ebola virus disease outbreaks with varying interventions & yes & yes\\
\cellcolor{gray!6}{113} & \cellcolor{gray!6}{treatment–donation-stockpile dynamics in ebola convalescent blood transfusion therapy} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
114 & vaccine prioritization for effective pandemic response & yes & yes\\
\cellcolor{gray!6}{115} & \cellcolor{gray!6}{a mathematical study of a tb model with treatment interruptions and two latent periods} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
116 & antiviral prophylaxis and isolation for the control of pandemic influenza & no & not applicable\\
\cellcolor{gray!6}{117} & \cellcolor{gray!6}{assessing the impact of travel restrictions on international spread of the 2014 west african ebola epidemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
118 & assessing the use of antiviral treatment to control influenza & no & not applicable\\
\cellcolor{gray!6}{119} & \cellcolor{gray!6}{behavior in the time of cholera: evidence from the 2008-2009 cholera outbreak in zimbabwe} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
120 & behavioural response in educated young adults towards influenza a(h1n1)pdm09 & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{121} & \cellcolor{gray!6}{cover your cough! quantifying the benefits of a localized healthy behavior intervention on flu epidemics in washington dc} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
122 & dynamics and control of ebola virus transmission in montserrado, liberia: a mathematical modelling analysis & yes & yes\\
\cellcolor{gray!6}{123} & \cellcolor{gray!6}{estimating the effectiveness of early control measures through school absenteeism surveillance in observed outbreaks at rural schools in hubei, china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
124 & evaluation of the benefit of emergency vaccination in a foot-and-mouth disease free country with low livestock density & no & not applicable\\
\cellcolor{gray!6}{125} & \cellcolor{gray!6}{modeling the dynamics of oral poliovirus vaccine cessation} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
126 & modeling the impact of optimal screening on typhoid dynamics & no & not applicable\\
\cellcolor{gray!6}{127} & \cellcolor{gray!6}{modeling the influence of environment and intervention oncholera in haiti} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
128 & sequential bayesian inference in hidden markov stochastic kinetic models with application to detection and response to seasonal epidemics & no & not applicable\\
\cellcolor{gray!6}{129} & \cellcolor{gray!6}{simulating optimal vaccination times during cholera outbreaks} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
130 & the role of vaccination coverage, individual behaviors, and the public health response in the control of measles epidemics: an agent-based simulation for california & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{131} & \cellcolor{gray!6}{time is (still) of the essence: quantifying the impact of emergency meningitis vaccination response in katsina state, nigeria} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
132 & a perspective on multiple waves of influenza pandemics & yes & yes\\
\cellcolor{gray!6}{133} & \cellcolor{gray!6}{an optimal control problem arising from a dengue disease transmission model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
134 & cholera in haiti: reproductive numbers and vaccination coverage estimates & yes & yes\\
\cellcolor{gray!6}{135} & \cellcolor{gray!6}{comparing control strategies against foot-and-mouth disease: will vaccination be cost-effective in denmark?} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
\addlinespace
136 & cost-effectiveness of influenza control measures: a dynamic transmission model-based analysis & yes & yes\\
\cellcolor{gray!6}{137} & \cellcolor{gray!6}{cost-effectiveness of workplace closure and travel restriction for mitigating influenza outbreaks: a network-based simulation} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
138 & decisions on control of foot-and-mouth disease informed using model predictions & no & not applicable\\
\cellcolor{gray!6}{139} & \cellcolor{gray!6}{dengue in cape verde: vector control and vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
140 & enhancement of collective immunity in tokyo metropolitan area by selective vaccination against an emerging influenza pandemic & yes & yes\\
\addlinespace
\cellcolor{gray!6}{141} & \cellcolor{gray!6}{estimated impact of aggressive empirical antiviral treatment in containing an outbreak of pandemic influenza h1n1 in an isolated first nations community} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
142 & multiregional dynamic vaccine allocation during an influenza epidemic & yes & yes\\
\cellcolor{gray!6}{143} & \cellcolor{gray!6}{policies to reduce influenza in the workplace: impact assessments using an agent-based model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
144 & transmission dynamics of the 2009 influenza a (h1n1) pandemic in india: the impact of holiday-related school closure & yes & no\\
\cellcolor{gray!6}{145} & \cellcolor{gray!6}{vaccination against foot-and-mouth disease: do initial conditions affect its benefit?} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
\addlinespace
146 & was mandatory quarantine necessary in china for controlling the 2009 h1n1 pandemic? & yes & no\\
\cellcolor{gray!6}{147} & \cellcolor{gray!6}{a contact-network-based simulation model for evaluating interventions under 'what-if' scenarios in epidemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
148 & campus quarantine (fengxiao) for curbing emergent infectious diseases: lessons from mitigating a/h1n1 in xi'an, china & yes & yes\\
\cellcolor{gray!6}{149} & \cellcolor{gray!6}{dynamic modelling of costs and health consequences of school closure during an influenza pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
150 & effect of vaccines and antivirals during the major 2009 a(h1n1) pandemic wave in norway - and the influence of vaccination timing & yes & no\\
\addlinespace
\cellcolor{gray!6}{151} & \cellcolor{gray!6}{estimating the value of containment strategies in delaying the arrival time of an influenza pandemic: a case study of travel restriction and patient isolation} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
152 & how to minimize the attack rate during multiple influenza outbreaks in a heterogeneous population & no & not applicable\\
\cellcolor{gray!6}{153} & \cellcolor{gray!6}{modeling strategies for controlling h1n1 outbreaks in china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
154 & modeling the effects of h1n1 influenza vaccine distribution in the united states & yes & yes\\
\cellcolor{gray!6}{155} & \cellcolor{gray!6}{modeling the impact of air, sea, and land travel restrictions supplemented by other interventions on the emergence of a new influenza pandemic virus} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
\addlinespace
156 & simulating school closure policies for cost effective pandemic decision making & yes & yes\\
\cellcolor{gray!6}{157} & \cellcolor{gray!6}{the impact of school closures on pandemic influenza: assessing potential repercussions using a seasonal sir model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
158 & vaccination against foot-and-mouth disease i: epidemiological consequences & yes & no\\
\cellcolor{gray!6}{159} & \cellcolor{gray!6}{a deterministic resource scheduling model in epidemic control: a case study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
160 & a model for the a(h1n1) epidemic in mexico, including social isolation & yes & no\\
\addlinespace
\cellcolor{gray!6}{161} & \cellcolor{gray!6}{a model to evaluate mass vaccination against pneumococcus as a countermeasure against pandemic influenza} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
162 & a multilayer framework to assess influenza intervention policies & no & not applicable\\
\cellcolor{gray!6}{163} & \cellcolor{gray!6}{a note on the use of optimal control on a discrete time model of influenza dynamics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
164 & a simulation-based assessment of school closure strategies during an influenza epidemic & yes & yes\\
\cellcolor{gray!6}{165} & \cellcolor{gray!6}{agent-based modeling of the spread of influenza-like illness in an emergency department: a simulation study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
\addlinespace
166 & antiviral treatment for pandemic influenza: assessing potential repercussions using a seasonally forced sir model & no & not applicable\\
\cellcolor{gray!6}{167} & \cellcolor{gray!6}{can antiviral drugs contain pandemic influenza transmission?} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
168 & characterizing the epidemiology of the 2009 influenza a/h1n1 pandemic in mexico & yes & yes\\
\cellcolor{gray!6}{169} & \cellcolor{gray!6}{cholera epidemic in haiti, 2010: using a transmission model to explain spatial spread of disease and identify optimal control interventions} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
170 & controlling an influenza outbreak in deterministic and stochastic models with the emergence and evolution of drug resistance (model 1) & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{171} & \cellcolor{gray!6}{modeling control strategies for concurrent epidemics of seasonal and pandemic h1n1 influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
172 & modeling the impact of behavior changes on the spread of pandemic influenza & no & not applicable\\
\cellcolor{gray!6}{173} & \cellcolor{gray!6}{modelling and analysis of influenza a (h1n1) on networks} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
174 & modelling the strategies for age specific vaccination scheduling during influenza pandemic outbreaks & yes & yes\\
\cellcolor{gray!6}{175} & \cellcolor{gray!6}{modelling the transmission dynamics and control of the novel 2009 swine influenza (h1n1) pandemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
\addlinespace
176 & planning for the control of pandemic influenza a (h1n1) in los angeles county and the united states & yes & yes\\
\cellcolor{gray!6}{177} & \cellcolor{gray!6}{prioritization of delayed vaccination for pandemic influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
178 & temporal factors in school closure policy for mitigating the spread of influenza & yes & no\\
\cellcolor{gray!6}{179} & \cellcolor{gray!6}{the global transmission and control of influenza} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
180 & toward effective vaccine deployment: a systematic study & yes & yes\\
\addlinespace
\cellcolor{gray!6}{181} & \cellcolor{gray!6}{vaccination against 2009 pandemic h1n1 in a population dynamical model of vancouver, canada: timing is everything} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
182 & a simulation model for the potential spread of foot-and-mouth disease in the castile and leon region of spain & yes & yes\\
\cellcolor{gray!6}{183} & \cellcolor{gray!6}{community-based measures for mitigating the 2009 h1n1 pandemic in china} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
184 & effective real-time allocation of pandemic interventions & no & not applicable\\
\cellcolor{gray!6}{185} & \cellcolor{gray!6}{efficient mitigation strategies for epidemics in rural regions} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
\addlinespace
186 & influenza pandemic waves under various mitigation strategies with 2009 h1n1 as a case study & no & not applicable\\
\cellcolor{gray!6}{187} & \cellcolor{gray!6}{is a mass immunization program for pandemic (h1n1) 2009 good value for money? early evidence from the canadian experience} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
188 & optimal control for pandemic influenza: the role of limited antiviral treatment and isolation & no & not applicable\\
\cellcolor{gray!6}{189} & \cellcolor{gray!6}{optimizing vaccine allocation at different points in time during an epidemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
190 & simulating school closure strategies to mitigate an influenza epidemic & yes & yes\\
\addlinespace
\cellcolor{gray!6}{191} & \cellcolor{gray!6}{the effect of mask use on the spread of influenza during a pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
192 & transmission dynamics of an influenza model with age of infection and antiviral treatment & no & not applicable\\
\cellcolor{gray!6}{193} & \cellcolor{gray!6}{transmission risks and control of foot-and-mouth disease in the netherlands: spatial patterns} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
194 & when should we intervene to control the 2009 influenza a(h1n1) pandemic? & no & not applicable\\
\cellcolor{gray!6}{195} & \cellcolor{gray!6}{adaptive vaccination strategies to mitigate pandemic influenza} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
\addlinespace
196 & antiviral resistance and the control of pandemic influenza: the roles of stochasticity, evolution and model details & no & not applicable\\
\cellcolor{gray!6}{197} & \cellcolor{gray!6}{economic evaluation of influenza pandemic mitigation strategies in the united states using a stochastic microsimulation transmission model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
198 & effectiveness and cost-effectiveness of expanded antiviral prophylaxis and adjuvanted vaccination strategies for an influenza a (h5n1) pandemic & yes & yes\\
\cellcolor{gray!6}{199} & \cellcolor{gray!6}{engineering responses to pandemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
200 & epidemiological benefits of more-effective tuberculosis vaccines, drugs, and diagnostics & yes & yes\\
\addlinespace
\cellcolor{gray!6}{201} & \cellcolor{gray!6}{household epidemics: modelling effects of early stage vaccination} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
202 & measures against transmission of pandemic h1n1 influenza in japan in 2009: simulation model & yes & yes\\
\cellcolor{gray!6}{203} & \cellcolor{gray!6}{modeling vaccination campaigns and the fall/winter 2009 activity of the new a(h1n1) influenza in the northern hemisphere} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
204 & modelling foot and mouth disease & yes & yes\\
\cellcolor{gray!6}{205} & \cellcolor{gray!6}{modelling of the influenza a(h1n1)v outbreak in mexico city, april-may 2009, with control sanitary measures} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
\addlinespace
206 & post-exposure prophylaxis during pandemic outbreaks & no & not applicable\\
\cellcolor{gray!6}{207} & \cellcolor{gray!6}{potential for a global dynamic of influenza a (h1n1)} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
208 & reducing the impact of the next influenza pandemic using householdbased public health interventions & no & not applicable\\
\cellcolor{gray!6}{209} & \cellcolor{gray!6}{seasonal transmission potential and activity peaks of the new influenza a(h1n1): a monte carlo likelihood analysis based on human mobility} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
210 & simulation of foot-and-mouth disease spread within an integrated livestock system in texas, usa & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{211} & \cellcolor{gray!6}{the transmissibility and control of pandemic influenza a (h1n1) virus} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
212 & bayesian analysis of severe acute respiratory syndrome: the 2003 hong kong epidemic & yes & yes\\
\cellcolor{gray!6}{213} & \cellcolor{gray!6}{hepatitis b vaccination and changes in sexual risk behaviour among men who have sex with men in amsterdam} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
214 & mathematical assessment of canada's pandemic influenza preparedness plan & no & not applicable\\
\cellcolor{gray!6}{215} & \cellcolor{gray!6}{modeling targeted layered containment of an influenza pandemic in the united states} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
\addlinespace
216 & optimal allocation of pandemic influenza vaccine depends on age, risk and timing & no & not applicable\\
\cellcolor{gray!6}{217} & \cellcolor{gray!6}{pandemic simulation of antivirals plus school closures: buying time until strain-specific vaccine is available} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
218 & preparedness for the spread of influenza: prohibition of traffic, school closure, and vaccination of children in the commuter towns of tokyo & yes & no\\
\cellcolor{gray!6}{219} & \cellcolor{gray!6}{scenarios of diffusion and control of an influenza pandemic in italy} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
220 & time is of the essence: exploring a measles outbreak response vaccination in niamey, niger & yes & no\\
\addlinespace
\cellcolor{gray!6}{221} & \cellcolor{gray!6}{a stochastic equation-based model of the value of international air-travel restrictions for controlling pandemic flu} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
222 & assessing the role of basic control measures, antivirals and vaccine in curtailing pandemic influenza: scenarios for the us, uk and the netherlands & no & not applicable\\
\cellcolor{gray!6}{223} & \cellcolor{gray!6}{deterministic sir (susceptible–infected–removed) models applied to varicella outbreaks} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
224 & effectiveness of movement-prevention regulations to reduce the spread of foot-and-mouth disease in the netherlands & yes & no\\
\cellcolor{gray!6}{225} & \cellcolor{gray!6}{effects of internal border control on spread of pandemic influenza} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
\addlinespace
226 & simple models of influenza progression within a heterogeneous population & no & not applicable\\
\cellcolor{gray!6}{227} & \cellcolor{gray!6}{stochastic model of an influenza epidemic with drug resistance} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
228 & the effect of public health measures on the 1918 influenza pandemic in u.s. cities & yes & yes\\
\cellcolor{gray!6}{229} & \cellcolor{gray!6}{vaccinating in disease-free regions: a vaccine model with application to yellow fever} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
230 & a 'small-world-like' model for comparing interventions aimed at preventing and controlling influenza pandemics & yes & no\\
\addlinespace
\cellcolor{gray!6}{231} & \cellcolor{gray!6}{containing pandemic influenza with antiviral agents: analytical commentary} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
232 & critical response to post-outbreak vaccination against foot-and-mouth disease & yes & no\\
\cellcolor{gray!6}{233} & \cellcolor{gray!6}{mitigation strategies for pandemic influenza in the united states} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
234 & simple models for containment of a pandemic & no & not applicable\\
\cellcolor{gray!6}{235} & \cellcolor{gray!6}{statistical inference in a stochastic epidemic seir model with control intervention: ebola as a case study} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
\addlinespace
236 & strategies for containing an emerging influenza pandemic in southeast asia & yes & no\\
\cellcolor{gray!6}{237} & \cellcolor{gray!6}{modeling alternative mitigation strategies for a hypothetical outbreak of foot-and-mouth disease in the united states} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
238 & modelling vaccination strategies against foot-and-mouth disease & yes & no\\
\cellcolor{gray!6}{239} & \cellcolor{gray!6}{a decision-tree to optimise control measures during the early stage of a foot-and-mouth disease epidemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
240 & effect of control measures on the course of simulated foot and mouth disease epidemics that started on different farm types in various dutch areas & no & not applicable\\
\addlinespace
\cellcolor{gray!6}{241} & \cellcolor{gray!6}{dynamics of the 2001 uk foot and mouth epidemic: stochastic dispersal in a heterogeneous landscape} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
242 & an extended state-transition model for foot-and-mouth disease epidemics in france & no & not applicable\\
\cellcolor{gray!6}{243} & \cellcolor{gray!6}{simulated economic consequences of foot-and-mouth disease epidemics and their public control in france} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
244 & effect of chemotherapy on malaria transmission among yanomami amerindians: simulated consequences of placebo treatment & yes & no\\
\cellcolor{gray!6}{245} & \cellcolor{gray!6}{modelling vaccination strategy against directly transmitted diseases using a series of pulses} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
\addlinespace
246 & mass vaccination to control chickenpox: the influence of zoster & yes & yes\\
\cellcolor{gray!6}{247} & \cellcolor{gray!6}{an evaluation of alternate control strategies for foot-and-mouth disease in australia: a regional approach} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
248 & analysis of a measles epidemic & yes & no\\
\cellcolor{gray!6}{249} & \cellcolor{gray!6}{a model of the transmission of dengue fever with an evaluation of the impact of ultra-low volume (ulv) insecticide applications on dengue epidemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
250 & a discrete-time model with vaccination for a measles epidemic & yes & yes\\
\addlinespace
\cellcolor{gray!6}{251} & \cellcolor{gray!6}{a stochastic model of epidemics in military recruits} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{not applicable}\\
252 & stochastic two-agent epidemic simulation models for a community of families & no & not applicable\\*
\end{longtable}
\endgroup{}
\end{landscape}

\hypertarget{table-8}{%
\subsection{Table 8}\label{table-8}}

This section presents extracted data on whether the simulation code was
made available (simulation\_code\_available) and whether vaccination was
modelled (vax\_modelled).

\begin{landscape}\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}{l>{\raggedright\arraybackslash}p{4cm}l>{\raggedright\arraybackslash}p{4cm}}
\toprule
num & title & simulation\_code\_available & vax\_modelled\\
\midrule
\endfirsthead
\multicolumn{4}{@{}l}{\textit{(continued)}}\\
\toprule
num & title & simulation\_code\_available & vax\_modelled\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{a cholera metapopulation model interlinking migration with intervention strategies - a case study of zimbabwe (2008-2009)} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
2 & a theoretical single-parameter model for urbanisation to study infectious disease spread and interventions & no & yes\\
\cellcolor{gray!6}{3} & \cellcolor{gray!6}{assessing the effects of modeling the spectrum of clinical symptoms on the dynamics and control of ebola} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
4 & dynamical analysis and control strategies in modelling ebola virus disease & no & no\\
\cellcolor{gray!6}{5} & \cellcolor{gray!6}{effect of a hepatitis a vaccination campaign during a hepatitis a outbreak in taiwan, 2015–2017: a modeling study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
6 & evaluating strategies for control of tuberculosis in prisons and prevention of spillover into communities: an observational and modeling study from brazil & no & no\\
\cellcolor{gray!6}{7} & \cellcolor{gray!6}{evaluating the effects of control interventions and estimating the inapparent infections for dengue outbreak in hangzhou, china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
8 & incidence dynamics and investigation of key interventions in a dengue outbreak in ningbo city, china & no & no\\
\cellcolor{gray!6}{9} & \cellcolor{gray!6}{incorporating media data into a model of infectious disease transmission} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
10 & influence of asymptomatic infections for the effectiveness of facemasks during pandemic influenza & no & no\\
\addlinespace
\cellcolor{gray!6}{11} & \cellcolor{gray!6}{mathematical analysis of a cholera infection model with vaccination strategy} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
12 & modeling and stability analysis of epidemic expansion disease ebola virus with implications prevention in population & no & yes\\
\cellcolor{gray!6}{13} & \cellcolor{gray!6}{modeling the effectiveness of respiratory protective devices in reducing influenza outbreak} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
14 & modeling the effects of vaccination and treatment on tuberculosis transmission dynamics & no & yes\\
\cellcolor{gray!6}{15} & \cellcolor{gray!6}{optimal control and cost-effective analysis of the 2017 meningitis outbreak in nigeria} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
16 & optimal control strategies for a two-group epidemic model with vaccination-resource constraints & no & yes\\
\cellcolor{gray!6}{17} & \cellcolor{gray!6}{optimal media reporting intensity on mitigating spread of an emerging infectious disease} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
18 & school dismissal as a pandemic influenza response: when, where and for how long? & no & no\\
\cellcolor{gray!6}{19} & \cellcolor{gray!6}{study on modeling simulation and optimal control method for the transmission risk of the ebola virus} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
20 & transmission dynamics of cholera with hyperinfectious and hypoinfectious vibrios: mathematical modelling and control strategies & no & yes\\
\addlinespace
\cellcolor{gray!6}{21} & \cellcolor{gray!6}{a new epidemics–logistics model: insights into controlling the ebola virus disease in west africa} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
22 & contact reductions from live poultry market closures limit the epidemic of human infections with h7n9 influenza & no & no\\
\cellcolor{gray!6}{23} & \cellcolor{gray!6}{disparities in spread and control of influenza in slums of delhi: findings from an agent-based modelling study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
24 & efficacy of control measures in the control of ebola, liberia 2014–2015 & no & no\\
\cellcolor{gray!6}{25} & \cellcolor{gray!6}{epidemiology of the silent polio outbreak in rahat, israel, based on modeling of environmental surveillance data} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
26 & evaluating costs and health consequences of sick leave strategies against pandemic and seasonal influenza in norway using a dynamic model & no & no\\
\cellcolor{gray!6}{27} & \cellcolor{gray!6}{evaluating vaccination strategies to control foot-and-mouth disease: a country comparison study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
28 & impact of public health responses during a measles outbreak in an amish community in ohio: modeling the dynamics of transmission & no & yes\\
\cellcolor{gray!6}{29} & \cellcolor{gray!6}{initial validation of a simulation model for estimating the impact of serogroup a neisseria meningitidis vaccination in the african meningitis belt} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
30 & logistical constraints lead to an intermediate optimum in outbreak response vaccination & no & yes\\
\addlinespace
\cellcolor{gray!6}{31} & \cellcolor{gray!6}{manipulation of contact network structure and the impact on foot-and-mouth disease transmission} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
32 & mathematical model and intervention strategies for mitigating tuberculosis in the philippines & no & no\\
\cellcolor{gray!6}{33} & \cellcolor{gray!6}{measles outbreak response decision-making under uncertainty: a retrospective analysis} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
34 & modeling the heterogeneity of dengue transmission in a city & no & yes\\
\cellcolor{gray!6}{35} & \cellcolor{gray!6}{modelling the large-scale yellow fever outbreak in luanda, angola, and the impact of vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
36 & quantifying the impact of early-stage contact tracing on controlling ebola diffusion & no & no\\
\cellcolor{gray!6}{37} & \cellcolor{gray!6}{simulation of key interventions for seasonal influenza outbreak control at school in changsha, china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
38 & the impact of regular school closure on seasonal influenza epidemics: a data-driven spatial transmission model for belgium & no & no\\
\cellcolor{gray!6}{39} & \cellcolor{gray!6}{the potential impact of case-area targeted interventions in response to cholera outbreaks: a modeling study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
40 & value of inventory information in allocating a limited supply of influenza vaccine during a pandemic & no & yes\\
\addlinespace
\cellcolor{gray!6}{41} & \cellcolor{gray!6}{an age-structured model for cholera control with vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
42 & an approach to and web-based tool for infectious disease outbreak intervention analysis & no & no\\
\cellcolor{gray!6}{43} & \cellcolor{gray!6}{an economic assessment of foot and mouth disease in japan} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
44 & analysis of an seriv epidemic model of human influenza & no & yes\\
\cellcolor{gray!6}{45} & \cellcolor{gray!6}{control strategies of avian influenza pandemic model with time delay} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
\addlinespace
46 & costs and benefits of including inactivated in addition to oral poliovirus vaccine in outbreak response after cessation of oral poliovirus vaccine use & no & yes\\
\cellcolor{gray!6}{47} & \cellcolor{gray!6}{deriving effective vaccine allocation strategies for pandemic influenza: comparison of an agent-based simulation and a compartmental model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
48 & early rigorous control interventions can largely reduce dengue outbreak magnitude: experience from chaozhou, china & no & no\\
\cellcolor{gray!6}{49} & \cellcolor{gray!6}{effects of reactive social distancing on the 1918 influenza pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
50 & epidemiological and economic impact of pandemic influenza in chicago: priorities for vaccine interventions & no & yes\\
\addlinespace
\cellcolor{gray!6}{51} & \cellcolor{gray!6}{estimating direct and indirect protective effect of influenza vaccination in the united states} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
52 & evaluating the effects of common control measures for influenza a (h1n1) outbreak at school in china: a modeling study & no & yes\\
\cellcolor{gray!6}{53} & \cellcolor{gray!6}{evaluation of strategies to control a potential outbreak of foot-and-mouth disease in sweden} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
54 & impact of a waning vaccine and altered behavior on the spread of influenza & no & yes\\
\cellcolor{gray!6}{55} & \cellcolor{gray!6}{mathematical models for devising the optimal ebola virus disease eradication} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
56 & modeling the role of public health education in ebola virus disease outbreaks in sudan & no & no\\
\cellcolor{gray!6}{57} & \cellcolor{gray!6}{modelling the transmission and control strategies of varicella among school children in shenzhen, china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
58 & optimal and adaptive control of an epidemic model of influenza with unknown parameters & no & yes\\
\cellcolor{gray!6}{59} & \cellcolor{gray!6}{simulating endogenous dynamics of intervention-capacity deployment: ebola outbreak in liberia} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
60 & simulating the potential role of media coverage and infected bats in the 2014 ebola outbreak & no & no\\
\addlinespace
\cellcolor{gray!6}{61} & \cellcolor{gray!6}{a mathematical model of ebola virus disease: using sensitivity analysis to determine effective intervention targets} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
62 & a multi-agent model for adaptive vaccination during infectious disease outbreaks & no & yes\\
\cellcolor{gray!6}{63} & \cellcolor{gray!6}{assessing the efficiency of movement restriction as a control strategy of ebola} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
64 & characterization of outbreak response strategies and potential vaccine stockpile needs for the polio endgame & no & yes\\
\cellcolor{gray!6}{65} & \cellcolor{gray!6}{designing public health policies to mitigate the adverse consequences of rural-urban migration via meta-population modeling} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
66 & dynamic model of influenza with age-structured and media coverage & no & no\\
\cellcolor{gray!6}{67} & \cellcolor{gray!6}{economic evaluation of individual school closure strategies: the hong kong 2009 h1n1 pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
68 & efficient vaccine distribution based on a hybrid compartmental model & no & yes\\
\cellcolor{gray!6}{69} & \cellcolor{gray!6}{epidemiological evaluation of different fmd control strategies in two selected regions in austria} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
70 & evaluating targeted interventions via meta-population models with multi-level mixing & no & yes\\
\addlinespace
\cellcolor{gray!6}{71} & \cellcolor{gray!6}{evaluation of outbreak response immunization in the control of pertussis using agent-based modeling} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
72 & global stability and optimal control for a tuberculosis model with vaccination and treatment & no & yes\\
\cellcolor{gray!6}{73} & \cellcolor{gray!6}{impact on epidemic measles of vaccination campaigns triggered by disease outbreaks or serosurveys: a modeling study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
74 & metapopulation and non-proportional vaccination models overview & no & yes\\
\cellcolor{gray!6}{75} & \cellcolor{gray!6}{model-based comprehensive analysis of school closure policies for mitigating influenza epidemics and pandemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
\addlinespace
76 & modeling ring-vaccination strategies to control ebola virus disease epidemics & no & yes\\
\cellcolor{gray!6}{77} & \cellcolor{gray!6}{modeling the effect of public health resources and alerting on the dynamics of pertussis spread*} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
78 & modeling the impact of behavior change on the spread of ebola & no & no\\
\cellcolor{gray!6}{79} & \cellcolor{gray!6}{modeling the spread of polio in an ipv-vaccinated population: lessons learned from the 2013 silent outbreak in southern israel} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
80 & modelling weekly vector control against dengue in the guangdong province of china & no & no\\
\addlinespace
\cellcolor{gray!6}{81} & \cellcolor{gray!6}{optimal control strategies for the spread of ebola in west africa} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
82 & potential impact of a ventilation intervention for influenza in the context of a dense indoor contact network in hong kong & no & yes\\
\cellcolor{gray!6}{83} & \cellcolor{gray!6}{predicting and evaluating the epidemic trend of ebola virus disease in the 2014-2015 outbreak and the effects of intervention measures} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
84 & projected impact of dengue vaccination in yucatán, mexico & no & yes\\
\cellcolor{gray!6}{85} & \cellcolor{gray!6}{seasonality and the effectiveness of mass vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
86 & simulation optimization for an age-based vaccines distribution strategy against the spread of influenza epidemic & no & yes\\
\cellcolor{gray!6}{87} & \cellcolor{gray!6}{spatiotemporal dynamics of the ebola epidemic in guinea and implications for vaccination and disease elimination: a computational modeling analysis} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
88 & the interplay of vaccination and vector control on small dengue networks & no & yes\\
\cellcolor{gray!6}{89} & \cellcolor{gray!6}{an epidemic patchy model with entry–exit screening} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
90 & assessing the role of voluntary self-isolation in the control of pandemic influenza using a household epidemic model & no & no\\
\addlinespace
\cellcolor{gray!6}{91} & \cellcolor{gray!6}{be-codis: a mathematical model to predict the risk of human diseases spread between countries—validation and application to the 2014–2015 ebola virus disease epidemic} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{no}\\
92 & dengue in madeira island & no & no\\
\cellcolor{gray!6}{93} & \cellcolor{gray!6}{dynamic simulation of a seiqr-v epidemic model based on cellular automata} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
94 & early vaccine availability represents an important public health advance for the control of pandemic influenza & no & yes\\
\cellcolor{gray!6}{95} & \cellcolor{gray!6}{effectiveness of ebola treatment units and community care centers — liberia, september 23–october 31, 2014} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
\addlinespace
96 & evaluation of the benefts and risks of introducing ebola community care centers, sierra leone & no & no\\
\cellcolor{gray!6}{97} & \cellcolor{gray!6}{evidence for emergency vaccination having played a crucial role to control the 1965/66 foot-and-mouth disease outbreak in switzerland} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
98 & measuring the impact of ebola control measures in sierra leone & no & no\\
\cellcolor{gray!6}{99} & \cellcolor{gray!6}{media impact switching surface during an infectious disease outbreak} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
100 & modeling options to manage type 1 wild poliovirus imported into israel in 2013 & no & yes\\
\addlinespace
\cellcolor{gray!6}{101} & \cellcolor{gray!6}{modeling the effect of comprehensive interventions on ebola virus transmission} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
102 & modeling the effect of school closures in a pandemic scenario: exploring two different contact matrices & yes & no\\
\cellcolor{gray!6}{103} & \cellcolor{gray!6}{modelling the effect of early detection of ebola} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
104 & multi-scale modeling for the transmission of influenza and the evaluation of interventions toward it & no & yes\\
\cellcolor{gray!6}{105} & \cellcolor{gray!6}{optimal intervention strategies for a seir control model of ebola epidemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
\addlinespace
106 & predicting the extinction of ebola spreading in liberia due to mitigation strategies & no & no\\
\cellcolor{gray!6}{107} & \cellcolor{gray!6}{school closure strategies for the 2009 hong kong hini influenza pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
108 & spatiotemporal spread of the 2014 outbreak of ebola virus disease in liberia and the effectiveness of non-pharmaceutical interventions: a computational modelling analysis & no & no\\
\cellcolor{gray!6}{109} & \cellcolor{gray!6}{strategies for early vaccination during novel influenza outbreaks} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
110 & the effects of media reports on disease spread and important public health measurements & no & yes\\
\addlinespace
\cellcolor{gray!6}{111} & \cellcolor{gray!6}{the impact of human behavioral changes in 2014 west africa ebola outbreak} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
112 & transmission dynamics and final epidemic size of ebola virus disease outbreaks with varying interventions & no & no\\
\cellcolor{gray!6}{113} & \cellcolor{gray!6}{treatment–donation-stockpile dynamics in ebola convalescent blood transfusion therapy} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
114 & vaccine prioritization for effective pandemic response & no & yes\\
\cellcolor{gray!6}{115} & \cellcolor{gray!6}{a mathematical study of a tb model with treatment interruptions and two latent periods} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
\addlinespace
116 & antiviral prophylaxis and isolation for the control of pandemic influenza & no & no\\
\cellcolor{gray!6}{117} & \cellcolor{gray!6}{assessing the impact of travel restrictions on international spread of the 2014 west african ebola epidemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
118 & assessing the use of antiviral treatment to control influenza & no & yes\\
\cellcolor{gray!6}{119} & \cellcolor{gray!6}{behavior in the time of cholera: evidence from the 2008-2009 cholera outbreak in zimbabwe} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
120 & behavioural response in educated young adults towards influenza a(h1n1)pdm09 & no & no\\
\addlinespace
\cellcolor{gray!6}{121} & \cellcolor{gray!6}{cover your cough! quantifying the benefits of a localized healthy behavior intervention on flu epidemics in washington dc} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
122 & dynamics and control of ebola virus transmission in montserrado, liberia: a mathematical modelling analysis & no & no\\
\cellcolor{gray!6}{123} & \cellcolor{gray!6}{estimating the effectiveness of early control measures through school absenteeism surveillance in observed outbreaks at rural schools in hubei, china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
124 & evaluation of the benefit of emergency vaccination in a foot-and-mouth disease free country with low livestock density & no & yes\\
\cellcolor{gray!6}{125} & \cellcolor{gray!6}{modeling the dynamics of oral poliovirus vaccine cessation} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
126 & modeling the impact of optimal screening on typhoid dynamics & no & no\\
\cellcolor{gray!6}{127} & \cellcolor{gray!6}{modeling the influence of environment and intervention oncholera in haiti} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
128 & sequential bayesian inference in hidden markov stochastic kinetic models with application to detection and response to seasonal epidemics & no & no\\
\cellcolor{gray!6}{129} & \cellcolor{gray!6}{simulating optimal vaccination times during cholera outbreaks} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
130 & the role of vaccination coverage, individual behaviors, and the public health response in the control of measles epidemics: an agent-based simulation for california & no & yes\\
\addlinespace
\cellcolor{gray!6}{131} & \cellcolor{gray!6}{time is (still) of the essence: quantifying the impact of emergency meningitis vaccination response in katsina state, nigeria} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
132 & a perspective on multiple waves of influenza pandemics & no & yes\\
\cellcolor{gray!6}{133} & \cellcolor{gray!6}{an optimal control problem arising from a dengue disease transmission model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
134 & cholera in haiti: reproductive numbers and vaccination coverage estimates & no & yes\\
\cellcolor{gray!6}{135} & \cellcolor{gray!6}{comparing control strategies against foot-and-mouth disease: will vaccination be cost-effective in denmark?} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
136 & cost-effectiveness of influenza control measures: a dynamic transmission model-based analysis & no & yes\\
\cellcolor{gray!6}{137} & \cellcolor{gray!6}{cost-effectiveness of workplace closure and travel restriction for mitigating influenza outbreaks: a network-based simulation} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
138 & decisions on control of foot-and-mouth disease informed using model predictions & no & yes\\
\cellcolor{gray!6}{139} & \cellcolor{gray!6}{dengue in cape verde: vector control and vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
140 & enhancement of collective immunity in tokyo metropolitan area by selective vaccination against an emerging influenza pandemic & no & yes\\
\addlinespace
\cellcolor{gray!6}{141} & \cellcolor{gray!6}{estimated impact of aggressive empirical antiviral treatment in containing an outbreak of pandemic influenza h1n1 in an isolated first nations community} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
142 & multiregional dynamic vaccine allocation during an influenza epidemic & no & yes\\
\cellcolor{gray!6}{143} & \cellcolor{gray!6}{policies to reduce influenza in the workplace: impact assessments using an agent-based model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
144 & transmission dynamics of the 2009 influenza a (h1n1) pandemic in india: the impact of holiday-related school closure & no & no\\
\cellcolor{gray!6}{145} & \cellcolor{gray!6}{vaccination against foot-and-mouth disease: do initial conditions affect its benefit?} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
146 & was mandatory quarantine necessary in china for controlling the 2009 h1n1 pandemic? & no & no\\
\cellcolor{gray!6}{147} & \cellcolor{gray!6}{a contact-network-based simulation model for evaluating interventions under 'what-if' scenarios in epidemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
148 & campus quarantine (fengxiao) for curbing emergent infectious diseases: lessons from mitigating a/h1n1 in xi'an, china & no & no\\
\cellcolor{gray!6}{149} & \cellcolor{gray!6}{dynamic modelling of costs and health consequences of school closure during an influenza pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
150 & effect of vaccines and antivirals during the major 2009 a(h1n1) pandemic wave in norway - and the influence of vaccination timing & no & yes\\
\addlinespace
\cellcolor{gray!6}{151} & \cellcolor{gray!6}{estimating the value of containment strategies in delaying the arrival time of an influenza pandemic: a case study of travel restriction and patient isolation} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
152 & how to minimize the attack rate during multiple influenza outbreaks in a heterogeneous population & no & no\\
\cellcolor{gray!6}{153} & \cellcolor{gray!6}{modeling strategies for controlling h1n1 outbreaks in china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
154 & modeling the effects of h1n1 influenza vaccine distribution in the united states & no & yes\\
\cellcolor{gray!6}{155} & \cellcolor{gray!6}{modeling the impact of air, sea, and land travel restrictions supplemented by other interventions on the emergence of a new influenza pandemic virus} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
\addlinespace
156 & simulating school closure policies for cost effective pandemic decision making & no & no\\
\cellcolor{gray!6}{157} & \cellcolor{gray!6}{the impact of school closures on pandemic influenza: assessing potential repercussions using a seasonal sir model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
158 & vaccination against foot-and-mouth disease i: epidemiological consequences & no & yes\\
\cellcolor{gray!6}{159} & \cellcolor{gray!6}{a deterministic resource scheduling model in epidemic control: a case study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
160 & a model for the a(h1n1) epidemic in mexico, including social isolation & no & no\\
\addlinespace
\cellcolor{gray!6}{161} & \cellcolor{gray!6}{a model to evaluate mass vaccination against pneumococcus as a countermeasure against pandemic influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
162 & a multilayer framework to assess influenza intervention policies & no & no\\
\cellcolor{gray!6}{163} & \cellcolor{gray!6}{a note on the use of optimal control on a discrete time model of influenza dynamics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
164 & a simulation-based assessment of school closure strategies during an influenza epidemic & no & no\\
\cellcolor{gray!6}{165} & \cellcolor{gray!6}{agent-based modeling of the spread of influenza-like illness in an emergency department: a simulation study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
\addlinespace
166 & antiviral treatment for pandemic influenza: assessing potential repercussions using a seasonally forced sir model & no & no\\
\cellcolor{gray!6}{167} & \cellcolor{gray!6}{can antiviral drugs contain pandemic influenza transmission?} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
168 & characterizing the epidemiology of the 2009 influenza a/h1n1 pandemic in mexico & no & no\\
\cellcolor{gray!6}{169} & \cellcolor{gray!6}{cholera epidemic in haiti, 2010: using a transmission model to explain spatial spread of disease and identify optimal control interventions} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
170 & controlling an influenza outbreak in deterministic and stochastic models with the emergence and evolution of drug resistance (model 1) & no & no\\
\addlinespace
\cellcolor{gray!6}{171} & \cellcolor{gray!6}{modeling control strategies for concurrent epidemics of seasonal and pandemic h1n1 influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
172 & modeling the impact of behavior changes on the spread of pandemic influenza & no & yes\\
\cellcolor{gray!6}{173} & \cellcolor{gray!6}{modelling and analysis of influenza a (h1n1) on networks} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
174 & modelling the strategies for age specific vaccination scheduling during influenza pandemic outbreaks & no & yes\\
\cellcolor{gray!6}{175} & \cellcolor{gray!6}{modelling the transmission dynamics and control of the novel 2009 swine influenza (h1n1) pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
176 & planning for the control of pandemic influenza a (h1n1) in los angeles county and the united states & yes & yes\\
\cellcolor{gray!6}{177} & \cellcolor{gray!6}{prioritization of delayed vaccination for pandemic influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
178 & temporal factors in school closure policy for mitigating the spread of influenza & no & no\\
\cellcolor{gray!6}{179} & \cellcolor{gray!6}{the global transmission and control of influenza} & \cellcolor{gray!6}{yes} & \cellcolor{gray!6}{yes}\\
180 & toward effective vaccine deployment: a systematic study & no & yes\\
\addlinespace
\cellcolor{gray!6}{181} & \cellcolor{gray!6}{vaccination against 2009 pandemic h1n1 in a population dynamical model of vancouver, canada: timing is everything} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
182 & a simulation model for the potential spread of foot-and-mouth disease in the castile and leon region of spain & no & yes\\
\cellcolor{gray!6}{183} & \cellcolor{gray!6}{community-based measures for mitigating the 2009 h1n1 pandemic in china} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
184 & effective real-time allocation of pandemic interventions & no & yes\\
\cellcolor{gray!6}{185} & \cellcolor{gray!6}{efficient mitigation strategies for epidemics in rural regions} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
186 & influenza pandemic waves under various mitigation strategies with 2009 h1n1 as a case study & no & yes\\
\cellcolor{gray!6}{187} & \cellcolor{gray!6}{is a mass immunization program for pandemic (h1n1) 2009 good value for money? early evidence from the canadian experience} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
188 & optimal control for pandemic influenza: the role of limited antiviral treatment and isolation & no & no\\
\cellcolor{gray!6}{189} & \cellcolor{gray!6}{optimizing vaccine allocation at different points in time during an epidemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
190 & simulating school closure strategies to mitigate an influenza epidemic & no & no\\
\addlinespace
\cellcolor{gray!6}{191} & \cellcolor{gray!6}{the effect of mask use on the spread of influenza during a pandemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
192 & transmission dynamics of an influenza model with age of infection and antiviral treatment & no & no\\
\cellcolor{gray!6}{193} & \cellcolor{gray!6}{transmission risks and control of foot-and-mouth disease in the netherlands: spatial patterns} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
194 & when should we intervene to control the 2009 influenza a(h1n1) pandemic? & no & no\\
\cellcolor{gray!6}{195} & \cellcolor{gray!6}{adaptive vaccination strategies to mitigate pandemic influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
196 & antiviral resistance and the control of pandemic influenza: the roles of stochasticity, evolution and model details & no & no\\
\cellcolor{gray!6}{197} & \cellcolor{gray!6}{economic evaluation of influenza pandemic mitigation strategies in the united states using a stochastic microsimulation transmission model} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
198 & effectiveness and cost-effectiveness of expanded antiviral prophylaxis and adjuvanted vaccination strategies for an influenza a (h5n1) pandemic & no & yes\\
\cellcolor{gray!6}{199} & \cellcolor{gray!6}{engineering responses to pandemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
200 & epidemiological benefits of more-effective tuberculosis vaccines, drugs, and diagnostics & no & yes\\
\addlinespace
\cellcolor{gray!6}{201} & \cellcolor{gray!6}{household epidemics: modelling effects of early stage vaccination} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
202 & measures against transmission of pandemic h1n1 influenza in japan in 2009: simulation model & no & yes\\
\cellcolor{gray!6}{203} & \cellcolor{gray!6}{modeling vaccination campaigns and the fall/winter 2009 activity of the new a(h1n1) influenza in the northern hemisphere} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
204 & modelling foot and mouth disease & no & yes\\
\cellcolor{gray!6}{205} & \cellcolor{gray!6}{modelling of the influenza a(h1n1)v outbreak in mexico city, april-may 2009, with control sanitary measures} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
\addlinespace
206 & post-exposure prophylaxis during pandemic outbreaks & no & no\\
\cellcolor{gray!6}{207} & \cellcolor{gray!6}{potential for a global dynamic of influenza a (h1n1)} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
208 & reducing the impact of the next influenza pandemic using householdbased public health interventions & no & no\\
\cellcolor{gray!6}{209} & \cellcolor{gray!6}{seasonal transmission potential and activity peaks of the new influenza a(h1n1): a monte carlo likelihood analysis based on human mobility} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
210 & simulation of foot-and-mouth disease spread within an integrated livestock system in texas, usa & no & no\\
\addlinespace
\cellcolor{gray!6}{211} & \cellcolor{gray!6}{the transmissibility and control of pandemic influenza a (h1n1) virus} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
212 & bayesian analysis of severe acute respiratory syndrome: the 2003 hong kong epidemic & no & no\\
\cellcolor{gray!6}{213} & \cellcolor{gray!6}{hepatitis b vaccination and changes in sexual risk behaviour among men who have sex with men in amsterdam} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
214 & mathematical assessment of canada's pandemic influenza preparedness plan & no & yes\\
\cellcolor{gray!6}{215} & \cellcolor{gray!6}{modeling targeted layered containment of an influenza pandemic in the united states} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
\addlinespace
216 & optimal allocation of pandemic influenza vaccine depends on age, risk and timing & no & yes\\
\cellcolor{gray!6}{217} & \cellcolor{gray!6}{pandemic simulation of antivirals plus school closures: buying time until strain-specific vaccine is available} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
218 & preparedness for the spread of influenza: prohibition of traffic, school closure, and vaccination of children in the commuter towns of tokyo & no & yes\\
\cellcolor{gray!6}{219} & \cellcolor{gray!6}{scenarios of diffusion and control of an influenza pandemic in italy} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
220 & time is of the essence: exploring a measles outbreak response vaccination in niamey, niger & no & yes\\
\addlinespace
\cellcolor{gray!6}{221} & \cellcolor{gray!6}{a stochastic equation-based model of the value of international air-travel restrictions for controlling pandemic flu} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
222 & assessing the role of basic control measures, antivirals and vaccine in curtailing pandemic influenza: scenarios for the us, uk and the netherlands & no & yes\\
\cellcolor{gray!6}{223} & \cellcolor{gray!6}{deterministic sir (susceptible–infected–removed) models applied to varicella outbreaks} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
224 & effectiveness of movement-prevention regulations to reduce the spread of foot-and-mouth disease in the netherlands & no & yes\\
\cellcolor{gray!6}{225} & \cellcolor{gray!6}{effects of internal border control on spread of pandemic influenza} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
\addlinespace
226 & simple models of influenza progression within a heterogeneous population & no & no\\
\cellcolor{gray!6}{227} & \cellcolor{gray!6}{stochastic model of an influenza epidemic with drug resistance} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
228 & the effect of public health measures on the 1918 influenza pandemic in u.s. cities & no & no\\
\cellcolor{gray!6}{229} & \cellcolor{gray!6}{vaccinating in disease-free regions: a vaccine model with application to yellow fever} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
230 & a 'small-world-like' model for comparing interventions aimed at preventing and controlling influenza pandemics & no & yes\\
\addlinespace
\cellcolor{gray!6}{231} & \cellcolor{gray!6}{containing pandemic influenza with antiviral agents: analytical commentary} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
232 & critical response to post-outbreak vaccination against foot-and-mouth disease & no & yes\\
\cellcolor{gray!6}{233} & \cellcolor{gray!6}{mitigation strategies for pandemic influenza in the united states} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
234 & simple models for containment of a pandemic & no & yes\\
\cellcolor{gray!6}{235} & \cellcolor{gray!6}{statistical inference in a stochastic epidemic seir model with control intervention: ebola as a case study} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
\addlinespace
236 & strategies for containing an emerging influenza pandemic in southeast asia & no & no\\
\cellcolor{gray!6}{237} & \cellcolor{gray!6}{modeling alternative mitigation strategies for a hypothetical outbreak of foot-and-mouth disease in the united states} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
238 & modelling vaccination strategies against foot-and-mouth disease & no & yes\\
\cellcolor{gray!6}{239} & \cellcolor{gray!6}{a decision-tree to optimise control measures during the early stage of a foot-and-mouth disease epidemic} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
240 & effect of control measures on the course of simulated foot and mouth disease epidemics that started on different farm types in various dutch areas & no & yes\\
\addlinespace
\cellcolor{gray!6}{241} & \cellcolor{gray!6}{dynamics of the 2001 uk foot and mouth epidemic: stochastic dispersal in a heterogeneous landscape} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
242 & an extended state-transition model for foot-and-mouth disease epidemics in france & no & yes\\
\cellcolor{gray!6}{243} & \cellcolor{gray!6}{simulated economic consequences of foot-and-mouth disease epidemics and their public control in france} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
244 & effect of chemotherapy on malaria transmission among yanomami amerindians: simulated consequences of placebo treatment & no & no\\
\cellcolor{gray!6}{245} & \cellcolor{gray!6}{modelling vaccination strategy against directly transmitted diseases using a series of pulses} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
\addlinespace
246 & mass vaccination to control chickenpox: the influence of zoster & no & yes\\
\cellcolor{gray!6}{247} & \cellcolor{gray!6}{an evaluation of alternate control strategies for foot-and-mouth disease in australia: a regional approach} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{yes}\\
248 & analysis of a measles epidemic & no & yes\\
\cellcolor{gray!6}{249} & \cellcolor{gray!6}{a model of the transmission of dengue fever with an evaluation of the impact of ultra-low volume (ulv) insecticide applications on dengue epidemics} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
250 & a discrete-time model with vaccination for a measles epidemic & no & yes\\
\addlinespace
\cellcolor{gray!6}{251} & \cellcolor{gray!6}{a stochastic model of epidemics in military recruits} & \cellcolor{gray!6}{no} & \cellcolor{gray!6}{no}\\
252 & stochastic two-agent epidemic simulation models for a community of families & no & yes\\*
\end{longtable}
\endgroup{}
\end{landscape}

\end{document}

### 2023-10-18 manuscript/submission2/submission_files/supplementary/S2_File.tex
Generate latex version of files

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[a4paper,left=3cm,right=2cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage{makecell}

\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review},
  pdfauthor={James M. Azam, Xiaoxi Pang, Elisha B. Are, Juliet R.C. Pulliam, Matthew J. Ferrari},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Outbreak response models of vaccine-preventable diseases in
humans (1970-2019) - A systematic review}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Supplementary file (analysis for main manuscript)}
\author{James M. Azam, Xiaoxi Pang, Elisha B. Are, Juliet R.C. Pulliam,
Matthew J. Ferrari}
\date{}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\hypertarget{general-analyses}{%
\section{General analyses}\label{general-analyses}}

\hypertarget{number-of-studies-included}{%
\subsection{Number of studies
included}\label{number-of-studies-included}}

The review involved 252 published between 1971 and 2019.

\hypertarget{breakdown-of-studies-before-and-after-2005}{%
\subsection{Breakdown of studies before and after
2005}\label{breakdown-of-studies-before-and-after-2005}}

\begin{tabular}{ll}
\toprule
before\_2005 & num\_of\_studies \\
\midrule
no & 218 (96.0\%) \\
yes & 9 (4.0\%) 
\end{tabular}

\hypertarget{publications-per-year}{%
\subsection{Publications per year}\label{publications-per-year}}

\includegraphics[width=\textwidth,height=\textheight]{S2_File_files/figure-latex/unnamed-chunk-5-1}

\hypertarget{human-vaccine-preventable-diseases}{%
\section{Human vaccine-preventable
diseases}\label{human-vaccine-preventable-diseases}}

\hypertarget{analysis-of-collaboration-type-compositions}{%
\subsection{Analysis of collaboration type
compositions}\label{analysis-of-collaboration-type-compositions}}

\hypertarget{aggregated}{%
\subsubsection{Aggregated}\label{aggregated}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-6}Number of studies per collaboration type (Human VPDs)}
\centering
\begin{tabular}[t]{ll}
\toprule
collab\_type & n\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{56.8\% (129)}\\
mixed & 43.2\%  (98)\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{100.0\% (227)}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{number-of-studies-per-year-and-broken-down-by-collaboration-types}{%
\subsubsection{Number of studies per year and broken down by
collaboration
types}\label{number-of-studies-per-year-and-broken-down-by-collaboration-types}}

\begin{table}

\caption{\label{tab:unnamed-chunk-7}Breakdown of studies per year by collaboration types}
\centering
\begin{tabular}[t]{lrrr}
\toprule
year\_aggreg & mixed & purely\_academic & Total\\
\midrule
2005 & 5 & 4 & 9\\

2006 & 2 & 3 & 5\\

2007 & 4 & 4 & 8\\

2008 & 8 & 1 & 9\\

2009 & 8 & 7 & 15\\

2010 & 7 & 4 & 11\\

2011 & 7 & 16 & 23\\

2012 & 4 & 7 & 11\\

2013 & 3 & 9 & 12\\

2014 & 6 & 10 & 16\\

2015 & 11 & 14 & 25\\

2016 & 10 & 17 & 27\\

2017 & 8 & 10 & 18\\

2018 & 9 & 9 & 18\\

2019 & 6 & 14 & 20\\

Total & 98 & 129 & 227\\
 \bottomrule
\end{tabular}
\end{table}

\begin{tabular}{ll}
\toprule 
author\_affiliation\_type & num\_of\_studies\\
 \midrule
academic\_institutions & 129  (56.8\%)\\
academic\_institutions + government\_institutions & 55  (24.2\%)\\
academic\_institutions + NGO & 17   (7.5\%)\\
academic\_institutions + government\_institutions + NGO & 14   (6.2\%)\\
NGO & 5   (2.2\%)\\
government\_institutions & 5   (2.2\%)\\
government\_institutions + NGO & 2   (0.9\%)\\
Total & 227 (100.0\%)\\
\bottomrule
\end{tabular}

\hypertarget{number-of-publications-per-year-by-collaboration-type}{%
\subsubsection{Number of publications per year by collaboration
type}\label{number-of-publications-per-year-by-collaboration-type}}

\includegraphics[width=\textwidth,height=\textheight]{S2_File_files/figure-latex/unnamed-chunk-9-1}

Even though non-academic collaborations increased over time, the share
of total publications per year over time decreased.

\hypertarget{proportion-of-the-total-publications-per-year-by-collaboration-type}{%
\subsubsection{Proportion of the total publications per year by
collaboration
type}\label{proportion-of-the-total-publications-per-year-by-collaboration-type}}

\includegraphics[width=\textwidth,height=\textheight]{S2_File_files/figure-latex/unnamed-chunk-10-1}

\hypertarget{mixed-collaborations-with-and-without-academics}{%
\subsubsection{Mixed collaborations with and without
academics}\label{mixed-collaborations-with-and-without-academics}}

\includegraphics[width=\textwidth,height=\textheight]{S2_File_files/figure-latex/unnamed-chunk-11-1}

\hypertarget{geographic-analyses}{%
\subsection{Geographic analyses}\label{geographic-analyses}}

\hypertarget{location-studied}{%
\subsubsection{Location studied}\label{location-studied}}

\hypertarget{real-versus-hypothetical}{%
\paragraph{Real versus hypothetical}\label{real-versus-hypothetical}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-12}Number of studies per location type}
\centering
\begin{tabular}[t]{ll}
\toprule
location\_type & n\\
\midrule
\cellcolor{gray!6}{real} & \cellcolor{gray!6}{78.9\% (195)}\\
none & 21.1\%  (52)\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{100.0\% (247)}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{larger-than-one-country}{%
\paragraph{Larger than one country}\label{larger-than-one-country}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-13}Number of studies per location larger than one country}
\centering
\begin{tabular}[t]{ll}
\toprule
country\_studied & n\\
\midrule
\cellcolor{gray!6}{west\_africa} & \cellcolor{gray!6}{47.4\%  (9)}\\
global & 36.8\%  (7)\\
\cellcolor{gray!6}{northern\_hemisphere} & \cellcolor{gray!6}{5.3\%  (1)}\\
southeast\_asia & 5.3\%  (1)\\
\cellcolor{gray!6}{who\_southeast\_asia\_region} & \cellcolor{gray!6}{5.3\%  (1)}\\
\addlinespace
Total & 100.0\% (19)\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{countries-studied}{%
\paragraph{Countries studied}\label{countries-studied}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-14}Number of studies per country}
\centering
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{ll}
\toprule
country\_studied & num\_of\_studies\\
\midrule
\cellcolor{gray!6}{US} & \cellcolor{gray!6}{21.6\%  (38)}\\
CN & 10.8\%  (19)\\
\cellcolor{gray!6}{CA} & \cellcolor{gray!6}{6.2\%  (11)}\\
LR & 5.7\%  (10)\\
\cellcolor{gray!6}{HK} & \cellcolor{gray!6}{5.1\%   (9)}\\
\addlinespace
MX & 5.1\%   (9)\\
\cellcolor{gray!6}{GB} & \cellcolor{gray!6}{2.8\%   (5)}\\
SL & 2.8\%   (5)\\
\cellcolor{gray!6}{BR} & \cellcolor{gray!6}{2.3\%   (4)}\\
GN & 2.3\%   (4)\\
\addlinespace
\cellcolor{gray!6}{HT} & \cellcolor{gray!6}{2.3\%   (4)}\\
JP & 2.3\%   (4)\\
\cellcolor{gray!6}{NL} & \cellcolor{gray!6}{2.3\%   (4)}\\
NO & 2.3\%   (4)\\
\cellcolor{gray!6}{IL} & \cellcolor{gray!6}{1.7\%   (3)}\\
\addlinespace
NG & 1.7\%   (3)\\
\cellcolor{gray!6}{TW} & \cellcolor{gray!6}{1.7\%   (3)}\\
DK & 1.1\%   (2)\\
\cellcolor{gray!6}{IN} & \cellcolor{gray!6}{1.1\%   (2)}\\
IT & 1.1\%   (2)\\
\addlinespace
\cellcolor{gray!6}{LY} & \cellcolor{gray!6}{1.1\%   (2)}\\
NE & 1.1\%   (2)\\
\cellcolor{gray!6}{SG} & \cellcolor{gray!6}{1.1\%   (2)}\\
ZW & 1.1\%   (2)\\
\cellcolor{gray!6}{AO} & \cellcolor{gray!6}{0.6\%   (1)}\\
\addlinespace
AU & 0.6\%   (1)\\
\cellcolor{gray!6}{BE} & \cellcolor{gray!6}{0.6\%   (1)}\\
BF & 0.6\%   (1)\\
\cellcolor{gray!6}{CD} & \cellcolor{gray!6}{0.6\%   (1)}\\
CO & 0.6\%   (1)\\
\addlinespace
\cellcolor{gray!6}{CV} & \cellcolor{gray!6}{0.6\%   (1)}\\
ET & 0.6\%   (1)\\
\cellcolor{gray!6}{FO} & \cellcolor{gray!6}{0.6\%   (1)}\\
FR & 0.6\%   (1)\\
\cellcolor{gray!6}{GR} & \cellcolor{gray!6}{0.6\%   (1)}\\
\addlinespace
HU & 0.6\%   (1)\\
\cellcolor{gray!6}{IS} & \cellcolor{gray!6}{0.6\%   (1)}\\
NP & 0.6\%   (1)\\
\cellcolor{gray!6}{PH} & \cellcolor{gray!6}{0.6\%   (1)}\\
PT & 0.6\%   (1)\\
\addlinespace
\cellcolor{gray!6}{SD} & \cellcolor{gray!6}{0.6\%   (1)}\\
SE & 0.6\%   (1)\\
\cellcolor{gray!6}{TD} & \cellcolor{gray!6}{0.6\%   (1)}\\
TZ & 0.6\%   (1)\\
\cellcolor{gray!6}{VE} & \cellcolor{gray!6}{0.6\%   (1)}\\
\addlinespace
YE & 0.6\%   (1)\\
\cellcolor{gray!6}{ZM} & \cellcolor{gray!6}{0.6\%   (1)}\\
Total & 100.0\% (176)\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{continents-studied}{%
\paragraph{Continents studied}\label{continents-studied}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-15}Number of studies per continent}
\centering
\begin{tabular}[t]{ll}
\toprule
continent\_studied & num\_of\_studies\\
\midrule
\cellcolor{gray!6}{americas} & \cellcolor{gray!6}{36.4\%  (68)}\\
asia & 25.1\%  (47)\\
\cellcolor{gray!6}{africa} & \cellcolor{gray!6}{24.6\%  (46)}\\
europe & 13.4\%  (25)\\
\cellcolor{gray!6}{oceania} & \cellcolor{gray!6}{0.5\%   (1)}\\
\addlinespace
Total & 100.0\% (187)\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{connection-of-authors-to-the-studied-locations}{%
\subsection{Connection of authors to the studied
locations}\label{connection-of-authors-to-the-studied-locations}}

\begingroup\fontsize{8}{10}\selectfont

\begin{longtable}[t]{llllr}
\caption{\label{tab:unnamed-chunk-16}Studies with at least one author affiliation in the location studied}\\
\toprule
collab\_type & country\_studied & yes & no & Total\\
\midrule
\endfirsthead
\caption[]{Studies with at least one author affiliation in the location studied \textit{(continued)}}\\
\toprule
collab\_type & country\_studied & yes & no & Total\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{US} & \cellcolor{gray!6}{94.7\%  (18)} & \cellcolor{gray!6}{5.3\%  (1)} & \cellcolor{gray!6}{19}\\
purely\_academic & CN & 100.0\%   (8) & 0.0\%  (0) & 8\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{HK} & \cellcolor{gray!6}{77.8\%   (7)} & \cellcolor{gray!6}{22.2\%  (2)} & \cellcolor{gray!6}{9}\\
purely\_academic & CA & 75.0\%   (3) & 25.0\%  (1) & 4\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{TW} & \cellcolor{gray!6}{100.0\%   (3)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{3}\\
\addlinespace
purely\_academic & BR & 100.0\%   (2) & 0.0\%  (0) & 2\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{GB} & \cellcolor{gray!6}{66.7\%   (2)} & \cellcolor{gray!6}{33.3\%  (1)} & \cellcolor{gray!6}{3}\\
purely\_academic & MX & 66.7\%   (2) & 33.3\%  (1) & 3\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{CO} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{1}\\
purely\_academic & GR & 100.0\%   (1) & 0.0\%  (0) & 1\\
\addlinespace
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{HU} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{1}\\
purely\_academic & IL & 100.0\%   (1) & 0.0\%  (0) & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{IN} & \cellcolor{gray!6}{50.0\%   (1)} & \cellcolor{gray!6}{50.0\%  (1)} & \cellcolor{gray!6}{2}\\
purely\_academic & JP & 100.0\%   (1) & 0.0\%  (0) & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{NL} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{1}\\
\addlinespace
purely\_academic & NO & 100.0\%   (1) & 0.0\%  (0) & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{PH} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{1}\\
purely\_academic & PT & 100.0\%   (1) & 0.0\%  (0) & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{SE} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{1}\\
purely\_academic & SG & 100.0\%   (1) & 0.0\%  (0) & 1\\
\addlinespace
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{TZ} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{1}\\
purely\_academic & LR & 0.0\%   (0) & 100.0\%  (5) & 5\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{HT} & \cellcolor{gray!6}{0.0\%   (0)} & \cellcolor{gray!6}{100.0\%  (3)} & \cellcolor{gray!6}{3}\\
purely\_academic & SL & 0.0\%   (0) & 100.0\%  (3) & 3\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{GN} & \cellcolor{gray!6}{0.0\%   (0)} & \cellcolor{gray!6}{100.0\%  (2)} & \cellcolor{gray!6}{2}\\
\addlinespace
purely\_academic & LY & 0.0\%   (0) & 100.0\%  (2) & 2\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{ZW} & \cellcolor{gray!6}{0.0\%   (0)} & \cellcolor{gray!6}{100.0\%  (2)} & \cellcolor{gray!6}{2}\\
purely\_academic & AO & 0.0\%   (0) & 100.0\%  (1) & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{CD} & \cellcolor{gray!6}{0.0\%   (0)} & \cellcolor{gray!6}{100.0\%  (1)} & \cellcolor{gray!6}{1}\\
purely\_academic & CV & 0.0\%   (0) & 100.0\%  (1) & 1\\
\addlinespace
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{DK} & \cellcolor{gray!6}{0.0\%   (0)} & \cellcolor{gray!6}{100.0\%  (1)} & \cellcolor{gray!6}{1}\\
purely\_academic & ET & 0.0\%   (0) & 100.0\%  (1) & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{FO} & \cellcolor{gray!6}{0.0\%   (0)} & \cellcolor{gray!6}{100.0\%  (1)} & \cellcolor{gray!6}{1}\\
purely\_academic & NG & 0.0\%   (0) & 100.0\%  (1) & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{SD} & \cellcolor{gray!6}{0.0\%   (0)} & \cellcolor{gray!6}{100.0\%  (1)} & \cellcolor{gray!6}{1}\\
\addlinespace
mixed & US & 100.0\%  (18) & 0.0\%  (0) & 18\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{CN} & \cellcolor{gray!6}{100.0\%  (11)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{11}\\
mixed & CA & 100.0\%   (7) & 0.0\%  (0) & 7\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{MX} & \cellcolor{gray!6}{83.3\%   (5)} & \cellcolor{gray!6}{16.7\%  (1)} & \cellcolor{gray!6}{6}\\
mixed & JP & 100.0\%   (3) & 0.0\%  (0) & 3\\
\addlinespace
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{NL} & \cellcolor{gray!6}{100.0\%   (3)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{3}\\
mixed & NO & 100.0\%   (3) & 0.0\%  (0) & 3\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{BR} & \cellcolor{gray!6}{100.0\%   (2)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{2}\\
mixed & GB & 100.0\%   (2) & 0.0\%  (0) & 2\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{IL} & \cellcolor{gray!6}{100.0\%   (2)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{2}\\
\addlinespace
mixed & IT & 100.0\%   (2) & 0.0\%  (0) & 2\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{LR} & \cellcolor{gray!6}{20.0\%   (1)} & \cellcolor{gray!6}{80.0\%  (4)} & \cellcolor{gray!6}{5}\\
mixed & AU & 100.0\%   (1) & 0.0\%  (0) & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{BE} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{1}\\
mixed & BF & 100.0\%   (1) & 0.0\%  (0) & 1\\
\addlinespace
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{DK} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{1}\\
mixed & FR & 100.0\%   (1) & 0.0\%  (0) & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{IS} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{1}\\
mixed & NE & 50.0\%   (1) & 50.0\%  (1) & 2\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{SG} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{1}\\
\addlinespace
mixed & TD & 100.0\%   (1) & 0.0\%  (0) & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{VE} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{1}\\
mixed & GN & 0.0\%   (0) & 100.0\%  (2) & 2\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{NG} & \cellcolor{gray!6}{0.0\%   (0)} & \cellcolor{gray!6}{100.0\%  (2)} & \cellcolor{gray!6}{2}\\
mixed & SL & 0.0\%   (0) & 100.0\%  (2) & 2\\
\addlinespace
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{HT} & \cellcolor{gray!6}{0.0\%   (0)} & \cellcolor{gray!6}{100.0\%  (1)} & \cellcolor{gray!6}{1}\\
mixed & NP & 0.0\%   (0) & 100.0\%  (1) & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{YE} & \cellcolor{gray!6}{0.0\%   (0)} & \cellcolor{gray!6}{100.0\%  (1)} & \cellcolor{gray!6}{1}\\
mixed & ZM & 0.0\%   (0) & 100.0\%  (1) & 1\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{-} & \cellcolor{gray!6}{72.6\% (127)} & \cellcolor{gray!6}{27.4\% (48)} & \cellcolor{gray!6}{175}\\*
\end{longtable}
\endgroup{}

\hypertarget{author-affiliation-in-the-studied-location-overall}{%
\subsubsection{Author affiliation in the studied location
(overall)}\label{author-affiliation-in-the-studied-location-overall}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-17}At least one author with an affiliation in the studied location}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & yes & no & Total\\
\midrule
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{84.0\%  (63)} & \cellcolor{gray!6}{16.0\% (12)} & \cellcolor{gray!6}{75}\\
purely\_academic & 67.1\%  (55) & 32.9\% (27) & 82\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{75.2\% (118)} & \cellcolor{gray!6}{24.8\% (39)} & \cellcolor{gray!6}{157}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{diseases-studied-per-collab-type}{%
\subsection{Diseases studied per collab
type}\label{diseases-studied-per-collab-type}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-18}Number of studies per disease and collaboration type}
\centering
\begin{tabular}[t]{lllr}
\toprule
disease & purely\_academic & mixed & Total\\
\midrule
\cellcolor{gray!6}{Influenza} & \cellcolor{gray!6}{54.1\%  (73)} & \cellcolor{gray!6}{45.9\%  (62)} & \cellcolor{gray!6}{135}\\
Ebola & 70.6\%  (24) & 29.4\%  (10) & 34\\
\cellcolor{gray!6}{Dengue} & \cellcolor{gray!6}{50.0\%   (6)} & \cellcolor{gray!6}{50.0\%   (6)} & \cellcolor{gray!6}{12}\\
Cholera & 81.8\%   (9) & 18.2\%   (2) & 11\\
\cellcolor{gray!6}{Measles} & \cellcolor{gray!6}{36.4\%   (4)} & \cellcolor{gray!6}{63.6\%   (7)} & \cellcolor{gray!6}{11}\\
\addlinespace
Poliomyelitis & 28.6\%   (2) & 71.4\%   (5) & 7\\
\cellcolor{gray!6}{Tuberculosis} & \cellcolor{gray!6}{83.3\%   (5)} & \cellcolor{gray!6}{16.7\%   (1)} & \cellcolor{gray!6}{6}\\
Varicella & 50.0\%   (2) & 50.0\%   (2) & 4\\
\cellcolor{gray!6}{Meningococcal meningitis} & \cellcolor{gray!6}{33.3\%   (1)} & \cellcolor{gray!6}{66.7\%   (2)} & \cellcolor{gray!6}{3}\\
Pertussis & 50.0\%   (1) & 50.0\%   (1) & 2\\
\addlinespace
\cellcolor{gray!6}{Pneumococcal disease} & \cellcolor{gray!6}{50.0\%   (1)} & \cellcolor{gray!6}{50.0\%   (1)} & \cellcolor{gray!6}{2}\\
Yellow fever & 50.0\%   (1) & 50.0\%   (1) & 2\\
\cellcolor{gray!6}{Hepatitis a} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{0.0\%   (0)} & \cellcolor{gray!6}{1}\\
Rubella & 100.0\%   (1) & 0.0\%   (0) & 1\\
\cellcolor{gray!6}{Typhoid} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{0.0\%   (0)} & \cellcolor{gray!6}{1}\\
\addlinespace
Hepatitis b & 0.0\%   (0) & 100.0\%   (1) & 1\\
\cellcolor{gray!6}{Malaria} & \cellcolor{gray!6}{0.0\%   (0)} & \cellcolor{gray!6}{100.0\%   (1)} & \cellcolor{gray!6}{1}\\
Mumps & 0.0\%   (0) & 100.0\%   (1) & 1\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{56.2\% (132)} & \cellcolor{gray!6}{43.8\% (103)} & \cellcolor{gray!6}{235}\\
\bottomrule
\end{tabular}
\end{table}

\includegraphics[width=\textwidth,height=\textheight]{S2_File_files/figure-latex/unnamed-chunk-19-1}

\hypertarget{interventions}{%
\subsection{Interventions}\label{interventions}}

\hypertarget{types-of-interventions}{%
\subsubsection{Types of interventions}\label{types-of-interventions}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-20}Number of studies per intervention categories}
\centering
\begin{tabular}[t]{llllr}
\toprule
collab\_type & no\_vax & vax\_as\_mixed\_intervention & vax\_compared\_to\_others & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{51.9\%  (67)} & \cellcolor{gray!6}{38.0\% (49)} & \cellcolor{gray!6}{10.1\% (13)} & \cellcolor{gray!6}{129}\\
mixed & 41.8\%  (41) & 44.9\% (44) & 13.3\% (13) & 98\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{47.6\% (108)} & \cellcolor{gray!6}{41.0\% (93)} & \cellcolor{gray!6}{11.5\% (26)} & \cellcolor{gray!6}{227}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{diseases-and-interventions}{%
\subsection{Diseases and
interventions}\label{diseases-and-interventions}}

\begin{longtable}{llr}
\toprule
disease & intervention\_modelled & num\_of\_studies\\
\midrule
\endhead
cholera & vaccination & 10\\

cholera & hygiene & 2\\

cholera & antibiotic\_prophylaxis & 1\\

cholera & point-of-use\_water\_treatment & 1\\

cholera & quarantine & 1\\

cholera & treatment & 1\\

cholera & water\_treatment & 1\\

dengue & vaccination & 5\\

dengue & larvicides & 4\\

dengue & adult\_vector\_control & 1\\

dengue & education & 1\\

dengue & isolation & 1\\

dengue & larva\_control & 1\\

dengue & mosquito\_repellent & 1\\

dengue & reducing\_mosquito\_density & 1\\

dengue & sterile\_insect\_technique & 1\\

dengue & treatment & 1\\

dengue & 
\makecell[l]{
	ultra-low\_volume\_\\
	(ulv)\_insecticide\_applications
	} & 1\\

dengue & vector\_control & 1\\

ebola & isolation & 9\\

ebola & safe\_burial & 9\\

ebola & vaccination & 7\\

ebola & quarantine & 5\\

ebola & treatment & 5\\

ebola & beds & 4\\

ebola & contact\_tracing & 4\\

ebola & ebola\_treatment\_units & 4\\

ebola & education & 4\\

ebola & behavioural\_change & 2\\

ebola & community\_care\_centers & 2\\

ebola & distancing & 2\\

ebola & hospitalization & 2\\

ebola & media\_campaign & 2\\

ebola & travel\_restriction & 2\\

ebola & PPE\_other\_1 & 1\\

ebola & capturing\_infected\_bats & 1\\

ebola & control\_the\_propagation & 1\\

ebola & early\_detection\_and\_diagnosis & 1\\

ebola & effective\_hospitalization & 1\\

ebola & household\_protective\_kits & 1\\

ebola & hygiene & 1\\

ebola & interventions\_to\_reduce\_transmission & 1\\

ebola & ppe\_other\_1 & 1\\

ebola & preventing\_importation & 1\\

ebola & protected\_sex\_with\_condoms & 1\\

	ebola & 
	\makecell[l]{
		reduce\_the\_number\_of\_\\
		susceptible\_and\_\\
		infected\_and\_simultaneously\\
		\_increase\_recovered
	} & 1\\

ebola & reducing\_transmission & 1\\

ebola &
\makecell[l]{several\_interventions\\
	\_to\_reduce\_transmission
	} & 1\\

ebola & social\_mobilisation & 1\\

hepatitis\_a & vaccination & 1\\

hepatitis\_b & vaccination & 1\\

influenza & vaccination & 65\\

influenza & school\_closure & 36\\

influenza & antiviral\_prophylaxis & 26\\

influenza & isolation & 16\\

influenza & distancing & 14\\

influenza & treatment & 10\\

influenza & quarantine & 9\\

influenza & travel\_restriction & 9\\

influenza & face\_masks & 8\\

influenza & antiviral\_treatment & 6\\

influenza & media\_campaign & 6\\

influenza & work\_closure & 6\\

influenza & behavioural\_change & 5\\

influenza & handwashing & 2\\

influenza & hospitalization & 2\\

influenza & hygiene & 2\\

influenza & screening & 2\\

influenza & unclear & 2\\

influenza & ventilation & 2\\

influenza & close\_live\_poultry\_market & 1\\

influenza & closure\_of\_public\_places & 1\\

influenza & contact\_tracing & 1\\

influenza & 
\makecell[l]{
	direct\_measures\_to\_\\
	reduce\_infectiousness
	} & 1\\

influenza & disease\_control & 1\\

influenza & 
\makecell[l]{
	high\_efficiency\_\\
	particulate\_air\_filtration
	} & 1\\

influenza & hygiene\_precaution & 1\\

influenza & mass\_immunization\_program & 1\\

influenza & onboard\_quarantine\_inspection & 1\\

influenza & paid\_sick\_days & 1\\

influenza & pallative\_care & 1\\

influenza & post-exposure\_prophylaxis & 1\\

influenza & prevention\_of\_mass\_gatherings & 1\\

influenza & prohibition\_of\_traffic & 1\\

influenza &
\makecell[l]{
	prophylactic\_measures\_\\
	to\_mitigate\_outbreak\\
	\_seasonality\_and\\
	\_morbidity
} & 1\\

influenza &
\makecell[l]{
	 reduction\_of\_\\
	 community\_transmission
} & 1\\

influenza & reduction\_of\_hospital\_transmission & 1\\

influenza & respiratory\_protective\_devices & 1\\

influenza & sanitary\_measures & 1\\

influenza & school\_absenteeism\_surveillance & 1\\

influenza & several\_combinations\_of\_interventions & 1\\

influenza & sick\_leave\_strategy & 1\\

influenza & stay-at-home & 1\\

influenza & stay-at-home\_behaviour & 1\\

influenza & stay\_home & 1\\

influenza & therapeutics & 1\\

influenza & ultraviolet\_germicidal\_irradiation & 1\\

malaria & drugs & 1\\

malaria & treatment & 1\\

measles & vaccination & 8\\

measles & behavioural\_change & 1\\

measles & contact\_tracing & 1\\

measles & isolation & 1\\

measles & quarantine & 1\\

meningococcal\_meningitis & vaccination & 3\\

meningococcal\_meningitis & PPE\_other\_1 & 1\\

pertussis & vaccination & 2\\

pertussis & contact\_tracing & 1\\

pneumococcal\_disease & treatment & 1\\

poliomyelitis & vaccination & 7\\

poliomyelitis & school\_closure & 1\\

rubella & vaccination & 1\\

tuberculosis & treatment & 4\\

tuberculosis & vaccination & 3\\

tuberculosis & active\_case\_finding & 1\\

tuberculosis & case\_holding & 1\\

tuberculosis & diagnostics & 1\\

tuberculosis & 
\makecell[l]{
	distancing\_from\\
	\_infectious\_individuals
} & 
1\\

tuberculosis & exit\_screening & 1\\

tuberculosis & latent\_case\_finding & 1\\

tuberculosis &
\makecell[l]{
	passive\_diagnosis\_active\\
	\_diagnosis\_and\\
	\_combined\_above
} & 1\\

tuberculosis & prison:\_entry\_screening & 1\\

tuberculosis & secondary\_ipt & 1\\

typhoid & screening & 1\\

varicella & vaccination & 3\\

varicella & isolation & 1\\

yellow\_fever & vaccination & 2\\
\bottomrule
\end{longtable}

\hypertarget{diseases-and-interventions-top-2-per-disease}{%
\subsubsection{Diseases and interventions (top 2 per
disease)}\label{diseases-and-interventions-top-2-per-disease}}

\begin{table}

\caption{\label{tab:unnamed-chunk-22}Top 2 most studied intervention per disease}
\centering
\begin{tabular}{llr}
\toprule
disease & intervention\_modelled & num\_of\_studies\\
\midrule
cholera & vaccination & 10\\

cholera & hygiene & 2\\

dengue & vaccination & 5\\

dengue & larvicides & 4\\

ebola & isolation & 9\\

ebola & safe\_burial & 9\\

hepatitis\_a & vaccination & 1\\

hepatitis\_b & vaccination & 1\\

influenza & vaccination & 65\\

influenza & school\_closure & 36\\

malaria & drugs & 1\\

malaria & treatment & 1\\

measles & vaccination & 8\\

measles & behavioural\_change & 1\\

meningococcal\_meningitis & vaccination & 3\\

meningococcal\_meningitis & PPE\_other\_1 & 1\\

pertussis & vaccination & 2\\

pertussis & contact\_tracing & 1\\

pneumococcal\_disease & treatment & 1\\

poliomyelitis & vaccination & 7\\

poliomyelitis & school\_closure & 1\\

rubella & vaccination & 1\\

tuberculosis & treatment & 4\\

tuberculosis & vaccination & 3\\

typhoid & screening & 1\\

varicella & vaccination & 3\\

varicella & isolation & 1\\

yellow\_fever & vaccination & 2\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{impact-of-vaccination}{%
\subsubsection{Impact of vaccination}\label{impact-of-vaccination}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-23}Conclusions about impact of vaccination}
\centering
\begin{tabular}[t]{llllr}
\toprule
collab\_type & yes & no & inconclusive & Total\\
\midrule
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{53.8\%  (7)} & \cellcolor{gray!6}{38.5\%  (5)} & \cellcolor{gray!6}{7.7\% (1)} & \cellcolor{gray!6}{13}\\
purely\_academic & 46.2\%  (6) & 38.5\%  (5) & 15.4\% (2) & 13\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{50.0\% (13)} & \cellcolor{gray!6}{38.5\% (10)} & \cellcolor{gray!6}{11.5\% (3)} & \cellcolor{gray!6}{26}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{modelling-objectives}{%
\subsection{Modelling objectives}\label{modelling-objectives}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-27}Study objectives by collaboration type}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & prospective\_analysis & retrospective\_analysis & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{97 (75.2\%)} & \cellcolor{gray!6}{32 (24.8\%)} & \cellcolor{gray!6}{129}\\
mixed & 68 (69.4\%) & 30 (30.6\%) & 98\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{165 (72.7\%)} & \cellcolor{gray!6}{62 (27.3\%)} & \cellcolor{gray!6}{227}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{outbreak-types}{%
\subsection{Outbreak types}\label{outbreak-types}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-28}outbreak types by collaboration type}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & hypothetical\_outbreak & real\_outbreak & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{52.7\%  (68)} & \cellcolor{gray!6}{47.3\%  (61)} & \cellcolor{gray!6}{129}\\
mixed & 45.9\%  (45) & 54.1\%  (53) & 98\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{49.8\% (113)} & \cellcolor{gray!6}{50.2\% (114)} & \cellcolor{gray!6}{227}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{individual-heterogeneity-agent-based-versus-compartmental-models}{%
\subsection{Individual heterogeneity: agent-based versus compartmental
models}\label{individual-heterogeneity-agent-based-versus-compartmental-models}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-30}How individuals were represented}
\centering
\begin{tabular}[t]{llllr}
\toprule
collab\_type & compartments & agents & individuals\_representation\_other & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{80.6\% (104)} & \cellcolor{gray!6}{18.6\% (24)} & \cellcolor{gray!6}{0.8\% (1)} & \cellcolor{gray!6}{129}\\
mixed & 76.5\%  (75) & 21.4\% (21) & 2.0\% (2) & 98\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{78.9\% (179)} & \cellcolor{gray!6}{19.8\% (45)} & \cellcolor{gray!6}{1.3\% (3)} & \cellcolor{gray!6}{227}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{spatial-heterogeneity}{%
\subsection{Spatial heterogeneity}\label{spatial-heterogeneity}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-31}Was space explicitly represented in the model}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & no & yes & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{74.4\%  (96)} & \cellcolor{gray!6}{25.6\% (33)} & \cellcolor{gray!6}{129}\\
mixed & 67.3\%  (66) & 32.7\% (32) & 98\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{71.4\% (162)} & \cellcolor{gray!6}{28.6\% (65)} & \cellcolor{gray!6}{227}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{model-dynamics-deterministic-vs-stochastic}{%
\subsection{Model dynamics: deterministic vs
stochastic}\label{model-dynamics-deterministic-vs-stochastic}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-32}Model dynamics (deterministic versus stochastic)}
\centering
\begin{tabular}[t]{llllr}
\toprule
collab\_type & both & deterministic & stochastic & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{5.4\%  (7)} & \cellcolor{gray!6}{71.3\%  (92)} & \cellcolor{gray!6}{23.3\% (30)} & \cellcolor{gray!6}{129}\\
mixed & 7.1\%  (7) & 53.1\%  (52) & 39.8\% (39) & 98\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{6.2\% (14)} & \cellcolor{gray!6}{63.4\% (144)} & \cellcolor{gray!6}{30.4\% (69)} & \cellcolor{gray!6}{227}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{outcomes-measured}{%
\subsection{Outcomes measured}\label{outcomes-measured}}

\begin{longtable}[t]{llr}
\caption{\label{tab:unnamed-chunk-33}Outcomes studied by the collaboration types}\\
\toprule
collab\_type & outcome\_measured & num\_of\_studies\\
\midrule
\endfirsthead
\caption[]{Outcomes studied by the collaboration types \textit{(continued)}}\\
\toprule
collab\_type & outcome\_measured & num\_of\_studies\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{final\_epidemic\_size} & \cellcolor{gray!6}{55}\\
purely\_academic & attack\_rate & 29\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{timing\_of\_peak} & \cellcolor{gray!6}{20}\\
purely\_academic & cost & 18\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{outbreak\_duration\_and\_timing} & \cellcolor{gray!6}{15}\\
\addlinespace
purely\_academic & cases\_averted & 12\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{intervention\_coverage} & \cellcolor{gray!6}{7}\\
purely\_academic & peak\_magnitude & 7\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{incidence} & \cellcolor{gray!6}{6}\\
purely\_academic & basic\_reproduction\_number & 5\\
\addlinespace
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{case\_fatality} & \cellcolor{gray!6}{5}\\
purely\_academic & cumulative\_incidence & 5\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{hospitalizations} & \cellcolor{gray!6}{4}\\
purely\_academic & campaign\_duration & 3\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{control\_reproduction\_number} & \cellcolor{gray!6}{3}\\
\addlinespace
purely\_academic & cumulative\_deaths & 3\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{deaths\_averted} & \cellcolor{gray!6}{3}\\
purely\_academic & cumulative\_attack\_rate & 2\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{cumulative\_cases} & \cellcolor{gray!6}{2}\\
purely\_academic & cumulative\_infections & 2\\
\addlinespace
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{peak\_size} & \cellcolor{gray!6}{2}\\
purely\_academic & total\_deaths & 2\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{
	\makecell[l]{and\_the\_individuals\_that\\
		\_have\_recovered\_and\_\\
		are\_immune\_to\_evd
	}
} & \cellcolor{gray!6}{1}\\
purely\_academic & cumulative\_hospital\_cases & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{date\_of\_first\_reported\_cases} & \cellcolor{gray!6}{1}\\
\addlinespace
purely\_academic & deaths & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{first\_arrival\_time} & \cellcolor{gray!6}{1}\\
purely\_academic & force\_of\_infection & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{funerals} & \cellcolor{gray!6}{1}\\
purely\_academic & geometric\_mean\_number\_of\_infected\_hosts & 1\\
\addlinespace
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{hospital\_notifications} & \cellcolor{gray!6}{1}\\
purely\_academic & household\_reproduction\_number & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{household\_reproduction\_number\_for} & \cellcolor{gray!6}{1}\\
purely\_academic & i\_and\_r\_curve & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{incremental\_cost\_effectiveness\_ratio} & \cellcolor{gray!6}{1}\\
\addlinespace
purely\_academic & infection\_rate & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{isolated\_or\_quarantined\_individuals} & \cellcolor{gray!6}{1}\\
purely\_academic & mortality & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{mortality\_rate} & \cellcolor{gray!6}{1}\\
purely\_academic & net\_benefits & 1\\
\addlinespace
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{number\_of\_exposed\_and\_infectious\_individuals} & \cellcolor{gray!6}{1}\\
purely\_academic & number\_of\_individuals\_in\_s & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{number\_of\_latently\_infected\_individuals} & \cellcolor{gray!6}{1}\\
purely\_academic & number\_of\_simulations\_with\_epidemic\_outbreak & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{number\_of\_susceptible\_individuals} & \cellcolor{gray!6}{1}\\
\addlinespace
purely\_academic & number\_of\_times\_countermeasures\_are\_started & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{peak\_daily\_infection} & \cellcolor{gray!6}{1}\\
purely\_academic & peak\_day & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{peak\_incidence} & \cellcolor{gray!6}{1}\\
purely\_academic & peak\_infection\_rate & 1\\
\addlinespace
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{peak\_infections} & \cellcolor{gray!6}{1}\\
purely\_academic & prevalence & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{proportion\_of\_susceptible\_individuals} & \cellcolor{gray!6}{1}\\
purely\_academic & 
\makecell[l]{
	proportion\_of\_time\_that\\
	\_infected\_size\\
	\_is\_above\_a\_\\
	threshold\_number\_of\\
	\_infecteds
	} & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{qualys} & \cellcolor{gray!6}{1}\\
\addlinespace
purely\_academic & r0 & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{reproduction\_number} & \cellcolor{gray!6}{1}\\
purely\_academic & return\_on\_investment & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{risk\_of\_death} & \cellcolor{gray!6}{1}\\
purely\_academic & total\_fraction\_of\_infected\_and\_exposed & 1\\
\addlinespace
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{transmission} & \cellcolor{gray!6}{1}\\
purely\_academic & vaccine\_doses & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{final\_epidemic\_size} & \cellcolor{gray!6}{31}\\
mixed & attack\_rate & 29\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{cases\_averted} & \cellcolor{gray!6}{22}\\
\addlinespace
mixed & timing\_of\_peak & 16\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{outbreak\_duration\_and\_timing} & \cellcolor{gray!6}{13}\\
mixed & hospitalizations & 9\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{incidence} & \cellcolor{gray!6}{7}\\
mixed & intervention\_coverage & 7\\
\addlinespace
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{case\_fatality} & \cellcolor{gray!6}{5}\\
mixed & cost & 5\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{cumulative\_incidence} & \cellcolor{gray!6}{5}\\
mixed & r0 & 5\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{peak\_magnitude} & \cellcolor{gray!6}{4}\\
\addlinespace
mixed & cumulative\_attack\_rate & 3\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{cumulative\_cases} & \cellcolor{gray!6}{3}\\
mixed & peak\_size & 3\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{qualys} & \cellcolor{gray!6}{3}\\
mixed & total\_deaths & 3\\
\addlinespace
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{cumulative\_deaths} & \cellcolor{gray!6}{2}\\
mixed & mortality\_rate & 2\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{peak\_incidence} & \cellcolor{gray!6}{2}\\
mixed & population\_immunity & 2\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{average\_expected\_number\_of\_cases} & \cellcolor{gray!6}{1}\\
\addlinespace
mixed & average\_number\_of\_weeks\_lost & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{campaign\_duration} & \cellcolor{gray!6}{1}\\
mixed & case\_reproduction\_number & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{cumulative\_infected} & \cellcolor{gray!6}{1}\\
mixed & dalys & 1\\
\addlinespace
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{deaths} & \cellcolor{gray!6}{1}\\
mixed & deaths\_averted & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{delay\_between\_epidemics} & \cellcolor{gray!6}{1}\\
mixed & duration\_of\_infection & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{effective\_reproduction\_number} & \cellcolor{gray!6}{1}\\
\addlinespace
mixed & effectiveness\_of\_vaccination\_strategies & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{extra\_protective\_rate} & \cellcolor{gray!6}{1}\\
mixed & immunization\_threshold & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{incremental\_cost\_effectiveness\_ratio} & \cellcolor{gray!6}{1}\\
mixed & incremental\_cost\_effectiveness\_ratio\_(icer) & 1\\
\addlinespace
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{incremental\_net\_benefits} & \cellcolor{gray!6}{1}\\
mixed & indirect\_protection & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{instantaneous\_reproduction\_number} & \cellcolor{gray!6}{1}\\
mixed & maximum\_number\_of\_symptomatic\_cases\_per\_day & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{morbidity} & \cellcolor{gray!6}{1}\\
\addlinespace
mixed & number\_of\_contacts\_traced & 1\\
\cellcolor{gray!6}{mixed} &
\cellcolor{gray!6}{
	\makecell[l]{
		number\_of\_courses\\
		\_of\_drug\_required\_to\\
		\_achieve\_containment
		}
} & 
\cellcolor{gray!6}{1}\\
mixed & number\_of\_deaths & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{paralytic\_incidence} & \cellcolor{gray!6}{1}\\
mixed & peak\_difference & 1\\
\addlinespace
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{prevalence\_of\_infection} & \cellcolor{gray!6}{1}\\
mixed & probability\_of\_preventing\_a\_large\_outbreak & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{resistant\_cases} & \cellcolor{gray!6}{1}\\
mixed & risk\_of\_case\_importation & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{time\_of\_detection} & \cellcolor{gray!6}{1}\\
\addlinespace
mixed & total\_vaccinated & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{vaccination\_coverage} & \cellcolor{gray!6}{1}\\
mixed & vaccine-derived\_virus\_prevalence & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{years\_of\_life\_lost} & \cellcolor{gray!6}{1}\\*
\end{longtable}

\hypertarget{top-6-outcomes-measured-by-collaboration-type}{%
\subsubsection{Top 6 outcomes measured by collaboration
type}\label{top-6-outcomes-measured-by-collaboration-type}}

\begin{longtable}[t]{lll}
\caption{\label{tab:unnamed-chunk-34}Top 6 outcomes studied by the collaboration types}\\
\toprule
collab\_type & outcome\_measured & num\_of\_studies\\
\midrule
\endfirsthead
\caption[]{Top 6 outcomes studied by the collaboration types \textit{(continued)}}\\
\toprule
collab\_type & outcome\_measured & num\_of\_studies\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{final\_epidemic\_size} & \cellcolor{gray!6}{22.0\%  (55)}\\
purely\_academic & attack\_rate & 11.6\%  (29)\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{timing\_of\_peak} & \cellcolor{gray!6}{8.0\%  (20)}\\
purely\_academic & cost & 7.2\%  (18)\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{outbreak\_duration\_and\_timing} & \cellcolor{gray!6}{6.0\%  (15)}\\
\addlinespace
purely\_academic & cases\_averted & 4.8\%  (12)\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{final\_epidemic\_size} & \cellcolor{gray!6}{14.4\%  (31)}\\
mixed & attack\_rate & 13.4\%  (29)\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{cases\_averted} & \cellcolor{gray!6}{10.2\%  (22)}\\
mixed & timing\_of\_peak & 7.4\%  (16)\\
\addlinespace
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{outbreak\_duration\_and\_timing} & \cellcolor{gray!6}{6.0\%  (13)}\\
mixed & hospitalizations & 4.2\%   (9)\\*
\end{longtable}

\hypertarget{parametrization-methods}{%
\subsection{Parametrization methods}\label{parametrization-methods}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-35}How model parameters are obtained}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llllllllr}
\toprule
collab\_type & literature and expert\_opinion & literature and fitted & literature & literature and expert\_opinion and fitted & expert\_opinion & fitted & expert\_opinion and fitted & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{27.1\% (35)} & \cellcolor{gray!6}{21.7\% (28)} & \cellcolor{gray!6}{17.8\% (23)} & \cellcolor{gray!6}{10.1\% (13)} & \cellcolor{gray!6}{14.0\% (18)} & \cellcolor{gray!6}{7.0\%  (9)} & \cellcolor{gray!6}{2.3\% (3)} & \cellcolor{gray!6}{129}\\
mixed & 24.5\% (24) & 28.6\% (28) & 14.3\% (14) & 19.4\% (19) & 7.1\%  (7) & 5.1\%  (5) & 1.0\% (1) & 98\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{26.0\% (59)} & \cellcolor{gray!6}{24.7\% (56)} & \cellcolor{gray!6}{16.3\% (37)} & \cellcolor{gray!6}{14.1\% (32)} & \cellcolor{gray!6}{11.0\% (25)} & \cellcolor{gray!6}{6.2\% (14)} & \cellcolor{gray!6}{1.8\% (4)} & \cellcolor{gray!6}{227}\\
\bottomrule
\end{tabular}}
\end{table}

\hypertarget{validation-methods}{%
\subsection{Validation methods}\label{validation-methods}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-36}How the model's performance is assessed}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllllr}
\toprule
collab\_type & none & data & another\_model & data\_and\_another\_model & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{71.3\%  (92)} & \cellcolor{gray!6}{27.9\% (36)} & \cellcolor{gray!6}{0.8\% (1)} & \cellcolor{gray!6}{0.0\% (0)} & \cellcolor{gray!6}{129}\\
mixed & 53.1\%  (52) & 42.9\% (42) & 3.1\% (3) & 1.0\% (1) & 98\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{63.4\% (144)} & \cellcolor{gray!6}{34.4\% (78)} & \cellcolor{gray!6}{1.8\% (4)} & \cellcolor{gray!6}{0.4\% (1)} & \cellcolor{gray!6}{227}\\
\bottomrule
\end{tabular}}
\end{table}

\hypertarget{sensitivity-analysis}{%
\subsection{Sensitivity analysis}\label{sensitivity-analysis}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-38}Sensitivity analysis}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & no & yes & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{58.1\%  (75)} & \cellcolor{gray!6}{41.9\%  (54)} & \cellcolor{gray!6}{129}\\
mixed & 48.0\%  (47) & 52.0\%  (51) & 98\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{53.7\% (122)} & \cellcolor{gray!6}{46.3\% (105)} & \cellcolor{gray!6}{227}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{data-use-and-data-availability}{%
\subsection{Data use and data
availability}\label{data-use-and-data-availability}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-39}Data accessibility}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & yes & no & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{82.5\% (52)} & \cellcolor{gray!6}{17.5\% (11)} & \cellcolor{gray!6}{63}\\
mixed & 58.7\% (37) & 41.3\% (26) & 63\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{70.6\% (89)} & \cellcolor{gray!6}{29.4\% (37)} & \cellcolor{gray!6}{126}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{code-availability}{%
\subsection{Code availability}\label{code-availability}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-40}Code availability}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & no & yes & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{98.4\% (127)} & \cellcolor{gray!6}{1.6\% (2)} & \cellcolor{gray!6}{129}\\
mixed & 98.0\%  (96) & 2.0\% (2) & 98\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{98.2\% (223)} & \cellcolor{gray!6}{1.8\% (4)} & \cellcolor{gray!6}{227}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{foot-and-mouth-disease-fmd}{%
\section{Foot and mouth disease
(FMD)}\label{foot-and-mouth-disease-fmd}}

\hypertarget{unique-combinations-of-author-affiliation-types}{%
\subsection{Unique combinations of author affiliation
types}\label{unique-combinations-of-author-affiliation-types}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-42}Number of studies by author affiliation type combination}
\centering
\begin{tabular}[t]{ll}
\toprule
author\_affiliation\_type & n\\
\midrule
\cellcolor{gray!6}{academic\_institutions} & \cellcolor{gray!6}{44.0\% (11)}\\
academic\_institutions + government\_institutions & 24.0\%  (6)\\
\cellcolor{gray!6}{government\_institutions} & \cellcolor{gray!6}{20.0\%  (5)}\\
academic\_institutions + government\_institutions + NGO & 8.0\%  (2)\\
\cellcolor{gray!6}{government\_institutions + NGO} & \cellcolor{gray!6}{4.0\%  (1)}\\
\addlinespace
Total & 100.0\% (25)\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{collaboration-types-aggregated}{%
\subsection{Collaboration types
(aggregated)}\label{collaboration-types-aggregated}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-43}Number of studies per collaboration type}
\centering
\begin{tabular}[t]{ll}
\toprule
collab\_type & n\\
\midrule
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{56.0\% (14)}\\
purely\_academic & 44.0\% (11)\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{100.0\% (25)}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{proportions-of-the-total-publications-per-year-by-collaboration-type}{%
\subsubsection{Proportions of the total publications per year by
collaboration
type}\label{proportions-of-the-total-publications-per-year-by-collaboration-type}}

\includegraphics[width=\textwidth,height=\textheight]{S2_File_files/figure-latex/unnamed-chunk-44-1}

\hypertarget{absolute-number-of-publications-per-year-by-collaboration-type}{%
\subsubsection{Absolute number of publications per year by collaboration
type}\label{absolute-number-of-publications-per-year-by-collaboration-type}}

\includegraphics[width=\textwidth,height=\textheight]{S2_File_files/figure-latex/unnamed-chunk-45-1}

\hypertarget{geographic-analyses-1}{%
\subsection{Geographic analyses}\label{geographic-analyses-1}}

\hypertarget{connection-of-authors-to-the-studied-locations-1}{%
\subsubsection{Connection of authors to the studied
locations}\label{connection-of-authors-to-the-studied-locations-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-46}Studies with at least one author affiliation in the location studied}
\centering
\begin{tabular}[t]{llllr}
\toprule
collab\_type & country\_studied & yes & no & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{NL} & \cellcolor{gray!6}{100.0\%  (4)} & \cellcolor{gray!6}{0.0\% (0)} & \cellcolor{gray!6}{4}\\
purely\_academic & DK & 100.0\%  (2) & 0.0\% (0) & 2\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{GB} & \cellcolor{gray!6}{66.7\%  (2)} & \cellcolor{gray!6}{33.3\% (1)} & \cellcolor{gray!6}{3}\\
purely\_academic & ES & 100.0\%  (1) & 0.0\% (0) & 1\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{US} & \cellcolor{gray!6}{100.0\%  (1)} & \cellcolor{gray!6}{0.0\% (0)} & \cellcolor{gray!6}{1}\\
\addlinespace
mixed & GB & 100.0\%  (3) & 0.0\% (0) & 3\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{AU} & \cellcolor{gray!6}{100.0\%  (2)} & \cellcolor{gray!6}{0.0\% (0)} & \cellcolor{gray!6}{2}\\
mixed & CH & 100.0\%  (2) & 0.0\% (0) & 2\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{FR} & \cellcolor{gray!6}{100.0\%  (2)} & \cellcolor{gray!6}{0.0\% (0)} & \cellcolor{gray!6}{2}\\
mixed & US & 100.0\%  (2) & 0.0\% (0) & 2\\
\addlinespace
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{AT} & \cellcolor{gray!6}{100.0\%  (1)} & \cellcolor{gray!6}{0.0\% (0)} & \cellcolor{gray!6}{1}\\
mixed & CA & 100.0\%  (1) & 0.0\% (0) & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{JP} & \cellcolor{gray!6}{100.0\%  (1)} & \cellcolor{gray!6}{0.0\% (0)} & \cellcolor{gray!6}{1}\\
mixed & NL & 100.0\%  (1) & 0.0\% (0) & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{NZ} & \cellcolor{gray!6}{100.0\%  (1)} & \cellcolor{gray!6}{0.0\% (0)} & \cellcolor{gray!6}{1}\\
\addlinespace
mixed & SE & 100.0\%  (1) & 0.0\% (0) & 1\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{UY} & \cellcolor{gray!6}{0.0\%  (0)} & \cellcolor{gray!6}{100.0\% (1)} & \cellcolor{gray!6}{1}\\
Total & - & 93.1\% (27) & 6.9\% (2) & 29\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{aggregated-1}{%
\subsubsection{Aggregated}\label{aggregated-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-47}Studies with at least one author affiliation in the location studied}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & yes & no & Total\\
\midrule
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{92.9\% (13)} & \cellcolor{gray!6}{7.1\% (1)} & \cellcolor{gray!6}{14}\\
purely\_academic & 90.9\% (10) & 9.1\% (1) & 11\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{92.0\% (23)} & \cellcolor{gray!6}{8.0\% (2)} & \cellcolor{gray!6}{25}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{interventions-1}{%
\subsection{Interventions}\label{interventions-1}}

\hypertarget{types-of-interventions-1}{%
\subsubsection{Types of interventions}\label{types-of-interventions-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-48}Number of studies per intervention type}
\centering
\begin{tabular}[t]{llllr}
\toprule
collab\_type & vax\_compared\_to\_others & vax\_as\_mixed\_intervention & no\_vax & Total\\
\midrule
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{71.4\% (10)} & \cellcolor{gray!6}{14.3\% (2)} & \cellcolor{gray!6}{14.3\% (2)} & \cellcolor{gray!6}{14}\\
purely\_academic & 36.4\%  (4) & 45.5\% (5) & 18.2\% (2) & 11\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{56.0\% (14)} & \cellcolor{gray!6}{28.0\% (7)} & \cellcolor{gray!6}{16.0\% (4)} & \cellcolor{gray!6}{25}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{impact-of-vaccination-1}{%
\subsubsection{Impact of vaccination}\label{impact-of-vaccination-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-49}Conclusions about impact of vaccination}
\centering
\begin{tabular}[t]{llllr}
\toprule
collab\_type & no & inconclusive & yes & Total\\
\midrule
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{60.0\% (6)} & \cellcolor{gray!6}{20.0\% (2)} & \cellcolor{gray!6}{20.0\% (2)} & \cellcolor{gray!6}{10}\\
purely\_academic & 50.0\% (2) & 50.0\% (2) & 0.0\% (0) & 4\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{57.1\% (8)} & \cellcolor{gray!6}{28.6\% (4)} & \cellcolor{gray!6}{14.3\% (2)} & \cellcolor{gray!6}{14}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{modelling-objectives-1}{%
\subsection{Modelling objectives}\label{modelling-objectives-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-50}Study objectives by collaboration type}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & prospective\_analysis & retrospective\_analysis & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{63.6\%  (7)} & \cellcolor{gray!6}{36.4\% (4)} & \cellcolor{gray!6}{11}\\
mixed & 71.4\% (10) & 28.6\% (4) & 14\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{68.0\% (17)} & \cellcolor{gray!6}{32.0\% (8)} & \cellcolor{gray!6}{25}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{outbreak-types-1}{%
\subsection{Outbreak types}\label{outbreak-types-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-51}Study objectives by collaboration type}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & hypothetical\_outbreak & real\_outbreak & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{72.7\%  (8)} & \cellcolor{gray!6}{27.3\% (3)} & \cellcolor{gray!6}{11}\\
mixed & 64.3\%  (9) & 35.7\% (5) & 14\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{68.0\% (17)} & \cellcolor{gray!6}{32.0\% (8)} & \cellcolor{gray!6}{25}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{individual-heterogeneity-agent-based-versus-compartmental-models-1}{%
\subsection{Individual heterogeneity: agent-based versus compartmental
models}\label{individual-heterogeneity-agent-based-versus-compartmental-models-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-52}How individuals are represented}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & agents & compartments & Total\\
\midrule
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{71.4\% (10)} & \cellcolor{gray!6}{28.6\% (4)} & \cellcolor{gray!6}{14}\\
purely\_academic & 81.8\%  (9) & 18.2\% (2) & 11\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{76.0\% (19)} & \cellcolor{gray!6}{24.0\% (6)} & \cellcolor{gray!6}{25}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{spatial-heterogeneity-1}{%
\subsection{Spatial heterogeneity}\label{spatial-heterogeneity-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-53}Models with spatial structure}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & yes & no & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{81.8\%  (9)} & \cellcolor{gray!6}{18.2\% (2)} & \cellcolor{gray!6}{11}\\
mixed & 64.3\%  (9) & 35.7\% (5) & 14\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{72.0\% (18)} & \cellcolor{gray!6}{28.0\% (7)} & \cellcolor{gray!6}{25}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{model-dynamics-deterministic-vs-stochastic-1}{%
\subsection{Model dynamics: deterministic vs
stochastic}\label{model-dynamics-deterministic-vs-stochastic-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-54}Model dynamics (deterministic versus stochastic)}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & deterministic & stochastic & Total\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{36.4\%  (4)} & \cellcolor{gray!6}{63.6\%  (7)} & \cellcolor{gray!6}{11}\\
mixed & 50.0\%  (7) & 50.0\%  (7) & 14\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{44.0\% (11)} & \cellcolor{gray!6}{56.0\% (14)} & \cellcolor{gray!6}{25}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{outcomes-measured-1}{%
\subsection{Outcomes measured}\label{outcomes-measured-1}}

\begin{longtable}[t]{lll}
\caption{\label{tab:unnamed-chunk-55}Model outcomes by collaboration type}\\
\toprule
collab\_type & outcome\_measured & num\_of\_studies\\
\midrule
\endfirsthead
\caption[]{Model outcomes by collaboration type \textit{(continued)}}\\
\toprule
collab\_type & outcome\_measured & num\_of\_studies\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{outbreak\_duration\_and\_timing} & \cellcolor{gray!6}{11.6\%  (8)}\\
purely\_academic & final\_epidemic\_size & 5.8\%  (4)\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{cost} & \cellcolor{gray!6}{2.9\%  (2)}\\
purely\_academic & number\_of\_infected\_farms & 2.9\%  (2)\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{attack\_rate} & \cellcolor{gray!6}{1.4\%  (1)}\\
\addlinespace
purely\_academic & basic\_reproduction\_number & 1.4\%  (1)\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{effective\_reproduction\_number} & \cellcolor{gray!6}{1.4\%  (1)}\\
purely\_academic & export\_losses & 1.4\%  (1)\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{intervention\_coverage} & \cellcolor{gray!6}{1.4\%  (1)}\\
purely\_academic & lives\_saved & 1.4\%  (1)\\
\addlinespace
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{number\_of\_depopulated\_herds} & \cellcolor{gray!6}{1.4\%  (1)}\\
purely\_academic & number\_of\_depopulated\_premises & 1.4\%  (1)\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{number\_of\_farms\_in\_control\_zones} & \cellcolor{gray!6}{1.4\%  (1)}\\
purely\_academic & number\_of\_infected\_herds & 1.4\%  (1)\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{number\_of\_infected\_premises} & \cellcolor{gray!6}{1.4\%  (1)}\\
\addlinespace
purely\_academic & number\_of\_quarantined\_premises & 1.4\%  (1)\\
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{the\_number\_of\_pre-emptively\_slaughtered\_farms} & \cellcolor{gray!6}{1.4\%  (1)}\\
mixed & outbreak\_duration\_and\_timing & 14.5\% (10)\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{final\_epidemic\_size} & \cellcolor{gray!6}{13.0\%  (9)}\\
mixed & cost & 7.2\%  (5)\\
\addlinespace
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{compensation} & \cellcolor{gray!6}{1.4\%  (1)}\\
mixed & control\_costs & 1.4\%  (1)\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{employment\_effects} & \cellcolor{gray!6}{1.4\%  (1)}\\
mixed & export\_losses & 1.4\%  (1)\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{income\_effects} & \cellcolor{gray!6}{1.4\%  (1)}\\
\addlinespace
mixed & intervention\_coverage & 1.4\%  (1)\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{number\_of\_animals\_culled} & \cellcolor{gray!6}{1.4\%  (1)}\\
mixed & number\_of\_herds\_slaughtered & 1.4\%  (1)\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{number\_of\_herds\_vaccinated} & \cellcolor{gray!6}{1.4\%  (1)}\\
mixed & number\_of\_premises\_culled & 1.4\%  (1)\\
\addlinespace
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{output\_effects} & \cellcolor{gray!6}{1.4\%  (1)}\\
mixed & total\_number\_of\_animals\_culled & 1.4\%  (1)\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{total\_number\_of\_herds\_culled} & \cellcolor{gray!6}{1.4\%  (1)}\\
mixed & total\_number\_of\_herds\_surveilled & 1.4\%  (1)\\
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{total\_number\_of\_herds\_vaccinated} & \cellcolor{gray!6}{1.4\%  (1)}\\
\addlinespace
mixed & total\_number\_of\_infected\_premises & 1.4\%  (1)\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{-} & \cellcolor{gray!6}{100.0\% (69)}\\*
\end{longtable}

\hypertarget{parametrization-methods-1}{%
\subsection{Parametrization methods}\label{parametrization-methods-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-57}Model parametrization methods}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llllllllr}
\toprule
collab\_type & literature and expert\_opinion & literature and expert\_opinion and fitted & fitted & literature & literature and fitted & expert\_opinion & expert\_opinion and fitted & Total\\
\midrule
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{42.9\% (6)} & \cellcolor{gray!6}{7.1\% (1)} & \cellcolor{gray!6}{21.4\% (3)} & \cellcolor{gray!6}{21.4\% (3)} & \cellcolor{gray!6}{0.0\% (0)} & \cellcolor{gray!6}{7.1\% (1)} & \cellcolor{gray!6}{0.0\% (0)} & \cellcolor{gray!6}{14}\\
purely\_academic & 9.1\% (1) & 27.3\% (3) & 18.2\% (2) & 9.1\% (1) & 18.2\% (2) & 9.1\% (1) & 9.1\% (1) & 11\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{28.0\% (7)} & \cellcolor{gray!6}{16.0\% (4)} & \cellcolor{gray!6}{20.0\% (5)} & \cellcolor{gray!6}{16.0\% (4)} & \cellcolor{gray!6}{8.0\% (2)} & \cellcolor{gray!6}{8.0\% (2)} & \cellcolor{gray!6}{4.0\% (1)} & \cellcolor{gray!6}{25}\\
\bottomrule
\end{tabular}}
\end{table}

\hypertarget{validation-methods-1}{%
\subsection{Validation methods}\label{validation-methods-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-58}Model validation methods}
\centering
\begin{tabular}[t]{llllr}
\toprule
collab\_type & none & data & another\_model & Total\\
\midrule
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{71.4\% (10)} & \cellcolor{gray!6}{21.4\% (3)} & \cellcolor{gray!6}{7.1\% (1)} & \cellcolor{gray!6}{14}\\
purely\_academic & 72.7\%  (8) & 27.3\% (3) & 0.0\% (0) & 11\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{72.0\% (18)} & \cellcolor{gray!6}{24.0\% (6)} & \cellcolor{gray!6}{4.0\% (1)} & \cellcolor{gray!6}{25}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{sensitivity-analysis-1}{%
\subsection{Sensitivity analysis}\label{sensitivity-analysis-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-59}Sensitivity analysis}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & no & yes & Total\\
\midrule
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{71.4\% (10)} & \cellcolor{gray!6}{28.6\%  (4)} & \cellcolor{gray!6}{14}\\
purely\_academic & 36.4\%  (4) & 63.6\%  (7) & 11\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{56.0\% (14)} & \cellcolor{gray!6}{44.0\% (11)} & \cellcolor{gray!6}{25}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{data-use-and-data-availability-1}{%
\subsection{Data use and data
availability}\label{data-use-and-data-availability-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-60}Data accessibility}
\centering
\begin{tabular}[t]{lllr}
\toprule
collab\_type & no & yes & Total\\
\midrule
\cellcolor{gray!6}{mixed} & \cellcolor{gray!6}{100.0\%  (6)} & \cellcolor{gray!6}{0.0\% (0)} & \cellcolor{gray!6}{6}\\
purely\_academic & 62.5\%  (5) & 37.5\% (3) & 8\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{78.6\% (11)} & \cellcolor{gray!6}{21.4\% (3)} & \cellcolor{gray!6}{14}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{code-availability-1}{%
\subsection{Code availability}\label{code-availability-1}}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-61}Code availability}
\centering
\begin{tabular}[t]{ll}
\toprule
collab\_type & no\\
\midrule
\cellcolor{gray!6}{purely\_academic} & \cellcolor{gray!6}{44.0\% (11)}\\
mixed & 56.0\% (14)\\
\cellcolor{gray!6}{Total} & \cellcolor{gray!6}{100.0\% (25)}\\
\bottomrule
\end{tabular}
\end{table}

\end{document}

### 2023-10-18 analyses/scripts/S4_Table.Rmd
Remove underscores as they make it difficult to break lines
Manually adjust column widths to fix overfull issues

@@
 
+# Remove underscores
 final_citation_table <- final_citation_table %>% 
-  rename(names_dict)
+  rename(names_dict) |> 
+  mutate(
+    across(!where(is.logical) | !where(is.numeric), 
+      ~str_replace_all(., "_", " ")
+      )
+    )
 ```
@@
   kableExtra::column_spec(column = c(2), width = "4cm") %>%
+   kableExtra::column_spec(column = c(4), width = "3.5cm") %>% 
+    kableExtra::column_spec(column = c(6), width = "1.5cm") %>% 
   kableExtra::landscape()
@@
                 ) %>% 
-  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
+  kableExtra::column_spec(column = c(2, 4), width = "3.3cm") %>% 
+kableExtra::column_spec(column = c(5), width = "2cm") %>% 
   kableExtra::landscape() 
@@
                 ) %>% 
-  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
+  kableExtra::column_spec(column = c(2, 4), width = "3cm") %>% 
   kableExtra::landscape() 
@@
                 ) %>% 
-  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
+  kableExtra::column_spec(column = c(2), width = "3cm") %>%
+   kableExtra::column_spec(column = c(4), width = "8cm") %>%
   kableExtra::landscape() 
@@
                 ) %>% 
-  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
+  kableExtra::column_spec(column = c(2), width = "4cm") %>%
+  kableExtra::column_spec(column = c(3), width = "6cm") %>%
   kableExtra::landscape() 
@@
                 ) %>% 
-  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
+  kableExtra::column_spec(column = c(2), width = "9cm") %>% 
   kableExtra::landscape() 
